### 2022-05-17 _book/thesis.tex
Start with tisemdown

% This a LaTeX thesis template. Most of the work
% for the document class was done by Sam Noble (SN), as well as this
% template. Later comments etc. by Ben Salzberg (BTS). Additional
% restructuring and APA support by Jess Youngberg (JY).
%
% Any line that starts with a percent symbol is a comment.
% They won't show up in the document, and are useful for notes
% to yourself and explaining commands.
% Commenting also removes a line from the document;
% very handy for troubleshooting problems. -BTS

% As far as I know, this follows the requirements laid out in
% the 2002-2003 Senior Handbook. Ask a librarian to check the
% document before binding. -SN

%%
%% Preamble
%%
% \documentclass{<something>} must begin each LaTeX document
\documentclass[12pt,oneside]{tisemthesis}
% Packages are extensions to the basic LaTeX functions. Whatever you
% want to typeset, there is probably a package out there for it.
% Chemistry (chemtex), screenplays, you name it.
% Check out CTAN to see: https://www.ctan.org/
%%
\usepackage{graphicx,latexsym}
\usepackage{amsmath}
\usepackage{amssymb,amsthm}
\usepackage{longtable,booktabs,setspace}
\usepackage{chemarr} %% Useful for one reaction arrow, useless if you're not a chem major
\usepackage[hyphens]{url}
% Added by CII
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{float}
\floatplacement{figure}{H}
% Thanks, @Xyv
\usepackage{calc}
% End of CII addition
\usepackage{rotating}

% Next line commented out by CII
%%% \usepackage{natbib}
% Comment out the natbib line above and uncomment the following two lines to use the new
% biblatex-chicago style, for Chicago A. Also make some changes at the end where the
% bibliography is included.
%\usepackage{biblatex-chicago}
%\bibliography{thesis}

% Added by CII (Thanks, Hadley!)
% Use ref for internal links
\renewcommand{\hyperref}[2][???]{\autoref{#1}}
\def\chapterautorefname{Chapter}
\def\sectionautorefname{Section}
\def\subsectionautorefname{Subsection}
% End of CII addition

% Added by CII
\usepackage{caption}
\captionsetup{width=5in}
% End of CII addition

% \usepackage{times} % other fonts are available like times, bookman, charter, palatino

% Syntax highlighting #22
  \usepackage{color}
  \usepackage{fancyvrb}
  \newcommand{\VerbBar}{|}
  \newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
  % Add ',fontsize=\small' for more characters per line
  \usepackage{framed}
  \definecolor{shadecolor}{RGB}{248,248,248}
  \newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
  \newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
  \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
  \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\BuiltInTok}[1]{#1}
  \newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
  \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
  \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
  \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
  \newcommand{\ExtensionTok}[1]{#1}
  \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
  \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\ImportTok}[1]{#1}
  \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
  \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
  \newcommand{\NormalTok}[1]{#1}
  \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
  \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
  \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
  \newcommand{\RegionMarkerTok}[1]{#1}
  \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
  \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
  \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% To pass between YAML and LaTeX the dollar signs are added by CII
\title{My Title}
\subtitle{My subtitle}
\author{Jiancheng Gu}
\studentnumber{2688643}
% The month and year that you submit your FINAL draft TO THE LIBRARY (May or December)
\date{June 2022}
\supervisor{Professor Dr.~Rene Bekkers}
\cosupervisor{Dr.~Brenda Barber}
\institute{Department of Marketing}
\university{Tilburg University}
\institute{Department of Marketing}
\faculty{Faculty of Social Sciences}
\location{Amsterdam, The Netherlands}
% \division{}
% \advisor{}
% \institution{}
\degree{Master of Science in Societal Resilience (Research)}
%If you have two advisors for some reason, you can use the following
% Uncommented out by CII
% End of CII addition

%%% Remember to use the correct department!
% \department{}
% if you're writing a thesis in an interdisciplinary major,
% uncomment the line below and change the text as appropriate.
% check the Senior Handbook if unsure.
%\thedivisionof{The Established Interdisciplinary Committee for}
% if you want the approval page to say "Approved for the Committee",
% uncomment the next line
%\approvedforthe{Committee}

% Added by CII
%%% Copied from knitr
%% maxwidth is the original width if it's less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

% From {rticles}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
% As noted by @mirh [2] is needed instead of [3] for 2.12
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\renewcommand{\contentsname}{Table of Contents}
% End of CII addition

\setlength{\parskip}{0pt}

% Added by CII

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\Acknowledgements{
I want to thank a few people.
}

\Dedication{

}

\Preface{

}

\Abstract{

}

\ManagementSummary{
There is a max. 1 page management summary.
}

	\linespread{1.25}
 \usepackage[tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in]{geometry}
 \usepackage{titlesec}
 \titleformat{\chapter}[display]{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Large}
 \titlespacing*{\chapter}{0pt}{-20pt}{40pt}
% End of CII addition
%%
%% End Preamble
%%
%
\begin{document}

% Everything below added by CII
  \maketitle

\frontmatter % this stuff will be roman-numbered
\pagestyle{empty} % this removes page numbers from the frontmatter
  \begin{managementsummary}
    There is a max. 1 page management summary.
  \end{managementsummary}
  \begin{acknowledgements}
    I want to thank a few people.
  \end{acknowledgements}

  \hypersetup{linkcolor=black}
  \setcounter{secnumdepth}{2}
  \setcounter{tocdepth}{2}
  \tableofcontents

\mainmatter % here the regular arabic numbering starts
\pagestyle{fancyplain} % turns page numbering back on

\hypertarget{guide}{%
\chapter*{Guide}\label{guide}}
\addcontentsline{toc}{chapter}{Guide}

Welcome to the \emph{R Markdown} thesis template. This template is based on (and in many places copied directly from) university LaTeX templates from a variety of sources, but hopefully it will provide a nicer interface for those that have never used TeX or LaTeX before.\\
Using \emph{R Markdown} will also allow you to easily keep track of your analyses in \textbf{R} chunks of code, with the resulting plots and output included as well.\\
The hope is this \emph{R Markdown} template gets you in the habit of doing reproducible research, which benefits you long-term as a researcher, but also will greatly help anyone that is trying to reproduce or build onto your results down the road.

Hopefully, you won't have much of a learning period to go through and you will reap the benefits of a nicely formatted thesis.\\
The use of LaTeX in combination with \emph{Markdown} is more consistent than the output of a word processor, much less prone to corruption or crashing, and the resulting file is smaller than a Word file. While you may have never had problems using Word in the past, your thesis is likely going to be about twice as large and complex as anything you've written before, taxing Word's capabilities.\\
After working with \emph{Markdown} and \textbf{R} together for a few weeks, we are confident this will be your reporting style of choice going forward.

\textbf{Why use it?}

\emph{R Markdown} creates a simple and straightforward way to interface with the beauty of LaTeX. Packages have been written in \textbf{R} to work directly with LaTeX to produce nicely formatting tables and paragraphs. In addition to creating a user friendly interface to LaTeX, \emph{R Markdown} also allows you to read in your data, to analyze it and to visualize it using \textbf{R} functions, and also to provide the documentation and commentary on the results of your project.\\
Further, it allows for \textbf{R} results to be passed inline to the commentary of your results. You'll see more on this later.

\textbf{Who should use it?}

Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use \emph{R Markdown}. Of particular use should be anyone in the sciences, but the user-friendly nature of \emph{Markdown} and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc. should make it of great benefit to nearly anyone writing a thesis project.

\textbf{For additional help with bookdown}

Please visit \href{https://bookdown.org/yihui/bookdown/}{the free online bookdown reference guide}.

\hypertarget{rmd-basics}{%
\chapter{R Markdown Basics}\label{rmd-basics}}

Here is a brief introduction into using \emph{R Markdown}. \emph{Markdown} is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. \emph{R Markdown} provides the flexibility of \emph{Markdown} with the implementation of \textbf{R} input and output.\\
For more details on using \emph{R Markdown} see \url{https://rmarkdown.rstudio.com}.

Be careful with your spacing in \emph{Markdown} documents.\\
While whitespace largely is ignored, it does at times give \emph{Markdown} signals as to how to proceed.\\
As a habit, try to keep everything left aligned whenever possible, especially as you type a new paragraph.\\
In other words, there is no need to indent basic text in the Rmd document (in fact, it might cause your text to do funny things if you do).
Starting each sentence on a new line is not required, but I have found it makes things easier to version control.

\hypertarget{lists}{%
\section{Lists}\label{lists}}

It's easy to create a list. It can be unordered like
\begin{itemize}
\tightlist
\item
  Item 1
\item
  Item 2
\end{itemize}
or it can be ordered like
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Item 1
\item
  Item 2
\end{enumerate}
Notice that I intentionally mislabeled Item 2 as number 4.
\emph{Markdown} automatically figures this out!\\
You can put any numbers in the list and it will create the list.
Check it out below.

To create a sublist, just indent the values a bit (at least four spaces or a tab).\\
(Here's one case where indentation is key!)
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Item 1
\item
  Item 2
\item
  Item 3
  \begin{itemize}
  \tightlist
  \item
    Item 3a
  \item
    Item 3b
  \end{itemize}
\end{enumerate}
\hypertarget{line-breaks}{%
\section{Line breaks}\label{line-breaks}}

Make sure to add white space between lines if you'd like to start a new paragraph.\\
Look at what happens below in the outputted document if you don't:

Here is the first sentence.\\
Here is another sentence.\\
Here is the last sentence to end the paragraph.
This should be a new paragraph.

\emph{Now for the correct way:}

Here is the first sentence.\\
Here is another sentence.\\
Here is the last sentence to end the paragraph.

This should be a new paragraph.

\hypertarget{r-chunks}{%
\section{R chunks}\label{r-chunks}}

When you click the \textbf{Knit} button above a document will be generated that includes both content as well as the output of any embedded \textbf{R} code chunks within the document.
You can embed an \textbf{R} code chunk like this (\texttt{cars} is a built-in \textbf{R} dataset):
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
     speed           dist       
 Min.   : 4.0   Min.   :  2.00  
 1st Qu.:12.0   1st Qu.: 26.00  
 Median :15.0   Median : 36.00  
 Mean   :15.4   Mean   : 42.98  
 3rd Qu.:19.0   3rd Qu.: 56.00  
 Max.   :25.0   Max.   :120.00  
\end{verbatim}
\hypertarget{inline-code}{%
\section{Inline code}\label{inline-code}}

If you'd like to put the results of your analysis directly into your discussion, add inline code like this:
\begin{quote}
The \texttt{cos} of \(2 \pi\) is 1.
\end{quote}
Another example would be the direct calculation of the standard deviation:
\begin{quote}
The standard deviation of \texttt{speed} in \texttt{cars} is 5.2876444.
\end{quote}
One last neat feature is the use of the \texttt{ifelse} conditional statement which can be used to output text depending on the result of an \textbf{R} calculation:
\begin{quote}
The standard deviation is less than 6.
\end{quote}
Note the use of \texttt{\textgreater{}} here, which signifies a quotation environment that will be indented.

As you see with \texttt{\$2\ \textbackslash{}pi\$} above, mathematics can be added by surrounding the mathematical text with dollar signs.\\
More examples of this are in \protect\hyperlink{math-sci}{Mathematics and Science} if you uncomment the code in \protect\hyperlink{math}{Math}.

\hypertarget{including-plots}{%
\section{Including plots}\label{including-plots}}

You can also embed plots.
For example, here is a way to use the base \textbf{R} graphics package to produce a plot using the built-in \texttt{pressure} dataset:

\includegraphics{thesis_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo=FALSE} parameter was added to the code chunk to prevent printing of the \textbf{R} code that generated the plot.
There are plenty of other ways to add chunk options (like \texttt{fig.height} and \texttt{fig.width} in the chunk above).\\
More information is available at \url{https://yihui.org/knitr/options/}.

Another useful chunk option is the setting of \texttt{cache=TRUE} as you see here.\\
If document rendering becomes time consuming due to long computations or plots that are expensive to generate you can use knitr caching to improve performance.\\
Later in this file, you'll see a way to reference plots created in \textbf{R} or external figures.

\hypertarget{loading-and-exploring-data}{%
\section{Loading and exploring data}\label{loading-and-exploring-data}}

Included in this template is a file called \texttt{flights.csv}.\\
This file includes a subset of the larger dataset of information about all flights that departed from Seattle and Portland in 2014.
More information about this dataset and its \textbf{R} package is available at \url{https://github.com/ismayc/pnwflights14}.
This subset includes only Portland flights and only rows that were complete with no missing values.
Merges were also done with the \texttt{airports} and \texttt{airlines} data sets in the \texttt{pnwflights14} package to get more descriptive airport and airline names.

We can load in this data set using the following commands:
\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# flights.csv is in the data directory}
\NormalTok{flights\_path }\OtherTok{\textless{}{-}}\NormalTok{ here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"flights.csv"}\NormalTok{)}
\CommentTok{\# string columns will be read in as strings and not factors now}
\NormalTok{flights }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(flights\_path, }\AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
The data is now stored in the data frame called \texttt{flights} in \textbf{R}.\\
To get a better feel for the variables included in this dataset we can use a variety of functions.
Here we can see the dimensions (rows by columns) and also the names of the columns.
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{dim}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
[1] 12649    16
\end{verbatim}
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{names}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
 [1] "month"        "day"          "dep_time"     "dep_delay"    "arr_time"    
 [6] "arr_delay"    "carrier"      "tailnum"      "flight"       "dest"        
[11] "air_time"     "distance"     "hour"         "minute"       "carrier_name"
[16] "dest_name"   
\end{verbatim}
Another good idea is to take a look at the dataset in table form. With this dataset having more than 20,000 rows, we won't explicitly show the results of the command here.
I recommend you enter the command into the Console \textbf{\emph{after}} you have run the \textbf{R} chunks above to load the data into \textbf{R}.
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{View}\NormalTok{(flights)}
\end{Highlighting}
\end{Shaded}
While not required, it is highly recommended you use the \texttt{dplyr} package to manipulate and summarize your data set as needed.\\
It uses a syntax that is easy to understand using chaining operations.\\
Below I've created a few examples of using \texttt{dplyr} to get information about the Portland flights in 2014.\\
You will also see the use of the \texttt{ggplot2} package, which produces beautiful, high-quality academic visuals.

We begin by checking to ensure that needed packages are installed and then we load them into our current working environment:
\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# List of packages required for this analysis}
\NormalTok{pkg }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{, }\StringTok{"ggplot2"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"bookdown"}\NormalTok{)}
\CommentTok{\# Check if packages are not installed and assign the}
\CommentTok{\# names of the packages not installed to the variable new.pkg}
\NormalTok{new.pkg }\OtherTok{\textless{}{-}}\NormalTok{ pkg[}\SpecialCharTok{!}\NormalTok{(pkg }\SpecialCharTok{\%in\%} \FunctionTok{installed.packages}\NormalTok{())]}
\CommentTok{\# If there are any packages in the list that aren\textquotesingle{}t installed,}
\CommentTok{\# install them}
\ControlFlowTok{if}\NormalTok{ (}\FunctionTok{length}\NormalTok{(new.pkg)) \{}
  \FunctionTok{install.packages}\NormalTok{(new.pkg, }\AttributeTok{repos =} \StringTok{"https://cran.rstudio.com"}\NormalTok{)}
\NormalTok{\}}
\CommentTok{\# Load packages}
\FunctionTok{library}\NormalTok{(tisemdown)}
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(knitr)}
\end{Highlighting}
\end{Shaded}
\clearpage

The example we show here does the following:
\begin{itemize}
\item
  Selects only the \texttt{carrier\_name} and \texttt{arr\_delay} from the \texttt{flights} dataset and then assigns this subset to a new variable called \texttt{flights2}.
\item
  Using \texttt{flights2}, we determine the largest arrival delay for each of the carriers.
\end{itemize}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights2 }\OtherTok{\textless{}{-}}\NormalTok{ flights }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(carrier\_name, arr\_delay)}
\NormalTok{max\_delays }\OtherTok{\textless{}{-}}\NormalTok{ flights2 }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(carrier\_name) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{max\_arr\_delay =} \FunctionTok{max}\NormalTok{(arr\_delay, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{))}
\end{Highlighting}
\end{Shaded}
A useful function in the \texttt{knitr} package for making nice tables in \emph{R Markdown} is called \texttt{kable}.\\
It is much easier to use than manually entering values into a table by copying and pasting values into Excel or LaTeX.\\
This again goes to show how nice reproducible documents can be! (Note the use of \texttt{results="asis"}, which will produce the table instead of the code to create the table.)\\
The \texttt{caption.short} argument is used to include a shorter title to appear in the List of Tables.
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{kable}\NormalTok{(max\_delays,}
  \AttributeTok{col.names =} \FunctionTok{c}\NormalTok{(}\StringTok{"Airline"}\NormalTok{, }\StringTok{"Max Arrival Delay"}\NormalTok{),}
  \AttributeTok{caption =} \StringTok{"Maximum Delays by Airline"}\NormalTok{,}
  \AttributeTok{caption.short =} \StringTok{"Max Delays by Airline"}\NormalTok{,}
  \AttributeTok{longtable =} \ConstantTok{TRUE}\NormalTok{,}
  \AttributeTok{booktabs =} \ConstantTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{longtable}[t]{lr}
\caption[Max Delays by Airline]{\label{tab:maxdelays}Maximum Delays by Airline}\\
\toprule
Airline & Max Arrival Delay\\
\midrule
Alaska Airlines Inc. & 338\\
American Airlines Inc. & 1539\\
Delta Air Lines Inc. & 371\\
Frontier Airlines Inc. & 166\\
Hawaiian Airlines Inc. & 116\\
\addlinespace
JetBlue Airways & 256\\
SkyWest Airlines Inc. & 321\\
Southwest Airlines Co. & 315\\
United Air Lines Inc. & 319\\
US Airways Inc. & 347\\
\addlinespace
Virgin America & 366\\
\bottomrule
\end{longtable}
The last two options make the table a little easier-to-read.

We can further look into the properties of the largest value here for American Airlines Inc.\\
To do so, we can isolate the row corresponding to the arrival delay of 1539 minutes for American in our original \texttt{flights} dataset.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(}
\NormalTok{    arr\_delay }\SpecialCharTok{==} \DecValTok{1539}\NormalTok{,}
\NormalTok{    carrier\_name }\SpecialCharTok{==} \StringTok{"American Airlines Inc."}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\FunctionTok{c}\NormalTok{(}
\NormalTok{    month, day, carrier, dest\_name, hour,}
\NormalTok{    minute, carrier\_name, arr\_delay}
\NormalTok{  ))}
\end{Highlighting}
\end{Shaded}
\begin{verbatim}
  dep_time dep_delay arr_time tailnum flight dest air_time distance
1     1403      1553     1934  N595AA   1568  DFW      182     1616
\end{verbatim}
We see that the flight occurred on March 3rd and departed a little after 2 PM on its way to Dallas/Fort Worth.\\
Lastly, we show how we can visualize the arrival delay of all departing flights from Portland on March 3rd against time of departure.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{flights }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(month }\SpecialCharTok{==} \DecValTok{3}\NormalTok{, day }\SpecialCharTok{==} \DecValTok{3}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ dep\_time, }\AttributeTok{y =}\NormalTok{ arr\_delay)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}
\includegraphics{thesis_files/figure-latex/march3plot-1.pdf}

\hypertarget{additional-resources}{%
\section{Additional resources}\label{additional-resources}}
\begin{itemize}
\item
  \emph{Markdown} Cheatsheet - \url{https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet}
\item
  \emph{R Markdown}
  \begin{itemize}
  \tightlist
  \item
    Reference Guide - \url{https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}
  \item
    Cheatsheet - \url{https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf}
  \end{itemize}
\item
  \emph{RStudio IDE}
  \begin{itemize}
  \tightlist
  \item
    Cheatsheet - \url{https://github.com/rstudio/cheatsheets/raw/master/rstudio-ide.pdf}
  \item
    Official website - \url{https://rstudio.com/products/rstudio/}
  \end{itemize}
\item
  Introduction to \texttt{dplyr} - \url{https://cran.rstudio.com/web/packages/dplyr/vignettes/dplyr.html}
\item
  \texttt{ggplot2}
  \begin{itemize}
  \tightlist
  \item
    Documentation - \url{https://ggplot2.tidyverse.org/}
  \item
    Cheatsheet - \url{https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf}
  \end{itemize}
\end{itemize}
\hypertarget{math-sci}{%
\chapter{Mathematics and Science}\label{math-sci}}

\hypertarget{math}{%
\section{Math}\label{math}}

\TeX~is the best way to typeset mathematics.
Donald Knuth designed \TeX~when he got frustrated at how long it was taking the typesetters to finish his book, which contained a lot of mathematics.\\
One nice feature of \emph{R Markdown} is its ability to read LaTeX code directly.

If you are doing a thesis that will involve lots of math, you will want to read the following section which has been commented out.
If you're not going to use math, skip over or delete this next commented section.

Some example equations so you get a sense of what to do:

\[\sum_{j=1}^n (\delta\theta_j)^2 \leq {{\beta_i^2}\over{\delta_i^2 + \rho_i^2}}
\left[ 2\rho_i^2 + {\delta_i^2\beta_i^2\over{\delta_i^2 + \rho_i^2}} \right] \equiv \omega_i^2
\]

From Informational Dynamics, we have the following (Dave Braden):

After \emph{n} such encounters the posterior density for \(\theta\) is

\[
\pi(\theta|X_1< y_1,\dots,X_n<y_n) \varpropto \pi(\theta) \prod_{i=1}^n\int_{-\infty}^{y_i}
   \exp\left(-{(x-\theta)^2\over{2\sigma^2}}\right)\ dx
\]

Another equation:

\[\det\left|\,\begin{matrix}%
c_0&c_1\hfill&c_2\hfill&\ldots&c_n\hfill\cr
c_1&c_2\hfill&c_3\hfill&\ldots&c_{n+1}\hfill\cr
c_2&c_3\hfill&c_4\hfill&\ldots&c_{n+2}\hfill\cr
\,\vdots\hfill&\,\vdots\hfill&
  \,\vdots\hfill&&\,\vdots\hfill\cr
c_n&c_{n+1}\hfill&c_{n+2}\hfill&\ldots&c_{2n}\hfill\cr
\end{matrix}\right|>0\]
Lapidus and Pindar, Numerical Solution of Partial Differential Equations in Science and
Engineering. Page 54

\[
\int_t\left\{\sum_{j=1}^3 T_j \left({d\phi_j\over dt}+k\phi_j\right)-kT_e\right\}w_i(t)\ dt=0,
   \qquad\quad i=1,2,3.
\]

L\&P Galerkin method weighting functions. Page 55

\[
\sum_{j=1}^3 T_j\int_0^1\left\{{d\phi_j\over dt} + k\phi_j\right\} \phi_i\ dt
   = \int_{0}^1k\,T_e\phi_idt, \qquad i=1,2,3 \]

Another L\&P (p145)

\[
\int_{-1}^1\!\int_{-1}^1\!\int_{-1}^1 f\big(\xi,\eta,\zeta\big)
   = \sum_{k=1}^n\sum_{j=1}^n\sum_{i=1}^n w_i w_j w_k f\big( \xi,\eta,\zeta\big).
\]

Another L\&P (p126)

\[
\int_{A_e} (\,\cdot\,) dx dy = \int_{-1}^1\!\int_{-1}^1 (\,\cdot\,) \det[J] d\xi d\eta.
\]

\hypertarget{ref-labels}{%
\chapter{Graphics, References, and Labels}\label{ref-labels}}

\hypertarget{figures}{%
\section{Figures}\label{figures}}

If your thesis has a lot of figures, \emph{R Markdown} might behave better for you than that other word processor.\\
One perk is that it will automatically number the figures accordingly in each chapter.\\
You'll also be able to create a label for each figure, add a caption, and then reference the figure in a way similar to what we saw with tables earlier.\\
If you label your figures, you can move the figures around and \emph{R Markdown} will automatically adjust the numbering for you. No need for you to remember!\\
So that you don't have to get too far into LaTeX to do this, a couple \textbf{R} functions have been created for you to assist. You'll see their use below.

In the \textbf{R} chunk below, we will load in a picture stored as \texttt{tilburg\_color.png} in the figures subdirectory.\\
We then give it the caption of ``Tilburg logo'', the label of ``tilburglogo'', and specify that this is a figure.\\
Make note of the different \textbf{R} chunk options that are given in the R Markdown file (not shown in the knitted document).
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{include\_graphics}\NormalTok{(}\AttributeTok{path =} \StringTok{"figure/tilburg\_color.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{figure}

{\centering \includegraphics[width=0.45\linewidth]{figure/tilburg_color}

}

\caption{Tilburg logo}\label{fig:tilburglogo}
\end{figure}
Here is a reference to the Tilburg logo: Figure \ref{fig:tilburglogo}.\\
Note the use of the \texttt{fig:} code here. By naming the \textbf{R} chunk that contains the figure, we can then reference that figure later as done in the first sentence here.\\
We can also specify the caption for the figure via the R chunk option \texttt{fig.cap}.

\clearpage

Below we will investigate how to save the output of an \textbf{R} plot and label it in a way similar to that done above.\\
Recall the \texttt{flights} dataset from Chapter \ref{rmd-basics}. (Note that we've shown a different way to reference a section or chapter here.)\\
We will next explore a bar graph with the mean flight departure delays by airline from Portland for 2014.
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mean\_delay\_by\_carrier }\OtherTok{\textless{}{-}}\NormalTok{ flights }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(carrier) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{mean\_dep\_delay =} \FunctionTok{mean}\NormalTok{(dep\_delay))}
\FunctionTok{ggplot}\NormalTok{(mean\_delay\_by\_carrier, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ carrier, }\AttributeTok{y =}\NormalTok{ mean\_dep\_delay)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{fill =} \StringTok{"red"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\begin{figure}
\centering
\includegraphics{thesis_files/figure-latex/delaysboxplot-1.pdf}
\caption{\label{fig:delaysboxplot}Mean Delays by Airline}
\end{figure}
Here is a reference to this image: Figure \ref{fig:delaysboxplot}.

A table linking these carrier codes to airline names is available at \url{https://github.com/ismayc/pnwflights14/blob/master/data/airlines.csv}.

\clearpage

Next, we will explore the use of the \texttt{out.extra} chunk option, which can be used to shrink or expand an image loaded from a file by specifying \texttt{"scale=\ "}.
Here we use the mathematical graph stored in the ``subdivision.pdf'' file.
\begin{figure}
\includegraphics[scale=0.75]{figure/subdivision} \caption{Subdiv. graph}\label{fig:subd}
\end{figure}
Here is a reference to this image: Figure \ref{fig:subd}.\\
Note that \texttt{echo=FALSE} is specified so that the \textbf{R} code is hidden in the document.

\textbf{More Figure Stuff}

Lastly, we will explore how to rotate and enlarge figures using the \texttt{out.extra} chunk option.\\
(Currently this only works in the PDF version of the book.)
\begin{figure}
\includegraphics[angle=180, scale=1.1]{figure/subdivision} \caption{A Larger Figure, Flipped Upside Down}\label{fig:subd2}
\end{figure}
As another example, here is a reference: Figure \ref{fig:subd2}.

\hypertarget{footnotes-and-endnotes}{%
\section{Footnotes and Endnotes}\label{footnotes-and-endnotes}}

You might want to footnote something.\footnote{footnote text}
The footnote will be in a smaller font and placed appropriately. Endnotes work in much the same way.

\hypertarget{bibliographies}{%
\section{Bibliographies}\label{bibliographies}}

Of course you will need to cite things, and you will probably accumulate an armful of sources.
There are a variety of tools available for creating a bibliography database (stored with the .bib extension).\\
In addition to BibTeX suggested below, you may want to consider using the free and easy-to-use tool called Zotero.

\emph{R Markdown} uses \emph{pandoc} (\url{https://pandoc.org/}) to build its bibliographies.\\
One nice caveat of this is that you won't have to do a second compile to load in references as standard LaTeX requires.
To cite references in your thesis (after creating your bibliography database), place the reference name inside square brackets and precede it by the ``at'' symbol.\\
For example, here's a reference to a book about worrying: (Molina \& Borkovec, 1994).\\
This \texttt{Molina1994} entry appears in a file called \texttt{thesis.bib} in the \texttt{bib} folder.\\
This bibliography database file was created by a program called BibTeX.\\
You can call this file something else if you like (look at the YAML header in the main .Rmd file) and, by default, is to placed in the \texttt{bib} folder.

If you look at the YAML header at the top of the main .Rmd file you can see that we can specify the style of the bibliography by referencing the appropriate csl file.\\
You can download a variety of different style files at \url{https://www.zotero.org/styles}.\\
Make sure to download the file into the csl folder.

\vfill

\textbf{Tips for Bibliographies}
\begin{itemize}
\tightlist
\item
  Like with thesis formatting, the sooner you start compiling your bibliography for something as large as thesis, the better. Typing in source after source is mind-numbing enough; do you really want to do it for hours on end in late April? Think of it as procrastination.
\item
  The cite key (a citation's label) needs to be unique from the other entries.
\item
  When you have more than one author or editor, you need to separate each author's name by the word ``and'' e.g.~\texttt{Author\ =\ \{Noble,\ Sam\ and\ Youngberg,\ Jessica\},}.
\item
  Bibliographies made using BibTeX (whether manually or using a manager) accept LaTeX markup, so you can italicize and add symbols as necessary.
\item
  To force capitalization in an article title or where all lowercase is generally used, bracket the capital letter in curly braces.
\end{itemize}
\hypertarget{anything-else}{%
\section{Anything else?}\label{anything-else}}

If you'd like to see examples of other things in this template, please contact the Lachlan Deer (email \href{mailto:lachlan.deer@gmail.com}{\nolinkurl{lachlan.deer@gmail.com}})
We love to see people using \emph{R Markdown} for their theses, and are happy to help.

\hypertarget{conclusion}{%
\chapter*{Conclusion}\label{conclusion}}
\addcontentsline{toc}{chapter}{Conclusion}

If we don't want Conclusion to have a chapter number next to it, we can add the \texttt{\{-\}} attribute.

\textbf{More info}

And here's some other random info: the first paragraph after a chapter title or section head \emph{shouldn't be} indented, because indents are to tell the reader that you're starting a new paragraph.
Since that's obvious after a chapter or section title, proper typesetting doesn't add an indent there.

\appendix

\hypertarget{the-first-appendix}{%
\chapter{The First Appendix}\label{the-first-appendix}}

This first appendix includes all of the R chunks of code that were hidden throughout the document (using the \texttt{include\ =\ FALSE} chunk tag) to help with readibility and/or setup.

\textbf{In the main Rmd file}

\textbf{In Chapter \ref{ref-labels}:}
\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(knitr)}
\NormalTok{flights }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"data/flights.csv"}\NormalTok{, }\AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
\hypertarget{the-second-appendix-for-fun}{%
\chapter{The Second Appendix, for Fun}\label{the-second-appendix-for-fun}}

\backmatter

\hypertarget{references}{%
\chapter*{References}\label{references}}
\addcontentsline{toc}{chapter}{References}

\markboth{References}{References}

\noindent

\setlength{\parindent}{-0.20in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-angel2000}{}}%
Angel, E. (2000). \emph{Interactive computer graphics : A top-down approach with OpenGL}. Boston, MA: Addison Wesley Longman.

\leavevmode\vadjust pre{\hypertarget{ref-angel2001}{}}%
Angel, E. (2001a). \emph{Batch-file computer graphics : A bottom-up approach with QuickTime}. Boston, MA: Wesley Addison Longman.

\leavevmode\vadjust pre{\hypertarget{ref-angel2002a}{}}%
Angel, E. (2001b). \emph{Test second book by angel}. Boston, MA: Wesley Addison Longman.

\leavevmode\vadjust pre{\hypertarget{ref-Molina1994}{}}%
Molina, S. T., \& Borkovec, T. D. (1994). The {P}enn {S}tate worry questionnaire: Psychometric properties and associated characteristics. In G. C. L. Davey \& F. Tallis (Eds.), \emph{Worrying: Perspectives on theory, assessment and treatment} (pp. 265--283). New York: Wiley.

\end{CSLReferences}

% Index?

\end{document}

### 2022-05-17 data/Gu-thesis-script.Rmd
Start with tisemdown

---
title: "Effect of Parental Absence on Adolescents' Academic Performance"
output: html_notebook
---

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
```

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
```

Remove wave 1's observations of grade 9; they were not followed up in wave 2
```{r}
d_stu1 <- d_stu1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, sweight, grade9))
d_stu2 <- d_stu2 %>% 
  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
d_par1 <- d_par1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, grade9))
```

Assemble a panel dataset in wide format
```{r}
d_1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
d_2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- d_1 %>% right_join(d_2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #children's age at baseline
  local.resi = age - a07 #years of residence at the current county05
)
```

Sample
```{r}
d_cl <- d %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
  filter(local.resi>=5)
```

## Variables 
Compute standardized exam grades (within-school z-scores)
```{r}
d_cl <- d_cl %>% #Total exam grades at wave 1 and at wave 2
  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
         w2ttl = w2chn + w2mat + w2eng) 
d_cl <- d_cl %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_std = as.numeric(scale(tr_chn)),
         w1mat_std = as.numeric(scale(tr_mat)),
         w1eng_std = as.numeric(scale(tr_eng)),
         w1ttl_std = as.numeric(scale(w1ttl)),
         w2chn_std = as.numeric(scale(w2chn)),
         w2mat_std = as.numeric(scale(w2mat)),
         w2eng_std = as.numeric(scale(w2eng)),
         w2ttl_std = as.numeric(scale(w2ttl))
         ) %>% ungroup()
```

Dependent variables: Outcome differences between wave 2 and wave 1
```{r}
d_cl <- d_cl %>% mutate(
  chn_std = w2chn_std - w1chn_std,
  mat_std = w2mat_std - w1mat_std,
  eng_std = w2eng_std - w1eng_std,
  ttl_std = w2ttl_std - w1ttl_std,
  cog = w2cog3pl - cog3pl #Cognitive test score, standardized
) %>%
  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
```

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         is.girl = if_else(a01 == 2, 1, 0), #student is girl
         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         is.only.child = if_else(b01 == 1, 1, 0), #student is only child
         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
         is.fa.mid.sch = if_else(b07 != 1 & b07 != 2, 1, 0), #father finished junior high school
         is.mo.mid.sch = if_else(b06 != 1 & b06 != 2, 1, 0) #mother finished junior high school
) %>% drop_na(
  is.girl, is.rural, is.only.child, is.boarding, is.fa.mid.sch, is.mo.mid.sch)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  treat_leave = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  treat_fa_only = NA,
  treat_mo_only = NA,
  treat_both = NA
  )
```

Only mother migrated
```{r}
d_cl$treat_mo_only[d_cl$treat_leave == 0] <- 0
d_cl$treat_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
```

Mother migrated
```{r}
d_cl$treat_mo[d_cl$treat_leave == 0] <- 0
d_cl$treat_mo[d_cl$w2ba0202==0] <- 1
```

Only father migrated
```{r}
d_cl$treat_fa_only[d_cl$treat_leave == 0] <- 0
d_cl$treat_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
```

Father migrated
```{r}
d_cl$treat_fa[d_cl$treat_leave == 0] <- 0
d_cl$treat_fa[d_cl$w2ba0201==0] <- 1
```

Both parents migrated
```{r}
d_cl$treat_both[d_cl$treat_leave == 0] <- 0
d_cl$treat_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
```

## Descriptive statistics
```{r}
des_gender <- d_cl %>% count(is.girl)
des_rural <- d_cl %>% count(is.rural)
des_only.child <- d_cl %>% count(is.only.child)
des_boarding <- d_cl %>% count(is.boarding)
des_fa.mid.sch <- d_cl %>% count(is.fa.mid.sch)
des_mo.mid.sch <- d_cl %>% count(is.mo.mid.sch)
des_gender
des_rural
des_only.child
des_boarding
des_fa.mid.sch
des_mo.mid.sch
```

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(treat_leave) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(treat_leave) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(treat_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

## DID basic
Regressing on cognitive test score (standardized)
```{r}
did_cog <- feols(cog ~ treat_leave | schids + ctyids, data = d_cl) 
did_cog_m_only <- feols(cog ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_cog_m <- feols(cog ~ treat_mo | schids + ctyids, data = d_cl) 
did_cog_f_only <- feols(cog ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_cog_f <- feols(cog ~ treat_fa | schids + ctyids, data = d_cl) 
did_cog_both <- feols(cog ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f,
did_cog_f_only,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_ttl <- feols(ttl_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_ttl_m_only <- feols(ttl_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_ttl_m <- feols(ttl_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_ttl_f <- feols(ttl_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_ttl_f_only <- feols(ttl_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_ttl_both <- feols(ttl_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f,
did_ttl_f_only,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_chn <- feols(chn_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_chn_m_only <- feols(chn_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_chn_m <- feols(chn_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_chn_f_only <- feols(chn_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_chn_f <- feols(chn_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_chn_both <- feols(chn_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f,
did_chn_f_only,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_mat <- feols(mat_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_mat_m_only <- feols(mat_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_mat_m <- feols(mat_std ~ treat_mo | schids + ctyids, data = d_cl) 
did_mat_f_only <- feols(mat_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_mat_f <- feols(mat_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_mat_both <- feols(mat_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f,
did_mat_f_only,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_eng <- feols(eng_std ~ treat_leave | schids + ctyids, data = d_cl) 
did_eng_m <- feols(eng_std ~ treat_mo | schids + ctyids, data = d_cl)
did_eng_m_only <- feols(eng_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
did_eng_f <- feols(eng_std ~ treat_fa | schids + ctyids, data = d_cl) 
did_eng_f_only <- feols(eng_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
did_eng_both <- feols(eng_std ~ treat_both | schids + ctyids, data = d_cl)
```
Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f,
did_eng_f_only,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

## DID unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog ~ treat_leave + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_m_only <- feols(cog ~ treat_mo_only + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_m <- feols(cog ~ treat_mo + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_f_only <- feols(cog ~ treat_fa_only + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_f <- feols(cog ~ treat_fa + cog3pl | schids + ctyids, data = d_cl) 
did_unres_cog_both <- feols(cog ~ treat_both + cog3pl | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f,
did_unres_cog_f_only,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_unres_ttl <- feols(ttl_std ~ treat_leave + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_m_only <- feols(ttl_std ~ treat_mo_only + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_m <- feols(ttl_std ~ treat_mo + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_f <- feols(ttl_std ~ treat_fa + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_f_only <- feols(ttl_std ~ treat_fa_only + w1ttl_std | schids + ctyids, data = d_cl) 
did_unres_ttl_both <- feols(ttl_std ~ treat_both + w1ttl_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f,
did_unres_ttl_f_only,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_std ~ treat_leave + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_m_only <- feols(chn_std ~ treat_mo_only + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_m <- feols(chn_std ~ treat_mo + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_f_only <- feols(chn_std ~ treat_fa_only + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_f <- feols(chn_std ~ treat_fa + w1chn_std | schids + ctyids, data = d_cl) 
did_unres_chn_both <- feols(chn_std ~ treat_both + w1chn_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f,
did_unres_chn_f_only,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_std ~ treat_leave + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_m_only <- feols(mat_std ~ treat_mo_only + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_m <- feols(mat_std ~ treat_mo + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_f_only <- feols(mat_std ~ treat_fa_only + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_f <- feols(mat_std ~ treat_fa + w1mat_std | schids + ctyids, data = d_cl) 
did_unres_mat_both <- feols(mat_std ~ treat_both + w1mat_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f,
did_unres_mat_f_only,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_std ~ treat_leave + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_m <- feols(eng_std ~ treat_mo + w1eng_std | schids + ctyids, data = d_cl)
did_unres_eng_m_only <- feols(eng_std ~ treat_mo_only + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_f <- feols(eng_std ~ treat_fa + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_f_only <- feols(eng_std ~ treat_fa_only + w1eng_std | schids + ctyids, data = d_cl) 
did_unres_eng_both <- feols(eng_std ~ treat_both + w1eng_std | schids + ctyids, data = d_cl)
```
Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f,
did_unres_eng_f_only,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

## DID adjusted
Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ treat_leave + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_cog <- list(
did_adj_cog,
did_adj_cog_m_only,
did_adj_cog_m,
did_adj_cog_f,
did_adj_cog_f_only,
did_adj_cog_both) 
models_adj_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_ttl <- list(
did_adj_ttl,
did_adj_ttl_m_only,
did_adj_ttl_m,
did_adj_ttl_f,
did_adj_ttl_f_only,
did_adj_ttl_both) 
models_adj_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_chn <- list(
did_adj_chn,
did_adj_chn_m_only,
did_adj_chn_m,
did_adj_chn_f,
did_adj_chn_f_only,
did_adj_chn_both) 
models_adj_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_mat <- list(
did_adj_mat,
did_adj_mat_m_only,
did_adj_mat_m,
did_adj_mat_f,
did_adj_mat_f_only,
did_adj_mat_both) 
models_adj_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ treat_leave + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ treat_mo + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ treat_mo_only + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ treat_fa + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ treat_fa_only + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ treat_both + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_eng <- list(
did_adj_eng,
did_adj_eng_m_only,
did_adj_eng_m,
did_adj_eng_f,
did_adj_eng_f_only,
did_adj_eng_both) 
models_adj_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

## DID adjusted unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ treat_leave + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ treat_mo_only + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ treat_mo + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ treat_fa_only + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ treat_fa + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ treat_both + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f,
did_adj_unres_cog_f_only,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ treat_leave + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ treat_mo_only + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ treat_mo + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ treat_fa + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ treat_fa_only + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ treat_both + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ treat_leave + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ treat_mo_only + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ treat_mo + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ treat_fa_only + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ treat_fa + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ treat_both + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
did_adj_unres_chn,
did_adj_unres_chn_m_only,
did_adj_unres_chn_m,
did_adj_unres_chn_f,
did_adj_unres_chn_f_only,
did_adj_unres_chn_both) 
models_adj_unres_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ treat_leave + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ treat_mo_only + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ treat_mo + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ treat_fa_only + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ treat_fa + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ treat_both + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
```
Results
```{r}
models_mat_adj_unres <- list(
did_adj_unres_mat,
did_adj_unres_mat_m_only,
did_adj_unres_mat_m,
did_adj_unres_mat_f,
did_adj_unres_mat_f_only,
did_adj_unres_mat_both) 
models_mat_adj_unres %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

Regressing on English score
```{r}
did_adj_unres_eng <- feols(eng_std ~ treat_leave + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_unres_eng_m <- feols(eng_std ~ treat_mo + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
did_adj_unres_eng_m_only <- feols(eng_std ~ treat_mo_only + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_unres_eng_f <- feols(eng_std ~ treat_fa + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_unres_eng_f_only <- feols(eng_std ~ treat_fa_only + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
did_adj_unres_eng_both <- feols(eng_std ~ treat_both + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
```
Results
```{r}
models_adj_unres_eng <- list(
did_adj_unres_eng,
did_adj_unres_eng_m_only,
did_adj_unres_eng_m,
did_adj_unres_eng_f,
did_adj_unres_eng_f_only,
did_adj_unres_eng_both) 
models_adj_unres_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
```

### 2022-05-17 index.Rmd
Start with tisemdown

---
title: "My Title"
subtitle: "My subtitle"
author: "Jiancheng Gu"
studentnumber: "2688643"
supervisor: "Professor Dr. Rene Bekkers"
#cosupervisor: "Dr. Brenda Barber"
degree: 'Master of Science in Societal Resilience (Research)'
university: "Vrije Universiteit Amsterdam"
#institute: "Department of Marketing"
faculty: "Faculty of Social Sciences"
location: "Amsterdam, The Netherlands"
date: "June 2022"

knit: bookdown::render_book
site: bookdown::bookdown_site

# The next two lines allow you to change the spacing in your thesis. You can 
# switch out \onehalfspacing with \singlespacing or \doublespacing, if desired.
header-includes:
    - \linespread{1.25}
    - \usepackage[tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in]{geometry}
    - \usepackage{titlesec}
    - \titleformat{\chapter}[display]{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Large}
    - \titlespacing*{\chapter}{0pt}{-20pt}{40pt}

# This will automatically install the {remotes} package and {tisemdown}
# Change this to FALSE if you'd like to install them manually on your own.
params:
  'Install needed packages for {tisemdown}': True

# Remove the hashtag to specify which version of output you would like.
# Can only choose one at a time.
output:
  tisemdown::thesis_pdf: default 
#  tisemdown::thesis_gitbook: default         
#  tisemdown::thesis_word: default
#  tisemdown::thesis_epub: default

# If you are creating a PDF you'll need to write your preliminary content 
# (e.g., abstract, acknowledgements) below or use code similar to line 25-26 
# for the .RMD files. If you are NOT producing a PDF, delete or silence
# lines 25-39 in this YAML header.
abstract: '`r if(knitr:::is_latex_output()) paste(readLines(here::here("prelims", "00-abstract.Rmd")), collapse = "\n  ")`'
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab 
# is needed on the line after the `|`.
#managementsummary: '`r if(knitr:::is_latex_output()) paste(readLines(here::here("prelims", "00-managementsummary.Rmd")), collapse = "\n  ")`'

acknowledgements: |
  I want to thank a few people.
# dedication: |
#   You can have a dedication here if you wish. 
# preface: |
#   This is an example of a thesis setup to use the TiSEM thesis document class 
#   (for LaTeX) and the R bookdown package, in general.

# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
# list of tabs?
lot: false
# list of figs?
lof: false
---

```{=html}
<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of 
metadata used to produce the document.  Be careful with spacing in this header!

If you'd prefer to not include a Dedication, for example, simply delete the section entirely, or silence them (add # before each line).

If you have other LaTeX packages you would like to include, delete the # before header-includes and list the packages after hyphens on new lines.

If you'd like to include a comment that won't be produced in your resulting file enclose it in a block like this.

If you receive a duplicate label error after knitting, make sure to delete the index.Rmd file and then knit again.
-->
```
```{=html}
<!--
The acknowledgments, preface, dedication, and abstract are added into the PDF
version automatically by inputting them in the YAML at the top of this file.
Alternatively, you can put that content in files like 00--prelim.Rmd and
00-abstract.Rmd like done below.
-->
```
```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00-managementsummary.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00--prelim.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00-abstract.Rmd")}

```

```{=html}
<!-- The {.unnumbered} option here means that the introduction will be 
"Chapter 0." You can also use {-} for no numbers on chapters.
For your own thesis you should delete everything below this comment.
-->
```
# Guide {.unnumbered}

Welcome to the *R Markdown* thesis template. This template is based on (and in many places copied directly from) university LaTeX templates from a variety of sources, but hopefully it will provide a nicer interface for those that have never used TeX or LaTeX before.\
Using *R Markdown* will also allow you to easily keep track of your analyses in **R** chunks of code, with the resulting plots and output included as well.\
The hope is this *R Markdown* template gets you in the habit of doing reproducible research, which benefits you long-term as a researcher, but also will greatly help anyone that is trying to reproduce or build onto your results down the road.

Hopefully, you won't have much of a learning period to go through and you will reap the benefits of a nicely formatted thesis.\
The use of LaTeX in combination with *Markdown* is more consistent than the output of a word processor, much less prone to corruption or crashing, and the resulting file is smaller than a Word file. While you may have never had problems using Word in the past, your thesis is likely going to be about twice as large and complex as anything you've written before, taxing Word's capabilities.\
After working with *Markdown* and **R** together for a few weeks, we are confident this will be your reporting style of choice going forward.

```{=html}
<!-- 
If you're still on the fence about using _R Markdown_, check out the resource
for newbies available at <https://rbasics.netlify.com>. 
-->
```
**Why use it?**

*R Markdown* creates a simple and straightforward way to interface with the beauty of LaTeX. Packages have been written in **R** to work directly with LaTeX to produce nicely formatting tables and paragraphs. In addition to creating a user friendly interface to LaTeX, *R Markdown* also allows you to read in your data, to analyze it and to visualize it using **R** functions, and also to provide the documentation and commentary on the results of your project.\
Further, it allows for **R** results to be passed inline to the commentary of your results. You'll see more on this later.

```{=html}
<!-- 
Having your code and commentary all together in one place has a plethora of 
benefits!
-->
```
**Who should use it?**

Anyone who needs to use data analysis, math, tables, a lot of figures, complex cross-references, or who just cares about the final appearance of their document should use *R Markdown*. Of particular use should be anyone in the sciences, but the user-friendly nature of *Markdown* and its ability to keep track of and easily include figures, automatically generate a table of contents, index, references, table of figures, etc. should make it of great benefit to nearly anyone writing a thesis project.

**For additional help with bookdown**

Please visit [the free online bookdown reference guide](https://bookdown.org/yihui/bookdown/).

### 2022-05-20 data/Gu-thesis-script.Rmd
z-score calculation before sampling; sampling children with 7 years or longer local residency

@@
 ---
-title: "Effect of Parental Absence on Adolescents' Academic Performance"
+title: "Parental migration, cognitive development and educational performance"
 output: html_notebook
@@
 d <- d %>% mutate(
-  age = 2013 - a02a, #children's age at baseline
+  age = 2014 - a02a, #children's age at baseline
   local.resi = age - a07 #years of residence at the current county05
@@
 
-Sample
-```{r}
-d_cl <- d %>% 
-  filter(w2a0801==1) %>% #parents who are married (and alive)
-  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
-  filter(local.resi>=5)
-```
-
-## Variables 
 Compute standardized exam grades (within-school z-scores)
 ```{r}
-d_cl <- d_cl %>% #Total exam grades at wave 1 and at wave 2
+d <- d %>% #Total exam grades at wave 1 and at wave 2
   mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
          w2ttl = w2chn + w2mat + w2eng) 
-d_cl <- d_cl %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
+d <- d %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
   group_by(schids) %>%
@@
 
+Sample
+```{r}
+d_cl <- d_cl %>% 
+  filter(w2a0801==1) %>% #parents who are married (and alive)
+  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
+  filter(local.resi>=7)
+```
+
+## Variables 
 Dependent variables: Outcome differences between wave 2 and wave 1

### 2022-05-23 MScThesisText.Rmd
change template

---
title             : "Parental Migration and Children's School Performance"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
bibliography: references.bib
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work. These so-called "left behind children" are common in migrant-sending regions in the Global South. Their exact numbers in total are unavailable, but surveys provide some estimation. According to the Mexican and Latin American Migration Projects, around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s [@dewaard2018]. The World Bank's Migration and Remittances Surveys indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010 [@chae2019]. In China, the 2015 one percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration [@nbs2017].

Parental migration can alter children's life course.

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-05-23 data/Gu-thesis-script.Rmd
change template

@@
 ---
-title: "Parental migration, cognitive development and educational performance"
+title: "Parental migration and adolescent's educational performance"
 output: html_notebook
@@
 d <- d %>% mutate(
-  age = 2014 - a02a, #children's age at baseline
-  local.resi = age - a07 #years of residence at the current county05
+  age = 2013 - a02a, #student's age at baseline
+  local.resi = age - a07 #years of residence at the current county
 )
@@
 ```{r}
-d_cl <- d_cl %>% 
+d_cl <- d %>% 
   filter(w2a0801==1) %>% #parents who are married (and alive)
-  filter(be1201==1 & be1202==1) %>% #both parents stay with children at baseline
-  filter(local.resi>=7)
+  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
+  filter(local.resi>=6) #having stayed in the current county for at least six years (duration of primary school) before baseline
 ```
@@
 d_cl <- d_cl %>% mutate(
-  treat_leave = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
-  treat_fa_only = NA,
-  treat_mo_only = NA,
-  treat_both = NA
+  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
+  migr_fa_only = NA,
+  migr_fa = NA,
+  migr_mo_only = NA,
+  migr_mo = NA,
+  migr_both = NA
   )
@@
 ```{r}
-d_cl$treat_mo_only[d_cl$treat_leave == 0] <- 0
-d_cl$treat_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
+d_cl$migr_mo_only[d_cl$migr == 0] <- 0
+d_cl$migr_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
 ```
@@
 ```{r}
-d_cl$treat_mo[d_cl$treat_leave == 0] <- 0
-d_cl$treat_mo[d_cl$w2ba0202==0] <- 1
+d_cl$migr_mo[d_cl$migr == 0] <- 0
+d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
 ```
@@
 ```{r}
-d_cl$treat_fa_only[d_cl$treat_leave == 0] <- 0
-d_cl$treat_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
+d_cl$migr_fa_only[d_cl$migr == 0] <- 0
+d_cl$migr_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
 ```
@@
 ```{r}
-d_cl$treat_fa[d_cl$treat_leave == 0] <- 0
-d_cl$treat_fa[d_cl$w2ba0201==0] <- 1
+d_cl$migr_fa[d_cl$migr == 0] <- 0
+d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
 ```
@@
 ```{r}
-d_cl$treat_both[d_cl$treat_leave == 0] <- 0
-d_cl$treat_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
+d_cl$migr_both[d_cl$migr == 0] <- 0
+d_cl$migr_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
 ```
@@
 d_cl %>%
-  group_by(treat_leave) %>% 
+  group_by(migr) %>% 
   summarise(n_cases = n(),
@@
 d_cl %>%
-  group_by(treat_mo_only) %>% 
+  group_by(migr_mo_only) %>% 
   summarise(n_cases = n(),
@@
 d_cl %>%
-  group_by(treat_mo) %>% 
+  group_by(migr_mo) %>% 
   summarise(n_cases = n(),
@@
 d_cl %>%
-  group_by(treat_fa_only) %>% 
+  group_by(migr_fa_only) %>% 
   summarise(n_cases = n(),
@@
 d_cl %>%
-  group_by(treat_fa) %>% 
+  group_by(migr_fa) %>% 
   summarise(n_cases = n(),
@@
 d_cl %>%
-  group_by(treat_both) %>% 
+  group_by(migr_both) %>% 
   summarise(n_cases = n(),
@@
 ## DID basic
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
+For student i in school s, $$\Delta score_{i,s}$$ is the change in standardized test score between baseline survey and endline survey, $$migr_{i,s}$$ is the treatment dummy variable, and $$FE_{s}$$ is the school-level fixed effect.
+
 Regressing on cognitive test score (standardized)
 ```{r}
-did_cog <- feols(cog ~ treat_leave | schids + ctyids, data = d_cl) 
-did_cog_m_only <- feols(cog ~ treat_mo_only | schids + ctyids, data = d_cl) 
-did_cog_m <- feols(cog ~ treat_mo | schids + ctyids, data = d_cl) 
-did_cog_f_only <- feols(cog ~ treat_fa_only | schids + ctyids, data = d_cl) 
-did_cog_f <- feols(cog ~ treat_fa | schids + ctyids, data = d_cl) 
-did_cog_both <- feols(cog ~ treat_both | schids + ctyids, data = d_cl)
+did_cog <- feols(cog ~ migr | schids, data = d_cl) 
+did_cog_m_only <- feols(cog ~ migr_mo_only | schids, data = d_cl) 
+did_cog_m <- feols(cog ~ migr_mo | schids, data = d_cl) 
+did_cog_f_only <- feols(cog ~ migr_fa_only | schids, data = d_cl) 
+did_cog_f <- feols(cog ~ migr_fa | schids, data = d_cl) 
+did_cog_both <- feols(cog ~ migr_both | schids, data = d_cl)
 ```
+
 Results
@@
 did_cog_both) 
-models_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
+
 Regressing on total exam score
 ```{r}
-did_ttl <- feols(ttl_std ~ treat_leave | schids + ctyids, data = d_cl) 
-did_ttl_m_only <- feols(ttl_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
-did_ttl_m <- feols(ttl_std ~ treat_mo | schids + ctyids, data = d_cl) 
-did_ttl_f <- feols(ttl_std ~ treat_fa | schids + ctyids, data = d_cl) 
-did_ttl_f_only <- feols(ttl_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
-did_ttl_both <- feols(ttl_std ~ treat_both | schids + ctyids, data = d_cl)
+did_ttl <- feols(ttl_std ~ migr | schids, data = d_cl) 
+did_ttl_m_only <- feols(ttl_std ~ migr_mo_only | schids, data = d_cl) 
+did_ttl_m <- feols(ttl_std ~ migr_mo | schids, data = d_cl) 
+did_ttl_f <- feols(ttl_std ~ migr_fa | schids, data = d_cl) 
+did_ttl_f_only <- feols(ttl_std ~ migr_fa_only | schids, data = d_cl) 
+did_ttl_both <- feols(ttl_std ~ migr_both | schids, data = d_cl)
 ```
+
 Results
@@
 did_ttl_both) 
-models_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_chn <- feols(chn_std ~ treat_leave | schids + ctyids, data = d_cl) 
-did_chn_m_only <- feols(chn_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
-did_chn_m <- feols(chn_std ~ treat_mo | schids + ctyids, data = d_cl) 
-did_chn_f_only <- feols(chn_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
-did_chn_f <- feols(chn_std ~ treat_fa | schids + ctyids, data = d_cl) 
-did_chn_both <- feols(chn_std ~ treat_both | schids + ctyids, data = d_cl)
+did_chn <- feols(chn_std ~ migr | schids, data = d_cl) 
+did_chn_m_only <- feols(chn_std ~ migr_mo_only | schids, data = d_cl) 
+did_chn_m <- feols(chn_std ~ migr_mo | schids, data = d_cl) 
+did_chn_f_only <- feols(chn_std ~ migr_fa_only | schids, data = d_cl) 
+did_chn_f <- feols(chn_std ~ migr_fa | schids, data = d_cl) 
+did_chn_both <- feols(chn_std ~ migr_both | schids, data = d_cl)
 ```
+
 Results
@@
 did_chn_both) 
-models_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_mat <- feols(mat_std ~ treat_leave | schids + ctyids, data = d_cl) 
-did_mat_m_only <- feols(mat_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
-did_mat_m <- feols(mat_std ~ treat_mo | schids + ctyids, data = d_cl) 
-did_mat_f_only <- feols(mat_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
-did_mat_f <- feols(mat_std ~ treat_fa | schids + ctyids, data = d_cl) 
-did_mat_both <- feols(mat_std ~ treat_both | schids + ctyids, data = d_cl)
+did_mat <- feols(mat_std ~ migr | schids, data = d_cl) 
+did_mat_m_only <- feols(mat_std ~ migr_mo_only | schids, data = d_cl) 
+did_mat_m <- feols(mat_std ~ migr_mo | schids, data = d_cl) 
+did_mat_f_only <- feols(mat_std ~ migr_fa_only | schids, data = d_cl) 
+did_mat_f <- feols(mat_std ~ migr_fa | schids, data = d_cl) 
+did_mat_both <- feols(mat_std ~ migr_both | schids, data = d_cl)
 ```
+
 Results
@@
 did_mat_both) 
-models_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_eng <- feols(eng_std ~ treat_leave | schids + ctyids, data = d_cl) 
-did_eng_m <- feols(eng_std ~ treat_mo | schids + ctyids, data = d_cl)
-did_eng_m_only <- feols(eng_std ~ treat_mo_only | schids + ctyids, data = d_cl) 
-did_eng_f <- feols(eng_std ~ treat_fa | schids + ctyids, data = d_cl) 
-did_eng_f_only <- feols(eng_std ~ treat_fa_only | schids + ctyids, data = d_cl) 
-did_eng_both <- feols(eng_std ~ treat_both | schids + ctyids, data = d_cl)
+did_eng <- feols(eng_std ~ migr | schids, data = d_cl) 
+did_eng_m <- feols(eng_std ~ migr_mo | schids, data = d_cl)
+did_eng_m_only <- feols(eng_std ~ migr_mo_only | schids, data = d_cl) 
+did_eng_f <- feols(eng_std ~ migr_fa | schids, data = d_cl) 
+did_eng_f_only <- feols(eng_std ~ migr_fa_only | schids, data = d_cl) 
+did_eng_both <- feols(eng_std ~ migr_both | schids, data = d_cl)
 ```
+
 Results
@@
 did_eng_both) 
-models_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ## DID unrestricted
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \lambda \cdot score_{i,s;base} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
+where baseline score is a variable on right hand side
+
 Regressing on cognitive test score (standardized)
 ```{r}
-did_unres_cog <- feols(cog ~ treat_leave + cog3pl | schids + ctyids, data = d_cl) 
-did_unres_cog_m_only <- feols(cog ~ treat_mo_only + cog3pl | schids + ctyids, data = d_cl) 
-did_unres_cog_m <- feols(cog ~ treat_mo + cog3pl | schids + ctyids, data = d_cl) 
-did_unres_cog_f_only <- feols(cog ~ treat_fa_only + cog3pl | schids + ctyids, data = d_cl) 
-did_unres_cog_f <- feols(cog ~ treat_fa + cog3pl | schids + ctyids, data = d_cl) 
-did_unres_cog_both <- feols(cog ~ treat_both + cog3pl | schids + ctyids, data = d_cl)
+did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
+did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
+did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
+did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
 ```
+
 Results
@@
 did_unres_cog_both) 
-models_unres_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
+
 Regressing on total exam score
 ```{r}
-did_unres_ttl <- feols(ttl_std ~ treat_leave + w1ttl_std | schids + ctyids, data = d_cl) 
-did_unres_ttl_m_only <- feols(ttl_std ~ treat_mo_only + w1ttl_std | schids + ctyids, data = d_cl) 
-did_unres_ttl_m <- feols(ttl_std ~ treat_mo + w1ttl_std | schids + ctyids, data = d_cl) 
-did_unres_ttl_f <- feols(ttl_std ~ treat_fa + w1ttl_std | schids + ctyids, data = d_cl) 
-did_unres_ttl_f_only <- feols(ttl_std ~ treat_fa_only + w1ttl_std | schids + ctyids, data = d_cl) 
-did_unres_ttl_both <- feols(ttl_std ~ treat_both + w1ttl_std | schids + ctyids, data = d_cl)
+did_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std | schids, data = d_cl)
 ```
+
 Results
@@
 did_unres_ttl_both) 
-models_unres_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_unres_chn <- feols(chn_std ~ treat_leave + w1chn_std | schids + ctyids, data = d_cl) 
-did_unres_chn_m_only <- feols(chn_std ~ treat_mo_only + w1chn_std | schids + ctyids, data = d_cl) 
-did_unres_chn_m <- feols(chn_std ~ treat_mo + w1chn_std | schids + ctyids, data = d_cl) 
-did_unres_chn_f_only <- feols(chn_std ~ treat_fa_only + w1chn_std | schids + ctyids, data = d_cl) 
-did_unres_chn_f <- feols(chn_std ~ treat_fa + w1chn_std | schids + ctyids, data = d_cl) 
-did_unres_chn_both <- feols(chn_std ~ treat_both + w1chn_std | schids + ctyids, data = d_cl)
+did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
+did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
+did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
+did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
+did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
+did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
 ```
+
 Results
@@
 did_unres_chn_both) 
-models_unres_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_unres_mat <- feols(mat_std ~ treat_leave + w1mat_std | schids + ctyids, data = d_cl) 
-did_unres_mat_m_only <- feols(mat_std ~ treat_mo_only + w1mat_std | schids + ctyids, data = d_cl) 
-did_unres_mat_m <- feols(mat_std ~ treat_mo + w1mat_std | schids + ctyids, data = d_cl) 
-did_unres_mat_f_only <- feols(mat_std ~ treat_fa_only + w1mat_std | schids + ctyids, data = d_cl) 
-did_unres_mat_f <- feols(mat_std ~ treat_fa + w1mat_std | schids + ctyids, data = d_cl) 
-did_unres_mat_both <- feols(mat_std ~ treat_both + w1mat_std | schids + ctyids, data = d_cl)
+did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
+did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
+did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
+did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
+did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
+did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
 ```
+
 Results
@@
 did_unres_mat_both) 
-models_unres_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_unres_eng <- feols(eng_std ~ treat_leave + w1eng_std | schids + ctyids, data = d_cl) 
-did_unres_eng_m <- feols(eng_std ~ treat_mo + w1eng_std | schids + ctyids, data = d_cl)
-did_unres_eng_m_only <- feols(eng_std ~ treat_mo_only + w1eng_std | schids + ctyids, data = d_cl) 
-did_unres_eng_f <- feols(eng_std ~ treat_fa + w1eng_std | schids + ctyids, data = d_cl) 
-did_unres_eng_f_only <- feols(eng_std ~ treat_fa_only + w1eng_std | schids + ctyids, data = d_cl) 
-did_unres_eng_both <- feols(eng_std ~ treat_both + w1eng_std | schids + ctyids, data = d_cl)
+did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
+did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
+did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
+did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
+did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
+did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
 ```
+
 Results
@@
 did_unres_eng_both) 
-models_unres_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ## DID adjusted
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
+$$X_{i,s}$$ denotes a vector of covariates about the characteristics of students, parents, and households.
+
 Regressing on cognitive test score (standardized)
 ```{r}
-did_adj_cog <- feols(cog ~ treat_leave + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
+
 Results
@@
 did_adj_cog_both) 
-models_adj_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
+
 Regressing on total exam score
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
+
 Results
@@
 did_adj_ttl_both) 
-models_adj_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
+
 Results
@@
 did_adj_chn_both) 
-models_adj_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ treat_leave  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ treat_mo_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ treat_mo  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ treat_fa_only  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ treat_fa  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ treat_both  + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
+
 Results
@@
 did_adj_mat_both) 
-models_adj_mat %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ treat_leave + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ treat_mo + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ treat_mo_only + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ treat_fa + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ treat_fa_only + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ treat_both + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
 ```
+
 Results
@@
 did_adj_eng_both) 
-models_adj_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ## DID adjusted unrestricted
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
+
 Regressing on cognitive test score (standardized)
 ```{r}
-did_adj_unres_cog <- feols(cog ~ treat_leave + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ treat_mo_only + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ treat_mo + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ treat_fa_only + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ treat_fa + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ treat_both + cog3pl + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
@@
 did_adj_unres_cog_both) 
-models_adj_unres_cog %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ treat_leave + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ treat_mo_only + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ treat_mo + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ treat_fa + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ treat_fa_only + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ treat_both + w1ttl_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
@@
 did_adj_unres_ttl_both) 
-models_adj_unres_ttl %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ treat_leave + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ treat_mo_only + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ treat_mo + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ treat_fa_only + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ treat_fa + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ treat_both + w1chn_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
@@
 did_adj_unres_chn_both) 
-models_adj_unres_chn %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ treat_leave + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ treat_mo_only + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ treat_mo + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ treat_fa_only + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ treat_fa + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ treat_both + w1mat_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids + ctyids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
 ```
@@
 did_adj_unres_mat_both) 
-models_mat_adj_unres %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ treat_leave + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ treat_mo + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ treat_mo_only + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ treat_fa + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ treat_fa_only + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ treat_both + w1eng_std + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids + ctyids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
 ```
@@
 did_adj_unres_eng_both) 
-models_adj_unres_eng %>% msummary(stars = c('*' = .1, '**' = .05, '***' = .01))
+models_adj_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
 ```

### 2022-05-26 MScThesisText.tex
Change from thesisdown to papaja

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Parental Migration and Left-Behind Adolescent's School Performance},
  pdfauthor={Jiancheng Gu1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Parental Migration and Left-Behind Adolescent's School Performance}
\author{Jiancheng Gu\textsuperscript{1}}
\date{}

\shorttitle{Left-Behind Adolescent}

\authornote{

Correspondence concerning this article should be addressed to Jiancheng Gu, Postal address. E-mail: \href{mailto:j4.gu@student.vu.nl}{\nolinkurl{j4.gu@student.vu.nl}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Social Sciences, Vrije Universiteit Amsterdam}

\abstract{%
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work. These so-called ``left behind children'' are common in migrant-sending regions in the Global South. Their exact numbers in total are unavailable, but surveys provide some estimation. According to the Mexican and Latin American Migration Projects, around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s (DeWaard et al., 2018). The World Bank's Migration and Remittances Surveys indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010 (Chae \& Glick, 2019). In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration (NBS et al., 2017).

Parental migration can alter children's life course (Murphy, 2020).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. \url{https://cran.r-project.org/package=tinylabels}

\leavevmode\vadjust pre{\hypertarget{ref-chae2019}{}}%
Chae, S., \& Glick, J. E. (2019). Educational Selectivity of Migrants and Current School Enrollment of Children Left behind: Analyses in Three African Countries. \emph{International Migration Review}, \emph{53}(3), 736--769. \url{https://doi.org/10.1177/0197918318772261}

\leavevmode\vadjust pre{\hypertarget{ref-dewaard2018}{}}%
DeWaard, J., Nobles, J., \& Donato, K. M. (2018). Migration and parental absence: A comparative assessment of transnational families in Latin America. \emph{Population, Space and Place}, \emph{24}(7), e2166. \url{https://doi.org/10.1002/psp.2166}

\leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
Murphy, R. (2020). \emph{The children of china's great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}

\leavevmode\vadjust pre{\hypertarget{ref-nbs2017}{}}%
NBS, UNICEF, \& UNFPA. (2017). \emph{Population Status of Children in China in 2015: Facts and Figures}. \url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\end{CSLReferences}

\end{document}

### 2022-05-27 data/Gu-thesis-script.Rmd
change control variables

@@
 title: "Parental migration and adolescent's educational performance"
-output: html_notebook
+output: html_notebook:
+self_contained: no
 ---
@@
          is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
-         is.fa.mid.sch = if_else(b07 != 1 & b07 != 2, 1, 0), #father finished junior high school
-         is.mo.mid.sch = if_else(b06 != 1 & b06 != 2, 1, 0) #mother finished junior high school
+         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
+         has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
+         has.book = b12 #Amount of book at home, student self-rated 
 ) %>% drop_na(
-  is.girl, is.rural, is.only.child, is.boarding, is.fa.mid.sch, is.mo.mid.sch)
+  is.girl, is.rural, is.only.child, is.boarding, par.edu, has.internet, has.book)
+```
+
+Best-educated parent's years of education
+```{r}
+d_cl <- d_cl %>% mutate(par.edu.year = NA)
+d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
+d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
+d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
+d_cl$par.edu.year[d_cl$par.edu == 4|5|6] <- 12
+d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
+d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
+d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
 ```
@@
 des_boarding <- d_cl %>% count(is.boarding)
-des_fa.mid.sch <- d_cl %>% count(is.fa.mid.sch)
-des_mo.mid.sch <- d_cl %>% count(is.mo.mid.sch)
+des_book <- d_cl %>% group_by(has.book) %>% count
+des_internet <- d_cl %>% group_by(has.internet) %>% count
+des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
 des_gender
@@
 des_boarding
-des_fa.mid.sch
-des_mo.mid.sch
+des_par.edu.year
+des_book
+des_internet
 ```
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl) 
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + has.book + has.internet | schids, data = d_cl)
 ```

### 2022-05-28 MScThesisText.Rmd
change control var

@@
 ---
-title             : "Parental Migration and Children's School Performance"
-shorttitle        : "Title"
+title             : "Parental Migration and Left-Behind Adolescent's School Performance"
+shorttitle        : "Left-Behind Adolescent"
 
 author: 
-  - name          : "First Author"
+  - name          : "Jiancheng Gu"
     affiliation   : "1"
@@
     address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - "Conceptualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - "Writing - Review & Editing"
-      - "Supervision"
+    email         : "j4.gu@student.vu.nl"
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
-  - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Faculty of Social Sciences, Vrije Universiteit Amsterdam"
 
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
 
@@
 
-bibliography      : "references.bib"
-
 floatsintext      : no
-linenumbers       : yes
+linenumbers       : no
 draft             : no
@@
 
+header-includes:
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+
 classoption       : "man"
 output            : papaja::apa6_pdf
-bibliography: references.bib
+bibliography      : references.bib
 ---
@@
 library("papaja")
-r_refs("r-references.bib")
+r_refs("references.bib")
 ```
@@
 The World Bank's Migration and Remittances Surveys indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010 [@chae2019].
-In China, the 2015 one percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration [@nbs2017].
+In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration [@nbs2017].
 

### 2022-05-28 data/Gu-thesis-script.Rmd
change control var

--- 2022-05-23 data/Gu-thesis-script.Rmd
@@
 ---
-title: "Parental migration and adolescent's educational performance"
+title: 'parental migration and adolescents educational performance'
 output: html_notebook
@@
          is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
-         is.fa.mid.sch = if_else(b07 != 1 & b07 != 2, 1, 0), #father finished junior high school
-         is.mo.mid.sch = if_else(b06 != 1 & b06 != 2, 1, 0) #mother finished junior high school
+         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
+         #fa.edu = b07,
+         #mo.edu = b06,
+         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
+         home.book = b12 #Amount of book at home, student self-rated 
 ) %>% drop_na(
-  is.girl, is.rural, is.only.child, is.boarding, is.fa.mid.sch, is.mo.mid.sch)
+  is.girl, is.rural, is.only.child, is.boarding, par.edu, home.internet, home.book)
+```
+
+Best-educated parent's years of education
+```{r}
+d_cl <- d_cl %>% mutate(par.edu.year = NA)
+d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
+d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
+d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
+d_cl$par.edu.year[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
+d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
+d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
+d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
+```
+
+```{r}
+d_cl <- d_cl %>% mutate(fa.edu.year = NA)
+d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
+d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
+d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
+d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
+d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
+d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
+d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
+```
+
+```{r}
+d_cl <- d_cl %>% mutate(mo.edu.year = NA)
+d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
+d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
+d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
+d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
+d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
+d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
+d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
 ```
@@
 des_boarding <- d_cl %>% count(is.boarding)
-des_fa.mid.sch <- d_cl %>% count(is.fa.mid.sch)
-des_mo.mid.sch <- d_cl %>% count(is.mo.mid.sch)
+des_book <- d_cl %>% group_by(home.book) %>% count
+des_internet <- d_cl %>% group_by(home.internet) %>% count
+des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
 des_gender
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + is.fa.mid.sch + is.mo.mid.sch  | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```

### 2022-05-28 data/Gu-thesis-script-more-control-var.Rmd
more control var

--- 2022-05-28 data/Gu-thesis-script.Rmd
@@
 
+```{r}
+d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., is.na(.), 0))
+```
+
 Control variables
@@
          is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
+         siblings = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204),
+         health = NA,
          par.edu = if_else(b06 > b07, b06, b07), #best educated parent
-         #fa.edu = b07,
-         #mo.edu = b06,
+         fa.edu = b07,
+         mo.edu = b06,
          home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
-         home.book = b12 #Amount of book at home, student self-rated 
-) %>% drop_na(
-  is.girl, is.rural, is.only.child, is.boarding, par.edu, home.internet, home.book)
+         home.book = NA #Amount of book at home, student self-rated 
+)
 ```
@@
 d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
+```
+
+```{r}
+d_cl$home.book[d_cl$b12==1 | d_cl$b12==2] <- 1
+d_cl$home.book[d_cl$b12==3] <- 2
+d_cl$home.book[d_cl$b12==4 | d_cl$b12==5] <- 3
+```
+
+```{r}
+d_cl$health[d_cl$a17==1 | d_cl$a17==2] <- 1
+d_cl$health[d_cl$a17==3] <- 2
+d_cl$health[d_cl$a17==4 | d_cl$a17==5] <- 3
+```
+
+```{r}
+d_cl <- d_cl %>% drop_na(
+  is.girl, is.rural, is.only.child, is.boarding, par.edu, fa.edu, mo.edu, health, home.internet, home.book)
 ```
@@
 des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
+des_health <- d_cl %>% group_by(health) %>% count
 des_gender
@@
 des_internet
+des_health
 ```
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```

### 2022-05-28 data/Gu-thesis-script.Rmd
control var: num of siblings

@@
          is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
-         is.only.child = if_else(b01 == 1, 1, 0), #student is only child
+         #is.only.child = if_else(b01 == 1, 1, 0), #student is only child
          is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
+         is.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
          par.edu = if_else(b06 > b07, b06, b07), #best educated parent
@@
 ) %>% drop_na(
-  is.girl, is.rural, is.only.child, is.boarding, par.edu, home.internet, home.book)
+  is.girl, is.rural, is.boarding, is.ethn.minority, par.edu, home.internet, home.book)
+```
+
+```{r}
+d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., is.na(.), 0))
+d_cl <- d_cl %>% mutate(sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
+  drop_na(sibling)
 ```
@@
 des_rural <- d_cl %>% count(is.rural)
-des_only.child <- d_cl %>% count(is.only.child)
+des_sibling <- d_cl %>% group_by(sibling) %>% count
 des_boarding <- d_cl %>% count(is.boarding)
@@
 des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
+des_ethn.minority <- d_cl %>% group_by(is.ethn.minority) %>% count
 des_gender
 des_rural
-des_only.child
+des_sibling
 des_boarding
@@
 des_internet
+des_ethn.minority
 ```
@@
 did_cog_m,
+did_cog_f_only,
 did_cog_f,
-did_cog_f_only,
 did_cog_both) 
-models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_ttl_m,
+did_ttl_f_only,
 did_ttl_f,
-did_ttl_f_only,
 did_ttl_both) 
-models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_chn_m,
+did_chn_f_only,
 did_chn_f,
-did_chn_f_only,
 did_chn_both) 
-models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_mat_m,
+did_mat_f_only,
 did_mat_f,
-did_mat_f_only,
 did_mat_both) 
-models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_eng_m,
+did_eng_f_only,
 did_eng_f,
-did_eng_f_only,
 did_eng_both) 
-models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_unres_cog_m,
+did_unres_cog_f_only,
 did_unres_cog_f,
-did_unres_cog_f_only,
 did_unres_cog_both) 
-models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_unres_ttl_m,
+did_unres_ttl_f_only,
 did_unres_ttl_f,
-did_unres_ttl_f_only,
 did_unres_ttl_both) 
-models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_unres_chn_m,
+did_unres_chn_f_only,
 did_unres_chn_f,
-did_unres_chn_f_only,
 did_unres_chn_both) 
-models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_unres_mat_m,
+did_unres_mat_f_only,
 did_unres_mat_f,
-did_unres_mat_f_only,
 did_unres_mat_both) 
-models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 did_unres_eng_m,
+did_unres_eng_f_only,
 did_unres_eng_f,
-did_unres_eng_f_only,
 did_unres_eng_both) 
-models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_cog_m,
+did_adj_cog_f_only,
 did_adj_cog_f,
-did_adj_cog_f_only,
 did_adj_cog_both) 
-models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_ttl_m,
+did_adj_ttl_f_only,
 did_adj_ttl_f,
-did_adj_ttl_f_only,
 did_adj_ttl_both) 
-models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_chn_m,
+did_adj_chn_f_only,
 did_adj_chn_f,
-did_adj_chn_f_only,
 did_adj_chn_both) 
-models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_mat_m,
+did_adj_mat_f_only,
 did_adj_mat_f,
-did_adj_mat_f_only,
 did_adj_mat_both) 
-models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_eng_m,
+did_adj_eng_f_only,
 did_adj_eng_f,
-did_adj_eng_f_only,
 did_adj_eng_both) 
-models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_unres_cog_m,
+did_adj_unres_cog_f_only,
 did_adj_unres_cog_f,
-did_adj_unres_cog_f_only,
 did_adj_unres_cog_both) 
-models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_unres_ttl_m,
+did_adj_unres_ttl_f_only,
 did_adj_unres_ttl_f,
-did_adj_unres_ttl_f_only,
 did_adj_unres_ttl_both) 
-models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_unres_chn_m,
+did_adj_unres_chn_f_only,
 did_adj_unres_chn_f,
-did_adj_unres_chn_f_only,
 did_adj_unres_chn_both) 
-models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_unres_mat_m,
+did_adj_unres_mat_f_only,
 did_adj_unres_mat_f,
-did_adj_unres_mat_f_only,
 did_adj_unres_mat_both) 
-models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + is.only.child + is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 did_adj_unres_eng_both) 
-models_adj_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
+models_adj_unres_eng %>% 
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
 ```

### 2022-05-28 data/Gu-thesis-script.Rmd
model summary output coef rename

@@
 
-```{r}
+```
 d_cl <- d_cl %>% mutate(fa.edu.year = NA)
@@
 
-```{r}
+```
 d_cl <- d_cl %>% mutate(mo.edu.year = NA)

### 2022-05-29 data/Gu-thesis-script.Rmd
add health as control var

@@
 d_cl <- d_cl %>% mutate(
-         is.girl = if_else(a01 == 2, 1, 0), #student is girl
-         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
-         #is.only.child = if_else(b01 == 1, 1, 0), #student is only child
-         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
-         is.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
+         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
+         ch.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
+         ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
+         ch.boarding = if_else(c18 == 1, 1, 0), #student is boarding at school
+         ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
+         ch.health = a17, #student's self-reported health
+         par.edu = if_else(b06 > b07, b06, b07), #Among two parents, the best-educated one's educational level
          #fa.edu = b07,
@@
 ) %>% drop_na(
-  is.girl, is.rural, is.boarding, is.ethn.minority, par.edu, home.internet, home.book)
+  ch.girl, ch.rural, ch.health, ch.only.child, ch.boarding, ch.ethn.minority, ch.health, par.edu, home.internet, home.book)
 ```
 
-```{r}
-d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., is.na(.), 0))
+```
+d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., ch.na(.), 0))
 d_cl <- d_cl %>% mutate(sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
@@
 ```{r}
-des_gender <- d_cl %>% count(is.girl)
-des_rural <- d_cl %>% count(is.rural)
-des_sibling <- d_cl %>% group_by(sibling) %>% count
-des_boarding <- d_cl %>% count(is.boarding)
+des_gender <- d_cl %>% count(ch.girl)
+des_rural <- d_cl %>% count(ch.rural)
+#des_sibling <- d_cl %>% group_by(sibling) %>% count
+des_boarding <- d_cl %>% count(ch.boarding)
 des_book <- d_cl %>% group_by(home.book) %>% count
@@
 des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
-des_ethn.minority <- d_cl %>% group_by(is.ethn.minority) %>% count
+des_ethn.minority <- d_cl %>% group_by(ch.ethn.minority) %>% count
 des_gender
 des_rural
-des_sibling
+#des_sibling
 des_boarding
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```

### 2022-06-02 MScThesisText.Rmd

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
 
@@
 output            : papaja::apa6_pdf
-bibliography      : references.bib
+
+bibliography: references.bib
 ---
@@
 Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
-These so-called "left behind children" are common in migrant-sending regions in the Global South.
-Their exact numbers in total are unavailable, but surveys provide some estimation.
-According to the Mexican and Latin American Migration Projects, around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s [@dewaard2018].
-The World Bank's Migration and Remittances Surveys indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010 [@chae2019].
-In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration [@nbs2017].
+These are the so-called "left behind children" who are common in migrant-sending regions in the Global South.
+The global size of left behind children population is unavailable, but in-country surveys provide some estimation.
+[@dewaard2018] analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
+[@popova2018] cited a 2016 study by UN Children's Fund Bulgaria, suggesting that one-fifth of Bulgarian children had one or both parents working abroad.
+In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration [@nbs2017].
 
-Parental migration can alter children's life course.
+Parental migration shapes child-and-adolescence development by exerting different effects that work oppositely.
+Consider children's human capital accumulation.
+Labor migrants send remittances back home, boosting the family income.
+Higher income can fund children's schooling as well as improve their nutritional and living conditions.
+All these may enhance children's educational outcome.
+The inflow of remittances, however, cannot substitute for the loss of parental care.
+Parental migration halts the day-to-day, face-to-face contact between parents and children.
+It decreases the amount and quality of parental guidance, protection, and support.
+All these may hinder children's school performance.
+It is uncertain how these two opposing effects affect children's educational performance, which merits empirical investigation.
+
+A challenge arises in the methodology for assessing the causal relation between parental migration and children's education.
+It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+Statistical advances in causal inference provides an alternative.
+We can infer causality from a quasi-experimental design -- that is, only if the cause is as good as randomly assigned to individuals in the analysis, conditional on identification assumptions.
+
+For studying left behind children, a suitable case is China.
+The country has seen a huge scale of internal migration and salient challenges facing migrant parents and left behind children.
+The National Bureau of Statistics reported that the number of in-country migrant workers exceeded 292.5 million by 2021[@nbs2022].
+According to [@gu2021], current policy still limits internal migrants' access to public services and social benefits outside their hometowns, including public school for their children.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children?
+This thesis aims to address the shortcomings in the existing literature.
+I analyze the data from a nationally representative two-wave panel survey.
+The sample includes children in both urban and rural areas.
+I develop a difference-in-differences design for causal inference.
+The dependent variables include children's cognitive test scores and their Chinese, mathematics, and English exam scores.
+
+# Literature Review
+
+Researchers obtained mixed results regarding how migration-induced parental absence affects children's education.
+Using data collected from junior high school students, [@li2017] found that parental migration negatively impacts left-behind children's achievement in standardized mathematical test.
+[@wang2019] also collected data from students of junior high school, but discovered no overall effect of parental migration on the mathematical test grades of children left behind.
+[@bai2018] gathered data from primary school pupils.
+They reported that parental migration "does not appear to have a negative effect" on the standardized English test scores of left-behind children, and "in some cases even appears to have a positive effect" (p.
+1165).
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+
+Two competing theoretical frameworks, one of which is the resource generation model.
+According to this model, parental migration brings forth greater economic capital to improve household environment.
+Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
+[@chang2019] provided evidence through interviews with migrant workers and their families.
+They said that labor migration can boost household income, as the city offers more jobs and higher pay than does the countryside.
+
+The other theoretical model is the family disruption model.
+Children flourish under parental nurturing care.
+This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
+Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
+The loss of nurturing care represents a decreased investment in children's human capital.
+Human capital is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016, @botev2019].
+In disadvantaged families, the migrant parent is likely the best educated adult in the household.
+Their absence makes it harder for children to overcome learning obstacles.
+
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+As [@nbs2017] stated, the number of urban left behind children had been growing, and the trend would continue.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional data, making it hard to infer causal relations [@zhou2014; @jin2020].
+Others suffer from a limited sample size of less than one thousand participants [@liu2021; @yang2022] or a limited geographic coverage of one or a few towns [@yang2022; @shu2021; @jin2020].
+The third shortcoming lies in the selection and measurement of outcome.
+[@chang2019; @wang2019] measure students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+## Participants
+
+I obtained the data from the China Education Panel Survey (CEPS).
+It is a nationally representative, school-based survey featuring junior high school students.
+The survey administrator is the National Survey Research Center at Renmin University of China.
+The survey's sampling adopted a multi-stage stratified probability proportional to size approach.
+Moreover, designed deliberately to focus on migrant children, the survey also oversampled those counties with large intranational migrant populations.
+The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in seventh and ninth grades.
+These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
+I only kept the 9,449 observations of seventh grade students and their parents, who completed the follow-up survey in the 2014-2015 academic year.
+
+## Measurement
+
+~~I explored two categories of adolescence development: academic and cognitive abilities.
+One key dependent variable, the student's cognitive skill, is measured by a fifteen-minute standardized test.
+The test covered three types of reasoning: verbal, visuospatial, and numerical.
+The raw scores of cognitive skill were then standardized.
+The other~~ set of dependent variables concern students' academic performance.
+This is measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
+To facilitate comparison across schools and counties, I use standardized test scores instead of raw test scores.
+
+The key independent variable, the parental migration status, was identified by two items in the parent survey.
+In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
+I identified seven types of migration arrangement: both parents absent, only father absent, only mother absent, father absent, mother absent, and both parents at home.
+I then removed the observations that reported other types of parental absence induced by divorce or death.
 
@@
 
-We used `r cite_r("r-references.bib")` for all our analyses.
+I adopted `r cite_r("r-references.bib")` for all the analyses.
+
+Following [@bai2018], I adopted a difference-in-differences design to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
+The model is:
+
+$$
+\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}
+$$
+
+whereas for student i in school s, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the baseline exam score, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
+The control variables on children includes age, gender, ethnicity, self-rated health, hukou type, and only child.
+The control variables on household include the years of education of the best-educated parent, the number of books at home, and the internet assess at home.
 

### 2022-06-02 MScThesisText.tex

@@
 
-\abstract{%
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
-}
-
 \begin{document}
@@
 Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
-These so-called ``left behind children'' are common in migrant-sending regions in the Global South.
+These are the so-called ``left behind children'' who are common in migrant-sending regions in the Global South.
 Their exact numbers in total are unavailable, but surveys provide some estimation.
-According to the Mexican and Latin American Migration Projects, around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s (DeWaard et al., 2018).
-The World Bank's Migration and Remittances Surveys indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010 (Chae \& Glick, 2019).
+(DeWaard et al., 2018) analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
+(Chae \& Glick, 2019) studied the World Bank's Migration and Remittances Surveys and indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010.
 In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration (NBS et al., 2017).
 
-Parental migration can alter children's life course (Murphy, 2020).
+Parental migration shapes child development -- such as human capital accumulation -- by exerting different effects that work oppositely.
+Labor migrants send remittances back home, boosting the family income.
+Higher income can fund children's schooling as well as improve their nutritional and living conditions.
+All these may enhance children's educational outcome.
+The inflow of remittances, however, cannot substitute for the loss of parental care.
+Parental migration halts the day-to-day, face-to-face contact between parents and children.
+It decreases the amount and quality of parental guidance, protection, and support.
+All these may hinder children's school performance.
+It is uncertain how these two opposing effects affect children's educational performance, which merits empirical investigation.
+
+For studying left behind children, a suitable case is China.
+The country has seen a huge scale of internal migration and salient challenges facing migrant parents and left behind children.
+More than 285 million Chinese people were in-country migrant workers.
+According to (Gu, 2021), current policy still limits internal migrants' access to public services and social benefits outside their hometowns, including public school for their children.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while negleting the urban counterparts.
+As (NBS et al., 2017) stated, the number of urban left behind children had been growing, and the trend would continue expectedly.
+Meanwhile, in-situ urbanization has turned a small proportion of children left behind in the countryside as urban residents.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional surveys, making it hard to infer causal relations (Wen et al., 2020; Zhou et al., 2014).
+Others suffer from a limited sample size of less than one thousand participants (Liu et al., 2021; Yang et al., 2022) or a limited geographic coverage of one or a few towns (Shu, 2021; Yang et al., 2022).
+The third shortcoming lies in the selection and measurement of outcome.
+Wang et al.
+(2019) measure students' educational performance with the test score of only one academic subject, such as English or mathematics.
+The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
+
+This thesis aims to address the shortcomings in the study of parental migration's effect on left behind children's educational performance.
+I analyze the data from a nationally representative two-wave panel survey.
+The sample includes children in both urban and rural areas.
+I develop a difference-in-differences design for causal inference.
+The dependent variables include children's cognitive test scores and their Chinese, mathematics, and English exam scores.
+
+\hypertarget{literature-review}{%
+\section{Literature Review}\label{literature-review}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bai2018}{}}%
+Bai, Y., Zhang, L., Liu, C., Shi, Y., Mo, D., \& Rozelle, S.
+(2018).
+Effect of parental migration on the academic performance of left behind children in north western china.
+\emph{The Journal of Development Studies}, \emph{54}(7), 1154--1170.
+\url{https://doi.org/10.1080/00220388.2017.1333108}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chang2019}{}}%
+Chang, F., Jiang, Y., Loyalka, P., Chu, J., Shi, Y., Osborn, A., \& Rozelle, S.
+(2019).
+Parental migration, educational achievement, and mental health of junior high school students in rural China.
+\emph{China Economic Review}, \emph{54}, 337--349.
+\url{https://doi.org/10.1016/j.chieco.2019.01.007}
+
 \leavevmode\vadjust pre{\hypertarget{ref-dewaard2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
-Murphy, R. (2020). \emph{The children of china's great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
+\leavevmode\vadjust pre{\hypertarget{ref-gu2021}{}}%
+Gu, X.
+(2021).
+{`}Save the children!{'}: Governing left-behind children through family in China{'}s Great Migration.
+\emph{Current Sociology}, 0011392120985874.
+\url{https://doi.org/10.1177/0011392120985874}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2021}{}}%
+Liu, Y., Deng, Z., \& Katz, I.
+(2021).
+Transmission of Educational Outcomes Across Three Generations: Evidence From Migrant Workers{'} Children in China.
+\emph{Applied Research in Quality of Life}.
+\url{https://doi.org/10.1007/s11482-021-09990-y}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-shu2021}{}}%
+Shu, B.
+(2021).
+Parental Migration, Parental Emotional Support, and Adolescent Children{'}s Life Satisfaction in Rural China: The Roles of Parent and Child Gender.
+\emph{Journal of Family Issues}, \emph{42}(8), 1663--1705.
+\url{https://doi.org/10.1177/0192513X20946345}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wang2019}{}}%
+Wang, L., Zheng, Y., Li, G., Li, Y., Fang, Z., Abbey, C., \& Rozelle, S.
+(2019).
+Academic achievement and mental health of left-behind children in rural china: A causal study on parental migration.
+\emph{China Agricultural Economic Review}, \emph{11}(4), 569--582.
+\url{https://doi.org/10.1108/CAER-09-2018-0194}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wen2020}{}}%
+Wen, M., Wang, W., Wan, N., \& Su, D.
+(2020).
+Family Income and Student Educational and Cognitive Outcomes in China: Exploring the Material and Psychosocial Mechanisms.
+\emph{Social Sciences}, \emph{9}(12), 225.
+\url{https://doi.org/10.3390/socsci9120225}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
+Yang, F., Wang, Z., Liu, J., \& Tang, S.
+(2022).
+The Effect of Social Interaction on Rural Children{'}s Self-identity: an Empirical Study Based on Survey Data from Jintang County, China.
+\emph{Child Indicators Research}, \emph{15}(3), 839--861.
+\url{https://doi.org/10.1007/s12187-021-09887-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhou2014}{}}%
+Zhou, M., Murphy, R., \& Tao, R.
+(2014).
+Effects of Parents' Migration on the Education of Children Left Behind in Rural China.
+\emph{Population and Development Review}, \emph{40}(2), 273--292.
+\url{https://doi.org/10.1111/j.1728-4457.2014.00673.x}
+
 \end{CSLReferences}

### 2022-06-03 MScThesisText.Rmd
add table display in Rmd

@@
 ```{r setup, include = FALSE}
+load('.Rdata')
 library("papaja")
@@
 
-Parental migration shapes child-and-adolescence development by exerting different effects that work oppositely.
-Consider children's human capital accumulation.
+Parental migration impacts child-and-adolescence development by exerting different effects that work oppositely [@vanhook2020].
+Consider children's education.
 Labor migrants send remittances back home, boosting the family income.
@@
 All these may hinder children's school performance.
-It is uncertain how these two opposing effects affect children's educational performance, which merits empirical investigation.
+It is uncertain how these two opposing effects shape children's educational performance, which merits empirical investigation.
 
-A challenge arises in the methodology for assessing the causal relation between parental migration and children's education.
+A challenge arises in the empirical assessment of the causal relation between parental migration and children's education.
 It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
@@
 
-To what extent do parental migration affect the cognitive development and academic performance of left-behind children?
-This thesis aims to address the shortcomings in the existing literature.
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
 I analyze the data from a nationally representative two-wave panel survey.
@@
 I develop a difference-in-differences design for causal inference.
-The dependent variables include children's cognitive test scores and their Chinese, mathematics, and English exam scores.
+The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
 
@@
 
-Two competing theoretical frameworks, one of which is the resource generation model.
-According to this model, parental migration brings forth greater economic capital to improve household environment.
+Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
+One model, the generation model, holds that parental migration brings forth greater resources in the form of economic capital.
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
-[@chang2019] provided evidence through interviews with migrant workers and their families.
-They said that labor migration can boost household income, as the city offers more jobs and higher pay than does the countryside.
+Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
+[@chang2019] provided evidence through interviews with migrant workers and their family members.
+They said that the city offered more jobs and higher pay than did the countryside.
+Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
 
@@
 Children flourish under parental nurturing care.
-This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
+This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black, p.1].
 Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
-The loss of nurturing care represents a decreased investment in children's human capital.
-Human capital is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016, @botev2019].
-In disadvantaged families, the migrant parent is likely the best educated adult in the household.
-Their absence makes it harder for children to overcome learning obstacles.
+The loss of nurturing care hinders children's accumulation of human capital.
+[@hong2019] talked to a group of left behind children in grade nine.
+These students expressed the utter sense of loneliness "with no advocate, no support and with no one looking out for them" (p.
+13).
+Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.
+14).
 
@@
 The survey administrator is the National Survey Research Center at Renmin University of China.
-The survey's sampling adopted a multi-stage stratified probability proportional to size approach.
+The project's sampling adopted a multi-stage stratified probability proportional to size approach.
 Moreover, designed deliberately to focus on migrant children, the survey also oversampled those counties with large intranational migrant populations.
+The participants filled a paper-and-pencil questionnaire.
 The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in seventh and ninth grades.
@@
 
-~~I explored two categories of adolescence development: academic and cognitive abilities.
+I explored two categories of adolescence development: academic and cognitive abilities.
 One key dependent variable, the student's cognitive skill, is measured by a fifteen-minute standardized test.
@@
 The raw scores of cognitive skill were then standardized.
-The other~~ set of dependent variables concern students' academic performance.
-This is measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
-To facilitate comparison across schools and counties, I use standardized test scores instead of raw test scores.
+The other set of dependent variables concerned students' academic performance.
+This was measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
+To facilitate comparison across schools and counties, I used standardized test scores instead of raw test scores.
+I removed the observations with missing values in any of the test score mentioned above.
 
@@
 In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
-I identified seven types of migration arrangement: both parents absent, only father absent, only mother absent, father absent, mother absent, and both parents at home.
+I identified seven types of migration arrangement: both parents absent, only father absent, only mother absent, father absent (unconditional), mother absent (unconditional), and both parents at home.
 I then removed the observations that reported other types of parental absence induced by divorce or death.
@@
 
-I adopted `r cite_r("r-references.bib")` for all the analyses.
+Following Bai and colleagues' [-@bai2018; -@bai2020] approach, I adopted a difference-in-differences design to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
+The model is: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the baseline exam score, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
 
-Following [@bai2018], I adopted a difference-in-differences design to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-The model is:
+The control variables at the student level include: student's age, gender, ethnicity, self-rated health, hukou type, and the number of siblings.
+I obtained the age by subtracting the student's birth year from the year 2013, the start of the baseline academic year.
+I coded students' gender as male = 0 and female = 1, ethnic minority status as Han Chinese = 0 and other ethnicity = 1, hukou status as rural (agricultural) hukou = 1 and other types = 0.
+I obtained the number of siblings of students through two items.
+Students who answered yes to the question "Are you the only child of your family" had no sibling.
+Those who answered no to this question were instructed to proceed to the next question, "How many full or half siblings do you have" -- elder brother, younger brother, elder sister, and younger sister, respectively.
+In these four columns, I transformed `NA` to zero.
+Then I added the four columns as the number of siblings of a student.
 
-$$
-\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}
-$$
+The control variables include the internet assess at home, the self-rated number of books at home, and the years of education of the best-educated parent.
+These variables can approximate the level of human capital in a household.
+The internet assess was measured by the item "Do [sic] your family own a computer and have an access to the Internet".
+Those who answered "Yes, we have both" were coded as 1, and others as 0.
+The number of books was measured by the item "How many books do your family own?
+(not including textbooks or magazines)".
+Students chose from a range of 1 as "very few" to 5 as "a great number".
+The years of education of the best-educated parent were measured by two items.
+Students indicated their father's and mother's educational level, respectively.
+I transformed these two variables into years of education and retained the larger value.
 
-whereas for student i in school s, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the baseline exam score, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
-The control variables on children includes age, gender, ethnicity, self-rated health, hukou type, and only child.
-The control variables on household include the years of education of the best-educated parent, the number of books at home, and the internet assess at home.
+I adopted `r cite_r("r-references.bib")` for all the analyses and the `fixest` package [@bergé2018] for building the two-way fixed effect models.
 
 # Results
+
+```{r}
+table_adj_unres_cog
+```
+
+```{r}
+table_adj_unres_chn
+```
+
+```{r}
+table_adj_unres_mat
+```
+
+```{r}
+table_adj_unres_eng
+```
 

### 2022-06-03 data/Gu-thesis-script.Rmd
add table display in Rmd

--- 2022-05-28 data/Gu-thesis-script.Rmd
@@
   ttl_std = w2ttl_std - w1ttl_std,
-  cog = w2cog3pl - cog3pl #Cognitive test score, standardized
+  cog = w2cog3pl - cog3pl 
 ) %>%
@@
 d_cl <- d_cl %>% mutate(
-         is.girl = if_else(a01 == 2, 1, 0), #student is girl
-         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
-         #is.only.child = if_else(b01 == 1, 1, 0), #student is only child
-         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
-         is.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
+         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
+         ch.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
+         #ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
+         ch.boarding = if_else(c18 == 1, 1, 0), #student is boarding at school
+         ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
+         ch.health = a17, #student's self-reported health
+         par.edu = if_else(b06 > b07, b06, b07), #Among two parents, the best-educated one's educational level
          #fa.edu = b07,
@@
 ) %>% drop_na(
-  is.girl, is.rural, is.boarding, is.ethn.minority, par.edu, home.internet, home.book)
+  ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.minority, ch.health, par.edu, home.internet, home.book)
 ```
@@
 ```{r}
-d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., is.na(.), 0))
-d_cl <- d_cl %>% mutate(sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
-  drop_na(sibling)
+d_cl$b0201 <- d_cl$b0201 %>% replace_na(0)
+d_cl$b0202 <- d_cl$b0202 %>% replace_na(0)
+d_cl$b0203 <- d_cl$b0203 %>% replace_na(0)
+d_cl$b0204 <- d_cl$b0204 %>% replace_na(0)
+d_cl <- d_cl %>% mutate(ch.sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
+  drop_na(ch.sibling)
 ```
@@
   migr_both = NA
-  )
+  ) %>% drop_na(migr)
 ```
@@
 ```{r}
-des_gender <- d_cl %>% count(is.girl)
-des_rural <- d_cl %>% count(is.rural)
-des_sibling <- d_cl %>% group_by(sibling) %>% count
-des_boarding <- d_cl %>% count(is.boarding)
+des_gender <- d_cl %>% count(ch.girl)
+des_rural <- d_cl %>% count(ch.rural)
+des_sibling <- d_cl %>% group_by(ch.sibling) %>% count
+des_boarding <- d_cl %>% count(ch.boarding)
 des_book <- d_cl %>% group_by(home.book) %>% count
@@
 des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
-des_ethn.minority <- d_cl %>% group_by(is.ethn.minority) %>% count
+des_ethn.minority <- d_cl %>% group_by(ch.ethn.minority) %>% count
 des_gender
@@
 
-## DID basic
-$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
-For student i in school s, $$\Delta score_{i,s}$$ is the change in standardized test score between baseline survey and endline survey, $$migr_{i,s}$$ is the treatment dummy variable, and $$FE_{s}$$ is the school-level fixed effect.
-
-Regressing on cognitive test score (standardized)
-```{r}
-did_cog <- feols(cog ~ migr | schids, data = d_cl) 
-did_cog_m_only <- feols(cog ~ migr_mo_only | schids, data = d_cl) 
-did_cog_m <- feols(cog ~ migr_mo | schids, data = d_cl) 
-did_cog_f_only <- feols(cog ~ migr_fa_only | schids, data = d_cl) 
-did_cog_f <- feols(cog ~ migr_fa | schids, data = d_cl) 
-did_cog_both <- feols(cog ~ migr_both | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_cog <- list(
-did_cog,
-did_cog_m_only,
-did_cog_m,
-did_cog_f_only,
-did_cog_f,
-did_cog_both) 
-models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on total exam score
-```{r}
-did_ttl <- feols(ttl_std ~ migr | schids, data = d_cl) 
-did_ttl_m_only <- feols(ttl_std ~ migr_mo_only | schids, data = d_cl) 
-did_ttl_m <- feols(ttl_std ~ migr_mo | schids, data = d_cl) 
-did_ttl_f <- feols(ttl_std ~ migr_fa | schids, data = d_cl) 
-did_ttl_f_only <- feols(ttl_std ~ migr_fa_only | schids, data = d_cl) 
-did_ttl_both <- feols(ttl_std ~ migr_both | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_ttl <- list(
-did_ttl,
-did_ttl_m_only,
-did_ttl_m,
-did_ttl_f_only,
-did_ttl_f,
-did_ttl_both) 
-models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on Chinese exam score
-```{r}
-did_chn <- feols(chn_std ~ migr | schids, data = d_cl) 
-did_chn_m_only <- feols(chn_std ~ migr_mo_only | schids, data = d_cl) 
-did_chn_m <- feols(chn_std ~ migr_mo | schids, data = d_cl) 
-did_chn_f_only <- feols(chn_std ~ migr_fa_only | schids, data = d_cl) 
-did_chn_f <- feols(chn_std ~ migr_fa | schids, data = d_cl) 
-did_chn_both <- feols(chn_std ~ migr_both | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_chn <- list(
-did_chn,
-did_chn_m_only,
-did_chn_m,
-did_chn_f_only,
-did_chn_f,
-did_chn_both) 
-models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on Math score
-```{r}
-did_mat <- feols(mat_std ~ migr | schids, data = d_cl) 
-did_mat_m_only <- feols(mat_std ~ migr_mo_only | schids, data = d_cl) 
-did_mat_m <- feols(mat_std ~ migr_mo | schids, data = d_cl) 
-did_mat_f_only <- feols(mat_std ~ migr_fa_only | schids, data = d_cl) 
-did_mat_f <- feols(mat_std ~ migr_fa | schids, data = d_cl) 
-did_mat_both <- feols(mat_std ~ migr_both | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_mat <- list(
-did_mat,
-did_mat_m_only,
-did_mat_m,
-did_mat_f_only,
-did_mat_f,
-did_mat_both) 
-models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on English score
-```{r}
-did_eng <- feols(eng_std ~ migr | schids, data = d_cl) 
-did_eng_m <- feols(eng_std ~ migr_mo | schids, data = d_cl)
-did_eng_m_only <- feols(eng_std ~ migr_mo_only | schids, data = d_cl) 
-did_eng_f <- feols(eng_std ~ migr_fa | schids, data = d_cl) 
-did_eng_f_only <- feols(eng_std ~ migr_fa_only | schids, data = d_cl) 
-did_eng_both <- feols(eng_std ~ migr_both | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_eng <- list(
-did_eng,
-did_eng_m_only,
-did_eng_m,
-did_eng_f_only,
-did_eng_f,
-did_eng_both) 
-models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-## DID unrestricted
-$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \lambda \cdot score_{i,s;base} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
-where baseline score is a variable on right hand side
-
-Regressing on cognitive test score (standardized)
-```{r}
-did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
-did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
-did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
-did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
-did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
-did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_cog <- list(
-did_unres_cog,
-did_unres_cog_m_only,
-did_unres_cog_m,
-did_unres_cog_f_only,
-did_unres_cog_f,
-did_unres_cog_both) 
-models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on total exam score
-```{r}
-did_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std | schids, data = d_cl) 
-did_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
-did_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std | schids, data = d_cl) 
-did_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std | schids, data = d_cl) 
-did_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
-did_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_ttl <- list(
-did_unres_ttl,
-did_unres_ttl_m_only,
-did_unres_ttl_m,
-did_unres_ttl_f_only,
-did_unres_ttl_f,
-did_unres_ttl_both) 
-models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on Chinese exam score
-```{r}
-did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
-did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
-did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
-did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
-did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
-did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_chn <- list(
-did_unres_chn,
-did_unres_chn_m_only,
-did_unres_chn_m,
-did_unres_chn_f_only,
-did_unres_chn_f,
-did_unres_chn_both) 
-models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on Math score
-```{r}
-did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
-did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
-did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
-did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
-did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
-did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_mat <- list(
-did_unres_mat,
-did_unres_mat_m_only,
-did_unres_mat_m,
-did_unres_mat_f_only,
-did_unres_mat_f,
-did_unres_mat_both) 
-models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on English score
-```{r}
-did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
-did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
-did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
-did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
-did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
-did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_eng <- list(
-did_unres_eng,
-did_unres_eng_m_only,
-did_unres_eng_m,
-did_unres_eng_f_only,
-did_unres_eng_f,
-did_unres_eng_both) 
-models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
 ## DID adjusted
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl_both <- feols(ttl_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn_m <- feols(chn_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn_f <- feols(chn_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat_m <- feols(mat_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat_f <- feols(mat_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 models_adj_unres_cog <- list(
-did_adj_unres_cog,
-did_adj_unres_cog_m_only,
-did_adj_unres_cog_m,
-did_adj_unres_cog_f_only,
-did_adj_unres_cog_f,
-did_adj_unres_cog_both) 
-models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+'Any Parent Absent' = did_adj_unres_cog,
+'Only Mother Absent' = did_adj_unres_cog_m_only,
+'Mother Absent' = did_adj_unres_cog_m,
+'Only Father Absent' = did_adj_unres_cog_f,
+'Mother Absent' = did_adj_unres_cog_f_only,
+'Both Parents Absent' = did_adj_unres_cog_both) 
+table_adj_unres_cog <- models_adj_unres_cog %>% 
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 models_adj_unres_chn <- list(
-did_adj_unres_chn,
-did_adj_unres_chn_m_only,
-did_adj_unres_chn_m,
-did_adj_unres_chn_f_only,
-did_adj_unres_chn_f,
-did_adj_unres_chn_both) 
-models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+'Any Parent Absent' = did_adj_unres_chn,
+'Only Mother Absent' = did_adj_unres_chn_m_only,
+'Mother Absent' = did_adj_unres_chn_m,
+'Only Father Absent' = did_adj_unres_chn_f,
+'Mother Absent' = did_adj_unres_chn_f_only,
+'Both Parents Absent' = did_adj_unres_chn_both) 
+table_adj_unres_chn <- models_adj_unres_chn %>% 
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"), output = 'markdown')
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-models_mat_adj_unres <- list(
-did_adj_unres_mat,
-did_adj_unres_mat_m_only,
-did_adj_unres_mat_m,
-did_adj_unres_mat_f_only,
-did_adj_unres_mat_f,
-did_adj_unres_mat_both) 
-models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+models_adj_unres_mat <- list(
+'Any Parent Absent' = did_adj_unres_mat,
+'Only Mother Absent' = did_adj_unres_mat_m_only,
+'Mother Absent' = did_adj_unres_mat_m,
+'Only Father Absent' = did_adj_unres_mat_f,
+'Mother Absent' = did_adj_unres_mat_f_only,
+'Both Parents Absent' = did_adj_unres_mat_both) 
+table_adj_unres_mat <- models_adj_unres_mat %>% 
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"), output = 'markdown')
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + sibling + is.boarding + is.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
+
 Results
@@
 models_adj_unres_eng <- list(
-did_adj_unres_eng,
-did_adj_unres_eng_m_only,
-did_adj_unres_eng_m,
-did_adj_unres_eng_f,
-did_adj_unres_eng_f_only,
-did_adj_unres_eng_both) 
-models_adj_unres_eng %>% 
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+'Any Parent Absent' = did_adj_unres_eng,
+'Only Mother Absent' = did_adj_unres_eng_m_only,
+'Mother Absent' = did_adj_unres_eng_m,
+'Only Father Absent' = did_adj_unres_eng_f,
+'Mother Absent' = did_adj_unres_eng_f_only,
+'Both Parents Absent' = did_adj_unres_eng_both) 
+table_adj_unres_eng <- models_adj_unres_eng %>% 
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"), output = 'markdown')
 ```

### 2022-06-03 MScThesisText.Rmd
bring back unadjusted model

@@
 ---
-title             : "Parental Migration and Left-Behind Adolescent's School Performance"
-shorttitle        : "Left-Behind Adolescent"
+title             : "Parental Migration and Left-Behind Children's Cognitive and Academic Performances"
+shorttitle        : "Left-Behind Children"
 
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
+    address       : "De Boelelaan 1105, 1081 HV - Amsterdam, The Netherlands"
     email         : "j4.gu@student.vu.nl"
@@
 library("papaja")
+library("modelsummary")
 r_refs("references.bib")
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work [@antia2020].
 These are the so-called "left behind children" who are common in migrant-sending regions in the Global South.
@@
 [@dewaard2018] analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
-[@popova2018] cited a 2016 study by UN Children's Fund Bulgaria, suggesting that one-fifth of Bulgarian children had one or both parents working abroad.
+[@popova2018] cited a 2016 study by UN Children's Fund Bulgaria indicating that one-fifth of Bulgarian children had one or both parents working abroad.
 In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration [@nbs2017].
@@
 
-A challenge arises in the empirical assessment of the causal relation between parental migration and children's education.
-It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Statistical advances in causal inference provides an alternative.
+A challenge arises in when we want to assess the causality between parental migration and children's education.
+Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+Statistical advances in causal inference provides an alternative approach.
 We can infer causality from a quasi-experimental design -- that is, only if the cause is as good as randomly assigned to individuals in the analysis, conditional on identification assumptions.
@@
 
+I hypothesized that in the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+This is because parental migration immediately disrupts family structure, resulting in lower academic performance of children.
+It takes longer time for parental migration to generate resources that improve children's performance at school.
+
+Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+[@xu2019] adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+They found that the absence of father only or both parents had "little or no association with negative outcomes" on children's academic and cognitive performances.
+Only-mother absence, however, showed a "strong association with negative outcomes" (p.
+1646).
+[@chen2019] conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+They found that mother migration was "negatively associated with children's social competence and academic performance," while father migration had no direct effects on the two outcomes (pp.
+860-861).
+
+I hypothesized that in the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+This relates to the social norms that designate men as breadwinners and women as caregivers.
+Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
+Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+
 The research on China's left behind children has three major shortcomings.
@@
 The survey administrator is the National Survey Research Center at Renmin University of China.
-The project's sampling adopted a multi-stage stratified probability proportional to size approach.
-Moreover, designed deliberately to focus on migrant children, the survey also oversampled those counties with large intranational migrant populations.
-The participants filled a paper-and-pencil questionnaire.
+The research team adopted the approach of multi-stage stratified probability proportional to size sampling.
+The selected participants filled a paper-and-pencil questionnaire.
 The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in seventh and ninth grades.
@@
 This was measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
-To facilitate comparison across schools and counties, I used standardized test scores instead of raw test scores.
+I calculated the standardized exam grades at the school-by-grade level to facilitate comparison across schools and counties.
 I removed the observations with missing values in any of the test score mentioned above.
+My choice of standardized exam grades over raw grades follows previous research [@young2018; @xu2019].
 
@@
 In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
-I identified seven types of migration arrangement: both parents absent, only father absent, only mother absent, father absent (unconditional), mother absent (unconditional), and both parents at home.
+I constructed six treatment dummy variables measuring migration arrangements: both parents absent, only father absent, only mother absent, father absent (unconditional), mother absent (unconditional).
+These arrangements can overlap with each other.
+The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
 I then removed the observations that reported other types of parental absence induced by divorce or death.
-
-## Data analysis
-
-Following Bai and colleagues' [-@bai2018; -@bai2020] approach, I adopted a difference-in-differences design to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-The model is: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the baseline exam score, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
 
@@
 
-The control variables include the internet assess at home, the self-rated number of books at home, and the years of education of the best-educated parent.
+The control variables at the household level include the internet assess at home, the self-rated number of books at home, and the years of education of the best-educated parent.
 These variables can approximate the level of human capital in a household.
@@
 
-I adopted `r cite_r("r-references.bib")` for all the analyses and the `fixest` package [@bergé2018] for building the two-way fixed effect models.
+## Data analysis
+
+I adopted `r cite_r("r-references.bib")` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
+I built a two-way fixed effect model in a difference-in-differences design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
+The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
+The model is: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the standardized test score at baseline, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
+The standard errors were clustered at the school level.
 

### 2022-06-03 MScThesisText.tex
bring back unadjusted model

@@
 \hypersetup{
-  pdftitle={Parental Migration and Left-Behind Adolescent's School Performance},
+  pdftitle={Parental Migration and Left-Behind Children's Cognitive and Academic Performances},
   pdfauthor={Jiancheng Gu1},
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-\title{Parental Migration and Left-Behind Adolescent's School Performance}
+\title{Parental Migration and Left-Behind Children's Cognitive and Academic Performances}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 
-\shorttitle{Left-Behind Adolescent}
+\shorttitle{Left-Behind Children}
 
@@
 
-Correspondence concerning this article should be addressed to Jiancheng Gu, Postal address. E-mail: \href{mailto:j4.gu@student.vu.nl}{\nolinkurl{j4.gu@student.vu.nl}}
+Correspondence concerning this article should be addressed to Jiancheng Gu, De Boelelaan 1105, 1081 HV - Amsterdam, The Netherlands.
+E-mail: \href{mailto:j4.gu@student.vu.nl}{\nolinkurl{j4.gu@student.vu.nl}}
 
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020).
 These are the so-called ``left behind children'' who are common in migrant-sending regions in the Global South.
-Their exact numbers in total are unavailable, but surveys provide some estimation.
+The global size of left behind children population is unavailable, but in-country surveys provide some estimation.
 (DeWaard et al., 2018) analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
-(Chae \& Glick, 2019) studied the World Bank's Migration and Remittances Surveys and indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010.
-In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration (NBS et al., 2017).
+(Popova, 2018) cited a 2016 study by UN Children's Fund Bulgaria indicating that one-fifth of Bulgarian children had one or both parents working abroad.
+In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration (NBS et al., 2017).
 
-Parental migration shapes child development -- such as human capital accumulation -- by exerting different effects that work oppositely.
+Parental migration impacts child-and-adolescence development by exerting different effects that work oppositely (Van Hook \& Glick, 2020).
+Consider children's education.
 Labor migrants send remittances back home, boosting the family income.
@@
 All these may hinder children's school performance.
-It is uncertain how these two opposing effects affect children's educational performance, which merits empirical investigation.
+It is uncertain how these two opposing effects shape children's educational performance, which merits empirical investigation.
+
+A challenge arises in when we want to assess the causality between parental migration and children's education.
+Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+Statistical advances in causal inference provides an alternative approach.
+We can infer causality from a quasi-experimental design -- that is, only if the cause is as good as randomly assigned to individuals in the analysis, conditional on identification assumptions.
 
@@
 The country has seen a huge scale of internal migration and salient challenges facing migrant parents and left behind children.
-More than 285 million Chinese people were in-country migrant workers.
+The National Bureau of Statistics reported that the number of in-country migrant workers exceeded 292.5 million by 2021(NBS, 2022).
 According to (Gu, 2021), current policy still limits internal migrants' access to public services and social benefits outside their hometowns, including public school for their children.
@@
 
-The research on China's left behind children has three major shortcomings.
-First, most literature focuses on children left behind in rural areas while negleting the urban counterparts.
-As (NBS et al., 2017) stated, the number of urban left behind children had been growing, and the trend would continue expectedly.
-Meanwhile, in-situ urbanization has turned a small proportion of children left behind in the countryside as urban residents.
-The second shortcoming lies in data and sampling.
-Some studies draw from cross-sectional surveys, making it hard to infer causal relations (Wen et al., 2020; Zhou et al., 2014).
-Others suffer from a limited sample size of less than one thousand participants (Liu et al., 2021; Yang et al., 2022) or a limited geographic coverage of one or a few towns (Shu, 2021; Yang et al., 2022).
-The third shortcoming lies in the selection and measurement of outcome.
-Wang et al.
-(2019) measure students' educational performance with the test score of only one academic subject, such as English or mathematics.
-The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
-
-This thesis aims to address the shortcomings in the study of parental migration's effect on left behind children's educational performance.
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
 I analyze the data from a nationally representative two-wave panel survey.
@@
 
+Researchers obtained mixed results regarding how migration-induced parental absence affects children's education.
+Using data collected from junior high school students, (Li et al., 2017) found that parental migration negatively impacts left-behind children's achievement in standardized mathematical test.
+(Wang et al., 2019) also collected data from students of junior high school, but discovered no overall effect of parental migration on the mathematical test grades of children left behind.
+(Bai et al., 2018) gathered data from primary school pupils.
+They reported that parental migration ``does not appear to have a negative effect'' on the standardized English test scores of left-behind children, and ``in some cases even appears to have a positive effect'' (p.~1165).
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+
+Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
+One model, the generation model, holds that parental migration brings forth greater resources in the form of economic capital.
+Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
+16).
+Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
+(Chang et al., 2019) provided evidence through interviews with migrant workers and their family members.
+They said that the city offered more jobs and higher pay than did the countryside.
+Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+
+The other theoretical model is the family disruption model.
+Children flourish under parental nurturing care.
+This term refers to the ``stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships'' (\textbf{black?}).
+Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
+The loss of nurturing care hinders children's accumulation of human capital.
+(Hong \& Fuller, 2019) talked to a group of left behind children in grade nine.
+These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
+Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.~14).
+
+I hypothesized that in the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+This is because parental migration immediately disrupts family structure, resulting in lower academic performance of children.
+It takes longer time for parental migration to generate resources that improve children's performance at school.
+
+Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+(Xu et al., 2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+They found that the absence of father only or both parents had ``little or no association with negative outcomes'' on children's academic and cognitive performances.
+Only-mother absence, however, showed a ``strong association with negative outcomes'' (p.~1646).
+(Chen et al., 2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+They found that mother migration was ``negatively associated with children's social competence and academic performance,'' while father migration had no direct effects on the two outcomes (pp.~860-861).
+
+I hypothesized that in the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+This relates to the social norms that designate men as breadwinners and women as caregivers.
+Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
+Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+As (NBS et al., 2017) stated, the number of urban left behind children had been growing, and the trend would continue.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014).
+Others suffer from a limited sample size of less than one thousand participants (Liu et al., 2021; Yang et al., 2022) or a limited geographic coverage of one or a few towns (Jin et al., 2020; Shu, 2021; Yang et al., 2022).
+The third shortcoming lies in the selection and measurement of outcome.
+(Chang et al., 2019; Wang et al., 2019) measure students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
+
 \hypertarget{methods}{%
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+I obtained the data from the China Education Panel Survey (CEPS).
+It is a nationally representative, school-based survey featuring junior high school students.
+The survey administrator is the National Survey Research Center at Renmin University of China.
+The research team adopted the approach of multi-stage stratified probability proportional to size sampling.
+The selected participants filled a paper-and-pencil questionnaire.
+The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in seventh and ninth grades.
+These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
+I only kept the 9,449 observations of seventh grade students and their parents, who completed the follow-up survey in the 2014-2015 academic year.
+
+\hypertarget{measurement}{%
+\subsection{Measurement}\label{measurement}}
+
+I explored two categories of adolescence development: academic and cognitive abilities.
+One key dependent variable, the student's cognitive skill, is measured by a fifteen-minute standardized test.
+The test covered three types of reasoning: verbal, visuospatial, and numerical.
+The raw scores of cognitive skill were then standardized.
+The other set of dependent variables concerned students' academic performance.
+This was measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
+I calculated the standardized exam grades at the school-by-grade level to facilitate comparison across schools and counties.
+I removed the observations with missing values in any of the test score mentioned above.
+My choice of standardized exam grades over raw grades follows previous research (Xu et al., 2019; Young \& Hannum, 2018).
+
+The key independent variable, the parental migration status, was identified by two items in the parent survey.
+In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
+I constructed six treatment dummy variables measuring migration arrangements: both parents absent, only father absent, only mother absent, father absent (unconditional), mother absent (unconditional).
+These arrangements can overlap with each other.
+The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
+I then removed the observations that reported other types of parental absence induced by divorce or death.
+
+The control variables at the student level include: student's age, gender, ethnicity, self-rated health, hukou type, and the number of siblings.
+I obtained the age by subtracting the student's birth year from the year 2013, the start of the baseline academic year.
+I coded students' gender as male = 0 and female = 1, ethnic minority status as Han Chinese = 0 and other ethnicity = 1, hukou status as rural (agricultural) hukou = 1 and other types = 0.
+I obtained the number of siblings of students through two items.
+Students who answered yes to the question ``Are you the only child of your family'' had no sibling.
+Those who answered no to this question were instructed to proceed to the next question, ``How many full or half siblings do you have'' -- elder brother, younger brother, elder sister, and younger sister, respectively.
+In these four columns, I transformed \texttt{NA} to zero.
+Then I added the four columns as the number of siblings of a student.
+
+The control variables include the internet assess at home, the self-rated number of books at home, and the years of education of the best-educated parent.
+These variables can approximate the level of human capital in a household.
+The internet assess was measured by the item ``Do {[}sic{]} your family own a computer and have an access to the Internet''.
+Those who answered ``Yes, we have both'' were coded as 1, and others as 0.
+The number of books was measured by the item ``How many books do your family own?
+(not including textbooks or magazines)''.
+Students chose from a range of 1 as ``very few'' to 5 as ``a great number''.
+The years of education of the best-educated parent were measured by two items.
+Students indicated their father's and mother's educational level, respectively.
+I transformed these two variables into years of education and retained the larger value.
 
@@
 
-We used R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+I built a two-way fixed effect model in a difference-in-differences design, following Bai and colleagues' (2018; 2020) approach.
+The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
+The model is: \[\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}\]For student \(i\) in school \(s\), \(\Delta score_{i,s}\) is the change in standardized test score between baseline and follow-up surveys, \(migr_{i,s}\) is the treatment dummy variable, \(FE_{s}\) is the school-level fixed effect, \(score_{i,s;base}\) is the baseline exam score, and \(X_{i,s}\) is the vector of covariates capturing the characteristics of children and their households.
+The standard errors were clustered at the school level.
 
@@
 \section{Results}\label{results}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1328}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1484}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1172}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1641}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.12*** & -0.08 & -0.10** & -0.16*** & -0.16*** & -0.14* \\
+& (0.03) & (0.04) & (0.04) & (0.04) & (0.04) & (0.06) \\
+Baseline Score & -0.64*** & -0.64*** & -0.64*** & -0.64*** & -0.64*** & -0.64*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+age & -0.11*** & -0.10*** & -0.11*** & -0.11*** & -0.10*** & -0.11*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.girl & 0.02 & 0.03 & 0.03 & 0.02 & 0.03 & 0.03 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.health & 0.00 & -0.01 & 0.00 & -0.01 & -0.01 & -0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.rural & 0.02 & 0.02 & 0.02 & 0.03 & 0.02 & 0.03 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.03) \\
+ch.sibling & -0.03 & -0.03 & -0.03 & -0.03 & -0.03 & -0.03 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.boarding & 0.01 & 0.01 & 0.01 & 0.00 & -0.01 & 0.00 \\
+& (0.04) & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\
+ch.ethn.minority & 0.07 & 0.08 & 0.08 & 0.07 & 0.07 & 0.07 \\
+& (0.06) & (0.07) & (0.07) & (0.07) & (0.07) & (0.08) \\
+par.edu.year & 0.01* & 0.01* & 0.01** & 0.01 & 0.01 & 0.01* \\
+& (0.00) & (0.00) & (0.00) & (0.00) & (0.00) & (0.00) \\
+home.book & 0.03** & 0.03* & 0.03** & 0.03** & 0.03** & 0.03** \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.internet & -0.01 & -0.02 & -0.01 & -0.02 & -0.02 & -0.02 \\
+& (0.02) & (0.03) & (0.03) & (0.02) & (0.03) & (0.03) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3869 & 3745 & 3629 \\
+R2 & 0.451 & 0.459 & 0.453 & 0.456 & 0.462 & 0.458 \\
+R2 Adj. & 0.434 & 0.441 & 0.435 & 0.438 & 0.444 & 0.439 \\
+R2 Within & 0.383 & 0.390 & 0.387 & 0.389 & 0.393 & 0.394 \\
+R2 Pseudo & & & & & & \\
+AIC & 7633.6 & 6948.9 & 7211.4 & 7117.0 & 6853.3 & 6694.5 \\
+BIC & 8418.1 & 7722.0 & 7988.5 & 7893.3 & 7625.6 & 7462.9 \\
+Log.Lik. & -3692.791 & -3350.450 & -3481.690 & -3434.478 & -3302.665 & -3223.231 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1328}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1484}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1172}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1641}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.07* & -0.13* & -0.09* & -0.03 & -0.03 & -0.03 \\
+& (0.03) & (0.05) & (0.04) & (0.04) & (0.05) & (0.07) \\
+Baseline Score & -0.36*** & -0.36*** & -0.36*** & -0.37*** & -0.36*** & -0.37*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+age & -0.05** & -0.06** & -0.05** & -0.06*** & -0.07*** & -0.06** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.girl & 0.19*** & 0.19*** & 0.19*** & 0.20*** & 0.20*** & 0.20*** \\
+& (0.02) & (0.03) & (0.02) & (0.03) & (0.03) & (0.03) \\
+ch.health & 0.04** & 0.05** & 0.04** & 0.04** & 0.04** & 0.04** \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.rural & -0.02 & -0.01 & -0.03 & -0.04 & -0.02 & -0.04 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+ch.sibling & -0.02 & -0.02 & -0.02 & -0.02 & -0.02 & -0.03 \\
+& (0.02) & (0.02) & (0.01) & (0.02) & (0.02) & (0.02) \\
+ch.boarding & 0.00 & 0.00 & 0.00 & -0.01 & 0.00 & -0.01 \\
+& (0.05) & (0.05) & (0.05) & (0.05) & (0.05) & (0.05) \\
+ch.ethn.minority & -0.04 & -0.05 & -0.03 & -0.06 & -0.08 & -0.05 \\
+& (0.06) & (0.06) & (0.06) & (0.06) & (0.06) & (0.06) \\
+par.edu.year & 0.00 & 0.01 & 0.00 & 0.00 & 0.01 & 0.00 \\
+& (0.00) & (0.00) & (0.00) & (0.00) & (0.00) & (0.00) \\
+home.book & 0.03** & 0.03* & 0.03* & 0.04** & 0.04** & 0.04** \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.internet & -0.05 & -0.05 & -0.06 & -0.04 & -0.04 & -0.06 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3869 & 3745 & 3629 \\
+R2 & 0.185 & 0.188 & 0.186 & 0.195 & 0.196 & 0.196 \\
+R2 Adj. & 0.160 & 0.161 & 0.160 & 0.168 & 0.169 & 0.168 \\
+R2 Within & 0.170 & 0.170 & 0.170 & 0.179 & 0.179 & 0.179 \\
+R2 Pseudo & & & & & & \\
+AIC & 8661.6 & 7865.5 & 8146.6 & 8018.7 & 7738.7 & 7505.3 \\
+BIC & 9446.1 & 8638.6 & 8923.7 & 8795.0 & 8511.0 & 8273.6 \\
+Log.Lik. & -4206.775 & -3808.734 & -3949.295 & -3885.352 & -3745.366 & -3628.626 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1328}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1484}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1172}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1641}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.07* & -0.13* & -0.12** & -0.03 & 0.01 & -0.13 \\
+& (0.03) & (0.05) & (0.04) & (0.04) & (0.05) & (0.07) \\
+Baseline Score & -0.30*** & -0.30*** & -0.30*** & -0.30*** & -0.30*** & -0.31*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+age & -0.07*** & -0.05** & -0.06** & -0.06*** & -0.06** & -0.05** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.girl & 0.08*** & 0.10*** & 0.09*** & 0.08** & 0.08** & 0.08** \\
+& (0.02) & (0.02) & (0.02) & (0.03) & (0.03) & (0.03) \\
+ch.health & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 & 0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.rural & 0.03 & 0.05 & 0.04 & 0.03 & 0.04 & 0.03 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+ch.sibling & 0.00 & -0.01 & -0.01 & -0.01 & 0.00 & -0.02 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.02) \\
+ch.boarding & 0.04 & 0.03 & 0.05 & 0.04 & 0.03 & 0.05 \\
+& (0.05) & (0.05) & (0.05) & (0.05) & (0.05) & (0.05) \\
+ch.ethn.minority & -0.03 & -0.04 & -0.04 & -0.04 & -0.04 & -0.05 \\
+& (0.06) & (0.07) & (0.07) & (0.07) & (0.07) & (0.07) \\
+par.edu.year & 0.01* & 0.01** & 0.01* & 0.01* & 0.01* & 0.01* \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.book & 0.00 & -0.01 & -0.01 & 0.00 & 0.00 & -0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.internet & -0.01 & -0.01 & -0.01 & -0.01 & -0.01 & -0.02 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3869 & 3745 & 3629 \\
+R2 & 0.173 & 0.182 & 0.180 & 0.175 & 0.178 & 0.182 \\
+R2 Adj. & 0.148 & 0.154 & 0.153 & 0.148 & 0.150 & 0.153 \\
+R2 Within & 0.158 & 0.163 & 0.164 & 0.161 & 0.160 & 0.167 \\
+R2 Pseudo & & & & & & \\
+AIC & 8287.6 & 7529.5 & 7791.3 & 7748.0 & 7483.5 & 7255.4 \\
+BIC & 9072.1 & 8302.6 & 8568.4 & 8524.3 & 8255.8 & 8023.8 \\
+Log.Lik. & -4019.779 & -3640.738 & -3771.655 & -3749.997 & -3617.766 & -3503.687 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1328}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1484}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1172}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1562}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1641}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.06* & -0.06 & -0.04 & -0.06 & -0.09* & 0.00 \\
+& (0.03) & (0.05) & (0.04) & (0.04) & (0.04) & (0.05) \\
+Baseline Score & -0.20*** & -0.20*** & -0.20*** & -0.20*** & -0.20*** & -0.20*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+age & -0.03* & -0.03 & -0.03 & -0.04* & -0.03 & -0.03 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.girl & 0.10*** & 0.10*** & 0.10*** & 0.10*** & 0.10*** & 0.10*** \\
+& (0.02) & (0.02) & (0.02) & (0.03) & (0.03) & (0.03) \\
+ch.health & 0.02* & 0.02* & 0.03** & 0.02 & 0.01 & 0.02* \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.rural & 0.03 & 0.03 & 0.03 & 0.02 & 0.02 & 0.02 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.sibling & 0.00 & 0.00 & 0.00 & 0.01 & 0.01 & 0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.boarding & -0.02 & 0.00 & -0.01 & -0.03 & -0.03 & -0.03 \\
+& (0.03) & (0.03) & (0.03) & (0.04) & (0.04) & (0.04) \\
+ch.ethn.minority & 0.02 & 0.01 & 0.00 & 0.02 & 0.02 & 0.00 \\
+& (0.04) & (0.04) & (0.05) & (0.05) & (0.05) & (0.05) \\
+par.edu.year & 0.01** & 0.01** & 0.01** & 0.01** & 0.01** & 0.01** \\
+& (0.00) & (0.00) & (0.00) & (0.00) & (0.00) & (0.00) \\
+home.book & 0.01 & 0.01 & 0.01 & 0.02 & 0.01 & 0.02 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.internet & -0.07** & -0.08** & -0.07** & -0.08** & -0.09*** & -0.09*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.03) & (0.03) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3869 & 3745 & 3629 \\
+R2 & 0.104 & 0.110 & 0.110 & 0.107 & 0.106 & 0.114 \\
+R2 Adj. & 0.077 & 0.079 & 0.081 & 0.078 & 0.076 & 0.083 \\
+R2 Within & 0.085 & 0.085 & 0.086 & 0.088 & 0.087 & 0.090 \\
+R2 Pseudo & & & & & & \\
+AIC & 7145.5 & 6470.0 & 6702.6 & 6708.4 & 6477.6 & 6268.0 \\
+BIC & 7930.1 & 7243.1 & 7479.7 & 7484.7 & 7249.9 & 7036.4 \\
+Log.Lik. & -3448.758 & -3110.976 & -3227.279 & -3230.208 & -3114.781 & -3009.986 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{verbatim}
+msummary(models_adj_unres_cog,
+  stars = c('*' = .05, '**' = .01, '***' = .001), 
+  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"),
+  output = 'markdown')
+\end{verbatim}
+
+\begin{verbatim}
+msummary(models_adj_unres_chn,
+         stars = c('*' = .05, '**' = .01, '***' = .001), 
+         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"),
+         output = 'markdown')
+\end{verbatim}
+
+\begin{verbatim}
+msummary(models_adj_unres_mat,
+         stars = c('*' = .05, '**' = .01, '***' = .001), 
+         fmt = 2,
+         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"),
+         output = 'markdown')
+\end{verbatim}
+
+\begin{verbatim}
+msummary(models_adj_unres_eng,
+         stars = c('*' = .05, '**' = .01, '***' = .001), 
+         fmt = 2,
+         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"),
+         output = 'markdown')
+\end{verbatim}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
+Antia, K., Boucsein, J., Deckert, A., Dambach, P., Račaitė, J., Šurkienė, G., Jaenisch, T., Horstick, O., \& Winkler, V.
+(2020).
+Effects of International Labour Migration on the Mental Health and Well-Being of Left-Behind Children: A Systematic Literature Review.
+\emph{International Journal of Environmental Research and Public Health}, \emph{17}(12), 4335.
+\url{https://doi.org/10.3390/ijerph17124335}
+
+\leavevmode\vadjust pre{\hypertarget{ref-arel-bundock2022}{}}%
+Arel-Bundock, V.
+(2022).
+\emph{Modelsummary: Summary tables and plots for statistical models and data: Beautiful, customizable, and publication-ready}.
+\url{https://vincentarelbundock.github.io/modelsummary/}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bai2020}{}}%
+Bai, Y., Neubauer, M., Ru, T., Shi, Y., Kenny, K., \& Rozelle, S.
+(2020).
+Impact of Second-Parent Migration on Student Academic Performance in Northwest China and its Implications.
+\emph{The Journal of Development Studies}, \emph{56}(8), 1523--1540.
+\url{https://doi.org/10.1080/00220388.2019.1690136}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chae2019}{}}%
-Chae, S., \& Glick, J.
-E.
-(2019).
-Educational Selectivity of Migrants and Current School Enrollment of Children Left behind: Analyses in Three African Countries.
-\emph{International Migration Review}, \emph{53}(3), 736--769.
-\url{https://doi.org/10.1177/0197918318772261}
+\leavevmode\vadjust pre{\hypertarget{ref-berguxe92018}{}}%
+Bergé, L. (2018). \emph{Efficient estimation of maximum likelihood models with multiple fixed-effects: the R package FENmlm}. \url{https://ideas.repec.org/p/luc/wpaper/18-13.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-botev2019}{}}%
+Botev, J., Égert, B., Smidova, Z., \& Turner, D. (2019). \emph{A new macroeconomic measure of human capital with strong empirical links to productivity}. \url{https://doi.org/10.1787/d12d7305-en}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bourdieu2002}{}}%
+Bourdieu, P. (2002). \emph{The Forms of Capital} (N. W. Biggart, Ed.; pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
 
@@
 \url{https://doi.org/10.1016/j.chieco.2019.01.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2019}{}}%
+Chen, X., Li, D., Liu, J., Fu, R., \& Liu, S.
+(2019).
+Father migration and mother migration: Different implications for social, school, and psychological adjustment of left-behind children in rural china.
+\emph{Journal of Contemporary China}, \emph{28}(120), 849--863.
+\url{https://doi.org/10.1080/10670564.2019.1594100}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
+Goldin, C. (2016). \emph{Human Capital} (C. Diebolt \& M. Haupert, Eds.; pp. 55--86). Springer. \url{https://doi.org/10.1007/978-3-642-40406-1_23}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gu2021}{}}%
@@
 \url{https://doi.org/10.1177/0011392120985874}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hong2019}{}}%
+Hong, Y., \& Fuller, C.
+(2019).
+Alone and {``}left behind{''}: A case study of {``}left-behind children{''} in rural china.
+\emph{Cogent Education}, \emph{6}(1), 1654236.
+\url{https://doi.org/10.1080/2331186X.2019.1654236}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
+Jin, X., Chen, W., Sun, I.
+Y., \& Liu, L.
+(2020).
+Physical health, school performance and delinquency: A comparative study of left-behind and non-left-behind children in rural China.
+\emph{Child Abuse \& Neglect}, \emph{109}, 104707.
+\url{https://doi.org/10.1016/j.chiabu.2020.104707}
+
+\leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
+Li, L., Wang, L., \& Nie, J.
+(2017).
+Effect of Parental Migration on the Academic Performance of Left-behind Middle School Students in Rural China.
+\emph{China \& World Economy}, \emph{25}(2), 45--59.
+\url{https://doi.org/10.1111/cwe.12193}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-murphy2022}{}}%
+Murphy, R. (2022). What does {`}left behind{'} mean to children living in migratory regions in rural China? \emph{Geoforum}, \emph{129}, 181--190. \url{https://doi.org/10.1016/j.geoforum.2022.01.012}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
+NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in Chinese{]}}. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}
+
 \leavevmode\vadjust pre{\hypertarget{ref-nbs2017}{}}%
@@
 \url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
+
+\leavevmode\vadjust pre{\hypertarget{ref-popova2018}{}}%
+Popova, A.
+(2018).
+Risk factors for the safety of the children from transnational families children left behind.
+\emph{Anthropological Researches and Studies}, \emph{1}(8), 25--35.
+\url{https://doi.org/10.26758/8.1.3}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vanhook2020}{}}%
+Van Hook, J., \& Glick, J.
+E.
+(2020).
+Spanning Borders, Cultures, and Generations: A~Decade of Research on Immigrant Families.
+\emph{Journal of Marriage and Family}, \emph{82}(1), 224--243.
+\url{https://doi.org/10.1111/jomf.12621}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wen2020}{}}%
-Wen, M., Wang, W., Wan, N., \& Su, D.
-(2020).
-Family Income and Student Educational and Cognitive Outcomes in China: Exploring the Material and Psychosocial Mechanisms.
-\emph{Social Sciences}, \emph{9}(12), 225.
-\url{https://doi.org/10.3390/socsci9120225}
+\leavevmode\vadjust pre{\hypertarget{ref-xu2019}{}}%
+Xu, Y., Xu, D., Simpkins, S., \& Warschauer, M.
+(2019).
+Does It Matter Which Parent is Absent?
+Labor Migration, Parenting, and Adolescent Development in China.
+\emph{Journal of Child and Family Studies}, \emph{28}(6), 1635--1649.
+\url{https://doi.org/10.1007/s10826-019-01382-z}
 
@@
 \url{https://doi.org/10.1007/s12187-021-09887-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-young2018}{}}%
+Young, N.
+A.
+E., \& Hannum, E.
+C.
+(2018).
+Childhood Inequality in China: Evidence from Recent Survey Data (2012{\textendash}2014).
+\emph{The China Quarterly}, \emph{236}, 1063--1087.
+\url{https://doi.org/10.1017/S0305741018001303}
 

### 2022-06-03 data/Gu-thesis-script.Rmd
bring back unadjusted model

@@
 
+```{r}
+df <- d_cl %>% select(
+  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
+  cog3pl, w1chn_std, w1mat_std, w1eng_std,
+  cog, chn_std, mat_std, eng_std,
+  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
+  par.edu.year, home.book, home.internet
+)
+```
+
+t-test
+```{r}
+t.test(w2cog3pl ~ migr, data = d_cl)
+t.test(w2chn ~ migr, data = d_cl)
+t.test(w2mat ~ migr, data = d_cl)
+t.test(w2eng ~ migr, data = d_cl)
+```
+
 ## Descriptive statistics
@@
 
+## DID unrestricted
+Regressing on cognitive test score (standardized)
+```{r}
+did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
+did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
+did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
+did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
+```
+
+Results
+```{r}
+models_unres_cog <- list(
+'Any Parent Absent' = did_unres_cog,
+'Only Mother Absent' = did_unres_cog_m_only,
+'Mother Absent' = did_unres_cog_m,
+'Only Father Absent' = did_unres_cog_f_only,
+'Father Absent' = did_unres_cog_f,
+'Both Parents Absent' = did_unres_cog_both) 
+models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"))
+```
+
+Regressing on Chinese exam score
+```{r}
+did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
+did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
+did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
+did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
+did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
+did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
+```
+
+Results
+```{r}
+models_unres_chn <- list(
+'Any Parent Absent' = did_unres_chn,
+'Only Mother Absent' = did_unres_chn_m_only,
+'Mother Absent' = did_unres_chn_m,
+'Only Father Absent' = did_unres_chn_f_only,
+'Father Absent' = did_unres_chn_f,
+'Both Parents Absent' = did_unres_chn_both) 
+models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"))
+```
+
+Regressing on Math score
+```{r}
+did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
+did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
+did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
+did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
+did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
+did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
+```
+
+Results
+```{r}
+models_unres_mat <- list(
+'Any Parent Absent' = did_unres_mat,
+'Only Mother Absent' = did_unres_mat_m_only,
+'Mother Absent' = did_unres_mat_m,
+'Only Father Absent' = did_unres_mat_f_only,
+'Father Absent' = did_unres_mat_f,
+'Both Parents Absent' = did_unres_mat_both) 
+models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"))
+```
+
+Regressing on English score
+```{r}
+did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
+did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
+did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
+did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
+did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
+did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
+```
+
+Results
+```{r}
+models_unres_eng <- list(
+'Any Parent Absent' = did_unres_eng,
+'Only Mother Absent' = did_unres_eng_m_only,
+'Mother Absent' = did_unres_eng_m,
+'Only Father Absent' = did_unres_eng_f_only,
+'Father Absent' = did_unres_eng_f,
+'Both Parents Absent' = did_unres_eng_both) 
+models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"))
+```
+
 ## DID adjusted
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2,
            coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2,
            coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"), output = 'markdown')
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2,
            coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"), output = 'markdown')
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2,
            coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"), output = 'markdown')

### 2022-06-10 MScThesisText.Rmd
change dependent var measures; remove outliers

@@
 I adopted `r cite_r("r-references.bib")` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
-I built a two-way fixed effect model in a difference-in-differences design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
+I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-The model is: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, $score_{i,s;base}$ is the standardized test score at baseline, and $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, and $score_{i,s;base}$ is the standardized test score at baseline.
+The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The model is unadjusted as it does not adjust for additional covariates.
+Theoretically, it is unnecessary to include covariates that vary over group but remain consant over time; They would cancel out in the two-way fixed effect model.
 The standard errors were clustered at the school level.
 
+In addition, I presented an unrestricted and adjusted DID model: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$where $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
+The control variables were measured in the baseline survey.
+This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
+
 # Results
+
+```{r}
+table_unres_cog
+```
+
+```{r}
+table_unres_chn
+```
+
+```{r}
+table_unres_mat
+```
+
+```{r}
+table_unres_eng
+```
 

### 2022-06-10 MScThesisText.tex
change dependent var measures; remove outliers

@@
 I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
-I built a two-way fixed effect model in a difference-in-differences design, following Bai and colleagues' (2018; 2020) approach.
+I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-The model is: \[\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}\]For student \(i\) in school \(s\), \(\Delta score_{i,s}\) is the change in standardized test score between baseline and follow-up surveys, \(migr_{i,s}\) is the treatment dummy variable, \(FE_{s}\) is the school-level fixed effect, \(score_{i,s;base}\) is the baseline exam score, and \(X_{i,s}\) is the vector of covariates capturing the characteristics of children and their households.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \varepsilon_{i,s}\]For student \(i\) in school \(s\), \(\Delta score_{i,s}\) is the change in standardized test score between baseline and follow-up surveys, \(migr_{i,s}\) is the treatment dummy variable, \(FE_{s}\) is the school-level fixed effect, and \(score_{i,s;base}\) is the standardized test score at baseline.
+The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The model is unadjusted as it does not adjust for additional covariates.
+Theoretically, it is unnecessary to include covariates that vary over group but remain consant over time; They would cancel out in the two-way fixed effect model.
 The standard errors were clustered at the school level.
+
+In addition, I presented an unrestricted and adjusted DID model: \[\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}\]where \(X_{i,s}\) is the vector of covariates capturing the characteristics of children and their households.
+The control variables were measured in the baseline survey.
+This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
 
@@
 \section{Results}\label{results}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1520}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1680}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.12*** & -0.07 & -0.10* & -0.16*** & -0.16*** & -0.16* \\
+& (0.03) & (0.04) & (0.04) & (0.04) & (0.04) & (0.07) \\
+Baseline Score & -0.62*** & -0.63*** & -0.63*** & -0.62*** & -0.62*** & -0.63*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3745 & 3869 & 3629 \\
+R2 & 0.440 & 0.449 & 0.442 & 0.453 & 0.445 & 0.448 \\
+R2 Adj. & 0.424 & 0.432 & 0.425 & 0.436 & 0.429 & 0.430 \\
+R2 Within & 0.371 & 0.379 & 0.374 & 0.383 & 0.377 & 0.382 \\
+R2 Pseudo & & & & & & \\
+AIC & 7697.6 & 6999.8 & 7273.5 & 6898.0 & 7171.1 & 6746.1 \\
+BIC & 8418.9 & 7710.6 & 7988.0 & 7608.0 & 7884.8 & 7452.5 \\
+Log.Lik. & -3734.792 & -3385.924 & -3522.761 & -3335.002 & -3471.561 & -3259.049 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1520}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1680}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.08* & -0.12* & -0.10* & -0.05 & -0.05 & -0.05 \\
+& (0.03) & (0.05) & (0.04) & (0.05) & (0.04) & (0.07) \\
+Baseline Score & -0.31*** & -0.31*** & -0.31*** & -0.32*** & -0.32*** & -0.32*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3745 & 3869 & 3629 \\
+R2 & 0.163 & 0.166 & 0.165 & 0.170 & 0.170 & 0.172 \\
+R2 Adj. & 0.140 & 0.140 & 0.140 & 0.144 & 0.145 & 0.145 \\
+R2 Within & 0.148 & 0.147 & 0.148 & 0.153 & 0.153 & 0.153 \\
+R2 Pseudo & & & & & & \\
+AIC & 8749.8 & 7947.9 & 8227.8 & 7838.8 & 8117.1 & 7596.2 \\
+BIC & 9471.1 & 8658.6 & 8942.3 & 8548.8 & 8830.8 & 8302.6 \\
+Log.Lik. & -4260.905 & -3859.940 & -3999.901 & -3805.376 & -3944.541 & -3684.093 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1520}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1680}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.08* & -0.12* & -0.13** & 0.01 & -0.04 & -0.14* \\
+& (0.03) & (0.05) & (0.04) & (0.05) & (0.04) & (0.07) \\
+Baseline Score & -0.29*** & -0.29*** & -0.29*** & -0.29*** & -0.29*** & -0.30*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3745 & 3869 & 3629 \\
+R2 & 0.164 & 0.172 & 0.170 & 0.169 & 0.167 & 0.173 \\
+R2 Adj. & 0.141 & 0.146 & 0.145 & 0.143 & 0.142 & 0.147 \\
+R2 Within & 0.149 & 0.153 & 0.154 & 0.151 & 0.153 & 0.158 \\
+R2 Pseudo & & & & & & \\
+AIC & 8312.4 & 7556.5 & 7816.0 & 7503.0 & 7765.6 & 7272.1 \\
+BIC & 9033.7 & 8267.3 & 8530.5 & 8213.0 & 8479.3 & 7978.5 \\
+Log.Lik. & -4042.216 & -3664.273 & -3794.002 & -3637.509 & -3768.779 & -3522.049 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1520}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1600}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1200}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1680}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.06* & -0.05 & -0.04 & -0.09* & -0.07 & -0.01 \\
+& (0.03) & (0.05) & (0.04) & (0.04) & (0.04) & (0.05) \\
+Baseline Score & -0.17*** & -0.17*** & -0.18*** & -0.17*** & -0.18*** & -0.18*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4134 & 3770 & 3894 & 3745 & 3869 & 3629 \\
+R2 & 0.091 & 0.097 & 0.098 & 0.092 & 0.094 & 0.100 \\
+R2 Adj. & 0.065 & 0.069 & 0.071 & 0.064 & 0.066 & 0.071 \\
+R2 Within & 0.071 & 0.072 & 0.073 & 0.073 & 0.073 & 0.076 \\
+R2 Pseudo & & & & & & \\
+AIC & 7185.6 & 6502.1 & 6737.9 & 6513.7 & 6748.0 & 6303.0 \\
+BIC & 7906.8 & 7212.8 & 7452.4 & 7223.7 & 7461.7 & 7009.4 \\
+Log.Lik. & -3478.783 & -3137.026 & -3254.945 & -3142.869 & -3259.978 & -3037.495 \\
+Std.Errors & by: schids & by: schids & by: schids & by: schids & by: schids & by: schids \\
+FE: schids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
 
@@
 
-\begin{verbatim}
-msummary(models_adj_unres_cog,
-  stars = c('*' = .05, '**' = .01, '***' = .001), 
-  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"),
-  output = 'markdown')
-\end{verbatim}
-
-\begin{verbatim}
-msummary(models_adj_unres_chn,
-         stars = c('*' = .05, '**' = .01, '***' = .001), 
-         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"),
-         output = 'markdown')
-\end{verbatim}
-
-\begin{verbatim}
-msummary(models_adj_unres_mat,
-         stars = c('*' = .05, '**' = .01, '***' = .001), 
-         fmt = 2,
-         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"),
-         output = 'markdown')
-\end{verbatim}
-
-\begin{verbatim}
-msummary(models_adj_unres_eng,
-         stars = c('*' = .05, '**' = .01, '***' = .001), 
-         fmt = 2,
-         coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"),
-         output = 'markdown')
-\end{verbatim}
-
 \hypertarget{discussion}{%

### 2022-06-10 data/Gu-thesis-script.Rmd
change dependent var measures; remove outliers

--- 2022-06-03 data/Gu-thesis-script.Rmd
@@
 library(modelsummary)
+library(MatchIt)
+library(datawizard)
 ```
@@
 ```{r}
-d_1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
-d_2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
-d <- d_1 %>% right_join(d_2, by=c('ids', 'clsids', 'schids', 'ctyids'))
+dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
+dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
+d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
@@
   age = 2013 - a02a, #student's age at baseline
-  local.resi = age - a07 #years of residence at the current county
+  local.resi = age - a07, #years of residence at the current county
+  w1chn_100 = tr_chn/w2upchn*100,
+  w1mat_100 = tr_mat/w2upmat*100,
+  w1eng_100 = tr_eng/w2upeng*100,
+  w2chn_100 = w2chn/w2upchn*100,
+  w2mat_100 = w2mat/w2upmat*100,
+  w2eng_100 = w2eng/w2upeng*100
 )
+d <- d %>% mutate(
+  w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
+  w2ttl_100 = w2chn_100 + w2mat_100 + w2eng_100,
+  )
+```
+
+```{r}
+d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
@@
 ```{r}
-d <- d %>% #Total exam grades at wave 1 and at wave 2
-  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
-         w2ttl = w2chn + w2mat + w2eng) 
-d <- d %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
+d <- d %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
   group_by(schids) %>%
-  mutate(w1chn_std = as.numeric(scale(tr_chn)),
-         w1mat_std = as.numeric(scale(tr_mat)),
-         w1eng_std = as.numeric(scale(tr_eng)),
-         w1ttl_std = as.numeric(scale(w1ttl)),
-         w2chn_std = as.numeric(scale(w2chn)),
-         w2mat_std = as.numeric(scale(w2mat)),
-         w2eng_std = as.numeric(scale(w2eng)),
-         w2ttl_std = as.numeric(scale(w2ttl))
+  mutate(w1chn_mean = mean(w1chn_100, na.rm=T),
+         w1mat_mean = mean(w1mat_100, na.rm=T),
+         w1eng_mean = mean(w1eng_100, na.rm=T),
+         w1ttl_mean = mean(w1ttl_100, na.rm=T),
+         w2chn_mean = mean(w2chn_100, na.rm=T),
+         w2mat_mean = mean(w2mat_100, na.rm=T),
+         w2eng_mean = mean(w2eng_100, na.rm=T),
+         w2ttl_mean = mean(w2ttl_100, na.rm=T),
          )  %>% ungroup()
+d <- d %>% 
+  mutate(w1chn_dif = w1chn_100 - w1chn_mean,
+         w1mat_dif = w1mat_100 - w1mat_mean,
+         w1eng_dif = w1eng_100 - w1eng_mean,
+         w1ttl_dif = w1ttl_100 - w1ttl_mean,
+         w2chn_dif = w2chn_100 - w2chn_mean,
+         w2mat_dif = w2mat_100 - w2mat_mean,
+         w2eng_dif = w2eng_100 - w2eng_mean,
+         w2ttl_dif = w2ttl_100 - w2ttl_mean,
+         cog_dif = w2cog3pl - cog3pl
+         )
 ```
@@
 ## Variables 
-Dependent variables: Outcome differences between wave 2 and wave 1
 ```{r}
-d_cl <- d_cl %>% mutate(
-  chn_std = w2chn_std - w1chn_std,
-  mat_std = w2mat_std - w1mat_std,
-  eng_std = w2eng_std - w1eng_std,
-  ttl_std = w2ttl_std - w1ttl_std,
-  cog = w2cog3pl - cog3pl 
-) %>%
-  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
+d_cl <- d_cl %>% 
+  mutate(chn_dif = w2chn_dif - w1chn_dif,
+         mat_dif = w2mat_dif - w1mat_dif,
+         eng_dif = w2eng_dif - w1eng_dif,
+         ttl_dif = w2ttl_dif - w1ttl_dif) %>%
+  drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
 ```
@@
 
+```
+df <- d_cl %>% select(
+  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
+  cog3pl, w1chn_dif, w1mat_std, w1eng_std,
+  cog, chn_std, mat_dif, eng_dif,
+  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
+  par.edu.year, home.book, home.internet
+)
+```
+
+t-test
+```{r}
+t.test(cog_dif ~ migr, data = d_cl1)
+t.test(ttl_dif ~ migr, data = d_cl1)
+t.test(chn_dif ~ migr, data = d_cl1)
+t.test(mat_dif ~ migr, data = d_cl1)
+t.test(eng_dif ~ migr, data = d_cl1)
+```
+
 ## Descriptive statistics
@@
             mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_std, na.rm=T),
-            mean_chn = mean(w2chn_std, na.rm=T),
-            mean_mat = mean(w2mat_std, na.rm=T),
-            mean_eng = mean(w2eng_std, na.rm=T)
+            mean_ttl = mean(w2ttl_dif, na.rm=T),
+            mean_chn = mean(w2chn_dif, na.rm=T),
+            mean_mat = mean(w2mat_dif, na.rm=T),
+            mean_eng = mean(w2eng_dif, na.rm=T)
             ) %>%
@@
   summarise(n_cases = n(),
-            mean_change_cog = mean(cog, na.rm=T),
-            mean_change_ttl = mean(ttl_std, na.rm=T),
-            mean_change_chn = mean(chn_std, na.rm=T),
-            mean_change_mat = mean(mat_std, na.rm=T),
-            mean_change_eng = mean(eng_std, na.rm=T)
+            mean_change_cog = mean(cog_dif, na.rm=T),
+            mean_change_ttl = mean(ttl_dif, na.rm=T),
+            mean_change_chn = mean(chn_dif, na.rm=T),
+            mean_change_mat = mean(mat_dif, na.rm=T),
+            mean_change_eng = mean(eng_dif, na.rm=T)
             ) %>%
@@
   summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_std, na.rm=T),
-            mean_chn = mean(w2chn_std, na.rm=T),
-            mean_mat = mean(w2mat_std, na.rm=T),
-            mean_eng = mean(w2eng_std, na.rm=T)
+            mean_change_cog = mean(cog_dif, na.rm=T),
+            mean_change_ttl = mean(ttl_dif, na.rm=T),
+            mean_change_chn = mean(chn_dif, na.rm=T),
+            mean_change_mat = mean(mat_dif, na.rm=T),
+            mean_change_eng = mean(eng_dif, na.rm=T)
             ) %>%
@@
 
-## DID adjusted
-$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
-$$X_{i,s}$$ denotes a vector of covariates about the characteristics of students, parents, and households.
-
+## DID unrestricted
 Regressing on cognitive test score (standardized)
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl1) 
+did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl1) 
+did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl1) 
+did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl1) 
+did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl1) 
+did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl1)
 ```
@@
 ```{r}
-models_adj_cog <- list(
-did_adj_cog,
-did_adj_cog_m_only,
-did_adj_cog_m,
-did_adj_cog_f_only,
-did_adj_cog_f,
-did_adj_cog_both) 
-models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+models_unres_cog <- list(
+'Any Parent Absent' = did_unres_cog,
+'Only Mother Absent' = did_unres_cog_m_only,
+'Mother Absent' = did_unres_cog_m,
+'Only Father Absent' = did_unres_cog_f_only,
+'Father Absent' = did_unres_cog_f,
+'Both Parents Absent' = did_unres_cog_both) 
+table_unres_cog <- models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
+table_unres_cog
 ```
 
-Regressing on total exam score
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_ttl_both <- feols(ttl_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif | schids, data = d_cl1) 
+did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif | schids, data = d_cl1) 
+did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif | schids, data = d_cl1) 
+did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif | schids, data = d_cl1) 
+did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif | schids, data = d_cl1) 
+did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif | schids, data = d_cl1)
+```
+
+```{r}
+models_unres_ttl <- list(
+'Any Parent Absent' = did_unres_ttl,
+'Only Mother Absent' = did_unres_ttl_m_only,
+'Mother Absent' = did_unres_ttl_m,
+'Only Father Absent' = did_unres_ttl_f_only,
+'Father Absent' = did_unres_ttl_f,
+'Both Parents Absent' = did_unres_ttl_both) 
+table_unres_ttl <- models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl
+```
+
+Regressing on Chinese exam score
+```{r}
+did_unres_chn <- feols(chn_dif ~ migr + w1chn_dif | schids, data = d_cl1) 
+did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif | schids, data = d_cl1) 
+did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif | schids, data = d_cl1) 
+did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif | schids, data = d_cl1) 
+did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif | schids, data = d_cl1) 
+did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif | schids, data = d_cl1)
 ```
@@
 ```{r}
-models_adj_ttl <- list(
-did_adj_ttl,
-did_adj_ttl_m_only,
-did_adj_ttl_m,
-did_adj_ttl_f_only,
-did_adj_ttl_f,
-did_adj_ttl_both) 
-models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+models_unres_chn <- list(
+'Any Parent Absent' = did_unres_chn,
+'Only Mother Absent' = did_unres_chn_m_only,
+'Mother Absent' = did_unres_chn_m,
+'Only Father Absent' = did_unres_chn_f_only,
+'Father Absent' = did_unres_chn_f,
+'Both Parents Absent' = did_unres_chn_both) 
+table_unres_chn <- models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_dif" = "Baseline difference"), output = 'markdown')
+table_unres_chn
 ```
 
-Regressing on Chinese exam score
+Regressing on Math score
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_chn_m <- feols(chn_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_chn_f <- feols(chn_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_unres_mat <- feols(mat_dif ~ migr + w1mat_dif| schids, data = d_cl1) 
+did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif| schids, data = d_cl1) 
+did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif| schids, data = d_cl1) 
+did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif| schids, data = d_cl1) 
+did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif| schids, data = d_cl1) 
+did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif| schids, data = d_cl1)
 ```
@@
 ```{r}
-models_adj_chn <- list(
-did_adj_chn,
-did_adj_chn_m_only,
-did_adj_chn_m,
-did_adj_chn_f_only,
-did_adj_chn_f,
-did_adj_chn_both) 
-models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+models_unres_mat <- list(
+'Any Parent Absent' = did_unres_mat,
+'Only Mother Absent' = did_unres_mat_m_only,
+'Mother Absent' = did_unres_mat_m,
+'Only Father Absent' = did_unres_mat_f_only,
+'Father Absent' = did_unres_mat_f,
+'Both Parents Absent' = did_unres_mat_both) 
+table_unres_mat <- models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_dif" = "Baseline Score"), output = 'markdown')
+table_unres_mat
 ```
 
-Regressing on Math score
+Regressing on English score
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_mat_m <- feols(mat_std ~ migr_mo + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_mat_f <- feols(mat_std ~ migr_fa + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_unres_eng <- feols(eng_dif ~ migr + w1eng_dif| schids, data = d_cl1) 
+did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif| schids, data = d_cl1)
+did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif| schids, data = d_cl1) 
+did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif| schids, data = d_cl1) 
+did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif| schids, data = d_cl1) 
+did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif| schids, data = d_cl1)
 ```
@@
 ```{r}
-models_adj_mat <- list(
-did_adj_mat,
-did_adj_mat_m_only,
-did_adj_mat_m,
-did_adj_mat_f_only,
-did_adj_mat_f,
-did_adj_mat_both) 
-models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
-```
-
-Regressing on English score
-```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_adj_eng <- list(
-did_adj_eng,
-did_adj_eng_m_only,
-did_adj_eng_m,
-did_adj_eng_f_only,
-did_adj_eng_f,
-did_adj_eng_both) 
-models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+models_unres_eng <- list(
+'Any Parent Absent' = did_unres_eng,
+'Only Mother Absent' = did_unres_eng_m_only,
+'Mother Absent' = did_unres_eng_m,
+'Only Father Absent' = did_unres_eng_f_only,
+'Father Absent' = did_unres_eng_f,
+'Both Parents Absent' = did_unres_eng_both) 
+table_unres_eng <- models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_dif" = "Baseline difference"), output = 'markdown')
+table_unres_eng
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog_dif ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
+
 Results
@@
 'Mother Absent' = did_adj_unres_cog_m,
-'Only Father Absent' = did_adj_unres_cog_f,
-'Mother Absent' = did_adj_unres_cog_f_only,
+'Only Father Absent' = did_adj_unres_cog_f_only,
+'Father Absent' = did_adj_unres_cog_f,
 'Both Parents Absent' = did_adj_unres_cog_both) 
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2,
            coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
+table_adj_unres_cog
 ```
+
 Regressing on total exam score
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
+
 Results
@@
 models_adj_unres_ttl <- list(
-did_adj_unres_ttl,
-did_adj_unres_ttl_m_only,
-did_adj_unres_ttl_m,
-did_adj_unres_ttl_f_only,
-did_adj_unres_ttl_f,
-did_adj_unres_ttl_both) 
-models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
+'Any Parent Absent' = did_adj_unres_ttl,
+'Only Mother Absent' = did_adj_unres_ttl_m_only,
+'Mother Absent' = did_adj_unres_ttl_m,
+'Only Father Absent' = did_adj_unres_ttl_f_only,
+'Father Absent' = did_adj_unres_ttl_f,
+'Both Parents Absent' = did_adj_unres_ttl_both) 
+table_adj_unres_ttl <- models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_ttl
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
+
 Results
@@
 'Mother Absent' = did_adj_unres_chn_m,
-'Only Father Absent' = did_adj_unres_chn_f,
-'Mother Absent' = did_adj_unres_chn_f_only,
+'Only Father Absent' = did_adj_unres_chn_f_only,
+'Father Absent' = did_adj_unres_chn_f,
 'Both Parents Absent' = did_adj_unres_chn_both) 
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_std" = "Baseline Score"), output = 'markdown')
+           fmt = 2,
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_chn
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
+
 Results
@@
 'Mother Absent' = did_adj_unres_mat_m,
-'Only Father Absent' = did_adj_unres_mat_f,
-'Mother Absent' = did_adj_unres_mat_f_only,
+'Only Father Absent' = did_adj_unres_mat_f_only,
+'Father Absent' = did_adj_unres_mat_f,
 'Both Parents Absent' = did_adj_unres_mat_both) 
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_std" = "Baseline Score"), output = 'markdown')
+           fmt = 2,
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_mat
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
@@
 'Mother Absent' = did_adj_unres_eng_m,
-'Only Father Absent' = did_adj_unres_eng_f,
-'Mother Absent' = did_adj_unres_eng_f_only,
+'Only Father Absent' = did_adj_unres_eng_f_only,
+'Father Absent' = did_adj_unres_eng_f,
 'Both Parents Absent' = did_adj_unres_eng_both) 
@@
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_std" = "Baseline Score"), output = 'markdown')
+           fmt = 2,
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_eng
 ```
+
+## Matching
+```{r}
+m.out <- matchit(migr ~ age + cog3pl + w1ttl_100 + ch.girl + ch.health + ch.rural + ch.sibling + ch.boarding + ch.ethn.minority + par.edu.year	+ home.book	+ home.internet, data = d_cl1, method = "nearest")
+summary(m.out, un = FALSE)
+```
+
+```{r}
+d_match <- match.data(m.out)
+```
+
+```{r}
+feols(cog_dif ~ migr + cog3pl + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2)
+feols(ttl_dif ~ migr + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2)
+```

### 2022-06-11 data/Gu-thesis-script.Rmd
school and county info

@@
 d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
+d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
 ```
@@
 
+Detect outliers
 ```{r}
+d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
 d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))

### 2022-06-11 data/Gu-thesis-script.Rmd
raw score as independent var

@@
 d_cl <- d_cl %>% 
-  mutate(chn_dif = w2chn_dif - w1chn_dif,
-         mat_dif = w2mat_dif - w1mat_dif,
-         eng_dif = w2eng_dif - w1eng_dif,
-         ttl_dif = w2ttl_dif - w1ttl_dif) %>%
+  mutate(chn_dif = w2chn_100 - w1chn_100,
+         mat_dif = w2mat_100 - w1mat_100,
+         eng_dif = w2eng_100 - w1eng_100,
+         ttl_dif = w2ttl_100 - w1ttl_100) %>%
   drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
@@
 ```{r}
-did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif | schids, data = d_cl1)
+did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | schids, data = d_cl1) 
+did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | schids, data = d_cl1) 
+did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | schids, data = d_cl1) 
+did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | schids, data = d_cl1) 
+did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | schids, data = d_cl1) 
+did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | schids, data = d_cl1)
 ```
@@
 ```{r}
-did_unres_chn <- feols(chn_dif ~ migr + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif | schids, data = d_cl1)
+did_unres_chn <- feols(chn_dif ~ migr + w1chn_100 | schids, data = d_cl1) 
+did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100 | schids, data = d_cl1) 
+did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100 | schids, data = d_cl1) 
+did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100 | schids, data = d_cl1) 
+did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100 | schids, data = d_cl1) 
+did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100 | schids, data = d_cl1)
 ```
@@
 ```{r}
-did_unres_mat <- feols(mat_dif ~ migr + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif| schids, data = d_cl1)
+did_unres_mat <- feols(mat_dif ~ migr + w1mat_100| schids, data = d_cl1) 
+did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100| schids, data = d_cl1) 
+did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100| schids, data = d_cl1) 
+did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100| schids, data = d_cl1) 
+did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100| schids, data = d_cl1) 
+did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100| schids, data = d_cl1)
 ```
@@
 ```{r}
-did_unres_eng <- feols(eng_dif ~ migr + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif| schids, data = d_cl1)
-did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif| schids, data = d_cl1)
+did_unres_eng <- feols(eng_dif ~ migr + w1eng_100| schids, data = d_cl1) 
+did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100| schids, data = d_cl1)
+did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100| schids, data = d_cl1) 
+did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100| schids, data = d_cl1) 
+did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100| schids, data = d_cl1) 
+did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100| schids, data = d_cl1)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
 ```

### 2022-06-11 data/Gu-thesis-script.Rmd
more control var

--- 2022-06-10 data/Gu-thesis-script.Rmd
@@
 d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
+d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
+d_sch2 <- read_dta('cepsw2principalCN.dta')
 ```
@@
 ```{r}
-dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
+dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) %>% left_join(d_sch1, by=c('schids', 'ctyids', 'fall'))
 dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
@@
   local.resi = age - a07, #years of residence at the current county
-  w1chn_100 = tr_chn/w2upchn*100,
+  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
   w1mat_100 = tr_mat/w2upmat*100,
@@
 
+Detect outliers
 ```{r}
-d_cl1 <- d_cl %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
+d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
+d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
@@
 Compute standardized exam grades (within-school z-scores)
-```{r}
-d <- d %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
+```{}
+d1 <- d1 %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
   group_by(schids) %>%
@@
          )  %>% ungroup()
-d <- d %>% 
+```
+
+```{}
+d1 <- d1 %>% 
   mutate(w1chn_dif = w1chn_100 - w1chn_mean,
@@
          w2ttl_dif = w2ttl_100 - w2ttl_mean,
-         cog_dif = w2cog3pl - cog3pl
+
          )
@@
 ```{r}
-d_cl <- d %>% 
+d_cl <- d1 %>% 
   filter(w2a0801==1) %>% #parents who are married (and alive)
   filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
-  filter(local.resi>=6) #having stayed in the current county for at least six years (duration of primary school) before baseline
+  filter(stmigrant==1) #having stayed in the current county for at least six years (duration of primary school) before baseline
 ```
@@
 d_cl <- d_cl %>% 
-  mutate(chn_dif = w2chn_dif - w1chn_dif,
-         mat_dif = w2mat_dif - w1mat_dif,
-         eng_dif = w2eng_dif - w1eng_dif,
-         ttl_dif = w2ttl_dif - w1ttl_dif) %>%
+  mutate(chn_dif = w2chn_100 - w1chn_100,
+         mat_dif = w2mat_100 - w1mat_100,
+         eng_dif = w2eng_100 - w1eng_100,
+         ttl_dif = w2ttl_100 - w1ttl_100,
+         cog_dif = w2cog3pl - cog3pl) %>%
   drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
@@
          ch.girl = if_else(a01 == 2, 1, 0), #student is girl
-         ch.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
+         ch.rural = sthktype, #student holds rural (agricultural) hukou
          #ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
-         ch.boarding = if_else(c18 == 1, 1, 0), #student is boarding at school
+         ch.boarding = stbrd, #student is boarding at school
          ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
          ch.health = a17, #student's self-reported health
-         par.edu = if_else(b06 > b07, b06, b07), #Among two parents, the best-educated one's educational level
-         #fa.edu = b07,
-         #mo.edu = b06,
+         ch.skip.grd = if_else(c03 == 0, 0, 1),
+         ch.repeat.grd = if_else(c04 == 0, 0, 1),
+         ch.illness = if_else(a10 == 1, 1, 0),
+         ch.preschool = if_else(c01 == 1, 1, 0),
+         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
+         par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
+         home.finances = steco_3c,
          home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
@@
 ) %>% drop_na(
-  ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.minority, ch.health, par.edu, home.internet, home.book)
+ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.minority, ch.health, ch.skip.grd, ch.repeat.grd, ch.illness, ch.preschool, par.edu, par.ccp, home.internet, home.book, home.finances)
 ```
@@
 ```{r}
-d_cl$b0201 <- d_cl$b0201 %>% replace_na(0)
-d_cl$b0202 <- d_cl$b0202 %>% replace_na(0)
-d_cl$b0203 <- d_cl$b0203 %>% replace_na(0)
-d_cl$b0204 <- d_cl$b0204 %>% replace_na(0)
-d_cl <- d_cl %>% mutate(ch.sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
+d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
+d_cl <- d_cl %>% mutate(ch.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
   drop_na(ch.sibling)
@@
   migr_both = NA
-  ) %>% drop_na(migr)
+  ) 
+d_cl <- d_cl %>% drop_na(migr)
 ```
@@
 ```{r}
-t.test(cog_dif ~ migr, data = d_cl1)
-t.test(ttl_dif ~ migr, data = d_cl1)
-t.test(chn_dif ~ migr, data = d_cl1)
-t.test(mat_dif ~ migr, data = d_cl1)
-t.test(eng_dif ~ migr, data = d_cl1)
+t.test(cog_dif ~ migr, data = d_cl)
+t.test(ttl_dif ~ migr, data = d_cl)
+t.test(chn_dif ~ migr, data = d_cl)
+t.test(mat_dif ~ migr, data = d_cl)
+t.test(eng_dif ~ migr, data = d_cl)
 ```
@@
 ```{r}
-did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl1) 
-did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl1) 
-did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl1) 
-did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl1) 
-did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl1) 
-did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl1)
+did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl) 
+did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl) 
+did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl) 
+did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl) 
+did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl)
 ```
@@
 ```{r}
-did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif | schids, data = d_cl1) 
-did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif | schids, data = d_cl1)
+did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | schids, data = d_cl) 
+did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | schids, data = d_cl) 
+did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | schids, data = d_cl) 
+did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | schids, data = d_cl) 
+did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | schids, data = d_cl) 
+did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | schids, data = d_cl)
 ```
@@
 ```{r}
-did_unres_chn <- feols(chn_dif ~ migr + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif | schids, data = d_cl1) 
-did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif | schids, data = d_cl1)
+did_unres_chn <- feols(chn_dif ~ migr + w1chn_100 | schids, data = d_cl) 
+did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100 | schids, data = d_cl) 
+did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100 | schids, data = d_cl) 
+did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100 | schids, data = d_cl) 
+did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100 | schids, data = d_cl) 
+did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100 | schids, data = d_cl)
 ```
@@
 ```{r}
-did_unres_mat <- feols(mat_dif ~ migr + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif| schids, data = d_cl1) 
-did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif| schids, data = d_cl1)
+did_unres_mat <- feols(mat_dif ~ migr + w1mat_100| schids, data = d_cl) 
+did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100| schids, data = d_cl) 
+did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100| schids, data = d_cl) 
+did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100| schids, data = d_cl) 
+did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100| schids, data = d_cl) 
+did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100| schids, data = d_cl)
 ```
@@
 ```{r}
-did_unres_eng <- feols(eng_dif ~ migr + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif| schids, data = d_cl1)
-did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif| schids, data = d_cl1) 
-did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif| schids, data = d_cl1)
+did_unres_eng <- feols(eng_dif ~ migr + w1eng_100| schids, data = d_cl) 
+did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100| schids, data = d_cl)
+did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100| schids, data = d_cl) 
+did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100| schids, data = d_cl) 
+did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100| schids, data = d_cl) 
+did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100| schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog_dif ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_cog <- feols(cog_dif ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_dif  + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
-did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl1)
+did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-m.out <- matchit(migr ~ age + cog3pl + w1ttl_100 + ch.girl + ch.health + ch.rural + ch.sibling + ch.boarding + ch.ethn.minority + par.edu.year	+ home.book	+ home.internet, data = d_cl1, method = "nearest")
+m.out <- matchit(migr ~ age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet, data = d_cl, method = "cem")
 summary(m.out, un = FALSE)
@@
 ```{r}
-feols(cog_dif ~ migr + cog3pl + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
+feols(cog_dif ~ migr + cog3pl + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_match, weights = d_match$weights) %>%
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
            fmt = 2)
-feols(ttl_dif ~ migr + w1ttl_dif + age + ch.girl + ch.health + ch.rural + ch.sibling +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
+feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
   msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 

### 2022-06-12 data/Gu-thesis-script.Rmd
more dependent var: raw score, z-score, std score, difference to mean

@@
 d <- d %>% mutate(
+  w1ttl = tr_chn + tr_mat + tr_eng,
+  w2ttl = w2chn + w2mat + w2eng,
   w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
@@
 
+```{r}
+d1 <- d %>% filter(w2ttl_100<=300 & w1ttl_100<=300) #remove outliers with total scores greater than 300
+```
+
+within-class z score
+```{r}
+d1 <- d1 %>% group_by(clsids) %>%
+  mutate(
+    w1ttl_z = as.numeric(scale(tr_chn + tr_mat + tr_eng)),
+    w2ttl_z = as.numeric(scale(w2chn + w2mat + w2eng))
+  ) %>% ungroup()
+```
+
+```{r}
+d1 <- d1 %>% group_by(clsids) %>%
+  mutate(
+    w1ttl_max = max(w1ttl, na.rm = T),
+    w1ttl_min = min(w1ttl, na.rm = T),
+    w2ttl_max = max(w2ttl, na.rm = T),
+    w2ttl_min = min(w2ttl, na.rm = T),
+    w1ttl_100_mean = mean(w1ttl_100, na.rm = T),
+    w2ttl_100_mean = mean(w2ttl_100, na.rm = T)
+  ) %>% ungroup()
+d1 <- d1 %>%
+  mutate(
+    w1ttl_std = (w1ttl - w1ttl_min)/(w1ttl_max - w1ttl_min),
+    w2ttl_std = (w2ttl - w2ttl_min)/(w2ttl_max - w2ttl_min),
+    w1ttl_100_dm = (w1ttl_100 - w1ttl_100_mean),
+    w2ttl_100_dm = (w2ttl_100 - w2ttl_100_mean)
+  )
+```
+
 Detect outliers
-```{r}
+```{}
 d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
+d_outlier1 <- d_outlier %>% select(clsids, schids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
 d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
@@
 
-Sample
 ```{r}
-d_cl <- d1 %>% 
-  filter(w2a0801==1) %>% #parents who are married (and alive)
-  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
-  filter(stmigrant==1) #having stayed in the current county for at least six years (duration of primary school) before baseline
-```
-
-## Variables 
-```{r}
-d_cl <- d_cl %>% 
+d2 <- d1 %>% 
   mutate(chn_dif = w2chn_100 - w1chn_100,
@@
          ttl_dif = w2ttl_100 - w1ttl_100,
+         ttl_z_dif = w2ttl_z - w1ttl_z,
+         ttl_std_dif = w2ttl_std - w1ttl_std,
+         ttl_dm_dif = w2ttl_100_dm - w1ttl_100_dm,
          cog_dif = w2cog3pl - cog3pl) %>%
-  drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
+  drop_na(cog_dif)
 ```
+
+Sample
+```{r}
+d_cl <- d2 %>% 
+  filter(w2a0801==1) %>% #keep parents who are married (and alive)
+  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
+  filter(stmigrant==1) #keep local children 
+```
+
+## Variables
 
@@
          ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         ch.health = a17, #student's self-reported health
-         ch.skip.grd = if_else(c03 == 0, 0, 1),
-         ch.repeat.grd = if_else(c04 == 0, 0, 1),
-         ch.illness = if_else(a10 == 1, 1, 0),
-         ch.preschool = if_else(c01 == 1, 1, 0),
+         ch.health = a17, #student's self-rated health
+         ch.skip.grd = if_else(c03 == 0, 0, 1), #student has skipped grade
+         ch.repeat.grd = if_else(c04 == 0, 0, 1), #student has repeated grade
+         ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
+         ch.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
          par.edu = stprhedu, #Among two parents, the best-educated one's educational level
          par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
-         home.finances = steco_3c,
+         home.finances = steco_5c, #self-rated household financial situation
          home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
@@
 
+raw score
 ```{r}
@@
 
+z score
+```{r}
+did_unres_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | schids, data = d_cl) 
+did_unres_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | schids, data = d_cl) 
+did_unres_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | schids, data = d_cl) 
+did_unres_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | schids, data = d_cl) 
+did_unres_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | schids, data = d_cl) 
+did_unres_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | schids, data = d_cl)
+```
+
+```{r}
+models_unres_ttl_z <- list(
+'Any Parent Absent' = did_unres_ttl_z,
+'Only Mother Absent' = did_unres_ttl_z_m_only,
+'Mother Absent' = did_unres_ttl_z_m,
+'Only Father Absent' = did_unres_ttl_z_f_only,
+'Father Absent' = did_unres_ttl_z_f,
+'Both Parents Absent' = did_unres_ttl_z_both) 
+table_unres_ttl_z <- models_unres_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_z
+```
+
+std
+```{r}
+did_unres_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | schids, data = d_cl) 
+did_unres_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | schids, data = d_cl)
+```
+
+```{r}
+models_unres_ttl_std <- list(
+'Any Parent Absent' = did_unres_ttl_std,
+'Only Mother Absent' = did_unres_ttl_std_m_only,
+'Mother Absent' = did_unres_ttl_std_m,
+'Only Father Absent' = did_unres_ttl_std_f_only,
+'Father Absent' = did_unres_ttl_std_f,
+'Both Parents Absent' = did_unres_ttl_std_both) 
+table_unres_ttl_std <- models_unres_ttl_std %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_std
+```
+
+dif to mean
+```{r}
+did_unres_ttl_dm <- feols(ttl_dm_dif ~ migr + w1ttl_100_dm | schids, data = d_cl) 
+did_unres_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1ttl_100_dm | schids, data = d_cl) 
+did_unres_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1ttl_100_dm | schids, data = d_cl) 
+did_unres_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1ttl_100_dm | schids, data = d_cl) 
+did_unres_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1ttl_100_dm | schids, data = d_cl) 
+did_unres_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1ttl_100_dm | schids, data = d_cl)
+```
+
+```{r}
+models_unres_ttl_dm <- list(
+'Any Parent Absent' = did_unres_ttl_dm,
+'Only Mother Absent' = did_unres_ttl_dm_m_only,
+'Mother Absent' = did_unres_ttl_dm_m,
+'Only Father Absent' = did_unres_ttl_dm_f_only,
+'Father Absent' = did_unres_ttl_dm_f,
+'Both Parents Absent' = did_unres_ttl_dm_both) 
+table_unres_ttl_dm <- models_unres_ttl_dm %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_dm
+```
+
+### DID by subject
 Regressing on Chinese exam score
@@
 
+Regressing on total exam score
+```{r}
+did_adj_unres_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+```
+
+Results
+```{r}
+models_adj_unres_ttl_z <- list(
+'Any Parent Absent' = did_adj_unres_ttl_z,
+'Only Mother Absent' = did_adj_unres_ttl_z_m_only,
+'Mother Absent' = did_adj_unres_ttl_z_m,
+'Only Father Absent' = did_adj_unres_ttl_z_f_only,
+'Father Absent' = did_adj_unres_ttl_z_f,
+'Both Parents Absent' = did_adj_unres_ttl_z_both) 
+table_adj_unres_ttl_z <- models_adj_unres_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_ttl_z
+```
+
+### DID by subject
 Regressing on Chinese exam score

### 2022-06-12 data/Gu-thesis-script.Rmd
Scales package for min-max rescaling

@@
   mutate(
-    w1ttl_max = max(w1ttl, na.rm = T),
-    w1ttl_min = min(w1ttl, na.rm = T),
-    w2ttl_max = max(w2ttl, na.rm = T),
-    w2ttl_min = min(w2ttl, na.rm = T),
+    w1ttl_std1 = rescale(w1ttl),
+    w2ttl_std1 = rescale(w2ttl)
+    ) %>% ungroup()
+```
+
+```{r}
+d1 <- d1 %>% group_by(clsids) %>%
+  mutate(
     w1ttl_100_mean = mean(w1ttl_100, na.rm = T),
@@
 t.test(ttl_dif ~ migr, data = d_cl)
-t.test(chn_dif ~ migr, data = d_cl)
-t.test(mat_dif ~ migr, data = d_cl)
-t.test(eng_dif ~ migr, data = d_cl)
+t.test(ttl_dm_dif ~ migr, data = d_cl)
 ```
@@
 des_ethn.minority
-```
-
-### Wave 2 outcomes of treatment group vs control group
-```{r}
-d_cl %>%
-  group_by(migr) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo_only) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa_only) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_both) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-### Change in outcomes of treatment group vs control group
-```{r}
-d_cl %>%
-  group_by(migr) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo_only) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa_only) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_both) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
 ```

### 2022-06-21 MScThesisText.Rmd
write up main text, set matching criteria, add summary tables

@@
 ---
-title             : "Parental Migration and Left-Behind Children's Cognitive and Academic Performances"
+title             : "Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
 shorttitle        : "Left-Behind Children"
@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
     address       : "De Boelelaan 1105, 1081 HV - Amsterdam, The Netherlands"
@@
 
-floatsintext      : no
+floatsintext      : yes
 linenumbers       : no
@@
 library("papaja")
-library("modelsummary")
+library("kableExtra")
 r_refs("references.bib")
@@
 Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work [@antia2020].
-These are the so-called "left behind children" who are common in migrant-sending regions in the Global South.
-The global size of left behind children population is unavailable, but in-country surveys provide some estimation.
-[@dewaard2018] analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
-[@popova2018] cited a 2016 study by UN Children's Fund Bulgaria indicating that one-fifth of Bulgarian children had one or both parents working abroad.
-In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration [@nbs2017].
+These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
+Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children, [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
 
-Parental migration impacts child-and-adolescence development by exerting different effects that work oppositely [@vanhook2020].
+How are stay-behind children faring when parents have migrated?
+Scholars have obtained mixed results due to the differential effects of parental migration.
 Consider children's education.
-Labor migrants send remittances back home, boosting the family income.
-Higher income can fund children's schooling as well as improve their nutritional and living conditions.
-All these may enhance children's educational outcome.
+According to [@vanhook2020] and [@debrauw2019], labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
-Parental migration halts the day-to-day, face-to-face contact between parents and children.
-It decreases the amount and quality of parental guidance, protection, and support.
-All these may hinder children's school performance.
-It is uncertain how these two opposing effects shape children's educational performance, which merits empirical investigation.
+Parental migration decreases the amount and quality of parental guidance, protection, and support.
+It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
 
@@
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Statistical advances in causal inference provides an alternative approach.
-We can infer causality from a quasi-experimental design -- that is, only if the cause is as good as randomly assigned to individuals in the analysis, conditional on identification assumptions.
+Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
 
-For studying left behind children, a suitable case is China.
-The country has seen a huge scale of internal migration and salient challenges facing migrant parents and left behind children.
-The National Bureau of Statistics reported that the number of in-country migrant workers exceeded 292.5 million by 2021[@nbs2022].
-According to [@gu2021], current policy still limits internal migrants' access to public services and social benefits outside their hometowns, including public school for their children.
-Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
-The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+To what extent do parental migration affect the educational performance of left-behind children in the short term?
+I choose China as the case and analyze data from a nationally representative two-wave panel survey.
+The sample includes children in both urban and rural areas.
+I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness check.
+The outcome was measured with children's cognitive test score and academic exam scores.
+I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
 
-To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
-I analyze the data from a nationally representative two-wave panel survey.
-The sample includes children in both urban and rural areas.
-I develop a difference-in-differences design for causal inference.
-The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
+\newpage
 
@@
 
-Researchers obtained mixed results regarding how migration-induced parental absence affects children's education.
-Using data collected from junior high school students, [@li2017] found that parental migration negatively impacts left-behind children's achievement in standardized mathematical test.
-[@wang2019] also collected data from students of junior high school, but discovered no overall effect of parental migration on the mathematical test grades of children left behind.
-[@bai2018] gathered data from primary school pupils.
-They reported that parental migration "does not appear to have a negative effect" on the standardized English test scores of left-behind children, and "in some cases even appears to have a positive effect" (p.
-1165).
-The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+## Theoretical Framework
 
 Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
-One model, the generation model, holds that parental migration brings forth greater resources in the form of economic capital.
+One is the resource generation model.
+It holds that parental migration brings forth greater resources in the form of economic capital.
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
 Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
-[@chang2019] provided evidence through interviews with migrant workers and their family members.
-They said that the city offered more jobs and higher pay than did the countryside.
+[@yang2008] noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+This subsequently boosted children's school enrollment and educational expenditure.
+In China, [@chang2019] interviewed migrant workers and their family members.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
@@
 Children flourish under parental nurturing care.
-This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black, p.1].
+This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
 Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
-The loss of nurturing care hinders children's accumulation of human capital.
-[@hong2019] talked to a group of left behind children in grade nine.
+The loss of nurturing care slows children's accumulation of human capital.
+Hong talked to a group of left behind children at a rural school [@hong2019].
 These students expressed the utter sense of loneliness "with no advocate, no support and with no one looking out for them" (p.
@@
 
-I hypothesized that in the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
-This is because parental migration immediately disrupts family structure, resulting in lower academic performance of children.
+Researchers obtained mixed results regarding how parental migration affects children's education.
+[@botezat2020] studied the case of Romania and found a positive effect of parents' migration on academic grades of adolesents aged eleven to fifteen.
+[@wang2019] collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, [@debrauw2017] showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+[@nguyen2016] demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+
+Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
 It takes longer time for parental migration to generate resources that improve children's performance at school.
+I propose the first hypothesis:
+
+$H_1$ In the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
 
 Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
-[@xu2019] adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+Xu and others [-@xu2019] adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
 They found that the absence of father only or both parents had "little or no association with negative outcomes" on children's academic and cognitive performances.
@@
 1646).
-[@chen2019] conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+Chen and others [-@chen2019] conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
 They found that mother migration was "negatively associated with children's social competence and academic performance," while father migration had no direct effects on the two outcomes (pp.
@@
 
-I hypothesized that in the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
-This relates to the social norms that designate men as breadwinners and women as caregivers.
+The social norms designate men as breadwinners and women as caregivers.
 Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
 Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+I propose the second hypothesis:
+
+$H_2$ In the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+
+## China's Context
+
+Three features make China a suitable case for studying left behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
+The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+The second feature is the neoliberal welfare regime.
+Neoliberalism extends the logic of the market to most spheres of human life.
+Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
+Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families [@duckett2020].
+The third is the authoritarian control against citizens.
+According to Gu [-@gu2021] and Zhang [-@zhang2018], the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+One can move out of town freely but cannot change hukou freely.
+For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
+Without an urban hukou they cannot send children to public school in the host city.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
 
@@
 First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-As [@nbs2017] stated, the number of urban left behind children had been growing, and the trend would continue.
+[@nbs2017] stated that the number of urban left behind children had been growing and expected that the trend would continue.
 The second shortcoming lies in data and sampling.
 Some studies draw from cross-sectional data, making it hard to infer causal relations [@zhou2014; @jin2020].
-Others suffer from a limited sample size of less than one thousand participants [@liu2021; @yang2022] or a limited geographic coverage of one or a few towns [@yang2022; @shu2021; @jin2020].
+Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
 The third shortcoming lies in the selection and measurement of outcome.
-[@chang2019; @wang2019] measure students' educational performance with the test score of only one academic subject, namely mathematics.
-The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
+[@chang2019; @wang2019] measured students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included to measure comprehensive academic achievement.
+
+\newpage
 
@@
 
-I obtained the data from the China Education Panel Survey (CEPS).
+I obtained the data from the China Education Panel Survey (CEPS) [@nsrc].
 It is a nationally representative, school-based survey featuring junior high school students.
 The survey administrator is the National Survey Research Center at Renmin University of China.
-The research team adopted the approach of multi-stage stratified probability proportional to size sampling.
-The selected participants filled a paper-and-pencil questionnaire.
-The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in seventh and ninth grades.
+The research team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
+The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
 These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
-I only kept the 9,449 observations of seventh grade students and their parents, who completed the follow-up survey in the 2014-2015 academic year.
+The follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed `r printnum(nrow(d))` of the seventh grade cohort.
+I further restricted the sample to students staying with both parents at the original domicile at the baseline survey.
+To deal with missing values, I adopted list-wise deletion for dependent, independent, and control variables.
+The final sample size amounted to `r printnum(nrow(d_cl))` .
 
@@
 
-I explored two categories of adolescence development: academic and cognitive abilities.
-One key dependent variable, the student's cognitive skill, is measured by a fifteen-minute standardized test.
+I explored two categories of educational performance: cognitive and academic abilities.
+One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The raw scores of cognitive skill were then standardized.
-The other set of dependent variables concerned students' academic performance.
-This was measured by the mid-term exam scores in three subjects: Chinese, mathematics, and English.
-I calculated the standardized exam grades at the school-by-grade level to facilitate comparison across schools and counties.
-I removed the observations with missing values in any of the test score mentioned above.
-My choice of standardized exam grades over raw grades follows previous research [@young2018; @xu2019].
+The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
+
+Another dependent variables concerned students' academic performance.
+This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
+These three subjects constitute the core parts in the senior high school entrance exam.
+Junior high school students study these subjects throughout three academic years.
+Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period.
+Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort.
+I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+After the conversion, I checked for abnormal values outside the 0-100 range.
+`r printnum(num.outlier$n)` observations are outliers, accounting for less than one percent of the sample.
+I trim the values of subject exam score with minimum of zero and maximum of one hundred.
+In this way, I can limit the impact of outliers while retaining these observations in the sample.
+After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
 
@@
 In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
-I constructed six treatment dummy variables measuring migration arrangements: both parents absent, only father absent, only mother absent, father absent (unconditional), mother absent (unconditional).
-These arrangements can overlap with each other.
+I constructed four treatment dummy variables measuring migration arrangements: any parents absent, only father absent, only mother absent, and both parents absent.
+These arrangements are mutually exclusive.
 The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
-I then removed the observations that reported other types of parental absence induced by divorce or death.
-
-The control variables at the student level include: student's age, gender, ethnicity, self-rated health, hukou type, and the number of siblings.
-I obtained the age by subtracting the student's birth year from the year 2013, the start of the baseline academic year.
-I coded students' gender as male = 0 and female = 1, ethnic minority status as Han Chinese = 0 and other ethnicity = 1, hukou status as rural (agricultural) hukou = 1 and other types = 0.
-I obtained the number of siblings of students through two items.
-Students who answered yes to the question "Are you the only child of your family" had no sibling.
-Those who answered no to this question were instructed to proceed to the next question, "How many full or half siblings do you have" -- elder brother, younger brother, elder sister, and younger sister, respectively.
-In these four columns, I transformed `NA` to zero.
-Then I added the four columns as the number of siblings of a student.
-
-The control variables at the household level include the internet assess at home, the self-rated number of books at home, and the years of education of the best-educated parent.
-These variables can approximate the level of human capital in a household.
-The internet assess was measured by the item "Do [sic] your family own a computer and have an access to the Internet".
-Those who answered "Yes, we have both" were coded as 1, and others as 0.
-The number of books was measured by the item "How many books do your family own?
-(not including textbooks or magazines)".
-Students chose from a range of 1 as "very few" to 5 as "a great number".
-The years of education of the best-educated parent were measured by two items.
-Students indicated their father's and mother's educational level, respectively.
-I transformed these two variables into years of education and retained the larger value.
+I then removed the observations that reported parental divorce or death.
+These type of parental absence are irrelevant to migration.
 
@@
 
-I adopted `r cite_r("r-references.bib")` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
+I adopted `r cite_r` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \varepsilon_{i,s}$$For student $i$ in school $s$, $\Delta score_{i,s}$ is the change in standardized test score between baseline and follow-up surveys, $migr_{i,s}$ is the treatment dummy variable, $FE_{s}$ is the school-level fixed effect, and $score_{i,s;base}$ is the standardized test score at baseline.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $C_{j}$ and $C_{k}$ are respectively the classroom fixed-effects at baseline and follow-up, and $score_{i,j,k;1}$ is the test score at baseline.
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain consant over time; They would cancel out in the two-way fixed effect model.
-The standard errors were clustered at the school level.
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein].
+The standard errors were clustered at the classroom level.
 
-In addition, I presented an unrestricted and adjusted DID model: $$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$where $X_{i,s}$ is the vector of covariates capturing the characteristics of children and their households.
+In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
+\newpage
+
 # Results
 
+## Descriptive Statistics
+
+The table below summarizes the changes in migration status in the sample.
+All `r printnum(nrow(d_cl))` children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
+In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
+The remaining one-fifth was both-parents migration.
+
 ```{r}
-table_unres_cog
+table_independent_variable
+```
+
+: Parental migration status at follow-up survey.
+
+The table below provides the summary statistics.
+
+```{r}
+table_dependent_variable
+```
+
+: The independent variables
+
+```{r}
+table_control_variable
+```
+
+: The control variables
+
+## Regression Analysis
+
+The unrestricted DID models support my hypothesis one -- newly left behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left behind counterparts.
+If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
+Parental migration is linked to is `r round(coef(did_cog)[1],2)` SD in cognitive test score and `r round(coef(did_cog)[1],2)` points in academic exam grades.
+Both relationships are slight in strength.
+
+The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
+This holds true for academic abilities.
+Children from only mother migrate households are associated with `r round(coef(did_cog_m_only)[1],2)` points relative to that of children whose parents stay along.
+The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left behind children.
+Regarding cognitive abilities, the reverse is true.
+Children with only mother migrated do not show statistically significant difference from the non left behind children.
+Children with only father absent are associated with (`r round(coef(did_cog_f_only)[1],2)` SD), and both parents absent (`r round(coef(did_cog_both)[1],2)` SD) compared to the non left behind children.
+
+```{r}
+table_cog
 ```
@@
 ```{r}
-table_unres_chn
+table_ttl
+```
+
+The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
+That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
+
+Some predictors are strong in both models of cognitive and academic abilities.
+These are children's age and educational asiration as well as parents' expectation on children.
+In terms of age, the older students' scores drop relatively more than younger students'.
+One year older in age is associated with `r round(coef(did_adj_cog)[3],2)` SD for standardized cognitive test and `r round(coef(did_adj_ttl)[3],2)` points for academic exams.
+Parent's expectation for children comleting university and children's own aspiration for finishing university are associated with higher scores.
+The effect sizes are `r round(coef(did_adj_cog)[15],2)` SD and `r round(coef(did_adj_cog)[12],2)` SD for standardized cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
+
+Several predictors are strong in the model of academic grades but not in that of cognitive scores.
+These are children's gender and self-reported health, and the years of parental education.
+Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive test.
+Students who consider themselves healthier are associated with higher scores in academic exams.
+Parents with more education are associated with their children's higher scores in academic exams.
+If the years of parental education of the best-educated among the two increase by one, it would be linked to a `r round(coef(did_adj_ttl)[14],2)` points increase in the child's academic exam grade.
+These three predictors are not significant for cognitive outcomes.
+
+Preschool attendance is associated with higher cognitive outcomes `r round(coef(did_adj_cog)[8],2)` SD, but its effect for academic outcomes is not significant.
+
+```{r}
+table_adj_cog
 ```
@@
 ```{r}
-table_unres_mat
+table_adj_ttl
+```
+
+## Matching
+
+Researchers noted that migrants represent a positively selected group compared to non-migrants [@vanhook2020].
+One technique to tackle the selectivity issue is matching.
+This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+Popular choices include coarsened exact matching (CEM) [@waldman2022], nearest-neighbor propensity score matching (PSM) [@xu2015], and nearest-neighbor Mahalanobis distance matching (MDM) [@guo2021].
+CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+The downside is that it leaves many units without an exact match and discards these unmatched units.
+The nearest-neighbor matching examines all the treated units and selects the closest eligible control unit to be paired.
+The eligibility as the "closest" can be determined with the differences in Mahalanobis distance or in propensity score.
+Propensity score denotes the probability of receiving treatment based on the specified covariates.
+Nearest-neighbor PSM does not try to optimize any condition as each pairing ignores how other units will be or have been paired.
+This matching method may result in more "imbalance, model dependence, and bias" on highly balanced data [@king2019].
+
+I conducted matching with all the covariates used in the adjusted DID model.
+I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
+Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others [-@bai2018].
+Exact matching based on county of residence preserves the original geographic distribution.
+The propensity score was estimated using a logistic regression of the treatment on the covariates.
+The matching ratio was set at one treatment unit with up to three control units.
+
+Alike are the results with matching and those without.
+In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
+In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
+The magnitudes of the coefficients are also similar.
+
+```{r}
+table_m_cog
 ```
@@
 ```{r}
-table_unres_eng
+table_m_ttl
 ```
@@
 ```{r}
-table_adj_unres_cog
+table_m_adj_cog
 ```
@@
 ```{r}
-table_adj_unres_chn
+table_m_adj_ttl
 ```
 
-```{r}
-table_adj_unres_mat
-```
-
-```{r}
-table_adj_unres_eng
-```
+\newpage
 
 # Discussion
+
+This thesis proposed a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
+I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
+I further examined whether the effect varies across different arrangements of parental migration.
+Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
+In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
+
+My research has several limitations in sample selection.
+The CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
+Given such constraint, I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+It is possible that some parents are jailed or hospitalized.
+These types of absence would be wrongly attributed to migration.
+The CEPS also lacks information on parents' migration history.
+Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as newly left behind.
 

### 2022-06-21 MScThesisText.tex
write up main text, set matching criteria, add summary tables

--- 2022-06-02 MScThesisText.tex
@@
 \documentclass[
-  man]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{csquotes}
@@
 
-\shorttitle{Left-Behind Adolescent}
-
-\authornote{
-
-Correspondence concerning this article should be addressed to Jiancheng Gu, Postal address. E-mail: \href{mailto:j4.gu@student.vu.nl}{\nolinkurl{j4.gu@student.vu.nl}}
-
-}
+\shorttitle{Left-Behind Children}
 
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
-These are the so-called ``left behind children'' who are common in migrant-sending regions in the Global South.
-Their exact numbers in total are unavailable, but surveys provide some estimation.
-(DeWaard et al., 2018) analyzed the Mexican and Latin American Migration Projects and estimated that around 15 percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
-(Chae \& Glick, 2019) studied the World Bank's Migration and Remittances Surveys and indicated that about one-third of the children live in migrant-sending households in Kenya, Senegal, and Burkina Faso around 2010.
-In China, the 2015 one-percent National Population Sample Survey showed that 25 percent of children lived under parental absence induced by migration (NBS et al., 2017).
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020).
+These are the so-called ``left behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
+Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children, (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
 
-Parental migration shapes child development -- such as human capital accumulation -- by exerting different effects that work oppositely.
-Labor migrants send remittances back home, boosting the family income.
-Higher income can fund children's schooling as well as improve their nutritional and living conditions.
-All these may enhance children's educational outcome.
+How are children faring when parents have migrated?
+Scholars have obtained mixed results due to the differential effects of parental migration.
+Consider children's education.
+(Van Hook \& Glick, 2020) labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
-Parental migration halts the day-to-day, face-to-face contact between parents and children.
-It decreases the amount and quality of parental guidance, protection, and support.
-All these may hinder children's school performance.
-It is uncertain how these two opposing effects affect children's educational performance, which merits empirical investigation.
+Parental migration decreases the amount and quality of parental guidance, protection, and support.
+It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
 
-For studying left behind children, a suitable case is China.
-The country has seen a huge scale of internal migration and salient challenges facing migrant parents and left behind children.
-More than 285 million Chinese people were in-country migrant workers.
-According to (Gu, 2021), current policy still limits internal migrants' access to public services and social benefits outside their hometowns, including public school for their children.
-Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
-The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+A challenge arises in when we want to assess the causality between parental migration and children's education.
+Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
 
-The research on China's left behind children has three major shortcomings.
-First, most literature focuses on children left behind in rural areas while negleting the urban counterparts.
-As (NBS et al., 2017) stated, the number of urban left behind children had been growing, and the trend would continue expectedly.
-Meanwhile, in-situ urbanization has turned a small proportion of children left behind in the countryside as urban residents.
-The second shortcoming lies in data and sampling.
-Some studies draw from cross-sectional surveys, making it hard to infer causal relations (Wen et al., 2020; Zhou et al., 2014).
-Others suffer from a limited sample size of less than one thousand participants (Liu et al., 2021; Yang et al., 2022) or a limited geographic coverage of one or a few towns (Shu, 2021; Yang et al., 2022).
-The third shortcoming lies in the selection and measurement of outcome.
-Wang et al.
-(2019) measure students' educational performance with the test score of only one academic subject, such as English or mathematics.
-The test results of multiple subjects should be included, as parental migration's impact may vary across subject areas.
-
-This thesis aims to address the shortcomings in the study of parental migration's effect on left behind children's educational performance.
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
 I analyze the data from a nationally representative two-wave panel survey.
@@
 I develop a difference-in-differences design for causal inference.
-The dependent variables include children's cognitive test scores and their Chinese, mathematics, and English exam scores.
+The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
+
+\newpage
 
@@
 
+\hypertarget{theoretical-framework}{%
+\subsection{Theoretical Framework}\label{theoretical-framework}}
+
+Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
+One model, the resource generation model, holds that parental migration brings forth greater resources in the form of economic capital.
+Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
+16).
+Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
+(D.
+Yang, 2008) noted that a depreciation of Filipino peso increased the amount of foreign remittances, which subsequently boosted children's school enrollment and educational expenditure.
+In China, (Chang et al., 2019) interviewed migrant workers and their family members.
+Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+
+The other theoretical model is the family disruption model.
+Children flourish under parental nurturing care.
+This term refers to the ``stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships'' (Black et al., 2021, p.
+1).
+Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
+The loss of nurturing care slows children's accumulation of human capital.
+Hong talked to a group of left behind children at a rural school (Hong \& Fuller, 2019).
+These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
+Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.~14).
+
+Researchers obtained mixed results regarding how parental migration affects children's education.
+(Botezat \& Pfeiffer, 2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolesents aged eleven to fifteen.
+(Wang et al., 2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, (Brauw \& Giles, 2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+(Nguyen, 2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+
+Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
+It takes longer time for parental migration to generate resources that improve children's performance at school.
+I propose the first hypothesis:
+
+\(H_1\) In the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+
+Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+Xu and others (2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+They found that the absence of father only or both parents had ``little or no association with negative outcomes'' on children's academic and cognitive performances.
+Only-mother absence, however, showed a ``strong association with negative outcomes'' (p.~1646).
+Chen and others (2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+They found that mother migration was ``negatively associated with children's social competence and academic performance,'' while father migration had no direct effects on the two outcomes (pp.~860-861).
+
+The social norms designate men as breadwinners and women as caregivers.
+Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
+Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+I propose the second hypothesis:
+
+\(H_2\) In the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+
+\hypertarget{chinas-context}{%
+\subsection{China's Context}\label{chinas-context}}
+
+Three features make China a suitable case for studying left behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
+The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+The second feature is the neoliberal welfare regime.
+Neoliberalism extends the logic of the market to most spheres of human life.
+Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
+Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Zhan, 2020).
+The third feature is the authoritarian control against citizens.
+According to Gu (2021), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+One can move to another place freely but cannot change hukou freely.
+For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
+Without an urban hukou they cannot send children to public school in the host city.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+(NBS et al., 2017) stated that the number of urban left behind children had been growing and expected that the trend would continue.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014).
+Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Liu et al., 2021; Shu, 2021; F.
+Yang et al., 2022).
+The third shortcoming lies in the selection and measurement of outcome.
+(Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included to measure comprehensive academic achievement.
+
+\newpage
+
 \hypertarget{methods}{%
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+I obtained the data from the China Education Panel Survey (CEPS) (NSRC, n.d.).
+It is a nationally representative, school-based survey featuring junior high school students.
+The survey administrator is the National Survey Research Center at Renmin University of China.
+The research team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
+The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
+These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
+The follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed 9449 of the seventh grade cohort.
+I further restricted the sample to students staying with both parents at the original domicile at the baseline survey.
+To deal with missing values, I adopted list-wise deletion for dependent, independent, and control variables.
+The final sample size amounted to 4088 .
+
+\hypertarget{measurement}{%
+\subsection{Measurement}\label{measurement}}
+
+I explored two categories of adolescence development: cognitive and academic abilities.
+One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
+The test covered three types of reasoning: verbal, visuospatial, and numerical.
+The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
+
+Another dependent variables concerned students' academic performance.
+This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
+These three subjects constitute the core parts in the senior high school entrance exam.
+Within one particular school, teachers of the same subject use the same syllabus, administering the same exams during a given assessment period.
+Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort.
+I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+Accordingly, the total score of three subjects has a 300-point scale.
+
+The key independent variable, the parental migration status, was identified by two items in the parent survey.
+In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
+I constructed four treatment dummy variables measuring migration arrangements: any parents absent, only father absent, only mother absent, and both parents absent.
+These arrangements are mutually exclusive.
+The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
+I then removed the observations that reported parental divorce or death.
+These type of parental absence are irrelevant to migration.
 
@@
 
-We used R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
+I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
+The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j}\] For student \(i\) taking the test of type \(j\), \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{1}\) and \(C_{2}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j;1}\) is the test score at baseline.
+The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The model is unadjusted as it does not adjust for additional covariates.
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, n.d.).
+The standard errors were clustered at the classroom level.
+
+In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \zeta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+The control variables were measured in the baseline survey.
+This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
+
+\newpage
 
@@
 
+\hypertarget{descriptive-statistics}{%
+\subsection{Descriptive Statistics}\label{descriptive-statistics}}
+
+The table below summarizes the changes in migration status in the sample.
+All 4088 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
+In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
+The remaining one-fifth was both-parents migration.
+
+\begin{longtable}[]{@{}llrr@{}}
+\caption{Parental migration status at follow-up survey.}\tabularnewline
+\toprule
+& & N & \% \\
+\midrule
+\endfirsthead
+\toprule
+& & N & \% \\
+\midrule
+\endhead
+Parental Migration & No & 3452 & 84.4 \\
+& Yes & 636 & 15.6 \\
+Parental Migration Type & Both Parents At Home & 3452 & 84.4 \\
+& Both Parents Migrated & 131 & 3.2 \\
+& Only Father Migrated & 251 & 6.1 \\
+& Only Mother Migrated & 254 & 6.2 \\
+\bottomrule
+\end{longtable}
+
+The table below provides the summary statistics.
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{The independent variables}\tabularnewline
+\toprule
+& Mean & SD & Min & Max \\
+\midrule
+\endfirsthead
+\toprule
+& Mean & SD & Min & Max \\
+\midrule
+\endhead
+migr & 0.16 & 0.36 & 0.00 & 1.00 \\
+Cognitive score difference & 0.27 & 0.80 & -2.88 & 4.03 \\
+Cognitive score at wave 1 & 0.15 & 0.85 & -2.03 & 2.33 \\
+Cognitive score at wave 2 & 0.42 & 0.78 & -3.14 & 2.06 \\
+Academic exam score difference & -8.82 & 33.21 & -207.50 & 166.00 \\
+Academic exam score at wave 1 & 213.11 & 49.46 & 19.33 & 297.50 \\
+Academic exam score at wave 2 & 204.29 & 55.41 & 0.00 & 293.33 \\
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}llrr@{}}
+\caption{The control variables}\tabularnewline
+\toprule
+& & N & \% \\
+\midrule
+\endfirsthead
+\toprule
+& & N & \% \\
+\midrule
+\endhead
+migr & 0 & 3452 & 84.4 \\
+& 1 & 636 & 15.6 \\
+child.is.girl & 0 & 2002 & 49.0 \\
+& 1 & 2086 & 51.0 \\
+child.has.rural.hukou & 0 & 2221 & 54.3 \\
+& 1 & 1867 & 45.7 \\
+child.in.boarding.school & 0 & 2906 & 71.1 \\
+& 1 & 1182 & 28.9 \\
+child.is.ethnic.minority & 0 & 3800 & 93.0 \\
+& 1 & 288 & 7.0 \\
+child.had.skipped.grade & 0 & 4042 & 98.9 \\
+& 1 & 46 & 1.1 \\
+child.had.repeated.grade & 0 & 3700 & 90.5 \\
+& 1 & 388 & 9.5 \\
+child.went.to.preschool & 0 & 639 & 15.6 \\
+& 1 & 3449 & 84.4 \\
+parent.has.white.collar.job & 0 & 3238 & 79.2 \\
+& 1 & 850 & 20.8 \\
+home.has.internet & 0 & 1316 & 32.2 \\
+& 1 & 2772 & 67.8 \\
+child.health.self.rated & Very poor & 21 & 0.5 \\
+& Not very good & 113 & 2.8 \\
+& Moderate & 807 & 19.7 \\
+& Good & 1383 & 33.8 \\
+& Very good & 1764 & 43.2 \\
+child.educational.aspiration & Junior high school & 140 & 3.4 \\
+& Senior high school & 418 & 10.2 \\
+& Associate college & 616 & 15.1 \\
+& University & 1205 & 29.5 \\
+& Postgraduate & 1709 & 41.8 \\
+parent.educational.level & Primary school and below & 248 & 6.1 \\
+& Junior high school & 1580 & 38.6 \\
+& Senior high school & 1254 & 30.7 \\
+& Associate college & 385 & 9.4 \\
+& University & 543 & 13.3 \\
+& Postgraduate & 78 & 1.9 \\
+parent.expectation.on.child & Junior high school & 36 & 0.9 \\
+& Senior high school & 257 & 6.3 \\
+& Associate college & 426 & 10.4 \\
+& University & 1574 & 38.5 \\
+& Postgraduate & 1795 & 43.9 \\
+home.extracurricular.book & Very few & 395 & 9.7 \\
+& Not many & 414 & 10.1 \\
+& Some & 1312 & 32.1 \\
+& Quite a few & 1111 & 27.2 \\
+& A great number & 856 & 20.9 \\
+home.economic.resource & Very poor & 115 & 2.8 \\
+& Somewhat poor & 598 & 14.6 \\
+& Moderate & 3124 & 76.4 \\
+& Somewhat rich & 239 & 5.8 \\
+& Very rich & 12 & 0.3 \\
+\bottomrule
+\end{longtable}
+
+\hypertarget{regression-analysis}{%
+\subsection{Regression Analysis}\label{regression-analysis}}
+
+The unrestricted DID models support my hypothesis one -- newly left behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left behind counterparts.
+If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
+Parental migration is linked to is -0.09 SD in cognitive test score and -0.09 points in academic exam grades.
+Both relationships are slight in strength.
+
+The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
+This holds true for academic abilities.
+Children from only mother migrate households are associated with -0.04 points relative to that of children whose parents stay along.
+The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left behind children.
+Regarding cognitive abilities, the reverse is true.
+Children with only mother migrated do not show statistically significant difference from the non left behind children.
+Children with only father absent are associated with (-0.14 SD), and both parents absent (-0.10 SD) compared to the non left behind children.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.09** & -0.04 & -0.14** & -0.10 \\
+& (0.03) & (0.05) & (0.04) & (0.06) \\
+W1 score & -0.62*** & -0.63*** & -0.62*** & -0.62*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
+R2 & 0.494 & 0.502 & 0.505 & 0.499 \\
+R2 Adj. & 0.424 & 0.426 & 0.430 & 0.419 \\
+R2 Within & 0.370 & 0.378 & 0.378 & 0.374 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -2.67* & -5.85* & -0.25 & -1.13 \\
+& (1.26) & (2.36) & (1.66) & (2.28) \\
+W1 score & 0.04 & 0.04† & 0.04† & 0.04 \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
+R2 & 0.562 & 0.577 & 0.566 & 0.577 \\
+R2 Adj. & 0.501 & 0.513 & 0.500 & 0.510 \\
+R2 Within & 0.005 & 0.009 & 0.004 & 0.004 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
+That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
+
+Some predictors are strong in both models of cognitive and academic abilities.
+These are children's age and educational asiration as well as parents' expectation on children.
+In terms of age, the older students' scores drop relatively more than younger students'.
+One year older in age is associated with -0.07 SD for standardized cognitive test and -1.23 points for academic exams.
+Parent's expectation for children comleting university and children's own aspiration for finishing university are associated with higher scores.
+The effect sizes are 0.01 SD and 0.07 SD for standardized cognitive test, respectively; and 0.29 points and 1.82 points for academic exams, respectively.
+
+Several predictors are strong in the model of academic grades but not in that of cognitive scores.
+These are children's gender and self-reported health, and the years of parental education.
+Girls outperform boys by 4.49 points in academic exams, but do not show advantage in cognitive test.
+Students who consider themselves healthier are associated with higher scores in academic exams.
+Parents with more education are associated with their children's higher scores in academic exams.
+If the years of parental education of the best-educated among the two increase by one, it would be linked to a 0.88 points increase in the child's academic exam grade.
+These three predictors are not significant for cognitive outcomes.
+
+Preschool attendance is associated with higher cognitive outcomes 0.07 SD, but its effect for academic outcomes is not significant.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.09** & -0.04 & -0.14*** & -0.08 \\
+& (0.03) & (0.05) & (0.04) & (0.06) \\
+W1 score & -0.67*** & -0.67*** & -0.67*** & -0.67*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+child.age & -0.07*** & -0.06** & -0.07*** & -0.08*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+child.is.girl & -0.01 & 0.00 & 0.00 & -0.01 \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+child.health.self.rated & -0.02 & -0.02 & -0.02 & -0.02 \\
+& (0.01) & (0.01) & (0.01) & (0.01) \\
+child.has.rural.hukou & -0.01 & 0.00 & -0.01 & 0.00 \\
+& (0.02) & (0.03) & (0.03) & (0.03) \\
+child.number.of.sibling & -0.03 & -0.02 & -0.02 & -0.02 \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+child.went.to.preschool & 0.07* & 0.06† & 0.05† & 0.07* \\
+& (0.03) & (0.03) & (0.03) & (0.03) \\
+child.had.skipped.grade & -0.17 & -0.11 & -0.20 & -0.10 \\
+& (0.12) & (0.12) & (0.12) & (0.12) \\
+child.had.repeated.grade & -0.08* & -0.11** & -0.07† & -0.06 \\
+& (0.04) & (0.04) & (0.04) & (0.04) \\
+child.in.boarding.school & 0.04 & 0.02 & 0.02 & 0.01 \\
+& (0.04) & (0.04) & (0.04) & (0.04) \\
+child.educational.aspiration & 0.07*** & 0.07*** & 0.07*** & 0.08*** \\
+& (0.01) & (0.01) & (0.01) & (0.01) \\
+child.is.ethnic.minority & 0.04 & 0.04 & 0.02 & 0.02 \\
+& (0.06) & (0.06) & (0.06) & (0.06) \\
+parent.expectation.on.child & 0.08*** & 0.09*** & 0.09*** & 0.09*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+parent.has.white.collar.job & 0.01 & -0.01 & 0.01 & 0.00 \\
+& (0.03) & (0.03) & (0.03) & (0.03) \\
+parent.educational.level & 0.01 & 0.01 & 0.01 & 0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) \\
+home.economic.resource & -0.02 & -0.01 & 0.00 & 0.00 \\
+& (0.02) & (0.02) & (0.02) & (0.02) \\
+home.extracurricular.book & 0.01 & 0.00 & 0.01 & 0.00 \\
+& (0.01) & (0.01) & (0.01) & (0.01) \\
+home.has.internet & -0.01 & -0.01 & -0.02 & -0.02 \\
+& (0.03) & (0.03) & (0.03) & (0.03) \\
+Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
+R2 & 0.525 & 0.533 & 0.537 & 0.530 \\
+R2 Adj. & 0.458 & 0.459 & 0.464 & 0.452 \\
+R2 Within & 0.409 & 0.416 & 0.418 & 0.413 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -2.65* & -5.87** & -0.20 & -0.92 \\
+& (1.25) & (2.24) & (1.68) & (2.35) \\
+W1 score & -0.01 & -0.01 & 0.00 & -0.01 \\
+& (0.02) & (0.03) & (0.02) & (0.02) \\
+child.age & -1.23† & -1.04 & -1.21† & -0.96 \\
+& (0.65) & (0.68) & (0.70) & (0.70) \\
+child.is.girl & 4.49*** & 4.78*** & 4.54*** & 4.43*** \\
+& (0.92) & (0.95) & (0.92) & (0.97) \\
+child.health.self.rated & 1.05* & 1.12* & 0.92* & 0.85† \\
+& (0.43) & (0.45) & (0.47) & (0.47) \\
+child.has.rural.hukou & 1.08 & 1.50 & 0.80 & 0.98 \\
+& (1.02) & (1.06) & (1.05) & (1.07) \\
+child.number.of.sibling & 1.03† & 0.87 & 1.21* & 0.66 \\
+& (0.58) & (0.59) & (0.60) & (0.62) \\
+child.went.to.preschool & 1.65 & 2.22† & 0.85 & 1.97 \\
+& (1.20) & (1.24) & (1.28) & (1.27) \\
+child.had.skipped.grade & -0.73 & 0.23 & -0.98 & 1.01 \\
+& (4.82) & (4.82) & (5.41) & (5.07) \\
+child.had.repeated.grade & -1.81 & -1.22 & -1.55 & -0.20 \\
+& (1.85) & (1.98) & (1.89) & (1.81) \\
+child.in.boarding.school & -1.14 & -0.19 & -0.72 & -1.19 \\
+& (1.65) & (1.65) & (1.66) & (1.81) \\
+child.educational.aspiration & 1.82*** & 2.08*** & 1.90*** & 1.91*** \\
+& (0.52) & (0.55) & (0.51) & (0.53) \\
+child.is.ethnic.minority & 0.48 & -0.24 & -0.33 & -1.14 \\
+& (2.15) & (2.29) & (2.38) & (2.56) \\
+parent.expectation.on.child & 0.88† & 0.85 & 0.86 & 0.96† \\
+& (0.53) & (0.55) & (0.54) & (0.55) \\
+parent.has.white.collar.job & 0.29 & 0.03 & 0.59 & 0.42 \\
+& (1.19) & (1.23) & (1.21) & (1.25) \\
+parent.educational.level & 1.02† & 1.14* & 1.14* & 1.15* \\
+& (0.53) & (0.53) & (0.54) & (0.56) \\
+home.economic.resource & -0.74 & -0.18 & -0.66 & -0.24 \\
+& (0.81) & (0.88) & (0.87) & (0.87) \\
+home.extracurricular.book & -0.78† & -1.18* & -0.86† & -0.85† \\
+& (0.45) & (0.46) & (0.45) & (0.46) \\
+home.has.internet & -1.41 & -1.65 & -1.33 & -1.37 \\
+& (1.13) & (1.14) & (1.18) & (1.17) \\
+Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
+R2 & 0.573 & 0.590 & 0.578 & 0.588 \\
+R2 Adj. & 0.512 & 0.525 & 0.512 & 0.520 \\
+R2 Within & 0.032 & 0.039 & 0.032 & 0.030 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\hypertarget{matching}{%
+\subsection{Matching}\label{matching}}
+
+Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020).
+One technique to tackle the selectivity issue is matching.
+This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+Popular choices include coarsened exact matching (CEM) (Waldman, 2022), nearest-neighbor propensity score matching (PSM) (H.
+Xu \& Xie, 2015), and nearest-neighbor Mahalanobis distance matching (MDM) (Guo et al., 2021).
+CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+The downside is that it leaves many units without an exact match and discards these unmatched units.
+The nearest-neighbor matching examines all the treated units and selects the closest eligible control unit to be paired.
+The eligibility as the ``closest'' can be determined with the differences in Mahalanobis distance or in propensity score.
+Propensity score denotes the probability of receiving treatment based on the specified covariates.
+Nearest-neighbor PSM does not try to optimize any condition as each pairing ignores how other units will be or have been paired.
+This matching method may result in more ``imbalance, model dependence, and bias'' on highly balanced data (King \& Nielsen, 2019).
+
+I conducted matching with all the covariates used in the adjusted DID model.
+I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
+Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others (2018).
+Exact matching based on county of residence preserves the original geographic distribution.
+The propensity score was estimated using a logistic regression of the treatment on the covariates.
+The matching ratio was set at one treatment unit with up to three control units.
+
+Alike are the results with matching and those without.
+In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
+In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant in the any parent migrated households and only mother migrated households.
+The magnitudes of the coefficients are also similar.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.09** & -0.05 & -0.13* & -0.05 \\
+& (0.03) & (0.06) & (0.06) & (0.11) \\
+W1 score & -0.61*** & -0.65*** & -0.60*** & -0.63*** \\
+& (0.03) & (0.04) & (0.04) & (0.06) \\
+Num.Obs. & 1958 & 913 & 897 & 475 \\
+R2 & 0.528 & 0.627 & 0.638 & 0.646 \\
+R2 Adj. & 0.375 & 0.313 & 0.320 & -0.312 \\
+R2 Within & 0.363 & 0.407 & 0.372 & 0.351 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -2.65† & -5.34* & -2.42 & -2.45 \\
+& (1.47) & (2.67) & (2.56) & (3.96) \\
+W1 score & 0.03 & 0.08† & 0.05 & 0.03 \\
+& (0.03) & (0.04) & (0.04) & (0.06) \\
+Num.Obs. & 1958 & 913 & 897 & 475 \\
+R2 & 0.590 & 0.682 & 0.637 & 0.706 \\
+R2 Adj. & 0.457 & 0.413 & 0.319 & -0.087 \\
+R2 Within & 0.006 & 0.026 & 0.008 & 0.005 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.09** & -0.04 & -0.15* & -0.08 \\
+& (0.03) & (0.06) & (0.06) & (0.11) \\
+W1 score & -0.67*** & -0.67*** & -0.67*** & -0.69*** \\
+& (0.03) & (0.04) & (0.04) & (0.06) \\
+child.age & -0.08* & -0.02 & -0.03 & -0.15 \\
+& (0.03) & (0.05) & (0.04) & (0.10) \\
+child.is.girl & 0.02 & 0.01 & 0.05 & -0.06 \\
+& (0.03) & (0.05) & (0.06) & (0.10) \\
+child.health.self.rated & 0.00 & -0.03 & -0.02 & -0.07 \\
+& (0.02) & (0.03) & (0.03) & (0.06) \\
+child.has.rural.hukou & 0.01 & -0.07 & 0.06 & 0.04 \\
+& (0.04) & (0.07) & (0.07) & (0.12) \\
+child.number.of.sibling & -0.07* & -0.09* & -0.05 & -0.10 \\
+& (0.03) & (0.04) & (0.04) & (0.07) \\
+child.went.to.preschool & 0.04 & 0.08 & 0.03 & 0.30* \\
+& (0.04) & (0.08) & (0.06) & (0.12) \\
+child.had.skipped.grade & -0.08 & -0.13 & -0.37† & 0.34 \\
+& (0.16) & (0.24) & (0.19) & (0.45) \\
+child.had.repeated.grade & -0.08 & -0.26* & -0.02 & 0.05 \\
+& (0.06) & (0.11) & (0.11) & (0.16) \\
+child.in.boarding.school & 0.09 & 0.15 & -0.10 & -0.02 \\
+& (0.07) & (0.12) & (0.11) & (0.20) \\
+child.educational.aspiration & 0.07*** & 0.03 & 0.10** & 0.10† \\
+& (0.02) & (0.03) & (0.03) & (0.05) \\
+child.is.ethnic.minority & -0.01 & 0.01 & -0.20 & 0.39 \\
+& (0.09) & (0.10) & (0.23) & (0.44) \\
+parent.expectation.on.child & 0.07** & 0.08† & 0.06† & 0.01 \\
+& (0.03) & (0.05) & (0.03) & (0.06) \\
+parent.has.white.collar.job & 0.02 & -0.10† & 0.03 & -0.15 \\
+& (0.05) & (0.05) & (0.08) & (0.16) \\
+parent.educational.level & 0.01 & 0.03 & 0.00 & -0.08 \\
+& (0.02) & (0.03) & (0.03) & (0.06) \\
+home.economic.resource & -0.05 & 0.00 & 0.02 & 0.05 \\
+& (0.03) & (0.05) & (0.05) & (0.08) \\
+home.extracurricular.book & 0.01 & 0.01 & 0.02 & 0.01 \\
+& (0.02) & (0.03) & (0.03) & (0.05) \\
+home.has.internet & -0.05 & -0.07 & -0.06 & 0.05 \\
+& (0.04) & (0.08) & (0.07) & (0.11) \\
+Num.Obs. & 1958 & 913 & 897 & 475 \\
+R2 & 0.562 & 0.653 & 0.672 & 0.691 \\
+R2 Adj. & 0.413 & 0.337 & 0.361 & -0.318 \\
+R2 Within & 0.409 & 0.447 & 0.431 & 0.435 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -2.91† & -5.90* & -2.68 & -2.94 \\
+& (1.48) & (2.64) & (2.56) & (4.21) \\
+W1 score & -0.01 & 0.01 & 0.00 & -0.03 \\
+& (0.03) & (0.04) & (0.05) & (0.06) \\
+child.age & -0.61 & 1.45 & 2.59 & -2.15 \\
+& (1.21) & (2.00) & (1.99) & (3.48) \\
+child.is.girl & 4.51** & 4.40† & 6.58** & 3.76 \\
+& (1.43) & (2.57) & (2.41) & (4.21) \\
+child.health.self.rated & 0.71 & 2.30 & 1.13 & 2.38 \\
+& (0.69) & (1.42) & (1.15) & (2.27) \\
+child.has.rural.hukou & 0.85 & -0.13 & -1.10 & -2.75 \\
+& (1.70) & (3.10) & (2.97) & (4.45) \\
+child.number.of.sibling & 1.20 & 1.92† & 1.00 & -2.50 \\
+& (1.06) & (1.06) & (1.61) & (2.69) \\
+child.went.to.preschool & 1.75 & -0.30 & -2.26 & 6.39 \\
+& (1.76) & (2.47) & (2.57) & (5.13) \\
+child.had.skipped.grade & 2.29 & -9.76 & 3.12 & 32.64 \\
+& (6.62) & (11.90) & (12.03) & (29.40) \\
+child.had.repeated.grade & -6.07† & -13.55† & -13.33** & -0.09 \\
+& (3.18) & (7.61) & (4.86) & (5.92) \\
+child.in.boarding.school & -0.64 & -0.65 & -3.42 & -3.10 \\
+& (3.53) & (5.38) & (4.25) & (8.17) \\
+child.educational.aspiration & 1.48† & 1.63 & 0.37 & 0.44 \\
+& (0.86) & (1.06) & (1.20) & (1.92) \\
+child.is.ethnic.minority & 3.81 & 4.84 & 2.79 & -2.54 \\
+& (4.31) & (4.68) & (6.53) & (7.64) \\
+parent.expectation.on.child & 0.19 & 1.71 & 1.41 & 3.97 \\
+& (0.83) & (1.49) & (1.35) & (2.49) \\
+parent.has.white.collar.job & -0.85 & 0.54 & 2.13 & -1.42 \\
+& (1.82) & (2.56) & (2.87) & (6.14) \\
+parent.educational.level & 1.30 & 2.30** & 1.91 & -2.63 \\
+& (0.97) & (0.85) & (1.41) & (2.54) \\
+home.economic.resource & -0.23 & -1.90 & -0.51 & -0.54 \\
+& (1.23) & (2.24) & (1.81) & (4.05) \\
+home.extracurricular.book & -0.66 & -0.66 & -1.59 & 0.08 \\
+& (0.71) & (1.24) & (1.01) & (1.93) \\
+home.has.internet & -2.89 & -1.61 & 0.08 & 3.67 \\
+& (1.81) & (2.87) & (3.26) & (4.98) \\
+Num.Obs. & 1958 & 913 & 897 & 475 \\
+R2 & 0.603 & 0.702 & 0.660 & 0.731 \\
+R2 Adj. & 0.468 & 0.431 & 0.337 & -0.150 \\
+R2 Within & 0.037 & 0.088 & 0.070 & 0.087 \\
+FE: clsids & X & X & X & X \\
+FE: w2clsids & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+\newpage
+
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
+
+Results show that parental migration is negatively associated with children's short-term cognitive and academic abilities.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chae2019}{}}%
-Chae, S., \& Glick, J.
-E.
-(2019).
-Educational Selectivity of Migrants and Current School Enrollment of Children Left behind: Analyses in Three African Countries.
-\emph{International Migration Review}, \emph{53}(3), 736--769.
-\url{https://doi.org/10.1177/0197918318772261}
+\leavevmode\vadjust pre{\hypertarget{ref-berguxe92018}{}}%
+Bergé, L. (2018). \emph{Efficient estimation of maximum likelihood models with multiple fixed-effects: the R package FENmlm}. \url{https://ideas.repec.org/p/luc/wpaper/18-13.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-black2021}{}}%
+Black, M.
+M., Behrman, J.
+R., Daelmans, B., Prado, E.
+L., Richter, L., Tomlinson, M., Trude, A.
+C.
+B., Wertlieb, D., Wuermli, A.
+J., \& Yoshikawa, H.
+(2021).
+The principles of Nurturing Care promote human capital and mitigate adversities from preconception through adolescence.
+\emph{BMJ Global Health}, \emph{6}(4), e004436.
+\url{https://doi.org/10.1136/bmjgh-2020-004436}
+
+\leavevmode\vadjust pre{\hypertarget{ref-botev2019}{}}%
+Botev, J., Égert, B., Smidova, Z., \& Turner, D. (2019). \emph{A new macroeconomic measure of human capital with strong empirical links to productivity}. \url{https://doi.org/10.1787/d12d7305-en}
+
+\leavevmode\vadjust pre{\hypertarget{ref-botezat2020}{}}%
+Botezat, A., \& Pfeiffer, F.
+(2020).
+The impact of parental labour migration on left{-}behind children's educational and psychosocial outcomes: Evidence from Romania.
+\emph{Population, Space and Place}, \emph{26}(2).
+\url{https://doi.org/10.1002/psp.2277}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bourdieu2002}{}}%
+Bourdieu, P. (2002). \emph{The Forms of Capital} (N. W. Biggart, Ed.; pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
+
+\leavevmode\vadjust pre{\hypertarget{ref-debrauw2017}{}}%
+Brauw, A.
+de, \& Giles, J.
+(2017).
+Migrant Opportunity and the Educational Attainment of Youth in Rural China.
+\emph{Journal of Human Resources}, \emph{52}(1), 272--311.
+\url{https://doi.org/10.3368/jhr.52.1.0813-5900R}
 
@@
 \url{https://doi.org/10.1016/j.chieco.2019.01.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2019}{}}%
+Chen, X., Li, D., Liu, J., Fu, R., \& Liu, S.
+(2019).
+Father migration and mother migration: Different implications for social, school, and psychological adjustment of left-behind children in rural china.
+\emph{Journal of Contemporary China}, \emph{28}(120), 849--863.
+\url{https://doi.org/10.1080/10670564.2019.1594100}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cunningham2021}{}}%
+Cunningham, S. (2021). \emph{Causal inference: The mixtape}. Yale University Press. \url{https://mixtape.scunning.com/}
 
@@
 \url{https://doi.org/10.1177/0011392120985874}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guo2021}{}}%
+Guo, S., Li, L., Sun, Y., Houang, R., \& Schmidt, W.
+H.
+(2021).
+Does boarding benefit the mathematics achievement of primary and middle school students?
+Evidence from china.
+\emph{Asia Pacific Journal of Education}, \emph{41}(1), 16--38.
+\url{https://doi.org/10.1080/02188791.2020.1760081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hong2019}{}}%
+Hong, Y., \& Fuller, C.
+(2019).
+Alone and {``}left behind{''}: A case study of {``}left-behind children{''} in rural china.
+\emph{Cogent Education}, \emph{6}(1), 1654236.
+\url{https://doi.org/10.1080/2331186X.2019.1654236}
+
+\leavevmode\vadjust pre{\hypertarget{ref-huntington-klein}{}}%
+Huntington-Klein, N. (n.d.). \emph{The effect: An introduction to research design and causality \textbar{} the effect}. \url{https://theeffectbook.net/index.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
+Jin, X., Chen, W., Sun, I.
+Y., \& Liu, L.
+(2020).
+Physical health, school performance and delinquency: A comparative study of left-behind and non-left-behind children in rural China.
+\emph{Child Abuse \& Neglect}, \emph{109}, 104707.
+\url{https://doi.org/10.1016/j.chiabu.2020.104707}
+
+\leavevmode\vadjust pre{\hypertarget{ref-king2019}{}}%
+King, G., \& Nielsen, R. (2019). Why Propensity Scores Should Not Be Used for Matching. \emph{Political Analysis}, \emph{27}(4), 435--454. \url{https://doi.org/10.1017/pan.2019.11}
 
@@
 \url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nguyen2016}{}}%
+Nguyen, C.
+V.
+(2016).
+Does parental migration really benefit left-behind children?
+Comparative evidence from Ethiopia, India, Peru and Vietnam.
+\emph{Social Science \& Medicine}, \emph{153}, 230--239.
+\url{https://doi.org/10.1016/j.socscimed.2016.02.021}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nsrc}{}}%
+NSRC. (n.d.). \emph{Overview-china education panel survey}. \url{http://ceps.ruc.edu.cn/English/Overview/Overview.htm}
+
+\leavevmode\vadjust pre{\hypertarget{ref-popova2018}{}}%
+Popova, A.
+(2018).
+Risk factors for the safety of the children from transnational families children left behind.
+\emph{Anthropological Researches and Studies}, \emph{1}(8), 25--35.
+\url{https://doi.org/10.26758/8.1.3}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vanhook2020}{}}%
+Van Hook, J., \& Glick, J.
+E.
+(2020).
+Spanning Borders, Cultures, and Generations: A~Decade of Research on Immigrant Families.
+\emph{Journal of Marriage and Family}, \emph{82}(1), 224--243.
+\url{https://doi.org/10.1111/jomf.12621}
+
+\leavevmode\vadjust pre{\hypertarget{ref-waldman2022}{}}%
+Waldman, K.
+E.
+(2022).
+Transnational Social Stratification?
+Legal Status of Immigrant Parents and the Educational Achievements of Mexican Children.
+\emph{International Migration Review}, 01979183221084329.
+\url{https://doi.org/10.1177/01979183221084329}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wen2020}{}}%
-Wen, M., Wang, W., Wan, N., \& Su, D.
-(2020).
-Family Income and Student Educational and Cognitive Outcomes in China: Exploring the Material and Psychosocial Mechanisms.
-\emph{Social Sciences}, \emph{9}(12), 225.
-\url{https://doi.org/10.3390/socsci9120225}
+\leavevmode\vadjust pre{\hypertarget{ref-xu2015}{}}%
+Xu, H., \& Xie, Y.
+(2015).
+The Causal Effects of Rural-to-Urban Migration on Children{'}s Well-being in China.
+\emph{European Sociological Review}, \emph{31}(4), 502--519.
+\url{https://doi.org/10.1093/esr/jcv009}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xu2019}{}}%
+Xu, Y., Xu, D., Simpkins, S., \& Warschauer, M.
+(2019).
+Does It Matter Which Parent is Absent?
+Labor Migration, Parenting, and Adolescent Development in China.
+\emph{Journal of Child and Family Studies}, \emph{28}(6), 1635--1649.
+\url{https://doi.org/10.1007/s10826-019-01382-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yang2008}{}}%
+Yang, D.
+(2008).
+International Migration, Remittances and Household Investment: Evidence from Philippine Migrants{'} Exchange Rate Shocks.
+\emph{The Economic Journal}, \emph{118}(528), 591--630.
+\url{https://doi.org/10.1111/j.1468-0297.2008.02134.x}
 
@@
 \url{https://doi.org/10.1007/s12187-021-09887-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
+Zhan, Y.
+(2020).
+The moralization of philanthropy in China: NGOs, voluntarism, and the reconfiguration of social responsibility.
+\emph{China Information}, \emph{34}(1), 68--87.
+\url{https://doi.org/10.1177/0920203X19879593}
 

### 2022-06-21 data/Gu-thesis-script.Rmd
write up main text, set matching criteria, add summary tables

--- 2022-06-11 data/Gu-thesis-script.Rmd
@@
 library(MatchIt)
-library(datawizard)
+#library(vtable)
+library(ggplot2)
+library(gtsummary)
+#library(DescTools)
 ```
@@
 d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
-d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
-d_sch2 <- read_dta('cepsw2principalCN.dta')
+#d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
+#d_sch2 <- read_dta('cepsw2principalCN.dta')
 ```
@@
 ```{r}
-dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) %>% left_join(d_sch1, by=c('schids', 'ctyids', 'fall'))
+dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
 dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
@@
 d <- d %>% mutate(
-  age = 2013 - a02a, #student's age at baseline
-  local.resi = age - a07, #years of residence at the current county
+  child.age = 2013 - a02a, #student's age at baseline
   w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
@@
 )
+```
+
+```{}
+set.seed(1)
+d %>% select(
+  w1chn_100:w2eng_100) %>%
+ggplot(aes(x=w1chn_100:w2eng_100)) + 
+  geom_boxplot(alpha=0.2)
+```
+
+Trimming outliers
+```{r}
 d <- d %>% mutate(
-  w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
-  w2ttl_100 = w2chn_100 + w2mat_100 + w2eng_100,
+  w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
+  w2chn_100_trim = if_else(w2chn_100>100, 100, w2chn_100),
+  w1mat_100_trim = if_else(w1mat_100>100, 100, w1mat_100),
+  w2mat_100_trim = if_else(w2mat_100>100, 100, w2mat_100),
+  w1eng_100_trim = if_else(w1eng_100>100, 100, w1eng_100),
+  w2eng_100_trim = if_else(w2eng_100>100, 100, w2eng_100)
 )
@@
 
-Detect outliers
 ```{r}
-d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
-d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
+d <- d %>% mutate(
+  w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
+  w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
+  ttl_dif = w2ttl_100 - w1ttl_100,
+  cog_dif = w2cog3pl - cog3pl
+  )
 ```
 
-Compute standardized exam grades (within-school z-scores)
+```{r}
+d1 <- d %>%
+  drop_na(cog_dif, ttl_dif, child.age)
+```
+
+within-class z score
 ```{}
-d1 <- d1 %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
-  group_by(schids) %>%
-  mutate(w1chn_mean = mean(w1chn_100, na.rm=T),
-         w1mat_mean = mean(w1mat_100, na.rm=T),
-         w1eng_mean = mean(w1eng_100, na.rm=T),
-         w1ttl_mean = mean(w1ttl_100, na.rm=T),
-         w2chn_mean = mean(w2chn_100, na.rm=T),
-         w2mat_mean = mean(w2mat_100, na.rm=T),
-         w2eng_mean = mean(w2eng_100, na.rm=T),
-         w2ttl_mean = mean(w2ttl_100, na.rm=T),
+d1 <- d1 %>% group_by(clsids + w2clsids) %>%
+  mutate(
+    w1ttl_z = as.numeric(scale(w1ttl)),
+    w2ttl_z = as.numeric(scale(w2ttl))
   ) %>% ungroup()
@@
 ```{}
-d1 <- d1 %>% 
-  mutate(w1chn_dif = w1chn_100 - w1chn_mean,
-         w1mat_dif = w1mat_100 - w1mat_mean,
-         w1eng_dif = w1eng_100 - w1eng_mean,
-         w1ttl_dif = w1ttl_100 - w1ttl_mean,
-         w2chn_dif = w2chn_100 - w2chn_mean,
-         w2mat_dif = w2mat_100 - w2mat_mean,
-         w2eng_dif = w2eng_100 - w2eng_mean,
-         w2ttl_dif = w2ttl_100 - w2ttl_mean,
+d1 <- d1 %>% group_by(clsids + w2clsids) %>%
+  mutate(
+    w1ttl_std = rescale(w1ttl),
+    w2ttl_std = rescale(w2ttl)
+    ) %>% ungroup()
+```
 
-         )
+Detect outliers
+```{}
+d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
+d_outlier1 <- d_outlier %>% select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
+d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
 ```
@@
 d_cl <- d1 %>% 
-  filter(w2a0801==1) %>% #parents who are married (and alive)
-  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
-  filter(stmigrant==1) #having stayed in the current county for at least six years (duration of primary school) before baseline
+  filter(w2a0801==1) %>% #keep parents who are married (and alive)
+  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
+  filter(stmigrant==1) #keep local children 
 ```
@@
 ## Variables
-```{r}
-d_cl <- d_cl %>% 
-  mutate(chn_dif = w2chn_100 - w1chn_100,
-         mat_dif = w2mat_100 - w1mat_100,
-         eng_dif = w2eng_100 - w1eng_100,
-         ttl_dif = w2ttl_100 - w1ttl_100,
-         cog_dif = w2cog3pl - cog3pl) %>%
-  drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
-```
 
@@
 d_cl <- d_cl %>% mutate(
-         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
-         ch.rural = sthktype, #student holds rural (agricultural) hukou
-         #ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
-         ch.boarding = stbrd, #student is boarding at school
-         ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         ch.health = a17, #student's self-reported health
-         ch.skip.grd = if_else(c03 == 0, 0, 1),
-         ch.repeat.grd = if_else(c04 == 0, 0, 1),
-         ch.illness = if_else(a10 == 1, 1, 0),
-         ch.preschool = if_else(c01 == 1, 1, 0),
+         child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
+         child.has.rural.hukou = sthktype, #student holds rural (agricultural) hukou
+         child.in.boarding.school = stbrd, #student is boarding at school
+         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
+         child.health.self.rated = a17, #student's self-rated health
+         child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
+         child.had.repeated.grade = if_else(c04 == 0, 0, 1), #student had repeated grade
+         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
+         child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
+         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
+         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
          par.edu = stprhedu, #Among two parents, the best-educated one's educational level
-         par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
-         home.finances = steco_3c,
-         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
-         home.book = b12 #Amount of book at home, student self-rated 
+         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
+         #par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
+         home.economic.resource = steco_5c, #self-rated household financial situation
+         home.has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
+         home.extracurricular.book = b12 #Amount of book at home, student self-rated 
 ) %>% drop_na(
-ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.minority, ch.health, ch.skip.grd, ch.repeat.grd, ch.illness, ch.preschool, par.edu, par.ccp, home.internet, home.book, home.finances)
+child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu,
+#par.ccp, 
+parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
 ```
@@
 d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
-d_cl <- d_cl %>% mutate(ch.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
-  drop_na(ch.sibling)
+d_cl <- d_cl %>% mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
+  drop_na(child.number.of.sibling)
 ```
@@
 Best-educated parent's years of education
-```{r}
-d_cl <- d_cl %>% mutate(par.edu.year = NA)
-d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
-d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
-d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
-d_cl$par.edu.year[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
-d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
-d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
-d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
+```{}
+d_cl <- d_cl %>% mutate(parent.educational.level = NA)
+d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
+d_cl$parent.educational.level[d_cl$par.edu == 2] <- 6
+d_cl$parent.educational.level[d_cl$par.edu == 3] <- 9
+d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
+d_cl$parent.educational.level[d_cl$par.edu == 7] <- 15
+d_cl$parent.educational.level[d_cl$par.edu == 8] <- 16
+d_cl$parent.educational.level[d_cl$par.edu == 9] <- 19
 ```
 
-```
-d_cl <- d_cl %>% mutate(fa.edu.year = NA)
-d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
-d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
-d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
-d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
-d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
-d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
-d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
+```{r}
+d_cl <- d_cl %>% mutate(parent.educational.level = NA)
+d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
+d_cl$parent.educational.level[d_cl$par.edu == 3] <- 2
+d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 3
+d_cl$parent.educational.level[d_cl$par.edu == 7] <- 4
+d_cl$parent.educational.level[d_cl$par.edu == 8] <- 5
+d_cl$parent.educational.level[d_cl$par.edu == 9] <- 6
 ```
 
+```{r}
+d_cl <- d_cl %>% mutate(parent.expectation.on.child = NA)
+d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
+d_cl$parent.expectation.on.child[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
+d_cl$parent.expectation.on.child[d_cl$ba18 == 6] <- 3
+d_cl$parent.expectation.on.child[d_cl$ba18 == 7] <- 4
+d_cl$parent.expectation.on.child[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
 ```
-d_cl <- d_cl %>% mutate(mo.edu.year = NA)
-d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
-d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
-d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
-d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
-d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
-d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
-d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
+
+```{r}
+d_cl <- d_cl %>% mutate(child.educational.aspiration = NA)
+d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
+d_cl$child.educational.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
+d_cl$child.educational.aspiration[d_cl$c22 == 6] <- 3
+d_cl$child.educational.aspiration[d_cl$c22 == 7] <- 4
+d_cl$child.educational.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
+```
+
+```{r}
+d_cl <- d_cl %>%  drop_na(
+  parent.educational.level, 
+  parent.expectation.on.child, 
+  child.educational.aspiration)
 ```
@@
   migr_fa_only = NA,
-  migr_fa = NA,
+  #migr_fa = NA,
   migr_mo_only = NA,
-  migr_mo = NA,
+  #migr_mo = NA,
   migr_both = NA
-  ) 
-d_cl <- d_cl %>% drop_na(migr)
+  ) %>% drop_na(migr)
 ```
@@
 Mother migrated
-```{r}
+```{}
 d_cl$migr_mo[d_cl$migr == 0] <- 0
@@
 Father migrated
-```{r}
+```{}
 d_cl$migr_fa[d_cl$migr == 0] <- 0
@@
 
-```
+```{}
 df <- d_cl %>% select(
   migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
-  cog3pl, w1chn_dif, w1mat_std, w1eng_std,
-  cog, chn_std, mat_dif, eng_dif,
-  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
-  par.edu.year, home.book, home.internet
+  cog3pl, w1ttl_100, cog_dif, ttl_dif,
+  child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.educational.aspiration,
+  par.edu, par.ccp, par.expt.univ, 
+  home.has.internet, home.extracurricular.book, home.economic.resource
 )
+```
+
+## Descriptive statistics
+```{r}
+d_migr <- d_cl %>%
+  select(
+  migr, migr_mo_only, migr_fa_only, migr_both,
+  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
+  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
+  child.health.self.rated, child.educational.aspiration, 
+  parent.educational.level, parent.expectation.on.child, 
+  home.extracurricular.book, home.economic.resource) %>%
+  remove_labels()
+```
+
+```{r}
+d_smr <- d_migr %>% 
+  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
+  mutate(`Parental Migration Type` = 0) 
+d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
+d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother Migrated'
+d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father Migrated'
+d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
+d_smr <- d_smr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+```
+
+```{r}
+datasummary_balance(
+  ~migr,
+  data = d_migr,
+  fmt = 2)
+```
+
+```{r}
+d_dpvar <- d_migr %>%
+  select(migr, 
+         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) %>%
+  rename(
+    `Cognitive score at wave 1` = cog3pl,
+    `Cognitive score at wave 2` = w2cog3pl,
+    `Academic exam score at wave 1` = w1ttl_100,
+    `Academic exam score at wave 2` = w2ttl_100,
+    `Cognitive score difference` = cog_dif,
+    `Academic exam score difference` = ttl_dif
+  ) 
+```
+
+```{}
+d_dpvar %>%
+  tbl_summary(
+    by = migr,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} / {N} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    ) %>% add_p() %>% as_kable()
+```
+
+```{r}
+#table_independent_variable <- 
+  st(
+  d_dpvar,
+  digits = 2, 
+  group = 'migr',
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = 'kable')
+#table_independent_variable 
+```
+
+```{r}
+d_dpvar <- as.data.frame(d_dpvar)
+table_dependent_variable <- datasummary(
+  All(d_dpvar) ~ Mean + SD + Min + Max,
+  data = d_dpvar,
+  output = 'markdown'
+  )
+```
+
+```{r}
+table_independent_variable <- datasummary_skim(
+    data=d_idpvar,
+    type = 'categorical',
+    output = 'markdown')
+
+```
+
+```{r}
+d_idpvar <- d_migr %>% 
+  select(migr, migr_mo_only, migr_fa_only, migr_both) %>% 
+  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
+  mutate(`Parental Migration Type` = 0) 
+d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
+d_idpvar <- d_idpvar %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+```
+
+```{r}
+
+```
+
+```{r}
+d_ctvar <- d_migr %>%
+  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
+  child.health.self.rated, child.educational.aspiration, 
+  parent.educational.level, parent.expectation.on.child, 
+  home.extracurricular.book, home.economic.resource) %>% 
+  mutate_if(is.numeric, as.factor)
+```
+
+```{r}
+d_ctvar$parent.educational.level <- d_ctvar$parent.educational.level %>% 
+  recode_factor(
+    '1' = 'Primary school and below',
+    '2' = 'Junior high school',
+    '3' = 'Senior high school',
+    '4' = 'Associate college',
+    '5' = 'University',
+    '6' = 'Postgraduate'
+  )
+d_ctvar$child.educational.aspiration <- d_ctvar$child.educational.aspiration %>%
+  recode_factor(
+    '1' = 'Junior high school',
+    '2' = 'Senior high school',
+    '3' = 'Associate college',
+    '4' = 'University',
+    '5' = 'Postgraduate'     
+  )
+d_ctvar$parent.expectation.on.child  <- d_ctvar$parent.expectation.on.child %>%
+  recode_factor(
+    '1' = 'Junior high school',
+    '2' = 'Senior high school',
+    '3' = 'Associate college',
+    '4' = 'University',
+    '5' = 'Postgraduate'    
+  )
+d_ctvar$home.economic.resource <- d_ctvar$home.economic.resource %>% 
+  recode_factor(
+    '1' = 'Very poor',
+    '2' = 'Somewhat poor',
+    '3' = 'Moderate',
+    '4' = 'Somewhat rich',
+    '5' = 'Very rich'
+  )
+d_ctvar$child.health.self.rated <- d_ctvar$child.health.self.rated %>%
+  recode_factor(
+    '1' = 'Very poor',
+    '2' = 'Not very good',
+    '3' = 'Moderate',
+    '4' = 'Good',
+    '5' = 'Very good'
+  )
+d_ctvar$home.extracurricular.book <- d_ctvar$home.extracurricular.book %>%
+  recode_factor(
+    '1' = 'Very few',
+    '2' = 'Not many',
+    '3' = 'Some',
+    '4' = 'Quite a few',
+    '5' = 'A great number'
+  )
+```
+
+```{}
+test.table <- d_ctvar %>%
+  tbl_summary(
+    by = migr,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    ) 
+```
+
+```{r}
+test_table <- datasummary_balance(
+  ~migr,
+  data = d_ctvar
+)
+test_table
+```
+
+```{r}
+#table_control_variable <- 
+table_balance <- st(
+  d_ctvar,
+  digits = 2, 
+  group = 'migr',
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = "return")
+#table_control_variable 
+```
+
+```{r}
+table_control_variable <- datasummary_skim(
+  data = d_ctvar,
+  type = 'categorical',
+  output = 'markdown'
+)
+```
+
+```{r}
+d_migr <- d_migr %>% mutate(`Parental Migration` = ifelse(migr == 1, 'Yes', 'No'))
+d_migr <- d_migr %>% mutate(`Parental Migration Type` = 0) 
+d_migr$`Parental Migration Type`[d_migr$migr==0] <- 'Both Parents At Home'
+d_migr$`Parental Migration Type`[d_migr$migr_mo_only==1] <- 'Only Mother Migrated'
+d_migr$`Parental Migration Type`[d_migr$migr_fa_only==1] <- 'Only Father Migrated'
+d_migr$`Parental Migration Type`[d_migr$migr_both==1] <- 'Both Parents Migrated'
+d_migr <- d_migr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+```
+
+Whole sample summary
+```{r}
+table_sum <- st(
+  d_migr,
+  digits = 2, 
+  out = 'kable')
+table_sum
+```
+
+```{r}
+table_sum_migr <- st(
+  d_migr,
+  group = 'Parental Migration', 
+  digits = 2, 
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = 'kable')
+table_sum_migr
 ```
@@
 ```{r}
-t.test(cog_dif ~ migr, data = d_cl)
-t.test(ttl_dif ~ migr, data = d_cl)
-t.test(chn_dif ~ migr, data = d_cl)
-t.test(mat_dif ~ migr, data = d_cl)
-t.test(eng_dif ~ migr, data = d_cl)
-```
-
-## Descriptive statistics
-```{r}
-des_gender <- d_cl %>% count(ch.girl)
-des_rural <- d_cl %>% count(ch.rural)
-des_sibling <- d_cl %>% group_by(ch.sibling) %>% count
-des_boarding <- d_cl %>% count(ch.boarding)
-des_book <- d_cl %>% group_by(home.book) %>% count
-des_internet <- d_cl %>% group_by(home.internet) %>% count
-des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
-des_ethn.minority <- d_cl %>% group_by(ch.ethn.minority) %>% count
-des_gender
-des_rural
-des_sibling
-des_boarding
-des_par.edu.year
-des_book
-des_internet
-des_ethn.minority
-```
-
-### Wave 2 outcomes of treatment group vs control group
-```{r}
-d_cl %>%
-  group_by(migr) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
+ttest_cog <- t.test(cog_dif ~ migr, data = d_cl)
+ttest_ttl <- t.test(ttl_dif ~ migr, data = d_cl)
+ttest_cog
+ttest_ttl
 ```
@@
 ```{r}
-d_cl %>%
-  group_by(migr_mo_only) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
+set.seed(1)
+fig_cog <- 
+  ggplot(d_migr, aes(x='Parental Migration Type', y=cog_dif, fill = `Parental Migration`)) + 
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    geom_boxplot(alpha=0.2)
 ```
@@
 ```{r}
-d_cl %>%
-  group_by(migr_mo) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
+set.seed(1)
+fig_ttl <- 
+ggplot(d_migr, aes(x='Parental Migration Type', y=ttl_dif, fill = `Parental Migration`)) + 
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    geom_boxplot(alpha=0.2)
 ```
@@
 ```{r}
-d_cl %>%
-  group_by(migr_fa_only) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
+set.seed(1)
+fig_cog_by_migration_type <-
+  ggplot(d_migr, aes(x='Parental Migration Type', y=cog_dif, fill = `Parental Migration Type`)) + 
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    geom_boxplot(alpha=0.2)
+
 ```
@@
 ```{r}
-d_cl %>%
-  group_by(migr_fa) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_both) %>% 
-  summarise(n_cases = n(),
-            mean_cog = mean(w2cog3pl, na.rm=T),
-            mean_ttl = mean(w2ttl_dif, na.rm=T),
-            mean_chn = mean(w2chn_dif, na.rm=T),
-            mean_mat = mean(w2mat_dif, na.rm=T),
-            mean_eng = mean(w2eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-### Change in outcomes of treatment group vs control group
-```{r}
-d_cl %>%
-  group_by(migr) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo_only) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_mo) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa_only) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_fa) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
-```
-
-```{r}
-d_cl %>%
-  group_by(migr_both) %>% 
-  summarise(n_cases = n(),
-            mean_change_cog = mean(cog_dif, na.rm=T),
-            mean_change_ttl = mean(ttl_dif, na.rm=T),
-            mean_change_chn = mean(chn_dif, na.rm=T),
-            mean_change_mat = mean(mat_dif, na.rm=T),
-            mean_change_eng = mean(eng_dif, na.rm=T)
-            ) %>%
-  drop_na()
+set.seed(1)
+fig_ttl_by_migration_type <-
+  ggplot(d_migr, aes(x='Parental Migration Type', y=ttl_dif, fill = `Parental Migration Type`)) + 
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    geom_boxplot(alpha=0.2)
 ```
@@
 ```{r}
-did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl) 
-did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl) 
-did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl) 
-did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl) 
-did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl) 
-did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl)
+did_cog <- feols(cog_dif ~ migr + cog3pl | clsids + w2clsids, data = d_cl) 
+did_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | clsids + w2clsids, data = d_cl) 
+#did_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | clsids + w2clsids, data = d_cl) 
+did_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | clsids + w2clsids, data = d_cl) 
+#did_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | clsids + w2clsids, data = d_cl) 
+did_cog_both <- feols(cog_dif ~ migr_both + cog3pl | clsids + w2clsids, data = d_cl)
 ```
@@
 ```{r}
-models_unres_cog <- list(
-'Any Parent Absent' = did_unres_cog,
-'Only Mother Absent' = did_unres_cog_m_only,
-'Mother Absent' = did_unres_cog_m,
-'Only Father Absent' = did_unres_cog_f_only,
-'Father Absent' = did_unres_cog_f,
-'Both Parents Absent' = did_unres_cog_both) 
-table_unres_cog <- models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-                              fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
-table_unres_cog
+models_cog <- list(
+'Any Parent Absent' = did_cog,
+'Only Mother Absent' = did_cog_m_only,
+#'Mother Absent' = #did_cog_m,
+'Only Father Absent' = did_cog_f_only,
+#'Father Absent' = #did_cog_f,
+'Both Parents Absent' = did_cog_both) 
 ```
@@
 ```{r}
-did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | schids, data = d_cl) 
-did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | schids, data = d_cl) 
-did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | schids, data = d_cl) 
-did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | schids, data = d_cl) 
-did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | schids, data = d_cl) 
-did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | schids, data = d_cl)
+table_cog <- models_cog %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+  fmt = 2,
+  title = 'Parental migration’s effect on children’s cognitive abilities',
+  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+  output = 'markdown')
+table_cog
+```
+
+raw score
+```{r}
+did_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | clsids + w2clsids, data = d_cl) 
+did_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | clsids + w2clsids, data = d_cl) 
+#did_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | clsids + w2clsids, data = d_cl) 
+did_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | clsids + w2clsids, data = d_cl) 
+#did_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | clsids + w2clsids, data = d_cl) 
+did_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | clsids + w2clsids, data = d_cl)
 ```
@@
 ```{r}
-models_unres_ttl <- list(
-'Any Parent Absent' = did_unres_ttl,
-'Only Mother Absent' = did_unres_ttl_m_only,
-'Mother Absent' = did_unres_ttl_m,
-'Only Father Absent' = did_unres_ttl_f_only,
-'Father Absent' = did_unres_ttl_f,
-'Both Parents Absent' = did_unres_ttl_both) 
-table_unres_ttl <- models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+models_ttl <- list(
+'Any Parent Absent' = did_ttl,
+'Only Mother Absent' = did_ttl_m_only,
+#'Mother Absent' = #did_ttl_m,
+'Only Father Absent' = did_ttl_f_only,
+#'Father Absent' = #did_ttl_f,
+'Both Parents Absent' = did_ttl_both) 
+```
+
+```{r}
+table_ttl <- models_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
+  title = 'Parental migration’s effect on children’s academic abilities',
+  fmt = 2,
+  coef_rename = c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
+  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+  output = 'markdown')
+table_ttl
+```
+
+z score
+```{}
+did_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | clsids + w2clsids, data = d_cl) 
+did_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | clsids + w2clsids, data = d_cl) 
+did_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | clsids + w2clsids, data = d_cl) 
+did_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | clsids + w2clsids, data = d_cl) 
+did_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | clsids + w2clsids, data = d_cl) 
+did_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | clsids + w2clsids, data = d_cl)
+```
+
+```{}
+models_ttl_z <- list(
+'Any Parent Absent' = did_ttl_z,
+'Only Mother Absent' = did_ttl_z_m_only,
+#'Mother Absent' = did_ttl_z_m,
+'Only Father Absent' = did_ttl_z_f_only,
+#'Father Absent' = did_ttl_z_f,
+'Both Parents Absent' = did_ttl_z_both) 
+table_ttl_z <- models_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
                               coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
-table_unres_ttl
+table_ttl_z
 ```
 
-Regressing on Chinese exam score
-```{r}
-did_unres_chn <- feols(chn_dif ~ migr + w1chn_100 | schids, data = d_cl) 
-did_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100 | schids, data = d_cl) 
-did_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100 | schids, data = d_cl) 
-did_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100 | schids, data = d_cl) 
-did_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100 | schids, data = d_cl) 
-did_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100 | schids, data = d_cl)
+std
+```{}
+did_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | clsids + w2clsids, data = d_cl) 
+did_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | clsids + w2clsids, data = d_cl) 
+did_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | clsids + w2clsids, data = d_cl) 
+did_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | clsids + w2clsids, data = d_cl) 
+did_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | clsids + w2clsids, data = d_cl) 
+did_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | clsids + w2clsids, data = d_cl)
 ```
 
-Results
-```{r}
-models_unres_chn <- list(
-'Any Parent Absent' = did_unres_chn,
-'Only Mother Absent' = did_unres_chn_m_only,
-'Mother Absent' = did_unres_chn_m,
-'Only Father Absent' = did_unres_chn_f_only,
-'Father Absent' = did_unres_chn_f,
-'Both Parents Absent' = did_unres_chn_both) 
-table_unres_chn <- models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+```{}
+models_ttl_std <- list(
+'Any Parent Absent' = did_ttl_std,
+'Only Mother Absent' = did_ttl_std_m_only,
+#'Mother Absent' = did_ttl_std_m,
+'Only Father Absent' = did_ttl_std_f_only,
+#'Father Absent' = did_ttl_std_f,
+'Both Parents Absent' = did_ttl_std_both) 
+table_ttl_std <- models_ttl_std %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_dif" = "Baseline difference"), output = 'markdown')
-table_unres_chn
-```
-
-Regressing on Math score
-```{r}
-did_unres_mat <- feols(mat_dif ~ migr + w1mat_100| schids, data = d_cl) 
-did_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100| schids, data = d_cl) 
-did_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100| schids, data = d_cl) 
-did_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100| schids, data = d_cl) 
-did_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100| schids, data = d_cl) 
-did_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100| schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_mat <- list(
-'Any Parent Absent' = did_unres_mat,
-'Only Mother Absent' = did_unres_mat_m_only,
-'Mother Absent' = did_unres_mat_m,
-'Only Father Absent' = did_unres_mat_f_only,
-'Father Absent' = did_unres_mat_f,
-'Both Parents Absent' = did_unres_mat_both) 
-table_unres_mat <- models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-                              fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_dif" = "Baseline Score"), output = 'markdown')
-table_unres_mat
-```
-
-Regressing on English score
-```{r}
-did_unres_eng <- feols(eng_dif ~ migr + w1eng_100| schids, data = d_cl) 
-did_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100| schids, data = d_cl)
-did_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100| schids, data = d_cl) 
-did_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100| schids, data = d_cl) 
-did_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100| schids, data = d_cl) 
-did_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100| schids, data = d_cl)
-```
-
-Results
-```{r}
-models_unres_eng <- list(
-'Any Parent Absent' = did_unres_eng,
-'Only Mother Absent' = did_unres_eng_m_only,
-'Mother Absent' = did_unres_eng_m,
-'Only Father Absent' = did_unres_eng_f_only,
-'Father Absent' = did_unres_eng_f,
-'Both Parents Absent' = did_unres_eng_both) 
-table_unres_eng <- models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-                              fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_dif" = "Baseline difference"), output = 'markdown')
-table_unres_eng
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_ttl_std
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog_dif ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
-did_adj_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
-did_adj_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
-did_adj_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
-did_adj_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
-did_adj_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book  + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog_dif ~ migr + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
 ```
@@
 ```{r}
-models_adj_unres_cog <- list(
-'Any Parent Absent' = did_adj_unres_cog,
-'Only Mother Absent' = did_adj_unres_cog_m_only,
-'Mother Absent' = did_adj_unres_cog_m,
-'Only Father Absent' = did_adj_unres_cog_f_only,
-'Father Absent' = did_adj_unres_cog_f,
-'Both Parents Absent' = did_adj_unres_cog_both) 
-table_adj_unres_cog <- models_adj_unres_cog %>% 
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+models_adj_cog <- list(
+'Any Parent Absent' = did_adj_cog,
+'Only Mother Absent' = did_adj_cog_m_only,
+#'Mother Absent' = #did_adj_cog_m,
+'Only Father Absent' = did_adj_cog_f_only,
+#'Father Absent' = #did_adj_cog_f,
+'Both Parents Absent' = did_adj_cog_both) 
+```
+
+```{r}
+table_adj_cog <- models_adj_cog %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s cognitive abilities',
            fmt = 2, 
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
-table_adj_unres_cog
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+           output = 'markdown'
+  )
+table_adj_cog
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
 ```
@@
 ```{r}
-models_adj_unres_ttl <- list(
-'Any Parent Absent' = did_adj_unres_ttl,
-'Only Mother Absent' = did_adj_unres_ttl_m_only,
-'Mother Absent' = did_adj_unres_ttl_m,
-'Only Father Absent' = did_adj_unres_ttl_f_only,
-'Father Absent' = did_adj_unres_ttl_f,
-'Both Parents Absent' = did_adj_unres_ttl_both) 
-table_adj_unres_ttl <- models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
-table_adj_unres_ttl
+models_adj_ttl <- list(
+'Any Parent Absent' = did_adj_ttl,
+'Only Mother Absent' = did_adj_ttl_m_only,
+#'Mother Absent' = #did_adj_ttl_m,
+'Only Father Absent' = did_adj_ttl_f_only,
+#'Father Absent' = #did_adj_ttl_f,
+'Both Parents Absent' = did_adj_ttl_both)
 ```
 
-Regressing on Chinese exam score
 ```{r}
-did_adj_unres_chn <- feols(chn_dif ~ migr + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m_only <- feols(chn_dif ~ migr_mo_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_m <- feols(chn_dif ~ migr_mo + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f_only <- feols(chn_dif ~ migr_fa_only + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_f <- feols(chn_dif ~ migr_fa + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_chn_both <- feols(chn_dif ~ migr_both + w1chn_100  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+table_adj_ttl <- models_adj_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
+  title = 'Parental migration’s effect on children’s academic abilities',
+  fmt = 2, 
+  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"), output = 'markdown')
+table_adj_ttl
+```
+
+Regressing on total exam score
+```{}
+did_adj_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
 ```
@@
 Results
-```{r}
-models_adj_unres_chn <- list(
-'Any Parent Absent' = did_adj_unres_chn,
-'Only Mother Absent' = did_adj_unres_chn_m_only,
-'Mother Absent' = did_adj_unres_chn_m,
-'Only Father Absent' = did_adj_unres_chn_f_only,
-'Father Absent' = did_adj_unres_chn_f,
-'Both Parents Absent' = did_adj_unres_chn_both) 
-table_adj_unres_chn <- models_adj_unres_chn %>% 
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           fmt = 2,
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1chn_dif" = "Baseline difference"), output = 'markdown')
-table_adj_unres_chn
+```{}
+models_adj_ttl_z <- list(
+'Any Parent Absent' = did_adj_ttl_z,
+'Only Mother Absent' = did_adj_ttl_z_m_only,
+#'Mother Absent' = did_adj_ttl_z_m,
+'Only Father Absent' = did_adj_ttl_z_f_only,
+#'Father Absent' = did_adj_ttl_z_f,
+'Both Parents Absent' = did_adj_ttl_z_both) 
+table_adj_ttl_z <- models_adj_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_ttl_z
 ```
 
-Regressing on Math score
-```{r}
-did_adj_unres_mat <- feols(mat_dif ~ migr + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m_only <- feols(mat_dif ~ migr_mo_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_m <- feols(mat_dif ~ migr_mo + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f_only <- feols(mat_dif ~ migr_fa_only + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_f <- feols(mat_dif ~ migr_fa + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_mat_both <- feols(mat_dif ~ migr_both + w1mat_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
+Regressing on total exam score
+```{}
+did_adj_ttl_dm <- feols(ttl_dm_dif ~ migr + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
 ```
@@
 Results
-```{r}
-models_adj_unres_mat <- list(
-'Any Parent Absent' = did_adj_unres_mat,
-'Only Mother Absent' = did_adj_unres_mat_m_only,
-'Mother Absent' = did_adj_unres_mat_m,
-'Only Father Absent' = did_adj_unres_mat_f_only,
-'Father Absent' = did_adj_unres_mat_f,
-'Both Parents Absent' = did_adj_unres_mat_both) 
-table_adj_unres_mat <- models_adj_unres_mat %>% 
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           fmt = 2,
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1mat_dif" = "Baseline difference"), output = 'markdown')
-table_adj_unres_mat
-```
-
-Regressing on English score
-```{r}
-did_adj_unres_eng <- feols(eng_dif ~ migr + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m <- feols(eng_dif ~ migr_mo + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_dif ~ migr_mo_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f <- feols(eng_dif ~ migr_fa + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_f_only <- feols(eng_dif ~ migr_fa_only + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_both <- feols(eng_dif ~ migr_both + w1eng_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_adj_unres_eng <- list(
-'Any Parent Absent' = did_adj_unres_eng,
-'Only Mother Absent' = did_adj_unres_eng_m_only,
-'Mother Absent' = did_adj_unres_eng_m,
-'Only Father Absent' = did_adj_unres_eng_f_only,
-'Father Absent' = did_adj_unres_eng_f,
-'Both Parents Absent' = did_adj_unres_eng_both) 
-table_adj_unres_eng <- models_adj_unres_eng %>% 
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           fmt = 2,
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1eng_dif" = "Baseline difference"), output = 'markdown')
-table_adj_unres_eng
+```{}
+models_adj_ttl_dm <- list(
+'Any Parent Absent' = did_adj_ttl_dm,
+'Only Mother Absent' = did_adj_ttl_dm_m_only,
+#'Mother Absent' = did_adj_ttl_dm_m,
+'Only Father Absent' = did_adj_ttl_dm_f_only,
+#'Father Absent' = did_adj_ttl_dm_f,
+'Both Parents Absent' = did_adj_ttl_dm_both) 
+table_adj_ttl_dm <- models_adj_ttl_dm %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_ttl_dm
 ```
@@
 ```{r}
-m.out <- matchit(migr ~ age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet, data = d_cl, method = "cem")
-summary(m.out, un = FALSE)
+m.out <- matchit(
+  migr ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  data = d_cl, 
+  replace = T,
+  ratio = 3,
+  method = "nearest", 
+  distance = "glm",
+  exact = migr ~ ctyids
+  )
+summary(m.out) %>% plot()
 ```
@@
 ```{r}
-d_match <- match.data(m.out)
+dm <- match.data(m.out)
 ```
@@
 ```{r}
-feols(cog_dif ~ migr + cog3pl + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet | schids, data = d_match, weights = d_match$weights) %>%
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           fmt = 2)
-feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.illness + ch.preschool + ch.skip.grd + ch.repeat.grd +ch.boarding + ch.ethn.minority + par.edu.year + par.ccp + home.finances + home.book + home.internet  | schids, data = d_match, weights = d_match$weights) %>%
-  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-           fmt = 2)
+didm_cog <- feols(cog_dif ~ migr + cog3pl | clsids + w2clsids, data = dm, weights = dm$weights)
+
+didm_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | clsids + w2clsids, data = dm, weights = dm$weights)
+
+didm_adj_cog <- feols(cog_dif ~ migr + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm, weights = dm$weights)
+
+didm_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm, weights = dm$weights)
+
 ```
+
+```{r}
+d_mo_only <- d_cl %>% drop_na(migr_mo_only)
+m.out_mo_only <- 
+  matchit(migr_mo_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  data = d_mo_only, 
+  replace = T,
+  method = "nearest",
+  distance = "glm",
+  ratio = 3,
+  exact = migr_mo_only ~ ctyids
+  )
+summary(m.out_mo_only) %>% plot()
+```
+
+```{r}
+dm_mo_only <- match.data(m.out_mo_only)
+```
+
+```{r}
+didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + cog3pl | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_ttl_mo_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_adj_ttl_mo_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+```
+
+```{r}
+d_fa_only <- d_cl %>% drop_na(migr_fa_only)
+m.out_fa_only <- matchit(
+  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  data = d_fa_only,
+  replace = T,
+  method = "nearest",
+  distance = "glm",
+  ratio = 3,
+  exact = migr_fa_only ~ ctyids
+  )
+summary(m.out_fa_only) %>% plot()
+```
+
+```{r}
+dm_fa_only <- match.data(m.out_fa_only)
+```
+
+```{r}
+didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + cog3pl | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_ttl_fa_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_adj_ttl_fa_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+```
+
+```{r}
+d_both <- d_cl %>% drop_na(migr_both) 
+m.out_both <- matchit(
+  migr_both ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level + home.economic.resource + home.extracurricular.book + home.has.internet,
+  data = d_both, 
+  method = "nearest",
+  distance = "glm",
+  replace = T,
+  ratio = 3,
+  exact = migr_both ~ ctyids
+  )
+summary(m.out_both) %>% plot()
+```
+
+```{r}
+dm_both <- match.data(m.out_both)
+```
+
+```{r}
+didm_cog_both <- feols(cog_dif ~ migr_both + cog3pl | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
+
+didm_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
+
+didm_adj_cog_both <- feols(cog_dif ~ migr_both + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
+
+didm_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
+
+```
+
+```{}
+d_mo <- d_cl %>% drop_na(migr_mo)
+m.out_mo <- matchit(
+  migr_mo ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, data = d_mo,
+  method = "nearest",
+  replace = T,
+  ratio = 3,
+  exact = migr_mo ~ ctyids
+  )
+summary(m.out_mo, un = FALSE)
+```
+
+```{}
+dm_mo <- match.data(m.out_mo)
+```
+
+```{}
+feols(cog_dif ~ migr_mo + cog3pl| clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
+
+feols(ttl_dif ~ migr_mo + w1ttl_100  | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
+
+feols(cog_dif ~ migr_mo + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
+
+feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
+
+```
+
+```{}
+d_fa <- d_cl %>% drop_na(migr_fa)
+m.out_fa <- matchit(
+  migr_fa ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, data = d_fa,
+  method = "nearest",
+  replace = T,
+  ratio = 3,
+  exact = migr_fa_only ~ ctyids
+  )
+summary(m.out_fa, un = FALSE)
+```
+
+```{}
+dm_fa <- match.data(m.out_fa)
+```
+
+```{}
+feols(cog_dif ~ migr_fa + cog3pl | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
+
+feols(ttl_dif ~ migr_fa + w1ttl_100 | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
+
+feols(cog_dif ~ migr_fa + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
+
+feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
+
+```
+
+```{r}
+models_m_cog <- list(
+'Any Parent Absent' = didm_cog,
+'Only Mother Absent' = didm_cog_mo_only,
+##'Mother Absent' = #did_adj_cog_m,
+'Only Father Absent' = didm_cog_fa_only,
+##'Father Absent' = #did_adj_cog_f,
+'Both Parents Absent' = didm_cog_both) 
+table_m_cog <- models_m_cog %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s cognitive abilities',
+           fmt = 2,
+           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+           output = 'markdown'
+  )
+table_m_cog
+```
+
+```{r}
+models_m_ttl <- list(
+'Any Parent Absent' = didm_ttl,
+'Only Mother Absent' = didm_ttl_mo_only,
+##'Mother Absent' = #did_adj_ttl_m,
+'Only Father Absent' = didm_ttl_fa_only,
+##'Father Absent' = #did_adj_ttl_f,
+'Both Parents Absent' = didm_ttl_both) 
+table_m_ttl <- models_m_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s academic abilities',
+           fmt = 2,
+           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
+           output = 'markdown'
+  )
+table_m_ttl
+```
+
+```{r}
+models_m_adj_cog <- list(
+'Any Parent Absent' = didm_adj_cog,
+'Only Mother Absent' = didm_adj_cog_mo_only,
+##'Mother Absent' = #did_adj_cog_m,
+'Only Father Absent' = didm_adj_cog_fa_only,
+##'Father Absent' = #did_adj_cog_f,
+'Both Parents Absent' = didm_adj_cog_both) 
+table_m_adj_cog <- models_m_adj_cog %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s cognitive abilities',
+           fmt = 2,
+           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+           output = 'markdown'
+  )
+table_m_adj_cog
+```
+
+```{r}
+models_m_adj_ttl <- list(
+'Any Parent Absent' = didm_adj_ttl,
+'Only Mother Absent' = didm_adj_ttl_mo_only,
+##'Mother Absent' = #did_adj_ttl_m,
+'Only Father Absent' = didm_adj_ttl_fa_only,
+##'Father Absent' = #did_adj_ttl_f,
+'Both Parents Absent' = didm_adj_ttl_both) 
+table_m_adj_ttl <- models_m_adj_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s academic abilities',
+           fmt = 2,
+           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
+           output = 'markdown'
+  )
+table_m_adj_ttl
+```
+
+```{r}
+num.outlier <- d_cl%>%filter(w1mat_100>100|w1eng_100>100|w2mat_100>100|w2eng_100>100)%>%count
+```
+
+## Interaction
+```{r}
+d_cl1 <- d_cl %>% mutate(
+  home.economic.resource.w2 = if_else(is.na(w2be23), w2a09, w2be23)
+)
+d_cl1 <- d_cl %>% mutate(
+  fin.better = if_else(home.economic.resource.w2 > home.economic.resource,
+                       1,
+                       0)
+  )
+
+```
+
+```{r}
+feols(ttl_dif ~ migr*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) %>%
+  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  %>%
+  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+```
+
+```{r}
+feols(ttl_dif ~ migr*fin.better + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr*fin.better + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+```
+
+```{r}
+d_cl1=d_cl1 %>% mutate(
+  supervision.less = if_else(b2201 > w2a18 & b2202 > w2a19, 1, 0)
+)
+```
+
+```{r}
+feols(ttl_dif ~ migr*supervision.less + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr*supervision.less + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+```

### 2022-06-23 MScThesisText.Rmd
First draft

@@
 library("papaja")
-library("kableExtra")
 r_refs("references.bib")
@@
 Consider children's education.
-According to [@vanhook2020] and [@debrauw2019], labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by De Brauw [-@debrauw2019] and by Van Hook and Glick [-@vanhook2020], labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
@@
 
-To what extent do parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyze data from a nationally representative two-wave panel survey.
-The sample includes children in both urban and rural areas.
+In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
+I choose China as the case and analyze data from a two-wave panel survey.
+The nationally representative sample includes children in both urban and rural areas.
 I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness check.
@@
 Researchers obtained mixed results regarding how parental migration affects children's education.
-[@botezat2020] studied the case of Romania and found a positive effect of parents' migration on academic grades of adolesents aged eleven to fifteen.
-[@wang2019] collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, [@debrauw2017] showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-[@nguyen2016] demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
+Botezat and Pfeiffer [-@botezat2020] studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
+Wang and others [-@wang2019] collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, De Brauw and Giles [-@debrauw2017] showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+Nguyen [-@nguyen2016] demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
 The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
@@
 
-The social norms designate men as breadwinners and women as caregivers.
+In China, the social norms designate men as breadwinners and women as caregivers.
 Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
@@
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
+They form the backbone of essential industries, such as delivery, transportation, and manufacturing.
 The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
@@
 One can move out of town freely but cannot change hukou freely.
-For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
-Without an urban hukou they cannot send children to public school in the host city.
-Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiveing urban hukou, they enjoy limited access to public service in the host city, including public education for children.
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns [@gu2021; @zhang2018].
+Migrant laborers had attempted to strike or protest, only to meet with police crackdown [@chan2017].
 
-The research on China's left behind children has three major shortcomings.
-First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-[@nbs2017] stated that the number of urban left behind children had been growing and expected that the trend would continue.
+The existing research about China's left behind children has three major shortcomings that I aim to tackle.
+The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+I included urban left behind children as well.
+The National Bureau of Statistics stated that the number of urban left behind children had been growing and expected that the trend would continue [@nbs2017].
 The second shortcoming lies in data and sampling.
@@
 Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
-The third shortcoming lies in the selection and measurement of outcome.
+I adopted a nationally representative two-wave panel dataset.
+The third shortcoming lies in the measurement of outcome.
 [@chang2019; @wang2019] measured students' educational performance with the test score of only one academic subject, namely mathematics.
-The test results of multiple subjects should be included to measure comprehensive academic achievement.
+I included the test results of multiple subjects to measure comprehensive academic achievement.
 
@@
 
-I adopted `r cite_r` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
+I adopted `R` for all the analyses, the `fixest` package for building the econometric models [@berge2022], and the `modelsummary` package for presenting the results [@arel-bundock2022].
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
@@
 
-The table below provides the summary statistics.
+The tables below provide the whole-sample summary statistics.
+In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatmeng group and the control group.
 
@@
 
-Researchers noted that migrants represent a positively selected group compared to non-migrants [@vanhook2020].
-One technique to tackle the selectivity issue is matching.
+Researchers noted that migrants represent a positively selected group compared to non-migrants [@vanhook2020], which may present systematic differences between left behind children and their non-left-behind peers.
+One technique to tackle this selection bias is matching.
 This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-Popular choices include coarsened exact matching (CEM) [@waldman2022], nearest-neighbor propensity score matching (PSM) [@xu2015], and nearest-neighbor Mahalanobis distance matching (MDM) [@guo2021].
-CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+Popular choices include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
+As Greifer [-@greifer2022] introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
 The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest eligible control unit to be paired.
-The eligibility as the "closest" can be determined with the differences in Mahalanobis distance or in propensity score.
+The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
+The eligibility as the "closest" can be determined with the differences in propensity score.
 Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition as each pairing ignores how other units will be or have been paired.
-This matching method may result in more "imbalance, model dependence, and bias" on highly balanced data [@king2019].
+Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred [@greifer2022].
+King and Nelson [-@king2019] argue against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
 
-I conducted matching with all the covariates used in the adjusted DID model.
+I adopted the `MatchIt` package to perform matching with all the covariates of the adjusted DID model [@ho2022].
 I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
@@
 The matching ratio was set at one treatment unit with up to three control units.
+The matching produced absolute standardized mean differences below 0.1 for all but a few covariates.
 
-Alike are the results with matching and those without.
+Alike are the results from DID models with matching (DIDM) and those without.
 In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
 In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
-The magnitudes of the coefficients are also similar.
+The significance level of any parent migration drops to ten percent.
+In all models, the magnitudes of the statistically significant coefficients are similar.
+I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
 
@@
 ```
+
+\newpage
+
+# Discussion
+
+This thesis proposed a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
+I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
+I further examined whether the effect varies across different arrangements of parental migration.
+Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
+In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
+
+My research has limitations in sample identification due to data constraint.
+First, the CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
+I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+It is possible that some parents are jailed or hospitalized.
+These types of absence would be wrongly attributed to migration.
+Second, the CEPS also lacks information on parents' migration history.
+Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left behind.
+Both limitations may lead to selection bias.
+
+Limitations also arise from unaccounted endogeneity and exogeneity.
+Endogenous factors may create selection bias.
+As Chen and coauthors [-@chen2009] stated: When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
+Exogenous factors may create omitted variable bias.
+Suppose that a natural hazard hit many counties of a province in the sample.
+This shock can simultaneously increase parents' out-migration and reduce students' grades [@chen2009].
+I could not account for such shocks as CEPS data does not include detailed geographic information.
+
+From my research, we can find future directions for scholarly inquiry.
+Researchers can improve my research design with new releases of CEPS data.
+A three-wave panel dataset will facilitate the examination of parallel trend assumption through multi-period DID models.
+Researchers can also examine how would left behind children respond when one or both of the migrant parents return home and settle down [@liang2021].
+In English-language publications, only one piece has explored return migrants and their stay-behind children in the Chinese context [@liu2018].
+
+Let us consider the policy implications.
+The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
+A slight drop of educational performance may worsen with time.
+Besides, parental migration also affects left behind children's mental health and non-cognitive skills [@antia2020].
+These outcomes are also important for human development.
+Policymakers should reduce institutional barriers at destination cities so that the split migrant families can unify without concern.
+Meanwhile, schools should dedicate more advisory and counseling support to left-behind children.
+
+\newpage
+
+# Appendix
+
+## Figures
+
+```{r, fig.cap = "Changes in standardized cognitive test score for newly left behind students and non-left-behind students"}
+fig_cog
+```
+
+```{r, fig.cap = "Changes in academic exam score for newly left behind students and non-left-behind students"}
+fig_ttl
+```
+
+```{fig.cap = "Sample balance before and after matching by any parent migration"}
+plot(summary(m.out), xlim = c(0, 0.55), position = 'right')
+```
+
+```{fig.cap = "Sample balance before and after matching by only mother migration"}
+plot(summary(m.out_mo_only), xlim = c(0, 0.55), position = 'right')```
+```
+
+```{fig.cap = "Sample balance before and after matching by only father migration"}
+plot(summary(m.out_fa_only), xlim = c(0, 0.55), position = 'right')
+```
+
+```{fig.cap = "Sample balance before and after matching by both parents migration"}
+plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+```
+
+## Tables
 
@@
 
-# Discussion
-
-This thesis proposed a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
-I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
-I further examined whether the effect varies across different arrangements of parental migration.
-Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
-
-My research has several limitations in sample selection.
-The CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
-Given such constraint, I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
-It is possible that some parents are jailed or hospitalized.
-These types of absence would be wrongly attributed to migration.
-The CEPS also lacks information on parents' migration history.
-Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as newly left behind.
-
-\newpage
-
 # References

### 2022-06-23 MScThesisText.tex
First draft

@@
 \hypersetup{
-  pdftitle={Parental Migration and Left-Behind Children's Cognitive and Academic Performances},
+  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
   pdfauthor={Jiancheng Gu1},
@@
 
-\title{Parental Migration and Left-Behind Children's Cognitive and Academic Performances}
+\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020).
-These are the so-called ``left behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
+These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
 Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children, (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
 
-How are children faring when parents have migrated?
+How are stay-behind children faring when parents have migrated?
 Scholars have obtained mixed results due to the differential effects of parental migration.
 Consider children's education.
-(Van Hook \& Glick, 2020) labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by De Brauw (2019) and by Van Hook and Glick (2020), labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
@@
 
-To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
-I analyze the data from a nationally representative two-wave panel survey.
-The sample includes children in both urban and rural areas.
-I develop a difference-in-differences design for causal inference.
-The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
+In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
+I choose China as the case and analyze data from a two-wave panel survey.
+The nationally representative sample includes children in both urban and rural areas.
+I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness check.
+The outcome was measured with children's cognitive test score and academic exam scores.
+I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
 
@@
 Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
-One model, the resource generation model, holds that parental migration brings forth greater resources in the form of economic capital.
+One is the resource generation model.
+It holds that parental migration brings forth greater resources in the form of economic capital.
 Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
@@
 (D.
-Yang, 2008) noted that a depreciation of Filipino peso increased the amount of foreign remittances, which subsequently boosted children's school enrollment and educational expenditure.
+Yang, 2008) noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+This subsequently boosted children's school enrollment and educational expenditure.
 In China, (Chang et al., 2019) interviewed migrant workers and their family members.
@@
 Researchers obtained mixed results regarding how parental migration affects children's education.
-(Botezat \& Pfeiffer, 2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolesents aged eleven to fifteen.
-(Wang et al., 2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, (Brauw \& Giles, 2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-(Nguyen, 2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
+Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
+Wang and others (2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, De Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
 The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
@@
 
-The social norms designate men as breadwinners and women as caregivers.
+In China, the social norms designate men as breadwinners and women as caregivers.
 Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
@@
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
+They form the backbone of essential industries, such as delivery, transportation, and manufacturing.
 The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
@@
 Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
-Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Zhan, 2020).
-The third feature is the authoritarian control against citizens.
-According to Gu (2021), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
-One can move to another place freely but cannot change hukou freely.
-For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
-Without an urban hukou they cannot send children to public school in the host city.
-Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
-
-The research on China's left behind children has three major shortcomings.
-First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-(NBS et al., 2017) stated that the number of urban left behind children had been growing and expected that the trend would continue.
+Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Duckett, 2020).
+The third is the authoritarian control against citizens.
+According to Gu (2021) and Zhang (2018), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+One can move out of town freely but cannot change hukou freely.
+For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiveing urban hukou, they enjoy limited access to public service in the host city, including public education for children.
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns (Gu, 2021; Zhang, 2018).
+Migrant laborers had attempted to strike or protest, only to meet with police crackdown (Chan \& Selden, 2017).
+
+The existing research about China's left behind children has three major shortcomings that I aim to tackle.
+The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+I included urban left behind children as well.
+The National Bureau of Statistics stated that the number of urban left behind children had been growing and expected that the trend would continue (NBS et al., 2017).
 The second shortcoming lies in data and sampling.
 Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014).
-Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Liu et al., 2021; Shu, 2021; F.
+Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Y.
+Liu et al., 2021; Shu, 2021; F.
 Yang et al., 2022).
-The third shortcoming lies in the selection and measurement of outcome.
+I adopted a nationally representative two-wave panel dataset.
+The third shortcoming lies in the measurement of outcome.
 (Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
-The test results of multiple subjects should be included to measure comprehensive academic achievement.
+I included the test results of multiple subjects to measure comprehensive academic achievement.
 
@@
 
-I explored two categories of adolescence development: cognitive and academic abilities.
+I explored two categories of educational performance: cognitive and academic abilities.
 One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
@@
 These three subjects constitute the core parts in the senior high school entrance exam.
-Within one particular school, teachers of the same subject use the same syllabus, administering the same exams during a given assessment period.
+Junior high school students study these subjects throughout three academic years.
+Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period.
 Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort.
 I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
-Accordingly, the total score of three subjects has a 300-point scale.
+After the conversion, I checked for abnormal values outside the 0-100 range.
+31 observations are outliers, accounting for less than one percent of the sample.
+I trim the values of subject exam score with minimum of zero and maximum of one hundred.
+In this way, I can limit the impact of outliers while retaining these observations in the sample.
+After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
 
@@
 
-I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for building the econometric models (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j}\] For student \(i\) taking the test of type \(j\), \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{1}\) and \(C_{2}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j;1}\) is the test score at baseline.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{j}\) and \(C_{k}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j,k;1}\) is the test score at baseline.
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
@@
 
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{1} + \lambda \cdot C_{2} + \theta \cdot score_{i,j;1} + \zeta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 \endhead
-migr & 0.16 & 0.36 & 0.00 & 1.00 \\
 Cognitive score difference & 0.27 & 0.80 & -2.88 & 4.03 \\
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
 \toprule
@@
 
-Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020).
-One technique to tackle the selectivity issue is matching.
+Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020), which may present systematic differences between left behind children and their non-left-behind peers.
+One technique to tackle this selection bias is matching.
 This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-Popular choices include coarsened exact matching (CEM) (Waldman, 2022), nearest-neighbor propensity score matching (PSM) (H.
-Xu \& Xie, 2015), and nearest-neighbor Mahalanobis distance matching (MDM) (Guo et al., 2021).
-CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+Popular choices include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H.
+Xu \& Xie, 2015).
+As Greifer (2022) introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
 The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest eligible control unit to be paired.
-The eligibility as the ``closest'' can be determined with the differences in Mahalanobis distance or in propensity score.
+The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
+The eligibility as the ``closest'' can be determined with the differences in propensity score.
 Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition as each pairing ignores how other units will be or have been paired.
-This matching method may result in more ``imbalance, model dependence, and bias'' on highly balanced data (King \& Nielsen, 2019).
-
-I conducted matching with all the covariates used in the adjusted DID model.
+Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred (Greifer, 2022).
+King and Nelson (2019) argue against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
+
+I adopted the \texttt{MatchIt} package to perform matching with all the covariates of the adjusted DID model (Ho et al., 2022).
 I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
@@
 The matching ratio was set at one treatment unit with up to three control units.
-
-Alike are the results with matching and those without.
+The matching produced absolute standardized mean differences below 0.1 for all but a few covariates.
+
+Alike are the results from DID models with matching (DIDM) and those without.
 In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
-In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant in the any parent migrated households and only mother migrated households.
-The magnitudes of the coefficients are also similar.
+In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
+The significance level of any parent migration drops to ten percent.
+In all models, the magnitudes of the statistically significant coefficients are similar.
+I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
 
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
-\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\caption{Parental migration's effect on children's cognitive abilities, estimated with matching}\tabularnewline
 \toprule
@@
 
+\textbf{Note:}
+\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
+
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
-\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
 \toprule
@@
 
+\textbf{Note:}
+\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
+
+\newpage
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+This thesis proposed a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
+I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
+I further examined whether the effect varies across different arrangements of parental migration.
+Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
+In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
+
+My research has limitations in sample identification due to data constraint.
+First, the CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
+I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+It is possible that some parents are jailed or hospitalized.
+These types of absence would be wrongly attributed to migration.
+Second, the CEPS also lacks information on parents' migration history.
+Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left behind.
+Both limitations may lead to selection bias.
+
+Limitations also arise from unaccounted endogeneity and exogeneity.
+Endogenous factors may create selection bias.
+As Chen and coauthors (2009) stated: When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
+Exogenous factors may create omitted variable bias.
+Suppose that a natural hazard hit many counties of a province in the sample.
+This shock can simultaneously increase parents' out-migration and reduce students' grades (Chen et al., 2009).
+I could not account for such shocks as CEPS data does not include detailed geographic information.
+
+From my research, we can find future directions for scholarly inquiry.
+Researchers can improve my research design with new releases of CEPS data.
+A three-wave panel dataset will facilitate the examination of parallel trend assumption through multi-period DID models.
+Researchers can also examine how would left behind children respond when one or both of the migrant parents return home and settle down (Liang \& Li, 2021).
+In English-language publications, only one piece has explored return migrants and their stay-behind children in the Chinese context (Z.
+Liu et al., 2018).
+
+Let us consider the policy implications.
+The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
+A slight drop of educational performance may worsen with time.
+Besides, parental migration also affects left behind children's mental health and non-cognitive skills (Antia et al., 2020).
+These outcomes are also important for human development.
+Policymakers should reduce institutional barriers at destination cities so that the split migrant families can unify without concern.
+Meanwhile, schools should dedicate more advisory and counseling support to left-behind children.
+
+\newpage
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{figures}{%
+\subsection{Figures}\label{figures}}
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}Changes in standardized cognitive test score for newly left behind students and non-left-behind students}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\label{fig:unnamed-chunk-11}Changes in academic exam score for newly left behind students and non-left-behind students}
+\end{figure}
+
+\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ any\ parent\ migration"\}\ plot(summary(m.out),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
+
+\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ only\ mother\ migration"\}\ plot(summary(m.out\_mo\_only),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
+
+\begin{verbatim}
+```{fig.cap = "Sample balance before and after matching by only father migration"}
+plot(summary(m.out_fa_only), xlim = c(0, 0.55), position = 'right')
+\end{verbatim}
+
+\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ both\ parents\ migration"\}\ plot(summary(m.out\_both),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
+
+\hypertarget{tables}{%
+\subsection{Tables}\label{tables}}
+
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
 \toprule
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
 \toprule
@@
 \^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-\newpage
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Results show that parental migration is negatively associated with children's short-term cognitive and academic abilities.
+
+\textbf{Note:}
+\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
-
 \leavevmode\vadjust pre{\hypertarget{ref-bai2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
-Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. \url{https://cran.r-project.org/package=tinylabels}
-
-\leavevmode\vadjust pre{\hypertarget{ref-berguxe92018}{}}%
-Bergé, L. (2018). \emph{Efficient estimation of maximum likelihood models with multiple fixed-effects: the R package FENmlm}. \url{https://ideas.repec.org/p/luc/wpaper/18-13.html}
+\leavevmode\vadjust pre{\hypertarget{ref-berge2022}{}}%
+Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-debrauw2019}{}}%
+Brauw, A.
+de.
+(2019).
+Migration Out of Rural Areas and Implications for Rural Livelihoods.
+\emph{Annual Review of Resource Economics}, \emph{11}(1), 461--481.
+\url{https://doi.org/10.1146/annurev-resource-100518-093906}
+
 \leavevmode\vadjust pre{\hypertarget{ref-debrauw2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chan2017}{}}%
+Chan, J., \& Selden, M. (2017). The labour politics of china{'}s rural migrant workers. \emph{Globalizations}, \emph{14}(2), 259--271. \url{https://doi.org/10.1080/14747731.2016.1200263}
+
 \leavevmode\vadjust pre{\hypertarget{ref-chang2019}{}}%
@@
 \url{https://doi.org/10.1016/j.chieco.2019.01.007}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2009}{}}%
+Chen, X., Huang, Q., Rozelle, S., Shi, Y., \& Zhang, L.
+(2009).
+Effect of Migration on Children's Educational Performance in Rural China.
+\emph{Comparative Economic Studies}, \emph{51}(3), 323--343.
+\url{https://doi.org/10.1057/ces.2008.44}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-duckett2020}{}}%
+Duckett, J. (2020). Neoliberalism, Authoritarian Politics and Social Policy in China. \emph{Development and Change}, \emph{51}(2), 523--539. \url{https://doi.org/10.1111/dech.12568}
+
 \leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
 Goldin, C. (2016). \emph{Human Capital} (C. Diebolt \& M. Haupert, Eds.; pp. 55--86). Springer. \url{https://doi.org/10.1007/978-3-642-40406-1_23}
+
+\leavevmode\vadjust pre{\hypertarget{ref-greifer2022}{}}%
+Greifer, N. (2022). \emph{Matching methods}. \url{https://kosukeimai.github.io/MatchIt/articles/matching-methods.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-guo2021}{}}%
-Guo, S., Li, L., Sun, Y., Houang, R., \& Schmidt, W.
-H.
-(2021).
-Does boarding benefit the mathematics achievement of primary and middle school students?
-Evidence from china.
-\emph{Asia Pacific Journal of Education}, \emph{41}(1), 16--38.
-\url{https://doi.org/10.1080/02188791.2020.1760081}
+\leavevmode\vadjust pre{\hypertarget{ref-ho2022}{}}%
+Ho, D., Imai, K., King, G., Stuart, E., Whitworth, A., \& Greifer, N.
+(2022).
+\emph{MatchIt: Nonparametric preprocessing for parametric causal inference}.
+\url{https://CRAN.R-project.org/package=MatchIt}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-liang2021}{}}%
+Liang, Z., \& Li, W.
+(2021).
+Migration and children in China: a review and future research agenda.
+\emph{Chinese Sociological Review}, \emph{53}(3), 312--331.
+\url{https://doi.org/10.1080/21620555.2021.1908823}
+
 \leavevmode\vadjust pre{\hypertarget{ref-liu2021}{}}%
@@
 \url{https://doi.org/10.1007/s11482-021-09990-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2018}{}}%
+Liu, Z., Yu, L., \& Zheng, X.
+(2018).
+No longer left-behind: The impact of return migrant parents on children's performance.
+\emph{China Economic Review}, \emph{49}, 184--196.
+\url{https://doi.org/10.1016/j.chieco.2017.06.004}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-shu2021}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
-Zhan, Y.
-(2020).
-The moralization of philanthropy in China: NGOs, voluntarism, and the reconfiguration of social responsibility.
-\emph{China Information}, \emph{34}(1), 68--87.
-\url{https://doi.org/10.1177/0920203X19879593}
+\leavevmode\vadjust pre{\hypertarget{ref-zhang2018}{}}%
+Zhang, C.
+(2018).
+Governing neoliberal authoritarian citizenship: Theorizing hukou and the changing mobility regime in china.
+\emph{Citizenship Studies}, \emph{22}(8), 855--881.
+\url{https://doi.org/10.1080/13621025.2018.1531824}
 

### 2022-06-23 data/Gu-thesis-script.Rmd
First draft

@@
 library(ggplot2)
-library(gtsummary)
+#library(gtsummary)
 #library(DescTools)
+#knitr::opts_chunk$set(modelsummary_get="broom")
 ```
@@
 d_dpvar <- d_migr %>%
-  select(migr, 
+  select(#migr, 
          cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) %>%
@@
   )
+table_dependent_variable
 ```
@@
     output = 'markdown')
-
+table_independent_variable
 ```
@@
 fig_cog <- 
-  ggplot(d_migr, aes(x='Parental Migration Type', y=cog_dif, fill = `Parental Migration`)) + 
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    geom_boxplot(alpha=0.2)
+  ggplot(d_migr, aes(x=`Parental Migration`, y=cog_dif, fill = `Parental Migration`)) + 
+    geom_violin()+
+    xlab('Parental Migration') +
+    theme(legend.position="none") +
+    ylab("")
+fig_cog
 ```
@@
 fig_ttl <- 
-ggplot(d_migr, aes(x='Parental Migration Type', y=ttl_dif, fill = `Parental Migration`)) + 
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    geom_boxplot(alpha=0.2)
+  ggplot(d_migr, aes(x=`Parental Migration`, y=ttl_dif, fill = `Parental Migration`)) + 
+    geom_violin()+
+    xlab('Parental Migration') +
+    theme(legend.position="none") +
+    ylab("")
+fig_ttl
 ```
@@
 fig_cog_by_migration_type <-
-  ggplot(d_migr, aes(x='Parental Migration Type', y=cog_dif, fill = `Parental Migration Type`)) + 
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    geom_boxplot(alpha=0.2)
-
+  ggplot(d_migr, aes(x=`Parental Migration Type`, y=cog_dif, fill = `Parental Migration Type`)) + 
+    geom_violin()+
+    xlab('Parental Migration Type') +
+    theme(legend.position="none") +
+    ylab("")
+fig_cog_by_migration_type
 ```
@@
 fig_ttl_by_migration_type <-
-  ggplot(d_migr, aes(x='Parental Migration Type', y=ttl_dif, fill = `Parental Migration Type`)) + 
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    geom_boxplot(alpha=0.2)
+  ggplot(d_migr, aes(x=`Parental Migration Type`, y=ttl_dif, fill = `Parental Migration Type`)) + 
+    geom_violin()+
+    xlab('Parental Migration Type') +
+    theme(legend.position="none") +
+    ylab("")
+fig_ttl_by_migration_type
 ```
@@
 ```{r}
+stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
+coef_rename <- c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score", "w1ttl_100" = "W1 score")
+title_cog <- 'Parental migration’s effect on children’s cognitive abilities'
+title_ttl <- 'Parental migration’s effect on children’s academic abilities'
+gof_omit <- 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
+```
+
+```{r}
 table_cog <- models_cog %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+  stars =  stars,
   fmt = 2,
-  title = 'Parental migration’s effect on children’s cognitive abilities',
-  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+  title = title_cog,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
   output = 'markdown')
@@
 table_ttl <- models_ttl %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
-  title = 'Parental migration’s effect on children’s academic abilities',
+  stars =  stars,
   fmt = 2,
-  coef_rename = c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
-  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+  title = title_ttl,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
   output = 'markdown')
@@
 table_adj_cog <- models_adj_cog %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           title = 'Parental migration’s effect on children’s cognitive abilities',
+  stars =  stars,
   fmt = 2,
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
-  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
+  title = title_ttl,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
   output = 'markdown'
@@
 table_adj_ttl <- models_adj_ttl %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
-  title = 'Parental migration’s effect on children’s academic abilities',
+  stars =  stars,
   fmt = 2,
-  gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"), output = 'markdown')
+  title = title_ttl,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  output = 'markdown'
+  )
 table_adj_ttl
@@
   )
-summary(m.out) %>% plot()
+fig_msmd_any <- summary(m.out) %>% plot(xlim = c(0, 0.55), position = 'right')
 ```
@@
   )
-summary(m.out_mo_only) %>% plot()
+fig_msmd_mo_only <- summary(m.out_mo_only) %>% plot(xlim = c(0, 0.55), position = 'right')
 ```
@@
   )
-summary(m.out_fa_only) %>% plot()
+fig_msmd_fa_only <- summary(m.out_fa_only) %>% plot(xlim = c(0, 0.55), position = 'right')
 ```
@@
   )
-summary(m.out_both) %>% plot()
+fig_msmd_both <- plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
 ```
@@
 ```{r}
+title_cog_matching <- 'Parental migration’s effect on children’s cognitive abilities, estimated with matching'
+title_ttl_matching <- 'Parental migration’s effect on children’s academic abilities, estimated with matching'
+note_matching <- "3:1 nearest neighbor propensity score matching with replacement; exact matching by county"
+```
+
+```{r}
 models_m_cog <- list(
@@
 'Both Parents Absent' = didm_cog_both) 
+```
+
+```{r}
 table_m_cog <- models_m_cog %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           title = 'Parental migration’s effect on children’s cognitive abilities',
+  stars =  stars,
   fmt = 2,
-           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+  title = title_cog_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
   output = 'markdown'
@@
 table_m_ttl <- models_m_ttl %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           title = 'Parental migration’s effect on children’s academic abilities',
+  stars =  stars,
   fmt = 2,
-           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
+  title = title_ttl_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
   output = 'markdown'
@@
 table_m_adj_cog <- models_m_adj_cog %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           title = 'Parental migration’s effect on children’s cognitive abilities',
+  stars =  stars,
   fmt = 2,
-           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"),
+  title = title_ttl_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
   output = 'markdown'
@@
 table_m_adj_ttl <- models_m_adj_ttl %>% msummary(
-  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           title = 'Parental migration’s effect on children’s academic abilities',
+  stars =  stars,
   fmt = 2,
-           gof_omit = 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors',
-           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"),
+  title = title_ttl_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
   output = 'markdown'
@@
 d_cl1=d_cl1 %>% mutate(
-  supervision.less = if_else(b2201 > w2a18 & b2202 > w2a19, 1, 0)
+  supervision.less = if_else((b2201 + b2202) > (w2a18 + w2a19), 1, 0)
 )

### 2022-06-23 MScThesisText.Rmd
writing up

@@
 abstract: |
+  Millions of children worldwide are "left behind" when their parents migrate away for work. 
+  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance. 
+  To what extent do different arrangements of parental migration affect children's schooling performance in the short term? 
+  Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey. 
+  I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
+  I measured children's educational performance by standardized cognitive test score and academic exam grades.
+  For causal inference, I built difference-in-differences models with propensity score matching. 
+  Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers. 
+  Father-only migration is negatively associated with children’s cognitive abilities, while mother-only migration is negatively associated with children’s academic grades.
 
@@
 floatsintext      : yes
-linenumbers       : no
+linenumbers       : yes
 draft             : no
@@
 library("papaja")
+library("cobalt")
 r_refs("references.bib")
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work [@antia2020].
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
 These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children, [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
+Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
 
@@
 Consider children's education.
-According to the review articles by De Brauw [-@debrauw2019] and by Van Hook and Glick [-@vanhook2020], labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by @debrauw2019 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
@@
 
-A challenge arises in when we want to assess the causality between parental migration and children's education.
+A challenge arises when we want to assess the causality between parent's migration and children's educational achievement.
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
@@
 In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyze data from a two-wave panel survey.
+I chose China as the case and analyzed data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness check.
+I developed a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
 The outcome was measured with children's cognitive test score and academic exam scores.
@@
 Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
-[@yang2008] noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+@yang2008 noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
 This subsequently boosted children's school enrollment and educational expenditure.
-In China, [@chang2019] interviewed migrant workers and their family members.
+In China, @chang2019 interviewed migrant workers and their family members.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
@@
 The loss of nurturing care slows children's accumulation of human capital.
-Hong talked to a group of left behind children at a rural school [@hong2019].
+Hong talked to a group of left-behind children at a rural school [@hong2019].
 These students expressed the utter sense of loneliness "with no advocate, no support and with no one looking out for them" (p.
@@
 Researchers obtained mixed results regarding how parental migration affects children's education.
-Botezat and Pfeiffer [-@botezat2020] studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
-Wang and others [-@wang2019] collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, De Brauw and Giles [-@debrauw2017] showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-Nguyen [-@nguyen2016] demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
+@botezat2020 studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
+@wang2019 collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, @debrauw2017 showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+@nguyen2016 demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
 The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
@@
 Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
-It takes longer time for parental migration to generate resources that improve children's performance at school.
+It takes longer time for parental migration to generate resources that improve children's educational attainment.
 I propose the first hypothesis:
 
-$H_1$ In the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+$H_1$ In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
 
 Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
-Xu and others [-@xu2019] adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+@xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
 They found that the absence of father only or both parents had "little or no association with negative outcomes" on children's academic and cognitive performances.
@@
 1646).
-Chen and others [-@chen2019] conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+@chen2019 conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
 They found that mother migration was "negatively associated with children's social competence and academic performance," while father migration had no direct effects on the two outcomes (pp.
@@
 Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
-Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+Left-behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
 I propose the second hypothesis:
 
-$H_2$ In the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+$H_2$ In the short term, mother migration negatively affect the cognitive development and academic performance of children left-behind, while father migration does not show a effect.
 
@@
 
-Three features make China a suitable case for studying left behind children.
+Three features make China a suitable case for studying left-behind children.
 The first feature is the huge scale of internal labor migration.
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
-They form the backbone of essential industries, such as delivery, transportation, and manufacturing.
-The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+The number of left-behind Chinese children reached 68.7 million in 2015 [@nbs2017].
 The second feature is the neoliberal welfare regime.
@@
 The third is the authoritarian control against citizens.
-According to Gu [-@gu2021] and Zhang [-@zhang2018], the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+According to @gu2021 and @zhang2018, the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
 One can move out of town freely but cannot change hukou freely.
 For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiveing urban hukou, they enjoy limited access to public service in the host city, including public education for children.
+Before receiving urban hukou, they only enjoy limited access to public service in the host city, including public education for children.
+Migrant laborers had organized strikes and protests, only to meet with police crackdown [@chan2017].
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns [@gu2021; @zhang2018].
-Migrant laborers had attempted to strike or protest, only to meet with police crackdown [@chan2017].
 
-The existing research about China's left behind children has three major shortcomings that I aim to tackle.
+The existing research about China's left-behind children has three major shortcomings.
 The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-I included urban left behind children as well.
-The National Bureau of Statistics stated that the number of urban left behind children had been growing and expected that the trend would continue [@nbs2017].
-The second shortcoming lies in data and sampling.
-Some studies draw from cross-sectional data, making it hard to infer causal relations [@zhou2014; @jin2020].
-Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
-I adopted a nationally representative two-wave panel dataset.
-The third shortcoming lies in the measurement of outcome.
-[@chang2019; @wang2019] measured students' educational performance with the test score of only one academic subject, namely mathematics.
+The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
+My sample includes urban left-behind children as well.
+The second shortcoming lies in sampling and research design.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
+Others only estimate correlation using cross-sectional data [@akezhuoli2022; @jin2020].
+These studies could have applied causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+Others s The third shortcoming lies in the measurement of outcome.
+@chang2019 and @wang2019 measured students' educational performance with the test score of only one academic subject, namely mathematics.
+To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
 I included the test results of multiple subjects to measure comprehensive academic achievement.
@@
 
-## Participants
+## Sampling
 
@@
 The survey administrator is the National Survey Research Center at Renmin University of China.
-The research team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
+The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
 The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
@@
 
-Another dependent variables concerned students' academic performance.
+Another dependent variable concerned students' academic performance.
 This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
-These three subjects constitute the core parts in the senior high school entrance exam.
-Junior high school students study these subjects throughout three academic years.
+Throughout junior high school, students study these subjects, which are included in the entrance exam to senior high school.
 Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period.
@@
 After the conversion, I checked for abnormal values outside the 0-100 range.
-`r printnum(num.outlier$n)` observations are outliers, accounting for less than one percent of the sample.
-I trim the values of subject exam score with minimum of zero and maximum of one hundred.
+`r printnum(num.outlier$n)` observations were outliers, accounting for less than one percent of the sample.
+I trimed the values of subject exam score with minimum of zero and maximum of one hundred.
 In this way, I can limit the impact of outliers while retaining these observations in the sample.
@@
 
-I adopted `R` for all the analyses, the `fixest` package for building the econometric models [@berge2022], and the `modelsummary` package for presenting the results [@arel-bundock2022].
+I adopted `R` for all the analyses, the `fixest` package for econometric modeling [@berge2022], and the `modelsummary` package for presenting the results [@arel-bundock2022].
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $C_{j}$ and $C_{k}$ are respectively the classroom fixed-effects at baseline and follow-up, and $score_{i,j,k;1}$ is the test score at baseline.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $C_{j}$ and $C_{k}$ are respectively the classroom fixed-effects at baseline and follow-up, and $score_{i,j,k;1}$ is the test score at baseline.
+Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
+About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
+This necessitates adding the wave-two classroom fixed-effect.
+
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
@@
 
-In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 The tables below provide the whole-sample summary statistics.
-In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatmeng group and the control group.
+In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
 
@@
 
-The unrestricted DID models support my hypothesis one -- newly left behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left behind counterparts.
+The unrestricted DID models support my hypothesis one -- newly left-behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left-behind counterparts.
 If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
@@
 Children from only mother migrate households are associated with `r round(coef(did_cog_m_only)[1],2)` points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left behind children.
+The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
 Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left behind children.
-Children with only father absent are associated with (`r round(coef(did_cog_f_only)[1],2)` SD), and both parents absent (`r round(coef(did_cog_both)[1],2)` SD) compared to the non left behind children.
+Children with only mother migrated do not show statistically significant difference from the non left-behind children.
+Children with only father absent are associated with (`r round(coef(did_cog_f_only)[1],2)` SD), and both parents absent (`r round(coef(did_cog_both)[1],2)` SD) compared to the non left-behind children.
 
@@
 Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational asiration as well as parents' expectation on children.
+These are children's age and educational aspiration as well as parents' expectation on children.
 In terms of age, the older students' scores drop relatively more than younger students'.
 One year older in age is associated with `r round(coef(did_adj_cog)[3],2)` SD for standardized cognitive test and `r round(coef(did_adj_ttl)[3],2)` points for academic exams.
-Parent's expectation for children comleting university and children's own aspiration for finishing university are associated with higher scores.
+Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
 The effect sizes are `r round(coef(did_adj_cog)[15],2)` SD and `r round(coef(did_adj_cog)[12],2)` SD for standardized cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
@@
 
-Researchers noted that migrants represent a positively selected group compared to non-migrants [@vanhook2020], which may present systematic differences between left behind children and their non-left-behind peers.
+Parental migration is not a randomly assigned treatment.
 One technique to tackle this selection bias is matching.
@@
 Popular choices include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
-As Greifer [-@greifer2022] introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+As @greifer2022 introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
 The downside is that it leaves many units without an exact match and discards these unmatched units.
@@
 Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred [@greifer2022].
-King and Nelson [-@king2019] argue against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
+@king2019 argued against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
 
-I adopted the `MatchIt` package to perform matching with all the covariates of the adjusted DID model [@ho2022].
-I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
-Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others [-@bai2018].
+Using the `MatchIt` package [@ho2022], I performed matching with all the covariates of the adjusted DID model.
+I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
+I then made do with the PSM.
+I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of @bai2018.
 Exact matching based on county of residence preserves the original geographic distribution.
@@
 The matching ratio was set at one treatment unit with up to three control units.
-The matching produced absolute standardized mean differences below 0.1 for all but a few covariates.
+The matching produced absolute standardized mean differences below 0.1 for all but a few covariates, suggesting an improved overall balance.
 
@@
 Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
+In all scenarios, the educational performance of newly left-behind children only decreased slightly compared to that of non-left-behind peers.
 
-My research has limitations in sample identification due to data constraint.
-First, the CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
-I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
-It is possible that some parents are jailed or hospitalized.
+My research has limitations in sampling due to data constraint.
+Regarding sample size, the treatment group for the both-parents migration is small, lowering the statistical power.
+Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
+It is possible that some parents were jailed or hospitalized.
 These types of absence would be wrongly attributed to migration.
-Second, the CEPS also lacks information on parents' migration history.
+Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
 Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left behind.
-Both limitations may lead to selection bias.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind.
+These limitations may bias the estimation.
 
 Limitations also arise from unaccounted endogeneity and exogeneity.
-Endogenous factors may create selection bias.
-As Chen and coauthors [-@chen2009] stated: When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+As @chen2009 stated in their research on left-behind children, endogenous factors may create selection bias.
+When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
 Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
+Parental beliefs of this sort are unavailable in CEPS data.
 Exogenous factors may create omitted variable bias.
 Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce students' grades [@chen2009].
+This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades [@chen2009].
 I could not account for such shocks as CEPS data does not include detailed geographic information.
 
-From my research, we can find future directions for scholarly inquiry.
-Researchers can improve my research design with new releases of CEPS data.
-A three-wave panel dataset will facilitate the examination of parallel trend assumption through multi-period DID models.
-Researchers can also examine how would left behind children respond when one or both of the migrant parents return home and settle down [@liang2021].
-In English-language publications, only one piece has explored return migrants and their stay-behind children in the Chinese context [@liu2018].
+From my research, we can find new directions for scholarly inquiry.
+First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
+This would facilitate examination of the parallel trend assumption.
+Second, researchers can try novel methods.
+Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
+Synthetic control can evaluate the aggregate outcome of "large-scale but infrequent interventions" at municipal or provincial levels [@abadie2021], such as the policy experimentations that liberalize the hukou system in certain cities [@wang2020].
+Third, researchers can go beyond outbound migration to study return migration of parents [@liang2021].
+Only a few publications, such as that of @liu2018, have explored return migrants and their stay-behind children in the Chinese context.
 
-Let us consider the policy implications.
+Let us consider the policy implications for China.
 The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
-A slight drop of educational performance may worsen with time.
-Besides, parental migration also affects left behind children's mental health and non-cognitive skills [@antia2020].
-These outcomes are also important for human development.
-Policymakers should reduce institutional barriers at destination cities so that the split migrant families can unify without concern.
-Meanwhile, schools should dedicate more advisory and counseling support to left-behind children.
+The slight reduction is only the short-term consequence.
+Longer duration of parental migration may hamper educational performance to a greater extent.
+Besides, educational performance is only part of human development outcomes [@antia2020].
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence.
+Policymakers should reduce institutional barriers at destination cities, opening more doors for parents to migrate together with their children.
+Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
 
@@
 
-## Figures
-
-```{r, fig.cap = "Changes in standardized cognitive test score for newly left behind students and non-left-behind students"}
+```{r, fig.cap = "Changes in standardized cognitive test score for newly left-behind students and non-left-behind students"}
 fig_cog
@@
 
-```{r, fig.cap = "Changes in academic exam score for newly left behind students and non-left-behind students"}
+\newpage
+
+```{r, fig.cap = "Changes in academic exam score for newly left-behind students and non-left-behind students"}
 fig_ttl
@@
 
-```{fig.cap = "Sample balance before and after matching by any parent migration"}
-plot(summary(m.out), xlim = c(0, 0.55), position = 'right')
+\newpage
+
+```{r, fig.cap = "Changes in standardized cognitive test score by household migration arrangement"}
+fig_cog_by_migration_type
 ```
 
-```{fig.cap = "Sample balance before and after matching by only mother migration"}
-plot(summary(m.out_mo_only), xlim = c(0, 0.55), position = 'right')```
+\newpage
+
+```{r, fig.cap = "Changes in academic exam score by household migration type"}
+fig_ttl_by_migration_type
 ```
 
-```{fig.cap = "Sample balance before and after matching by only father migration"}
-plot(summary(m.out_fa_only), xlim = c(0, 0.55), position = 'right')
-```
-
-```{fig.cap = "Sample balance before and after matching by both parents migration"}
-plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
-```
-
-## Tables
+\newpage
 
@@
 ```
+
+\newpage
 

### 2022-06-23 MScThesisText.tex
writing up

@@
 \keywords{keywords\newline\indent Word count: X}
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
@@
 
+\abstract{%
+Millions of children worldwide are ``left behind'' when their parents migrate away for work.
+Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance.
+To what extent do different arrangements of parental migration affect children's schooling performance in the short term?
+Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey.
+I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
+I measured children's educational performance by standardized cognitive test score and academic exam grades.
+For causal inference, I built difference-in-differences models with propensity score matching.
+Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers.
+Father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic grades.
+}
+
 \begin{document}
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020).
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
 These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children, (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
+Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
 
@@
 Consider children's education.
-According to the review articles by De Brauw (2019) and by Van Hook and Glick (2020), labor migrants send remittances back home, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by Brauw (2019) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
@@
 Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
-(D.
-Yang, 2008) noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+D.
+Yang (2008) noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
 This subsequently boosted children's school enrollment and educational expenditure.
-In China, (Chang et al., 2019) interviewed migrant workers and their family members.
+In China, Chang et al.
+(2019) interviewed migrant workers and their family members.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
@@
 The loss of nurturing care slows children's accumulation of human capital.
-Hong talked to a group of left behind children at a rural school (Hong \& Fuller, 2019).
+Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
 These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
@@
 Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
-Wang and others (2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, De Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+L.
+Wang et al.
+(2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Studying four Chinese provinces, Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
 Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
@@
 Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
-It takes longer time for parental migration to generate resources that improve children's performance at school.
+It takes longer time for parental migration to generate resources that improve children's educational attainment.
 I propose the first hypothesis:
 
-\(H_1\) In the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+\(H_1\) In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
 
 Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
-Xu and others (2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+Y.
+Xu et al.
+(2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
 They found that the absence of father only or both parents had ``little or no association with negative outcomes'' on children's academic and cognitive performances.
 Only-mother absence, however, showed a ``strong association with negative outcomes'' (p.~1646).
-Chen and others (2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+Chen et al.
+(2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
 They found that mother migration was ``negatively associated with children's social competence and academic performance,'' while father migration had no direct effects on the two outcomes (pp.~860-861).
@@
 Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
-Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+Left-behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
 I propose the second hypothesis:
 
-\(H_2\) In the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+\(H_2\) In the short term, mother migration negatively affect the cognitive development and academic performance of children left-behind, while father migration does not show a effect.
 
@@
 
-Three features make China a suitable case for studying left behind children.
+Three features make China a suitable case for studying left-behind children.
 The first feature is the huge scale of internal labor migration.
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
-They form the backbone of essential industries, such as delivery, transportation, and manufacturing.
-The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+The number of left-behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
 The second feature is the neoliberal welfare regime.
@@
 For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiveing urban hukou, they enjoy limited access to public service in the host city, including public education for children.
+Before receiving urban hukou, they only enjoy limited access to public service in the host city, including public education for children.
+Migrant laborers had organized strikes and protests, only to meet with police crackdown (Chan \& Selden, 2017).
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns (Gu, 2021; Zhang, 2018).
-Migrant laborers had attempted to strike or protest, only to meet with police crackdown (Chan \& Selden, 2017).
-
-The existing research about China's left behind children has three major shortcomings that I aim to tackle.
+
+The existing research about China's left-behind children has three major shortcomings.
 The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-I included urban left behind children as well.
-The National Bureau of Statistics stated that the number of urban left behind children had been growing and expected that the trend would continue (NBS et al., 2017).
-The second shortcoming lies in data and sampling.
-Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014).
-Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Y.
+The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
+My sample includes urban left-behind children as well.
+The second shortcoming lies in sampling and research design.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Jin et al., 2020; Y.
 Liu et al., 2021; Shu, 2021; F.
 Yang et al., 2022).
-I adopted a nationally representative two-wave panel dataset.
-The third shortcoming lies in the measurement of outcome.
-(Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
+Others only estimate correlation using cross-sectional data (Akezhuoli et al., 2022; Jin et al., 2020).
+These studies could have applied causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+Others s The third shortcoming lies in the measurement of outcome.
+Chang et al.
+(2019) and L.
+Wang et al.
+(2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
+To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
 I included the test results of multiple subjects to measure comprehensive academic achievement.
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\hypertarget{sampling}{%
+\subsection{Sampling}\label{sampling}}
 
@@
 After the conversion, I checked for abnormal values outside the 0-100 range.
-31 observations are outliers, accounting for less than one percent of the sample.
-I trim the values of subject exam score with minimum of zero and maximum of one hundred.
+31 observations were outliers, accounting for less than one percent of the sample.
+I trimed the values of subject exam score with minimum of zero and maximum of one hundred.
 In this way, I can limit the impact of outliers while retaining these observations in the sample.
@@
 
-I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for building the econometric models (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for econometric modeling (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{j}\) and \(C_{k}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j,k;1}\) is the test score at baseline.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{j}\) and \(C_{k}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j,k;1}\) is the test score at baseline.
+Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
+About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
+This necessitates adding the wave-two classroom fixed-effect.
+
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
@@
 
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{i} + \lambda \cdot C_{j} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 Children from only mother migrate households are associated with -0.04 points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left behind children.
+The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
 Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left behind children.
-Children with only father absent are associated with (-0.14 SD), and both parents absent (-0.10 SD) compared to the non left behind children.
+Children with only mother migrated do not show statistically significant difference from the non left-behind children.
+Children with only father absent are associated with (-0.14 SD), and both parents absent (-0.10 SD) compared to the non left-behind children.
 
@@
 Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational asiration as well as parents' expectation on children.
+These are children's age and educational aspiration as well as parents' expectation on children.
 In terms of age, the older students' scores drop relatively more than younger students'.
 One year older in age is associated with -0.07 SD for standardized cognitive test and -1.23 points for academic exams.
-Parent's expectation for children comleting university and children's own aspiration for finishing university are associated with higher scores.
+Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
 The effect sizes are 0.01 SD and 0.07 SD for standardized cognitive test, respectively; and 0.29 points and 1.82 points for academic exams, respectively.
@@
 
-Researchers noted that migrants represent a positively selected group compared to non-migrants (Van Hook \& Glick, 2020), which may present systematic differences between left behind children and their non-left-behind peers.
+Parental migration is not a randomly assigned treatment.
 One technique to tackle this selection bias is matching.
@@
 Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred (Greifer, 2022).
-King and Nelson (2019) argue against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
-
-I adopted the \texttt{MatchIt} package to perform matching with all the covariates of the adjusted DID model (Ho et al., 2022).
-I first attempted CEM, which left most units unmatched and resulted in a tiny sample.
-Then I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates), which is the configuration of Bai and others (2018).
+King and Nielsen (2019) argued against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
+
+Using the \texttt{MatchIt} package (Ho et al., 2022), I performed matching with all the covariates of the adjusted DID model.
+I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
+I then made do with the PSM.
+I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of Bai et al.
+(2018).
 Exact matching based on county of residence preserves the original geographic distribution.
@@
 Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left behind children only decreased slightly compared to that of non-left-behind peers.
-
-My research has limitations in sample identification due to data constraint.
-First, the CEPS questionnaire asks if parents live in the household, but does not ask why parents are absent.
-I can only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
-It is possible that some parents are jailed or hospitalized.
+In all scenarios, the educational performance of newly left-behind children only decreased slightly compared to that of non-left-behind peers.
+
+My research has limitations in sampling due to data constraint.
+Regarding sample size, the treatment group for the both-parents migration is small, lowering the statistical power.
+Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
+It is possible that some parents were jailed or hospitalized.
 These types of absence would be wrongly attributed to migration.
-Second, the CEPS also lacks information on parents' migration history.
+Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
 Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left behind.
-Both limitations may lead to selection bias.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind.
+These limitations may bias the estimation.
 
 Limitations also arise from unaccounted endogeneity and exogeneity.
-Endogenous factors may create selection bias.
-As Chen and coauthors (2009) stated: When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+As Chen et al.
+(2009) stated in their research on left-behind children, endogenous factors may create selection bias.
+When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
 Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
+Parental beliefs of this sort are unavailable in CEPS data.
 Exogenous factors may create omitted variable bias.
 Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce students' grades (Chen et al., 2009).
+This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades (Chen et al., 2009).
 I could not account for such shocks as CEPS data does not include detailed geographic information.
 
-From my research, we can find future directions for scholarly inquiry.
-Researchers can improve my research design with new releases of CEPS data.
-A three-wave panel dataset will facilitate the examination of parallel trend assumption through multi-period DID models.
-Researchers can also examine how would left behind children respond when one or both of the migrant parents return home and settle down (Liang \& Li, 2021).
-In English-language publications, only one piece has explored return migrants and their stay-behind children in the Chinese context (Z.
-Liu et al., 2018).
-
-Let us consider the policy implications.
+From my research, we can find new directions for scholarly inquiry.
+First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
+This would facilitate examination of the parallel trend assumption.
+Second, researchers can try novel methods.
+Machine learning, for example, can estimate the heterogeneous effects across subgroups (R.
+Liu, 2021).
+Synthetic control can evaluate the aggregate outcome of ``large-scale but infrequent interventions'' at municipal or provincial levels (Abadie, 2021), such as the policy experimentations that liberalize the hukou system in certain cities (X.
+Wang, 2020).
+Third, researchers can go beyond outbound migration to study return migration of parents (Liang \& Li, 2021).
+Only a few publications, such as that of Z.
+Liu et al.
+(2018), have explored return migrants and their stay-behind children in the Chinese context.
+
+Let us consider the policy implications for China.
 The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
-A slight drop of educational performance may worsen with time.
-Besides, parental migration also affects left behind children's mental health and non-cognitive skills (Antia et al., 2020).
-These outcomes are also important for human development.
-Policymakers should reduce institutional barriers at destination cities so that the split migrant families can unify without concern.
-Meanwhile, schools should dedicate more advisory and counseling support to left-behind children.
+The slight reduction is only the short-term consequence.
+Longer duration of parental migration may hamper educational performance to a greater extent.
+Besides, educational performance is only part of human development outcomes (Antia et al., 2020).
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence.
+Policymakers should reduce institutional barriers at destination cities, opening more doors for parents to migrate together with their children.
+Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
 
@@
 \section{Appendix}\label{appendix}}
-
-\hypertarget{figures}{%
-\subsection{Figures}\label{figures}}
 
@@
 \includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}Changes in standardized cognitive test score for newly left behind students and non-left-behind students}
+\caption{\label{fig:unnamed-chunk-10}Changes in standardized cognitive test score for newly left-behind students and non-left-behind students}
 \end{figure}
+
+\newpage
 
@@
 \includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}Changes in academic exam score for newly left behind students and non-left-behind students}
+\caption{\label{fig:unnamed-chunk-11}Changes in academic exam score for newly left-behind students and non-left-behind students}
 \end{figure}
 
-\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ any\ parent\ migration"\}\ plot(summary(m.out),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
-
-\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ only\ mother\ migration"\}\ plot(summary(m.out\_mo\_only),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
-
-\begin{verbatim}
-```{fig.cap = "Sample balance before and after matching by only father migration"}
-plot(summary(m.out_fa_only), xlim = c(0, 0.55), position = 'right')
-\end{verbatim}
-
-\texttt{\{fig.cap\ =\ "Sample\ balance\ before\ and\ after\ matching\ by\ both\ parents\ migration"\}\ plot(summary(m.out\_both),\ xlim\ =\ c(0,\ 0.55),\ position\ =\ \textquotesingle{}right\textquotesingle{})}
-
-\hypertarget{tables}{%
-\subsection{Tables}\label{tables}}
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\label{fig:unnamed-chunk-12}Changes in standardized cognitive test score by household migration arrangement}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\label{fig:unnamed-chunk-13}Changes in academic exam score by household migration type}
+\end{figure}
+
+\newpage
 
@@
 
+\newpage
+
 \begin{longtable}[]{@{}
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abadie2021}{}}%
+Abadie, A.
+(2021).
+Using Synthetic Controls: Feasibility, Data Requirements, and Methodological Aspects.
+\emph{Journal of Economic Literature}, \emph{59}(2), 391--425.
+\url{https://doi.org/10.1257/jel.20191450}
+
+\leavevmode\vadjust pre{\hypertarget{ref-akezhuoli2022}{}}%
+Akezhuoli, H., Lu, J., Zhao, G., Xu, J., Wang, M., Wang, F., Li, L., \& Zhou, X.
+(2022).
+Mother's and father's migrating in china: Differing relations to mental health and risk behaviors among left-behind children.
+\emph{Frontiers in Public Health}, \emph{10}.
+\url{https://www.frontiersin.org/article/10.3389/fpubh.2022.894741}
+
 \leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-liu2021a}{}}%
+Liu, R.
+(2021).
+Leveraging machine learning methods to estimate heterogeneous effects: Father absence in china as an example.
+\emph{Chinese Sociological Review}, \emph{0}(0), 1--29.
+\url{https://doi.org/10.1080/21620555.2021.1948828}
+
 \leavevmode\vadjust pre{\hypertarget{ref-liu2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
+Wang, X.
+(2020).
+Permits, Points, and Permanent Household Registration: Recalibrating Hukou Policy under {``}Top-Level Design{''}.
+\emph{Journal of Current Chinese Affairs}, \emph{49}(3), 269--290.
+\url{https://doi.org/10.1177/1868102619894739}
+
 \leavevmode\vadjust pre{\hypertarget{ref-xu2015}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhou2014}{}}%
-Zhou, M., Murphy, R., \& Tao, R.
-(2014).
-Effects of Parents' Migration on the Education of Children Left Behind in Rural China.
-\emph{Population and Development Review}, \emph{40}(2), 273--292.
-\url{https://doi.org/10.1111/j.1728-4457.2014.00673.x}
-
 \end{CSLReferences}

### 2022-06-23 data/Gu-thesis-script.Rmd
writing up

@@
 library(ggplot2)
+library(cobalt) 
 #library(gtsummary)
@@
   )
-fig_msmd_any <- summary(m.out) %>% plot(xlim = c(0, 0.55), position = 'right')
+```
+
+```{r}
+sum_m.out <- summary(m.out)
+fig_msmd_any <- plot(sum_m.out, xlim = c(0, 0.55), position = 'right')
+```
+
+```{r}
+love.plot(
+  m.out,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 0.55),
+  )
 ```
@@
   )
-fig_msmd_mo_only <- summary(m.out_mo_only) %>% plot(xlim = c(0, 0.55), position = 'right')
+```
+
+```{r}
+sum_m.out_fa_only <- summary(m.out_fa_only)
+fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
+```
+
+```{r}
+love.plot(
+  m.out_mo_only,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 1.5),
+  )
 ```
@@
   )
-fig_msmd_fa_only <- summary(m.out_fa_only) %>% plot(xlim = c(0, 0.55), position = 'right')
+sum_m.out_fa_only <- summary(m.out_fa_only)
+fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
+```
+```{r}
+love.plot(
+  m.out_fa_only,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 0.55),
+  )
 ```
@@
   )
-fig_msmd_both <- plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+```
+
+```{r}
+ #plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+love.plot(
+  m.out_both,
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+love.plot(
+  m.out_both,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 0.55),
+  abs = T
+  )
+
 ```

### 2022-06-25 MScThesisText.Rmd
write up main text, put more visuals in appendix

@@
 ---
-title             : "Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
+title             : "Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
 shorttitle        : "Left-Behind Children"
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
 These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
 Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
+In a 2021 resolution, the Council of Europe's @parliamentaryassembly2021a expressed concern about "the scale of this phenomenon and the long-term damage it creates" (p.
+2) and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights" (p.
+1).
 
 How are stay-behind children faring when parents have migrated?
-Scholars have obtained mixed results due to the differential effects of parental migration.
+Research results are mixed due to the differential effects of parental migration.
 Consider children's education.
@@
 
-A challenge arises when we want to assess the causality between parent's migration and children's educational achievement.
+A challenge arises in assessing the causality between parent's migration and children's educational achievement.
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
+Alternatively, a quasi-experimental design can help with causal inference.
+The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
 
-In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
-I chose China as the case and analyzed data from a two-wave panel survey.
+In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
+I choose China as the case and analyzed data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I developed a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
+I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
 The outcome was measured with children's cognitive test score and academic exam scores.
@@
 This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
-Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
-The loss of nurturing care slows children's accumulation of human capital.
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@wen2019].
 Hong talked to a group of left-behind children at a rural school [@hong2019].
@@
 13).
-Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.
+Many of them felt indifferent to grades and disengaged with school.
+Some even longed to quit school to pursue a free, independent life (p.
 14).
 
-Researchers obtained mixed results regarding how parental migration affects children's education.
+Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
 @botezat2020 studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
@@
 @nguyen2016 demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
 
@@
 
-Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
 @xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
@@
 
-In China, the social norms designate men as breadwinners and women as caregivers.
-Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
-Left-behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Under such norms, children are more likely to accept fathers' migration than mothers' [@murphy2022].
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
 I propose the second hypothesis:
 
-$H_2$ In the short term, mother migration negatively affect the cognitive development and academic performance of children left-behind, while father migration does not show a effect.
+$H_2$ In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
 
@@
 The number of left-behind Chinese children reached 68.7 million in 2015 [@nbs2017].
-The second feature is the neoliberal welfare regime.
-Neoliberalism extends the logic of the market to most spheres of human life.
-Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
-Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families [@duckett2020].
-The third is the authoritarian control against citizens.
-According to @gu2021 and @zhang2018, the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
-One can move out of town freely but cannot change hukou freely.
-For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they only enjoy limited access to public service in the host city, including public education for children.
-Migrant laborers had organized strikes and protests, only to meet with police crackdown [@chan2017].
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns [@gu2021; @zhang2018].
+The internal migration stemmed from the neoliberal economic regime.
+
+The neoliberal economic regime sounds at odds with China, a so-called socialist country.
+Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
+Since then, China has integrated in the global economy and contributed substantial growth to it.
+The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
+The rural hinterlands, however, have lagged behind.
+The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
+Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
+As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
+The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere [@duckett2020; @zhang2018].
+
+The institutionalized discrimination against migrant laborers find its roots in China's "multilevel citizenship" system.
+As @vortherms2021 demonstrated, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through the *hukou*, or household registration system:
+
+> A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
+Accessing fundamental citizenship rights depends on your registration status ...
+Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
+[@vortherms2021]
+
+In other words, the hukou system binds one's citizenship rights with one's place of registry.
+In theory, anyone can move out of town freely.
+In practice, they cannot change hukou freely.
+When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2021].
+Migrant workers had organized petitions, strikes, and protests, only to fall on deaf ears or even end with police crackdown [@chan2017].
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
 
@@
 The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
-Others only estimate correlation using cross-sectional data [@akezhuoli2022; @jin2020].
-These studies could have applied causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-Others s The third shortcoming lies in the measurement of outcome.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021].
+Others only estimated correlation using cross-sectional data [@akezhuoli2022; @jin2020].
+These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+The third shortcoming lies in the measurement of outcome.
 @chang2019 and @wang2019 measured students' educational performance with the test score of only one academic subject, namely mathematics.
@@
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
+The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one [@wang2015].
 
@@
 This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
-Throughout junior high school, students study these subjects, which are included in the entrance exam to senior high school.
-Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period.
-Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort.
-I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
+This is related to how junior high schools operate as part of the compulsory education system in China.
+According to @oecd2016, China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
+At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
+Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
+Within each cohort in one particular school, teachers use the same syllabus and administer the same exams during a given assessment period.
+Across cities and regions, junior high schools adopt the educational content and assessment set by the Ministry of Education [@oecd2016].
+
+I transformed the exam grades through the following steps.
+I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
 After the conversion, I checked for abnormal values outside the 0-100 range.
 `r printnum(num.outlier$n)` observations were outliers, accounting for less than one percent of the sample.
-I trimed the values of subject exam score with minimum of zero and maximum of one hundred.
+I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
 In this way, I can limit the impact of outliers while retaining these observations in the sample.
@@
 
+The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
+
 ## Data analysis
@@
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $C_{j}$ and $C_{k}$ are respectively the classroom fixed-effects at baseline and follow-up, and $score_{i,j,k;1}$ is the test score at baseline.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j,k;1}$ is the test score at baseline, and $C_{j}$ and $C_{k}$ are the classroom fixed-effects at baseline and follow-up, respectively.
 Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
@@
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein].
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
 The standard errors were clustered at the classroom level.
 
-In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
-The table below summarizes the changes in migration status in the sample.
+Table 1 below summarizes the changes in migration status in the sample.
 All `r printnum(nrow(d_cl))` children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
@@
 
-```{r}
+```{r i-var}
 table_independent_variable
@@
 
-The tables below provide the whole-sample summary statistics.
+Tables 2 and 3 below provide the whole-sample summary statistics.
 In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
 
-```{r}
+```{r d-var}
 table_dependent_variable
@@
 
-```{r}
+```{r c-var}
 table_control_variable
@@
 If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to is `r round(coef(did_cog)[1],2)` SD in cognitive test score and `r round(coef(did_cog)[1],2)` points in academic exam grades.
+Parental migration is linked to `r round(coef(did_cog)[1],2)` SD in cognitive test score and `r round(coef(did_cog)[1],2)` points in academic exam grades.
 Both relationships are slight in strength.
@@
 
-```{r}
+```{r reg-cog}
 table_cog
@@
 
-```{r}
+```{r reg-ttl}
 table_ttl
@@
 
-```{r}
+```{r reg-cog-adj}
 table_adj_cog
@@
 
-```{r}
+```{r reg-ttl-adj}
 table_adj_ttl
@@
 Parental migration is not a randomly assigned treatment.
-One technique to tackle this selection bias is matching.
-This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-Popular choices include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
+A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
+Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
+To tackle the selection bias herein, an applicable technique is matching.
+This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+
+Popular choices for matching include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
 As @greifer2022 introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
@@
 Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred [@greifer2022].
+Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred [@greifer2022].
 @king2019 argued against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
@@
 
-```{r}
+```{r reg-m-cog}
 table_m_cog
@@
 
-```{r}
+```{r reg-m-ttl}
 table_m_ttl
@@
 
-This thesis proposed a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
-I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
+I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
 Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
-I further examined whether the effect varies across different arrangements of parental migration.
+I further examine whether the effect varies across different arrangements of parental migration.
 Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreased slightly compared to that of non-left-behind peers.
+In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
 
 My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small, lowering the statistical power.
+Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
 Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
 This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
-It is possible that some parents were jailed or hospitalized.
-These types of absence would be wrongly attributed to migration.
+If some parents were jailed or hospitalized, their absence would be wrongly attributed to migration.
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
@@
 Let us consider the policy implications for China.
-The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
+The government has pushed for reforming the multilevel citizenship scheme.
+By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
+However, the most popular migration destinations are metropolises like Beijing and Shanghai.
+These mega-cities still restrict migrant workers' local citizenship rights [@wang2020].
+The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
 The slight reduction is only the short-term consequence.
 Longer duration of parental migration may hamper educational performance to a greater extent.
-Besides, educational performance is only part of human development outcomes [@antia2020].
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence.
-Policymakers should reduce institutional barriers at destination cities, opening more doors for parents to migrate together with their children.
+Besides, educational attainment is only part of human development outcomes.
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020].
+Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
 Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
@@
 
-```{r, fig.cap = "Changes in standardized cognitive test score for newly left-behind students and non-left-behind students"}
+(ref:cog-dif) Changes in standardized cognitive test score
+
+(ref:ttl-dif) Changes in academic exam score
+
+(ref:migr) for new left-behind students and non-left-behind students
+
+(ref:migr-type) by household migration arrangement
+
+```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)")}
 fig_cog
@@
 
-```{r, fig.cap = "Changes in academic exam score for newly left-behind students and non-left-behind students"}
+```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)")}
 fig_ttl
@@
 
-```{r, fig.cap = "Changes in standardized cognitive test score by household migration arrangement"}
+```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
 fig_cog_by_migration_type
@@
 
-```{r, fig.cap = "Changes in academic exam score by household migration type"}
+```{r v-plot-ttl-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
 fig_ttl_by_migration_type
@@
 
-```{r}
+(ref:cobalt-match) Covariate balance before and after matching
+
+(ref:cobalt-any) by any parent migration
+
+(ref:cobalt-fa) by father-only migration
+
+(ref:cobalt-mo) by mother-only migration
+
+(ref:cobalt-both) by both parents migration
+
+```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)")}
+love.plot(
+  m.out,
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+\newpage
+
+```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)")}
+love.plot(
+  m.out_mo_only,
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+\newpage
+
+```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)")}
+love.plot(
+  m.out_fa_only,
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+\newpage
+
+```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)")}
+love.plot(
+  m.out_both,
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+\newpage
+
+```{r reg-m-adj-cog}
 table_m_adj_cog
@@
 
-```{r}
+```{r reg-m-adj-ttl}
 table_m_adj_ttl

### 2022-06-25 MScThesisText.tex
write up main text, put more visuals in appendix

@@
 \hypersetup{
-  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
+  pdftitle={Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
   pdfauthor={Jiancheng Gu1},
@@
 
-\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
+\title{Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 
-Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
 These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
@@
 How are stay-behind children faring when parents have migrated?
-Scholars have obtained mixed results due to the differential effects of parental migration.
+Research results are mixed due to the differential effects of parental migration.
 Consider children's education.
@@
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
+Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause can be on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
 
 In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
-I chose China as the case and analyzed data from a two-wave panel survey.
+I choose China as the case and analyzed data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I developed a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
+I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
 The outcome was measured with children's cognitive test score and academic exam scores.
@@
 1).
-Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
-The loss of nurturing care slows children's accumulation of human capital.
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents (Wen \& Xie, 2019).
 Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
 These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
-Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.~14).
-
-Researchers obtained mixed results regarding how parental migration affects children's education.
+Many of them felt indifferent to grades and disengaged with school.
+Some even longed to quit school to pursue a free, independent life (p.~14).
+
+Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
 Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
@@
 Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
 
@@
 
-In China, the social norms designate men as breadwinners and women as caregivers.
-Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
-Left-behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Under such norms, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
 I propose the second hypothesis:
 
-\(H_2\) In the short term, mother migration negatively affect the cognitive development and academic performance of children left-behind, while father migration does not show a effect.
+\(H_2\) In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
 
@@
 The number of left-behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
-The second feature is the neoliberal welfare regime.
-Neoliberalism extends the logic of the market to most spheres of human life.
-Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
-Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Duckett, 2020).
-The third is the authoritarian control against citizens.
-According to Gu (2021) and Zhang (2018), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+The internal migration stemmed from the neoliberal economic regime.
+
+The neoliberal economic regime sounds at odds with China, a so-called socialist country.
+Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
+Since then, China has integrated in the world economy and contributed substantial growth to it.
+The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
+The rural hinterlands, however, have lagged behind.
+The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
+Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
+As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
+The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere (Duckett, 2020; Zhang, 2018).
+
+The institutionalized discrimination against migrant laborers find its roots in China's ``multilevel citizenship'' .
+As Vortherms (2021) demonstrated, citizenship is defined by ``membership rules and rights entitlements;'' they operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
+
+\begin{quote}
+A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
+Accessing fundamental citizenship rights depends on your registration status \ldots{} Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
+(Vortherms, 2021)
+\end{quote}
+
+In other words, the hukou system binds one's citizenship rights with one's place of registry.
 One can move out of town freely but cannot change hukou freely.
-For rural household members moving to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they only enjoy limited access to public service in the host city, including public education for children.
-Migrant laborers had organized strikes and protests, only to meet with police crackdown (Chan \& Selden, 2017).
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns (Gu, 2021; Zhang, 2018).
+When a rural resident moves to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiving urban hukou, they can hardly send their children into public schools in the city {[}Gu (2021); wang2020{]}.
+Migrant workers had organized strikes and protests, only to meet with police crackdown (Chan \& Selden, 2017).
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
 
@@
 The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Jin et al., 2020; Y.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Y.
 Liu et al., 2021; Shu, 2021; F.
 Yang et al., 2022).
-Others only estimate correlation using cross-sectional data (Akezhuoli et al., 2022; Jin et al., 2020).
-These studies could have applied causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-Others s The third shortcoming lies in the measurement of outcome.
+Others only estimated correlation using cross-sectional data (Akezhuoli et al., 2022; Jin et al., 2020).
+These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+The third shortcoming lies in the measurement of outcome.
 Chang et al.
@@
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
+The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one (W.
+Wang \& Li, 2015).
 
@@
 This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
-Throughout junior high school, students study these subjects, which are included in the entrance exam to senior high school.
-Within each cohort in one particular school, teachers adopt the same syllabus and administer the same exams during a given assessment period.
-Therefore, test scores for core subjects are reliable indicators of learning performance in the same school and cohort.
-I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
+This is related to how junior high schools operate as part of the compulsory education system in China.
+According to OECD (2016), China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
+At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
+Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
+Within each cohort in one particular school, teachers use the same syllabus and administer the same exams during a given assessment period.
+Across cities and regions, junior high schools adopt the educational content and assessment set by the Ministry of Education (OECD, 2016).
+
+I transformed the exam grades through the following steps.
+I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
 After the conversion, I checked for abnormal values outside the 0-100 range.
 31 observations were outliers, accounting for less than one percent of the sample.
-I trimed the values of subject exam score with minimum of zero and maximum of one hundred.
+I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
 In this way, I can limit the impact of outliers while retaining these observations in the sample.
@@
 
+The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet assess at home.
+
 \hypertarget{data-analysis}{%
@@
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j;1} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(C_{j}\) and \(C_{k}\) are respectively the classroom fixed-effects at baseline and follow-up, and \(score_{i,j,k;1}\) is the test score at baseline.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j,k;1}\) is the test score at baseline, and \(C_{j}\) and \(C_{k}\) are the classroom fixed-effects at baseline and follow-up, respectively.
 Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
@@
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, n.d.).
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
 The standard errors were clustered at the classroom level.
 
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot C_{j} + \lambda \cdot C_{k} + \theta \cdot score_{i,j,k;1} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
-The table below summarizes the changes in migration status in the sample.
+Table \ref{i-var} below summarizes the changes in migration status in the sample.
 All 4088 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
@@
 \begin{longtable}[]{@{}llrr@{}}
-\caption{Parental migration status at follow-up survey.}\tabularnewline
-\toprule
-& & N & \% \\
-\midrule
-\endfirsthead
 \toprule
@@
 \begin{longtable}[]{@{}lrrrr@{}}
-\caption{The independent variables}\tabularnewline
-\toprule
-& Mean & SD & Min & Max \\
-\midrule
-\endfirsthead
 \toprule
@@
 \begin{longtable}[]{@{}llrr@{}}
-\caption{The control variables}\tabularnewline
-\toprule
-& & N & \% \\
-\midrule
-\endfirsthead
 \toprule
@@
 Parental migration is not a randomly assigned treatment.
-One technique to tackle this selection bias is matching.
-This method works by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-Popular choices include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H.
+A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
+Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
+To tackle the selection bias herein, an applicable technique is matching.
+This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+
+Popular choices for matching include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H.
 Xu \& Xie, 2015).
@@
 Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will or have occurred (Greifer, 2022).
+Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred (Greifer, 2022).
 King and Nielsen (2019) argued against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
@@
 
-This thesis proposed a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
-I built econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+This thesis proposes a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
+I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
 Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
-I further examined whether the effect varies across different arrangements of parental migration.
+I further examine whether the effect varies across different arrangements of parental migration.
 Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreased slightly compared to that of non-left-behind peers.
+In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
 
 My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small, lowering the statistical power.
+Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
 Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
 This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
-It is possible that some parents were jailed or hospitalized.
-These types of absence would be wrongly attributed to migration.
+If some parents were jailed or hospitalized, their absence would be wrongly attributed to migration.
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
@@
 \centering
-\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}Changes in standardized cognitive test score for newly left-behind students and non-left-behind students}
+\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1.pdf}
+\caption{\label{fig:v-plot-cog}Changes in standardized cognitive test score for new left-behind students and non-left-behind students}
 \end{figure}
@@
 \centering
-\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\label{fig:unnamed-chunk-11}Changes in academic exam score for newly left-behind students and non-left-behind students}
+\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1.pdf}
+\caption{\label{fig:v-plot-ttl}Changes in academic exam score for new left-behind students and non-left-behind students}
 \end{figure}
@@
 \centering
-\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{\label{fig:unnamed-chunk-12}Changes in standardized cognitive test score by household migration arrangement}
+\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1-1.pdf}
+\caption{\label{fig:v-plot-cog-1}Changes in standardized cognitive test score by household migration arrangement}
 \end{figure}
@@
 \centering
-\includegraphics{MScThesisText_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\label{fig:unnamed-chunk-13}Changes in academic exam score by household migration type}
+\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1-1.pdf}
+\caption{\label{fig:v-plot-ttl-1}Changes in standardized cognitive test score by household migration arrangement}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/cobal-any-1.pdf}
+\caption{\label{fig:cobal-any}Covariate balance before and after matching by any parent migration}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/cobal-mo-1.pdf}
+\caption{\label{fig:cobal-mo}Covariate balance before and after matching by mother-only migration}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/cobal-fa-1.pdf}
+\caption{\label{fig:cobal-fa}Covariate balance before and after matching by father-only migration}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{MScThesisText_files/figure-latex/cobal-both-1.pdf}
+\caption{\label{fig:cobal-both}Covariate balance before and after matching by both parents migration}
 \end{figure}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-huntington-klein}{}}%
-Huntington-Klein, N. (n.d.). \emph{The effect: An introduction to research design and causality \textbar{} the effect}. \url{https://theeffectbook.net/index.html}
+\leavevmode\vadjust pre{\hypertarget{ref-huntington-klein2022}{}}%
+Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality \textbar{} The Effect}. CRC Press. \url{https://theeffectbook.net/index.html}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-oecd2016}{}}%
+OECD. (2016). \emph{Education in china: A snapshot}. \url{https://www.oecd.org/china/Education-in-China-a-snapshot.pdf}
+
 \leavevmode\vadjust pre{\hypertarget{ref-popova2018}{}}%
@@
 \url{https://doi.org/10.1111/jomf.12621}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vortherms2021}{}}%
+Vortherms, S. A. (2021). \emph{Hukou as a case of multi-level citizenship} (Z. Guo, Ed.; pp. 132--142). Routledge. \href{https://doi.org/10.4324/9781003225843-12}{doi.org/10.4324/9781003225843-12}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
+Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey {[}in chinese{]}}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
@@
 \url{https://doi.org/10.1177/1868102619894739}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wen2019}{}}%
+Wen, Y., \& Xie, J.
+(2019).
+Missing families and villages: The care deficit faced by rural left-behind children in china and its implications.
+\emph{International Journal of Care and Caring}, \emph{3}(2), 247--262.
+\url{https://doi.org/10.1332/239788218X15421003245041}
 

### 2022-06-25 data/Gu-thesis-script.Rmd
write up main text, put more visuals in appendix

@@
 library(ggplot2)
+library(labelled)
 library(cobalt) 
@@
 dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
-d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
+d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) %>% remove_labels()
 ```
@@
 )
-```
-
-```{}
-set.seed(1)
-d %>% select(
-  w1chn_100:w2eng_100) %>%
-ggplot(aes(x=w1chn_100:w2eng_100)) + 
-  geom_boxplot(alpha=0.2)
 ```
@@
   parent.educational.level, parent.expectation.on.child, 
-  home.extracurricular.book, home.economic.resource) %>%
-  remove_labels()
+  home.extracurricular.book, home.economic.resource) 
 ```
@@
 ```{r}
-table_independent_variable <- datasummary_skim(
-    data=d_idpvar,
-    type = 'categorical',
-    output = 'markdown')
-table_independent_variable
-```
-
-```{r}
 d_idpvar <- d_migr %>% 
@@
 ```{r}
-
+table_independent_variable <- datasummary_skim(
+    data=d_idpvar,
+    type = 'categorical',
+    output = 'markdown')
+table_independent_variable
 ```
@@
 
-```{r}
+```{}
 #table_control_variable <- 
@@
 )
+table_control_variable
 ```
@@
 Whole sample summary
-```{r}
+```{}
 table_sum <- st(
@@
 
-```{r}
+```{}
 table_sum_migr <- st(
@@
 ```{r}
-love.plot(
-  m.out,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 0.55),
-  )
-```
-
-```{r}
 dm <- match.data(m.out)
@@
 ```{r}
-sum_m.out_fa_only <- summary(m.out_fa_only)
-fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
+sum_m.out_mo_only <- summary(m.out_mo_only)
+fig_msmd_mo_only <- plot(sum_m.out_mo_only, xlim = c(0, 0.55), position = 'right')
 ```
@@
 ```
+
+```{r}
+love.plot(
+  m.out,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 0.55),
+  )
+```
+
+```{r}
+love.plot(
+  m.out_mo_only,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 0.55),
+  )
+```
+
 ```{r}
@@
 ```
+
+```{r}
+bal.tab(m.out)
+```

### 2022-06-29 MScThesisText.Rmd
version before presentation

@@
 library("cobalt")
+library("kableExtra")
 r_refs("references.bib")
@@
 Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
-@yang2008 noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+@yang2008 noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
 This subsequently boosted children's school enrollment and educational expenditure.
@@
 They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The number of left-behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind [@nbs2017].
 The internal migration stemmed from the neoliberal economic regime.
@@
 The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
+The regional inequality needs social policy to amend, but China's welfare program is discriminatory -- it segregates the population.
 Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2021].
-Migrant workers had organized petitions, strikes, and protests, only to fall on deaf ears or even end with police crackdown [@chan2017].
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2022].
+Migrant workers have organized petitions, strikes, and protests.
+These actions often fell on deaf ears and sometimes even ended with police crackdown [@chan2019].
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
@@
 
-```{r i-var}
+\renewcommand{\arraystretch}{0.75}
+```{r i-var, fig.cap='Parental migration status at follow-up survey'}
 table_independent_variable
@@
 
-: Parental migration status at follow-up survey.
+\newpage
 
-Tables 2 and 3 below provide the whole-sample summary statistics.
-In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
+Tables 2 below summarizes the dependent variables by the control group and the treatment group. In addition, the violin plots in the appendix visualize the distribution of outcome variables.
 
-```{r d-var}
-table_dependent_variable
+```{r fig.cap='Dependent variables by parental migration'}
+tab_dpvar |> 
+  kable(booktabs = T, position = "left", row.names = F) |>
+  add_indent(c(2,3,5,6)) |>
+  add_header_above(c(" ", "No = 3452" = 2, "Yes = 636" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
 ```
 
-: The independent variables
+\newpage
 
-```{r c-var}
-table_control_variable
+```{r fig.cap='Dichotomous control variables by parental migration'}
+tab_ctvar_dit |>
+  kable(booktabs = T, position = "left", row.names = F) |>
+  add_header_above(c(" ", "No = 3452" = 2, "Yes = 636" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
 ```
 
-: The control variables
+\newpage
+
+```{r fig.cap='Continuous control variables by parental migration'}
+tab_ctvar_cnt |>
+  kable(booktabs = T, position = "left", row.names = F) |>
+  add_header_above(c(" ", "No = 3452" = 2, "Yes = 636" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
+```
 
@@
 
+\newpage
+
 ```{r reg-m-ttl}
@@
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind.
+As I previously wrote, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
+Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind .
 These limitations may bias the estimation.
@@
 Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
-Synthetic control can evaluate the aggregate outcome of "large-scale but infrequent interventions" at municipal or provincial levels [@abadie2021], such as the policy experimentations that liberalize the hukou system in certain cities [@wang2020].
 Third, researchers can go beyond outbound migration to study return migration of parents [@liang2021].
-Only a few publications, such as that of @liu2018, have explored return migrants and their stay-behind children in the Chinese context.
+Only a few publications have explored return migrants and their stay-behind children in the Chinese context [@démurger2015; @liu2018].
 
 Let us consider the policy implications for China.
-The government has pushed for reforming the multilevel citizenship scheme.
+The government has enacted reforms in the multilevel citizenship scheme.
 By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
@@
 The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent.
+Longer duration of parental migration may hamper educational performance to a greater extent [@liang2020; @meng2017].
 Besides, educational attainment is only part of human development outcomes.
@@
 Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
-Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
+Schools could dedicate more advisory and counseling support to children who stay behind.
+"Social workers could test models for training paraprofessionals within different communities" to support left-behind children [@wang2020a, p.
+1436].
 
@@
 
-```{r v-plot-ttl-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
+```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)")}
 fig_ttl_by_migration_type
@@
 ```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)")}
-love.plot(
-  m.out,
+m.out |> love.plot(
   threshold = c(m = .1),
@@
 ```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)")}
-love.plot(
-  m.out_mo_only,
+m.out_mo_only |> love.plot(
   threshold = c(m = .1),
@@
 ```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)")}
-love.plot(
-  m.out_fa_only,
+m.out_fa_only |> love.plot(
   threshold = c(m = .1),
@@
 ```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)")}
-love.plot(
-  m.out_both,
+m.out_both |> love.plot(
   threshold = c(m = .1),

### 2022-06-29 MScThesisText.tex
version before presentation

@@
 Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
+In a 2021 resolution, the Council of Europe's Parliamentary Assembly (2021) expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' (p.~2) and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights'' (p.~1).
 
@@
 
-A challenge arises when we want to assess the causality between parent's migration and children's educational achievement.
+A challenge arises in assessing the causality between parent's migration and children's educational achievement.
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause can be on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
-
-In this thesis, my research question is: To what extent do parental migration affect the educational performance of left-behind children in the short term?
+Alternatively, a quasi-experimental design can help with causal inference.
+The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
+
+In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
 I choose China as the case and analyzed data from a two-wave panel survey.
@@
 D.
-Yang (2008) noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+Yang (2008) noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
 This subsequently boosted children's school enrollment and educational expenditure.
@@
 
-Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
 Y.
@@
 They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The number of left-behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS et al., 2017).
 The internal migration stemmed from the neoliberal economic regime.
@@
 Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the world economy and contributed substantial growth to it.
+Since then, China has integrated in the global economy and contributed substantial growth to it.
 The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
 The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
+The regional inequality needs social policy to amend, but China's welfare program is discriminatory -- it segregates the population.
 Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
@@
 
-The institutionalized discrimination against migrant laborers find its roots in China's ``multilevel citizenship'' .
-As Vortherms (2021) demonstrated, citizenship is defined by ``membership rules and rights entitlements;'' they operate below the national level in China.
+The institutionalized discrimination against migrant laborers find its roots in China's ``multilevel citizenship'' system.
+As Vortherms (2021) demonstrated, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
 The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
@@
 In other words, the hukou system binds one's citizenship rights with one's place of registry.
-One can move out of town freely but cannot change hukou freely.
-When a rural resident moves to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the city {[}Gu (2021); wang2020{]}.
-Migrant workers had organized strikes and protests, only to meet with police crackdown (Chan \& Selden, 2017).
+In theory, anyone can move out of town freely.
+In practice, they cannot change hukou freely.
+When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022).
+Migrant workers have organized petitions, strikes, and protests.
+These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019).
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
@@
 The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet assess at home.
+At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
 
@@
 
-Table \ref{i-var} below summarizes the changes in migration status in the sample.
+Table 1 below summarizes the changes in migration status in the sample.
 All 4088 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
@@
 The remaining one-fifth was both-parents migration.
+
+\renewcommand{\arraystretch}{0.75}
 
@@
 
-The tables below provide the whole-sample summary statistics.
-In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\toprule
-& Mean & SD & Min & Max \\
-\midrule
-\endhead
-Cognitive score difference & 0.27 & 0.80 & -2.88 & 4.03 \\
-Cognitive score at wave 1 & 0.15 & 0.85 & -2.03 & 2.33 \\
-Cognitive score at wave 2 & 0.42 & 0.78 & -3.14 & 2.06 \\
-Academic exam score difference & -8.82 & 33.21 & -207.50 & 166.00 \\
-Academic exam score at wave 1 & 213.11 & 49.46 & 19.33 & 297.50 \\
-Academic exam score at wave 2 & 204.29 & 55.41 & 0.00 & 293.33 \\
+\newpage
+
+Tables 2 below summarizes the dependent variables by the control group and the treatment group. In addition, the violin plots in the appendix visualize the distribution of outcome variables.
+
+\begin{tabular}{llllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+Variable & Mean & Sd & Mean & Sd & Test\\
+\midrule
+Cognitive test score difference & 0.28 & 0.8 & 0.19 & 0.8 & p=0.006**\\
+\hspace{1em}Wave 1 score & 0.15 & 0.86 & 0.13 & 0.84 & p=0.471\\
+\hspace{1em}Wave 2 score & 0.43 & 0.78 & 0.31 & 0.8 & p<0.001***\\
+Academic exam score difference & -8.2 & 32.75 & -12.15 & 35.43 & p=0.006**\\
+\hspace{1em}Wave 1 score & 213.39 & 49.31 & 211.58 & 50.3 & p=0.395\\
+\addlinespace
+\hspace{1em}Wave 2 score & 205.19 & 54.83 & 199.42 & 58.23 & p=0.016*\\
 \bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}llrr@{}}
-\toprule
-& & N & \% \\
-\midrule
-\endhead
-migr & 0 & 3452 & 84.4 \\
-& 1 & 636 & 15.6 \\
-child.is.girl & 0 & 2002 & 49.0 \\
-& 1 & 2086 & 51.0 \\
-child.has.rural.hukou & 0 & 2221 & 54.3 \\
-& 1 & 1867 & 45.7 \\
-child.in.boarding.school & 0 & 2906 & 71.1 \\
-& 1 & 1182 & 28.9 \\
-child.is.ethnic.minority & 0 & 3800 & 93.0 \\
-& 1 & 288 & 7.0 \\
-child.had.skipped.grade & 0 & 4042 & 98.9 \\
-& 1 & 46 & 1.1 \\
-child.had.repeated.grade & 0 & 3700 & 90.5 \\
-& 1 & 388 & 9.5 \\
-child.went.to.preschool & 0 & 639 & 15.6 \\
-& 1 & 3449 & 84.4 \\
-parent.has.white.collar.job & 0 & 3238 & 79.2 \\
-& 1 & 850 & 20.8 \\
-home.has.internet & 0 & 1316 & 32.2 \\
-& 1 & 2772 & 67.8 \\
-child.health.self.rated & Very poor & 21 & 0.5 \\
-& Not very good & 113 & 2.8 \\
-& Moderate & 807 & 19.7 \\
-& Good & 1383 & 33.8 \\
-& Very good & 1764 & 43.2 \\
-child.educational.aspiration & Junior high school & 140 & 3.4 \\
-& Senior high school & 418 & 10.2 \\
-& Associate college & 616 & 15.1 \\
-& University & 1205 & 29.5 \\
-& Postgraduate & 1709 & 41.8 \\
-parent.educational.level & Primary school and below & 248 & 6.1 \\
-& Junior high school & 1580 & 38.6 \\
-& Senior high school & 1254 & 30.7 \\
-& Associate college & 385 & 9.4 \\
-& University & 543 & 13.3 \\
-& Postgraduate & 78 & 1.9 \\
-parent.expectation.on.child & Junior high school & 36 & 0.9 \\
-& Senior high school & 257 & 6.3 \\
-& Associate college & 426 & 10.4 \\
-& University & 1574 & 38.5 \\
-& Postgraduate & 1795 & 43.9 \\
-home.extracurricular.book & Very few & 395 & 9.7 \\
-& Not many & 414 & 10.1 \\
-& Some & 1312 & 32.1 \\
-& Quite a few & 1111 & 27.2 \\
-& A great number & 856 & 20.9 \\
-home.economic.resource & Very poor & 115 & 2.8 \\
-& Somewhat poor & 598 & 14.6 \\
-& Moderate & 3124 & 76.4 \\
-& Somewhat rich & 239 & 5.8 \\
-& Very rich & 12 & 0.3 \\
+\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
+\end{tabular}
+
+\newpage
+
+\begin{tabular}{llllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+Variable & N & Percent & N & Percent & Test\\
+\midrule
+child.is.girl &  &  &  &  & X2=11.942***\\
+... 0 & 1650 & 48\% & 352 & 55\% & \\
+... 1 & 1802 & 52\% & 284 & 45\% & \\
+child.has.rural.hukou &  &  &  &  & X2=0.485\\
+... 0 & 1884 & 55\% & 337 & 53\% & \\
+\addlinespace
+... 1 & 1568 & 45\% & 299 & 47\% & \\
+child.in.boarding.school &  &  &  &  & X2=4.63*\\
+... 0 & 2477 & 72\% & 429 & 67\% & \\
+... 1 & 975 & 28\% & 207 & 33\% & \\
+child.is.ethnic.minority &  &  &  &  & X2=0.388\\
+\addlinespace
+... 0 & 3213 & 93\% & 587 & 92\% & \\
+... 1 & 239 & 7\% & 49 & 8\% & \\
+child.had.skipped.grade &  &  &  &  & X2=0.02\\
+... 0 & 3414 & 99\% & 628 & 99\% & \\
+... 1 & 38 & 1\% & 8 & 1\% & \\
+\addlinespace
+child.had.repeated.grade &  &  &  &  & X2=10.621**\\
+... 0 & 3147 & 91\% & 553 & 87\% & \\
+... 1 & 305 & 9\% & 83 & 13\% & \\
+child.went.to.preschool &  &  &  &  & X2=0.923\\
+... 0 & 531 & 15\% & 108 & 17\% & \\
+\addlinespace
+... 1 & 2921 & 85\% & 528 & 83\% & \\
+parent.has.white.collar.job &  &  &  &  & X2=0.001\\
+... 0 & 2735 & 79\% & 503 & 79\% & \\
+... 1 & 717 & 21\% & 133 & 21\% & \\
+home.has.internet &  &  &  &  & X2=12.815***\\
+\addlinespace
+... 0 & 1072 & 31\% & 244 & 38\% & \\
+... 1 & 2380 & 69\% & 392 & 62\% & \\
 \bottomrule
-\end{longtable}
+\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
+\end{tabular}
+
+\newpage
+
+\begin{tabular}{llllll}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
+\cmidrule(l{3pt}r{3pt}){2-5}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+Variable & Mean & Sd & Mean & Sd & Test\\
+\midrule
+child.age & 12.45 & 0.63 & 12.5 & 0.72 & F=3.616\\
+child.health.self.rated & 4.17 & 0.87 & 4.14 & 0.9 & F=0.622\\
+child.educational.aspiration & 3.97 & 1.12 & 3.93 & 1.19 & F=0.617\\
+parent.educational.level & 2.9 & 1.19 & 2.94 & 1.21 & F=0.367\\
+parent.expectation.on.child & 4.19 & 0.91 & 4.15 & 0.94 & F=1.093\\
+\addlinespace
+home.extracurricular.book & 3.41 & 1.18 & 3.32 & 1.28 & F=3.09\\
+home.economic.resource & 2.87 & 0.55 & 2.84 & 0.58 & F=1.37\\
+\bottomrule
+\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
+\end{tabular}
 
@@
 If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to is -0.09 SD in cognitive test score and -0.09 points in academic exam grades.
+Parental migration is linked to -0.09 SD in cognitive test score and -0.09 points in academic exam grades.
 Both relationships are slight in strength.
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
-\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
+\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
 \toprule
@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Absent
+Any Parent Migrated
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Migrated
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Migrated
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Migrated
 \end{minipage} \\
@@
 \endhead
-Explanator & -0.09** & -0.04 & -0.14** & -0.10 \\
+Migration & -0.09** & -0.04 & -0.14** & -0.10 \\
 & (0.03) & (0.05) & (0.04) & (0.06) \\
@@
 
+\textbf{Note:}
+\^{}\^{} Control variables not included
+
+\newpage
+
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
-\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
+\caption{Parental migration's effect on children's academic exam score}\tabularnewline
 \toprule
@@
 \endhead
-Explanator & -2.67* & -5.85* & -0.25 & -1.13 \\
+Migration & -2.67* & -5.85* & -0.25 & -1.13 \\
 & (1.26) & (2.36) & (1.66) & (2.28) \\
@@
 
+\textbf{Note:}
+\^{}\^{} Control variables not included
+
 The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
 \toprule
@@
 \endhead
-Explanator & -0.09** & -0.04 & -0.14*** & -0.08 \\
+Migration & -0.09** & -0.04 & -0.14*** & -0.08 \\
 & (0.03) & (0.05) & (0.04) & (0.06) \\
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
+\caption{Parental migration's effect on children's academic exam score}\tabularnewline
 \toprule
@@
 \endhead
-Explanator & -2.65* & -5.87** & -0.20 & -0.92 \\
+Migration & -2.65* & -5.87** & -0.20 & -0.92 \\
 & (1.25) & (2.24) & (1.68) & (2.35) \\
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
-\caption{Parental migration's effect on children's cognitive abilities, estimated with matching}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
+\caption{Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
 \toprule
@@
 \endhead
-Explanator & -0.09** & -0.05 & -0.13* & -0.05 \\
+Migration & -0.09** & -0.05 & -0.13* & -0.05 \\
 & (0.03) & (0.06) & (0.06) & (0.11) \\
@@
 
+\newpage
+
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1398}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2043}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2151}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2258}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
 \caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
@@
 
-This thesis proposes a model to assess causality between parents' migration and their stay-behind children's educational performance in the short run.
+This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
 I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
@@
 Liu, 2021).
-Synthetic control can evaluate the aggregate outcome of ``large-scale but infrequent interventions'' at municipal or provincial levels (Abadie, 2021), such as the policy experimentations that liberalize the hukou system in certain cities (X.
+Third, researchers can go beyond outbound migration to study return migration of parents (Liang \& Li, 2021).
+Only a few publications have explored return migrants and their stay-behind children in the Chinese context (Démurger \& Xu, 2015; Z.
+Liu et al., 2018).
+
+Let us consider the policy implications for China.
+The government has enacted reforms in the multilevel citizenship scheme.
+By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
+However, the most popular migration destinations are metropolises like Beijing and Shanghai.
+These mega-cities still restrict migrant workers' local citizenship rights (X.
 Wang, 2020).
-Third, researchers can go beyond outbound migration to study return migration of parents (Liang \& Li, 2021).
-Only a few publications, such as that of Z.
-Liu et al.
-(2018), have explored return migrants and their stay-behind children in the Chinese context.
-
-Let us consider the policy implications for China.
-The small reduction of newly left behind children's schooling performance by no means suggest that policies can remain as they are.
+The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
 The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent.
-Besides, educational performance is only part of human development outcomes (Antia et al., 2020).
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence.
-Policymakers should reduce institutional barriers at destination cities, opening more doors for parents to migrate together with their children.
-Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
+Longer duration of parental migration may hamper educational performance to a greater extent (Liang \& Sun, 2020; Meng \& Yamauchi, 2017).
+Besides, educational attainment is only part of human development outcomes.
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020).
+Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
+Schools could dedicate more advisory and counseling support to children who stay behind.
+``Social workers could test models for training paraprofessionals within different communities'' to support left-behind children (M.
+Wang et al., 2020, p.
+1436).
 
@@
 \includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1-1.pdf}
-\caption{\label{fig:v-plot-ttl-1}Changes in standardized cognitive test score by household migration arrangement}
+\caption{\label{fig:v-plot-ttl-1}Changes in academic exam score by household migration arrangement}
 \end{figure}
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
 \caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
+\caption{Parental migration's effect on children's academic exam scores, estimated with matching}\tabularnewline
 \toprule
@@
 \endhead
-Explanator & -2.91† & -5.90* & -2.68 & -2.94 \\
+Migration & -2.91† & -5.90* & -2.68 & -2.94 \\
 & (1.48) & (2.64) & (2.56) & (4.21) \\
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abadie2021}{}}%
-Abadie, A.
-(2021).
-Using Synthetic Controls: Feasibility, Data Requirements, and Methodological Aspects.
-\emph{Journal of Economic Literature}, \emph{59}(2), 391--425.
-\url{https://doi.org/10.1257/jel.20191450}
-
 \leavevmode\vadjust pre{\hypertarget{ref-akezhuoli2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chan2017}{}}%
-Chan, J., \& Selden, M. (2017). The labour politics of china{'}s rural migrant workers. \emph{Globalizations}, \emph{14}(2), 259--271. \url{https://doi.org/10.1080/14747731.2016.1200263}
+\leavevmode\vadjust pre{\hypertarget{ref-chan2019}{}}%
+Chan, J. (2019). State and labor in China, 1978{\textendash}2018. \emph{Journal of Labor and Society}, \emph{22}(2), 461--475. \url{https://doi.org/10.1111/wusa.12408}
 
@@
 Cunningham, S. (2021). \emph{Causal inference: The mixtape}. Yale University Press. \url{https://mixtape.scunning.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-duxe9murger2015}{}}%
+Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in china. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gu2021}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-gu2022}{}}%
 Gu, X.
-(2021).
+(2022).
 {`}Save the children!{'}: Governing left-behind children through family in China{'}s Great Migration.
-\emph{Current Sociology}, 0011392120985874.
+\emph{Current Sociology}, \emph{70}(4), 513--538.
 \url{https://doi.org/10.1177/0011392120985874}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-liang2020}{}}%
+Liang, Z., \& Sun, F.
+(2020).
+The lasting impact of parental migration on children's education and health outcomes: The case of china.
+\emph{Demographic Research}, \emph{S28}(9), 217--244.
+\url{https://doi.org/10.4054/DemRes.2020.43.9}
+
 \leavevmode\vadjust pre{\hypertarget{ref-liu2021a}{}}%
@@
 \url{https://doi.org/10.1016/j.chieco.2017.06.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meng2017}{}}%
+Meng, X., \& Yamauchi, C.
+(2017).
+Children of migrants: The cumulative impact of parental migration on children{'}s education and health outcomes in china.
+\emph{Demography}, \emph{54}(5), 1677--1714.
+\url{https://doi.org/10.1007/s13524-017-0613-z}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021a}{}}%
+Parliamentary Assembly.
+(2021).
+\emph{Resolution 2366: Impact of labour migration on {``}left-behind{''} children}.
+\url{https://pace.coe.int/pdf/750b8aea81ea5b757d3b0db7f9865a27e4982ffbc23c9f49d28122e772e123ef/resolution\%202366.pdf}
+
 \leavevmode\vadjust pre{\hypertarget{ref-popova2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wang2020a}{}}%
+Wang, M., Victor, B.
+G., Hong, J.
+S., Wu, S., Huang, J., Luan, H., \& Perron, B.
+E.
+(2020).
+A Scoping Review of Interventions to Promote Health and Well-Being of Left-behind Children in Mainland China.
+\emph{The British Journal of Social Work}, \emph{50}(5), 1419--1439.
+\url{https://doi.org/10.1093/bjsw/bcz116}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%

### 2022-06-29 data/Gu-thesis-script.Rmd
version before presentation

@@
 library(MatchIt)
-#library(vtable)
+library(vtable)
 library(ggplot2)
@@
 ```{r}
-d_stu1 <- d_stu1 %>% 
-  subset(grade9==0) %>% 
+d_stu1 <- d_stu1 |> 
+  subset(grade9==0) |> 
   select(!c(frame, subsample, sweight, grade9))
-d_stu2 <- d_stu2 %>% 
+d_stu2 <- d_stu2 |> 
   select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
-d_par1 <- d_par1 %>% 
-  subset(grade9==0) %>% 
+d_par1 <- d_par1 |> 
+  subset(grade9==0) |> 
   select(!c(frame, subsample, grade9))
@@
 ```{r}
-dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
-dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
-d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) %>% remove_labels()
-```
-
-```{r}
-d <- d %>% mutate(
+dw1 <- d_stu1 |> left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
+dw2 <- d_stu2 |> left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
+d <- dw1 |> right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) |> remove_labels()
+```
+
+```{r}
+d <- d |> mutate(
   child.age = 2013 - a02a, #student's age at baseline
@@
 ```{r}
-d <- d %>% mutate(
+d <- d |> mutate(
   w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
@@
 ```{r}
-d <- d %>% mutate(
+d <- d |> mutate(
   w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
@@
 ```{r}
-d1 <- d %>%
+d1 <- d |>
   drop_na(cog_dif, ttl_dif, child.age)
@@
 ```{}
-d1 <- d1 %>% group_by(clsids + w2clsids) %>%
+d1 <- d1 |> group_by(clsids + w2clsids) |>
   mutate(
@@
     w2ttl_z = as.numeric(scale(w2ttl))
-  ) %>% ungroup()
-```
-
-```{}
-d1 <- d1 %>% group_by(clsids + w2clsids) %>%
+  ) |> ungroup()
+```
+
+```{}
+d1 <- d1 |> group_by(clsids + w2clsids) |>
   mutate(
@@
     w2ttl_std = rescale(w2ttl)
-    ) %>% ungroup()
+    ) |> ungroup()
 ```
@@
 ```{}
-d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
-d_outlier1 <- d_outlier %>% select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
-d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
+d_outlier <- d |> filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
+d_outlier1 <- d_outlier |> select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
+d1 <- d |> anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
 ```
@@
 ```{r}
-d_cl <- d1 %>% 
-  filter(w2a0801==1) %>% #keep parents who are married (and alive)
-  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
+d_cl <- d1 |> 
+  filter(w2a0801==1) |> #keep parents who are married (and alive)
+  filter(be1201==1 & be1202==1) |> #keep both parents live with children at baseline
   filter(stmigrant==1) #keep local children 
@@
 ```{r}
-d_cl <- d_cl %>% mutate(
+d_cl <- d_cl |> mutate(
          child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
@@
          home.extracurricular.book = b12 #Amount of book at home, student self-rated 
-) %>% drop_na(
+) |> drop_na(
 child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu,
@@
 ```{r}
-d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
-d_cl <- d_cl %>% mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
+d_cl$stsib <- d_cl$stsib |> replace_na(0) |> as.numeric()
+d_cl <- d_cl |> mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) |> #number of siblings
   drop_na(child.number.of.sibling)
@@
 ```{}
-d_cl <- d_cl %>% mutate(parent.educational.level = NA)
+d_cl <- d_cl |> mutate(parent.educational.level = NA)
 d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
@@
 ```{r}
-d_cl <- d_cl %>% mutate(parent.educational.level = NA)
+d_cl <- d_cl |> mutate(parent.educational.level = NA)
 d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
@@
 ```{r}
-d_cl <- d_cl %>% mutate(parent.expectation.on.child = NA)
+d_cl <- d_cl |> mutate(parent.expectation.on.child = NA)
 d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
@@
 ```{r}
-d_cl <- d_cl %>% mutate(child.educational.aspiration = NA)
+d_cl <- d_cl |> mutate(child.educational.aspiration = NA)
 d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
@@
 ```{r}
-d_cl <- d_cl %>%  drop_na(
+d_cl <- d_cl |>  drop_na(
   parent.educational.level, 
@@
 ```{r}
-d_cl <- d_cl %>% mutate(
-  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
+d_cl <- d_cl |> mutate(
+  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became Migrated from household between baseline and endline survey
   migr_fa_only = NA,
@@
   migr_both = NA
-  ) %>% drop_na(migr)
+  ) |> drop_na(migr)
 ```
@@
 ```{}
-df <- d_cl %>% select(
+df <- d_cl |> select(
   migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
@@
 ```{r}
-d_migr <- d_cl %>%
+d_migr <- d_cl |>
   select(
@@
 ```{r}
-d_smr <- d_migr %>% 
-  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
+d_smr <- d_migr |> 
+  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |> 
   mutate(`Parental Migration Type` = 0) 
@@
 d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
-d_smr <- d_smr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+d_smr <- d_smr |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
 ```
@@
 ```{r}
-d_dpvar <- d_migr %>%
-  select(#migr, 
-         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) %>%
-  rename(
-    `Cognitive score at wave 1` = cog3pl,
-    `Cognitive score at wave 2` = w2cog3pl,
-    `Academic exam score at wave 1` = w1ttl_100,
-    `Academic exam score at wave 2` = w2ttl_100,
-    `Cognitive score difference` = cog_dif,
-    `Academic exam score difference` = ttl_dif
-  ) 
-```
-
-```{}
-d_dpvar %>%
-  tbl_summary(
-    by = migr,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} / {N} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    ) %>% add_p() %>% as_kable()
-```
-
-```{r}
-#table_independent_variable <- 
+d_dpvar1 <- d_migr |>
+  select(migr, 
+         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) |>
+  set_variable_labels(
+    migr = 'Parental migration',
+    cog3pl ='Wave 1 score',
+    w2cog3pl = 'Wave 2 score',
+    w1ttl_100='Wave 1 score',
+    w2ttl_100 = 'Wave 2 score',
+    cog_dif = 'Cognitive test score difference',
+    ttl_dif = 'Academic exam score difference'
+  )
+```
+
+```{r}
+tab_dpvar <- 
   st(
-  d_dpvar,
+  data = d_dpvar1,
+  summ = c('mean(x)', 'sd(x)'),
   digits = 2, 
   group = 'migr',
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = 'kable')
-#table_independent_variable 
-```
-
-```{r}
+  group.test = list(
+    star.cutoffs = c(0.001, 0.01, 0.05),
+    format = 'p={pval}{stars}'),
+  labels = T,
+  out = 'return') 
+tab_dpvar <- tab_dpvar[-c(1),]
+tab_dpvar[tab_dpvar == 'p=&lt0.001***'] <- 'p<0.001***'
+tab_dpvar 
+```
+
+```{}
 d_dpvar <- as.data.frame(d_dpvar)
@@
 ```{r}
-d_idpvar <- d_migr %>% 
-  select(migr, migr_mo_only, migr_fa_only, migr_both) %>% 
-  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
+d_idpvar <- d_migr |> 
+  select(migr, migr_mo_only, migr_fa_only, migr_both) |> 
+  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |> 
   mutate(`Parental Migration Type` = 0) 
@@
 d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
-d_idpvar <- d_idpvar %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
 ```
@@
 ```{r}
-d_ctvar <- d_migr %>%
-  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
-  child.health.self.rated, child.educational.aspiration, 
+d_ctvar_dit <- d_migr |>
+  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |>
+  mutate_all(as_factor)
+```
+
+```{r}
+d_ctvar_cnt <- d_migr |>
+  select(migr, child.age, child.health.self.rated, child.educational.aspiration, 
   parent.educational.level, parent.expectation.on.child, 
-  home.extracurricular.book, home.economic.resource) %>% 
-  mutate_if(is.numeric, as.factor)
-```
-
-```{r}
-d_ctvar$parent.educational.level <- d_ctvar$parent.educational.level %>% 
-  recode_factor(
-    '1' = 'Primary school and below',
-    '2' = 'Junior high school',
-    '3' = 'Senior high school',
-    '4' = 'Associate college',
-    '5' = 'University',
-    '6' = 'Postgraduate'
-  )
-d_ctvar$child.educational.aspiration <- d_ctvar$child.educational.aspiration %>%
-  recode_factor(
-    '1' = 'Junior high school',
-    '2' = 'Senior high school',
-    '3' = 'Associate college',
-    '4' = 'University',
-    '5' = 'Postgraduate'     
-  )
-d_ctvar$parent.expectation.on.child  <- d_ctvar$parent.expectation.on.child %>%
-  recode_factor(
-    '1' = 'Junior high school',
-    '2' = 'Senior high school',
-    '3' = 'Associate college',
-    '4' = 'University',
-    '5' = 'Postgraduate'    
-  )
-d_ctvar$home.economic.resource <- d_ctvar$home.economic.resource %>% 
-  recode_factor(
-    '1' = 'Very poor',
-    '2' = 'Somewhat poor',
-    '3' = 'Moderate',
-    '4' = 'Somewhat rich',
-    '5' = 'Very rich'
-  )
-d_ctvar$child.health.self.rated <- d_ctvar$child.health.self.rated %>%
-  recode_factor(
-    '1' = 'Very poor',
-    '2' = 'Not very good',
-    '3' = 'Moderate',
-    '4' = 'Good',
-    '5' = 'Very good'
-  )
-d_ctvar$home.extracurricular.book <- d_ctvar$home.extracurricular.book %>%
-  recode_factor(
-    '1' = 'Very few',
-    '2' = 'Not many',
-    '3' = 'Some',
-    '4' = 'Quite a few',
-    '5' = 'A great number'
-  )
-```
-
-```{}
-test.table <- d_ctvar %>%
+  home.extracurricular.book, home.economic.resource)
+```
+
+```{r}
+d_ctvar <- d_ctvar |> 
+  add_value_labels(
+    parent.educational.level = c(
+     'Primary school and below' = 1,
+     'Junior high school' = 2 ,
+     'Senior high school' = 3,
+     'Associate college' = 4,
+     'University' = 5,
+     'Postgraduate' = 6),
+    child.educational.aspiration = c(
+     'Junior high school' = 1 ,
+     'Senior high school' = 2,
+     'Associate college' = 3,
+     'University' = 4,
+     'Postgraduate' = 5),
+    child.educational.aspiration = c(
+     'Junior high school' = 1 ,
+     'Senior high school' = 2,
+     'Associate college' = 3,
+     'University' = 4,
+     'Postgraduate' = 5), 
+    parent.expectation.on.child = c(
+     'Junior high school' = 1 ,
+     'Senior high school' = 2,
+     'Associate college' = 3,
+     'University' = 4,
+     'Postgraduate' = 5),
+    home.economic.resource = c(
+      'Very poor' = 1,
+      'Somewhat poor' = 2,
+      'Moderate' = 3,
+      'Somewhat rich' = 4,
+      'Very rich' = 5),
+    child.health.self.rated = c(
+      'Very poor' = 1,
+      'Somewhat poor' = 2,
+      'Moderate' = 3,
+      'Good' = 4,
+      'Very good' = 5),
+    home.extracurricular.book = c(
+      'Very few' = 1,
+      'Not many' = 2,
+      'Some' = 3,
+      'Quite a few' = 4,
+      'A great number' = 5),
+    )
+```
+
+```{}
+test.table <- d_ctvar |>
   tbl_summary(
@@
   ~migr,
-  data = d_ctvar
+  data = d_ctvar,
+  output = 'markdown'
 )
@@
 
-```{}
-#table_control_variable <- 
-table_balance <- st(
-  d_ctvar,
+```{r}
+tab_ctvar_dit <- 
+  st(
+  data = d_ctvar_dit,
   digits = 2,
@@
   group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = "return"
+  )
+tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
+tab_ctvar_dit[tab_ctvar_dit == 3452|tab_ctvar_dit == 636] <- ''
+```
+
+```{}
+tab_ctvar_cnt <- d_ctvar_cnt |> st(
+  digits = 2, 
+  summ = c('mean(x)', 'sd(x)'),
+  group = 'migr',
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
   out = "return")
-#table_control_variable 
-```
-
-```{r}
+tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
+```
+
+```{}
 table_control_variable <- datasummary_skim(
@@
 ```{r}
-d_migr <- d_migr %>% mutate(`Parental Migration` = ifelse(migr == 1, 'Yes', 'No'))
-d_migr <- d_migr %>% mutate(`Parental Migration Type` = 0) 
-d_migr$`Parental Migration Type`[d_migr$migr==0] <- 'Both Parents At Home'
-d_migr$`Parental Migration Type`[d_migr$migr_mo_only==1] <- 'Only Mother Migrated'
-d_migr$`Parental Migration Type`[d_migr$migr_fa_only==1] <- 'Only Father Migrated'
-d_migr$`Parental Migration Type`[d_migr$migr_both==1] <- 'Both Parents Migrated'
-d_migr <- d_migr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
-```
-
-Whole sample summary
-```{}
-table_sum <- st(
-  d_migr,
+table_sum <- d_ctvar |> st(
+  group = 'migr',
+  summ = c('mean(x)', 'sd(x)'),
   digits = 2, 
-  out = 'kable')
+  out = 'return')
 table_sum
-```
-
-```{}
-table_sum_migr <- st(
-  d_migr,
-  group = 'Parental Migration', 
-  digits = 2, 
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = 'kable')
-table_sum_migr
 ```
@@
 set.seed(1)
-fig_cog <- 
-  ggplot(d_migr, aes(x=`Parental Migration`, y=cog_dif, fill = `Parental Migration`)) + 
+fig_cog <- d_smr |>
+  ggplot(aes(x=`Parental Migration`, y=cog_dif, fill=`Parental Migration`)) + 
     geom_violin()+
@@
     theme(legend.position="none") +
-    ylab("")
+    ylab('Cognitive Test Score Difference') +
+    stat_summary(
+      fun = "mean",
+      geom = "crossbar", 
+      size = 0.4,
+      width = 0.5) +
+  scale_fill_manual(values = alpha(c("green", "red"), .3))
 fig_cog
@@
 set.seed(1)
-fig_ttl <- 
-  ggplot(d_migr, aes(x=`Parental Migration`, y=ttl_dif, fill = `Parental Migration`)) + 
+fig_ttl <-  d_smr |>
+  ggplot(aes(x=`Parental Migration`, y=ttl_dif, fill=`Parental Migration`)) + 
     geom_violin()+
@@
     theme(legend.position="none") +
-    ylab("")
+    ylab('Academic Exam Score Difference') +
+    stat_summary(
+      fun = "mean",
+      geom = "crossbar", 
+      size = 0.4,
+      width = 0.5) +
+  scale_fill_manual(values = alpha(c("green", "red"), .3))
 fig_ttl
@@
 set.seed(1)
-fig_cog_by_migration_type <-
-  ggplot(d_migr, aes(x=`Parental Migration Type`, y=cog_dif, fill = `Parental Migration Type`)) + 
+fig_cog_by_migration_type <- d_smr |>
+  ggplot(aes(x=`Parental Migration Type`, y=cog_dif)) + 
     geom_violin()+
@@
     theme(legend.position="none") +
-    ylab("")
+    ylab('Cognitive Test Score Difference') +
+    stat_summary(
+      fun = "mean",
+      geom = "crossbar", 
+      width = 0.5)
 fig_cog_by_migration_type
@@
 set.seed(1)
-fig_ttl_by_migration_type <-
-  ggplot(d_migr, aes(x=`Parental Migration Type`, y=ttl_dif, fill = `Parental Migration Type`)) + 
+fig_ttl_by_migration_type <- d_smr |>
+  ggplot(aes(x=`Parental Migration Type`, y=ttl_dif)) + 
     geom_violin()+
@@
     theme(legend.position="none") +
-    ylab("")
+    ylab('Academic Exam Score Difference') +
+    stat_summary(
+      fun = "mean",
+      geom = "crossbar", 
+      width = 0.5)
 fig_ttl_by_migration_type
@@
 models_cog <- list(
-'Any Parent Absent' = did_cog,
-'Only Mother Absent' = did_cog_m_only,
-#'Mother Absent' = #did_cog_m,
-'Only Father Absent' = did_cog_f_only,
-#'Father Absent' = #did_cog_f,
-'Both Parents Absent' = did_cog_both) 
+'Any Parent Migrated' = did_cog,
+'Only Mother Migrated' = did_cog_m_only,
+#'Mother Migrated' = #did_cog_m,
+'Only Father Migrated' = did_cog_f_only,
+#'Father Migrated' = #did_cog_f,
+'Both Parents Migrated' = did_cog_both) 
 ```
@@
 stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
-coef_rename <- c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score", "w1ttl_100" = "W1 score")
-title_cog <- 'Parental migration’s effect on children’s cognitive abilities'
-title_ttl <- 'Parental migration’s effect on children’s academic abilities'
+coef_rename <- c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "cog3pl" = "W1 score", "w1ttl_100" = "W1 score")
+title_cog <- 'Parental migration’s effect on children’s cognitive test score'
+title_ttl <- 'Parental migration’s effect on children’s academic exam score'
 gof_omit <- 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
-```
-
-```{r}
-table_cog <- models_cog %>% msummary(
+note_unadj <- 'Control variables not included'
+```
+
+```{r}
+table_cog <- models_cog |> msummary(
   stars =  stars,
@@
   coef_rename =  coef_rename,
+  notes = note_unadj,
   output = 'markdown')
@@
 models_ttl <- list(
-'Any Parent Absent' = did_ttl,
-'Only Mother Absent' = did_ttl_m_only,
-#'Mother Absent' = #did_ttl_m,
-'Only Father Absent' = did_ttl_f_only,
-#'Father Absent' = #did_ttl_f,
-'Both Parents Absent' = did_ttl_both) 
-```
-
-```{r}
-table_ttl <- models_ttl %>% msummary(
+'Any Parent Migrated' = did_ttl,
+'Only Mother Migrated' = did_ttl_m_only,
+#'Mother Migrated' = #did_ttl_m,
+'Only Father Migrated' = did_ttl_f_only,
+#'Father Migrated' = #did_ttl_f,
+'Both Parents Migrated' = did_ttl_both) 
+```
+
+```{r}
+table_ttl <- models_ttl |> msummary(
   stars =  stars,
@@
   coef_rename =  coef_rename, 
+  notes = note_unadj,
   output = 'markdown')
@@
 models_ttl_z <- list(
-'Any Parent Absent' = did_ttl_z,
-'Only Mother Absent' = did_ttl_z_m_only,
-#'Mother Absent' = did_ttl_z_m,
-'Only Father Absent' = did_ttl_z_f_only,
-#'Father Absent' = did_ttl_z_f,
-'Both Parents Absent' = did_ttl_z_both) 
-table_ttl_z <- models_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+'Any Parent Migrated' = did_ttl_z,
+'Only Mother Migrated' = did_ttl_z_m_only,
+#'Mother Migrated' = did_ttl_z_m,
+'Only Father Migrated' = did_ttl_z_f_only,
+#'Father Migrated' = did_ttl_z_f,
+'Both Parents Migrated' = did_ttl_z_both) 
+table_ttl_z <- models_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
 table_ttl_z
@@
 models_ttl_std <- list(
-'Any Parent Absent' = did_ttl_std,
-'Only Mother Absent' = did_ttl_std_m_only,
-#'Mother Absent' = did_ttl_std_m,
-'Only Father Absent' = did_ttl_std_f_only,
-#'Father Absent' = did_ttl_std_f,
-'Both Parents Absent' = did_ttl_std_both) 
-table_ttl_std <- models_ttl_std %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+'Any Parent Migrated' = did_ttl_std,
+'Only Mother Migrated' = did_ttl_std_m_only,
+#'Mother Migrated' = did_ttl_std_m,
+'Only Father Migrated' = did_ttl_std_f_only,
+#'Father Migrated' = did_ttl_std_f,
+'Both Parents Migrated' = did_ttl_std_both) 
+table_ttl_std <- models_ttl_std |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
-                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
 table_ttl_std
@@
 models_adj_cog <- list(
-'Any Parent Absent' = did_adj_cog,
-'Only Mother Absent' = did_adj_cog_m_only,
-#'Mother Absent' = #did_adj_cog_m,
-'Only Father Absent' = did_adj_cog_f_only,
-#'Father Absent' = #did_adj_cog_f,
-'Both Parents Absent' = did_adj_cog_both) 
-```
-
-```{r}
-table_adj_cog <- models_adj_cog %>% msummary(
+'Any Parent Migrated' = did_adj_cog,
+'Only Mother Migrated' = did_adj_cog_m_only,
+#'Mother Migrated' = #did_adj_cog_m,
+'Only Father Migrated' = did_adj_cog_f_only,
+#'Father Migrated' = #did_adj_cog_f,
+'Both Parents Migrated' = did_adj_cog_both) 
+```
+
+```{r}
+table_adj_cog <- models_adj_cog |> msummary(
+  stars =  stars,
+  fmt = 2,
+  title = title_cog,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  output = 'markdown'
+  )
+table_adj_cog
+```
+
+Regressing on total exam score
+```{r}
+did_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+#did_adj_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+```
+
+Results
+```{r}
+models_adj_ttl <- list(
+'Any Parent Migrated' = did_adj_ttl,
+'Only Mother Migrated' = did_adj_ttl_m_only,
+#'Mother Migrated' = #did_adj_ttl_m,
+'Only Father Migrated' = did_adj_ttl_f_only,
+#'Father Migrated' = #did_adj_ttl_f,
+'Both Parents Migrated' = did_adj_ttl_both)
+```
+
+```{r}
+table_adj_ttl <- models_adj_ttl |> msummary(
   stars =  stars,
@@
   )
-table_adj_cog
-```
-
-Regressing on total exam score
-```{r}
-did_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-```
-
-Results
-```{r}
-models_adj_ttl <- list(
-'Any Parent Absent' = did_adj_ttl,
-'Only Mother Absent' = did_adj_ttl_m_only,
-#'Mother Absent' = #did_adj_ttl_m,
-'Only Father Absent' = did_adj_ttl_f_only,
-#'Father Absent' = #did_adj_ttl_f,
-'Both Parents Absent' = did_adj_ttl_both)
-```
-
-```{r}
-table_adj_ttl <- models_adj_ttl %>% msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_ttl,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  output = 'markdown'
-  )
 table_adj_ttl
@@
 models_adj_ttl_z <- list(
-'Any Parent Absent' = did_adj_ttl_z,
-'Only Mother Absent' = did_adj_ttl_z_m_only,
-#'Mother Absent' = did_adj_ttl_z_m,
-'Only Father Absent' = did_adj_ttl_z_f_only,
-#'Father Absent' = did_adj_ttl_z_f,
-'Both Parents Absent' = did_adj_ttl_z_both) 
-table_adj_ttl_z <- models_adj_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+'Any Parent Migrated' = did_adj_ttl_z,
+'Only Mother Migrated' = did_adj_ttl_z_m_only,
+#'Mother Migrated' = did_adj_ttl_z_m,
+'Only Father Migrated' = did_adj_ttl_z_f_only,
+#'Father Migrated' = did_adj_ttl_z_f,
+'Both Parents Migrated' = did_adj_ttl_z_both) 
+table_adj_ttl_z <- models_adj_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
 table_adj_ttl_z
@@
 models_adj_ttl_dm <- list(
-'Any Parent Absent' = did_adj_ttl_dm,
-'Only Mother Absent' = did_adj_ttl_dm_m_only,
-#'Mother Absent' = did_adj_ttl_dm_m,
-'Only Father Absent' = did_adj_ttl_dm_f_only,
-#'Father Absent' = did_adj_ttl_dm_f,
-'Both Parents Absent' = did_adj_ttl_dm_both) 
-table_adj_ttl_dm <- models_adj_ttl_dm %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+'Any Parent Migrated' = did_adj_ttl_dm,
+'Only Mother Migrated' = did_adj_ttl_dm_m_only,
+#'Mother Migrated' = did_adj_ttl_dm_m,
+'Only Father Migrated' = did_adj_ttl_dm_f_only,
+#'Father Migrated' = did_adj_ttl_dm_f,
+'Both Parents Migrated' = did_adj_ttl_dm_both) 
+table_adj_ttl_dm <- models_adj_ttl_dm |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
 table_adj_ttl_dm
@@
 ```{r}
-d_mo_only <- d_cl %>% drop_na(migr_mo_only)
+d_mo_only <- d_cl |> drop_na(migr_mo_only)
 m.out_mo_only <- 
@@
 ```{r}
-d_fa_only <- d_cl %>% drop_na(migr_fa_only)
+d_fa_only <- d_cl |> drop_na(migr_fa_only)
 m.out_fa_only <- matchit(
@@
 ```{r}
-d_both <- d_cl %>% drop_na(migr_both) 
+d_both <- d_cl |> drop_na(migr_both) 
 m.out_both <- matchit(
@@
 ```{}
-d_mo <- d_cl %>% drop_na(migr_mo)
+d_mo <- d_cl |> drop_na(migr_mo)
 m.out_mo <- matchit(
@@
 ```{}
-d_fa <- d_cl %>% drop_na(migr_fa)
+d_fa <- d_cl |> drop_na(migr_fa)
 m.out_fa <- matchit(
@@
 ```{r}
-title_cog_matching <- 'Parental migration’s effect on children’s cognitive abilities, estimated with matching'
-title_ttl_matching <- 'Parental migration’s effect on children’s academic abilities, estimated with matching'
+title_cog_matching <- 'Parental migration’s effect on children’s cognitive test scores, estimated with matching'
+title_ttl_matching <- 'Parental migration’s effect on children’s academic exam scores, estimated with matching'
 note_matching <- "3:1 nearest neighbor propensity score matching with replacement; exact matching by county"
@@
 models_m_cog <- list(
-'Any Parent Absent' = didm_cog,
-'Only Mother Absent' = didm_cog_mo_only,
-##'Mother Absent' = #did_adj_cog_m,
-'Only Father Absent' = didm_cog_fa_only,
-##'Father Absent' = #did_adj_cog_f,
-'Both Parents Absent' = didm_cog_both) 
-```
-
-```{r}
-table_m_cog <- models_m_cog %>% msummary(
+'Any Parent Migrated' = didm_cog,
+'Only Mother Migrated' = didm_cog_mo_only,
+##'Mother Migrated' = #did_adj_cog_m,
+'Only Father Migrated' = didm_cog_fa_only,
+##'Father Migrated' = #did_adj_cog_f,
+'Both Parents Migrated' = didm_cog_both) 
+```
+
+```{r}
+table_m_cog <- models_m_cog |> msummary(
   stars =  stars,
@@
 models_m_ttl <- list(
-'Any Parent Absent' = didm_ttl,
-'Only Mother Absent' = didm_ttl_mo_only,
-##'Mother Absent' = #did_adj_ttl_m,
-'Only Father Absent' = didm_ttl_fa_only,
-##'Father Absent' = #did_adj_ttl_f,
-'Both Parents Absent' = didm_ttl_both) 
-table_m_ttl <- models_m_ttl %>% msummary(
+'Any Parent Migrated' = didm_ttl,
+'Only Mother Migrated' = didm_ttl_mo_only,
+##'Mother Migrated' = #did_adj_ttl_m,
+'Only Father Migrated' = didm_ttl_fa_only,
+##'Father Migrated' = #did_adj_ttl_f,
+'Both Parents Migrated' = didm_ttl_both) 
+table_m_ttl <- models_m_ttl |> msummary(
   stars =  stars,
@@
 models_m_adj_cog <- list(
-'Any Parent Absent' = didm_adj_cog,
-'Only Mother Absent' = didm_adj_cog_mo_only,
-##'Mother Absent' = #did_adj_cog_m,
-'Only Father Absent' = didm_adj_cog_fa_only,
-##'Father Absent' = #did_adj_cog_f,
-'Both Parents Absent' = didm_adj_cog_both) 
-table_m_adj_cog <- models_m_adj_cog %>% msummary(
+'Any Parent Migrated' = didm_adj_cog,
+'Only Mother Migrated' = didm_adj_cog_mo_only,
+##'Mother Migrated' = #did_adj_cog_m,
+'Only Father Migrated' = didm_adj_cog_fa_only,
+##'Father Migrated' = #did_adj_cog_f,
+'Both Parents Migrated' = didm_adj_cog_both) 
+table_m_adj_cog <- models_m_adj_cog |> msummary(
   stars =  stars,
@@
 models_m_adj_ttl <- list(
-'Any Parent Absent' = didm_adj_ttl,
-'Only Mother Absent' = didm_adj_ttl_mo_only,
-##'Mother Absent' = #did_adj_ttl_m,
-'Only Father Absent' = didm_adj_ttl_fa_only,
-##'Father Absent' = #did_adj_ttl_f,
-'Both Parents Absent' = didm_adj_ttl_both) 
-table_m_adj_ttl <- models_m_adj_ttl %>% msummary(
+'Any Parent Migrated' = didm_adj_ttl,
+'Only Mother Migrated' = didm_adj_ttl_mo_only,
+##'Mother Migrated' = #did_adj_ttl_m,
+'Only Father Migrated' = didm_adj_ttl_fa_only,
+##'Father Migrated' = #did_adj_ttl_f,
+'Both Parents Migrated' = didm_adj_ttl_both) 
+table_m_adj_ttl <- models_m_adj_ttl |> msummary(
   stars =  stars,
@@
 ```{r}
-d_cl1 <- d_cl %>% mutate(
+d_cl1 <- d_cl |> mutate(
   home.economic.resource.w2 = if_else(is.na(w2be23), w2a09, w2be23)
-)
-d_cl1 <- d_cl %>% mutate(
+) |> mutate(
   fin.better = if_else(home.economic.resource.w2 > home.economic.resource,
@@
 ```{r}
-feols(ttl_dif ~ migr*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) %>%
+feols(ttl_dif ~ migr*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
-feols(cog_dif ~ migr*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  %>%
+feols(cog_dif ~ migr*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
-```
-
-```{r}
-feols(ttl_dif ~ migr*fin.better + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+feols(ttl_dif ~ migr_mo_only*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
-feols(cog_dif ~ migr*fin.better + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+feols(cog_dif ~ migr_mo_only*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
-```
-
-```{r}
-d_cl1=d_cl1 %>% mutate(
-  supervision.less = if_else((b2201 + b2202) > (w2a18 + w2a19), 1, 0)
-)
-```
-
-```{r}
-feols(ttl_dif ~ migr*supervision.less + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+feols(ttl_dif ~ migr_fa_only*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
-feols(cog_dif ~ migr*supervision.less + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) %>%
+feols(cog_dif ~ migr_fa_only*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
            output = 'markdown')
+feols(ttl_dif ~ migr_both*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
+  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr_both*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
+  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+```
+
+```{r}
+feols(ttl_dif ~ migr*fin.better + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr*fin.better + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+```
+
+```{r}
+d_cl1=d_cl1 |> mutate(
+  supervision.less = if_else((w2a18 + w2a19) < (b2201 + b2202), 1, 0)
+)
+```
+
+```{r}
+feols(ttl_dif ~ migr*supervision.less + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
+feols(cog_dif ~ migr*supervision.less + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           output = 'markdown')
 ```

### 2022-07-03 MScThesisText.Rmd
almost there

--- 2022-06-25 MScThesisText.Rmd
@@
 ---
-title             : "Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
+title             : "Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
 shorttitle        : "Left-Behind Children"
@@
 abstract: |
-  Millions of children worldwide are "left behind" when their parents migrate away for work. 
-  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance. 
-  To what extent do different arrangements of parental migration affect children's schooling performance in the short term? 
+  Millions of children worldwide are "left behind" at home communities as their parents migrate away for work. 
+  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on children's educational attainment. 
+  To what extent do different arrangements of parental migration affect children's educational performance in the short term? 
   Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey. 
   I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
-  I measured children's educational performance by standardized cognitive test score and academic exam grades.
+  I measured children's schooling performance by cognitive test scores and academic exam grades.
   For causal inference, I built difference-in-differences models with propensity score matching. 
-  Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers. 
-  Father-only migration is negatively associated with children’s cognitive abilities, while mother-only migration is negatively associated with children’s academic grades.
+  Results show that the newly left-behind children's performance at school dropped slightly compared to that of non-left-behind peers. 
+  Mother-only migration is negatively associated with children’s academic grades and cognitive abilities. 
+  Father-only migration is negatively associated with children’s cognitive abilities, but its magnitude is greater than mother-only migration.
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "labor migration, left-behind children, educational performance"
+wordcount         : "6,600"
 
 floatsintext      : yes
-linenumbers       : yes
+linenumbers       : no
 draft             : no
@@
 
+    \usepackage{float}
+    \usepackage{booktabs}
+    \usepackage{siunitx}
+    \usepackage{setspace}
+    \onehalfspacing
+
 csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
@@
 output            : papaja::apa6_pdf
-
+appendix: 
+  - "appendix.Rmd"
+  - "appendix-b.Rmd"
 bibliography: references.bib
@@
 library("cobalt")
+library("kableExtra")
+library("modelsummary")
 r_refs("references.bib")
@@
 
-Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Globally, millions of children reside in their home communities but live apart from their parents as either one or both parents have migrated for work.
 These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
-In a 2021 resolution, the Council of Europe's @parliamentaryassembly2021a expressed concern about "the scale of this phenomenon and the long-term damage it creates" (p.
-2) and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights" (p.
-1).
+Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were separated from their migrating parents [@nbs2017].
+The issue of left-behind children has caught the attention of policymakers and legislators.
+In a resolution, the Council of Europe's @parliamentaryassembly2021 expressed concern about "the scale of this phenomenon and the long-term damage it creates" and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights".
 
-How are stay-behind children faring when parents have migrated?
-Research results are mixed due to the differential effects of parental migration.
+How are stay-behind children faring in the absence of parents?
+Research findings are mixed due to the differential effects of parental migration.
 Consider children's education.
 According to the review articles by @debrauw2019 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
-The inflow of remittances, however, cannot substitute for the loss of parental care.
+To what degree can the inflow of remittances compensate for the loss of parental attention?
 Parental migration decreases the amount and quality of parental guidance, protection, and support.
-It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
+It is uncertain how these two opposing effects together shape children's educational performance.
+This uncertainty merits empirical investigation.
 
-A challenge arises in assessing the causality between parent's migration and children's educational achievement.
-Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+A challenge arises in estimating the effect of parent's migration on children's educational achievement.
+Experiments can unveil causal relations.
+It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
 Alternatively, a quasi-experimental design can help with causal inference.
-The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
+It requires that the cause br on par with random assignment to participants, conditional on identification assumptions [@cunningham2021].
 
 In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyzed data from a two-wave panel survey.
+I choose China as the case and analyze data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
-The outcome was measured with children's cognitive test score and academic exam scores.
+I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness checks.
+The outcome was measured with children's cognitive test score and academic exam grade.
 I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
 
-\newpage
+## China's Context
 
-# Literature Review
+Three features make China a suitable case for studying left-behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers.
+They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind [@nbs2022; @nbs2017].
 
-## Theoretical Framework
+The internal migration stemmed from the neoliberal economic regime.
+Scholars like @duckett2020 and @zhan2020 argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
+In the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
+Since then, China has integrated in the global economy and contributed substantial growth to it.
+The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
+The rural hinterlands, however, have lagged behind.
+Simultaneously, many people have left the countryside for the city.
+The regional inequality needs social policy to amend.
+But China's welfare program, as @qian2021 argued, is fragmented and stratified.
+Those who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
+As rural migrants arrive in the city, they find themselves with limited access to social welfare, such as health care and children's education [@qian2021].
+The welfare system's exclusion of rural migrants means that the state shifts its responsibility to individuals, resembling the neoliberal governmentality [@zhan2020].
+
+The institutionalized discrimination against rural migrants finds its roots in China's "multilevel citizenship" system.
+As @vortherms2021 explained, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through the *hukou*, or household registration system:
+
+> A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
+Accessing fundamental citizenship rights depends on your registration status ...
+Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
+[@vortherms2021]
+
+In other words, the hukou system binds one's citizenship rights with one's place of registry.
+In theory, Chinese citizens can migrate freely within the country.
+In practice, they cannot change hukou freely.
+When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2022].
+Migrant workers have organized petitions, strikes, and protests.
+These actions often fell on deaf ears and sometimes even ended with police crackdown [@chan2019].
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
+
+How does China counter the issue of labor migration and left-behind children?
+According to @wang2020 and @zhang2018, the government has gradually liberalized the multilevel citizenship scheme.
+It has introduced residence permit for internal migrants as the basis for social entitlements.
+First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
+Criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
+This parallels how European states differentially incorporate foreign immigrants into national welfare regimes [@zhang2018].
+Another policy response, as stated by @roberts2018, is the centralized boarding schools.
+The Ministry of Education promotes boarding schools in the rural county-seats.
+These schools serve as a cost-efficient way to enroll students in surrounding villages and to look after the left-behind children.
+In reality, such schools "are often ill-equipped to ensure the healthy upbringing and psychological wellbeing of children" (p.
+6).
+
+Social scientists have researched extensively about China's left-behind children, but the current literature still has three major shortcomings.
+The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
+My sample includes urban left-behind children as well.
+The second shortcoming lies in sampling and research design.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021].
+Others only estimated correlation using cross-sectional data [@akezhuoli2022; @jin2020; @huang2020].
+These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+The third shortcoming lies in the measurement of outcome.
+@chang2019 and @wang2019 measured students' educational performance with the standardized test score of only one academic subject, namely mathematics.
+To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
+I included the test results of multiple subjects to measure comprehensive academic achievement.
+
+## Theory and Hypotheses
 
@@
 Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
-@yang2008 noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
+@yang2008 noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
 This subsequently boosted children's school enrollment and educational expenditure.
+@cebotari2020 developed a fixed effect model with three-wave panel data collected in Ghana.
+He found that stay-behind children's education benefits from "the steady inflow of both in-kind and monetary remittances" contributed by migrant parents.
 In China, @chang2019 interviewed migrant workers and their family members.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+@peng2018 interviewed first-generation migrant mothers whose initial migration dated back to the 1990s.
+To them, "good mothering" primarily means offering economic support for their children in education, which can help their children climb the ladder of success.
 
@@
 Children flourish under parental nurturing care.
-This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
+This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.
+1].
 Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@wen2019].
@@
 14).
+Similarly, @murphy2022 talked to left-behind adolescents at a village.
+Some of them "embraced the 'left-behind' label" because it captured their need for more parental care (p.
+185), "especially companionship and affection in daily life" (p.
+186).
 
-Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
-@botezat2020 studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
-@wang2019 collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+Given the two opposing effects, researchers have obtained mixed results on how parental migration impacts children's education.
+@botezat2020 adopted past immigration rate as an instrumental variable.
+They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
+@wang2019 collected data from junior high school students in central China.
+The researchers' two-way fixed-effect model showed no effect of parental on left-behind children's achievement in mathematical test.
 Studying four Chinese provinces, @debrauw2017 showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-@nguyen2016 demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+@nguyen2016 conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
 
@@
 
-$H_1$ In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
+$H_1$ In the short term, parental migration reduces the educational performance of children left-behind.
 
-Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
+$H_1a$ In the short term, parental migration negatively affects left-behind children's cognitive test score.
+
+$H_1b$ In the short term, parental migration negatively affects left-behind children's academic exam score.
+
+Researchers have studied whether the impact differ between mother's migration and father's migration.
 @xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
@@
 
-Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
-Under such norms, children are more likely to accept fathers' migration than mothers' [@murphy2022].
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
+Scholars like @murphy2020 noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles [@murphy2020].
 I propose the second hypothesis:
 
-$H_2$ In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
+$H_2$ In the short term, mother's migration more negatively affect the educational performance of children left-behind than do father's migration.
 
-## China's Context
+$H_2a$ In the short term, mother's migration more negatively affect left-behind children's cognitive test score than do father's migration.
 
-Three features make China a suitable case for studying left-behind children.
-The first feature is the huge scale of internal labor migration.
-According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The number of left-behind Chinese children reached 68.7 million in 2015 [@nbs2017].
-The internal migration stemmed from the neoliberal economic regime.
-
-The neoliberal economic regime sounds at odds with China, a so-called socialist country.
-Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the global economy and contributed substantial growth to it.
-The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
-The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
-As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
-The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere [@duckett2020; @zhang2018].
-
-The institutionalized discrimination against migrant laborers find its roots in China's "multilevel citizenship" system.
-As @vortherms2021 demonstrated, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the *hukou*, or household registration system:
-
-> A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status ...
-Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-[@vortherms2021]
-
-In other words, the hukou system binds one's citizenship rights with one's place of registry.
-In theory, anyone can move out of town freely.
-In practice, they cannot change hukou freely.
-When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2021].
-Migrant workers had organized petitions, strikes, and protests, only to fall on deaf ears or even end with police crackdown [@chan2017].
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
-
-The existing research about China's left-behind children has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
-My sample includes urban left-behind children as well.
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021].
-Others only estimated correlation using cross-sectional data [@akezhuoli2022; @jin2020].
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-The third shortcoming lies in the measurement of outcome.
-@chang2019 and @wang2019 measured students' educational performance with the test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
+$H_2b$ In the short term, mother's migration more negatively affect left-behind children's academic exam score than do father's migration.
 
@@
 It is a nationally representative, school-based survey featuring junior high school students.
-The survey administrator is the National Survey Research Center at Renmin University of China.
+Currently, two waves of data are available.
+The CEPS team operates under the National Survey Research Center at the Renmin University of China.
 The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
-The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
-These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
-The follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed `r printnum(nrow(d))` of the seventh grade cohort.
-I further restricted the sample to students staying with both parents at the original domicile at the baseline survey.
-To deal with missing values, I adopted list-wise deletion for dependent, independent, and control variables.
-The final sample size amounted to `r printnum(nrow(d_cl))` .
+The baseline survey (wave one) took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
+These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter 'counties').
+The follow-up survey (wave two) in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed `r printnum(nrow(d))` of the seventh grade cohort.
+I further restricted the sample to students living with both parents at the original domicile at the baseline survey.
+To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
+The final sample size amounts to `r printnum(nrow(d_cl))`.
 
@@
 I explored two categories of educational performance: cognitive and academic abilities.
-One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
+One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test administered by the CEPS research team.
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one [@wang2015].
+The baseline and follow-up tests consisted of 20 and 35 items, respectively.
+The raw score was calculated based on the Item Response Theory [@wang2015].
+I transformed the raw scores to the 100-point scale.
+I chose the raw score instead of the z-score, as z-standardization fails to document the change of mean between time points, which is also of interest [@moeller2015].
 
 Another dependent variable concerned students' academic performance.
-This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
+This was measured by the average scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
 Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
-This is related to how junior high schools operate as part of the compulsory education system in China.
+This is related to how junior high schools operate within the compulsory education system in China.
 According to @oecd2016, China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
-At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
+At school, the subjects of Chinese, mathematics, and English are core subjects and others as supplementary subjects.
 Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
@@
 I transformed the exam grades through the following steps.
-I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
-After the conversion, I checked for abnormal values outside the 0-100 range.
+I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) with the 100-point scale.
+After the conversion, I checked for abnormal values lower than zero or higher than one hundred.
 `r printnum(num.outlier$n)` observations were outliers, accounting for less than one percent of the sample.
-I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
-In this way, I can limit the impact of outliers while retaining these observations in the sample.
-After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
+I retained these observations in the sample and trimmed the subject exam scores.
+The trimming ensured that all values would be within the 0-100 range.
+In this way, I can limit the impact of outliers.
+Finally, I calculated the average score of these three subjects.
 
@@
 In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
-I constructed four treatment dummy variables measuring migration arrangements: any parents absent, only father absent, only mother absent, and both parents absent.
+I constructed four treatment dummy variables measuring migration arrangements: any parents migrated, only father migrated, only mother migrated, and both parents migrated.
 These arrangements are mutually exclusive.
@@
 
-The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
+The control variables on children's level include age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
+The lists of covariates are in Tables 3-5 in the Results section.
 
-## Data analysis
+## Analytical Strategy
 
-I adopted `R` for all the analyses, the `fixest` package for econometric modeling [@berge2022], and the `modelsummary` package for presenting the results [@arel-bundock2022].
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j,k;1}$ is the test score at baseline, and $C_{j}$ and $C_{k}$ are the classroom fixed-effects at baseline and follow-up, respectively.
-Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
-About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
-This necessitates adding the wave-two classroom fixed-effect.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \varepsilon_{i,j}$$ For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
+School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in the same school are also in the same county.
+An alternative is to use a class fixed-effect to control for time-invariant factors in the classroom.
+However, about one-sixth of the students were reassigned into new classes at the end of baseline academic year.
+As the reassignment of classroom will complicate the model, I ruled out the classroom fixed-effect.
 
-The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The DID model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
 The model is unadjusted as it does not adjust for additional covariates.
@@
 
-In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \theta \cdot X_{i} + \varepsilon_{i,j}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
 This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
+
+I adopted `R` (version 4.2.0) for all the analyses [@R-base].
+This involved the following packages: `tidyverse` (version 1.3.1) for data cleaning [@R-tidyverse]; `fixest` (version 0.10.4) for econometric modeling [@R-fixest]; `MatchIt` (version 4.4.0) and `cobalt` (version 4.3.2) for matching [@R-MatchIt; @R-cobalt]; `modelsummary` (version 1.0.0), `vtable` (version 1.3.3), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.0) for typesetting [@R-papaja].
 
@@
 
-Table 1 below summarizes the changes in migration status in the sample.
-All `r printnum(nrow(d_cl))` children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
-In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
+Table 1 summarizes the independent variables, namely the migration status reported in the wave two survey.
+All `r printnum(nrow(d_cl))` children were living with parents in one household in baseline, but about fifteen percent saw at least one parent migrated between the two waves of survey.
+I call these students "newly left-behind children" and their households "new migration households." In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
 The remaining one-fifth was both-parents migration.
 
-```{r i-var}
-table_independent_variable
+\renewcommand{\arraystretch}{0.72}
+
+```{r}
+datasummary_df(
+  data = tab_idpvar,
+  output = 'latex',
+  title = 'Independent variables by parental migration'
+)
 ```
 
-: Parental migration status at follow-up survey.
+\newpage
 
-Tables 2 and 3 below provide the whole-sample summary statistics.
-In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
+The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figures B1-B4 in the appendix.
+Compared to non-left-behind peers, newly left-behind children score lower in wave two's cognitive and academic tests; Their cognitive test score increases less and their academic exam score drops more.
+T-tests show that for the baseline outcomes, the differences of the mean values between-group are probably due to chance.
+For the wave two outcomes and the between-wave changes, the differences of the mean value are statistically significant.
 
-```{r d-var}
-table_dependent_variable
+```{r}
+tab_dpvar |> 
+  kbl(booktabs = T, caption = 'Dependent variables by parental migration', row.names = F) |>
+  add_indent(c(2,3,5,6)) |>
+  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
 ```
 
-: The independent variables
+\newpage
 
-```{r c-var}
-table_control_variable
+Table 3 summarizes the bivariate analysis on the binary control variables.
+New migration households have lower internet access rate.
+Among the newly left-behind children, male sex, past grade retention, and boarding at school were more common compared to the non-left-behind peers.
+Chi-square tests show that these differences in variance are unlikely due to chance.
+
+```{r}
+tab_ctvar_dit |>
+  kbl(booktabs = T, caption = 'Dichotomous control variables by parental migration', row.names = F) |>
+  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
 ```
 
-: The control variables
+\newpage
+
+Table 4 presents the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
+While the majority of mothers and fathers have only finished high school or below, they hold big expectations for children.
+Eight out of ten parents wish that their children complete university education.
+Scholars like @willis2019 explained this pattern with the Chinese social norms and cultural traditions.
+In ancient China, the Confucian teaching emphasized the cultivation of personhood through learning, diligence, and persistence.
+In real life, knowledge could translate into power and privilege.
+Ordinary people could study for the highly competitive *keju* (civil service examination).
+As the world's "earliest meritocratic institution," this exam system recruited top performers into the imperial government and the elite class [@chen2020, p.
+2030].
+Nowadays in China, the emperor and *keju* are long gone, but the influences are long-lasting.
+Chinese parents hope that their children receive the best education to secure a decent career [@luo2013; @ng2020].
+
+```{r}
+tab_ctvar_cnt |>
+  kbl(booktabs = T, caption = 'Categorical and continuous control variables by parental migration', row.names = F) |>
+  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "Parental Migration" = 4)) |>
+  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
+```
+
+\newpage
+
+```{r}
+datasummary_df(
+  data = tab_var,
+  title = 'Measurement of categorical variables',
+  output = 'latex'
+)
+```
+
+\newpage
 
@@
 
-The unrestricted DID models support my hypothesis one -- newly left-behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left-behind counterparts.
-If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to `r round(coef(did_cog)[1],2)` SD in cognitive test score and `r round(coef(did_cog)[1],2)` points in academic exam grades.
-Both relationships are slight in strength.
-
-The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
-This holds true for academic abilities.
-Children from only mother migrate households are associated with `r round(coef(did_cog_m_only)[1],2)` points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
-Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left-behind children.
-Children with only father absent are associated with (`r round(coef(did_cog_f_only)[1],2)` SD), and both parents absent (`r round(coef(did_cog_both)[1],2)` SD) compared to the non left-behind children.
+I first present the results on children's cognitive test score.
+According to the unadjusted DID models (see Table 6 below), newly left-behind adolescents are more likely to score lower in cognitive tests than their non-left-behind counterparts, lending support to Hypothesis 1a.
+Parental migration is linked to a `r coef(did_cog)[1] |> abs() |> round(2)` points decrease in cognitive test score.
+Hypothesis 2a is only partially supported.
+Compared with the non-left-behind children, children with only father absent are associated with greater decrease (`r coef(did_cog_f_only)[1] |> abs() |> round(2)` points) in cognitive test score than those with only mother absent (`r coef(did_cog_m_only)[1] |> abs() |> round(2)` points).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (See Table A1 in appendix).
+That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
 
@@
 
+Next, I show the results on children's academic test grades.
+In line with Hypothesis 1b, the unadjusted DID models (see Table 7 below) show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers.
+Parental migration is associated with a drop of `r coef(did_ttl)[1] |> abs() |> round(2)` points in academic exam score.
+Hypothesis 2b finds partial support.
+The exam grade of only-mother-migrated children sees a `r coef(did_ttl_m_only)[1] |> abs() |> round(2)` points decrease relative to non-left-behind counterparts.
+In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
+The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in appendix).
+Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
+
+\newpage
+
 ```{r reg-ttl}
@@
 
-The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
-That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
+Some predictors are strong in both models of cognitive and academic abilities.
+These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
+One year older in age is associated with decreases of `r coef(did_adj_cog)[3] |> abs() |> round(2)` points for cognitive test and of `r coef(did_adj_ttl)[3] |> abs() |> round(2)` points for academic exam.
+Preschool attendance is linked to increases of `r round(coef(did_adj_cog)[8],2)` points for cognitive test and of `r round(coef(did_adj_ttl)[8],2)` points for academic exam.
+Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
+The coefficients are `r round(coef(did_adj_cog)[15],2)` points and `r round(coef(did_adj_cog)[12],2)` points for cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
 
-Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational aspiration as well as parents' expectation on children.
-In terms of age, the older students' scores drop relatively more than younger students'.
-One year older in age is associated with `r round(coef(did_adj_cog)[3],2)` SD for standardized cognitive test and `r round(coef(did_adj_ttl)[3],2)` points for academic exams.
-Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
-The effect sizes are `r round(coef(did_adj_cog)[15],2)` SD and `r round(coef(did_adj_cog)[12],2)` SD for standardized cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
-
-Several predictors are strong in the model of academic grades but not in that of cognitive scores.
-These are children's gender and self-reported health, and the years of parental education.
+Several predictors are strong in predicting one outcome but not the other.
+Covariates related to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
 Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive test.
 Students who consider themselves healthier are associated with higher scores in academic exams.
-Parents with more education are associated with their children's higher scores in academic exams.
-If the years of parental education of the best-educated among the two increase by one, it would be linked to a `r round(coef(did_adj_ttl)[14],2)` points increase in the child's academic exam grade.
-These three predictors are not significant for cognitive outcomes.
+On the contrary, students who perceive their households having more extracurricular books are associated with lower scores in academic exams.
+Covariates related to cognitive scores is the number of siblings.
+Having an additional sibling is associated with lower cognitive score of `r coef(did_adj_cog)[7] |> abs() |> round(2)` points, but its effect for academic grade is not significant statistically.
 
-Preschool attendance is associated with higher cognitive outcomes `r round(coef(did_adj_cog)[8],2)` SD, but its effect for academic outcomes is not significant.
-
-```{r reg-cog-adj}
-table_adj_cog
-```
-
-```{r reg-ttl-adj}
-table_adj_ttl
-```
+\newpage
 
@@
 Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
+A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
 Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
 To tackle the selection bias herein, an applicable technique is matching.
-This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+It makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@greifer2022].
 
-Popular choices for matching include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
-As @greifer2022 introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
-The eligibility as the "closest" can be determined with the differences in propensity score.
-Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred [@greifer2022].
-@king2019 argued against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
+Popular choices for matching include propensity score matching (PSM) and coarsened exact matching (CEM).
+As @pan2018 introduced, PSM will first calculate the propensity score, namely the probability of receiving treatment based on the specified covariates.
+This score serves as a measure of the distance between two units.
+PSM can match the units with two different approaches to handle distance.
+The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance to be paired.
+This approach does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred.
+The optimal-pair approach works in a similar fashion but tries to minimize the sum of the absolute pairwise distances [@pan2018].
+Regardless of specific approaches, @king2019 argued against PSM in general as it risks more "imbalance, model dependence, and bias" for already balanced data (p.
+444).
+They recommended CEM as a viable alternative "for data with continuous, discrete, and mixed variables" (p.
+450).
+CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+The downside is that it leaves many units without an exact match and discards these unmatched units [@costalli2021].
 
-Using the `MatchIt` package [@ho2022], I performed matching with all the covariates of the adjusted DID model.
-I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
+I performed matching with all the covariates of the adjusted DID model.
+My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
 I then made do with the PSM.
-I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of @bai2018.
-Exact matching based on county of residence preserves the original geographic distribution.
+I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
+Exact matching based on county of residence can preserve the original geographic distribution [@bai2018].
 The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio was set at one treatment unit with up to three control units.
-The matching produced absolute standardized mean differences below 0.1 for all but a few covariates, suggesting an improved overall balance.
+The matching ratio of 3:1 means that one treatment unit would pair with up to three control units.
+According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
+In the appendix, Figures B5-B8 presents the plots of absolute standardized mean differences before and after matching.
 
-Alike are the results from DID models with matching (DIDM) and those without.
-In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
-In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
-The significance level of any parent migration drops to ten percent.
-In all models, the magnitudes of the statistically significant coefficients are similar.
-I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
+The results from models with matching strongly resemble the models without matching (see Tables 8 and 9 below, and Tables A3 and A4 in the appendix).
+In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
+In the models of academic exam score, the treatment variables' coefficients are negative and statistically significant for the any-parent-migrated scenario and the only-mother-migrated scenario.
+The magnitudes of the statistically significant coefficients are similar to those without matching.
 
@@
 
-This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
+This thesis proposes a model to infer the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
 I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as shown by a 1.2 percent drop in academic exam grades and a 2.5 percent drop in cognitive test scores.
+This contrasts with the results of DID models by @bai2018: parental migration is linked to higher English test scores for stay-behind children.
+The discrepancy could be attributed the study's location, a poverty-stricken Northwestern province.
+There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.
+1165).
+In my nationwide sample the reverse may hold.
+The households may be better off, so the labor migrant's additional income helps less.
+Another plausibility is that family disruption precedes resource generation.
+The former's negative effect befalls the left-behind child at once, but the latter's positive effect occurs a while later.
+Consequently, I obtain a short-term negative effect.
+
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
+Results indicate that in the short term, father's absence is not linked to children's academic exam scores; Mother's absence is negatively associated with children's academic and cognitive test results, with a 2.1 percent drop for both indicators.
+An explanation is that the mother's migration, by defying the cultural expectations on maternal care, harbors bitterness in the child's mind [@murphy2020].
+On the other hand, father's migration is negatively associated with children's cognitive test score with a 3 percent decrease.
+This echoes the findings of @shen2021 -- in rural China, the father is often a household's best educated adult.
+His absence means a loss of household human capital, which slows the cognitive development of children.
+The stay-at-home mother may devote more to the caregiving role.
+This can partially buffers the impact by her husband's absence and help her child maintain academic performance.
 
 My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
+Regarding sample size, the treatment group for the both-parents migration is small (n = 130), making the statistical power low.
 Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
@@
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind.
-These limitations may bias the estimation.
+According to @liang2021, some parents out-migrated at an earlier date and returned before the baseline survey.
+These children would be attributed to the non-left-behind group.
+However, they "suffer similar disadvantage as that of left behind children" (p.
+12).
+@liang2021 argued for a new category: the formerly left-behind children.
 
 Limitations also arise from unaccounted endogeneity and exogeneity.
-As @chen2009 stated in their research on left-behind children, endogenous factors may create selection bias.
-When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+As @chen2009 discussed in their research on left-behind children, endogenous factors may create selection bias.
+When migration opportunities arise, some parents may worry that leaving children behind would hamper children's education, thereby giving up the opportunity.
 Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
@@
 From my research, we can find new directions for scholarly inquiry.
-First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
+Researchers can explore interaction and moderation in the pathways of resource generation and family disruption.
+When the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
 This would facilitate examination of the parallel trend assumption.
-Second, researchers can try novel methods.
+Novel methods also offer new possibilities.
 Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
-Synthetic control can evaluate the aggregate outcome of "large-scale but infrequent interventions" at municipal or provincial levels [@abadie2021], such as the policy experimentations that liberalize the hukou system in certain cities [@wang2020].
-Third, researchers can go beyond outbound migration to study return migration of parents [@liang2021].
-Only a few publications, such as that of @liu2018, have explored return migrants and their stay-behind children in the Chinese context.
+Looking beyond outbound migration, return migration of parents also worth studying [@liang2021].
+Not many publications have explored return migrants and their formerly left-behind children in the Chinese context [@démurger2015; @liu2018].
 
-Let us consider the policy implications for China.
-The government has pushed for reforming the multilevel citizenship scheme.
-By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
-However, the most popular migration destinations are metropolises like Beijing and Shanghai.
-These mega-cities still restrict migrant workers' local citizenship rights [@wang2020].
-The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
-The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent.
+Let us consider the policy implications.
+China's multilevel citizenship scheme shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
+The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive [@liang2020; @meng2017].
 Besides, educational attainment is only part of human development outcomes.
 Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020].
-Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
-Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
-
-\newpage
-
-# Appendix
-
-(ref:cog-dif) Changes in standardized cognitive test score
-
-(ref:ttl-dif) Changes in academic exam score
-
-(ref:migr) for new left-behind students and non-left-behind students
-
-(ref:migr-type) by household migration arrangement
-
-```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)")}
-fig_cog
-```
-
-\newpage
-
-```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)")}
-fig_ttl
-```
-
-\newpage
-
-```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
-fig_cog_by_migration_type
-```
-
-\newpage
-
-```{r v-plot-ttl-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
-fig_ttl_by_migration_type
-```
-
-\newpage
-
-(ref:cobalt-match) Covariate balance before and after matching
-
-(ref:cobalt-any) by any parent migration
-
-(ref:cobalt-fa) by father-only migration
-
-(ref:cobalt-mo) by mother-only migration
-
-(ref:cobalt-both) by both parents migration
-
-```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)")}
-love.plot(
-  m.out,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)")}
-love.plot(
-  m.out_mo_only,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)")}
-love.plot(
-  m.out_fa_only,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)")}
-love.plot(
-  m.out_both,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r reg-m-adj-cog}
-table_m_adj_cog
-```
-
-\newpage
-
-```{r reg-m-adj-ttl}
-table_m_adj_ttl
-```
+Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
+Besides top-down policymaking, bottom-up approaches are also necessary.
+School administrators could dedicate advisory and counseling programs.
+Social workers could provide paraprofessional training in communities [@wang2020a].
 
@@
 :::
+
+\newpage
+
+# (APPENDIX) Appendix {.unnumbered}
+
+```{r child = "appendix.Rmd"}
+```
+
+```{r child = "appendix-b.Rmd"}
+```

### 2022-07-03 MScThesisText.tex
almost there

@@
 \hypersetup{
-  pdftitle={Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
+  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
   pdfauthor={Jiancheng Gu1},
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={labor migration, left-behind children, educational performance},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{keywords\newline\indent Word count: X}
-\usepackage{lineno}
-
-\linenumbers
+\keywords{labor migration, left-behind children, educational performance\newline\indent Word count: 6,600}
 \usepackage{csquotes}
@@
 
+\usepackage{float}
+\usepackage{booktabs}
+\usepackage{siunitx}
+\usepackage{setspace}
+\onehalfspacing
+
 \ifLuaTeX
@@
 
-\title{Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
+\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 \abstract{%
-Millions of children worldwide are ``left behind'' when their parents migrate away for work.
-Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance.
-To what extent do different arrangements of parental migration affect children's schooling performance in the short term?
+Millions of children worldwide are ``left behind'' at home communities as their parents migrate away for work.
+Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on children's educational attainment.
+To what extent do different arrangements of parental migration affect children's educational performance in the short term?
 Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey.
 I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
-I measured children's educational performance by standardized cognitive test score and academic exam grades.
+I measured children's schooling performance by cognitive test scores and academic exam grades.
 For causal inference, I built difference-in-differences models with propensity score matching.
-Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers.
-Father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic grades.
+Results show that the newly left-behind children's performance at school dropped slightly compared to that of non-left-behind peers.
+Mother-only migration is negatively associated with children's academic grades and cognitive abilities.
+Father-only migration is negatively associated with children's cognitive abilities, but its magnitude is greater than mother-only migration.
 }
@@
 
-Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
+Globally, millions of children reside in their home communities but live apart from their parents as either one or both parents have migrated for work.
 These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
-In a 2021 resolution, the Council of Europe's Parliamentary Assembly (2021) expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' (p.~2) and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights'' (p.~1).
-
-How are stay-behind children faring when parents have migrated?
-Research results are mixed due to the differential effects of parental migration.
+Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were separated from their migrating parents (NBS et al., 2017).
+The issue of left-behind children has caught the attention of policymakers and legislators.
+In a resolution, the Council of Europe's Parliamentary Assembly (2021) expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights''.
+
+How are stay-behind children faring in the absence of parents?
+Research findings are mixed due to the differential effects of parental migration.
 Consider children's education.
 According to the review articles by Brauw (2019) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
-The inflow of remittances, however, cannot substitute for the loss of parental care.
+To what degree can the inflow of remittances compensate for the loss of parental attention?
 Parental migration decreases the amount and quality of parental guidance, protection, and support.
-It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
-
-A challenge arises in assessing the causality between parent's migration and children's educational achievement.
-Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
+It is uncertain how these two opposing effects together shape children's educational performance.
+This uncertainty merits empirical investigation.
+
+A challenge arises in estimating the effect of parent's migration on children's educational achievement.
+Experiments can unveil causal relations.
+It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
 Alternatively, a quasi-experimental design can help with causal inference.
-The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
+It requires that the cause br on par with random assignment to participants, conditional on identification assumptions (Cunningham, 2021).
 
 In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyzed data from a two-wave panel survey.
+I choose China as the case and analyze data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
-The outcome was measured with children's cognitive test score and academic exam scores.
+I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness checks.
+The outcome was measured with children's cognitive test score and academic exam grade.
 I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
 
-\newpage
-
-\hypertarget{literature-review}{%
-\section{Literature Review}\label{literature-review}}
-
-\hypertarget{theoretical-framework}{%
-\subsection{Theoretical Framework}\label{theoretical-framework}}
+\hypertarget{chinas-context}{%
+\subsection{China's Context}\label{chinas-context}}
+
+Three features make China a suitable case for studying left-behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers.
+They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS, 2022; NBS et al., 2017).
+
+The internal migration stemmed from the neoliberal economic regime.
+Scholars like Duckett (2020) and Zhan (2020) argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
+In the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
+Since then, China has integrated in the global economy and contributed substantial growth to it.
+The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
+The rural hinterlands, however, have lagged behind.
+Simultaneously, many people have left the countryside for the city.
+The regional inequality needs social policy to amend.
+But China's welfare program, as Qian (2021) argued, is fragmented and stratified.
+Those who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
+As rural migrants arrive in the city, they find themselves with limited access to social welfare, such as health care and children's education (Qian, 2021).
+The welfare system's exclusion of rural migrants means that the state shifts its responsibility to individuals, resembling the neoliberal governmentality (Zhan, 2020).
+
+The institutionalized discrimination against rural migrants finds its roots in China's ``multilevel citizenship'' system.
+As Vortherms (2021) explained, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
+
+\begin{quote}
+A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
+Accessing fundamental citizenship rights depends on your registration status \ldots{} Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
+(Vortherms, 2021)
+\end{quote}
+
+In other words, the hukou system binds one's citizenship rights with one's place of registry.
+In theory, Chinese citizens can migrate freely within the country.
+In practice, they cannot change hukou freely.
+When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022).
+Migrant workers have organized petitions, strikes, and protests.
+These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019).
+Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
+
+How does China counter the issue of labor migration and left-behind children?
+According to X.
+Wang (2020) and Zhang (2018), the government has gradually liberalized the multilevel citizenship scheme.
+It has introduced residence permit for internal migrants as the basis for social entitlements.
+First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
+Criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
+This parallels how European states differentially incorporate foreign immigrants into national welfare regimes (Zhang, 2018).
+Another policy response, as stated by Roberts and Hannum (2018), is the centralized boarding schools.
+The Ministry of Education promotes boarding schools in the rural county-seats.
+These schools serve as a cost-efficient way to enroll students in surrounding villages and to look after the left-behind children.
+In reality, such schools ``are often ill-equipped to ensure the healthy upbringing and psychological wellbeing of children'' (p.~6).
+
+Social scientists have researched extensively about China's left-behind children, but the current literature still has three major shortcomings.
+The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
+My sample includes urban left-behind children as well.
+The second shortcoming lies in sampling and research design.
+Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Y.
+Liu et al., 2021; Shu, 2021; F.
+Yang et al., 2022).
+Others only estimated correlation using cross-sectional data (Akezhuoli et al., 2022; Huang et al., 2020; Jin et al., 2020).
+These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+The third shortcoming lies in the measurement of outcome.
+Chang et al.
+(2019) and L.
+Wang et al.
+(2019) measured students' educational performance with the standardized test score of only one academic subject, namely mathematics.
+To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
+I included the test results of multiple subjects to measure comprehensive academic achievement.
+
+\hypertarget{theory-and-hypotheses}{%
+\subsection{Theory and Hypotheses}\label{theory-and-hypotheses}}
 
@@
 This subsequently boosted children's school enrollment and educational expenditure.
+Cebotari (2020) developed a fixed effect model with three-wave panel data collected in Ghana.
+He found that stay-behind children's education benefits from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
 In China, Chang et al.
@@
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+Peng (2018) interviewed first-generation migrant mothers whose initial migration dated back to the 1990s.
+To them, ``good mothering'' primarily means offering economic support for their children in education, which can help their children climb the ladder of success.
 
@@
 Some even longed to quit school to pursue a free, independent life (p.~14).
-
-Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
-Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
+Similarly, Murphy (2022) talked to left-behind adolescents at a village.
+Some of them ``embraced the `left-behind' label'' because it captured their need for more parental care (p.~185), ``especially companionship and affection in daily life'' (p.~186).
+
+Given the two opposing effects, researchers have obtained mixed results on how parental migration impacts children's education.
+Botezat and Pfeiffer (2020) adopted past immigration rate as an instrumental variable.
+They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
 L.
 Wang et al.
-(2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
+(2019) collected data from junior high school students in central China.
+The researchers' two-way fixed-effect model showed no effect of parental on left-behind children's achievement in mathematical test.
 Studying four Chinese provinces, Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+Nguyen (2016) conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
 
@@
 
-\(H_1\) In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
-
-Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
-Y.
+\(H_1\) In the short term, parental migration reduces the educational performance of children left-behind.
+
+\(H_1a\) In the short term, parental migration negatively affects left-behind children's cognitive test score.
+
+\(H_1b\) In the short term, parental migration negatively affects left-behind children's academic exam score.
+
+Researchers have studied whether the impact differ between mother's migration and father's migration.
 Xu et al.
@@
 
-Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
-Under such norms, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
+Scholars like Murphy (2020) noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles (Murphy, 2020).
 I propose the second hypothesis:
 
-\(H_2\) In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
-
-\hypertarget{chinas-context}{%
-\subsection{China's Context}\label{chinas-context}}
-
-Three features make China a suitable case for studying left-behind children.
-The first feature is the huge scale of internal labor migration.
-According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS et al., 2017).
-The internal migration stemmed from the neoliberal economic regime.
-
-The neoliberal economic regime sounds at odds with China, a so-called socialist country.
-Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the global economy and contributed substantial growth to it.
-The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
-The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare program is discriminatory -- it segregates the population.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
-As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
-The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere (Duckett, 2020; Zhang, 2018).
-
-The institutionalized discrimination against migrant laborers find its roots in China's ``multilevel citizenship'' system.
-As Vortherms (2021) demonstrated, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
-
-\begin{quote}
-A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status \ldots{} Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-(Vortherms, 2021)
-\end{quote}
-
-In other words, the hukou system binds one's citizenship rights with one's place of registry.
-In theory, anyone can move out of town freely.
-In practice, they cannot change hukou freely.
-When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022).
-Migrant workers have organized petitions, strikes, and protests.
-These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019).
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
-
-The existing research about China's left-behind children has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
-My sample includes urban left-behind children as well.
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Y.
-Liu et al., 2021; Shu, 2021; F.
-Yang et al., 2022).
-Others only estimated correlation using cross-sectional data (Akezhuoli et al., 2022; Jin et al., 2020).
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-The third shortcoming lies in the measurement of outcome.
-Chang et al.
-(2019) and L.
-Wang et al.
-(2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
+\(H_2\) In the short term, mother's migration more negatively affect the educational performance of children left-behind than do father's migration.
+
+\(H_2a\) In the short term, mother's migration more negatively affect left-behind children's cognitive test score than do father's migration.
+
+\(H_2b\) In the short term, mother's migration more negatively affect left-behind children's academic exam score than do father's migration.
 
@@
 It is a nationally representative, school-based survey featuring junior high school students.
-The survey administrator is the National Survey Research Center at Renmin University of China.
+Currently, two waves of data are available.
+The CEPS team operates under the National Survey Research Center at the Renmin University of China.
 The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
-The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
-These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties.
-The follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed 9449 of the seventh grade cohort.
-I further restricted the sample to students staying with both parents at the original domicile at the baseline survey.
-To deal with missing values, I adopted list-wise deletion for dependent, independent, and control variables.
-The final sample size amounted to 4088 .
+The baseline survey (wave one) took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
+These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter `counties').
+The follow-up survey (wave two) in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed 9449 of the seventh grade cohort.
+I further restricted the sample to students living with both parents at the original domicile at the baseline survey.
+To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
+The final sample size amounts to 4062.
 
@@
 I explored two categories of educational performance: cognitive and academic abilities.
-One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
+One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test administered by the CEPS research team.
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one (W.
+The baseline and follow-up tests consisted of 20 and 35 items, respectively.
+The raw score was calculated based on the Item Response Theory (W.
 Wang \& Li, 2015).
+I transformed the raw scores to the 100-point scale.
+I chose the raw score instead of the z-score, as z-standardization fails to document the change of mean between time points, which is also of interest (Moeller, 2015).
 
 Another dependent variable concerned students' academic performance.
-This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
+This was measured by the average scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
 Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
-This is related to how junior high schools operate as part of the compulsory education system in China.
+This is related to how junior high schools operate within the compulsory education system in China.
 According to OECD (2016), China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
-At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
+At school, the subjects of Chinese, mathematics, and English are core subjects and others as supplementary subjects.
 Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
@@
 I transformed the exam grades through the following steps.
-I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
-After the conversion, I checked for abnormal values outside the 0-100 range.
-31 observations were outliers, accounting for less than one percent of the sample.
-I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
-In this way, I can limit the impact of outliers while retaining these observations in the sample.
-After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
+I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) with the 100-point scale.
+After the conversion, I checked for abnormal values lower than zero or higher than one hundred.
+30 observations were outliers, accounting for less than one percent of the sample.
+I retained these observations in the sample and trimmed the subject exam scores.
+The trimming ensured that all values would be within the 0-100 range.
+In this way, I can limit the impact of outliers.
+Finally, I calculated the average score of these three subjects.
 
@@
 
-The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for econometric modeling (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+The control variables on children's level include age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
+The lists of covariates are in Tables 3-5 in the Results section.
+
+\hypertarget{analytical-strategy}{%
+\subsection{Analytical Strategy}\label{analytical-strategy}}
+
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j,k;1}\) is the test score at baseline, and \(C_{j}\) and \(C_{k}\) are the classroom fixed-effects at baseline and follow-up, respectively.
-Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
-About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
-This necessitates adding the wave-two classroom fixed-effect.
-
-The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \varepsilon_{i,j}\] For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
+School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in the same school are also in the same county.
+An alternative is to use a class fixed-effect to control for time-invariant factors in the classroom.
+However, about one-sixth of the students were reassigned into new classes at the end of baseline academic year.
+As the reassignment of classroom will complicate the model, I ruled out the classroom fixed-effect.
+
+The DID model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
 The model is unadjusted as it does not adjust for additional covariates.
@@
 
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \theta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
+I adopted \texttt{R} (version 4.2.0) for all the analyses (R Core Team, 2022).
+This involved the following packages: \texttt{tidyverse} (version 1.3.1) for data cleaning (Wickham et al., 2019); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022); \texttt{modelsummary} (version 1.0.0), \texttt{vtable} (version 1.3.3), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.0) for typesetting (Aust \& Barth, 2022).
+
 \newpage
@@
 
-Table 1 below summarizes the changes in migration status in the sample.
-All 4088 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
-In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
+Table 1 summarizes the independent variables, namely the migration status reported in the wave two survey.
+All 4062 children were living with parents in one household in baseline, but about fifteen percent saw at least one parent migrated between the two waves of survey.
+I call these students ``newly left-behind children'' and their households ``new migration households.'' In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
 The remaining one-fifth was both-parents migration.
 
-\renewcommand{\arraystretch}{0.75}
-
-\begin{longtable}[]{@{}llrr@{}}
+\renewcommand{\arraystretch}{0.72}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-1}Independent variables by parental migration}
+\centering
+\begin{tabular}[t]{lll}
 \toprule
-& & N & \% \\
-\midrule
-\endhead
-Parental Migration & No & 3452 & 84.4 \\
-& Yes & 636 & 15.6 \\
-Parental Migration Type & Both Parents At Home & 3452 & 84.4 \\
-& Both Parents Migrated & 131 & 3.2 \\
-& Only Father Migrated & 251 & 6.1 \\
-& Only Mother Migrated & 254 & 6.2 \\
+Variable & N & Percent\\
+\midrule
+Parental Migration &  & \\
+... No & 3422 & 84.2\%\\
+... Yes & 640 & 15.8\%\\
+Parental Migration Type &  & \\
+... Both Parents & 130 & 3.2\%\\
+... Both Parents At Home & 3422 & 84.2\%\\
+... Only Father & 252 & 6.2\%\\
+... Only Mother & 258 & 6.4\%\\
 \bottomrule
-\end{longtable}
+\end{tabular}
+\end{table}
 
@@
 
-Tables 2 below summarizes the dependent variables by the control group and the treatment group. In addition, the violin plots in the appendix visualize the distribution of outcome variables.
-
-\begin{tabular}{llllll}
+The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figures B1-B4 in the appendix.
+Compared to non-left-behind peers, newly left-behind children score lower in wave two's cognitive and academic tests; Their cognitive test score increases less and their academic exam score drops more.
+T-tests show that for the baseline outcomes, the differences of the mean values between-group are probably due to chance.
+For the wave two outcomes and the between-wave changes, the differences of the mean value are statistically significant.
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-2}Dependent variables by parental migration}
+\centering
+\begin{tabular}[t]{llllll}
 \toprule
@@
 \cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3422} & \multicolumn{2}{c}{Yes = 640} \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
@@
 \midrule
-Cognitive test score difference & 0.28 & 0.8 & 0.19 & 0.8 & p=0.006**\\
-\hspace{1em}Wave 1 score & 0.15 & 0.86 & 0.13 & 0.84 & p=0.471\\
-\hspace{1em}Wave 2 score & 0.43 & 0.78 & 0.31 & 0.8 & p<0.001***\\
-Academic exam score difference & -8.2 & 32.75 & -12.15 & 35.43 & p=0.006**\\
-\hspace{1em}Wave 1 score & 213.39 & 49.31 & 211.58 & 50.3 & p=0.395\\
+Cognitive test score difference & 11.48 & 19.85 & 9.58 & 20.71 & p=0.028*\\
+\hspace{1em}Wave 1 score & 56.75 & 16.63 & 55.98 & 16.62 & p=0.282\\
+\hspace{1em}Wave 2 score & 68.22 & 18.45 & 65.56 & 19.54 & p<0.001***\\
+Academic exam score difference & -2.78 & 10.91 & -4 & 11.78 & p=0.01**\\
+\hspace{1em}Wave 1 score & 71.21 & 16.37 & 70.4 & 16.93 & p=0.256\\
 \addlinespace
-\hspace{1em}Wave 2 score & 205.19 & 54.83 & 199.42 & 58.23 & p=0.016*\\
+\hspace{1em}Wave 2 score & 68.43 & 18.28 & 66.4 & 19.49 & p=0.011*\\
 \bottomrule
@@
 \end{tabular}
+\end{table}
 
@@
 
-\begin{tabular}{llllll}
+Table 3 summarizes the bivariate analysis on the binary control variables.
+New migration households have lower internet access rate.
+Among the newly left-behind children, male sex, past grade retention, and boarding at school were more common compared to the non-left-behind peers.
+Chi-square tests show that these differences in variance are unlikely due to chance.
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-3}Dichotomous control variables by parental migration}
+\centering
+\begin{tabular}[t]{llllll}
 \toprule
@@
 \midrule
-child.is.girl &  &  &  &  & X2=11.942***\\
-... 0 & 1650 & 48\% & 352 & 55\% & \\
-... 1 & 1802 & 52\% & 284 & 45\% & \\
-child.has.rural.hukou &  &  &  &  & X2=0.485\\
-... 0 & 1884 & 55\% & 337 & 53\% & \\
+child.is.girl &  &  &  &  & X2=12.261***\\
+... 0 & 1637 & 48\% & 355 & 55\% & \\
+... 1 & 1785 & 52\% & 285 & 45\% & \\
+child.has.rural.hukou &  &  &  &  & X2=1.09\\
+... 0 & 1887 & 55\% & 338 & 53\% & \\
 \addlinespace
-... 1 & 1568 & 45\% & 299 & 47\% & \\
-child.in.boarding.school &  &  &  &  & X2=4.63*\\
-... 0 & 2477 & 72\% & 429 & 67\% & \\
-... 1 & 975 & 28\% & 207 & 33\% & \\
-child.is.ethnic.minority &  &  &  &  & X2=0.388\\
+... 1 & 1535 & 45\% & 302 & 47\% & \\
+child.in.boarding.school &  &  &  &  & X2=4.49*\\
+... 0 & 2470 & 72\% & 435 & 68\% & \\
+... 1 & 952 & 28\% & 205 & 32\% & \\
+child.is.ethnic.minority &  &  &  &  & X2=0.514\\
 \addlinespace
-... 0 & 3213 & 93\% & 587 & 92\% & \\
-... 1 & 239 & 7\% & 49 & 8\% & \\
-child.had.skipped.grade &  &  &  &  & X2=0.02\\
-... 0 & 3414 & 99\% & 628 & 99\% & \\
-... 1 & 38 & 1\% & 8 & 1\% & \\
+... 0 & 3190 & 93\% & 591 & 92\% & \\
+... 1 & 232 & 7\% & 49 & 8\% & \\
+child.had.skipped.grade &  &  &  &  & X2=0.056\\
+... 0 & 3386 & 99\% & 632 & 99\% & \\
+... 1 & 36 & 1\% & 8 & 1\% & \\
 \addlinespace
-child.had.repeated.grade &  &  &  &  & X2=10.621**\\
-... 0 & 3147 & 91\% & 553 & 87\% & \\
-... 1 & 305 & 9\% & 83 & 13\% & \\
+child.had.repeated.grade &  &  &  &  & X2=10.485**\\
+... 0 & 3121 & 91\% & 557 & 87\% & \\
+... 1 & 301 & 9\% & 83 & 13\% & \\
 child.went.to.preschool &  &  &  &  & X2=0.923\\
-... 0 & 531 & 15\% & 108 & 17\% & \\
+... 0 & 523 & 15\% & 108 & 17\% & \\
 \addlinespace
-... 1 & 2921 & 85\% & 528 & 83\% & \\
+... 1 & 2899 & 85\% & 532 & 83\% & \\
 parent.has.white.collar.job &  &  &  &  & X2=0.001\\
-... 0 & 2735 & 79\% & 503 & 79\% & \\
-... 1 & 717 & 21\% & 133 & 21\% & \\
-home.has.internet &  &  &  &  & X2=12.815***\\
+... 0 & 2705 & 79\% & 505 & 79\% & \\
+... 1 & 717 & 21\% & 135 & 21\% & \\
+home.has.internet &  &  &  &  & X2=12.967***\\
 \addlinespace
-... 0 & 1072 & 31\% & 244 & 38\% & \\
-... 1 & 2380 & 69\% & 392 & 62\% & \\
+... 0 & 1054 & 31\% & 244 & 38\% & \\
+... 1 & 2368 & 69\% & 396 & 62\% & \\
 \bottomrule
@@
 
-\begin{tabular}{llllll}
+Table 4 presents the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
+While the majority of mothers and fathers have only finished high school or below, they hold big expectations for children.
+Eight out of ten parents wish that their children complete university education.
+Scholars like Willis (2019) explained this pattern with the Chinese social norms and cultural traditions.
+In ancient China, the Confucian teaching emphasized the cultivation of personhood through learning, diligence, and persistence.
+In real life, knowledge could translate into power and privilege.
+Ordinary people could study for the highly competitive \emph{keju} (civil service examination).
+As the world's ``earliest meritocratic institution,'' this exam system recruited top performers into the imperial government and the elite class (T.
+Chen et al., 2020, p.
+2030).
+Nowadays in China, the emperor and \emph{keju} are long gone, but the influences are long-lasting.
+Chinese parents hope that their children receive the best education to secure a decent career (Luo et al., 2013; Ng \& Wei, 2020).
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}Categorical and continuous control variables by parental migration}
+\centering
+\begin{tabular}[t]{llllll}
 \toprule
@@
 \midrule
-child.age & 12.45 & 0.63 & 12.5 & 0.72 & F=3.616\\
-child.health.self.rated & 4.17 & 0.87 & 4.14 & 0.9 & F=0.622\\
-child.educational.aspiration & 3.97 & 1.12 & 3.93 & 1.19 & F=0.617\\
-parent.educational.level & 2.9 & 1.19 & 2.94 & 1.21 & F=0.367\\
-parent.expectation.on.child & 4.19 & 0.91 & 4.15 & 0.94 & F=1.093\\
+child.age & 12.45 & 0.63 & 12.51 & 0.73 & F=4.263*\\
+child.health & 4.17 & 0.87 & 4.14 & 0.9 & F=0.576\\
+child.education.aspiration & 3.96 & 1.12 & 3.93 & 1.19 & F=0.522\\
+mother.education.level & 1.53 & 1.17 & 1.57 & 1.25 & F=0.468\\
+father.education.level & 1.72 & 1.18 & 1.75 & 1.21 & F=0.274\\
 \addlinespace
-home.extracurricular.book & 3.41 & 1.18 & 3.32 & 1.28 & F=3.09\\
-home.economic.resource & 2.87 & 0.55 & 2.84 & 0.58 & F=1.37\\
+parent.expectation & 4.19 & 0.91 & 4.14 & 0.95 & F=1.627\\
+home.extracurricular.book & 3.42 & 1.18 & 3.32 & 1.28 & F=3.392\\
+home.economic.resource & 2.87 & 0.55 & 2.84 & 0.57 & F=1.52\\
 \bottomrule
@@
 \end{tabular}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}Measurement of categorical variables}
+\centering
+\begin{tabular}[t]{lll}
+\toprule
+Variable & N & Percent\\
+\midrule
+child.health &  & \\
+... 1 = Very poor & 21 & 0.5\%\\
+... 2 = Somewhat poor & 112 & 2.8\%\\
+... 3 = Moderate & 797 & 19.6\%\\
+... 4 = Good & 1373 & 33.8\%\\
+... 5 = Very good & 1759 & 43.3\%\\
+child.education.aspiration &  & \\
+... 1 = Junior high school & 137 & 3.4\%\\
+... 2 = Senior high school & 418 & 10.3\%\\
+... 3 = Associate college & 615 & 15.1\%\\
+... 4 = University & 1195 & 29.4\%\\
+... 5 = Postgraduate & 1697 & 41.8\%\\
+mother.education.level &  & \\
+... 0 = Primary school and below & 702 & 17.3\%\\
+... 1 = Junior high school & 1618 & 39.8\%\\
+... 2 = Senior high school & 1034 & 25.5\%\\
+... 3 = Associate college & 304 & 7.5\%\\
+... 4 = University & 365 & 9\%\\
+... 5 = Postgraduate & 39 & 1\%\\
+father.education.level &  & \\
+... 0 = Primary school and below & 441 & 10.9\%\\
+... 1 = Junior high school & 1615 & 39.8\%\\
+... 2 = Senior high school & 1170 & 28.8\%\\
+... 3 = Associate college & 348 & 8.6\%\\
+... 4 = University & 422 & 10.4\%\\
+... 5 = Postgraduate & 66 & 1.6\%\\
+parent.expectation &  & \\
+... 1 = Junior high school & 34 & 0.8\%\\
+... 2 = Senior high school & 254 & 6.3\%\\
+... 3 = Associate college & 426 & 10.5\%\\
+... 4 = University & 1569 & 38.6\%\\
+... 5 = Postgraduate & 1779 & 43.8\%\\
+home.extracurricular.book &  & \\
+... 1 = Very few & 386 & 9.5\%\\
+... 2 = Not many & 411 & 10.1\%\\
+... 3 = Some & 1302 & 32.1\%\\
+... 4 = Quite a few & 1104 & 27.2\%\\
+... 5 = A great number & 859 & 21.1\%\\
+home.economic.resource &  & \\
+... 1 = Very poor & 110 & 2.7\%\\
+... 2 = Somewhat poor & 589 & 14.5\%\\
+... 3 = Moderate & 3112 & 76.6\%\\
+... 4 = Somewhat rich & 240 & 5.9\%\\
+... 5 = Very rich & 11 & 0.3\%\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
 
@@
 
-The unrestricted DID models support my hypothesis one -- newly left-behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left-behind counterparts.
-If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to -0.09 SD in cognitive test score and -0.09 points in academic exam grades.
-Both relationships are slight in strength.
-
-The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
-This holds true for academic abilities.
-Children from only mother migrate households are associated with -0.04 points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
-Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left-behind children.
-Children with only father absent are associated with (-0.14 SD), and both parents absent (-0.10 SD) compared to the non left-behind children.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
+I first present the results on children's cognitive test score.
+According to the unadjusted DID models (see Table 6 below), newly left-behind adolescents are more likely to score lower in cognitive tests than their non-left-behind counterparts, lending support to Hypothesis 1a.
+Parental migration is linked to a 2.56 points decrease in cognitive test score.
+Hypothesis 2a is only partially supported.
+Compared with the non-left-behind children, children with only father absent are associated with greater decrease (2.87 points) in cognitive test score than those with only mother absent (2.15 points).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (See Table A1 in appendix).
+That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test score}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.56}*** & \num{-2.15}* & \num{-2.87}* & \num{-2.96}*\\
+ & (\num{0.70}) & (\num{1.06}) & (\num{1.12}) & (\num{1.39})\\
+Baseline.score & \num{-0.71}*** & \num{-0.72}*** & \num{-0.71}*** & \num{-0.72}***\\
+ & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
+\midrule
+Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
+R2 & \num{0.379} & \num{0.382} & \num{0.386} & \num{0.389}\\
+R2 Adj. & \num{0.361} & \num{0.363} & \num{0.367} & \num{0.369}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}No control variables included in these models}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+Next, I show the results on children's academic test grades.
+In line with Hypothesis 1b, the unadjusted DID models (see Table 7 below) show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers.
+Parental migration is associated with a drop of 1.27 points in academic exam score.
+Hypothesis 2b finds partial support.
+The exam grade of only-mother-migrated children sees a 2.11 points decrease relative to non-left-behind counterparts.
+In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
+The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in appendix).
+Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam score}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -0.09** & -0.04 & -0.14** & -0.10 \\
-& (0.03) & (0.05) & (0.04) & (0.06) \\
-W1 score & -0.62*** & -0.63*** & -0.62*** & -0.62*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.494 & 0.502 & 0.505 & 0.499 \\
-R2 Adj. & 0.424 & 0.426 & 0.430 & 0.419 \\
-R2 Within & 0.370 & 0.378 & 0.378 & 0.374 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.27}* & \num{-2.11}* & \num{-0.88} & \num{-0.19}\\
+ & (\num{0.54}) & (\num{0.91}) & (\num{0.72}) & (\num{0.72})\\
+Baseline.score & \num{0.05} & \num{0.05} & \num{0.05} & \num{0.04}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+\midrule
+Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
+R2 & \num{0.481} & \num{0.498} & \num{0.484} & \num{0.501}\\
+R2 Adj. & \num{0.466} & \num{0.483} & \num{0.468} & \num{0.485}\\
+FE: schids & X & X & X & X\\
 \bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} Control variables not included
+\multicolumn{5}{l}{\rule{0pt}{1em}No control variables included in these models}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's academic exam score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -2.67* & -5.85* & -0.25 & -1.13 \\
-& (1.26) & (2.36) & (1.66) & (2.28) \\
-W1 score & 0.04 & 0.04† & 0.04† & 0.04 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.562 & 0.577 & 0.566 & 0.577 \\
-R2 Adj. & 0.501 & 0.513 & 0.500 & 0.510 \\
-R2 Within & 0.005 & 0.009 & 0.004 & 0.004 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} Control variables not included
-
-The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
-That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
-
 Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational aspiration as well as parents' expectation on children.
-In terms of age, the older students' scores drop relatively more than younger students'.
-One year older in age is associated with -0.07 SD for standardized cognitive test and -1.23 points for academic exams.
-Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
-The effect sizes are 0.01 SD and 0.07 SD for standardized cognitive test, respectively; and 0.29 points and 1.82 points for academic exams, respectively.
-
-Several predictors are strong in the model of academic grades but not in that of cognitive scores.
-These are children's gender and self-reported health, and the years of parental education.
-Girls outperform boys by 4.49 points in academic exams, but do not show advantage in cognitive test.
+These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
+One year older in age is associated with decreases of 2.61 points for cognitive test and of 0.44 points for academic exam.
+Preschool attendance is linked to increases of 2.33 points for cognitive test and of 1.17 points for academic exam.
+Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
+The coefficients are 0.75 points and 2.03 points for cognitive test, respectively; and 0.27 points and 0.77 points for academic exams, respectively.
+
+Several predictors are strong in predicting one outcome but not the other.
+Covariates related to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
+Girls outperform boys by 1.62 points in academic exams, but do not show advantage in cognitive test.
 Students who consider themselves healthier are associated with higher scores in academic exams.
-Parents with more education are associated with their children's higher scores in academic exams.
-If the years of parental education of the best-educated among the two increase by one, it would be linked to a 0.88 points increase in the child's academic exam grade.
-These three predictors are not significant for cognitive outcomes.
-
-Preschool attendance is associated with higher cognitive outcomes 0.07 SD, but its effect for academic outcomes is not significant.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Absent
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Absent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Absent
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -0.09** & -0.04 & -0.14*** & -0.08 \\
-& (0.03) & (0.05) & (0.04) & (0.06) \\
-W1 score & -0.67*** & -0.67*** & -0.67*** & -0.67*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.age & -0.07*** & -0.06** & -0.07*** & -0.08*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.is.girl & -0.01 & 0.00 & 0.00 & -0.01 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.health.self.rated & -0.02 & -0.02 & -0.02 & -0.02 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-child.has.rural.hukou & -0.01 & 0.00 & -0.01 & 0.00 \\
-& (0.02) & (0.03) & (0.03) & (0.03) \\
-child.number.of.sibling & -0.03 & -0.02 & -0.02 & -0.02 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.went.to.preschool & 0.07* & 0.06† & 0.05† & 0.07* \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-child.had.skipped.grade & -0.17 & -0.11 & -0.20 & -0.10 \\
-& (0.12) & (0.12) & (0.12) & (0.12) \\
-child.had.repeated.grade & -0.08* & -0.11** & -0.07† & -0.06 \\
-& (0.04) & (0.04) & (0.04) & (0.04) \\
-child.in.boarding.school & 0.04 & 0.02 & 0.02 & 0.01 \\
-& (0.04) & (0.04) & (0.04) & (0.04) \\
-child.educational.aspiration & 0.07*** & 0.07*** & 0.07*** & 0.08*** \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-child.is.ethnic.minority & 0.04 & 0.04 & 0.02 & 0.02 \\
-& (0.06) & (0.06) & (0.06) & (0.06) \\
-parent.expectation.on.child & 0.08*** & 0.09*** & 0.09*** & 0.09*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-parent.has.white.collar.job & 0.01 & -0.01 & 0.01 & 0.00 \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-parent.educational.level & 0.01 & 0.01 & 0.01 & 0.01 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-home.economic.resource & -0.02 & -0.01 & 0.00 & 0.00 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-home.extracurricular.book & 0.01 & 0.00 & 0.01 & 0.00 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-home.has.internet & -0.01 & -0.01 & -0.02 & -0.02 \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.525 & 0.533 & 0.537 & 0.530 \\
-R2 Adj. & 0.458 & 0.459 & 0.464 & 0.452 \\
-R2 Within & 0.409 & 0.416 & 0.418 & 0.413 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic exam score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -2.65* & -5.87** & -0.20 & -0.92 \\
-& (1.25) & (2.24) & (1.68) & (2.35) \\
-W1 score & -0.01 & -0.01 & 0.00 & -0.01 \\
-& (0.02) & (0.03) & (0.02) & (0.02) \\
-child.age & -1.23† & -1.04 & -1.21† & -0.96 \\
-& (0.65) & (0.68) & (0.70) & (0.70) \\
-child.is.girl & 4.49*** & 4.78*** & 4.54*** & 4.43*** \\
-& (0.92) & (0.95) & (0.92) & (0.97) \\
-child.health.self.rated & 1.05* & 1.12* & 0.92* & 0.85† \\
-& (0.43) & (0.45) & (0.47) & (0.47) \\
-child.has.rural.hukou & 1.08 & 1.50 & 0.80 & 0.98 \\
-& (1.02) & (1.06) & (1.05) & (1.07) \\
-child.number.of.sibling & 1.03† & 0.87 & 1.21* & 0.66 \\
-& (0.58) & (0.59) & (0.60) & (0.62) \\
-child.went.to.preschool & 1.65 & 2.22† & 0.85 & 1.97 \\
-& (1.20) & (1.24) & (1.28) & (1.27) \\
-child.had.skipped.grade & -0.73 & 0.23 & -0.98 & 1.01 \\
-& (4.82) & (4.82) & (5.41) & (5.07) \\
-child.had.repeated.grade & -1.81 & -1.22 & -1.55 & -0.20 \\
-& (1.85) & (1.98) & (1.89) & (1.81) \\
-child.in.boarding.school & -1.14 & -0.19 & -0.72 & -1.19 \\
-& (1.65) & (1.65) & (1.66) & (1.81) \\
-child.educational.aspiration & 1.82*** & 2.08*** & 1.90*** & 1.91*** \\
-& (0.52) & (0.55) & (0.51) & (0.53) \\
-child.is.ethnic.minority & 0.48 & -0.24 & -0.33 & -1.14 \\
-& (2.15) & (2.29) & (2.38) & (2.56) \\
-parent.expectation.on.child & 0.88† & 0.85 & 0.86 & 0.96† \\
-& (0.53) & (0.55) & (0.54) & (0.55) \\
-parent.has.white.collar.job & 0.29 & 0.03 & 0.59 & 0.42 \\
-& (1.19) & (1.23) & (1.21) & (1.25) \\
-parent.educational.level & 1.02† & 1.14* & 1.14* & 1.15* \\
-& (0.53) & (0.53) & (0.54) & (0.56) \\
-home.economic.resource & -0.74 & -0.18 & -0.66 & -0.24 \\
-& (0.81) & (0.88) & (0.87) & (0.87) \\
-home.extracurricular.book & -0.78† & -1.18* & -0.86† & -0.85† \\
-& (0.45) & (0.46) & (0.45) & (0.46) \\
-home.has.internet & -1.41 & -1.65 & -1.33 & -1.37 \\
-& (1.13) & (1.14) & (1.18) & (1.17) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.573 & 0.590 & 0.578 & 0.588 \\
-R2 Adj. & 0.512 & 0.525 & 0.512 & 0.520 \\
-R2 Within & 0.032 & 0.039 & 0.032 & 0.030 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+On the contrary, students who perceive their households having more extracurricular books are associated with lower scores in academic exams.
+Covariates related to cognitive scores is the number of siblings.
+Having an additional sibling is associated with lower cognitive score of 0.99 points, but its effect for academic grade is not significant statistically.
+
+\newpage
 
@@
 Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
+A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
 Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
@@
 
-Popular choices for matching include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H.
-Xu \& Xie, 2015).
-As Greifer (2022) introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
-The eligibility as the ``closest'' can be determined with the differences in propensity score.
-Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred (Greifer, 2022).
-King and Nielsen (2019) argued against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
-
-Using the \texttt{MatchIt} package (Ho et al., 2022), I performed matching with all the covariates of the adjusted DID model.
-I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
+Popular choices for matching include propensity score matching (PSM) and coarsened exact matching (CEM).
+As Pan and Bai (2018) introduced, PSM will first calculate the propensity score, namely the probability of receiving treatment based on the specified covariates.
+This score serves as a measure of the distance between two units.
+PSM can match the units with two different approaches to handle distance.
+The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance to be paired.
+This approach does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred.
+The optimal-pair approach works in a similar fashion but tries to minimize the sum of the absolute pairwise distances (Pan \& Bai, 2018).
+Regardless of specific approaches, King and Nielsen (2019) argued against PSM in general as it risks more ``imbalance, model dependence, and bias'' for already balanced data (p.~444).
+They recommended CEM as a viable alternative ``for data with continuous, discrete, and mixed variables'' (p.~450).
+CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
+The downside is that it leaves many units without an exact match and discards these unmatched units (Costalli \& Negri, 2021).
+
+I performed matching with all the covariates of the adjusted DID model.
+My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
 I then made do with the PSM.
-I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of Bai et al.
-(2018).
-Exact matching based on county of residence preserves the original geographic distribution.
+I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
+Exact matching based on county of residence can preserve the original geographic distribution (Bai et al., 2018).
 The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio was set at one treatment unit with up to three control units.
-The matching produced absolute standardized mean differences below 0.1 for all but a few covariates, suggesting an improved overall balance.
-
-Alike are the results from DID models with matching (DIDM) and those without.
-In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
-In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
-The significance level of any parent migration drops to ten percent.
-In all models, the magnitudes of the statistically significant coefficients are similar.
-I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
+The matching ratio of 3:1 means that one treatment unit would pair with up to three control units.
+According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
+In the appendix, Figures B5-B8 presents the plots of absolute standardized mean differences before and after matching.
+
+The results from models with matching strongly resemble the models without matching (see Tables 8 and 9 below, and Tables A3 and A4 in the appendix).
+In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
+In the models of academic exam score, the treatment variables' coefficients are negative and statistically significant for the any-parent-migrated scenario and the only-mother-migrated scenario.
+The magnitudes of the statistically significant coefficients are similar to those without matching.
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.64}*** & \num{-2.76}* & \num{-3.41}** & \num{-1.96}\\
+ & (\num{0.74}) & (\num{1.22}) & (\num{1.25}) & (\num{1.74})\\
+Baseline.score & \num{-0.70}*** & \num{-0.74}*** & \num{-0.62}*** & \num{-0.69}***\\
+ & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.392} & \num{0.450} & \num{0.423} & \num{0.467}\\
+R2 Adj. & \num{0.363} & \num{0.384} & \num{0.356} & \num{0.352}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -0.09** & -0.05 & -0.13* & -0.05 \\
-& (0.03) & (0.06) & (0.06) & (0.11) \\
-W1 score & -0.61*** & -0.65*** & -0.60*** & -0.63*** \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.528 & 0.627 & 0.638 & 0.646 \\
-R2 Adj. & 0.375 & 0.313 & 0.320 & -0.312 \\
-R2 Within & 0.363 & 0.407 & 0.372 & 0.351 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.22}* & \num{-1.65}* & \num{-1.15} & \num{0.46}\\
+ & (\num{0.57}) & (\num{0.81}) & (\num{0.86}) & (\num{0.98})\\
+Baseline.score & \num{0.05}† & \num{0.07}† & \num{0.04} & \num{0.01}\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.468} & \num{0.587} & \num{0.480} & \num{0.501}\\
+R2 Adj. & \num{0.444} & \num{0.538} & \num{0.420} & \num{0.393}\\
+FE: schids & X & X & X & X\\
 \bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Explanator & -2.65† & -5.34* & -2.42 & -2.45 \\
-& (1.47) & (2.67) & (2.56) & (3.96) \\
-W1 score & 0.03 & 0.08† & 0.05 & 0.03 \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.590 & 0.682 & 0.637 & 0.706 \\
-R2 Adj. & 0.457 & 0.413 & 0.319 & -0.087 \\
-R2 Within & 0.006 & 0.026 & 0.008 & 0.005 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
 
@@
 
-This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
+This thesis proposes a model to infer the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
 I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as shown by a 1.2 percent drop in academic exam grades and a 2.5 percent drop in cognitive test scores.
+This contrasts with the results of DID models by Bai et al.
+(2018): parental migration is linked to higher English test scores for stay-behind children.
+The discrepancy could be attributed the study's location, a poverty-stricken Northwestern province.
+There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.~1165).
+In my nationwide sample the reverse may hold.
+The households may be better off, so the labor migrant's additional income helps less.
+Another plausibility is that family disruption precedes resource generation.
+The former's negative effect befalls the left-behind child at once, but the latter's positive effect occurs a while later.
+Consequently, I obtain a short-term negative effect.
+
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
+Results indicate that in the short term, father's absence is not linked to children's academic exam scores; Mother's absence is negatively associated with children's academic and cognitive test results, with a 2.1 percent drop for both indicators.
+An explanation is that the mother's migration, by defying the cultural expectations on maternal care, harbors bitterness in the child's mind (Murphy, 2020).
+On the other hand, father's migration is negatively associated with children's cognitive test score with a 3 percent decrease.
+This echoes the findings of Shen et al.
+(2021) -- in rural China, the father is often a household's best educated adult.
+His absence means a loss of household human capital, which slows the cognitive development of children.
+The stay-at-home mother may devote more to the caregiving role.
+This can partially buffers the impact by her husband's absence and help her child maintain academic performance.
 
 My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
+Regarding sample size, the treatment group for the both-parents migration is small (n = 130), making the statistical power low.
 Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
@@
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-As I previously wrote, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind .
-These limitations may bias the estimation.
+According to Liang and Li (2021), some parents out-migrated at an earlier date and returned before the baseline survey.
+These children would be attributed to the non-left-behind group.
+However, they ``suffer similar disadvantage as that of left behind children'' (p.~12).
+Liang and Li (2021) argued for a new category: the formerly left-behind children.
 
@@
 As Chen et al.
-(2009) stated in their research on left-behind children, endogenous factors may create selection bias.
-When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
+(2009) discussed in their research on left-behind children, endogenous factors may create selection bias.
+When migration opportunities arise, some parents may worry that leaving children behind would hamper children's education, thereby giving up the opportunity.
 Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
@@
 From my research, we can find new directions for scholarly inquiry.
-First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
+Researchers can explore interaction and moderation in the pathways of resource generation and family disruption.
+When the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
 This would facilitate examination of the parallel trend assumption.
-Second, researchers can try novel methods.
+Novel methods also offer new possibilities.
 Machine learning, for example, can estimate the heterogeneous effects across subgroups (R.
 Liu, 2021).
-Third, researchers can go beyond outbound migration to study return migration of parents (Liang \& Li, 2021).
-Only a few publications have explored return migrants and their stay-behind children in the Chinese context (Démurger \& Xu, 2015; Z.
+Looking beyond outbound migration, return migration of parents also worth studying (Liang \& Li, 2021).
+Not many publications have explored return migrants and their formerly left-behind children in the Chinese context (Démurger \& Xu, 2015; Z.
 Liu et al., 2018).
 
-Let us consider the policy implications for China.
-The government has enacted reforms in the multilevel citizenship scheme.
-By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
-However, the most popular migration destinations are metropolises like Beijing and Shanghai.
-These mega-cities still restrict migrant workers' local citizenship rights (X.
-Wang, 2020).
-The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
-The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent (Liang \& Sun, 2020; Meng \& Yamauchi, 2017).
+Let us consider the policy implications.
+China's multilevel citizenship scheme shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
+The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive (Liang \& Sun, 2020; Meng \& Yamauchi, 2017).
 Besides, educational attainment is only part of human development outcomes.
 Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020).
-Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
-Schools could dedicate more advisory and counseling support to children who stay behind.
-``Social workers could test models for training paraprofessionals within different communities'' to support left-behind children (M.
-Wang et al., 2020, p.
-1436).
-
-\newpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1.pdf}
-\caption{\label{fig:v-plot-cog}Changes in standardized cognitive test score for new left-behind students and non-left-behind students}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1.pdf}
-\caption{\label{fig:v-plot-ttl}Changes in academic exam score for new left-behind students and non-left-behind students}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1-1.pdf}
-\caption{\label{fig:v-plot-cog-1}Changes in standardized cognitive test score by household migration arrangement}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1-1.pdf}
-\caption{\label{fig:v-plot-ttl-1}Changes in academic exam score by household migration arrangement}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-any-1.pdf}
-\caption{\label{fig:cobal-any}Covariate balance before and after matching by any parent migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-mo-1.pdf}
-\caption{\label{fig:cobal-mo}Covariate balance before and after matching by mother-only migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-fa-1.pdf}
-\caption{\label{fig:cobal-fa}Covariate balance before and after matching by father-only migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-both-1.pdf}
-\caption{\label{fig:cobal-both}Covariate balance before and after matching by both parents migration}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Explanator & -0.09** & -0.04 & -0.15* & -0.08 \\
-& (0.03) & (0.06) & (0.06) & (0.11) \\
-W1 score & -0.67*** & -0.67*** & -0.67*** & -0.69*** \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-child.age & -0.08* & -0.02 & -0.03 & -0.15 \\
-& (0.03) & (0.05) & (0.04) & (0.10) \\
-child.is.girl & 0.02 & 0.01 & 0.05 & -0.06 \\
-& (0.03) & (0.05) & (0.06) & (0.10) \\
-child.health.self.rated & 0.00 & -0.03 & -0.02 & -0.07 \\
-& (0.02) & (0.03) & (0.03) & (0.06) \\
-child.has.rural.hukou & 0.01 & -0.07 & 0.06 & 0.04 \\
-& (0.04) & (0.07) & (0.07) & (0.12) \\
-child.number.of.sibling & -0.07* & -0.09* & -0.05 & -0.10 \\
-& (0.03) & (0.04) & (0.04) & (0.07) \\
-child.went.to.preschool & 0.04 & 0.08 & 0.03 & 0.30* \\
-& (0.04) & (0.08) & (0.06) & (0.12) \\
-child.had.skipped.grade & -0.08 & -0.13 & -0.37† & 0.34 \\
-& (0.16) & (0.24) & (0.19) & (0.45) \\
-child.had.repeated.grade & -0.08 & -0.26* & -0.02 & 0.05 \\
-& (0.06) & (0.11) & (0.11) & (0.16) \\
-child.in.boarding.school & 0.09 & 0.15 & -0.10 & -0.02 \\
-& (0.07) & (0.12) & (0.11) & (0.20) \\
-child.educational.aspiration & 0.07*** & 0.03 & 0.10** & 0.10† \\
-& (0.02) & (0.03) & (0.03) & (0.05) \\
-child.is.ethnic.minority & -0.01 & 0.01 & -0.20 & 0.39 \\
-& (0.09) & (0.10) & (0.23) & (0.44) \\
-parent.expectation.on.child & 0.07** & 0.08† & 0.06† & 0.01 \\
-& (0.03) & (0.05) & (0.03) & (0.06) \\
-parent.has.white.collar.job & 0.02 & -0.10† & 0.03 & -0.15 \\
-& (0.05) & (0.05) & (0.08) & (0.16) \\
-parent.educational.level & 0.01 & 0.03 & 0.00 & -0.08 \\
-& (0.02) & (0.03) & (0.03) & (0.06) \\
-home.economic.resource & -0.05 & 0.00 & 0.02 & 0.05 \\
-& (0.03) & (0.05) & (0.05) & (0.08) \\
-home.extracurricular.book & 0.01 & 0.01 & 0.02 & 0.01 \\
-& (0.02) & (0.03) & (0.03) & (0.05) \\
-home.has.internet & -0.05 & -0.07 & -0.06 & 0.05 \\
-& (0.04) & (0.08) & (0.07) & (0.11) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.562 & 0.653 & 0.672 & 0.691 \\
-R2 Adj. & 0.413 & 0.337 & 0.361 & -0.318 \\
-R2 Within & 0.409 & 0.447 & 0.431 & 0.435 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic exam scores, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -2.91† & -5.90* & -2.68 & -2.94 \\
-& (1.48) & (2.64) & (2.56) & (4.21) \\
-W1 score & -0.01 & 0.01 & 0.00 & -0.03 \\
-& (0.03) & (0.04) & (0.05) & (0.06) \\
-child.age & -0.61 & 1.45 & 2.59 & -2.15 \\
-& (1.21) & (2.00) & (1.99) & (3.48) \\
-child.is.girl & 4.51** & 4.40† & 6.58** & 3.76 \\
-& (1.43) & (2.57) & (2.41) & (4.21) \\
-child.health.self.rated & 0.71 & 2.30 & 1.13 & 2.38 \\
-& (0.69) & (1.42) & (1.15) & (2.27) \\
-child.has.rural.hukou & 0.85 & -0.13 & -1.10 & -2.75 \\
-& (1.70) & (3.10) & (2.97) & (4.45) \\
-child.number.of.sibling & 1.20 & 1.92† & 1.00 & -2.50 \\
-& (1.06) & (1.06) & (1.61) & (2.69) \\
-child.went.to.preschool & 1.75 & -0.30 & -2.26 & 6.39 \\
-& (1.76) & (2.47) & (2.57) & (5.13) \\
-child.had.skipped.grade & 2.29 & -9.76 & 3.12 & 32.64 \\
-& (6.62) & (11.90) & (12.03) & (29.40) \\
-child.had.repeated.grade & -6.07† & -13.55† & -13.33** & -0.09 \\
-& (3.18) & (7.61) & (4.86) & (5.92) \\
-child.in.boarding.school & -0.64 & -0.65 & -3.42 & -3.10 \\
-& (3.53) & (5.38) & (4.25) & (8.17) \\
-child.educational.aspiration & 1.48† & 1.63 & 0.37 & 0.44 \\
-& (0.86) & (1.06) & (1.20) & (1.92) \\
-child.is.ethnic.minority & 3.81 & 4.84 & 2.79 & -2.54 \\
-& (4.31) & (4.68) & (6.53) & (7.64) \\
-parent.expectation.on.child & 0.19 & 1.71 & 1.41 & 3.97 \\
-& (0.83) & (1.49) & (1.35) & (2.49) \\
-parent.has.white.collar.job & -0.85 & 0.54 & 2.13 & -1.42 \\
-& (1.82) & (2.56) & (2.87) & (6.14) \\
-parent.educational.level & 1.30 & 2.30** & 1.91 & -2.63 \\
-& (0.97) & (0.85) & (1.41) & (2.54) \\
-home.economic.resource & -0.23 & -1.90 & -0.51 & -0.54 \\
-& (1.23) & (2.24) & (1.81) & (4.05) \\
-home.extracurricular.book & -0.66 & -0.66 & -1.59 & 0.08 \\
-& (0.71) & (1.24) & (1.01) & (1.93) \\
-home.has.internet & -2.89 & -1.61 & 0.08 & 3.67 \\
-& (1.81) & (2.87) & (3.26) & (4.98) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.603 & 0.702 & 0.660 & 0.731 \\
-R2 Adj. & 0.468 & 0.431 & 0.337 & -0.150 \\
-R2 Within & 0.037 & 0.088 & 0.070 & 0.087 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
+Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
+Besides top-down policymaking, bottom-up approaches are also necessary.
+School administrators could dedicate advisory and counseling programs.
+Social workers could provide paraprofessional training in communities (M.
+Wang et al., 2020).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-arel-bundock2022}{}}%
-Arel-Bundock, V.
-(2022).
-\emph{Modelsummary: Summary tables and plots for statistical models and data: Beautiful, customizable, and publication-ready}.
-\url{https://vincentarelbundock.github.io/modelsummary/}
+\leavevmode\vadjust pre{\hypertarget{ref-R-modelsummary}{}}%
+Arel-Bundock, V. (2022). {modelsummary}: Data and model summaries in {R}. \emph{Journal of Statistical Software}, \emph{103}(1), 1--23. \url{https://doi.org/10.18637/jss.v103.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://cran.r-project.org/web/packages/papaja/index.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-berge2022}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-fixest}{}}%
 Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bourdieu2002}{}}%
-Bourdieu, P. (2002). \emph{The Forms of Capital} (N. W. Biggart, Ed.; pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
+Bourdieu, P. (2002). The Forms of Capital. In N. W. Biggart (Ed.), \emph{Readings in Economic Sociology} (pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cebotari2020}{}}%
+Cebotari, V.
+(2020).
+Migration, remittances, and child education in ghana.
+Evidence from a longitudinal study.
+In M.
+Konte \& L.
+Mously Mbaye (Eds.), \emph{Migration, remittances, and sustainable development in africa} (pp.
+99--116).
+Routledge.
+\url{https://doi.org/10.4324/9780429288814-8}
+
 \leavevmode\vadjust pre{\hypertarget{ref-chan2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chen2020}{}}%
+Chen, T., Kung, J.
+K., \& Ma, C.
+(2020).
+Long Live Keju!
+The Persistent Effects of China{'}s Civil Examination System.
+\emph{The Economic Journal}, \emph{130}(631), 2030--2064.
+\url{https://doi.org/10.1093/ej/ueaa043}
+
 \leavevmode\vadjust pre{\hypertarget{ref-chen2009}{}}%
@@
 \url{https://doi.org/10.1080/10670564.2019.1594100}
+
+\leavevmode\vadjust pre{\hypertarget{ref-costalli2021}{}}%
+Costalli, S., \& Negri, F.
+(2021).
+Looking for twins: how to build better counterfactuals with matching.
+\emph{Italian Political Science Review / Rivista Italiana Di Scienza Politica}, \emph{51}(2), 215--230.
+\url{https://doi.org/10.1017/ipo.2021.1}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
-Goldin, C. (2016). \emph{Human Capital} (C. Diebolt \& M. Haupert, Eds.; pp. 55--86). Springer. \url{https://doi.org/10.1007/978-3-642-40406-1_23}
-
-\leavevmode\vadjust pre{\hypertarget{ref-greifer2022}{}}%
-Greifer, N. (2022). \emph{Matching methods}. \url{https://kosukeimai.github.io/MatchIt/articles/matching-methods.html}
+Goldin, C. (2016). Human Capital. In C. Diebolt \& M. Haupert (Eds.), \emph{Handbook of Cliometrics} (pp. 55--86). Springer. \url{https://doi.org/10.1007/978-3-642-40406-1_23}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-cobalt}{}}%
+Greifer, N. (2022). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ho2022}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-MatchIt}{}}%
 Ho, D., Imai, K., King, G., Stuart, E., Whitworth, A., \& Greifer, N.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-huang2020}{}}%
+Huang, Y., Liang, Z., Song, Q., \& Tao, R.
+(2020).
+Family Arrangements and Children's Education Among Migrants: A Case Study of China.
+\emph{International Journal of Urban and Regional Research}, \emph{44}(3), 484--504.
+\url{https://doi.org/10.1111/1468-2427.12649}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-vtable}{}}%
+Huntington-Klein, N. (2021). \emph{Vtable: Variable table for variable documentation}. \url{https://CRAN.R-project.org/package=vtable}
+
 \leavevmode\vadjust pre{\hypertarget{ref-huntington-klein2022}{}}%
-Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality \textbar{} The Effect}. CRC Press. \url{https://theeffectbook.net/index.html}
+Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality}. CRC Press. \url{https://theeffectbook.net/index.html}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-luo2013}{}}%
+Luo, R., Tamis-LeMonda, C.
+S., \& Song, L.
+(2013).
+Chinese parents{'} goals and practices in early childhood.
+\emph{Early Childhood Research Quarterly}, \emph{28}(4), 843--857.
+\url{https://doi.org/10.1016/j.ecresq.2013.08.001}
+
 \leavevmode\vadjust pre{\hypertarget{ref-meng2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moeller2015}{}}%
+Moeller, J. (2015). A word on standardization in longitudinal studies: don't. \emph{Frontiers in Psychology}, \emph{6}. \url{https://www.frontiersin.org/article/10.3389/fpsyg.2015.01389}
+
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2022}{}}%
 Murphy, R. (2022). What does {`}left behind{'} mean to children living in migratory regions in rural China? \emph{Geoforum}, \emph{129}, 181--190. \url{https://doi.org/10.1016/j.geoforum.2022.01.012}
+
+\leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
+Murphy, R. (2020). \emph{The children of china{'}s great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
 
@@
 \url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ng2020}{}}%
+Ng, F.
+F.-Y., \& Wei, J.
+(2020).
+Delving Into the Minds of Chinese Parents: What Beliefs Motivate Their Learning-Related Practices?
+\emph{Child Development Perspectives}, \emph{14}(1), 61--67.
+\url{https://doi.org/10.1111/cdep.12358}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021a}{}}%
-Parliamentary Assembly.
-(2021).
-\emph{Resolution 2366: Impact of labour migration on {``}left-behind{''} children}.
-\url{https://pace.coe.int/pdf/750b8aea81ea5b757d3b0db7f9865a27e4982ffbc23c9f49d28122e772e123ef/resolution\%202366.pdf}
+\leavevmode\vadjust pre{\hypertarget{ref-pan2018}{}}%
+Pan, W., \& Bai, H. (2018). Propensity score methods for causal inference: an overview. \emph{Behaviormetrika}, \emph{45}(2), 317--334. \url{https://doi.org/10.1007/s41237-018-0058-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021}{}}%
+Parliamentary Assembly. (2021). \emph{Resolution 2366: Impact of labour migration on {``}left-behind{''} children}. \url{https://pace.coe.int/en/files/29077/html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peng2018}{}}%
+Peng, Y.
+(2018).
+Migrant Mothering in Transition: A Qualitative Study of the Maternal Narratives and Practices of Two Generations of Rural-Urban Migrant Mothers in Southern China.
+\emph{Sex Roles}, \emph{79}(1), 16--35.
+\url{https://doi.org/10.1007/s11199-017-0855-7}
 
@@
 \url{https://doi.org/10.26758/8.1.3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-qian2021}{}}%
+Qian, J. (2021). \emph{The Political Economy of Making and Implementing Social Policy in China}. Springer Singapore. \url{https://doi.org/10.1007/978-981-16-5025-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-roberts2018}{}}%
+Roberts, P., \& Hannum, E.
+(2018).
+Education and Equity in Rural China: A critical introduction for the rural education field.
+\emph{Australian and International Journal of Rural Education}, \emph{28}(2).
+\url{https://doi.org/10.47381/aijre.v28i2.231}
+
+\leavevmode\vadjust pre{\hypertarget{ref-shen2021}{}}%
+Shen, W., Hu, L.-C., \& Hannum, E.
+(2021).
+Effect pathways of informal family separation on children's outcomes: Paternal labor migration and long-term educational attainment of left-behind children in rural China.
+\emph{Social Science Research}, \emph{97}, 102576.
+\url{https://doi.org/10.1016/j.ssresearch.2021.102576}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-vortherms2021}{}}%
-Vortherms, S. A. (2021). \emph{Hukou as a case of multi-level citizenship} (Z. Guo, Ed.; pp. 132--142). Routledge. \href{https://doi.org/10.4324/9781003225843-12}{doi.org/10.4324/9781003225843-12}
-
-\leavevmode\vadjust pre{\hypertarget{ref-waldman2022}{}}%
-Waldman, K.
-E.
-(2022).
-Transnational Social Stratification?
-Legal Status of Immigrant Parents and the Educational Achievements of Mexican Children.
-\emph{International Migration Review}, 01979183221084329.
-\url{https://doi.org/10.1177/01979183221084329}
+Vortherms, S.
+A.
+(2021).
+Hukou as a case of multi-level citizenship.
+In Z.
+Guo (Ed.), \emph{The Routledge Handbook of Chinese Citizenship} (pp.
+132--142).
+Routledge.
+\href{https://doi.org/10.4324/9781003225843-12}{doi.org/10.4324/9781003225843-12}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
-Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey {[}in chinese{]}}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
+Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey (in chinese)}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-xu2015}{}}%
-Xu, H., \& Xie, Y.
-(2015).
-The Causal Effects of Rural-to-Urban Migration on Children{'}s Well-being in China.
-\emph{European Sociological Review}, \emph{31}(4), 502--519.
-\url{https://doi.org/10.1093/esr/jcv009}
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
+L., Miller, E., Bache, S.
+M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
+P., Spinu, V., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-willis2019}{}}%
+Willis, P. (2019). \emph{Being Modern in China: A Western Cultural Analysis of Modernity, Tradition and Schooling in China Today}. Polity.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
+Zhan, Y.
+(2020).
+The moralization of philanthropy in China: NGOs, voluntarism, and the reconfiguration of social responsibility.
+\emph{China Information}, \emph{34}(1), 68--87.
+\url{https://doi.org/10.1177/0920203X19879593}
+
 \leavevmode\vadjust pre{\hypertarget{ref-zhang2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}
+
 \end{CSLReferences}
 
+\newpage
+
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{tables}{%
+\section{Tables}\label{tables}}
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test score}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.52}*** & \num{-2.12}* & \num{-3.00}** & \num{-2.43}†\\
+ & (\num{0.69}) & (\num{1.05}) & (\num{1.12}) & (\num{1.37})\\
+Baseline.score & \num{-0.79}*** & \num{-0.79}*** & \num{-0.78}*** & \num{-0.79}***\\
+ & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
+child.age & \num{-2.61}*** & \num{-2.56}*** & \num{-2.53}*** & \num{-2.51}***\\
+ & (\num{0.48}) & (\num{0.51}) & (\num{0.49}) & (\num{0.49})\\
+child.is.girl & \num{-0.75} & \num{-0.46} & \num{-0.73} & \num{-0.58}\\
+ & (\num{0.60}) & (\num{0.65}) & (\num{0.61}) & (\num{0.64})\\
+child.health & \num{-0.28} & \num{-0.22} & \num{-0.37} & \num{-0.25}\\
+ & (\num{0.33}) & (\num{0.33}) & (\num{0.35}) & (\num{0.34})\\
+child.has.rural.hukou & \num{0.13} & \num{0.47} & \num{0.22} & \num{0.67}\\
+ & (\num{0.63}) & (\num{0.64}) & (\num{0.67}) & (\num{0.70})\\
+child.number.of.sibling & \num{-0.99}* & \num{-1.06}* & \num{-0.89}* & \num{-0.96}*\\
+ & (\num{0.41}) & (\num{0.44}) & (\num{0.43}) & (\num{0.44})\\
+child.went.to.preschool & \num{2.33}** & \num{2.02}* & \num{2.21}** & \num{2.12}*\\
+ & (\num{0.79}) & (\num{0.87}) & (\num{0.83}) & (\num{0.87})\\
+child.had.skipped.grade & \num{-3.83} & \num{-3.84} & \num{-4.11} & \num{-2.98}\\
+ & (\num{2.64}) & (\num{2.76}) & (\num{2.73}) & (\num{2.90})\\
+child.had.repeated.grade & \num{-1.59} & \num{-2.61}* & \num{-1.92}† & \num{-1.45}\\
+ & (\num{0.96}) & (\num{1.19}) & (\num{1.14}) & (\num{1.14})\\
+child.in.boarding.school & \num{1.38} & \num{1.21} & \num{1.23} & \num{0.85}\\
+ & (\num{1.03}) & (\num{0.99}) & (\num{1.02}) & (\num{0.99})\\
+child.education.aspiration & \num{2.03}*** & \num{1.97}*** & \num{2.01}*** & \num{2.09}***\\
+ & (\num{0.29}) & (\num{0.31}) & (\num{0.29}) & (\num{0.31})\\
+child.is.ethnic.minority & \num{1.50} & \num{1.53} & \num{1.01} & \num{1.16}\\
+ & (\num{1.50}) & (\num{1.62}) & (\num{1.69}) & (\num{1.84})\\
+parent.expectation & \num{2.34}*** & \num{2.40}*** & \num{2.36}*** & \num{2.28}***\\
+ & (\num{0.35}) & (\num{0.35}) & (\num{0.34}) & (\num{0.34})\\
+parent.has.white.collar.job & \num{0.75} & \num{0.24} & \num{0.76} & \num{0.58}\\
+ & (\num{0.69}) & (\num{0.74}) & (\num{0.74}) & (\num{0.77})\\
+mother.education.level & \num{-0.02} & \num{0.02} & \num{-0.08} & \num{-0.16}\\
+ & (\num{0.31}) & (\num{0.33}) & (\num{0.36}) & (\num{0.35})\\
+father.education.level & \num{0.14} & \num{0.33} & \num{0.17} & \num{0.39}\\
+ & (\num{0.31}) & (\num{0.31}) & (\num{0.32}) & (\num{0.33})\\
+home.economic.resource & \num{-0.55} & \num{-0.60} & \num{-0.15} & \num{-0.15}\\
+ & (\num{0.52}) & (\num{0.53}) & (\num{0.52}) & (\num{0.55})\\
+home.extracurricular.book & \num{-0.03} & \num{-0.13} & \num{-0.09} & \num{-0.06}\\
+ & (\num{0.26}) & (\num{0.27}) & (\num{0.26}) & (\num{0.26})\\
+home.has.internet & \num{-0.56} & \num{-0.92} & \num{-0.85} & \num{-1.07}\\
+ & (\num{0.59}) & (\num{0.68}) & (\num{0.65}) & (\num{0.68})\\
+\midrule
+Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
+R2 & \num{0.424} & \num{0.427} & \num{0.430} & \num{0.432}\\
+R2 Adj. & \num{0.405} & \num{0.406} & \num{0.409} & \num{0.410}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam score}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.23}* & \num{-2.08}* & \num{-0.82} & \num{-0.13}\\
+ & (\num{0.53}) & (\num{0.84}) & (\num{0.71}) & (\num{0.76})\\
+Baseline.score & \num{-0.01} & \num{-0.01} & \num{-0.01} & \num{-0.01}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+child.age & \num{-0.44}* & \num{-0.40}† & \num{-0.44}* & \num{-0.37}\\
+ & (\num{0.19}) & (\num{0.20}) & (\num{0.21}) & (\num{0.22})\\
+child.is.girl & \num{1.62}*** & \num{1.68}*** & \num{1.60}*** & \num{1.54}***\\
+ & (\num{0.38}) & (\num{0.39}) & (\num{0.37}) & (\num{0.39})\\
+child.health & \num{0.37}** & \num{0.40}** & \num{0.27}† & \num{0.29}*\\
+ & (\num{0.13}) & (\num{0.13}) & (\num{0.15}) & (\num{0.14})\\
+child.has.rural.hukou & \num{0.34} & \num{0.41} & \num{0.21} & \num{0.33}\\
+ & (\num{0.40}) & (\num{0.39}) & (\num{0.38}) & (\num{0.39})\\
+child.number.of.sibling & \num{0.29} & \num{0.22} & \num{0.39}† & \num{0.21}\\
+ & (\num{0.19}) & (\num{0.20}) & (\num{0.22}) & (\num{0.22})\\
+child.went.to.preschool & \num{1.17}* & \num{1.41}** & \num{0.75}† & \num{1.28}**\\
+ & (\num{0.46}) & (\num{0.48}) & (\num{0.43}) & (\num{0.46})\\
+child.had.skipped.grade & \num{0.54} & \num{1.14} & \num{0.75} & \num{1.16}\\
+ & (\num{1.79}) & (\num{1.58}) & (\num{2.01}) & (\num{1.62})\\
+child.had.repeated.grade & \num{-0.44} & \num{-0.16} & \num{-0.19} & \num{0.20}\\
+ & (\num{0.70}) & (\num{0.77}) & (\num{0.80}) & (\num{0.85})\\
+child.in.boarding.school & \num{-0.38} & \num{-0.18} & \num{-0.29} & \num{-0.40}\\
+ & (\num{0.52}) & (\num{0.48}) & (\num{0.48}) & (\num{0.53})\\
+child.education.aspiration & \num{0.77}*** & \num{0.87}*** & \num{0.79}*** & \num{0.79}**\\
+ & (\num{0.21}) & (\num{0.25}) & (\num{0.21}) & (\num{0.25})\\
+child.is.ethnic.minority & \num{-0.02} & \num{-0.12} & \num{-0.32} & \num{-0.51}\\
+ & (\num{0.71}) & (\num{0.78}) & (\num{0.85}) & (\num{0.91})\\
+parent.expectation & \num{0.58}* & \num{0.52}* & \num{0.58}* & \num{0.59}*\\
+ & (\num{0.25}) & (\num{0.24}) & (\num{0.28}) & (\num{0.27})\\
+parent.has.white.collar.job & \num{0.27} & \num{0.11} & \num{0.32} & \num{0.17}\\
+ & (\num{0.40}) & (\num{0.43}) & (\num{0.42}) & (\num{0.45})\\
+mother.education.level & \num{0.00} & \num{-0.01} & \num{0.06} & \num{0.12}\\
+ & (\num{0.18}) & (\num{0.19}) & (\num{0.17}) & (\num{0.18})\\
+father.education.level & \num{0.19} & \num{0.28} & \num{0.21} & \num{0.19}\\
+ & (\num{0.19}) & (\num{0.19}) & (\num{0.19}) & (\num{0.19})\\
+home.economic.resource & \num{-0.25} & \num{-0.07} & \num{-0.14} & \num{-0.12}\\
+ & (\num{0.27}) & (\num{0.28}) & (\num{0.29}) & (\num{0.27})\\
+home.extracurricular.book & \num{-0.28}† & \num{-0.43}** & \num{-0.31}† & \num{-0.31}*\\
+ & (\num{0.17}) & (\num{0.16}) & (\num{0.17}) & (\num{0.15})\\
+home.has.internet & \num{-0.41} & \num{-0.46} & \num{-0.32} & \num{-0.33}\\
+ & (\num{0.37}) & (\num{0.39}) & (\num{0.40}) & (\num{0.41})\\
+\midrule
+Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
+R2 & \num{0.499} & \num{0.518} & \num{0.502} & \num{0.518}\\
+R2 Adj. & \num{0.482} & \num{0.500} & \num{0.483} & \num{0.500}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.52}*** & \num{-2.52}* & \num{-3.50}** & \num{-2.12}\\
+ & (\num{0.72}) & (\num{1.14}) & (\num{1.27}) & (\num{1.71})\\
+Baseline.score & \num{-0.78}*** & \num{-0.81}*** & \num{-0.71}*** & \num{-0.75}***\\
+ & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
+child.age & \num{-3.14}*** & \num{-1.66} & \num{-3.31}*** & \num{-2.72}*\\
+ & (\num{0.58}) & (\num{1.01}) & (\num{0.90}) & (\num{1.27})\\
+child.is.girl & \num{-1.27}† & \num{-0.63} & \num{-1.61} & \num{-1.89}\\
+ & (\num{0.71}) & (\num{1.12}) & (\num{1.09}) & (\num{1.63})\\
+child.health & \num{-0.38} & \num{0.52} & \num{-0.68} & \num{0.36}\\
+ & (\num{0.41}) & (\num{0.66}) & (\num{0.70}) & (\num{0.86})\\
+child.has.rural.hukou & \num{-0.72} & \num{-0.48} & \num{-2.46}† & \num{-3.39}†\\
+ & (\num{0.89}) & (\num{1.45}) & (\num{1.41}) & (\num{1.85})\\
+child.number.of.sibling & \num{-0.60} & \num{-1.99}** & \num{-0.45} & \num{-1.43}\\
+ & (\num{0.54}) & (\num{0.71}) & (\num{0.84}) & (\num{1.10})\\
+child.went.to.preschool & \num{2.11}* & \num{0.27} & \num{3.26}** & \num{4.12}*\\
+ & (\num{0.91}) & (\num{1.45}) & (\num{1.03}) & (\num{1.94})\\
+child.had.skipped.grade & \num{-3.08} & \num{-2.72} & \num{-8.72}* & \num{2.29}\\
+ & (\num{2.75}) & (\num{5.27}) & (\num{3.72}) & (\num{6.39})\\
+child.had.repeated.grade & \num{-0.95} & \num{-6.19}† & \num{-2.20} & \num{-0.01}\\
+ & (\num{1.05}) & (\num{3.24}) & (\num{1.61}) & (\num{2.19})\\
+child.in.boarding.school & \num{1.73} & \num{1.97} & \num{0.55} & \num{-1.64}\\
+ & (\num{1.23}) & (\num{2.06}) & (\num{1.99}) & (\num{2.64})\\
+child.education.aspiration & \num{1.73}*** & \num{1.18}* & \num{1.08}** & \num{2.07}**\\
+ & (\num{0.36}) & (\num{0.58}) & (\num{0.37}) & (\num{0.79})\\
+child.is.ethnic.minority & \num{1.33} & \num{1.52} & \num{3.98} & \num{3.44}\\
+ & (\num{1.59}) & (\num{2.04}) & (\num{3.21}) & (\num{3.82})\\
+parent.expectation & \num{2.34}*** & \num{3.45}*** & \num{2.40}*** & \num{1.37}\\
+ & (\num{0.46}) & (\num{0.77}) & (\num{0.64}) & (\num{0.95})\\
+parent.has.white.collar.job & \num{1.19} & \num{0.37} & \num{0.32} & \num{-6.22}*\\
+ & (\num{0.91}) & (\num{1.12}) & (\num{1.71}) & (\num{3.10})\\
+mother.education.level & \num{0.11} & \num{0.57} & \num{0.14} & \num{-1.02}\\
+ & (\num{0.39}) & (\num{0.68}) & (\num{0.84}) & (\num{1.19})\\
+father.education.level & \num{0.05} & \num{-0.09} & \num{0.45} & \num{1.06}\\
+ & (\num{0.41}) & (\num{0.50}) & (\num{0.69}) & (\num{1.13})\\
+home.economic.resource & \num{-0.58} & \num{-2.71}** & \num{0.40} & \num{0.43}\\
+ & (\num{0.74}) & (\num{1.03}) & (\num{1.10}) & (\num{1.27})\\
+home.extracurricular.book & \num{0.03} & \num{0.02} & \num{-0.38} & \num{0.84}\\
+ & (\num{0.37}) & (\num{0.48}) & (\num{0.50}) & (\num{0.70})\\
+home.has.internet & \num{-1.26} & \num{1.94} & \num{-0.44} & \num{-3.04}†\\
+ & (\num{0.79}) & (\num{1.87}) & (\num{1.25}) & (\num{1.79})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.438} & \num{0.495} & \num{0.477} & \num{0.523}\\
+R2 Adj. & \num{0.407} & \num{0.424} & \num{0.404} & \num{0.394}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.24}* & \num{-1.88}* & \num{-1.33} & \num{0.47}\\
+ & (\num{0.57}) & (\num{0.81}) & (\num{0.87}) & (\num{1.06})\\
+Baseline.score & \num{-0.01} & \num{0.00} & \num{-0.02} & \num{-0.08}\\
+ & (\num{0.03}) & (\num{0.05}) & (\num{0.04}) & (\num{0.06})\\
+child.age & \num{-0.20} & \num{-0.71} & \num{-0.43} & \num{-0.69}\\
+ & (\num{0.28}) & (\num{0.50}) & (\num{0.44}) & (\num{0.56})\\
+child.is.girl & \num{1.94}*** & \num{1.69}*** & \num{1.99}** & \num{3.48}**\\
+ & (\num{0.52}) & (\num{0.49}) & (\num{0.61}) & (\num{1.29})\\
+child.health & \num{0.45}* & \num{0.73}** & \num{0.75}* & \num{0.28}\\
+ & (\num{0.20}) & (\num{0.26}) & (\num{0.34}) & (\num{0.65})\\
+child.has.rural.hukou & \num{0.05} & \num{0.60} & \num{0.31} & \num{2.16}†\\
+ & (\num{0.48}) & (\num{0.65}) & (\num{0.65}) & (\num{1.12})\\
+child.number.of.sibling & \num{0.21} & \num{0.02} & \num{0.01} & \num{-0.30}\\
+ & (\num{0.28}) & (\num{0.27}) & (\num{0.42}) & (\num{0.62})\\
+child.went.to.preschool & \num{1.44}* & \num{1.38}† & \num{-0.34} & \num{3.27}*\\
+ & (\num{0.59}) & (\num{0.74}) & (\num{0.77}) & (\num{1.41})\\
+child.had.skipped.grade & \num{0.91} & \num{-0.66} & \num{0.43} & \num{5.78}†\\
+ & (\num{2.34}) & (\num{1.42}) & (\num{3.12}) & (\num{3.44})\\
+child.had.repeated.grade & \num{-0.37} & \num{-2.82}† & \num{-2.23}* & \num{1.40}\\
+ & (\num{0.84}) & (\num{1.54}) & (\num{0.97}) & (\num{1.85})\\
+child.in.boarding.school & \num{-0.25} & \num{1.60} & \num{0.66} & \num{-1.63}\\
+ & (\num{0.74}) & (\num{1.13}) & (\num{0.85}) & (\num{1.70})\\
+child.education.aspiration & \num{0.70}** & \num{0.81}† & \num{0.85}** & \num{0.27}\\
+ & (\num{0.23}) & (\num{0.41}) & (\num{0.30}) & (\num{0.56})\\
+child.is.ethnic.minority & \num{0.69} & \num{0.18} & \num{2.24} & \num{0.11}\\
+ & (\num{0.72}) & (\num{1.05}) & (\num{1.42}) & (\num{2.54})\\
+parent.expectation & \num{0.76}** & \num{0.51} & \num{0.36} & \num{0.91}\\
+ & (\num{0.28}) & (\num{0.36}) & (\num{0.44}) & (\num{0.60})\\
+parent.has.white.collar.job & \num{0.47} & \num{0.09} & \num{0.54} & \num{1.35}\\
+ & (\num{0.43}) & (\num{0.57}) & (\num{0.75}) & (\num{1.24})\\
+mother.education.level & \num{-0.10} & \num{0.19} & \num{0.20} & \num{-0.79}\\
+ & (\num{0.23}) & (\num{0.32}) & (\num{0.35}) & (\num{0.57})\\
+father.education.level & \num{0.15} & \num{-0.21} & \num{-0.01} & \num{0.04}\\
+ & (\num{0.26}) & (\num{0.36}) & (\num{0.34}) & (\num{0.57})\\
+home.economic.resource & \num{-0.16} & \num{0.20} & \num{-0.39} & \num{-0.39}\\
+ & (\num{0.36}) & (\num{0.59}) & (\num{0.51}) & (\num{0.69})\\
+home.extracurricular.book & \num{-0.36} & \num{-0.35} & \num{-0.40} & \num{0.51}\\
+ & (\num{0.23}) & (\num{0.31}) & (\num{0.30}) & (\num{0.49})\\
+home.has.internet & \num{-0.86}* & \num{-0.79} & \num{-1.48}* & \num{-0.83}\\
+ & (\num{0.41}) & (\num{0.83}) & (\num{0.62}) & (\num{1.17})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.491} & \num{0.609} & \num{0.512} & \num{0.544}\\
+R2 Adj. & \num{0.463} & \num{0.554} & \num{0.445} & \num{0.421}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{figures}{%
+\section{Figures}\label{figures}}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-cog-1} \caption{Changes in cognitive test score for newly left-behind students and non-left-behind students}\label{fig:v-plot-cog}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-ttl-1} \caption{Changes in academic exam score for newly left-behind students and non-left-behind students}\label{fig:v-plot-ttl}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-cog-1-1} \caption{Changes in cognitive test score by household migration arrangement}\label{fig:v-plot-cog-1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-ttl-1-1} \caption{Changes in academic exam score by household migration arrangement}\label{fig:v-plot-ttl-1}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-any-1} \caption{Covariate balance before and after matching by any parent migration}\label{fig:cobal-any}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-mo-1} \caption{Covariate balance before and after matching by mother-only migration}\label{fig:cobal-mo}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-fa-1} \caption{Covariate balance before and after matching by father-only migration}\label{fig:cobal-fa}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-both-1} \caption{Covariate balance before and after matching by both parents migration}\label{fig:cobal-both}
+\end{figure}
+
 \end{document}

### 2022-07-03 data/Gu-thesis-script.Rmd
almost there

@@
 library(vtable)
-library(ggplot2)
 library(labelled)
 library(cobalt) 
+options(modelsummary_get="broom")
 #library(gtsummary)
@@
 d <- d |> mutate(
-  child.age = 2013 - a02a, #student's age at baseline
   w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
@@
   w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
+  w1avg_100 = w1ttl_100/3,
+  w2avg_100 = w2ttl_100/3,
+  w1cog_100 = stcog*100/20,
+  w2cog_100 = w2cogscore*100/35,
   ttl_dif = w2ttl_100 - w1ttl_100,
-  cog_dif = w2cog3pl - cog3pl
-  )
-```
-
-```{r}
-d1 <- d |>
-  drop_na(cog_dif, ttl_dif, child.age)
+  avg_dif = w2avg_100 - w1avg_100,
+  cog_dif = w2cog_100 - w1cog_100,
+  #cog_std_dif = w2cog3pl - cog3pl
+  )
+```
+
+```{r}
+d_cl <- d |>
+  drop_na(cog_dif, avg_dif)
 ```
@@
 ```{}
-d1 <- d1 |> group_by(clsids + w2clsids) |>
+d1 <- d1 |> group_by(schids) |>
   mutate(
@@
 d_outlier <- d |> filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
-d_outlier1 <- d_outlier |> select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
-d1 <- d |> anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
+d_outlier1 <- d_outlier |> select(clsids, schids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
+d1 <- d |> anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
@@
 ```{r}
-d_cl <- d1 |> 
+d_cl <- d |> 
+  drop_na(cog_dif, avg_dif) |> 
   filter(w2a0801==1) |> #keep parents who are married (and alive)
@@
 d_cl <- d_cl |> mutate(
+         child.age = 2013 - a02a, #student's age at baseline
          child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
@@
          child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         child.health.self.rated = a17, #student's self-rated health
+         child.health = a17, #student's self-rated health
          child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
@@
          child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
+         child.number.of.sibling = if_else(stonly == 1, 0, stsib),
          #ch.par.rltn = if_else(stprrel == 2, 1, 0),
          #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
-         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
          parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
@@
 ) |> drop_na(
-child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu,
+child.age, child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
 #par.ccp, 
@@
 
-```{r}
+```{}
 d_cl$stsib <- d_cl$stsib |> replace_na(0) |> as.numeric()
@@
 Best-educated parent's years of education
-```{}
-d_cl <- d_cl |> mutate(parent.educational.level = NA)
-d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
-d_cl$parent.educational.level[d_cl$par.edu == 2] <- 6
-d_cl$parent.educational.level[d_cl$par.edu == 3] <- 9
-d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
-d_cl$parent.educational.level[d_cl$par.edu == 7] <- 15
-d_cl$parent.educational.level[d_cl$par.edu == 8] <- 16
-d_cl$parent.educational.level[d_cl$par.edu == 9] <- 19
-```
-
-```{r}
-d_cl <- d_cl |> mutate(parent.educational.level = NA)
-d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
-d_cl$parent.educational.level[d_cl$par.edu == 3] <- 2
-d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 3
-d_cl$parent.educational.level[d_cl$par.edu == 7] <- 4
-d_cl$parent.educational.level[d_cl$par.edu == 8] <- 5
-d_cl$parent.educational.level[d_cl$par.edu == 9] <- 6
-```
-
-```{r}
-d_cl <- d_cl |> mutate(parent.expectation.on.child = NA)
-d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
-d_cl$parent.expectation.on.child[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
-d_cl$parent.expectation.on.child[d_cl$ba18 == 6] <- 3
-d_cl$parent.expectation.on.child[d_cl$ba18 == 7] <- 4
-d_cl$parent.expectation.on.child[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
-```
-
-```{r}
-d_cl <- d_cl |> mutate(child.educational.aspiration = NA)
-d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
-d_cl$child.educational.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
-d_cl$child.educational.aspiration[d_cl$c22 == 6] <- 3
-d_cl$child.educational.aspiration[d_cl$c22 == 7] <- 4
-d_cl$child.educational.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
+```{r}
+d_cl <- d_cl |> mutate(parent.education.level = NA)
+d_cl$parent.education.level[d_cl$stprhedu == 1|d_cl$stprhedu == 2] <- 0
+d_cl$parent.education.level[d_cl$stprhedu == 3] <- 1
+d_cl$parent.education.level[d_cl$stprhedu == 4|d_cl$stprhedu == 5|d_cl$stprhedu == 6] <- 2
+d_cl$parent.education.level[d_cl$stprhedu == 7] <- 3
+d_cl$parent.education.level[d_cl$stprhedu == 8] <- 4
+d_cl$parent.education.level[d_cl$stprhedu == 9] <- 5
+```
+
+```{r}
+d_cl <- d_cl |> mutate(mother.education.level = NA)
+d_cl$mother.education.level[d_cl$stmedu == 1|d_cl$stmedu == 2] <- 0
+d_cl$mother.education.level[d_cl$stmedu == 3] <- 1
+d_cl$mother.education.level[d_cl$stmedu == 4|d_cl$stmedu == 5|d_cl$stmedu == 6] <- 2
+d_cl$mother.education.level[d_cl$stmedu == 7] <- 3
+d_cl$mother.education.level[d_cl$stmedu == 8] <- 4
+d_cl$mother.education.level[d_cl$stmedu == 9] <- 5
+```
+
+```{r}
+d_cl <- d_cl |> mutate(father.education.level = NA)
+d_cl$father.education.level[d_cl$stfedu == 1|d_cl$stfedu == 2] <- 0
+d_cl$father.education.level[d_cl$stfedu == 3] <- 1
+d_cl$father.education.level[d_cl$stfedu == 4|d_cl$stfedu == 5|d_cl$stfedu == 6] <- 2
+d_cl$father.education.level[d_cl$stfedu == 7] <- 3
+d_cl$father.education.level[d_cl$stfedu == 8] <- 4
+d_cl$father.education.level[d_cl$stfedu == 9] <- 5
+```
+
+```{r}
+d_cl <- d_cl |> mutate(parent.expectation = NA)
+d_cl$parent.expectation[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
+d_cl$parent.expectation[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
+d_cl$parent.expectation[d_cl$ba18 == 6] <- 3
+d_cl$parent.expectation[d_cl$ba18 == 7] <- 4
+d_cl$parent.expectation[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
+```
+
+```{r}
+d_cl <- d_cl |> mutate(child.education.aspiration = NA)
+d_cl$child.education.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
+d_cl$child.education.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
+d_cl$child.education.aspiration[d_cl$c22 == 6] <- 3
+d_cl$child.education.aspiration[d_cl$c22 == 7] <- 4
+d_cl$child.education.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
 ```
@@
 d_cl <- d_cl |>  drop_na(
-  parent.educational.level, 
-  parent.expectation.on.child, 
-  child.educational.aspiration)
+  parent.education.level, 
+  parent.expectation, 
+  child.education.aspiration)
 ```
@@
   cog3pl, w1ttl_100, cog_dif, ttl_dif,
-  child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.educational.aspiration,
+  child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.education.aspiration,
   par.edu, par.ccp, par.expt.univ, 
@@
   migr, migr_mo_only, migr_fa_only, migr_both,
-  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
+  w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
   child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
-  child.health.self.rated, child.educational.aspiration, 
-  parent.educational.level, parent.expectation.on.child, 
+  child.health, child.education.aspiration, 
+  mother.education.level, father.education.level, parent.expectation, 
   home.extracurricular.book, home.economic.resource) 
@@
 d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
-d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother Migrated'
-d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father Migrated'
-d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
+d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
+d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
+d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
 d_smr <- d_smr |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
@@
 
-```{r}
+```{}
 datasummary_balance(
@@
   select(migr, 
-         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) |>
+         cog_dif, w1cog_100, w2cog_100, avg_dif, w1avg_100, w2avg_100) |>
   set_variable_labels(
     migr = 'Parental migration',
-    cog3pl ='Wave 1 score',
-    w2cog3pl = 'Wave 2 score',
-    w1ttl_100='Wave 1 score',
-    w2ttl_100 = 'Wave 2 score',
+    w1cog_100 ='Wave 1 score',
+    w2cog_100 = 'Wave 2 score',
+    w1avg_100 ='Wave 1 score',
+    w2avg_100 = 'Wave 2 score',
     cog_dif = 'Cognitive test score difference',
-    ttl_dif = 'Academic exam score difference'
+    avg_dif = 'Academic exam score difference'
   )
@@
 tab_dpvar <- tab_dpvar[-c(1),]
-tab_dpvar[tab_dpvar == 'p=&lt0.001***'] <- 'p<0.001***'
+tab_dpvar[tab_dpvar =='p=&lt0.001***']<-'p<0.001***'
 tab_dpvar 
@@
   data = d_dpvar,
-  output = 'markdown'
+  output = 'latex'
   ) 
@@
 d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents'
 d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+```
+
+```{r}
+tab_idpvar <- st(
+  data = d_idpvar,
+  out = 'return'
+)
+tab_idpvar[tab_idpvar == 4062] <- ''
+tab_idpvar
 ```
@@
     type = 'categorical',
+    title = 'Independent variables',
     output = 'markdown')
@@
 d_ctvar_cnt <- d_migr |>
-  select(migr, child.age, child.health.self.rated, child.educational.aspiration, 
-  parent.educational.level, parent.expectation.on.child, 
+  select(migr, child.age, child.health, child.education.aspiration, 
+  mother.education.level, father.education.level, parent.expectation, 
   home.extracurricular.book, home.economic.resource)
@@
 ```{r}
-d_ctvar <- d_ctvar |> 
+d_ctvar_label <- d_ctvar_cnt|>
+  select(!(child.age:migr)) |> 
   add_value_labels(
-    parent.educational.level = c(
-     'Primary school and below' = 1,
-     'Junior high school' = 2 ,
-     'Senior high school' = 3,
-     'Associate college' = 4,
-     'University' = 5,
-     'Postgraduate' = 6),
-    child.educational.aspiration = c(
-     'Junior high school' = 1 ,
-     'Senior high school' = 2,
-     'Associate college' = 3,
-     'University' = 4,
-     'Postgraduate' = 5),
-    child.educational.aspiration = c(
-     'Junior high school' = 1 ,
-     'Senior high school' = 2,
-     'Associate college' = 3,
-     'University' = 4,
-     'Postgraduate' = 5), 
-    parent.expectation.on.child = c(
-     'Junior high school' = 1 ,
-     'Senior high school' = 2,
-     'Associate college' = 3,
-     'University' = 4,
-     'Postgraduate' = 5),
+    father.education.level = c(
+     '0 = Primary school and below' = 0,
+     '1 = Junior high school' = 1 ,
+     '2 = Senior high school' = 2,
+     '3 = Associate college' = 3,
+     '4 = University' = 4,
+     '5 = Postgraduate' = 5),
+    mother.education.level = c(
+     '0 = Primary school and below' = 0,
+     '1 = Junior high school' = 1 ,
+     '2 = Senior high school' = 2,
+     '3 = Associate college' = 3,
+     '4 = University' = 4,
+     '5 = Postgraduate' = 5),
+    child.education.aspiration = c(
+     '1 = Junior high school' = 1 ,
+     '2 = Senior high school' = 2,
+     '3 = Associate college' = 3,
+     '4 = University' = 4,
+     '5 = Postgraduate' = 5),
+    child.education.aspiration = c(
+     '1 = Junior high school' = 1 ,
+     '2 = Senior high school' = 2,
+     '3 = Associate college' = 3,
+     '4 = University' = 4,
+     '5 = Postgraduate' = 5), 
+    parent.expectation = c(
+     '1 = Junior high school' = 1 ,
+     '2 = Senior high school' = 2,
+     '3 = Associate college' = 3,
+     '4 = University' = 4,
+     '5 = Postgraduate' = 5),
     home.economic.resource = c(
-      'Very poor' = 1,
-      'Somewhat poor' = 2,
-      'Moderate' = 3,
-      'Somewhat rich' = 4,
-      'Very rich' = 5),
-    child.health.self.rated = c(
-      'Very poor' = 1,
-      'Somewhat poor' = 2,
-      'Moderate' = 3,
-      'Good' = 4,
-      'Very good' = 5),
+      '1 = Very poor' = 1,
+      '2 = Somewhat poor' = 2,
+      '3 = Moderate' = 3,
+      '4 = Somewhat rich' = 4,
+      '5 = Very rich' = 5),
+    child.health = c(
+      '1 = Very poor' = 1,
+      '2 = Somewhat poor' = 2,
+      '3 = Moderate' = 3,
+      '4 = Good' = 4,
+      '5 = Very good' = 5),
     home.extracurricular.book = c(
-      'Very few' = 1,
-      'Not many' = 2,
-      'Some' = 3,
-      'Quite a few' = 4,
-      'A great number' = 5),
-    )
+      '1 = Very few' = 1,
+      '2 = Not many' = 2,
+      '3 = Some' = 3,
+      '4 = Quite a few' = 4,
+      '5 = A great number' = 5),
+    ) |>
+  as_factor()
 ```
@@
 ```{r}
-test_table <- datasummary_balance(
-  ~migr,
-  data = d_ctvar,
-  output = 'markdown'
-)
-test_table
+table_variable <- datasummary_skim(
+  data = d_ctvar_label,
+  type = 'categorical',
+  title = 'Measurement of categorical variables',
+  output = 'latex'
+)
+#table_variable
+```
+
+```{r}
+tab_var <- st(
+  data = d_ctvar_label,
+  out = 'return'
+)
+tab_var[tab_var == 4062] <- ''
+tab_var
 ```
@@
 tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
-tab_ctvar_dit[tab_ctvar_dit == 3452|tab_ctvar_dit == 636] <- ''
-```
-
-```{}
+tab_ctvar_dit[tab_ctvar_dit == 3422|tab_ctvar_dit == 640] <- ''
+tab_ctvar_dit 
+```
+
+```{r}
 tab_ctvar_cnt <- d_ctvar_cnt |> st(
@@
 tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
+tab_ctvar_cnt
 ```
@@
   type = 'categorical',
-  output = 'markdown'
+  output = 'latex'
 )
@@
 
-```{r}
-table_sum <- d_ctvar |> st(
-  group = 'migr',
-  summ = c('mean(x)', 'sd(x)'),
-  digits = 2, 
-  out = 'return')
-table_sum
-```
-
 t-test
-```{r}
+```{}
 ttest_cog <- t.test(cog_dif ~ migr, data = d_cl)
-ttest_ttl <- t.test(ttl_dif ~ migr, data = d_cl)
+ttest_ttl <- t.test(avg_dif ~ migr, data = d_cl)
 ttest_cog
@@
       width = 0.5) +
-  scale_fill_manual(values = alpha(c("green", "red"), .3))
+  scale_fill_manual(values = alpha(c("green", "red"), .4))
 fig_cog
@@
 fig_ttl <-  d_smr |>
-  ggplot(aes(x=`Parental Migration`, y=ttl_dif, fill=`Parental Migration`)) + 
+  ggplot(aes(x=`Parental Migration`, y=avg_dif, fill=`Parental Migration`)) + 
     geom_violin()+
@@
       width = 0.5) +
-  scale_fill_manual(values = alpha(c("green", "red"), .3))
+  scale_fill_manual(values = alpha(c("green", "red"), .4))
 fig_ttl
@@
 fig_cog_by_migration_type <- d_smr |>
-  ggplot(aes(x=`Parental Migration Type`, y=cog_dif)) + 
+  ggplot(aes(x=`Parental Migration Type`, y=cog_dif, fill = `Parental Migration Type`)) + 
     geom_violin()+
@@
       geom = "crossbar", 
-      width = 0.5)
+      width = 0.5)+
+  scale_fill_manual(values = alpha(c("green", "tomato1", "tomato2", "tomato3"), .4))
 fig_cog_by_migration_type
@@
 fig_ttl_by_migration_type <- d_smr |>
-  ggplot(aes(x=`Parental Migration Type`, y=ttl_dif)) + 
+  ggplot(aes(x=`Parental Migration Type`, y=avg_dif, fill = `Parental Migration Type`)) + 
     geom_violin()+
@@
       geom = "crossbar", 
-      width = 0.5)
+      width = 0.5) +
+  scale_fill_manual(values = alpha(c("green", "tomato1", "tomato2", "tomato3"), .4))
 fig_ttl_by_migration_type
@@
 ```{r}
-did_cog <- feols(cog_dif ~ migr + cog3pl | clsids + w2clsids, data = d_cl) 
-did_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | clsids + w2clsids, data = d_cl) 
-#did_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | clsids + w2clsids, data = d_cl) 
-did_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | clsids + w2clsids, data = d_cl) 
-#did_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | clsids + w2clsids, data = d_cl) 
-did_cog_both <- feols(cog_dif ~ migr_both + cog3pl | clsids + w2clsids, data = d_cl)
+did_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = d_cl) 
+did_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = d_cl) 
+#did_cog_m <- feols(cog_dif ~ migr_mo + w1cog_100 | schids, data = d_cl) 
+did_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = d_cl) 
+#did_cog_f <- feols(cog_dif ~ migr_fa + w1cog_100 | schids, data = d_cl) 
+did_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = d_cl)
 ```
@@
 models_cog <- list(
-'Any Parent Migrated' = did_cog,
-'Only Mother Migrated' = did_cog_m_only,
-#'Mother Migrated' = #did_cog_m,
-'Only Father Migrated' = did_cog_f_only,
-#'Father Migrated' = #did_cog_f,
-'Both Parents Migrated' = did_cog_both) 
+'Any Parent' = did_cog,
+'Only Mother' = did_cog_m_only,
+#'Mother' = #did_cog_m,
+'Only Father' = did_cog_f_only,
+#'Father' = #did_cog_f,
+'Both Parents' = did_cog_both) 
 ```
@@
 stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
-coef_rename <- c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "cog3pl" = "W1 score", "w1ttl_100" = "W1 score")
+coef_rename <- c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1cog_100" = "Baseline.score", "w1avg_100" = "Baseline.score")
 title_cog <- 'Parental migration’s effect on children’s cognitive test score'
 title_ttl <- 'Parental migration’s effect on children’s academic exam score'
-gof_omit <- 'R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
-note_unadj <- 'Control variables not included'
+gof_omit <- 'R2 Within|R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
+note_unadj <- 'No control variables included in these models'
 ```
@@
   notes = note_unadj,
-  output = 'markdown')
-table_cog
+  output = 'latex')
+#table_cog
 ```
@@
 ```{r}
-did_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | clsids + w2clsids, data = d_cl) 
-did_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | clsids + w2clsids, data = d_cl) 
-#did_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | clsids + w2clsids, data = d_cl) 
-did_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | clsids + w2clsids, data = d_cl) 
-#did_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | clsids + w2clsids, data = d_cl) 
-did_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | clsids + w2clsids, data = d_cl)
+did_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = d_cl) 
+did_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = d_cl) 
+#did_ttl_m <- feols(avg_dif ~ migr_mo + w1avg_100 | schids, data = d_cl) 
+did_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = d_cl) 
+#did_ttl_f <- feols(avg_dif ~ migr_fa + w1avg_100 | schids, data = d_cl) 
+did_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = d_cl)
 ```
@@
 models_ttl <- list(
-'Any Parent Migrated' = did_ttl,
-'Only Mother Migrated' = did_ttl_m_only,
-#'Mother Migrated' = #did_ttl_m,
-'Only Father Migrated' = did_ttl_f_only,
-#'Father Migrated' = #did_ttl_f,
-'Both Parents Migrated' = did_ttl_both) 
+'Any Parent' = did_ttl,
+'Only Mother' = did_ttl_m_only,
+#'Mother' = #did_ttl_m,
+'Only Father' = did_ttl_f_only,
+#'Father' = #did_ttl_f,
+'Both Parents' = did_ttl_both) 
 ```
@@
   notes = note_unadj,
-  output = 'markdown')
-table_ttl
+  output = 'latex')
+#table_ttl
 ```
@@
 ```{}
-did_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | clsids + w2clsids, data = d_cl) 
-did_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | clsids + w2clsids, data = d_cl) 
-did_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | clsids + w2clsids, data = d_cl) 
-did_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | clsids + w2clsids, data = d_cl) 
-did_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | clsids + w2clsids, data = d_cl) 
-did_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | clsids + w2clsids, data = d_cl)
+did_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | schids, data = d_cl) 
+did_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | schids, data = d_cl) 
+did_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | schids, data = d_cl) 
+did_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | schids, data = d_cl) 
+did_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | schids, data = d_cl) 
+did_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | schids, data = d_cl)
 ```
@@
 models_ttl_z <- list(
-'Any Parent Migrated' = did_ttl_z,
-'Only Mother Migrated' = did_ttl_z_m_only,
-#'Mother Migrated' = did_ttl_z_m,
-'Only Father Migrated' = did_ttl_z_f_only,
-#'Father Migrated' = did_ttl_z_f,
-'Both Parents Migrated' = did_ttl_z_both) 
+'Any Parent' = did_ttl_z,
+'Only Mother' = did_ttl_z_m_only,
+#'Mother' = did_ttl_z_m,
+'Only Father' = did_ttl_z_f_only,
+#'Father' = did_ttl_z_f,
+'Both Parents' = did_ttl_z_both) 
 table_ttl_z <- models_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
-                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
 table_ttl_z
@@
 ```{}
-did_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | clsids + w2clsids, data = d_cl) 
-did_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | clsids + w2clsids, data = d_cl) 
-did_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | clsids + w2clsids, data = d_cl) 
-did_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | clsids + w2clsids, data = d_cl) 
-did_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | clsids + w2clsids, data = d_cl) 
-did_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | clsids + w2clsids, data = d_cl)
+did_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | schids, data = d_cl) 
+did_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
+did_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | schids, data = d_cl) 
+did_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
+did_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | schids, data = d_cl) 
+did_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | schids, data = d_cl)
 ```
@@
 models_ttl_std <- list(
-'Any Parent Migrated' = did_ttl_std,
-'Only Mother Migrated' = did_ttl_std_m_only,
-#'Mother Migrated' = did_ttl_std_m,
-'Only Father Migrated' = did_ttl_std_f_only,
-#'Father Migrated' = did_ttl_std_f,
-'Both Parents Migrated' = did_ttl_std_both) 
+'Any Parent' = did_ttl_std,
+'Only Mother' = did_ttl_std_m_only,
+#'Mother' = did_ttl_std_m,
+'Only Father' = did_ttl_std_f_only,
+#'Father' = did_ttl_std_f,
+'Both Parents' = did_ttl_std_both) 
 table_ttl_std <- models_ttl_std |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                               fmt = 2,
-                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
 table_ttl_std
@@
 
-Regressing on cognitive test score (standardized)
-```{r}
-did_adj_cog <- feols(cog_dif ~ migr + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book  + home.has.internet | clsids + w2clsids, data = d_cl)
+Regressing on cognitive test score 
+```{r}
+did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
+did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
+#did_adj_cog_m <- feols(cog_dif ~ migr_mo + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
+did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
+#did_adj_cog_f <- feols(cog_dif ~ migr_fa + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
+did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
 ```
@@
 models_adj_cog <- list(
-'Any Parent Migrated' = did_adj_cog,
-'Only Mother Migrated' = did_adj_cog_m_only,
-#'Mother Migrated' = #did_adj_cog_m,
-'Only Father Migrated' = did_adj_cog_f_only,
-#'Father Migrated' = #did_adj_cog_f,
-'Both Parents Migrated' = did_adj_cog_both) 
+'Any Parent' = did_adj_cog,
+'Only Mother' = did_adj_cog_m_only,
+#'Mother' = #did_adj_cog_m,
+'Only Father' = did_adj_cog_f_only,
+#'Father' = #did_adj_cog_f,
+'Both Parents' = did_adj_cog_both) 
 ```
@@
   coef_rename =  coef_rename, 
-  output = 'markdown'
-  )
-table_adj_cog
+  output = 'latex'
+  )
+#table_adj_cog
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-#did_adj_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+#did_adj_ttl_m <- feols(avg_dif ~ migr_mo + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+#did_adj_ttl_f <- feols(avg_dif ~ migr_fa + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
 ```
@@
 models_adj_ttl <- list(
-'Any Parent Migrated' = did_adj_ttl,
-'Only Mother Migrated' = did_adj_ttl_m_only,
-#'Mother Migrated' = #did_adj_ttl_m,
-'Only Father Migrated' = did_adj_ttl_f_only,
-#'Father Migrated' = #did_adj_ttl_f,
-'Both Parents Migrated' = did_adj_ttl_both)
+'Any Parent' = did_adj_ttl,
+'Only Mother' = did_adj_ttl_m_only,
+#'Mother' = #did_adj_ttl_m,
+'Only Father' = did_adj_ttl_f_only,
+#'Father' = #did_adj_ttl_f,
+'Both Parents' = did_adj_ttl_both)
 ```
@@
   coef_rename =  coef_rename, 
-  output = 'markdown'
-  )
-table_adj_ttl
+  output = 'latex'
+  )
+#table_adj_ttl
 ```
@@
 ```{}
-did_adj_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
 ```
@@
 models_adj_ttl_z <- list(
-'Any Parent Migrated' = did_adj_ttl_z,
-'Only Mother Migrated' = did_adj_ttl_z_m_only,
-#'Mother Migrated' = did_adj_ttl_z_m,
-'Only Father Migrated' = did_adj_ttl_z_f_only,
-#'Father Migrated' = did_adj_ttl_z_f,
-'Both Parents Migrated' = did_adj_ttl_z_both) 
-table_adj_ttl_z <- models_adj_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+'Any Parent' = did_adj_ttl_z,
+'Only Mother' = did_adj_ttl_z_m_only,
+#'Mother' = did_adj_ttl_z_m,
+'Only Father' = did_adj_ttl_z_f_only,
+#'Father' = did_adj_ttl_z_f,
+'Both Parents' = did_adj_ttl_z_both) 
+table_adj_ttl_z <- models_adj_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
 table_adj_ttl_z
@@
 ```{}
-did_adj_ttl_dm <- feols(ttl_dm_dif ~ migr + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
-did_adj_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1ttl_100_dm + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = d_cl)
+did_adj_ttl_dm <- feols(ttl_dm_dif ~ migr + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
+did_adj_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
 ```
@@
 models_adj_ttl_dm <- list(
-'Any Parent Migrated' = did_adj_ttl_dm,
-'Only Mother Migrated' = did_adj_ttl_dm_m_only,
-#'Mother Migrated' = did_adj_ttl_dm_m,
-'Only Father Migrated' = did_adj_ttl_dm_f_only,
-#'Father Migrated' = did_adj_ttl_dm_f,
-'Both Parents Migrated' = did_adj_ttl_dm_both) 
-table_adj_ttl_dm <- models_adj_ttl_dm |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+'Any Parent' = did_adj_ttl_dm,
+'Only Mother' = did_adj_ttl_dm_m_only,
+#'Mother' = did_adj_ttl_dm_m,
+'Only Father' = did_adj_ttl_dm_f_only,
+#'Father' = did_adj_ttl_dm_f,
+'Both Parents' = did_adj_ttl_dm_both) 
+table_adj_ttl_dm <- models_adj_ttl_dm |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
 table_adj_ttl_dm
@@
 m.out <- matchit(
-  migr ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_cl, 
-  replace = T,
+  #replace = T,
   ratio = 3,
-  method = "nearest", 
+  method = "optimal", 
   distance = "glm",
@@
 ```{r}
-didm_cog <- feols(cog_dif ~ migr + cog3pl | clsids + w2clsids, data = dm, weights = dm$weights)
-
-didm_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | clsids + w2clsids, data = dm, weights = dm$weights)
-
-didm_adj_cog <- feols(cog_dif ~ migr + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm, weights = dm$weights)
-
-didm_adj_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm, weights = dm$weights)
+didm_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = dm, weights = dm$weights)
+
+didm_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = dm, weights = dm$weights)
+
+didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
+
+didm_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm, weights = dm$weights)
 
@@
 m.out_mo_only <- 
-  matchit(migr_mo_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_mo_only, 
-  replace = T,
-  method = "nearest",
+  #replace = T,
+  method = "optimal",
   distance = "glm",
@@
 ```{r}
-love.plot(
-  m.out_mo_only,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 1.5),
-  )
-```
-
-```{r}
 dm_mo_only <- match.data(m.out_mo_only)
@@
 ```{r}
-didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + cog3pl | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_ttl_mo_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_adj_ttl_mo_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+
+didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
 
@@
 m.out_fa_only <- matchit(
-  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_fa_only,
-  replace = T,
-  method = "nearest",
+  #replace = T,
+  method = "optimal",
   distance = "glm",
@@
   )
+```
+
+```{r}
 sum_m.out_fa_only <- summary(m.out_fa_only)
@@
   )
-```
-
-```{r}
 love.plot(
@@
   )
+love.plot(
+  m.out_both,
+  stats = "variance.ratios",
+  binary = "std", 
+  #limits = c(0, 1.5),
+  )
 ```
@@
 ```{r}
-didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + cog3pl | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_ttl_fa_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_adj_ttl_fa_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+
+didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
 
@@
 m.out_both <- matchit(
-  migr_both ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level + home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_both, 
-  method = "nearest",
+  method = "optimal",
   distance = "glm",
-  replace = T,
+  #replace = T,
   ratio = 3,
@@
 ```{r}
- #plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+```
+```{}
 love.plot(
@@
 ```{r}
-didm_cog_both <- feols(cog_dif ~ migr_both + cog3pl | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
-
-didm_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
-
-didm_adj_cog_both <- feols(cog_dif ~ migr_both + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
-
-didm_adj_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_both, weights = dm_both$weights)
+didm_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = dm_both, weights = dm_both$weights)
+
+didm_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = dm_both, weights = dm_both$weights)
+
+didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
+
+didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
 
@@
 m.out_mo <- matchit(
-  migr_mo ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, data = d_mo,
-  method = "nearest",
-  replace = T,
+  migr_mo ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, data = d_mo,
+  method = "optimal",
+  #replace = T,
   ratio = 3,
@@
 ```{}
-feols(cog_dif ~ migr_mo + cog3pl| clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
-
-feols(ttl_dif ~ migr_mo + w1ttl_100  | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
-
-feols(cog_dif ~ migr_mo + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
-
-feols(ttl_dif ~ migr_mo + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_mo, weights = dm_mo$weights)
+feols(cog_dif ~ migr_mo + w1cog_100| schids, data = dm_mo, weights = dm_mo$weights)
+
+feols(avg_dif ~ migr_mo + w1avg_100  | schids, data = dm_mo, weights = dm_mo$weights)
+
+feols(cog_dif ~ migr_mo + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo, weights = dm_mo$weights)
+
+feols(avg_dif ~ migr_mo + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo, weights = dm_mo$weights)
 
@@
 m.out_fa <- matchit(
-  migr_fa ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, data = d_fa,
-  method = "nearest",
-  replace = T,
+  migr_fa ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, data = d_fa,
+  method = "optimal",
+  #replace = T,
   ratio = 3,
@@
 ```{}
-feols(cog_dif ~ migr_fa + cog3pl | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
-
-feols(ttl_dif ~ migr_fa + w1ttl_100 | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
-
-feols(cog_dif ~ migr_fa + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
-
-feols(ttl_dif ~ migr_fa + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = dm_fa, weights = dm_fa$weights)
+feols(cog_dif ~ migr_fa + w1cog_100 | schids, data = dm_fa, weights = dm_fa$weights)
+
+feols(avg_dif ~ migr_fa + w1avg_100 | schids, data = dm_fa, weights = dm_fa$weights)
+
+feols(cog_dif ~ migr_fa + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa, weights = dm_fa$weights)
+
+feols(avg_dif ~ migr_fa + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa, weights = dm_fa$weights)
 
@@
 title_ttl_matching <- 'Parental migration’s effect on children’s academic exam scores, estimated with matching'
-note_matching <- "3:1 nearest neighbor propensity score matching with replacement; exact matching by county"
+note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"
 ```
@@
 models_m_cog <- list(
-'Any Parent Migrated' = didm_cog,
-'Only Mother Migrated' = didm_cog_mo_only,
-##'Mother Migrated' = #did_adj_cog_m,
-'Only Father Migrated' = didm_cog_fa_only,
-##'Father Migrated' = #did_adj_cog_f,
-'Both Parents Migrated' = didm_cog_both) 
+'Any Parent' = didm_cog,
+'Only Mother' = didm_cog_mo_only,
+##'Mother' = #did_adj_cog_m,
+'Only Father' = didm_cog_fa_only,
+##'Father' = #did_adj_cog_f,
+'Both Parents' = didm_cog_both) 
 ```
@@
   notes = note_matching,
-  output = 'markdown'
-  )
-table_m_cog
+  output = 'latex'
+  )
+#table_m_cog
 ```
@@
 models_m_ttl <- list(
-'Any Parent Migrated' = didm_ttl,
-'Only Mother Migrated' = didm_ttl_mo_only,
-##'Mother Migrated' = #did_adj_ttl_m,
-'Only Father Migrated' = didm_ttl_fa_only,
-##'Father Migrated' = #did_adj_ttl_f,
-'Both Parents Migrated' = didm_ttl_both) 
+'Any Parent' = didm_ttl,
+'Only Mother' = didm_ttl_mo_only,
+##'Mother' = #did_adj_ttl_m,
+'Only Father' = didm_ttl_fa_only,
+##'Father' = #did_adj_ttl_f,
+'Both Parents' = didm_ttl_both) 
+```
+
+```{r}
 table_m_ttl <- models_m_ttl |> msummary(
@@
   notes = note_matching,
-  output = 'markdown'
-  )
-table_m_ttl
+  output = 'latex'
+  )
+#table_m_ttl
 ```
@@
 models_m_adj_cog <- list(
-'Any Parent Migrated' = didm_adj_cog,
-'Only Mother Migrated' = didm_adj_cog_mo_only,
-##'Mother Migrated' = #did_adj_cog_m,
-'Only Father Migrated' = didm_adj_cog_fa_only,
-##'Father Migrated' = #did_adj_cog_f,
-'Both Parents Migrated' = didm_adj_cog_both) 
+'Any Parent' = didm_adj_cog,
+'Only Mother' = didm_adj_cog_mo_only,
+##'Mother' = #did_adj_cog_m,
+'Only Father' = didm_adj_cog_fa_only,
+##'Father' = #did_adj_cog_f,
+'Both Parents' = didm_adj_cog_both) 
+```
+
+```{r}
 table_m_adj_cog <- models_m_adj_cog |> msummary(
@@
   fmt = 2,
-  title = title_ttl_matching,
+  title = title_cog_matching,
   gof_omit = gof_omit,
@@
   notes = note_matching,
-  output = 'markdown'
-  )
-table_m_adj_cog
+  output = 'latex'
+  )
+#table_m_adj_cog
 ```
@@
 models_m_adj_ttl <- list(
-'Any Parent Migrated' = didm_adj_ttl,
-'Only Mother Migrated' = didm_adj_ttl_mo_only,
-##'Mother Migrated' = #did_adj_ttl_m,
-'Only Father Migrated' = didm_adj_ttl_fa_only,
-##'Father Migrated' = #did_adj_ttl_f,
-'Both Parents Migrated' = didm_adj_ttl_both) 
+'Any Parent' = didm_adj_ttl,
+'Only Mother' = didm_adj_ttl_mo_only,
+##'Mother' = #did_adj_ttl_m,
+'Only Father' = didm_adj_ttl_fa_only,
+##'Father' = #did_adj_ttl_f,
+'Both Parents' = didm_adj_ttl_both) 
+```
+
+```{r}
 table_m_adj_ttl <- models_m_adj_ttl |> msummary(
@@
   notes = note_matching,
-  output = 'markdown'
-  )
-table_m_adj_ttl
+  output = 'latex'
+  )
+#table_m_adj_ttl
 ```
@@
 ## Interaction
-```{r}
+```{}
 d_cl1 <- d_cl |> mutate(
@@
 
-```{r}
-feols(ttl_dif ~ migr*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
+```{}
+feols(avg_dif ~ migr*fin.better + w1avg_100 | schids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
+           output = 'latex')
+feols(cog_dif ~ migr*fin.better + w1cog_100 | schids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(ttl_dif ~ migr_mo_only*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+feols(avg_dif ~ migr_mo_only*fin.better + w1avg_100 | schids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr_mo_only*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
+           output = 'latex')
+feols(cog_dif ~ migr_mo_only*fin.better + w1cog_100 | schids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(ttl_dif ~ migr_fa_only*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+feols(avg_dif ~ migr_fa_only*fin.better + w1avg_100 | schids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr_fa_only*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
+           output = 'latex')
+feols(cog_dif ~ migr_fa_only*fin.better + w1cog_100 | schids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(ttl_dif ~ migr_both*fin.better + w1ttl_100 | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+feols(avg_dif ~ migr_both*fin.better + w1avg_100 | schids, data = d_cl1) |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr_both*fin.better + cog3pl | clsids + w2clsids, data = d_cl1)  |>
+           output = 'latex')
+feols(cog_dif ~ migr_both*fin.better + w1cog_100 | schids, data = d_cl1)  |>
   msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-```
-
-```{r}
-feols(ttl_dif ~ migr*fin.better + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+```
+
+```{}
+feols(avg_dif ~ migr*fin.better + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
     msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr*fin.better + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+feols(cog_dif ~ migr*fin.better + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
     msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-```
-
-```{r}
+           output = 'latex')
+```
+
+```{}
 d_cl1=d_cl1 |> mutate(
@@
 
-```{r}
-feols(ttl_dif ~ migr*supervision.less + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+```{}
+feols(avg_dif ~ migr*supervision.less + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
     msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
-feols(cog_dif ~ migr*supervision.less + cog3pl + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.educational.aspiration + child.is.ethnic.minority + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet  | clsids + w2clsids, data = d_cl1) |>
+           output = 'latex')
+feols(cog_dif ~ migr*supervision.less + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
     msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'markdown')
+           output = 'latex')
 ```

### 2022-07-05 MScThesisText.tex
Final

@@
 \hypersetup{
-  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
+  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration},
   pdfauthor={Jiancheng Gu1},
@@
 
-\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
+\title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 Millions of children worldwide are ``left behind'' at home communities as their parents migrate away for work.
-Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on children's educational attainment.
+Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development outcomes like educational attainment.
 To what extent do different arrangements of parental migration affect children's educational performance in the short term?
@@
 Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause br on par with random assignment to participants, conditional on identification assumptions (Cunningham, 2021).
-
-In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
+It requires that the cause be on par with random assignment to participants, conditional on identification assumptions (Cunningham, 2021).
+
+My research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
 I choose China as the case and analyze data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness checks.
-The outcome was measured with children's cognitive test score and academic exam grade.
+I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness checks.
+The outcome is measured with children's cognitive test score and academic exam grade.
 I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
@@
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers.
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+They form the backbone of essential industries, such as retail, transportation, and manufacturing.
 The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS, 2022; NBS et al., 2017).
@@
 But China's welfare program, as Qian (2021) argued, is fragmented and stratified.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
+People who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
 As rural migrants arrive in the city, they find themselves with limited access to social welfare, such as health care and children's education (Qian, 2021).
@@
 
-The institutionalized discrimination against rural migrants finds its roots in China's ``multilevel citizenship'' system.
+The institutional discrimination against labor migrants finds its roots in China's ``multilevel citizenship'' system.
 As Vortherms (2021) explained, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
+The local state confers most of the rights and defines who is eligible to these rights through \emph{hukou}, or the household registration system:
 
@@
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-Criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
 This parallels how European states differentially incorporate foreign immigrants into national welfare regimes (Zhang, 2018).
-Another policy response, as stated by Roberts and Hannum (2018), is the centralized boarding schools.
+Another policy response, as stated by Roberts and Hannum (2018), is the centralized boarding school.
 The Ministry of Education promotes boarding schools in the rural county-seats.
-These schools serve as a cost-efficient way to enroll students in surrounding villages and to look after the left-behind children.
+These schools serve as a cost-effective way to enroll students in surrounding villages and to look after the left-behind children.
 In reality, such schools ``are often ill-equipped to ensure the healthy upbringing and psychological wellbeing of children'' (p.~6).
@@
 The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
-My sample includes urban left-behind children as well.
 The second shortcoming lies in sampling and research design.
@@
 To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
+My sample includes urban left-behind children as well.
 I included the test results of multiple subjects to measure comprehensive academic achievement.
@@
 This subsequently boosted children's school enrollment and educational expenditure.
-Cebotari (2020) developed a fixed effect model with three-wave panel data collected in Ghana.
-He found that stay-behind children's education benefits from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
+Cebotari (2020) developed a fixed effect model with longitudinal data collected in Ghana.
+He found that stay-behind children's education benefited from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
 In China, Chang et al.
 (2019) interviewed migrant workers and their family members.
-Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+Oftentimes, labor migration presented the only way to sustain their children's education and livelihood.
 Peng (2018) interviewed first-generation migrant mothers whose initial migration dated back to the 1990s.
-To them, ``good mothering'' primarily means offering economic support for their children in education, which can help their children climb the ladder of success.
+To them, ``good mothering'' primarily meant offering economic support for their children in education, which can help their children climb the ladder of success.
 
@@
 Children flourish under parental nurturing care.
-This term refers to the ``stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships'' (Black et al., 2021, p.
+This term refers to the ``stable environments that promote health and adequate nutrition, protect from threats \ldots{} opportunities for learning,'' and ``responsive, emotionally supportive and developmentally enriching relationships'' (Black et al., 2021, p.
 1).
@@
 They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
-L.
+The team of L.
 Wang et al.
 (2019) collected data from junior high school students in central China.
-The researchers' two-way fixed-effect model showed no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+Their two-way fixed-effect model showed no significant effect of parental migration on left-behind children's achievement in mathematical test.
 Nguyen (2016) conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
@@
 Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
-It takes longer time for parental migration to generate resources that improve children's educational attainment.
+It takes longer time for labor migration to generate resources that improve children's educational attainment.
 I propose the first hypothesis:
@@
 (2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
-They found that mother migration was ``negatively associated with children's social competence and academic performance,'' while father migration had no direct effects on the two outcomes (pp.~860-861).
+They found that maternal migration was ``negatively associated with children's social competence and academic performance,'' while paternal migration had no direct effects on the two outcomes (pp.~860-861).
 
@@
 The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
-The baseline survey (wave one) took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
-These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter `counties').
-The follow-up survey (wave two) in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed 9449 of the seventh grade cohort.
-I further restricted the sample to students living with both parents at the original domicile at the baseline survey.
+The wave one baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
+They were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter `counties').
+The wave two follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed 10279 of the seventh grade cohort.
+I further restricted the sample to students living with both parents at the original domicile (place of hukou registry) at the baseline survey.
 To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
@@
 I constructed four treatment dummy variables measuring migration arrangements: any parents migrated, only father migrated, only mother migrated, and both parents migrated.
-These arrangements are mutually exclusive.
-The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
+The latter three arrangements are mutually exclusive.
+The control group consisted of parents staying with their children throughout the two waves of survey.
 I then removed the observations that reported parental divorce or death.
@@
 
-The control variables on children's level include age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+The control variables at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority of Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
 At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
-The lists of covariates are in Tables 3-5 in the Results section.
+The lists of covariates are in Table~\ref{tab:tab-ctvar-dit} -- Table~\ref{tab:tab-ctvar-msr} in the Results section.
 
@@
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \varepsilon_{i,j}\] For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
-School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in the same school are also in the same county.
-An alternative is to use a class fixed-effect to control for time-invariant factors in the classroom.
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}\] For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between the two waves of surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
+School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in one school are also in the same county.
+An alternative is to use a class fixed-effect to control for time-invariant factors at the classroom level and above.
 However, about one-sixth of the students were reassigned into new classes at the end of baseline academic year.
@@
 Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
-The standard errors were clustered at the classroom level.
-
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \theta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+The standard errors are clustered at the classroom level.
+
+In addition, I made an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 I adopted \texttt{R} (version 4.2.0) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 1.3.1) for data cleaning (Wickham et al., 2019); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022); \texttt{modelsummary} (version 1.0.0), \texttt{vtable} (version 1.3.3), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.0) for typesetting (Aust \& Barth, 2022).
+This involved the following packages: \texttt{tidyverse} (version 1.3.1) for data cleaning (Wickham et al., 2019); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022b; Ho et al., 2022); \texttt{modelsummary} (version 1.0.0), \texttt{vtable} (version 1.3.3), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.0) for typesetting (Aust \& Barth, 2022).
 
@@
 
-Table 1 summarizes the independent variables, namely the migration status reported in the wave two survey.
-All 4062 children were living with parents in one household in baseline, but about fifteen percent saw at least one parent migrated between the two waves of survey.
+Table~\ref{tab:tab-idpvar} summarizes the independent variables, namely the migration status reported in the wave two survey.
+All 4062 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
 I call these students ``newly left-behind children'' and their households ``new migration households.'' In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
-The remaining one-fifth was both-parents migration.
+The remaining one-fifth were both-parents migration.
 
@@
 
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-1}Independent variables by parental migration}
-\centering
-\begin{tabular}[t]{lll}
+\begin{longtable}[]{@{}lll@{}}
+\caption{\label{tab:tab-idpvar}Independent variables by parental migration}\tabularnewline
 \toprule
-Variable & N & Percent\\
-\midrule
+Variable & N & Percent \\
+\midrule
+\endfirsthead
+\toprule
+Variable & N & Percent \\
+\midrule
+\endhead
 Parental Migration & & \\
-... No & 3422 & 84.2\%\\
-... Yes & 640 & 15.8\%\\
+\ldots{} No & 3422 & 84.2\% \\
+\ldots{} Yes & 640 & 15.8\% \\
 Parental Migration Type & & \\
-... Both Parents & 130 & 3.2\%\\
-... Both Parents At Home & 3422 & 84.2\%\\
-... Only Father & 252 & 6.2\%\\
-... Only Mother & 258 & 6.4\%\\
+\ldots{} Both Parents at Home & 3422 & 84.2\% \\
+\ldots{} Both Parents Migrated & 130 & 3.2\% \\
+\ldots{} Only Father Migrated & 252 & 6.2\% \\
+\ldots{} Only Mother Migrated & 258 & 6.4\% \\
 \bottomrule
-\end{tabular}
-\end{table}
+\end{longtable}
 
@@
 
-The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figures B1-B4 in the appendix.
-Compared to non-left-behind peers, newly left-behind children score lower in wave two's cognitive and academic tests; Their cognitive test score increases less and their academic exam score drops more.
+The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figure~\ref{fig:v-plot-cog} -- Figure~\ref{fig:v-plot-ttl-1} in the appendix.
+Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
 T-tests show that for the baseline outcomes, the differences of the mean values between-group are probably due to chance.
@@
 
-\caption{\label{tab:unnamed-chunk-2}Dependent variables by parental migration}
+\caption{\label{tab:tab-dpvar}Dependent variables by parental migration}
 \centering
@@
 
-Table 3 summarizes the bivariate analysis on the binary control variables.
-New migration households have lower internet access rate.
+Table~\ref{tab:tab-ctvar-dit} summarizes the bivariate analysis on the binary control variables.
+New migration households had lower internet access rate.
 Among the newly left-behind children, male sex, past grade retention, and boarding at school were more common compared to the non-left-behind peers.
@@
 
-\caption{\label{tab:unnamed-chunk-3}Dichotomous control variables by parental migration}
+\caption{\label{tab:tab-ctvar-dit}Dichotomous control variables by parental migration}
 \centering
@@
 \multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}0 = No, 1 = Yes; * p < 0.05, ** p < 0.01, *** p < 0.001}\\
 \end{tabular}
@@
 
-Table 4 presents the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
-While the majority of mothers and fathers have only finished high school or below, they hold big expectations for children.
-Eight out of ten parents wish that their children complete university education.
+Table~\ref{tab:tab-ctvar-cnt} displays the bivariate analysis for categorical control variables, and Table~\ref{tab:tab-ctvar-msr} documents their measurement scales.
+While the majority of mothers and fathers had only finished high school or below, they held big expectations for children.
+Eight out of ten parents wished that their children complete university education.
 Scholars like Willis (2019) explained this pattern with the Chinese social norms and cultural traditions.
@@
 Ordinary people could study for the highly competitive \emph{keju} (civil service examination).
-As the world's ``earliest meritocratic institution,'' this exam system recruited top performers into the imperial government and the elite class (T.
+As the world's ``earliest meritocratic institution,'' this national exam system recruited top performers into the imperial government and the elite class (T.
 Chen et al., 2020, p.
@@
 
-\caption{\label{tab:unnamed-chunk-4}Categorical and continuous control variables by parental migration}
+\caption{\label{tab:tab-ctvar-cnt}Categorical and continuous control variables by parental migration}
 \centering
@@
 child.age & 12.45 & 0.63 & 12.51 & 0.73 & F=4.263*\\
+child.number.of.sibling & 0.58 & 0.74 & 0.66 & 0.82 & F=4.896*\\
 child.health & 4.17 & 0.87 & 4.14 & 0.9 & F=0.576\\
@@
 mother.education.level & 1.53 & 1.17 & 1.57 & 1.25 & F=0.468\\
+\addlinespace
 father.education.level & 1.72 & 1.18 & 1.75 & 1.21 & F=0.274\\
-\addlinespace
 parent.expectation & 4.19 & 0.91 & 4.14 & 0.95 & F=1.627\\
@@
 
-\begin{table}
-
-\caption{\label{tab:unnamed-chunk-5}Measurement of categorical variables}
-\centering
-\begin{tabular}[t]{lll}
+\begin{longtable}[]{@{}lll@{}}
+\caption{\label{tab:tab-ctvar-msr}Measurement and distribution of categorical variables}\tabularnewline
 \toprule
-Variable & N & Percent\\
-\midrule
+Variable & N & Percent \\
+\midrule
+\endfirsthead
+\toprule
+Variable & N & Percent \\
+\midrule
+\endhead
 child.health & & \\
-... 1 = Very poor & 21 & 0.5\%\\
-... 2 = Somewhat poor & 112 & 2.8\%\\
-... 3 = Moderate & 797 & 19.6\%\\
-... 4 = Good & 1373 & 33.8\%\\
-... 5 = Very good & 1759 & 43.3\%\\
+\ldots{} 1 = Very poor & 21 & 0.5\% \\
+\ldots{} 2 = Somewhat poor & 112 & 2.8\% \\
+\ldots{} 3 = Moderate & 797 & 19.6\% \\
+\ldots{} 4 = Good & 1373 & 33.8\% \\
+\ldots{} 5 = Very good & 1759 & 43.3\% \\
 child.education.aspiration & & \\
-... 1 = Junior high school & 137 & 3.4\%\\
-... 2 = Senior high school & 418 & 10.3\%\\
-... 3 = Associate college & 615 & 15.1\%\\
-... 4 = University & 1195 & 29.4\%\\
-... 5 = Postgraduate & 1697 & 41.8\%\\
+\ldots{} 1 = Junior high school & 137 & 3.4\% \\
+\ldots{} 2 = Senior high school & 418 & 10.3\% \\
+\ldots{} 3 = Associate college & 615 & 15.1\% \\
+\ldots{} 4 = University & 1195 & 29.4\% \\
+\ldots{} 5 = Postgraduate & 1697 & 41.8\% \\
 mother.education.level & & \\
-... 0 = Primary school and below & 702 & 17.3\%\\
-... 1 = Junior high school & 1618 & 39.8\%\\
-... 2 = Senior high school & 1034 & 25.5\%\\
-... 3 = Associate college & 304 & 7.5\%\\
-... 4 = University & 365 & 9\%\\
-... 5 = Postgraduate & 39 & 1\%\\
+\ldots{} 0 = Primary school and below & 702 & 17.3\% \\
+\ldots{} 1 = Junior high school & 1618 & 39.8\% \\
+\ldots{} 2 = Senior high school & 1034 & 25.5\% \\
+\ldots{} 3 = Associate college & 304 & 7.5\% \\
+\ldots{} 4 = University & 365 & 9\% \\
+\ldots{} 5 = Postgraduate & 39 & 1\% \\
 father.education.level & & \\
-... 0 = Primary school and below & 441 & 10.9\%\\
-... 1 = Junior high school & 1615 & 39.8\%\\
-... 2 = Senior high school & 1170 & 28.8\%\\
-... 3 = Associate college & 348 & 8.6\%\\
-... 4 = University & 422 & 10.4\%\\
-... 5 = Postgraduate & 66 & 1.6\%\\
+\ldots{} 0 = Primary school and below & 441 & 10.9\% \\
+\ldots{} 1 = Junior high school & 1615 & 39.8\% \\
+\ldots{} 2 = Senior high school & 1170 & 28.8\% \\
+\ldots{} 3 = Associate college & 348 & 8.6\% \\
+\ldots{} 4 = University & 422 & 10.4\% \\
+\ldots{} 5 = Postgraduate & 66 & 1.6\% \\
 parent.expectation & & \\
-... 1 = Junior high school & 34 & 0.8\%\\
-... 2 = Senior high school & 254 & 6.3\%\\
-... 3 = Associate college & 426 & 10.5\%\\
-... 4 = University & 1569 & 38.6\%\\
-... 5 = Postgraduate & 1779 & 43.8\%\\
+\ldots{} 1 = Junior high school & 34 & 0.8\% \\
+\ldots{} 2 = Senior high school & 254 & 6.3\% \\
+\ldots{} 3 = Associate college & 426 & 10.5\% \\
+\ldots{} 4 = University & 1569 & 38.6\% \\
+\ldots{} 5 = Postgraduate & 1779 & 43.8\% \\
 home.extracurricular.book & & \\
-... 1 = Very few & 386 & 9.5\%\\
-... 2 = Not many & 411 & 10.1\%\\
-... 3 = Some & 1302 & 32.1\%\\
-... 4 = Quite a few & 1104 & 27.2\%\\
-... 5 = A great number & 859 & 21.1\%\\
+\ldots{} 1 = Very few & 386 & 9.5\% \\
+\ldots{} 2 = Not many & 411 & 10.1\% \\
+\ldots{} 3 = Some & 1302 & 32.1\% \\
+\ldots{} 4 = Quite a few & 1104 & 27.2\% \\
+\ldots{} 5 = A great number & 859 & 21.1\% \\
 home.economic.resource & & \\
-... 1 = Very poor & 110 & 2.7\%\\
-... 2 = Somewhat poor & 589 & 14.5\%\\
-... 3 = Moderate & 3112 & 76.6\%\\
-... 4 = Somewhat rich & 240 & 5.9\%\\
-... 5 = Very rich & 11 & 0.3\%\\
+\ldots{} 1 = Very poor & 110 & 2.7\% \\
+\ldots{} 2 = Somewhat poor & 589 & 14.5\% \\
+\ldots{} 3 = Moderate & 3112 & 76.6\% \\
+\ldots{} 4 = Somewhat rich & 240 & 5.9\% \\
+\ldots{} 5 = Very rich & 11 & 0.3\% \\
 \bottomrule
-\end{tabular}
-\end{table}
+\end{longtable}
 
@@
 I first present the results on children's cognitive test score.
-According to the unadjusted DID models (see Table 6 below), newly left-behind adolescents are more likely to score lower in cognitive tests than their non-left-behind counterparts, lending support to Hypothesis 1a.
+The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6 below).
+This lends support to Hypothesis 1a.
 Parental migration is linked to a 2.56 points decrease in cognitive test score.
 Hypothesis 2a is only partially supported.
-Compared with the non-left-behind children, children with only father absent are associated with greater decrease (2.87 points) in cognitive test score than those with only mother absent (2.15 points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (See Table A1 in appendix).
+Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.87 points) in cognitive test score than those with only mother absent (2.15 points).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in appendix).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
@@
 Next, I show the results on children's academic test grades.
-In line with Hypothesis 1b, the unadjusted DID models (see Table 7 below) show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers.
+In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
 Parental migration is associated with a drop of 1.27 points in academic exam score.
@@
 Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
+
+\newpage
 
@@
 
-\newpage
-
 Some predictors are strong in both models of cognitive and academic abilities.
 These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
-One year older in age is associated with decreases of 2.61 points for cognitive test and of 0.44 points for academic exam.
+For students, one year older in age is associated with decreases of 2.61 points for cognitive test and of 0.44 points for academic exam.
 Preschool attendance is linked to increases of 2.33 points for cognitive test and of 1.17 points for academic exam.
 Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
-The coefficients are 0.75 points and 2.03 points for cognitive test, respectively; and 0.27 points and 0.77 points for academic exams, respectively.
+The coefficients are 2.34 points and 2.03 points for cognitive test, respectively; and 0.58 points and 0.77 points for academic exams, respectively.
 
 Several predictors are strong in predicting one outcome but not the other.
-Covariates related to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
-Girls outperform boys by 1.62 points in academic exams, but do not show advantage in cognitive test.
+Covariates that only relate to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
+Girls outperform boys by 1.62 points in academic exams, but do not show advantage in cognitive tests.
 Students who consider themselves healthier are associated with higher scores in academic exams.
-On the contrary, students who perceive their households having more extracurricular books are associated with lower scores in academic exams.
-Covariates related to cognitive scores is the number of siblings.
-Having an additional sibling is associated with lower cognitive score of 0.99 points, but its effect for academic grade is not significant statistically.
+On the contrary, those who report having more extracurricular books at home are associated with lower scores in academic exams.
+Covariates that only relate to cognitive scores is the number of siblings.
+Having an additional sibling is associated with lower cognitive score of 0.99 points.
 
@@
 A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
-Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
+Another scenario is that poverty may hinder children's educational achievement while driving parents to migrate.
 To tackle the selection bias herein, an applicable technique is matching.
-This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
+It aims to two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Greifer, 2022a).
 
@@
 This score serves as a measure of the distance between two units.
-PSM can match the units with two different approaches to handle distance.
-The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance to be paired.
-This approach does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred.
-The optimal-pair approach works in a similar fashion but tries to minimize the sum of the absolute pairwise distances (Pan \& Bai, 2018).
+When handling this distance, PSM can match the units with two different approaches.
+The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance for pairing.
+This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
+The optimal-pair approach works in a similar fashion but tries to minimize the absolute pairwise distances in total (Pan \& Bai, 2018).
 Regardless of specific approaches, King and Nielsen (2019) argued against PSM in general as it risks more ``imbalance, model dependence, and bias'' for already balanced data (p.~444).
@@
 CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units (Costalli \& Negri, 2021).
-
-I performed matching with all the covariates of the adjusted DID model.
+The downside is that it leaves many units without a match and discards these unmatched units (Costalli \& Negri, 2021).
+
+I performed matching with all the covariates of the adjusted DID model on the four treatments respectively.
 My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
-I then made do with the PSM.
+I then made do with PSM.
 I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
@@
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
-In the appendix, Figures B5-B8 presents the plots of absolute standardized mean differences before and after matching.
-
-The results from models with matching strongly resemble the models without matching (see Tables 8 and 9 below, and Tables A3 and A4 in the appendix).
+In appendix, Figure~\ref{fig:cobal-any} -- Figure~\ref{fig:cobal-both} display the absolute standardized mean differences before and after matching.
+
+The results from models with matching strongly resemble the models without matching (see Tables 8 -- 9 below, and Tables A3 -- A4 in appendix).
 In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
 In the models of academic exam score, the treatment variables' coefficients are negative and statistically significant for the any-parent-migrated scenario and the only-mother-migrated scenario.
-The magnitudes of the statistically significant coefficients are similar to those without matching.
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s cognitive test scores, estimated with matching}
-\centering
-\begin{tabular}[t]{lcccc}
+The magnitudes of the statistically significant coefficients are similar to those in the models without matching.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2239}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1791}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2090}}@{}}
+\caption{\label{tab:tab-reg-m-cog}Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
 \toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-2.64}*** & \num{-2.76}* & \num{-3.41}** & \num{-1.96}\\
- & (\num{0.74}) & (\num{1.22}) & (\num{1.25}) & (\num{1.74})\\
-Baseline.score & \num{-0.70}*** & \num{-0.74}*** & \num{-0.62}*** & \num{-0.69}***\\
- & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
-\midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.392} & \num{0.450} & \num{0.423} & \num{0.467}\\
-R2 Adj. & \num{0.363} & \num{0.384} & \num{0.356} & \num{0.352}\\
-FE: schids & X & X & X & X\\
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents
+\end{minipage} \\
+\midrule
+\endhead
+Migration & -2.64*** & -2.76* & -3.41** & -1.96 \\
+& (0.74) & (1.22) & (1.25) & (1.74) \\
+Baseline.score & -0.70*** & -0.74*** & -0.62*** & -0.69*** \\
+& (0.02) & (0.04) & (0.03) & (0.05) \\
+Num.Obs. & 2503 & 1032 & 1008 & 515 \\
+R2 & 0.392 & 0.450 & 0.423 & 0.467 \\
+R2 Adj. & 0.363 & 0.384 & 0.356 & 0.352 \\
+FE: schids & X & X & X & X \\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\end{tabular}
-\end{table}
-
-\newpage
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s academic exam scores, estimated with matching}
-\centering
-\begin{tabular}[t]{lcccc}
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\textbf{Note:}
+\^{}\^{} 3:1 optimal pair propensity score matching; exact matching by county
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2239}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1791}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2090}}@{}}
+\caption{\label{tab:tab-reg-m-ttl}Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
 \toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-1.22}* & \num{-1.65}* & \num{-1.15} & \num{0.46}\\
- & (\num{0.57}) & (\num{0.81}) & (\num{0.86}) & (\num{0.98})\\
-Baseline.score & \num{0.05}† & \num{0.07}† & \num{0.04} & \num{0.01}\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
-\midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.468} & \num{0.587} & \num{0.480} & \num{0.501}\\
-R2 Adj. & \num{0.444} & \num{0.538} & \num{0.420} & \num{0.393}\\
-FE: schids & X & X & X & X\\
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents
+\end{minipage} \\
+\midrule
+\endhead
+Migration & -1.22* & -1.65* & -1.15 & 0.46 \\
+& (0.57) & (0.81) & (0.86) & (0.98) \\
+Baseline.score & 0.05† & 0.07† & 0.04 & 0.01 \\
+& (0.03) & (0.04) & (0.04) & (0.04) \\
+Num.Obs. & 2503 & 1032 & 1008 & 515 \\
+R2 & 0.468 & 0.587 & 0.480 & 0.501 \\
+R2 Adj. & 0.444 & 0.538 & 0.420 & 0.393 \\
+FE: schids & X & X & X & X \\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\end{tabular}
-\end{table}
+\end{longtable}
+
+\textbf{Note:}
+\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
+
+\textbf{Note:}
+\^{}\^{} 3:1 optimal pair propensity score matching; exact matching by county
 
@@
 
-This thesis proposes a model to infer the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
-I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as shown by a 1.2 percent drop in academic exam grades and a 2.5 percent drop in cognitive test scores.
-This contrasts with the results of DID models by Bai et al.
+This thesis infers the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
+I build difference-in-differences models with fixed-effect to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance.
+This is evidenced by a 1.2 points drop in academic exam grades and a 2.5 points drop in cognitive test scores.
+This result contrasts with that of DID models by Bai et al.
 (2018): parental migration is linked to higher English test scores for stay-behind children.
-The discrepancy could be attributed the study's location, a poverty-stricken Northwestern province.
+The discrepancy could be attributed their study's location, a Northwestern province with grinding poverty.
 There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.~1165).
 In my nationwide sample the reverse may hold.
-The households may be better off, so the labor migrant's additional income helps less.
+The households may be better off, so labor migration's additional income fails to compensate for the care deficit.
 Another plausibility is that family disruption precedes resource generation.
-The former's negative effect befalls the left-behind child at once, but the latter's positive effect occurs a while later.
+The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs a while later (Gao et al., 2019).
 Consequently, I obtain a short-term negative effect.
@@
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that in the short term, father's absence is not linked to children's academic exam scores; Mother's absence is negatively associated with children's academic and cognitive test results, with a 2.1 percent drop for both indicators.
-An explanation is that the mother's migration, by defying the cultural expectations on maternal care, harbors bitterness in the child's mind (Murphy, 2020).
-On the other hand, father's migration is negatively associated with children's cognitive test score with a 3 percent decrease.
+Results indicate that in the short term, only father's absence is not linked to children's academic performance; Only mother's absence is negatively associated with children's academic abilities, with a 2.1 points drop in the test score.
+This is in line with the findings of previous research.
+For example, Murphy (2020) observed that when a Chinese mother migrates, she defies the cultural expectations on maternal care, thereby harboring bitterness in the child's mind.
+This bitter sentiment can arise even if there is care by father or other relatives.
+Besides, only-mother migration sometimes indicates deeper issues within the household.
+The father may be unfit for work or engaged in domestic violence, prompting the mother's labor migration (Murphy, 2020).
+These may all hamper children's educational performance.
+
+Compared to only mother's migration, only father's migration carries a stronger influence on children's cognitive capability, as shown by a further decrease of 1 point in cognitive test score.
 This echoes the findings of Shen et al.
@@
 The stay-at-home mother may devote more to the caregiving role.
-This can partially buffers the impact by her husband's absence and help her child maintain academic performance.
+This can partially buffer the impact by her husband's absence and help her child maintain academic performance.
 
 My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small (n = 130), making the statistical power low.
-Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
+Regarding identification, I could only identify parental migration through such a condition: a parent's absence from a household without parental divorce or death.
 This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
@@
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-According to Liang and Li (2021), some parents out-migrated at an earlier date and returned before the baseline survey.
-These children would be attributed to the non-left-behind group.
-However, they ``suffer similar disadvantage as that of left behind children'' (p.~12).
+According to Liang and Li (2021), some parents might have out-migrated at an earlier date and returned before the baseline survey.
+Their children would be attributed to the non-left-behind group.
+However, these children ``suffer similar disadvantage as that of left behind children'' (p.~12).
 Liang and Li (2021) argued for a new category: the formerly left-behind children.
@@
 As Chen et al.
-(2009) discussed in their research on left-behind children, endogenous factors may create selection bias.
+(2009) discussed in their paper on left-behind children, endogenous factors may create selection bias.
 When migration opportunities arise, some parents may worry that leaving children behind would hamper children's education, thereby giving up the opportunity.
@@
 Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades (Chen et al., 2009).
+This shock can increase parents' out-migration and reduce stay-behind students' grades (Chen et al., 2009).
 I could not account for such shocks as CEPS data does not include detailed geographic information.
@@
 When the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
-This would facilitate examination of the parallel trend assumption.
+This would help examine the parallel trend assumption.
 Novel methods also offer new possibilities.
@@
 Looking beyond outbound migration, return migration of parents also worth studying (Liang \& Li, 2021).
-Not many publications have explored return migrants and their formerly left-behind children in the Chinese context (Démurger \& Xu, 2015; Z.
+Not many publications have explored return migrants and their formerly left-behind children in China (Démurger \& Xu, 2015; Z.
 Liu et al., 2018).
@@
 Besides top-down policymaking, bottom-up approaches are also necessary.
-School administrators could dedicate advisory and counseling programs.
+School administrators could dedicate more advisory and counseling programs.
 Social workers could provide paraprofessional training in communities (M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-debrauw2017}{}}%
-Brauw, A.
-de, \& Giles, J.
-(2017).
-Migrant Opportunity and the Educational Attainment of Youth in Rural China.
-\emph{Journal of Human Resources}, \emph{52}(1), 272--311.
-\url{https://doi.org/10.3368/jhr.52.1.0813-5900R}
-
 \leavevmode\vadjust pre{\hypertarget{ref-cebotari2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gao2019}{}}%
+Gao, Y., Bai, Y., Ma, Y., \& Shi, Y.
+(2019).
+Parental Migration{'}s Effects on the Academic and Non-Academic Performance of Left-Behind Children in Rural China.
+\emph{China Economist}, \emph{14}(5), 67--80.
+\url{https://doi.org/10.19602/j.chinaeconomist.2019.9.07}
+
 \leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-greifer2022}{}}%
+Greifer, N. (2022a). \emph{MatchIt: Getting started}. \url{https://kosukeimai.github.io/MatchIt/articles/MatchIt.html}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-cobalt}{}}%
-Greifer, N. (2022). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
+Greifer, N. (2022b). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
 
@@
 Leveraging machine learning methods to estimate heterogeneous effects: Father absence in china as an example.
-\emph{Chinese Sociological Review}, \emph{0}(0), 1--29.
+\emph{Chinese Sociological Review}, \emph{54}(3), 223--251.
 \url{https://doi.org/10.1080/21620555.2021.1948828}
@@
 
-\caption{Parental migration’s effect on children’s academic exam score}
+\caption{Parental migration’s effect on children’s cognitive test score}
 \centering
@@
 \midrule
-Migration & \num{-1.24}* & \num{-1.88}* & \num{-1.33} & \num{0.47}\\
- & (\num{0.57}) & (\num{0.81}) & (\num{0.87}) & (\num{1.06})\\
-Baseline.score & \num{-0.01} & \num{0.00} & \num{-0.02} & \num{-0.08}\\
- & (\num{0.03}) & (\num{0.05}) & (\num{0.04}) & (\num{0.06})\\
-child.age & \num{-0.20} & \num{-0.71} & \num{-0.43} & \num{-0.69}\\
- & (\num{0.28}) & (\num{0.50}) & (\num{0.44}) & (\num{0.56})\\
-child.is.girl & \num{1.94}*** & \num{1.69}*** & \num{1.99}** & \num{3.48}**\\
- & (\num{0.52}) & (\num{0.49}) & (\num{0.61}) & (\num{1.29})\\
-child.health & \num{0.45}* & \num{0.73}** & \num{0.75}* & \num{0.28}\\
+Migration & \num{-1.22}* & \num{-1.88}* & \num{-1.33} & \num{0.47}\\
+ & (\num{0.55}) & (\num{0.81}) & (\num{0.87}) & (\num{1.06})\\
+Baseline.score & \num{0.06}** & \num{0.00} & \num{-0.02} & \num{-0.08}\\
+ & (\num{0.02}) & (\num{0.05}) & (\num{0.04}) & (\num{0.06})\\
+child.age & \num{-0.08} & \num{-0.71} & \num{-0.43} & \num{-0.69}\\
+ & (\num{0.27}) & (\num{0.50}) & (\num{0.44}) & (\num{0.56})\\
+child.is.girl & \num{1.99}*** & \num{1.69}*** & \num{1.99}** & \num{3.48}**\\
+ & (\num{0.50}) & (\num{0.49}) & (\num{0.61}) & (\num{1.29})\\
+child.health & \num{0.47}* & \num{0.73}** & \num{0.75}* & \num{0.28}\\
  & (\num{0.20}) & (\num{0.26}) & (\num{0.34}) & (\num{0.65})\\
-child.has.rural.hukou & \num{0.05} & \num{0.60} & \num{0.31} & \num{2.16}†\\
- & (\num{0.48}) & (\num{0.65}) & (\num{0.65}) & (\num{1.12})\\
-child.number.of.sibling & \num{0.21} & \num{0.02} & \num{0.01} & \num{-0.30}\\
+child.has.rural.hukou & \num{0.03} & \num{0.60} & \num{0.31} & \num{2.16}†\\
+ & (\num{0.47}) & (\num{0.65}) & (\num{0.65}) & (\num{1.12})\\
+child.number.of.sibling & \num{0.25} & \num{0.02} & \num{0.01} & \num{-0.30}\\
  & (\num{0.28}) & (\num{0.27}) & (\num{0.42}) & (\num{0.62})\\
-child.went.to.preschool & \num{1.44}* & \num{1.38}† & \num{-0.34} & \num{3.27}*\\
- & (\num{0.59}) & (\num{0.74}) & (\num{0.77}) & (\num{1.41})\\
-child.had.skipped.grade & \num{0.91} & \num{-0.66} & \num{0.43} & \num{5.78}†\\
- & (\num{2.34}) & (\num{1.42}) & (\num{3.12}) & (\num{3.44})\\
-child.had.repeated.grade & \num{-0.37} & \num{-2.82}† & \num{-2.23}* & \num{1.40}\\
+child.went.to.preschool & \num{1.27}* & \num{1.38}† & \num{-0.34} & \num{3.27}*\\
+ & (\num{0.58}) & (\num{0.74}) & (\num{0.77}) & (\num{1.41})\\
+child.had.skipped.grade & \num{0.88} & \num{-0.66} & \num{0.43} & \num{5.78}†\\
+ & (\num{2.20}) & (\num{1.42}) & (\num{3.12}) & (\num{3.44})\\
+child.had.repeated.grade & \num{-0.31} & \num{-2.82}† & \num{-2.23}* & \num{1.40}\\
  & (\num{0.84}) & (\num{1.54}) & (\num{0.97}) & (\num{1.85})\\
-child.in.boarding.school & \num{-0.25} & \num{1.60} & \num{0.66} & \num{-1.63}\\
+child.in.boarding.school & \num{-0.30} & \num{1.60} & \num{0.66} & \num{-1.63}\\
  & (\num{0.74}) & (\num{1.13}) & (\num{0.85}) & (\num{1.70})\\
-child.education.aspiration & \num{0.70}** & \num{0.81}† & \num{0.85}** & \num{0.27}\\
- & (\num{0.23}) & (\num{0.41}) & (\num{0.30}) & (\num{0.56})\\
-child.is.ethnic.minority & \num{0.69} & \num{0.18} & \num{2.24} & \num{0.11}\\
+child.education.aspiration & \num{0.52}* & \num{0.81}† & \num{0.85}** & \num{0.27}\\
+ & (\num{0.21}) & (\num{0.41}) & (\num{0.30}) & (\num{0.56})\\
+child.is.ethnic.minority & \num{0.78} & \num{0.18} & \num{2.24} & \num{0.11}\\
  & (\num{0.72}) & (\num{1.05}) & (\num{1.42}) & (\num{2.54})\\
-parent.expectation & \num{0.76}** & \num{0.51} & \num{0.36} & \num{0.91}\\
- & (\num{0.28}) & (\num{0.36}) & (\num{0.44}) & (\num{0.60})\\
-parent.has.white.collar.job & \num{0.47} & \num{0.09} & \num{0.54} & \num{1.35}\\
- & (\num{0.43}) & (\num{0.57}) & (\num{0.75}) & (\num{1.24})\\
-mother.education.level & \num{-0.10} & \num{0.19} & \num{0.20} & \num{-0.79}\\
+parent.expectation & \num{0.64}** & \num{0.51} & \num{0.36} & \num{0.91}\\
+ & (\num{0.23}) & (\num{0.36}) & (\num{0.44}) & (\num{0.60})\\
+parent.has.white.collar.job & \num{0.40} & \num{0.09} & \num{0.54} & \num{1.35}\\
+ & (\num{0.44}) & (\num{0.57}) & (\num{0.75}) & (\num{1.24})\\
+mother.education.level & \num{-0.09} & \num{0.19} & \num{0.20} & \num{-0.79}\\
  & (\num{0.23}) & (\num{0.32}) & (\num{0.35}) & (\num{0.57})\\
-father.education.level & \num{0.15} & \num{-0.21} & \num{-0.01} & \num{0.04}\\
- & (\num{0.26}) & (\num{0.36}) & (\num{0.34}) & (\num{0.57})\\
+father.education.level & \num{0.14} & \num{-0.21} & \num{-0.01} & \num{0.04}\\
+ & (\num{0.25}) & (\num{0.36}) & (\num{0.34}) & (\num{0.57})\\
 home.economic.resource & \num{-0.16} & \num{0.20} & \num{-0.39} & \num{-0.39}\\
  & (\num{0.36}) & (\num{0.59}) & (\num{0.51}) & (\num{0.69})\\
-home.extracurricular.book & \num{-0.36} & \num{-0.35} & \num{-0.40} & \num{0.51}\\
+home.extracurricular.book & \num{-0.42}† & \num{-0.35} & \num{-0.40} & \num{0.51}\\
  & (\num{0.23}) & (\num{0.31}) & (\num{0.30}) & (\num{0.49})\\
-home.has.internet & \num{-0.86}* & \num{-0.79} & \num{-1.48}* & \num{-0.83}\\
- & (\num{0.41}) & (\num{0.83}) & (\num{0.62}) & (\num{1.17})\\
+home.has.internet & \num{-1.00}* & \num{-0.79} & \num{-1.48}* & \num{-0.83}\\
+ & (\num{0.42}) & (\num{0.83}) & (\num{0.62}) & (\num{1.17})\\
 \midrule
 Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.491} & \num{0.609} & \num{0.512} & \num{0.544}\\
-R2 Adj. & \num{0.463} & \num{0.554} & \num{0.445} & \num{0.421}\\
+R2 & \num{0.496} & \num{0.609} & \num{0.512} & \num{0.544}\\
+R2 Adj. & \num{0.469} & \num{0.554} & \num{0.445} & \num{0.421}\\
 FE: schids & X & X & X & X\\

### 2022-07-05 appendix.Rmd
Final

# Tables

```{r tab-reg-cog-adj}
table_adj_cog
```

```{r tab-reg-ttl-adj}
table_adj_ttl
```

```{r tab-reg-m-adj-cog}
table_m_adj_cog
```

```{r tab-reg-m-adj-ttl}
table_m_adj_ttl
```

\newpage

### 2022-07-05 data/Gu-thesis-script.Rmd
Final

@@
 
-Load packages
-```{r}
+```{r Load packages}
 library(tidyverse) 
@@
 library(cobalt) 
+library(DescTools)
 options(modelsummary_get="broom") 
-#library(gtsummary)
-#library(DescTools)
-#knitr::opts_chunk$set(modelsummary_get="broom")
 ```
@@
 ## Data cleaning
-Read CEPS data
-```{r}
+```{r Read data}
 d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
@@
 d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
-#d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
-#d_sch2 <- read_dta('cepsw2principalCN.dta')
 ```
 
-Remove wave 1's observations of grade 9; they were not followed up in wave 2
 ```{r}
@@
   subset(grade9==0) |> 
-  select(!c(frame, subsample, grade9))
+  select(!c(frame, subsample, grade9)) #Remove wave 1's observations of grade 9; they were not followed up in wave 2
 ```
 
-Assemble a panel dataset in wide format
-```{r}
-dw1 <- d_stu1 |> left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
-dw2 <- d_stu2 |> left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
-d <- dw1 |> right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids')) |> remove_labels()
+```{r Merge data}
+d <- d_stu1 |> 
+  left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) |>
+  left_join(d_stu2, by=c('ids', 'schids', 'clsids', 'ctyids')) |>
+  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) |> 
+  remove_labels() #Assemble a panel dataset in wide format
 ```
 
-```{r}
-d <- d |> mutate(
+```{r Sample}
+d_cl <- d |> 
+  filter(w2a0801==1) |> #keep parents who are married (and alive)
+  filter(be1201==1 & be1202==1) |> #keep households with both parents staying at baseline
+  filter(stmigrant==1) #keep local children 
+```
+
+## Variables 
+```{r Exam grade conversion}
+d_cl <- d_cl |> mutate(
   w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
@@
 
-Trimming outliers
-```{r}
-d <- d |> mutate(
-  w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
-  w2chn_100_trim = if_else(w2chn_100>100, 100, w2chn_100),
-  w1mat_100_trim = if_else(w1mat_100>100, 100, w1mat_100),
-  w2mat_100_trim = if_else(w2mat_100>100, 100, w2mat_100),
-  w1eng_100_trim = if_else(w1eng_100>100, 100, w1eng_100),
-  w2eng_100_trim = if_else(w2eng_100>100, 100, w2eng_100)
+```{r Outlier detection}
+outlier <- d_cl |> filter(
+  w1chn_100<0 | w1chn_100>100 | w1mat_100<0 | w1mat_100>100 | w1eng_100<0 | w1eng_100>100 |
+  w2chn_100<0 | w2chn_100>100 | w2mat_100<0 | w2mat_100>100 | w2eng_100<0 | w2eng_100>100)
+```
+
+```{r Trim outlying values}
+d_cl <- d_cl |> mutate(
+  w1chn_100_trim = Winsorize(w1chn_100, minval = 0, maxval = 100),
+  w2chn_100_trim = Winsorize(w2chn_100, minval = 0, maxval = 100),
+  w1mat_100_trim = Winsorize(w1mat_100, minval = 0, maxval = 100),
+  w2mat_100_trim = Winsorize(w2mat_100, minval = 0, maxval = 100),
+  w1eng_100_trim = Winsorize(w1eng_100, minval = 0, maxval = 100),
+  w2eng_100_trim = Winsorize(w2eng_100, minval = 0, maxval = 100)
 )
@@
 
-```{r}
-d <- d |> mutate(
+```{r Outcome variables}
+d_cl <- d_cl |> mutate(
   w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
@@
   w2cog_100 = w2cogscore*100/35,
-  ttl_dif = w2ttl_100 - w1ttl_100,
   avg_dif = w2avg_100 - w1avg_100,
   cog_dif = w2cog_100 - w1cog_100,
-  #cog_std_dif = w2cog3pl - cog3pl
-  )
+  ) |>
+  drop_na(avg_dif, cog_dif)
 ```
 
-```{r}
-d_cl <- d |>
-  drop_na(cog_dif, avg_dif)
-```
-
-within-class z score
-```{}
-d1 <- d1 |> group_by(schids) |>
-  mutate(
-    w1ttl_z = as.numeric(scale(w1ttl)),
-    w2ttl_z = as.numeric(scale(w2ttl))
-  ) |> ungroup()
-```
-
-```{}
-d1 <- d1 |> group_by(schids) |>
-  mutate(
-    w1ttl_std = rescale(w1ttl),
-    w2ttl_std = rescale(w2ttl)
-    ) |> ungroup()
-```
-
-Detect outliers
-```{}
-d_outlier <- d |> filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
-d_outlier1 <- d_outlier |> select(clsids, schids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
-d1 <- d |> anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
-```
-
-Sample
-```{r}
-d_cl <- d |> 
-  drop_na(cog_dif, avg_dif) |> 
-  filter(w2a0801==1) |> #keep parents who are married (and alive)
-  filter(be1201==1 & be1202==1) |> #keep both parents live with children at baseline
-  filter(stmigrant==1) #keep local children 
-```
-
-## Variables
-
-Control variables
-```{r}
+```{r Control variables}
 d_cl <- d_cl |> mutate(
-         child.age = 2013 - a02a, #student's age at baseline
-         child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
-         child.has.rural.hukou = sthktype, #student holds rural (agricultural) hukou
-         child.in.boarding.school = stbrd, #student is boarding at school
-         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
-         child.health = a17, #student's self-rated health
-         child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
-         child.had.repeated.grade = if_else(c04 == 0, 0, 1), #student had repeated grade
-         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
-         child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
+         child.age = 2013 - a02a, 
+         child.is.girl = if_else(a01 == 2, 1, 0), 
+         child.has.rural.hukou = sthktype, 
+         child.in.boarding.school = stbrd, 
+         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
+         child.health = a17, 
+         child.had.skipped.grade = if_else(c03 == 0, 0, 1), 
+         child.had.repeated.grade = if_else(c04 == 0, 0, 1), 
+         child.went.to.preschool = if_else(c01 == 1, 1, 0), 
          child.number.of.sibling = if_else(stonly == 1, 0, stsib),
-         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
-         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
          parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
-         #par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
-         home.economic.resource = steco_5c, #self-rated household financial situation
-         home.has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
-         home.extracurricular.book = b12 #Amount of book at home, student self-rated 
+         home.economic.resource = steco_5c, 
+         home.has.internet = if_else(b13 == 2, 1, 0), 
+         home.extracurricular.book = b12 
 ) |> drop_na(
 child.age, child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
-#par.ccp, 
 parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
@@
 
-```{}
-d_cl$stsib <- d_cl$stsib |> replace_na(0) |> as.numeric()
-d_cl <- d_cl |> mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) |> #number of siblings
-  drop_na(child.number.of.sibling)
-```
-
-Best-educated parent's years of education
-```{r}
-d_cl <- d_cl |> mutate(parent.education.level = NA)
-d_cl$parent.education.level[d_cl$stprhedu == 1|d_cl$stprhedu == 2] <- 0
-d_cl$parent.education.level[d_cl$stprhedu == 3] <- 1
-d_cl$parent.education.level[d_cl$stprhedu == 4|d_cl$stprhedu == 5|d_cl$stprhedu == 6] <- 2
-d_cl$parent.education.level[d_cl$stprhedu == 7] <- 3
-d_cl$parent.education.level[d_cl$stprhedu == 8] <- 4
-d_cl$parent.education.level[d_cl$stprhedu == 9] <- 5
-```
-
-```{r}
+```{r Mother education}
 d_cl <- d_cl |> mutate(mother.education.level = NA)
@@
 
-```{r}
+```{r Father education}
 d_cl <- d_cl |> mutate(father.education.level = NA)
@@
 
-```{r}
+```{r Parent expectation}
 d_cl <- d_cl |> mutate(parent.expectation = NA)
@@
 
-```{r}
+```{r Child aspiration}
 d_cl <- d_cl |> mutate(child.education.aspiration = NA)
@@
 d_cl <- d_cl |>  drop_na(
-  parent.education.level, 
+  mother.education.level, 
+  father.education.level,
   parent.expectation, 
@@
 Only mother migrated
-```{r}
+```{r Any parent migrated}
+d_cl <- d_cl |> mutate(
+  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
+  migr_fa_only = NA,
+  migr_mo_only = NA,
+  migr_both = NA
+  ) |> drop_na(migr)
+```
+
+```{r Only mother migrated}
 d_cl$migr_mo_only[d_cl$migr == 0] <- 0
@@
 
-Mother migrated
-```{}
-d_cl$migr_mo[d_cl$migr == 0] <- 0
-d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
-```
-
-Only father migrated
-```{r}
+```{r Only father migrated}
 d_cl$migr_fa_only[d_cl$migr == 0] <- 0
@@
 
-Father migrated
-```{}
-d_cl$migr_fa[d_cl$migr == 0] <- 0
-d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
-```
-
-Both parents migrated
-```{r}
+```{r Both parents migrated}
 d_cl$migr_both[d_cl$migr == 0] <- 0
@@
 
-```{}
-df <- d_cl |> select(
-  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
-  cog3pl, w1ttl_100, cog_dif, ttl_dif,
-  child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.education.aspiration,
-  par.edu, par.ccp, par.expt.univ, 
-  home.has.internet, home.extracurricular.book, home.economic.resource
-)
-```
-
 ## Descriptive statistics
-```{r}
-d_migr <- d_cl |>
+```{r Cleaned data}
+df <- d_cl |>
   select(
-  migr, migr_mo_only, migr_fa_only, migr_both,
+  migr, migr_mo_only, migr_fa_only, migr_both, schids, ctyids,
   w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
-  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
+  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
   child.health, child.education.aspiration, 
@@
 ```{r}
-d_smr <- d_migr |> 
+d_migr <- df |>
   mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |>
-  mutate(`Parental Migration Type` = 0) 
-d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
-d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
-d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
-d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
-d_smr <- d_smr |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+  select(!migr)
 ```
 
-```{}
-datasummary_balance(
-  ~migr,
-  data = d_migr,
-  fmt = 2)
+```{r Data for treatment variable summary}
+d_idpvar <- df |> 
+  select(migr:migr_both) |>
+  mutate(`Parental Migration` = if_else(migr==1, 'Yes', 'No')) |>
+  mutate(`Parental Migration Type` = NA) 
+d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents at Home'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
+d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
+d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
 ```
 
-```{r}
-d_dpvar1 <- d_migr |>
-  select(migr, 
-         cog_dif, w1cog_100, w2cog_100, avg_dif, w1avg_100, w2avg_100) |>
+```{r Treatment variable summary}
+tab_idpvar <- st(
+  data = d_idpvar,
+  out = 'return'
+)
+tab_idpvar[tab_idpvar == 4062] <- ''
+tab_idpvar
+```
+
+```{r Data for outcome variable summary}
+d_dpvar <- d_migr |>
+  select(`Parental Migration`, cog_dif, w1cog_100, w2cog_100, avg_dif, w1avg_100, w2avg_100) |>
   set_variable_labels(
-    migr = 'Parental migration',
     w1cog_100 ='Wave 1 score',
@@
 
-```{r}
+```{r Outcome variable summary}
 tab_dpvar <- 
   st(
-  data = d_dpvar1,
+  data = d_dpvar,
   summ = c('mean(x)', 'sd(x)'),
   digits = 2, 
-  group = 'migr',
+  group = 'Parental Migration',
   group.test = list(
@@
 
-```{}
-d_dpvar <- as.data.frame(d_dpvar)
-table_dependent_variable <- datasummary(
-  All(d_dpvar) ~ Mean + SD + Min + Max,
-  data = d_dpvar,
-  output = 'latex'
-  ) 
-table_dependent_variable
-```
-
-```{r}
-d_idpvar <- d_migr |> 
-  select(migr, migr_mo_only, migr_fa_only, migr_both) |> 
-  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |> 
-  mutate(`Parental Migration Type` = 0) 
-d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents'
-d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
-```
-
-```{r}
-tab_idpvar <- st(
-  data = d_idpvar,
-  out = 'return'
-)
-tab_idpvar[tab_idpvar == 4062] <- ''
-tab_idpvar
-```
-
-```{r}
-table_independent_variable <- datasummary_skim(
-    data=d_idpvar,
-    type = 'categorical',
-    title = 'Independent variables',
-    output = 'markdown')
-table_independent_variable
-```
-
-```{r}
+```{r Data for binary control variable summary}
 d_ctvar_dit <- d_migr |>
-  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |>
+  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |>
   mutate_all(as_factor)
@@
 
-```{r}
+```{r Binary control variable summary}
+tab_ctvar_dit <- 
+  st(
+  data = d_ctvar_dit,
+  digits = 2,
+  group = 'Parental Migration',
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = "return"
+  )
+tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
+tab_ctvar_dit[tab_ctvar_dit == 3422|tab_ctvar_dit == 640] <- ''
+tab_ctvar_dit 
+```
+
+```{r Data for categorical control variable summary}
 d_ctvar_cnt <- d_migr |>
-  select(migr, child.age, child.health, child.education.aspiration, 
+  select(`Parental Migration`, child.age, child.number.of.sibling, child.health, child.education.aspiration, 
   mother.education.level, father.education.level, parent.expectation, 
@@
 
-```{r}
+```{r Categorical control variable summary}
+tab_ctvar_cnt <- d_ctvar_cnt |> st(
+  digits = 2, 
+  summ = c('mean(x)', 'sd(x)'),
+  group = 'Parental Migration',
+  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
+  out = "return")
+tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
+tab_ctvar_cnt
+```
+
+```{r Data for categorical control variable measurement}
 d_ctvar_label <- d_ctvar_cnt|>
-  select(!(child.age:migr)) |> 
+  select(!(`Parental Migration`:child.number.of.sibling)) |> 
   add_value_labels(
@@
 
-```{}
-test.table <- d_ctvar |>
-  tbl_summary(
-    by = migr,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    ) 
-```
-
-```{r}
-table_variable <- datasummary_skim(
-  data = d_ctvar_label,
-  type = 'categorical',
-  title = 'Measurement of categorical variables',
-  output = 'latex'
-)
-#table_variable
-```
-
-```{r}
+```{r Measurement for categorical control variable}
 tab_var <- st(
@@
 
-```{r}
-tab_ctvar_dit <- 
-  st(
-  data = d_ctvar_dit,
-  digits = 2,
-  group = 'migr',
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = "return"
-  )
-tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
-tab_ctvar_dit[tab_ctvar_dit == 3422|tab_ctvar_dit == 640] <- ''
-tab_ctvar_dit 
-```
-
-```{r}
-tab_ctvar_cnt <- d_ctvar_cnt |> st(
-  digits = 2, 
-  summ = c('mean(x)', 'sd(x)'),
-  group = 'migr',
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = "return")
-tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
-tab_ctvar_cnt
-```
-
-```{}
-table_control_variable <- datasummary_skim(
-  data = d_ctvar,
-  type = 'categorical',
-  output = 'latex'
-)
-table_control_variable
-```
-
-t-test
-```{}
-ttest_cog <- t.test(cog_dif ~ migr, data = d_cl)
-ttest_ttl <- t.test(avg_dif ~ migr, data = d_cl)
-ttest_cog
-ttest_ttl
+```{r Data for violin plots}
+d_smr <- d_migr |> 
+  mutate(`Parental Migration Type` = 0) 
+d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
+d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
+d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
+d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
+d_smr <- d_smr |> select(!migr_mo_only & !migr_fa_only & !migr_both)
 ```
@@
 
-## DID unrestricted
-Regressing on cognitive test score (standardized)
-```{r}
-did_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = d_cl) 
-did_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = d_cl) 
-#did_cog_m <- feols(cog_dif ~ migr_mo + w1cog_100 | schids, data = d_cl) 
-did_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = d_cl) 
-#did_cog_f <- feols(cog_dif ~ migr_fa + w1cog_100 | schids, data = d_cl) 
-did_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = d_cl)
+# Econometric models
+## DID without covariates
+```{r Unadjusted regression on cognitive score}
+did_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = df) 
+did_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = df) 
+did_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = df) 
+did_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = df)
 ```
 
-Results
+```{r Unadjusted regression on exam grade}
+did_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = df) 
+did_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = df) 
+did_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = df) 
+did_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = df)
+```
+
 ```{r}
@@
 'Only Mother' = did_cog_m_only,
-#'Mother' = #did_cog_m,
 'Only Father' = did_cog_f_only,
-#'Father' = #did_cog_f,
 'Both Parents' = did_cog_both) 
@@
 ```{r}
+models_ttl <- list(
+'Any Parent' = did_ttl,
+'Only Mother' = did_ttl_m_only,
+'Only Father' = did_ttl_f_only,
+'Both Parents' = did_ttl_both) 
+```
+
+```{r Info for regression tables}
 stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
@@
 note_unadj <- 'No control variables included in these models'
+```
+
+```{r}
+models_cog <- list(
+'Any Parent' = did_cog,
+'Only Mother' = did_cog_m_only,
+'Only Father' = did_cog_f_only,
+'Both Parents' = did_cog_both) 
+```
+
+```{r}
+models_ttl <- list(
+'Any Parent' = did_ttl,
+'Only Mother' = did_ttl_m_only,
+'Only Father' = did_ttl_f_only,
+'Both Parents' = did_ttl_both) 
 ```
@@
   output = 'latex')
-#table_cog
-```
-
-raw score
-```{r}
-did_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = d_cl) 
-did_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = d_cl) 
-#did_ttl_m <- feols(avg_dif ~ migr_mo + w1avg_100 | schids, data = d_cl) 
-did_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = d_cl) 
-#did_ttl_f <- feols(avg_dif ~ migr_fa + w1avg_100 | schids, data = d_cl) 
-did_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = d_cl)
-```
-
-```{r}
-models_ttl <- list(
-'Any Parent' = did_ttl,
-'Only Mother' = did_ttl_m_only,
-#'Mother' = #did_ttl_m,
-'Only Father' = did_ttl_f_only,
-#'Father' = #did_ttl_f,
-'Both Parents' = did_ttl_both) 
 ```
@@
   output = 'latex')
-#table_ttl
 ```
 
-z score
-```{}
-did_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | schids, data = d_cl) 
-did_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | schids, data = d_cl) 
-did_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | schids, data = d_cl) 
-did_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | schids, data = d_cl) 
-did_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | schids, data = d_cl) 
-did_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | schids, data = d_cl)
+## DID with covariates
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
+
+```{r Adjusted regression on cognitive score}
+did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
 ```
 
-```{}
-models_ttl_z <- list(
-'Any Parent' = did_ttl_z,
-'Only Mother' = did_ttl_z_m_only,
-#'Mother' = did_ttl_z_m,
-'Only Father' = did_ttl_z_f_only,
-#'Father' = did_ttl_z_f,
-'Both Parents' = did_ttl_z_both) 
-table_ttl_z <- models_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-                              fmt = 2,
-                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
-table_ttl_z
+```{r Adjusted regression on exam grade}
+did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
 ```
 
-std
-```{}
-did_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | schids, data = d_cl) 
-did_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
-did_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | schids, data = d_cl) 
-did_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
-did_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | schids, data = d_cl) 
-did_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | schids, data = d_cl)
-```
-
-```{}
-models_ttl_std <- list(
-'Any Parent' = did_ttl_std,
-'Only Mother' = did_ttl_std_m_only,
-#'Mother' = did_ttl_std_m,
-'Only Father' = did_ttl_std_f_only,
-#'Father' = did_ttl_std_f,
-'Both Parents' = did_ttl_std_both) 
-table_ttl_std <- models_ttl_std |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
-                              fmt = 2,
-                              coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
-table_ttl_std
-```
-
-## DID adjusted unrestricted
-$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
-
-Regressing on cognitive test score 
-```{r}
-did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-#did_adj_cog_m <- feols(cog_dif ~ migr_mo + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-#did_adj_cog_f <- feols(cog_dif ~ migr_fa + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = d_cl)
-```
-
-Results
 ```{r}
@@
 'Only Mother' = did_adj_cog_m_only,
-#'Mother' = #did_adj_cog_m,
 'Only Father' = did_adj_cog_f_only,
-#'Father' = #did_adj_cog_f,
 'Both Parents' = did_adj_cog_both) 
+```
+
+```{r}
+models_adj_ttl <- list(
+'Any Parent' = did_adj_ttl,
+'Only Mother' = did_adj_ttl_m_only,
+'Only Father' = did_adj_ttl_f_only,
+'Both Parents' = did_adj_ttl_both)
 ```
@@
   )
-#table_adj_cog
-```
-
-Regressing on total exam score
-```{r}
-did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-#did_adj_ttl_m <- feols(avg_dif ~ migr_mo + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-#did_adj_ttl_f <- feols(avg_dif ~ migr_fa + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-```
-
-Results
-```{r}
-models_adj_ttl <- list(
-'Any Parent' = did_adj_ttl,
-'Only Mother' = did_adj_ttl_m_only,
-#'Mother' = #did_adj_ttl_m,
-'Only Father' = did_adj_ttl_f_only,
-#'Father' = #did_adj_ttl_f,
-'Both Parents' = did_adj_ttl_both)
 ```
@@
   fmt = 2,
-  title = title_ttl,
+  title = title_cog,
   gof_omit = gof_omit,
@@
   )
-#table_adj_ttl
-```
-
-Regressing on total exam score
-```{}
-did_adj_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-```
-
-Results
-```{}
-models_adj_ttl_z <- list(
-'Any Parent' = did_adj_ttl_z,
-'Only Mother' = did_adj_ttl_z_m_only,
-#'Mother' = did_adj_ttl_z_m,
-'Only Father' = did_adj_ttl_z_f_only,
-#'Father' = did_adj_ttl_z_f,
-'Both Parents' = did_adj_ttl_z_both) 
-table_adj_ttl_z <- models_adj_ttl_z |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
-table_adj_ttl_z
-```
-
-Regressing on total exam score
-```{}
-did_adj_ttl_dm <- feols(ttl_dm_dif ~ migr + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-did_adj_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1avg_100_dm + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = d_cl)
-```
-
-Results
-```{}
-models_adj_ttl_dm <- list(
-'Any Parent' = did_adj_ttl_dm,
-'Only Mother' = did_adj_ttl_dm_m_only,
-#'Mother' = did_adj_ttl_dm_m,
-'Only Father' = did_adj_ttl_dm_f_only,
-#'Father' = did_adj_ttl_dm_f,
-'Both Parents' = did_adj_ttl_dm_both) 
-table_adj_ttl_dm <- models_adj_ttl_dm |> msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1ttl_dif" = "Baseline difference"), output = 'latex')
-table_adj_ttl_dm
 ```
@@
 ## Matching
-```{r}
+```{r Match on any parent migration}
 m.out <- matchit(
   migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
-  data = d_cl, 
-  #replace = T,
+  data = df, 
   ratio = 3,
@@
 ```{r}
-sum_m.out <- summary(m.out)
-fig_msmd_any <- plot(sum_m.out, xlim = c(0, 0.55), position = 'right')
-```
-
-```{r}
 dm <- match.data(m.out)
@@
 
-```{r}
-didm_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = dm, weights = dm$weights)
-
-didm_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = dm, weights = dm$weights)
-
-didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
-
-didm_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm, weights = dm$weights)
-
-```
-
-```{r}
+```{r Match on mother-only migration}
 d_mo_only <- d_cl |> drop_na(migr_mo_only)
@@
   data = d_mo_only, 
-  #replace = T,
   method = "optimal",
@@
 ```{r}
-sum_m.out_mo_only <- summary(m.out_mo_only)
-fig_msmd_mo_only <- plot(sum_m.out_mo_only, xlim = c(0, 0.55), position = 'right')
-```
-
-```{r}
 dm_mo_only <- match.data(m.out_mo_only)
@@
 
-```{r}
-didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-
-```
-
-```{r}
+```{r Match on father-only migration}
 d_fa_only <- d_cl |> drop_na(migr_fa_only)
@@
   data = d_fa_only,
-  #replace = T,
   method = "optimal",
@@
 ```{r}
-sum_m.out_fa_only <- summary(m.out_fa_only)
-fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
-```
-
-```{r}
-love.plot(
-  m.out,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 0.55),
-  )
-love.plot(
-  m.out_mo_only,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 0.55),
-  )
-love.plot(
-  m.out_fa_only,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 0.55),
-  )
-love.plot(
-  m.out_both,
-  stats = "variance.ratios",
-  binary = "std", 
-  #limits = c(0, 1.5),
-  )
-```
-
-```{r}
 dm_fa_only <- match.data(m.out_fa_only)
@@
 
-```{r}
-didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-
-```
-
-```{r}
+```{r Match on both parents migration}
 d_both <- d_cl |> drop_na(migr_both) 
@@
   distance = "glm",
-  #replace = T,
   ratio = 3,
@@
 ```{r}
-plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
+dm_both <- match.data(m.out_both)
 ```
-```{}
-love.plot(
-  m.out_both,
+
+## Balance Assessment
+```{r ASMD plot any-parent}
+m.out |> love.plot(
   threshold = c(m = .1),
@@
   )
-love.plot(
-  m.out_both,
-  stats = "variance.ratios",
+```
+
+```{r ASMD plot only-mother}
+m.out_mo_only |> love.plot(
+  threshold = c(m = .1),
   binary = "std", 
-  #limits = c(0, 0.55),
+  limits = c(0, 0.55),
   abs = T
   )
-
 ```
 
-```{r}
-dm_both <- match.data(m.out_both)
+```{r ASMD plot only-father}
+m.out_fa_only |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
 ```
 
-```{r}
-didm_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = dm_both, weights = dm_both$weights)
-
-didm_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = dm_both, weights = dm_both$weights)
-
-didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
-
-didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
-
+```{r ASMD plot both-parents}
+m.out_both |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
 ```
 
-```{}
-d_mo <- d_cl |> drop_na(migr_mo)
-m.out_mo <- matchit(
-  migr_mo ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, data = d_mo,
-  method = "optimal",
-  #replace = T,
-  ratio = 3,
-  exact = migr_mo ~ ctyids
-  )
-summary(m.out_mo, un = FALSE)
+## Regression with matching
+
+```{r Unadjusted regression on cognitive score, with matching}
+didm_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = dm, weights = dm$weights)
+didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = dm_both, weights = dm_both$weights)
 ```
 
-```{}
-dm_mo <- match.data(m.out_mo)
+```{r Unadjusted regression on exam score, with matching}
+didm_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = dm, weights = dm$weights)
+didm_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = dm_both, weights = dm_both$weights)
 ```
 
-```{}
-feols(cog_dif ~ migr_mo + w1cog_100| schids, data = dm_mo, weights = dm_mo$weights)
-
-feols(avg_dif ~ migr_mo + w1avg_100  | schids, data = dm_mo, weights = dm_mo$weights)
-
-feols(cog_dif ~ migr_mo + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo, weights = dm_mo$weights)
-
-feols(avg_dif ~ migr_mo + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo, weights = dm_mo$weights)
-
+```{r Adjusted regression on cognitive score, with matching}
+didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
+didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
 ```
 
-```{}
-d_fa <- d_cl |> drop_na(migr_fa)
-m.out_fa <- matchit(
-  migr_fa ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, data = d_fa,
-  method = "optimal",
-  #replace = T,
-  ratio = 3,
-  exact = migr_fa_only ~ ctyids
-  )
-summary(m.out_fa, un = FALSE)
+```{r Adjusted regression on exam score, with matching}
+didm_adj_ttl <- feols(avg_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
+didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
 ```
 
-```{}
-dm_fa <- match.data(m.out_fa)
-```
-
-```{}
-feols(cog_dif ~ migr_fa + w1cog_100 | schids, data = dm_fa, weights = dm_fa$weights)
-
-feols(avg_dif ~ migr_fa + w1avg_100 | schids, data = dm_fa, weights = dm_fa$weights)
-
-feols(cog_dif ~ migr_fa + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa, weights = dm_fa$weights)
-
-feols(avg_dif ~ migr_fa + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa, weights = dm_fa$weights)
-
-```
-
-```{r}
+```{r Info for regression table with matching}
 title_cog_matching <- 'Parental migration’s effect on children’s cognitive test scores, estimated with matching'
@@
 'Only Mother' = didm_cog_mo_only,
-##'Mother' = #did_adj_cog_m,
 'Only Father' = didm_cog_fa_only,
-##'Father' = #did_adj_cog_f,
 'Both Parents' = didm_cog_both) 
+```
+
+```{r}
+models_m_ttl <- list(
+'Any Parent' = didm_ttl,
+'Only Mother' = didm_ttl_mo_only,
+'Only Father' = didm_ttl_fa_only,
+'Both Parents' = didm_ttl_both) 
+```
+
+```{r}
+models_m_adj_cog <- list(
+'Any Parent' = didm_adj_cog,
+'Only Mother' = didm_adj_cog_mo_only,
+'Only Father' = didm_adj_cog_fa_only,
+'Both Parents' = didm_adj_cog_both) 
+```
+
+```{r}
+models_m_adj_ttl <- list(
+'Any Parent' = didm_adj_ttl,
+'Only Mother' = didm_adj_ttl_mo_only,
+'Only Father' = didm_adj_ttl_fa_only,
+'Both Parents' = didm_adj_ttl_both) 
 ```
@@
   )
-#table_m_cog
-```
-
-```{r}
-models_m_ttl <- list(
-'Any Parent' = didm_ttl,
-'Only Mother' = didm_ttl_mo_only,
-##'Mother' = #did_adj_ttl_m,
-'Only Father' = didm_ttl_fa_only,
-##'Father' = #did_adj_ttl_f,
-'Both Parents' = didm_ttl_both) 
 ```
@@
 )
-#table_m_ttl
-```
-
-```{r}
-models_m_adj_cog <- list(
-'Any Parent' = didm_adj_cog,
-'Only Mother' = didm_adj_cog_mo_only,
-##'Mother' = #did_adj_cog_m,
-'Only Father' = didm_adj_cog_fa_only,
-##'Father' = #did_adj_cog_f,
-'Both Parents' = didm_adj_cog_both) 
 ```
@@
   )
-#table_m_adj_cog
-```
-
-```{r}
-models_m_adj_ttl <- list(
-'Any Parent' = didm_adj_ttl,
-'Only Mother' = didm_adj_ttl_mo_only,
-##'Mother' = #did_adj_ttl_m,
-'Only Father' = didm_adj_ttl_fa_only,
-##'Father' = #did_adj_ttl_f,
-'Both Parents' = didm_adj_ttl_both) 
 ```
@@
  )
-#table_m_adj_ttl
 ```
-
-```{r}
-num.outlier <- d_cl%>%filter(w1mat_100>100|w1eng_100>100|w2mat_100>100|w2eng_100>100)%>%count
-```
-
-## Interaction
-```{}
-d_cl1 <- d_cl |> mutate(
-  home.economic.resource.w2 = if_else(is.na(w2be23), w2a09, w2be23)
-) |> mutate(
-  fin.better = if_else(home.economic.resource.w2 > home.economic.resource,
-                       1,
-                       0)
-  )
-
-```
-
-```{}
-feols(avg_dif ~ migr*fin.better + w1avg_100 | schids, data = d_cl1) |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr*fin.better + w1cog_100 | schids, data = d_cl1)  |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(avg_dif ~ migr_mo_only*fin.better + w1avg_100 | schids, data = d_cl1) |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr_mo_only*fin.better + w1cog_100 | schids, data = d_cl1)  |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(avg_dif ~ migr_fa_only*fin.better + w1avg_100 | schids, data = d_cl1) |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr_fa_only*fin.better + w1cog_100 | schids, data = d_cl1)  |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(avg_dif ~ migr_both*fin.better + w1avg_100 | schids, data = d_cl1) |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr_both*fin.better + w1cog_100 | schids, data = d_cl1)  |>
-  msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-```
-
-```{}
-feols(avg_dif ~ migr*fin.better + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
-    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr*fin.better + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
-    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-```
-
-```{}
-d_cl1=d_cl1 |> mutate(
-  supervision.less = if_else((w2a18 + w2a19) < (b2201 + b2202), 1, 0)
-)
-```
-
-```{}
-feols(avg_dif ~ migr*supervision.less + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
-    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-feols(cog_dif ~ migr*supervision.less + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = d_cl1) |>
-    msummary(stars = c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
-           output = 'latex')
-```
-
-```{r}
-bal.tab(m.out)
-```

### 2022-07-07 MScThesisText.Rmd

--- 2022-06-25 MScThesisText.Rmd
@@
 ---
-title             : "Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
+title             : "Parental Migration and Left-Behind Children's Cognitive and Academic Performances"
 shorttitle        : "Left-Behind Children"
@@
 abstract: |
-  Millions of children worldwide are "left behind" when their parents migrate away for work. 
-  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance. 
-  To what extent do different arrangements of parental migration affect children's schooling performance in the short term? 
-  Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey. 
-  I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
-  I measured children's educational performance by standardized cognitive test score and academic exam grades.
-  For causal inference, I built difference-in-differences models with propensity score matching. 
-  Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers. 
-  Father-only migration is negatively associated with children’s cognitive abilities, while mother-only migration is negatively associated with children’s academic grades.
 
@@
 floatsintext      : yes
-linenumbers       : yes
+linenumbers       : no
 draft             : no
@@
 library("papaja")
-library("cobalt")
+library("magrittr")
 r_refs("references.bib")
@@
 
-Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
-These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were living apart from their migrating parents [@nbs2017].
-In a 2021 resolution, the Council of Europe's @parliamentaryassembly2021a expressed concern about "the scale of this phenomenon and the long-term damage it creates" (p.
-2) and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights" (p.
-1).
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work [@antia2020].
+These are the so-called "left behind children" who are common in migrant-sending regions -- Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
+We do not know the global size of left behind children population, but we can find estimate from in-country surveys.
+[@dewaard2018] analyzed the Mexican and Latin American Migration Projects and estimated that around fifteen percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
+[@popova2018] cited a 2016 study by UN Children's Fund Bulgaria indicating that one-fifth of Bulgarian children had one or both parents working abroad.
+In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration [@nbs2017].
 
-How are stay-behind children faring when parents have migrated?
-Research results are mixed due to the differential effects of parental migration.
+The issue of left behind children has attracted public attention. In March 2021, the Parliamentary Assembly of Council of Europe [-@parliamentaryassembly2021] passed a resolution that
+
+> deplores the complacency of both countries of origin and countries of destination of labour migration, which tend to tolerate excessive labour migration as it has significant short-term benefits in the form of remittances for the former, and of a cheap, flexible labour force for the latter.
+This situation is not acceptable, and it is not sustainable.
+Leaving millions of children without parental care is a mass violation of human rights and an unnecessary threat to the stability and prosperity of our countries.
+(p.
+1)
+
+The resolution suggests that parental migration impacts child development by exerting different effects that work oppositely.
 Consider children's education.
-According to the review articles by @debrauw2019 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to Van Hook and Glick [-@vanhook2020], labor migrants send remittances back home, boosting the family income.
+Higher income can fund children's schooling as well as improve their nutritional and living conditions.
+All these may enhance children's educational outcome.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
-Parental migration decreases the amount and quality of parental guidance, protection, and support.
-It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
+Parental migration halts the day-to-day, face-to-face contact between parents and children.
+It decreases the amount and quality of parental guidance, protection, and support.
+All these may hinder children's school performance.
+It is uncertain how these two opposing effects shape children's educational performance, which merits empirical investigation.
 
-A challenge arises in assessing the causality between parent's migration and children's educational achievement.
+A challenge arises in when we want to assess the causality between parental migration and children's education.
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, a quasi-experimental design can help with causal inference.
-The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
+Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions [@cunningham2021].
 
-In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyzed data from a two-wave panel survey.
-The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
-The outcome was measured with children's cognitive test score and academic exam scores.
-I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
+Three features make China a suitable case for studying left behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
+The second feature is the neoliberal welfare regime.
+Neoliberalism extends the logic of the market to most spheres of human life.
+Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
+Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families [@zhan2020].
+The third feature is the authoritarian control against citizens.
+According to Gu [-@gu2021], the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
+Without an urban hukou they cannot send children to public school in the host city.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+The number of left behind Chinese children reached 68.7 million in 2015 [@nbs2017].
+
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
+I analyze the data from a nationally representative two-wave panel survey.
+The sample includes children in both urban and rural areas.
+I develop a difference-in-differences design for causal inference.
+The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
 
@@
 
-## Theoretical Framework
+Researchers obtained mixed results regarding how migration-induced parental absence affects children's education.
+Using data collected from junior high school students, Li and colleagues [-@li2017] found that parental migration negatively impacts left-behind children's achievement in mathematical test.
+Wang and others [-@wang2019] also collected data from students of junior high school, but discovered no overall effect of parental migration on the mathematical test grades of children left behind.
+Bai and coauthors [-@bai2018] gathered data from primary school pupils.
+They reported that parental migration "does not appear to have a negative effect" on the English test results of left-behind children, and "in some cases even appears to have a positive effect" (p.
+1165).
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
 
 Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
-One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital.
+One model, the resource generation model, holds that parental migration brings forth greater resources in the form of economic capital.
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
 Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
-@yang2008 noted that in the Philippes, a sharp depreciation of peso increased the amount of remittances from migrant laborers working abroad.
-This subsequently boosted children's school enrollment and educational expenditure.
-In China, @chang2019 interviewed migrant workers and their family members.
+[@chang2019] provided evidence through interviews with migrant workers and their family members.
+The informants agreed that the city offered more jobs and higher pay than did the countryside.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
@@
 This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.1].
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@wen2019].
-Hong talked to a group of left-behind children at a rural school [@hong2019].
+Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
+The loss of nurturing care slows children's accumulation of human capital.
+Hong talked to a group of left behind children in grade nine when she conducted ethnography at a rural school [@hong2019].
 These students expressed the utter sense of loneliness "with no advocate, no support and with no one looking out for them" (p.
 13).
-Many of them felt indifferent to grades and disengaged with school.
-Some even longed to quit school to pursue a free, independent life (p.
+Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.
 14).
 
-Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
-@botezat2020 studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
-@wang2019 collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, @debrauw2017 showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-@nguyen2016 demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
+I hypothesized that (H1) in the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+This is because parental migration immediately disrupts family structure, resulting in lower academic performance of children.
+It takes longer time for parental migration to generate resources that improve children's performance at school.
 
-Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
-It takes longer time for parental migration to generate resources that improve children's educational attainment.
-I propose the first hypothesis:
-
-$H_1$ In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
-
-Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
-@xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+Xu and others [-@xu2019] adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
 They found that the absence of father only or both parents had "little or no association with negative outcomes" on children's academic and cognitive performances.
@@
 1646).
-@chen2019 conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+Chen and others [-@chen2019] conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
 They found that mother migration was "negatively associated with children's social competence and academic performance," while father migration had no direct effects on the two outcomes (pp.
@@
 
-Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
-Under such norms, children are more likely to accept fathers' migration than mothers' [@murphy2022].
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
-I propose the second hypothesis:
+I hypothesized that (H2) in the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+This relates to the social norms that designate men as breadwinners and women as caregivers.
+Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' [@murphy2022].
+Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
 
-$H_2$ In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
-
-## China's Context
-
-Three features make China a suitable case for studying left-behind children.
-The first feature is the huge scale of internal labor migration.
-According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers [@nbs2022].
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The number of left-behind Chinese children reached 68.7 million in 2015 [@nbs2017].
-The internal migration stemmed from the neoliberal economic regime.
-
-The neoliberal economic regime sounds at odds with China, a so-called socialist country.
-Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the global economy and contributed substantial growth to it.
-The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
-The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare programs are discriminatory -- it segregates the population.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
-As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
-The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere [@duckett2020; @zhang2018].
-
-The institutionalized discrimination against migrant laborers find its roots in China's "multilevel citizenship" system.
-As @vortherms2021 demonstrated, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the *hukou*, or household registration system:
-
-> A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status ...
-Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-[@vortherms2021]
-
-In other words, the hukou system binds one's citizenship rights with one's place of registry.
-In theory, anyone can move out of town freely.
-In practice, they cannot change hukou freely.
-When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2021].
-Migrant workers had organized petitions, strikes, and protests, only to fall on deaf ears or even end with police crackdown [@chan2017].
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
-
-The existing research about China's left-behind children has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
-My sample includes urban left-behind children as well.
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021].
-Others only estimated correlation using cross-sectional data [@akezhuoli2022; @jin2020].
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-The third shortcoming lies in the measurement of outcome.
-@chang2019 and @wang2019 measured students' educational performance with the test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+[@nbs2017] stated that the number of urban left behind children had been growing and expected that the trend would continue.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional data, making it hard to infer causal relations [@zhou2014; @jin2020].
+Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns [@liu2021; @yang2022; @shu2021; @jin2020].
+The third shortcoming lies in the selection and measurement of outcome.
+[@chang2019; @wang2019] measured students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included to measure comprehensive academic achievement.
 
@@
 
-## Sampling
+## Participants
 
@@
 The survey administrator is the National Survey Research Center at Renmin University of China.
-The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
+The research team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
 The baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
@@
 
-I explored two categories of educational performance: cognitive and academic abilities.
+I explored two categories of adolescence development: cognitive and academic abilities.
 One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one [@wang2015].
+The CEPS research team calculated the raw score based on Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
 
-Another dependent variable concerned students' academic performance.
+The other set of dependent variables concerned students' academic performance.
 This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
-Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
-This is related to how junior high schools operate as part of the compulsory education system in China.
-According to @oecd2016, China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
-At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
-Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
-Within each cohort in one particular school, teachers use the same syllabus and administer the same exams during a given assessment period.
-Across cities and regions, junior high schools adopt the educational content and assessment set by the Ministry of Education [@oecd2016].
-
-I transformed the exam grades through the following steps.
-I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
-After the conversion, I checked for abnormal values outside the 0-100 range.
-`r printnum(num.outlier$n)` observations were outliers, accounting for less than one percent of the sample.
-I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
-In this way, I can limit the impact of outliers while retaining these observations in the sample.
-After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
+I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+Accordingly, the total score of three subjects has a 300-point scale.
 
@@
 In both the baseline and the follow-up surveys, parents specified the family members living in the same household at the time.
-I constructed four treatment dummy variables measuring migration arrangements: any parents absent, only father absent, only mother absent, and both parents absent.
-These arrangements are mutually exclusive.
+I constructed six treatment dummy variables measuring migration arrangements: both parents absent, only father absent, only mother absent, father absent (unconditional on mother's migration status), mother absent (unconditional on father's migration status).
+These arrangements can overlap with each other.
 The control group consisted of parents staying with their children throughout at both the baseline and the follow-up surveys.
@@
 
-The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
-
 ## Data analysis
 
-I adopted `R` for all the analyses, the `fixest` package for econometric modeling [@berge2022], and the `modelsummary` package for presenting the results [@arel-bundock2022].
+I adopted `r cite_r("r-references.bib")` for all the analyses, the `fixest` package for building the econometric models [@bergé2018], and the `modelsummary` package for presenting the results [@arel-bundock2022].
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}$$ For student $i$ in class $j$ in baseline and class $k$ in endline, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j,k;1}$ is the test score at baseline, and $C_{j}$ and $C_{k}$ are the classroom fixed-effects at baseline and follow-up, respectively.
-Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
-About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
-This necessitates adding the wave-two classroom fixed-effect.
-
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,c} = \alpha + \beta \cdot migr_{i,c} + \gamma \cdot FE_{c} + \lambda \cdot score_{i,c;base} + \varepsilon_{i,c}$$ For student $i$ in classroom $c$, $\Delta score_{i,c}$ is the change in test score between baseline and follow-up surveys, $migr_{i,c}$ is the treatment dummy variable, $FE_{c}$ is the classroom-level fixed effect, and $score_{i,c;base}$ is the test score at baseline.
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein].
 The standard errors were clustered at the classroom level.
 
-In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I presented an unrestricted and adjusted DID model: $$\Delta score_{i,c} = \alpha + \beta \cdot migr_{i,c} + \gamma \cdot FE_{c} + \lambda \cdot score_{i,c;base} + \theta \cdot X_{i,c} + \varepsilon_{i,c}$$ where $X_{i,c}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
-Table 1 below summarizes the changes in migration status in the sample.
-All `r printnum(nrow(d_cl))` children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
+The table below summarizes the changes in migration status in the sample.
+All 4040 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
 In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
@@
 
-```{r i-var}
-table_independent_variable
+| (1) No migration | (2) Any Parent | (3) Only Mother | (4) Mother (Uncond.) | (5) Only Father | (6) Father (Uncond.) | (7) Both Parents |
+|-----------|-----------|-----------|-----------|-----------|-----------|-----------|
+| 3415             | 625            | 253             | 381                  | 244             | 372                  | 128              |
+
+: Parental migration status at follow-up survey. Among the columns: (2) = (3) + (5) + (7), (4) = (3) + (7), (6) = (5) + (7).
+
+The following two tables summarizes the control variables.
+The distributions between girls and boys, urban and rural hukou holders, as well as Han Chinese and ethnic minorities largely align with the figures reported in the 2015 one-percent National Population Sample Survey [@nbs2017].
+
+| Name          | Explanation                                      | Value             |    N |   \% |
+|:--------------|---------------|:--------------|--------------:|--------------:|
+| ch.girl       | gender                                           | 0 = Male          | 1980 | 49.0 |
+|               |                                                  | 1 = Female        | 2060 | 51.0 |
+| ch.rural      | hukou type                                       | 0 = Rural         | 2212 | 54.8 |
+|               |                                                  | 1 = Urban         | 1828 | 45.2 |
+| ch.health     | self-rated health                                | 1 = Very poor     |   21 |  0.5 |
+|               |                                                  | 2 = Not very good |  112 |  2.8 |
+|               |                                                  | 3 = Moderate      |  800 | 19.8 |
+|               |                                                  | 4 = Good          | 1369 | 33.9 |
+|               |                                                  | 5 = Very good     | 1738 | 43.0 |
+| ch.boarding   | boarding at school                               | 0 = No            | 2885 | 71.4 |
+|               |                                                  | 1 = Yes           | 1155 | 28.6 |
+| ch.ethn.mnrt  | ethnic minority other than Han Chinese           | 0 = No            | 3758 | 93.0 |
+|               |                                                  | 1 = Yes           |  282 |  7.0 |
+| ch.skip.grd   | has skipped grade                                | 0 = No            | 3996 | 98.9 |
+|               |                                                  | 1 = Yes           |   44 |  1.1 |
+| ch.repeat.grd | has repeated grade                               | 0 = No            | 3662 | 90.6 |
+|               |                                                  | 1 = Yes           |  378 |  9.4 |
+| ch.preschool  | attended preschool                               | 0 = No            |  628 | 15.5 |
+|               |                                                  | 1 = Yes           | 3412 | 84.5 |
+| ch.aspr.univ  | aspires to finish university bachelor's or above | 0 = No            | 1158 | 28.7 |
+|               |                                                  | 1 = Yes           | 2882 | 71.3 |
+
+: The control variables at children's level
+
+| Name          | Explanation                                                   | Value                         |    N |   \% |
+|:--------------|---------------|:--------------|--------------:|--------------:|
+| par.edu.year  | years of education of the best-educated parent                | 0 = no formal education       |    8 |  0.2 |
+|               |                                                               | 6 = primary school            |  235 |  5.8 |
+|               |                                                               | 9 = junior high school        | 1554 | 38.5 |
+|               |                                                               | 12 = senior high school       | 1239 | 30.7 |
+|               |                                                               | 15 = associate college        |  383 |  9.5 |
+|               |                                                               | 16 = university undergraduate |  542 | 13.4 |
+|               |                                                               | 19 = university postgraduate  |   79 |  2.0 |
+| par.ccp       | at least one parent is Communist Party member                 | 0 = No                        | 3498 | 86.6 |
+|               |                                                               | 1 = Yes                       |  542 | 13.4 |
+| par.expt.univ | parent expects child to finish university bachelor's or above | 0                             |  704 | 17.4 |
+|               |                                                               | 1                             | 3336 | 82.6 |
+| home.internet | internet access at home                                       | 0                             | 1285 | 31.8 |
+|               |                                                               | 1                             | 2755 | 68.2 |
+| home.book     | number of extracurricular books at home, self-rated by child  | 1 = Very few                  |  383 |  9.5 |
+|               |                                                               | 2 = Not many                  |  406 | 10.0 |
+|               |                                                               | 3 = Some                      | 1298 | 32.1 |
+|               |                                                               | 4 = Quite a few               | 1103 | 27.3 |
+|               |                                                               | 5 = A great number            |  850 | 21.0 |
+| home.finances | household financial situation self-rated by parent            | 1 = Very poor                 |  113 |  2.8 |
+|               |                                                               | 2 = Somewhat poor             |  583 | 14.4 |
+|               |                                                               | 3 = Moderate                  | 3102 | 76.8 |
+|               |                                                               | 4 = Somewhat rich             |  230 |  5.7 |
+|               |                                                               | 5 = Very rich                 |   12 |  0.3 |
+
+: The control variables at parent's and household level
+
+## Multiple Regression
+
+The unrestricted and unadjusted DID models present the following results.
+For both cognitive test score and total exam grade, the any-parent-absent variable has a negative coefficient that differs significantly from zero.
+If a household sees any parent migrated, their child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
+
+How about the coefficients of different types of migration arrangement?
+For total exam grade, the coefficients of mother absent and only mother absent are negative and significantly different from zero.
+The statistical significance does not hold for coefficients of father absent and only father absent.
+Regarding cognitive test score, all coefficients are negative and significantly different from zero, except for only mother absent.
+The effect size of father absent is greater than that of mother absent.
+
+```{r}
+table_unres_cog
 ```
 
-: Parental migration status at follow-up survey.
-
-Tables 2 and 3 below provide the whole-sample summary statistics.
-In addition, the violin plots in the appendix visualize the distribution of outcome variables for the treatment group and the control group.
-
-```{r d-var}
-table_dependent_variable
+```{r}
+table_unres_ttl
 ```
 
-: The independent variables
+To ensure robustness, I controlled for covariates in the unrestricted and adjusted DID models.
+The results from unadjusted models still hold, with only one exception.
+That is, for the cognitive test score, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
 
-```{r c-var}
-table_control_variable
+In the cognitive test score regression, children's age is associated with a negative coefficient that significantly differ from zero.
+Children's aspiration for university education and parents' expectation on children finishing university are both associated with positive coefficients that significantly differ from zero.
+In the total exam grade regression, the aforementioned findings also hold.
+In addition, the female gender of children is linked to a positive, statistically significant coefficient.
+The children's self reported health and the best-educated parent's year of education also have positive, statistically significant coefficients.
+
+```{r}
+table_adj_unres_cog
 ```
 
-: The control variables
-
-## Regression Analysis
-
-The unrestricted DID models support my hypothesis one -- newly left-behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left-behind counterparts.
-If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to `r round(coef(did_cog)[1],2)` SD in cognitive test score and `r round(coef(did_cog)[1],2)` points in academic exam grades.
-Both relationships are slight in strength.
-
-The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
-This holds true for academic abilities.
-Children from only mother migrate households are associated with `r round(coef(did_cog_m_only)[1],2)` points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
-Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left-behind children.
-Children with only father absent are associated with (`r round(coef(did_cog_f_only)[1],2)` SD), and both parents absent (`r round(coef(did_cog_both)[1],2)` SD) compared to the non left-behind children.
-
-```{r reg-cog}
-table_cog
-```
-
-```{r reg-ttl}
-table_ttl
-```
-
-The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
-That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
-
-Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational aspiration as well as parents' expectation on children.
-In terms of age, the older students' scores drop relatively more than younger students'.
-One year older in age is associated with `r round(coef(did_adj_cog)[3],2)` SD for standardized cognitive test and `r round(coef(did_adj_ttl)[3],2)` points for academic exams.
-Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
-The effect sizes are `r round(coef(did_adj_cog)[15],2)` SD and `r round(coef(did_adj_cog)[12],2)` SD for standardized cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
-
-Several predictors are strong in the model of academic grades but not in that of cognitive scores.
-These are children's gender and self-reported health, and the years of parental education.
-Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive test.
-Students who consider themselves healthier are associated with higher scores in academic exams.
-Parents with more education are associated with their children's higher scores in academic exams.
-If the years of parental education of the best-educated among the two increase by one, it would be linked to a `r round(coef(did_adj_ttl)[14],2)` points increase in the child's academic exam grade.
-These three predictors are not significant for cognitive outcomes.
-
-Preschool attendance is associated with higher cognitive outcomes `r round(coef(did_adj_cog)[8],2)` SD, but its effect for academic outcomes is not significant.
-
-```{r reg-cog-adj}
-table_adj_cog
-```
-
-```{r reg-ttl-adj}
-table_adj_ttl
-```
-
-## Matching
-
-Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
-Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
-To tackle the selection bias herein, an applicable technique is matching.
-This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-
-Popular choices for matching include coarsened exact matching (CEM) [@waldman2022] and nearest-neighbor propensity score matching (PSM) [@xu2015].
-As @greifer2022 introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
-The eligibility as the "closest" can be determined with the differences in propensity score.
-Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred [@greifer2022].
-@king2019 argued against this matching method as it risks more "imbalance, model dependence, and bias" for highly balanced data.
-
-Using the `MatchIt` package [@ho2022], I performed matching with all the covariates of the adjusted DID model.
-I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
-I then made do with the PSM.
-I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of @bai2018.
-Exact matching based on county of residence preserves the original geographic distribution.
-The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio was set at one treatment unit with up to three control units.
-The matching produced absolute standardized mean differences below 0.1 for all but a few covariates, suggesting an improved overall balance.
-
-Alike are the results from DID models with matching (DIDM) and those without.
-In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
-In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
-The significance level of any parent migration drops to ten percent.
-In all models, the magnitudes of the statistically significant coefficients are similar.
-I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
-
-```{r reg-m-cog}
-table_m_cog
-```
-
-```{r reg-m-ttl}
-table_m_ttl
+```{r}
+table_adj_unres_ttl
 ```
@@
 # Discussion
-
-This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
-I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
-I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
-
-My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
-Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
-This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
-If some parents were jailed or hospitalized, their absence would be wrongly attributed to migration.
-Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-Possibly, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind.
-These limitations may bias the estimation.
-
-Limitations also arise from unaccounted endogeneity and exogeneity.
-As @chen2009 stated in their research on left-behind children, endogenous factors may create selection bias.
-When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
-Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
-Parental beliefs of this sort are unavailable in CEPS data.
-Exogenous factors may create omitted variable bias.
-Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades [@chen2009].
-I could not account for such shocks as CEPS data does not include detailed geographic information.
-
-From my research, we can find new directions for scholarly inquiry.
-First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
-This would facilitate examination of the parallel trend assumption.
-Second, researchers can try novel methods.
-Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
-Synthetic control can evaluate the aggregate outcome of "large-scale but infrequent interventions" at municipal or provincial levels [@abadie2021], such as the policy experimentations that liberalize the hukou system in certain cities [@wang2020].
-Third, researchers can go beyond outbound migration to study return migration of parents [@liang2021].
-Only a few publications, such as that of @liu2018, have explored return migrants and their stay-behind children in the Chinese context.
-
-Let us consider the policy implications for China.
-The government has pushed for reforming the multilevel citizenship scheme.
-By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
-However, the most popular migration destinations are metropolises like Beijing and Shanghai.
-These mega-cities still restrict migrant workers' local citizenship rights [@wang2020].
-The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
-The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent.
-Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020].
-Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
-Meanwhile, schools should dedicate more advisory and counseling support to children who stay behind.
-
-\newpage
-
-# Appendix
-
-(ref:cog-dif) Changes in standardized cognitive test score
-
-(ref:ttl-dif) Changes in academic exam score
-
-(ref:migr) for new left-behind students and non-left-behind students
-
-(ref:migr-type) by household migration arrangement
-
-```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)")}
-fig_cog
-```
-
-\newpage
-
-```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)")}
-fig_ttl
-```
-
-\newpage
-
-```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
-fig_cog_by_migration_type
-```
-
-\newpage
-
-```{r v-plot-ttl-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)")}
-fig_ttl_by_migration_type
-```
-
-\newpage
-
-(ref:cobalt-match) Covariate balance before and after matching
-
-(ref:cobalt-any) by any parent migration
-
-(ref:cobalt-fa) by father-only migration
-
-(ref:cobalt-mo) by mother-only migration
-
-(ref:cobalt-both) by both parents migration
-
-```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)")}
-love.plot(
-  m.out,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)")}
-love.plot(
-  m.out_mo_only,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)")}
-love.plot(
-  m.out_fa_only,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)")}
-love.plot(
-  m.out_both,
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-\newpage
-
-```{r reg-m-adj-cog}
-table_m_adj_cog
-```
-
-\newpage
-
-```{r reg-m-adj-ttl}
-table_m_adj_ttl
-```
 

### 2022-07-07 MScThesisText.tex

--- 2022-06-29 MScThesisText.tex
@@
 \hypersetup{
-  pdftitle={Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated},
+  pdftitle={Parental Migration and Left-Behind Children's Cognitive and Academic Performances},
   pdfauthor={Jiancheng Gu1},
@@
 \keywords{keywords\newline\indent Word count: X}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 
-\title{Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated}
+\title{Parental Migration and Left-Behind Children's Cognitive and Academic Performances}
 \author{Jiancheng Gu\textsuperscript{1}}
@@
 
-\abstract{%
-Millions of children worldwide are ``left behind'' when their parents migrate away for work.
-Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development, including educational performance.
-To what extent do different arrangements of parental migration affect children's schooling performance in the short term?
-Studying the case of China, I obtained a sample of four thousand junior high school students from a nationally representative two-wave panel survey.
-I differentiated household migration arrangements of any one parent, of mother only, of father only, and of both parents.
-I measured children's educational performance by standardized cognitive test score and academic exam grades.
-For causal inference, I built difference-in-differences models with propensity score matching.
-Results show that the new left-behind children's performance at school dropped slightly compared to that of non-left-behind peers.
-Father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic grades.
-}
-
 \begin{document}
@@
 
-Worldwide, millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work.
-These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were living apart from their migrating parents (NBS et al., 2017).
-In a 2021 resolution, the Council of Europe's Parliamentary Assembly (2021) expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' (p.~2) and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights'' (p.~1).
-
-How are stay-behind children faring when parents have migrated?
-Research results are mixed due to the differential effects of parental migration.
+Millions of children are resided in their home communities but separated from their parents as either one or both parents have migrated for work (Antia et al., 2020).
+These are the so-called ``left behind children'' who are common in migrant-sending regions -- Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
+We do not know the global size of left behind children population, but we can find estimate from in-country surveys.
+(DeWaard et al., 2018) analyzed the Mexican and Latin American Migration Projects and estimated that around fifteen percent of children were left behind in Mexico, El Salvador, Nicaragua, and Puerto Rico in the 2000s.
+(Popova, 2018) cited a 2016 study by UN Children's Fund Bulgaria indicating that one-fifth of Bulgarian children had one or both parents working abroad.
+In China, the 2015 one-percent National Population Sample Survey showed that one out of four children lived under parental absence induced by migration (NBS et al., 2017).
+
+The issue of left behind children has attracted public attention. In March 2021, the Parliamentary Assembly of Council of Europe (2021) passed a resolution that
+
+\begin{quote}
+deplores the complacency of both countries of origin and countries of destination of labour migration, which tend to tolerate excessive labour migration as it has significant short-term benefits in the form of remittances for the former, and of a cheap, flexible labour force for the latter.
+This situation is not acceptable, and it is not sustainable.
+Leaving millions of children without parental care is a mass violation of human rights and an unnecessary threat to the stability and prosperity of our countries.
+(p.~1)
+\end{quote}
+
+The resolution suggests that parental migration impacts child development by exerting different effects that work oppositely.
 Consider children's education.
-According to the review articles by Brauw (2019) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to Van Hook and Glick (2020), labor migrants send remittances back home, boosting the family income.
+Higher income can fund children's schooling as well as improve their nutritional and living conditions.
+All these may enhance children's educational outcome.
 The inflow of remittances, however, cannot substitute for the loss of parental care.
-Parental migration decreases the amount and quality of parental guidance, protection, and support.
-It is uncertain how these two opposing effects together shape children's educational performance, which merits empirical investigation.
-
-A challenge arises in assessing the causality between parent's migration and children's educational achievement.
+Parental migration halts the day-to-day, face-to-face contact between parents and children.
+It decreases the amount and quality of parental guidance, protection, and support.
+All these may hinder children's school performance.
+It is uncertain how these two opposing effects shape children's educational performance, which merits empirical investigation.
+
+A challenge arises in when we want to assess the causality between parental migration and children's education.
 Experiments can unveil causal relations, but it is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, a quasi-experimental design can help with causal inference.
-The cause should be on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
-
-In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
-I choose China as the case and analyzed data from a two-wave panel survey.
-The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness check.
-The outcome was measured with children's cognitive test score and academic exam scores.
-I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
+Alternatively, we can infer causality from a quasi-experimental design -- that is, when the cause is on par with random assignment to participants in the analysis, conditional on identification assumptions (Cunningham, 2021).
+
+Three features make China a suitable case for studying left behind children.
+The first feature is the huge scale of internal labor migration.
+According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
+The second feature is the neoliberal welfare regime.
+Neoliberalism extends the logic of the market to most spheres of human life.
+Driven by the neoliberal doctrine, the government shifts its responsibilities of social services and welfare to individuals and communities.
+Since China initiated pro-market reforms in the 1980s, the state has reduced its welfare provisions and passed them to individuals and families (Zhan, 2020).
+The third feature is the authoritarian control against citizens.
+According to Gu (2021), the hukou (household registration) system controls people's mobility by binding a household's public welfare access with its place of registry.
+For a rural household member moving to the city, it takes much time and effort to apply for urban hukou status.
+Without an urban hukou they cannot send children to public school in the host city.
+Facing financial and policy constraints, many migrant laborers have to leave children in their original domiciles.
+The number of left behind Chinese children reached 68.7 million in 2015 (NBS et al., 2017).
+
+To what extent do parental migration affect the cognitive development and academic performance of left-behind children in the short term?
+I analyze the data from a nationally representative two-wave panel survey.
+The sample includes children in both urban and rural areas.
+I develop a difference-in-differences design for causal inference.
+The dependent variables include children's cognitive test score and Chinese, mathematics, and English exam scores.
 
@@
 
-\hypertarget{theoretical-framework}{%
-\subsection{Theoretical Framework}\label{theoretical-framework}}
+Researchers obtained mixed results regarding how migration-induced parental absence affects children's education.
+Using data collected from junior high school students, Li and colleagues (2017) found that parental migration negatively impacts left-behind children's achievement in mathematical test.
+Wang and others (2019) also collected data from students of junior high school, but discovered no overall effect of parental migration on the mathematical test grades of children left behind.
+Bai and coauthors (2018) gathered data from primary school pupils.
+They reported that parental migration ``does not appear to have a negative effect'' on the English test results of left-behind children, and ``in some cases even appears to have a positive effect'' (p.~1165).
+The inconsistency can result from factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
 
 Between parental migration and children's education, the mechanisms trace to two theoretical frameworks.
-One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital.
+One model, the resource generation model, holds that parental migration brings forth greater resources in the form of economic capital.
 Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
@@
 Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
-D.
-Yang (2008) noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
-This subsequently boosted children's school enrollment and educational expenditure.
-In China, Chang et al.
-(2019) interviewed migrant workers and their family members.
+(Chang et al., 2019) provided evidence through interviews with migrant workers and their family members.
+The informants agreed that the city offered more jobs and higher pay than did the countryside.
 Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
@@
 1).
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents (Wen \& Xie, 2019).
-Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
+Parental migration decreases nurturing care, thereby hindering children's developmental outcomes.
+The loss of nurturing care slows children's accumulation of human capital.
+Hong talked to a group of left behind children in grade nine when she conducted ethnography at a rural school (Hong \& Fuller, 2019).
 These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
-Many of them felt indifferent to grades and disengaged with school.
-Some even longed to quit school to pursue a free, independent life (p.~14).
-
-Given the two opposing effects, researchers have obtained mixed results regarding how parental migration impacts children's education.
-Botezat and Pfeiffer (2020) studied the case of Romania and found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen.
-L.
-Wang et al.
-(2019) collected data from junior high school students in central China and found no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, Brauw and Giles (2017) showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
-Nguyen (2016) demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
-The inconsistency can be complicated by factors such as the left-behind children's age and gender, the migrant parent's original domicile and eventual destination, and the arrangement of which parent migrate for how long.
-
-Parental migration immediately disrupts family structure, which in turn lowers academic performance of children.
-It takes longer time for parental migration to generate resources that improve children's educational attainment.
-I propose the first hypothesis:
-
-\(H_1\) In the short term, parental migration negatively affect the cognitive development and academic performance of children left-behind.
-
-Researchers have studied whether the impact differ between mother absence and father absence induced by labor migration.
-Y.
-Xu et al.
-(2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
+Many of them felt indifferent to school grades, and some even longed to ditch school to pursue a free, independent life (p.~14).
+
+I hypothesized that (H1) in the short term, parental migration negatively affect the cognitive development and academic performance of children left behind.
+This is because parental migration immediately disrupts family structure, resulting in lower academic performance of children.
+It takes longer time for parental migration to generate resources that improve children's performance at school.
+
+Researchers have studied whether the impact differ between mother absence and father absence in the context of labor migration.
+Xu and others (2019) adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
 They found that the absence of father only or both parents had ``little or no association with negative outcomes'' on children's academic and cognitive performances.
 Only-mother absence, however, showed a ``strong association with negative outcomes'' (p.~1646).
-Chen et al.
-(2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
+Chen and others (2019) conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
 They found that mother migration was ``negatively associated with children's social competence and academic performance,'' while father migration had no direct effects on the two outcomes (pp.~860-861).
 
-Studies noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
-Under such norms, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
-I propose the second hypothesis:
-
-\(H_2\) In the short term, mother's migration negatively affect the cognitive development and academic performance of children left-behind, while father's migration does not show a effect.
-
-\hypertarget{chinas-context}{%
-\subsection{China's Context}\label{chinas-context}}
-
-Three features make China a suitable case for studying left-behind children.
-The first feature is the huge scale of internal labor migration.
-According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers (NBS, 2022).
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
-The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS et al., 2017).
-The internal migration stemmed from the neoliberal economic regime.
-
-The neoliberal economic regime sounds at odds with China, a so-called socialist country.
-Actually, in the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the global economy and contributed substantial growth to it.
-The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
-The rural hinterlands, however, have lagged behind.
-The regional inequality needs social policy to amend, but China's welfare program is discriminatory -- it segregates the population.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed people.
-As rural people migrate to the city, they find themselves with limited access to social welfare in the destination.
-The municipal governments only provide welfare to local residents and expect non-local residents access public services elsewhere (Duckett, 2020; Zhang, 2018).
-
-The institutionalized discrimination against migrant laborers find its roots in China's ``multilevel citizenship'' system.
-As Vortherms (2021) demonstrated, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the \emph{hukou}, or household registration system:
-
-\begin{quote}
-A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status \ldots{} Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-(Vortherms, 2021)
-\end{quote}
-
-In other words, the hukou system binds one's citizenship rights with one's place of registry.
-In theory, anyone can move out of town freely.
-In practice, they cannot change hukou freely.
-When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022).
-Migrant workers have organized petitions, strikes, and protests.
-These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019).
-Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
-
-The existing research about China's left-behind children has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
-My sample includes urban left-behind children as well.
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Y.
-Liu et al., 2021; Shu, 2021; F.
-Yang et al., 2022).
-Others only estimated correlation using cross-sectional data (Akezhuoli et al., 2022; Jin et al., 2020).
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
-The third shortcoming lies in the measurement of outcome.
-Chang et al.
-(2019) and L.
-Wang et al.
-(2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
+I hypothesized that (H2) in the short term, mother migration negatively affect the cognitive development and academic performance of children left behind, while father migration does not show a effect.
+This relates to the social norms that designate men as breadwinners and women as caregivers.
+Studies noted that in some Asian and Latin American societies, children are more likely to accept fathers' migration than mothers' (Murphy, 2022).
+Left behind children may even resent their migrant mothers, viewing them as transgressing on the expected care-giving roles.
+
+The research on China's left behind children has three major shortcomings.
+First, most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
+(NBS et al., 2017) stated that the number of urban left behind children had been growing and expected that the trend would continue.
+The second shortcoming lies in data and sampling.
+Some studies draw from cross-sectional data, making it hard to infer causal relations (Jin et al., 2020; Zhou et al., 2014).
+Others suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one or a few towns (Jin et al., 2020; Liu et al., 2021; Shu, 2021; Yang et al., 2022).
+The third shortcoming lies in the selection and measurement of outcome.
+(Chang et al., 2019; Wang et al., 2019) measured students' educational performance with the test score of only one academic subject, namely mathematics.
+The test results of multiple subjects should be included to measure comprehensive academic achievement.
 
@@
 
-\hypertarget{sampling}{%
-\subsection{Sampling}\label{sampling}}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 To deal with missing values, I adopted list-wise deletion for dependent, independent, and control variables.
-The final sample size amounted to 4088 .
+The final sample size amounted to 4040 .
 
@@
 
-I explored two categories of educational performance: cognitive and academic abilities.
+I explored two categories of adolescence development: cognitive and academic abilities.
 One key dependent variable, the student's cognitive skill, was measured by a fifteen-minute standardized test.
 The test covered three types of reasoning: verbal, visuospatial, and numerical.
-The CEPS research team calculated the raw score based on the Item Response Theory and then standardized the score across the whole national sample with a mean of zero and standard deviation of one (W.
-Wang \& Li, 2015).
-
-Another dependent variable concerned students' academic performance.
+The CEPS research team calculated the raw score based on Item Response Theory and then standardized the score with a mean of zero and standard deviation of one.
+
+The other set of dependent variables concerned students' academic performance.
 This was measured by the total scores of mid-term exams in Chinese, mathematics, and English as provided by each school.
-Exam scores are reliable indicators of learning performance, and are comparable across schools for the same cohort of students.
-This is related to how junior high schools operate as part of the compulsory education system in China.
-According to OECD (2016), China's junior secondary education is a unified system that does not distinguish between academic and vocational tracks.
-At school, Chinese, mathematics, and English are core subjects and others as supplementary subjects.
-Throughout junior high school, students study the core subjects in preparation for the senior high school entrance exam.
-Within each cohort in one particular school, teachers use the same syllabus and administer the same exams during a given assessment period.
-Across cities and regions, junior high schools adopt the educational content and assessment set by the Ministry of Education (OECD, 2016).
-
-I transformed the exam grades through the following steps.
-I first aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
-After the conversion, I checked for abnormal values outside the 0-100 range.
-31 observations were outliers, accounting for less than one percent of the sample.
-I trimmed the values of subject exam score with minimum of zero and maximum of one hundred.
-In this way, I can limit the impact of outliers while retaining these observations in the sample.
-After trimming, I aggregated the subject exam scores to obtain a total score of a 300-point scale.
+I aligned different grading scales (full mark of 100, 120, and 150 for one subject) to the hundred-point scale.
+Accordingly, the total score of three subjects has a 300-point scale.
 
@@
 
-The control variables on children include their age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the level of education of the best-educated parent, the parental expectation on the child's level of education, the perceived household financial conditions, the number of extracurricular books at home, and the internet access at home.
-
 \hypertarget{data-analysis}{%
@@
 
-I adopted \texttt{R} for all the analyses, the \texttt{fixest} package for econometric modeling (Berge et al., 2022), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
+I adopted R (Version 4.2.0; R Core Team, 2022) and the R-packages \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all the analyses, the \texttt{fixest} package for building the econometric models (Bergé, 2018), and the \texttt{modelsummary} package for presenting the results (Arel-Bundock, 2022).
 I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \varepsilon_{i,j,k}\] For student \(i\) in class \(j\) in baseline and class \(k\) in endline, \(\Delta score_{i,j}\) is the change in test score between baseline and follow-up surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j,k;1}\) is the test score at baseline, and \(C_{j}\) and \(C_{k}\) are the classroom fixed-effects at baseline and follow-up, respectively.
-Classroom fixed-effect can account for differences due to time-invariant factors at the classroom level and above, as students nested in the same class are also in the same school and county.
-About one-sixth of the students were reassigned into new classroom at the end of baseline academic year.
-This necessitates adding the wave-two classroom fixed-effect.
-
+I first specified an unrestricted and unadjusted model: \[\Delta score_{i,c} = \alpha + \beta \cdot migr_{i,c} + \gamma \cdot FE_{c} + \lambda \cdot score_{i,c;base} + \varepsilon_{i,c}\] For student \(i\) in classroom \(c\), \(\Delta score_{i,c}\) is the change in test score between baseline and follow-up surveys, \(migr_{i,c}\) is the treatment dummy variable, \(FE_{c}\) is the classroom-level fixed effect, and \(score_{i,c;base}\) is the test score at baseline.
 The model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, n.d.).
 The standard errors were clustered at the classroom level.
 
-In addition, I present an unrestricted and adjusted DID model: \[\Delta score_{i,j,k} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i,j,k;1} + \lambda \cdot C_{j} + \theta \cdot C_{k} + \zeta \cdot X_{i} + \varepsilon_{i,j,k}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I presented an unrestricted and adjusted DID model: \[\Delta score_{i,c} = \alpha + \beta \cdot migr_{i,c} + \gamma \cdot FE_{c} + \lambda \cdot score_{i,c;base} + \theta \cdot X_{i,c} + \varepsilon_{i,c}\] where \(X_{i,c}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
-Table 1 below summarizes the changes in migration status in the sample.
-All 4088 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
+The table below summarizes the changes in migration status in the sample.
+All 4040 children were living together with parents in one household in baseline, but about fifteen percent saw at least one parent migrated during the two waves of survey.
 In these new migrant households, only-mother migration and only-father migration each accounted for two out of five cases.
@@
 
-\renewcommand{\arraystretch}{0.75}
-
-\begin{longtable}[]{@{}llrr@{}}
-\toprule
-& & N & \% \\
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1429}}@{}}
+\caption{Parental migration status at follow-up survey. Among the columns: (2) = (3) + (5) + (7), (4) = (3) + (7), (6) = (5) + (7).}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+(1) No migration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(2) Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(3) Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(4) Mother (Uncond.)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(5) Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(6) Father (Uncond.)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(7) Both Parents
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+(1) No migration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(2) Any Parent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(3) Only Mother
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(4) Mother (Uncond.)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(5) Only Father
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(6) Father (Uncond.)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+(7) Both Parents
+\end{minipage} \\
 \midrule
 \endhead
-Parental Migration & No & 3452 & 84.4 \\
-& Yes & 636 & 15.6 \\
-Parental Migration Type & Both Parents At Home & 3452 & 84.4 \\
-& Both Parents Migrated & 131 & 3.2 \\
-& Only Father Migrated & 251 & 6.1 \\
-& Only Mother Migrated & 254 & 6.2 \\
+3415 & 625 & 253 & 381 & 244 & 372 & 128 \\
 \bottomrule
@@
 
-\newpage
-
-Tables 2 below summarizes the dependent variables by the control group and the treatment group. In addition, the violin plots in the appendix visualize the distribution of outcome variables.
-
-\begin{tabular}{llllll}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
-\cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
-Variable & Mean & Sd & Mean & Sd & Test\\
-\midrule
-Cognitive test score difference & 0.28 & 0.8 & 0.19 & 0.8 & p=0.006**\\
-\hspace{1em}Wave 1 score & 0.15 & 0.86 & 0.13 & 0.84 & p=0.471\\
-\hspace{1em}Wave 2 score & 0.43 & 0.78 & 0.31 & 0.8 & p<0.001***\\
-Academic exam score difference & -8.2 & 32.75 & -12.15 & 35.43 & p=0.006**\\
-\hspace{1em}Wave 1 score & 213.39 & 49.31 & 211.58 & 50.3 & p=0.395\\
-\addlinespace
-\hspace{1em}Wave 2 score & 205.19 & 54.83 & 199.42 & 58.23 & p=0.016*\\
-\bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
-\end{tabular}
-
-\newpage
-
-\begin{tabular}{llllll}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
-\cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
-Variable & N & Percent & N & Percent & Test\\
-\midrule
-child.is.girl &  &  &  &  & X2=11.942***\\
-... 0 & 1650 & 48\% & 352 & 55\% & \\
-... 1 & 1802 & 52\% & 284 & 45\% & \\
-child.has.rural.hukou &  &  &  &  & X2=0.485\\
-... 0 & 1884 & 55\% & 337 & 53\% & \\
-\addlinespace
-... 1 & 1568 & 45\% & 299 & 47\% & \\
-child.in.boarding.school &  &  &  &  & X2=4.63*\\
-... 0 & 2477 & 72\% & 429 & 67\% & \\
-... 1 & 975 & 28\% & 207 & 33\% & \\
-child.is.ethnic.minority &  &  &  &  & X2=0.388\\
-\addlinespace
-... 0 & 3213 & 93\% & 587 & 92\% & \\
-... 1 & 239 & 7\% & 49 & 8\% & \\
-child.had.skipped.grade &  &  &  &  & X2=0.02\\
-... 0 & 3414 & 99\% & 628 & 99\% & \\
-... 1 & 38 & 1\% & 8 & 1\% & \\
-\addlinespace
-child.had.repeated.grade &  &  &  &  & X2=10.621**\\
-... 0 & 3147 & 91\% & 553 & 87\% & \\
-... 1 & 305 & 9\% & 83 & 13\% & \\
-child.went.to.preschool &  &  &  &  & X2=0.923\\
-... 0 & 531 & 15\% & 108 & 17\% & \\
-\addlinespace
-... 1 & 2921 & 85\% & 528 & 83\% & \\
-parent.has.white.collar.job &  &  &  &  & X2=0.001\\
-... 0 & 2735 & 79\% & 503 & 79\% & \\
-... 1 & 717 & 21\% & 133 & 21\% & \\
-home.has.internet &  &  &  &  & X2=12.815***\\
-\addlinespace
-... 0 & 1072 & 31\% & 244 & 38\% & \\
-... 1 & 2380 & 69\% & 392 & 62\% & \\
-\bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
-\end{tabular}
-
-\newpage
-
-\begin{tabular}{llllll}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Parental Migration} \\
-\cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3452} & \multicolumn{2}{c}{Yes = 636} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
-Variable & Mean & Sd & Mean & Sd & Test\\
-\midrule
-child.age & 12.45 & 0.63 & 12.5 & 0.72 & F=3.616\\
-child.health.self.rated & 4.17 & 0.87 & 4.14 & 0.9 & F=0.622\\
-child.educational.aspiration & 3.97 & 1.12 & 3.93 & 1.19 & F=0.617\\
-parent.educational.level & 2.9 & 1.19 & 2.94 & 1.21 & F=0.367\\
-parent.expectation.on.child & 4.19 & 0.91 & 4.15 & 0.94 & F=1.093\\
-\addlinespace
-home.extracurricular.book & 3.41 & 1.18 & 3.32 & 1.28 & F=3.09\\
-home.economic.resource & 2.87 & 0.55 & 2.84 & 0.58 & F=1.37\\
-\bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}* p < 0.05, ** p < 0.01, *** p < 0.001}\\
-\end{tabular}
-
-\hypertarget{regression-analysis}{%
-\subsection{Regression Analysis}\label{regression-analysis}}
-
-The unrestricted DID models support my hypothesis one -- newly left-behind adolescents are more likely to perform worse in cognitive and academic abilities than their non left-behind counterparts.
-If a household sees any parent migrated, the child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
-Parental migration is linked to -0.09 SD in cognitive test score and -0.09 points in academic exam grades.
-Both relationships are slight in strength.
-
-The results only partially support the hypothesis two -- mother migration has a more negative effect than father migration.
-This holds true for academic abilities.
-Children from only mother migrate households are associated with -0.04 points relative to that of children whose parents stay along.
-The performances of children with both parents migrated or only father migrated do not show statistically significant difference from the non left-behind children.
-Regarding cognitive abilities, the reverse is true.
-Children with only mother migrated do not show statistically significant difference from the non left-behind children.
-Children with only father absent are associated with (-0.14 SD), and both parents absent (-0.10 SD) compared to the non left-behind children.
+The following two tables summarizes the control variables.
+The distributions between girls and boys, urban and rural hukou holders, as well as Han Chinese and ethnic minorities largely align with the figures reported in the 2015 one-percent National Population Sample Survey (NBS et al., 2017).
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+\caption{The control variables at children's level}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Explanation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+N
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\%
 \end{minipage} \\
@@
 \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Explanation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+N
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\%
 \end{minipage} \\
@@
 \endhead
-Migration & -0.09** & -0.04 & -0.14** & -0.10 \\
-& (0.03) & (0.05) & (0.04) & (0.06) \\
-W1 score & -0.62*** & -0.63*** & -0.62*** & -0.62*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.494 & 0.502 & 0.505 & 0.499 \\
-R2 Adj. & 0.424 & 0.426 & 0.430 & 0.419 \\
-R2 Within & 0.370 & 0.378 & 0.378 & 0.374 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+ch.girl & gender & 0 = Male & 1980 & 49.0 \\
+& & 1 = Female & 2060 & 51.0 \\
+ch.rural & hukou type & 0 = Rural & 2212 & 54.8 \\
+& & 1 = Urban & 1828 & 45.2 \\
+ch.health & self-rated health & 1 = Very poor & 21 & 0.5 \\
+& & 2 = Not very good & 112 & 2.8 \\
+& & 3 = Moderate & 800 & 19.8 \\
+& & 4 = Good & 1369 & 33.9 \\
+& & 5 = Very good & 1738 & 43.0 \\
+ch.boarding & boarding at school & 0 = No & 2885 & 71.4 \\
+& & 1 = Yes & 1155 & 28.6 \\
+ch.ethn.mnrt & ethnic minority other than Han Chinese & 0 = No & 3758 & 93.0 \\
+& & 1 = Yes & 282 & 7.0 \\
+ch.skip.grd & has skipped grade & 0 = No & 3996 & 98.9 \\
+& & 1 = Yes & 44 & 1.1 \\
+ch.repeat.grd & has repeated grade & 0 = No & 3662 & 90.6 \\
+& & 1 = Yes & 378 & 9.4 \\
+ch.preschool & attended preschool & 0 = No & 628 & 15.5 \\
+& & 1 = Yes & 3412 & 84.5 \\
+ch.aspr.univ & aspires to finish university bachelor's or above & 0 = No & 1158 & 28.7 \\
+& & 1 = Yes & 2882 & 71.3 \\
 \bottomrule
@@
 
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+\caption{The control variables at parent's and household level}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Explanation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+N
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\%
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Explanation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+N
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\%
+\end{minipage} \\
+\midrule
+\endhead
+par.edu.year & years of education of the best-educated parent & 0 = no formal education & 8 & 0.2 \\
+& & 6 = primary school & 235 & 5.8 \\
+& & 9 = junior high school & 1554 & 38.5 \\
+& & 12 = senior high school & 1239 & 30.7 \\
+& & 15 = associate college & 383 & 9.5 \\
+& & 16 = university undergraduate & 542 & 13.4 \\
+& & 19 = university postgraduate & 79 & 2.0 \\
+par.ccp & at least one parent is Communist Party member & 0 = No & 3498 & 86.6 \\
+& & 1 = Yes & 542 & 13.4 \\
+par.expt.univ & parent expects child to finish university bachelor's or above & 0 & 704 & 17.4 \\
+& & 1 & 3336 & 82.6 \\
+home.internet & internet access at home & 0 & 1285 & 31.8 \\
+& & 1 & 2755 & 68.2 \\
+home.book & number of extracurricular books at home, self-rated by child & 1 = Very few & 383 & 9.5 \\
+& & 2 = Not many & 406 & 10.0 \\
+& & 3 = Some & 1298 & 32.1 \\
+& & 4 = Quite a few & 1103 & 27.3 \\
+& & 5 = A great number & 850 & 21.0 \\
+home.finances & household financial situation self-rated by parent & 1 = Very poor & 113 & 2.8 \\
+& & 2 = Somewhat poor & 583 & 14.4 \\
+& & 3 = Moderate & 3102 & 76.8 \\
+& & 4 = Somewhat rich & 230 & 5.7 \\
+& & 5 = Very rich & 12 & 0.3 \\
+\bottomrule
+\end{longtable}
+
+\hypertarget{multiple-regression}{%
+\subsection{Multiple Regression}\label{multiple-regression}}
+
+The unrestricted and unadjusted DID models present the following results.
+For both cognitive test score and total exam grade, the any-parent-absent variable has a negative coefficient that differs significantly from zero.
+If a household sees any parent migrated, their child's cognitive test score and total exam grade would decrease relative to that of children whose parents stay with them, holding everything else constant.
+
+How about the coefficients of different types of migration arrangement?
+For total exam grade, the coefficients of mother absent and only mother absent are negative and significantly different from zero.
+The statistical significance does not hold for coefficients of father absent and only father absent.
+Regarding cognitive test score, all coefficients are negative and significantly different from zero, except for only mother absent.
+The effect size of father absent is greater than that of mother absent.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0909}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1570}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1653}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1240}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1653}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1240}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1736}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
+\end{minipage} \\
+\midrule
+\endhead
+Explanator & -0.10*** & -0.05 & -0.08* & -0.14*** & -0.14*** & -0.13* \\
+& (0.03) & (0.05) & (0.04) & (0.04) & (0.03) & (0.06) \\
+W1 score & -0.61*** & -0.62*** & -0.62*** & -0.61*** & -0.61*** & -0.62*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4040 & 3668 & 3796 & 3659 & 3787 & 3543 \\
+R2 & 0.476 & 0.483 & 0.475 & 0.488 & 0.480 & 0.479 \\
+R2 Adj. & 0.446 & 0.451 & 0.443 & 0.456 & 0.448 & 0.445 \\
+R2 Within & 0.364 & 0.370 & 0.364 & 0.372 & 0.367 & 0.367 \\
+R2 Pseudo & & & & & & \\
+AIC & 7443.2 & 6769.4 & 7041.9 & 6674.9 & 6947.4 & 6547.5 \\
+BIC & 8830.1 & 8128.8 & 8415.1 & 8033.8 & 8320.1 & 7905.5 \\
+Log.Lik. & -3501.606 & -3165.681 & -3300.971 & -3118.446 & -3253.719 & -3053.770 \\
+Std.Errors & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids \\
+FE: clsids & X & X & X & X & X & X \\
+\bottomrule
+\end{longtable}
+
 \textbf{Note:}
@@
 
-\textbf{Note:}
-\^{}\^{} Control variables not included
-
-\newpage
-
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's academic exam score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0909}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1570}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1653}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1240}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1653}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1240}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1736}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
 \end{minipage} \\
@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
 \end{minipage} \\
@@
 \endhead
-Migration & -2.67* & -5.85* & -0.25 & -1.13 \\
-& (1.26) & (2.36) & (1.66) & (2.28) \\
-W1 score & 0.04 & 0.04† & 0.04† & 0.04 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.562 & 0.577 & 0.566 & 0.577 \\
-R2 Adj. & 0.501 & 0.513 & 0.500 & 0.510 \\
-R2 Within & 0.005 & 0.009 & 0.004 & 0.004 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+Explanator & -2.88* & -6.31** & -4.12* & -0.71 & -0.71 & -0.18 \\
+& (1.21) & (2.22) & (1.71) & (1.64) & (1.31) & (2.19) \\
+W1 score & 0.04 & 0.04 & 0.03 & 0.04 & 0.04 & 0.03 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+Num.Obs. & 4040 & 3668 & 3796 & 3659 & 3787 & 3543 \\
+R2 & 0.547 & 0.562 & 0.558 & 0.552 & 0.550 & 0.562 \\
+R2 Adj. & 0.521 & 0.534 & 0.531 & 0.524 & 0.522 & 0.533 \\
+R2 Within & 0.006 & 0.008 & 0.006 & 0.004 & 0.003 & 0.002 \\
+R2 Pseudo & & & & & & \\
+AIC & 37012.2 & 33524.8 & 34717.7 & 33408.4 & 34591.1 & 32296.6 \\
+BIC & 38399.1 & 34884.3 & 36090.9 & 34767.3 & 35963.7 & 33654.6 \\
+Log.Lik. & -18286.101 & -16543.420 & -17138.864 & -16485.186 & -17075.527 & -15928.290 \\
+Std.Errors & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids \\
+FE: clsids & X & X & X & X & X & X \\
 \bottomrule
@@
 
-\textbf{Note:}
-\^{}\^{} Control variables not included
-
-The adjusted DID models produce similar results compared to the unadjusted models, with only one exception.
-That is, for the cognitive skills, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
-
-Some predictors are strong in both models of cognitive and academic abilities.
-These are children's age and educational aspiration as well as parents' expectation on children.
-In terms of age, the older students' scores drop relatively more than younger students'.
-One year older in age is associated with -0.07 SD for standardized cognitive test and -1.23 points for academic exams.
-Parent's expectation for children completing university and children's own aspiration for finishing university are associated with higher scores.
-The effect sizes are 0.01 SD and 0.07 SD for standardized cognitive test, respectively; and 0.29 points and 1.82 points for academic exams, respectively.
-
-Several predictors are strong in the model of academic grades but not in that of cognitive scores.
-These are children's gender and self-reported health, and the years of parental education.
-Girls outperform boys by 4.49 points in academic exams, but do not show advantage in cognitive test.
-Students who consider themselves healthier are associated with higher scores in academic exams.
-Parents with more education are associated with their children's higher scores in academic exams.
-If the years of parental education of the best-educated among the two increase by one, it would be linked to a 0.88 points increase in the child's academic exam grade.
-These three predictors are not significant for cognitive outcomes.
-
-Preschool attendance is associated with higher cognitive outcomes 0.07 SD, but its effect for academic outcomes is not significant.
+To ensure robustness, I controlled for covariates in the unrestricted and adjusted DID models.
+The results from unadjusted models still hold, with only one exception.
+That is, for the cognitive test score, the both-parent-absent coefficient saw a change of statistical significance level from five percent level to ten percent level.
+
+In the cognitive test score regression, children's age is associated with a negative coefficient that significantly differ from zero.
+Children's aspiration for university education and parents' expectation on children finishing university are both associated with positive coefficients that significantly differ from zero.
+In the total exam grade regression, the aforementioned findings also hold.
+In addition, the female gender of children is linked to a positive, statistically significant coefficient.
+The children's self reported health and the best-educated parent's year of education also have positive, statistically significant coefficients.
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2661}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1743}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1835}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1927}}@{}}
-\caption{Parental migration's effect on children's cognitive test score}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1129}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1532}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1613}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1210}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1613}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1210}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1694}}@{}}
+\caption{Parental migration's effect on children's cognitive abilities}\tabularnewline
 \toprule
@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
 Only Father Absent
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
 Both Parents Absent
@@
 \endhead
-Migration & -0.09** & -0.04 & -0.14*** & -0.08 \\
-& (0.03) & (0.05) & (0.04) & (0.06) \\
-W1 score & -0.67*** & -0.67*** & -0.67*** & -0.67*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.age & -0.07*** & -0.06** & -0.07*** & -0.08*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.is.girl & -0.01 & 0.00 & 0.00 & -0.01 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.health.self.rated & -0.02 & -0.02 & -0.02 & -0.02 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-child.has.rural.hukou & -0.01 & 0.00 & -0.01 & 0.00 \\
-& (0.02) & (0.03) & (0.03) & (0.03) \\
-child.number.of.sibling & -0.03 & -0.02 & -0.02 & -0.02 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-child.went.to.preschool & 0.07* & 0.06† & 0.05† & 0.07* \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-child.had.skipped.grade & -0.17 & -0.11 & -0.20 & -0.10 \\
-& (0.12) & (0.12) & (0.12) & (0.12) \\
-child.had.repeated.grade & -0.08* & -0.11** & -0.07† & -0.06 \\
-& (0.04) & (0.04) & (0.04) & (0.04) \\
-child.in.boarding.school & 0.04 & 0.02 & 0.02 & 0.01 \\
-& (0.04) & (0.04) & (0.04) & (0.04) \\
-child.educational.aspiration & 0.07*** & 0.07*** & 0.07*** & 0.08*** \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-child.is.ethnic.minority & 0.04 & 0.04 & 0.02 & 0.02 \\
-& (0.06) & (0.06) & (0.06) & (0.06) \\
-parent.expectation.on.child & 0.08*** & 0.09*** & 0.09*** & 0.09*** \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-parent.has.white.collar.job & 0.01 & -0.01 & 0.01 & 0.00 \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-parent.educational.level & 0.01 & 0.01 & 0.01 & 0.01 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-home.economic.resource & -0.02 & -0.01 & 0.00 & 0.00 \\
-& (0.02) & (0.02) & (0.02) & (0.02) \\
-home.extracurricular.book & 0.01 & 0.00 & 0.01 & 0.00 \\
-& (0.01) & (0.01) & (0.01) & (0.01) \\
-home.has.internet & -0.01 & -0.01 & -0.02 & -0.02 \\
-& (0.03) & (0.03) & (0.03) & (0.03) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.525 & 0.533 & 0.537 & 0.530 \\
-R2 Adj. & 0.458 & 0.459 & 0.464 & 0.452 \\
-R2 Within & 0.409 & 0.416 & 0.418 & 0.413 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+Explanator & -0.10*** & -0.06 & -0.08* & -0.14*** & -0.13*** & -0.12† \\
+& (0.03) & (0.04) & (0.04) & (0.04) & (0.03) & (0.06) \\
+W1 score & -0.65*** & -0.66*** & -0.66*** & -0.65*** & -0.65*** & -0.65*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+age & -0.08*** & -0.08*** & -0.09*** & -0.08*** & -0.09*** & -0.09*** \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.girl & -0.01 & -0.01 & -0.01 & -0.01 & -0.01 & -0.01 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.health & -0.02 & -0.02 & -0.02 & -0.02 & -0.01 & -0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+ch.rural & 0.01 & 0.01 & 0.01 & 0.00 & 0.00 & 0.01 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.03) \\
+ch.sibling & -0.02 & -0.02 & -0.02 & -0.02 & -0.02 & -0.02 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+ch.preschool & 0.07* & 0.05† & 0.07* & 0.05† & 0.07* & 0.07* \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+ch.skip.grd & -0.18 & -0.14 & -0.11 & -0.20† & -0.18 & -0.11 \\
+& (0.12) & (0.12) & (0.12) & (0.12) & (0.12) & (0.13) \\
+ch.repeat.grd & -0.07† & -0.09* & -0.07† & -0.06 & -0.05 & -0.04 \\
+& (0.04) & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\
+ch.boarding & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 \\
+& (0.04) & (0.04) & (0.04) & (0.04) & (0.04) & (0.04) \\
+ch.aspr.univ & 0.16*** & 0.15*** & 0.16*** & 0.15*** & 0.16*** & 0.15*** \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+ch.ethn.mnrt & 0.05 & 0.06 & 0.05 & 0.04 & 0.03 & 0.03 \\
+& (0.06) & (0.06) & (0.06) & (0.06) & (0.06) & (0.06) \\
+par.edu.year & 0.01† & 0.01* & 0.01* & 0.01 & 0.01 & 0.01 \\
+& (0.00) & (0.00) & (0.00) & (0.00) & (0.00) & (0.00) \\
+par.expt.univ & 0.19*** & 0.22*** & 0.20*** & 0.21*** & 0.20*** & 0.21*** \\
+& (0.03) & (0.04) & (0.03) & (0.03) & (0.03) & (0.03) \\
+par.ccp & -0.02 & -0.03 & -0.03 & 0.00 & -0.01 & -0.02 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+home.finances & -0.01 & -0.01 & -0.01 & 0.00 & 0.00 & 0.01 \\
+& (0.02) & (0.02) & (0.02) & (0.02) & (0.02) & (0.02) \\
+home.book & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+& (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) \\
+home.internet & -0.01 & -0.01 & 0.00 & -0.01 & -0.01 & -0.01 \\
+& (0.03) & (0.03) & (0.03) & (0.03) & (0.03) & (0.03) \\
+Num.Obs. & 4040 & 3668 & 3796 & 3659 & 3787 & 3543 \\
+R2 & 0.505 & 0.512 & 0.504 & 0.516 & 0.508 & 0.507 \\
+R2 Adj. & 0.474 & 0.478 & 0.471 & 0.483 & 0.476 & 0.472 \\
+R2 Within & 0.399 & 0.404 & 0.399 & 0.406 & 0.401 & 0.401 \\
+R2 Pseudo & & & & & & \\
+AIC & 7248.7 & 6594.9 & 6862.4 & 6503.7 & 6770.3 & 6386.0 \\
+BIC & 8742.7 & 8059.8 & 8341.7 & 7968.1 & 8249.0 & 7848.9 \\
+Log.Lik. & -3387.339 & -3061.440 & -3194.183 & -3015.858 & -3148.127 & -2956.003 \\
+Std.Errors & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids \\
+FE: clsids & X & X & X & X & X & X \\
 \bottomrule
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic exam score}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1129}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1532}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1613}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1210}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1613}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1210}}
+  >{\centering\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1694}}@{}}
+\caption{Parental migration's effect on children's academic abilities}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Any Parent Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Mother Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Only Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Father Absent
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Both Parents Absent
 \end{minipage} \\
@@
 \endhead
-Migration & -2.65* & -5.87** & -0.20 & -0.92 \\
-& (1.25) & (2.24) & (1.68) & (2.35) \\
-W1 score & -0.01 & -0.01 & 0.00 & -0.01 \\
-& (0.02) & (0.03) & (0.02) & (0.02) \\
-child.age & -1.23† & -1.04 & -1.21† & -0.96 \\
-& (0.65) & (0.68) & (0.70) & (0.70) \\
-child.is.girl & 4.49*** & 4.78*** & 4.54*** & 4.43*** \\
-& (0.92) & (0.95) & (0.92) & (0.97) \\
-child.health.self.rated & 1.05* & 1.12* & 0.92* & 0.85† \\
-& (0.43) & (0.45) & (0.47) & (0.47) \\
-child.has.rural.hukou & 1.08 & 1.50 & 0.80 & 0.98 \\
-& (1.02) & (1.06) & (1.05) & (1.07) \\
-child.number.of.sibling & 1.03† & 0.87 & 1.21* & 0.66 \\
-& (0.58) & (0.59) & (0.60) & (0.62) \\
-child.went.to.preschool & 1.65 & 2.22† & 0.85 & 1.97 \\
-& (1.20) & (1.24) & (1.28) & (1.27) \\
-child.had.skipped.grade & -0.73 & 0.23 & -0.98 & 1.01 \\
-& (4.82) & (4.82) & (5.41) & (5.07) \\
-child.had.repeated.grade & -1.81 & -1.22 & -1.55 & -0.20 \\
-& (1.85) & (1.98) & (1.89) & (1.81) \\
-child.in.boarding.school & -1.14 & -0.19 & -0.72 & -1.19 \\
-& (1.65) & (1.65) & (1.66) & (1.81) \\
-child.educational.aspiration & 1.82*** & 2.08*** & 1.90*** & 1.91*** \\
-& (0.52) & (0.55) & (0.51) & (0.53) \\
-child.is.ethnic.minority & 0.48 & -0.24 & -0.33 & -1.14 \\
-& (2.15) & (2.29) & (2.38) & (2.56) \\
-parent.expectation.on.child & 0.88† & 0.85 & 0.86 & 0.96† \\
-& (0.53) & (0.55) & (0.54) & (0.55) \\
-parent.has.white.collar.job & 0.29 & 0.03 & 0.59 & 0.42 \\
-& (1.19) & (1.23) & (1.21) & (1.25) \\
-parent.educational.level & 1.02† & 1.14* & 1.14* & 1.15* \\
-& (0.53) & (0.53) & (0.54) & (0.56) \\
-home.economic.resource & -0.74 & -0.18 & -0.66 & -0.24 \\
-& (0.81) & (0.88) & (0.87) & (0.87) \\
-home.extracurricular.book & -0.78† & -1.18* & -0.86† & -0.85† \\
-& (0.45) & (0.46) & (0.45) & (0.46) \\
-home.has.internet & -1.41 & -1.65 & -1.33 & -1.37 \\
-& (1.13) & (1.14) & (1.18) & (1.17) \\
-Num.Obs. & 4088 & 3706 & 3703 & 3583 \\
-R2 & 0.573 & 0.590 & 0.578 & 0.588 \\
-R2 Adj. & 0.512 & 0.525 & 0.512 & 0.520 \\
-R2 Within & 0.032 & 0.039 & 0.032 & 0.030 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
+Explanator & -2.85* & -6.35** & -4.13* & -0.65 & -0.59 & 0.01 \\
+& (1.20) & (2.13) & (1.69) & (1.62) & (1.31) & (2.27) \\
+W1 score & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+& (0.02) & (0.03) & (0.03) & (0.03) & (0.02) & (0.02) \\
+age & -1.58* & -1.49* & -1.39* & -1.52* & -1.47* & -1.24† \\
+& (0.61) & (0.63) & (0.63) & (0.64) & (0.63) & (0.66) \\
+ch.girl & 4.34*** & 4.60*** & 4.46*** & 4.39*** & 4.18*** & 4.28*** \\
+& (0.89) & (0.92) & (0.92) & (0.91) & (0.91) & (0.93) \\
+ch.health & 1.08* & 1.09* & 1.06* & 0.96* & 0.91* & 0.89† \\
+& (0.43) & (0.45) & (0.44) & (0.46) & (0.45) & (0.47) \\
+ch.rural & 1.34 & 1.82 & 1.61 & 1.19 & 0.89 & 1.26 \\
+& (1.06) & (1.12) & (1.11) & (1.08) & (1.07) & (1.10) \\
+ch.sibling & 0.63 & 0.48 & 0.33 & 0.72 & 0.59 & 0.25 \\
+& (0.55) & (0.57) & (0.57) & (0.57) & (0.57) & (0.60) \\
+ch.preschool & 1.85 & 2.45* & 2.81* & 1.06 & 1.34 & 2.24† \\
+& (1.19) & (1.21) & (1.20) & (1.27) & (1.23) & (1.25) \\
+ch.skip.grd & 0.69 & 1.23 & 1.81 & 0.47 & 0.96 & 2.30 \\
+& (4.53) & (4.44) & (4.28) & (5.08) & (4.91) & (4.70) \\
+ch.repeat.grd & -1.41 & -0.40 & -0.34 & -0.98 & -0.76 & 0.40 \\
+& (1.80) & (1.94) & (1.84) & (1.86) & (1.72) & (1.78) \\
+ch.boarding & -1.23 & -0.31 & -0.92 & -0.88 & -1.47 & -1.19 \\
+& (1.62) & (1.62) & (1.67) & (1.67) & (1.76) & (1.82) \\
+ch.aspr.univ & 2.69* & 3.13** & 2.85* & 2.71* & 2.39* & 2.53* \\
+& (1.15) & (1.18) & (1.17) & (1.14) & (1.13) & (1.14) \\
+ch.ethn.mnrt & 0.21 & -0.44 & -0.52 & -0.51 & -0.41 & -1.24 \\
+& (2.08) & (2.22) & (2.21) & (2.28) & (2.27) & (2.44) \\
+par.edu.year & 0.44* & 0.49* & 0.46* & 0.54** & 0.50* & 0.53** \\
+& (0.20) & (0.20) & (0.20) & (0.20) & (0.20) & (0.20) \\
+par.expt.univ & 3.06* & 2.88* & 2.92* & 3.16* & 3.23* & 3.06* \\
+& (1.37) & (1.42) & (1.39) & (1.36) & (1.32) & (1.34) \\
+par.ccp & 0.24 & 0.50 & 0.30 & 0.20 & 0.02 & 0.08 \\
+& (1.06) & (1.20) & (1.17) & (1.17) & (1.14) & (1.22) \\
+home.finances & -0.89 & -0.44 & -0.55 & -0.74 & -0.81 & -0.47 \\
+& (0.81) & (0.85) & (0.83) & (0.86) & (0.84) & (0.85) \\
+home.book & -0.72† & -1.09* & -0.92* & -0.76† & -0.60 & -0.79† \\
+& (0.43) & (0.43) & (0.43) & (0.43) & (0.42) & (0.42) \\
+home.internet & -1.54 & -1.65 & -1.46 & -1.50 & -1.37 & -1.37 \\
+& (1.12) & (1.16) & (1.15) & (1.16) & (1.15) & (1.18) \\
+Num.Obs. & 4040 & 3668 & 3796 & 3659 & 3787 & 3543 \\
+R2 & 0.557 & 0.573 & 0.569 & 0.563 & 0.560 & 0.572 \\
+R2 Adj. & 0.530 & 0.544 & 0.540 & 0.533 & 0.530 & 0.541 \\
+R2 Within & 0.028 & 0.034 & 0.029 & 0.027 & 0.025 & 0.025 \\
+R2 Pseudo & & & & & & \\
+AIC & 36952.4 & 33462.4 & 34660.9 & 33354.2 & 34542.9 & 32251.3 \\
+BIC & 38446.5 & 34927.3 & 36140.1 & 34818.6 & 36021.6 & 33714.3 \\
+Log.Lik. & -18239.211 & -16495.201 & -17093.431 & -16441.114 & -17034.432 & -15888.663 \\
+Std.Errors & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids & by: clsids \\
+FE: clsids & X & X & X & X & X & X \\
 \bottomrule
@@
 
-\hypertarget{matching}{%
-\subsection{Matching}\label{matching}}
-
-Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school; their high performance and ambition prompt parents to migrate to support children's schooling.
-Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
-To tackle the selection bias herein, an applicable technique is matching.
-This method makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
-
-Popular choices for matching include coarsened exact matching (CEM) (Waldman, 2022) and nearest-neighbor propensity score matching (PSM) (H.
-Xu \& Xie, 2015).
-As Greifer (2022) introduced, CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units.
-The nearest-neighbor matching examines all the treated units and selects the closest control unit to be paired.
-The eligibility as the ``closest'' can be determined with the differences in propensity score.
-Propensity score denotes the probability of receiving treatment based on the specified covariates.
-Nearest-neighbor PSM does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred (Greifer, 2022).
-King and Nielsen (2019) argued against this matching method as it risks more ``imbalance, model dependence, and bias'' for highly balanced data.
-
-Using the \texttt{MatchIt} package (Ho et al., 2022), I performed matching with all the covariates of the adjusted DID model.
-I first attempted CEM, but it left most units unmatched and resulted in a tiny sample.
-I then made do with the PSM.
-I combined exact matching (based on the student's county of residence) and nearest neighbor PSM (based on the other covariates) following the configuration of Bai et al.
-(2018).
-Exact matching based on county of residence preserves the original geographic distribution.
-The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio was set at one treatment unit with up to three control units.
-The matching produced absolute standardized mean differences below 0.1 for all but a few covariates, suggesting an improved overall balance.
-
-Alike are the results from DID models with matching (DIDM) and those without.
-In the models of cognitive abilities, I obtained negative, statistically significant coefficients on the treatment variables in the any parent migrated household and only father migrated households.
-In the models of academic abilities, the treatment variables' coefficients are negative and statistically significant for the any parent migrated households and only mother migrated households.
-The significance level of any parent migration drops to ten percent.
-In all models, the magnitudes of the statistically significant coefficients are similar.
-I present the unadjusted DIDM models below and the adjusted DIDM models in the appendix.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -0.09** & -0.05 & -0.13* & -0.05 \\
-& (0.03) & (0.06) & (0.06) & (0.11) \\
-W1 score & -0.61*** & -0.65*** & -0.60*** & -0.63*** \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.528 & 0.627 & 0.638 & 0.646 \\
-R2 Adj. & 0.375 & 0.313 & 0.320 & -0.312 \\
-R2 Within & 0.363 & 0.407 & 0.372 & 0.351 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1287}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2079}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2178}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2277}}@{}}
-\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Explanator & -2.65† & -5.34* & -2.42 & -2.45 \\
-& (1.47) & (2.67) & (2.56) & (3.96) \\
-W1 score & 0.03 & 0.08† & 0.05 & 0.03 \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.590 & 0.682 & 0.637 & 0.706 \\
-R2 Adj. & 0.457 & 0.413 & 0.319 & -0.087 \\
-R2 Within & 0.006 & 0.026 & 0.008 & 0.005 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
 \newpage
@@
 
-This thesis proposes a model to infer causality between parents' migration and their stay-behind children's educational performance in the short run.
-I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as measured by academic exams and standardized cognitive tests.
-I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that father-only migration is negatively associated with children's cognitive abilities, while mother-only migration is negatively associated with children's academic abilities.
-In all scenarios, the educational performance of newly left-behind children only decreases slightly compared to that of non-left-behind peers.
-
-My research has limitations in sampling due to data constraint.
-Regarding sample size, the treatment group for the both-parents migration is small (n = 131), making the statistical power low.
-Regarding identification, I could only identify parental migration through such a condition: parental absence from a household without parental divorce or death.
-This is because the CEPS questionnaire asked if parents were living in the household, but did not ask why parents were absent.
-If some parents were jailed or hospitalized, their absence would be wrongly attributed to migration.
-Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-As I previously wrote, some parents out-migrated at an earlier date, returned before the baseline survey, and migrated away again during the survey period.
-Their children might better cope with parental absence during the survey period, yet they would be mistaken as the newly left-behind .
-These limitations may bias the estimation.
-
-Limitations also arise from unaccounted endogeneity and exogeneity.
-As Chen et al.
-(2009) stated in their research on left-behind children, endogenous factors may create selection bias.
-When migration opportunities arise, some parents may believe that leaving children behind would hamper children's education, thereby giving up the opportunity.
-Some other parents may believe that their children's schooling would not suffer from parental absence, thereby embarking on migration.
-Parental beliefs of this sort are unavailable in CEPS data.
-Exogenous factors may create omitted variable bias.
-Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades (Chen et al., 2009).
-I could not account for such shocks as CEPS data does not include detailed geographic information.
-
-From my research, we can find new directions for scholarly inquiry.
-First, when the CEPS team releases the next round of data, researchers can capitalize a the three-wave panel dataset to build multi-period DID models.
-This would facilitate examination of the parallel trend assumption.
-Second, researchers can try novel methods.
-Machine learning, for example, can estimate the heterogeneous effects across subgroups (R.
-Liu, 2021).
-Third, researchers can go beyond outbound migration to study return migration of parents (Liang \& Li, 2021).
-Only a few publications have explored return migrants and their stay-behind children in the Chinese context (Démurger \& Xu, 2015; Z.
-Liu et al., 2018).
-
-Let us consider the policy implications for China.
-The government has enacted reforms in the multilevel citizenship scheme.
-By 2022, small- and medium-sized cities have liberalized the application for local, urban hukou.
-However, the most popular migration destinations are metropolises like Beijing and Shanghai.
-These mega-cities still restrict migrant workers' local citizenship rights (X.
-Wang, 2020).
-The hukou scheme shall not remain as it is, despite the small reduction of newly left behind children's schooling performance.
-The slight reduction is only the short-term consequence.
-Longer duration of parental migration may hamper educational performance to a greater extent (Liang \& Sun, 2020; Meng \& Yamauchi, 2017).
-Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020).
-Policymakers should accelerate the reforms on the multilevel citizenship scheme, opening more doors for parents to migrate together with their children.
-Schools could dedicate more advisory and counseling support to children who stay behind.
-``Social workers could test models for training paraprofessionals within different communities'' to support left-behind children (M.
-Wang et al., 2020, p.
-1436).
-
-\newpage
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1.pdf}
-\caption{\label{fig:v-plot-cog}Changes in standardized cognitive test score for new left-behind students and non-left-behind students}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1.pdf}
-\caption{\label{fig:v-plot-ttl}Changes in academic exam score for new left-behind students and non-left-behind students}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-cog-1-1.pdf}
-\caption{\label{fig:v-plot-cog-1}Changes in standardized cognitive test score by household migration arrangement}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/v-plot-ttl-1-1.pdf}
-\caption{\label{fig:v-plot-ttl-1}Changes in academic exam score by household migration arrangement}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-any-1.pdf}
-\caption{\label{fig:cobal-any}Covariate balance before and after matching by any parent migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-mo-1.pdf}
-\caption{\label{fig:cobal-mo}Covariate balance before and after matching by mother-only migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-fa-1.pdf}
-\caption{\label{fig:cobal-fa}Covariate balance before and after matching by father-only migration}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{MScThesisText_files/figure-latex/cobal-both-1.pdf}
-\caption{\label{fig:cobal-both}Covariate balance before and after matching by both parents migration}
-\end{figure}
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic abilities, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Explanator & -0.09** & -0.04 & -0.15* & -0.08 \\
-& (0.03) & (0.06) & (0.06) & (0.11) \\
-W1 score & -0.67*** & -0.67*** & -0.67*** & -0.69*** \\
-& (0.03) & (0.04) & (0.04) & (0.06) \\
-child.age & -0.08* & -0.02 & -0.03 & -0.15 \\
-& (0.03) & (0.05) & (0.04) & (0.10) \\
-child.is.girl & 0.02 & 0.01 & 0.05 & -0.06 \\
-& (0.03) & (0.05) & (0.06) & (0.10) \\
-child.health.self.rated & 0.00 & -0.03 & -0.02 & -0.07 \\
-& (0.02) & (0.03) & (0.03) & (0.06) \\
-child.has.rural.hukou & 0.01 & -0.07 & 0.06 & 0.04 \\
-& (0.04) & (0.07) & (0.07) & (0.12) \\
-child.number.of.sibling & -0.07* & -0.09* & -0.05 & -0.10 \\
-& (0.03) & (0.04) & (0.04) & (0.07) \\
-child.went.to.preschool & 0.04 & 0.08 & 0.03 & 0.30* \\
-& (0.04) & (0.08) & (0.06) & (0.12) \\
-child.had.skipped.grade & -0.08 & -0.13 & -0.37† & 0.34 \\
-& (0.16) & (0.24) & (0.19) & (0.45) \\
-child.had.repeated.grade & -0.08 & -0.26* & -0.02 & 0.05 \\
-& (0.06) & (0.11) & (0.11) & (0.16) \\
-child.in.boarding.school & 0.09 & 0.15 & -0.10 & -0.02 \\
-& (0.07) & (0.12) & (0.11) & (0.20) \\
-child.educational.aspiration & 0.07*** & 0.03 & 0.10** & 0.10† \\
-& (0.02) & (0.03) & (0.03) & (0.05) \\
-child.is.ethnic.minority & -0.01 & 0.01 & -0.20 & 0.39 \\
-& (0.09) & (0.10) & (0.23) & (0.44) \\
-parent.expectation.on.child & 0.07** & 0.08† & 0.06† & 0.01 \\
-& (0.03) & (0.05) & (0.03) & (0.06) \\
-parent.has.white.collar.job & 0.02 & -0.10† & 0.03 & -0.15 \\
-& (0.05) & (0.05) & (0.08) & (0.16) \\
-parent.educational.level & 0.01 & 0.03 & 0.00 & -0.08 \\
-& (0.02) & (0.03) & (0.03) & (0.06) \\
-home.economic.resource & -0.05 & 0.00 & 0.02 & 0.05 \\
-& (0.03) & (0.05) & (0.05) & (0.08) \\
-home.extracurricular.book & 0.01 & 0.01 & 0.02 & 0.01 \\
-& (0.02) & (0.03) & (0.03) & (0.05) \\
-home.has.internet & -0.05 & -0.07 & -0.06 & 0.05 \\
-& (0.04) & (0.08) & (0.07) & (0.11) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.562 & 0.653 & 0.672 & 0.691 \\
-R2 Adj. & 0.413 & 0.337 & 0.361 & -0.318 \\
-R2 Within & 0.409 & 0.447 & 0.431 & 0.435 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
-\newpage
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2479}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1880}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1966}}@{}}
-\caption{Parental migration's effect on children's academic exam scores, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father Migrated
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents Migrated
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -2.91† & -5.90* & -2.68 & -2.94 \\
-& (1.48) & (2.64) & (2.56) & (4.21) \\
-W1 score & -0.01 & 0.01 & 0.00 & -0.03 \\
-& (0.03) & (0.04) & (0.05) & (0.06) \\
-child.age & -0.61 & 1.45 & 2.59 & -2.15 \\
-& (1.21) & (2.00) & (1.99) & (3.48) \\
-child.is.girl & 4.51** & 4.40† & 6.58** & 3.76 \\
-& (1.43) & (2.57) & (2.41) & (4.21) \\
-child.health.self.rated & 0.71 & 2.30 & 1.13 & 2.38 \\
-& (0.69) & (1.42) & (1.15) & (2.27) \\
-child.has.rural.hukou & 0.85 & -0.13 & -1.10 & -2.75 \\
-& (1.70) & (3.10) & (2.97) & (4.45) \\
-child.number.of.sibling & 1.20 & 1.92† & 1.00 & -2.50 \\
-& (1.06) & (1.06) & (1.61) & (2.69) \\
-child.went.to.preschool & 1.75 & -0.30 & -2.26 & 6.39 \\
-& (1.76) & (2.47) & (2.57) & (5.13) \\
-child.had.skipped.grade & 2.29 & -9.76 & 3.12 & 32.64 \\
-& (6.62) & (11.90) & (12.03) & (29.40) \\
-child.had.repeated.grade & -6.07† & -13.55† & -13.33** & -0.09 \\
-& (3.18) & (7.61) & (4.86) & (5.92) \\
-child.in.boarding.school & -0.64 & -0.65 & -3.42 & -3.10 \\
-& (3.53) & (5.38) & (4.25) & (8.17) \\
-child.educational.aspiration & 1.48† & 1.63 & 0.37 & 0.44 \\
-& (0.86) & (1.06) & (1.20) & (1.92) \\
-child.is.ethnic.minority & 3.81 & 4.84 & 2.79 & -2.54 \\
-& (4.31) & (4.68) & (6.53) & (7.64) \\
-parent.expectation.on.child & 0.19 & 1.71 & 1.41 & 3.97 \\
-& (0.83) & (1.49) & (1.35) & (2.49) \\
-parent.has.white.collar.job & -0.85 & 0.54 & 2.13 & -1.42 \\
-& (1.82) & (2.56) & (2.87) & (6.14) \\
-parent.educational.level & 1.30 & 2.30** & 1.91 & -2.63 \\
-& (0.97) & (0.85) & (1.41) & (2.54) \\
-home.economic.resource & -0.23 & -1.90 & -0.51 & -0.54 \\
-& (1.23) & (2.24) & (1.81) & (4.05) \\
-home.extracurricular.book & -0.66 & -0.66 & -1.59 & 0.08 \\
-& (0.71) & (1.24) & (1.01) & (1.93) \\
-home.has.internet & -2.89 & -1.61 & 0.08 & 3.67 \\
-& (1.81) & (2.87) & (3.26) & (4.98) \\
-Num.Obs. & 1958 & 913 & 897 & 475 \\
-R2 & 0.603 & 0.702 & 0.660 & 0.731 \\
-R2 Adj. & 0.468 & 0.431 & 0.337 & -0.150 \\
-R2 Within & 0.037 & 0.088 & 0.070 & 0.087 \\
-FE: clsids & X & X & X & X \\
-FE: w2clsids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 nearest neighbor propensity score matching with replacement; exact matching by county
-
 \newpage
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-akezhuoli2022}{}}%
-Akezhuoli, H., Lu, J., Zhao, G., Xu, J., Wang, M., Wang, F., Li, L., \& Zhou, X.
-(2022).
-Mother's and father's migrating in china: Differing relations to mental health and risk behaviors among left-behind children.
-\emph{Frontiers in Public Health}, \emph{10}.
-\url{https://www.frontiersin.org/article/10.3389/fpubh.2022.894741}
-
 \leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
+
 \leavevmode\vadjust pre{\hypertarget{ref-bai2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-berge2022}{}}%
-Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-berguxe92018}{}}%
+Bergé, L. (2018). \emph{Efficient estimation of maximum likelihood models with multiple fixed-effects: the R package FENmlm}. \url{https://ideas.repec.org/p/luc/wpaper/18-13.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-botezat2020}{}}%
-Botezat, A., \& Pfeiffer, F.
-(2020).
-The impact of parental labour migration on left{-}behind children's educational and psychosocial outcomes: Evidence from Romania.
-\emph{Population, Space and Place}, \emph{26}(2).
-\url{https://doi.org/10.1002/psp.2277}
-
 \leavevmode\vadjust pre{\hypertarget{ref-bourdieu2002}{}}%
 Bourdieu, P. (2002). \emph{The Forms of Capital} (N. W. Biggart, Ed.; pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
-
-\leavevmode\vadjust pre{\hypertarget{ref-debrauw2019}{}}%
-Brauw, A.
-de.
-(2019).
-Migration Out of Rural Areas and Implications for Rural Livelihoods.
-\emph{Annual Review of Resource Economics}, \emph{11}(1), 461--481.
-\url{https://doi.org/10.1146/annurev-resource-100518-093906}
-
-\leavevmode\vadjust pre{\hypertarget{ref-debrauw2017}{}}%
-Brauw, A.
-de, \& Giles, J.
-(2017).
-Migrant Opportunity and the Educational Attainment of Youth in Rural China.
-\emph{Journal of Human Resources}, \emph{52}(1), 272--311.
-\url{https://doi.org/10.3368/jhr.52.1.0813-5900R}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chan2019}{}}%
-Chan, J. (2019). State and labor in China, 1978{\textendash}2018. \emph{Journal of Labor and Society}, \emph{22}(2), 461--475. \url{https://doi.org/10.1111/wusa.12408}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2009}{}}%
-Chen, X., Huang, Q., Rozelle, S., Shi, Y., \& Zhang, L.
-(2009).
-Effect of Migration on Children's Educational Performance in Rural China.
-\emph{Comparative Economic Studies}, \emph{51}(3), 323--343.
-\url{https://doi.org/10.1057/ces.2008.44}
-
 \leavevmode\vadjust pre{\hypertarget{ref-chen2019}{}}%
@@
 Cunningham, S. (2021). \emph{Causal inference: The mixtape}. Yale University Press. \url{https://mixtape.scunning.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-duxe9murger2015}{}}%
-Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in china. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-duckett2020}{}}%
-Duckett, J. (2020). Neoliberalism, Authoritarian Politics and Social Policy in China. \emph{Development and Change}, \emph{51}(2), 523--539. \url{https://doi.org/10.1111/dech.12568}
-
 \leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-greifer2022}{}}%
-Greifer, N. (2022). \emph{Matching methods}. \url{https://kosukeimai.github.io/MatchIt/articles/matching-methods.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gu2022}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-gu2021}{}}%
 Gu, X.
-(2022).
+(2021).
 {`}Save the children!{'}: Governing left-behind children through family in China{'}s Great Migration.
-\emph{Current Sociology}, \emph{70}(4), 513--538.
+\emph{Current Sociology}, 0011392120985874.
 \url{https://doi.org/10.1177/0011392120985874}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ho2022}{}}%
-Ho, D., Imai, K., King, G., Stuart, E., Whitworth, A., \& Greifer, N.
-(2022).
-\emph{MatchIt: Nonparametric preprocessing for parametric causal inference}.
-\url{https://CRAN.R-project.org/package=MatchIt}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-huntington-klein2022}{}}%
-Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality \textbar{} The Effect}. CRC Press. \url{https://theeffectbook.net/index.html}
+\leavevmode\vadjust pre{\hypertarget{ref-huntington-klein}{}}%
+Huntington-Klein, N. (n.d.). \emph{The effect: An introduction to research design and causality \textbar{} the effect}. \url{https://theeffectbook.net/index.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-king2019}{}}%
-King, G., \& Nielsen, R. (2019). Why Propensity Scores Should Not Be Used for Matching. \emph{Political Analysis}, \emph{27}(4), 435--454. \url{https://doi.org/10.1017/pan.2019.11}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liang2021}{}}%
-Liang, Z., \& Li, W.
-(2021).
-Migration and children in China: a review and future research agenda.
-\emph{Chinese Sociological Review}, \emph{53}(3), 312--331.
-\url{https://doi.org/10.1080/21620555.2021.1908823}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liang2020}{}}%
-Liang, Z., \& Sun, F.
-(2020).
-The lasting impact of parental migration on children's education and health outcomes: The case of china.
-\emph{Demographic Research}, \emph{S28}(9), 217--244.
-\url{https://doi.org/10.4054/DemRes.2020.43.9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liu2021a}{}}%
-Liu, R.
-(2021).
-Leveraging machine learning methods to estimate heterogeneous effects: Father absence in china as an example.
-\emph{Chinese Sociological Review}, \emph{0}(0), 1--29.
-\url{https://doi.org/10.1080/21620555.2021.1948828}
+\leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
+Li, L., Wang, L., \& Nie, J.
+(2017).
+Effect of Parental Migration on the Academic Performance of Left-behind Middle School Students in Rural China.
+\emph{China \& World Economy}, \emph{25}(2), 45--59.
+\url{https://doi.org/10.1111/cwe.12193}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-liu2018}{}}%
-Liu, Z., Yu, L., \& Zheng, X.
-(2018).
-No longer left-behind: The impact of return migrant parents on children's performance.
-\emph{China Economic Review}, \emph{49}, 184--196.
-\url{https://doi.org/10.1016/j.chieco.2017.06.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-meng2017}{}}%
-Meng, X., \& Yamauchi, C.
-(2017).
-Children of migrants: The cumulative impact of parental migration on children{'}s education and health outcomes in china.
-\emph{Demography}, \emph{54}(5), 1677--1714.
-\url{https://doi.org/10.1007/s13524-017-0613-z}
-
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nguyen2016}{}}%
-Nguyen, C.
-V.
-(2016).
-Does parental migration really benefit left-behind children?
-Comparative evidence from Ethiopia, India, Peru and Vietnam.
-\emph{Social Science \& Medicine}, \emph{153}, 230--239.
-\url{https://doi.org/10.1016/j.socscimed.2016.02.021}
-
 \leavevmode\vadjust pre{\hypertarget{ref-nsrc}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-oecd2016}{}}%
-OECD. (2016). \emph{Education in china: A snapshot}. \url{https://www.oecd.org/china/Education-in-China-a-snapshot.pdf}
-
-\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021a}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021}{}}%
 Parliamentary Assembly.
@@
 \url{https://doi.org/10.26758/8.1.3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vortherms2021}{}}%
-Vortherms, S. A. (2021). \emph{Hukou as a case of multi-level citizenship} (Z. Guo, Ed.; pp. 132--142). Routledge. \href{https://doi.org/10.4324/9781003225843-12}{doi.org/10.4324/9781003225843-12}
-
-\leavevmode\vadjust pre{\hypertarget{ref-waldman2022}{}}%
-Waldman, K.
-E.
-(2022).
-Transnational Social Stratification?
-Legal Status of Immigrant Parents and the Educational Achievements of Mexican Children.
-\emph{International Migration Review}, 01979183221084329.
-\url{https://doi.org/10.1177/01979183221084329}
-
 \leavevmode\vadjust pre{\hypertarget{ref-wang2019}{}}%
@@
 \url{https://doi.org/10.1108/CAER-09-2018-0194}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2020a}{}}%
-Wang, M., Victor, B.
-G., Hong, J.
-S., Wu, S., Huang, J., Luan, H., \& Perron, B.
-E.
-(2020).
-A Scoping Review of Interventions to Promote Health and Well-Being of Left-behind Children in Mainland China.
-\emph{The British Journal of Social Work}, \emph{50}(5), 1419--1439.
-\url{https://doi.org/10.1093/bjsw/bcz116}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
-Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey {[}in chinese{]}}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
-Wang, X.
-(2020).
-Permits, Points, and Permanent Household Registration: Recalibrating Hukou Policy under {``}Top-Level Design{''}.
-\emph{Journal of Current Chinese Affairs}, \emph{49}(3), 269--290.
-\url{https://doi.org/10.1177/1868102619894739}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wen2019}{}}%
-Wen, Y., \& Xie, J.
-(2019).
-Missing families and villages: The care deficit faced by rural left-behind children in china and its implications.
-\emph{International Journal of Care and Caring}, \emph{3}(2), 247--262.
-\url{https://doi.org/10.1332/239788218X15421003245041}
-
-\leavevmode\vadjust pre{\hypertarget{ref-xu2015}{}}%
-Xu, H., \& Xie, Y.
-(2015).
-The Causal Effects of Rural-to-Urban Migration on Children{'}s Well-being in China.
-\emph{European Sociological Review}, \emph{31}(4), 502--519.
-\url{https://doi.org/10.1093/esr/jcv009}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-yang2008}{}}%
-Yang, D.
-(2008).
-International Migration, Remittances and Household Investment: Evidence from Philippine Migrants{'} Exchange Rate Shocks.
-\emph{The Economic Journal}, \emph{118}(528), 591--630.
-\url{https://doi.org/10.1111/j.1468-0297.2008.02134.x}
-
 \leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhang2018}{}}%
-Zhang, C.
-(2018).
-Governing neoliberal authoritarian citizenship: Theorizing hukou and the changing mobility regime in china.
-\emph{Citizenship Studies}, \emph{22}(8), 855--881.
-\url{https://doi.org/10.1080/13621025.2018.1531824}
+\leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
+Zhan, Y.
+(2020).
+The moralization of philanthropy in China: NGOs, voluntarism, and the reconfiguration of social responsibility.
+\emph{China Information}, \emph{34}(1), 68--87.
+\url{https://doi.org/10.1177/0920203X19879593}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhou2014}{}}%
+Zhou, M., Murphy, R., \& Tao, R.
+(2014).
+Effects of Parents' Migration on the Education of Children Left Behind in Rural China.
+\emph{Population and Development Review}, \emph{40}(2), 273--292.
+\url{https://doi.org/10.1111/j.1728-4457.2014.00673.x}
 

### 2022-07-07 data/Gu-thesis-script.Rmd

@@
 
-```{r Load packages}
+Load packages
+```{r}
 library(tidyverse) 
@@
 library(modelsummary)
-library(MatchIt)
-library(vtable)
-library(labelled)
-library(cobalt) 
-library(DescTools)
-options(modelsummary_get="broom") 
 ```
@@
 ## Data cleaning
-```{r Read data}
+Read CEPS data
+```{r}
 d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
@@
 d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
+#d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
+#d_sch2 <- read_dta('cepsw2principalCN.dta')
+```
+
+Remove wave 1's observations of grade 9; they were not followed up in wave 2
+```{r}
+d_stu1 <- d_stu1 %>% 
+  subset(grade9==0) %>% 
+  select(!c(frame, subsample, sweight, grade9))
+d_stu2 <- d_stu2 %>% 
+  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
+d_par1 <- d_par1 %>% 
+  subset(grade9==0) %>% 
+  select(!c(frame, subsample, grade9))
+```
+
+Assemble a panel dataset in wide format
+```{r}
+dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
+#%>% left_join(d_sch1, by=c('schids', 'ctyids', 'fall'))
+dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
+d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
@@
 ```{r}
-d_stu1 <- d_stu1 |> 
-  subset(grade9==0) |> 
-  select(!c(frame, subsample, sweight, grade9))
-d_stu2 <- d_stu2 |> 
-  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
-d_par1 <- d_par1 |> 
-  subset(grade9==0) |> 
-  select(!c(frame, subsample, grade9)) #Remove wave 1's observations of grade 9; they were not followed up in wave 2
-```
-
-```{r Merge data}
-d <- d_stu1 |> 
-  left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) |>
-  left_join(d_stu2, by=c('ids', 'schids', 'clsids', 'ctyids')) |>
-  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) |> 
-  remove_labels() #Assemble a panel dataset in wide format
-```
-
-```{r Sample}
-d_cl <- d |> 
-  filter(w2a0801==1) |> #keep parents who are married (and alive)
-  filter(be1201==1 & be1202==1) |> #keep households with both parents staying at baseline
-  filter(stmigrant==1) #keep local children 
-```
-
-## Variables 
-```{r Exam grade conversion}
-d_cl <- d_cl |> mutate(
+d <- d %>% mutate(
+  age = 2013 - a02a, #student's age at baseline
   w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
@@
 )
-```
-
-```{r Outlier detection}
-outlier <- d_cl |> filter(
-  w1chn_100<0 | w1chn_100>100 | w1mat_100<0 | w1mat_100>100 | w1eng_100<0 | w1eng_100>100 |
-  w2chn_100<0 | w2chn_100>100 | w2mat_100<0 | w2mat_100>100 | w2eng_100<0 | w2eng_100>100)
-```
-
-```{r Trim outlying values}
-d_cl <- d_cl |> mutate(
-  w1chn_100_trim = Winsorize(w1chn_100, minval = 0, maxval = 100),
-  w2chn_100_trim = Winsorize(w2chn_100, minval = 0, maxval = 100),
-  w1mat_100_trim = Winsorize(w1mat_100, minval = 0, maxval = 100),
-  w2mat_100_trim = Winsorize(w2mat_100, minval = 0, maxval = 100),
-  w1eng_100_trim = Winsorize(w1eng_100, minval = 0, maxval = 100),
-  w2eng_100_trim = Winsorize(w2eng_100, minval = 0, maxval = 100)
+d <- d %>% mutate(
+  w1ttl = tr_chn + tr_mat + tr_eng,
+  w2ttl = w2chn + w2mat + w2eng,
+  w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
+  w2ttl_100 = w2chn_100 + w2mat_100 + w2eng_100,
+  ttl_dif = w2ttl_100 - w1ttl_100,
+  cog_dif = w2cog3pl - cog3pl
   )
@@
 
-```{r Outcome variables}
-d_cl <- d_cl |> mutate(
-  w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
-  w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
-  w1avg_100 = w1ttl_100/3,
-  w2avg_100 = w2ttl_100/3,
-  w1cog_100 = stcog*100/20,
-  w2cog_100 = w2cogscore*100/35,
-  avg_dif = w2avg_100 - w1avg_100,
-  cog_dif = w2cog_100 - w1cog_100,
-  ) |>
-  drop_na(avg_dif, cog_dif)
+```{r}
+d1 <- d %>% filter(w2ttl_100<=300 & w1ttl_100<=300) %>% #remove outliers with total scores greater than 300
+  drop_na(cog_dif, ttl_dif, age)
 ```
 
-```{r Control variables}
-d_cl <- d_cl |> mutate(
-         child.age = 2013 - a02a, 
-         child.is.girl = if_else(a01 == 2, 1, 0), 
-         child.has.rural.hukou = sthktype, 
-         child.in.boarding.school = stbrd, 
-         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
-         child.health = a17, 
-         child.had.skipped.grade = if_else(c03 == 0, 0, 1), 
-         child.had.repeated.grade = if_else(c04 == 0, 0, 1), 
-         child.went.to.preschool = if_else(c01 == 1, 1, 0), 
-         child.number.of.sibling = if_else(stonly == 1, 0, stsib),
-         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
-         home.economic.resource = steco_5c, 
-         home.has.internet = if_else(b13 == 2, 1, 0), 
-         home.extracurricular.book = b12 
-) |> drop_na(
-child.age, child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
-parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
+within-class z score
+```{}
+d1 <- d1 %>% group_by(schids) %>%
+  mutate(
+    w1ttl_z = as.numeric(scale(w1ttl)),
+    w2ttl_z = as.numeric(scale(w2ttl))
+  ) %>% ungroup()
 ```
 
-```{r Mother education}
-d_cl <- d_cl |> mutate(mother.education.level = NA)
-d_cl$mother.education.level[d_cl$stmedu == 1|d_cl$stmedu == 2] <- 0 
-d_cl$mother.education.level[d_cl$stmedu == 3] <- 1
-d_cl$mother.education.level[d_cl$stmedu == 4|d_cl$stmedu == 5|d_cl$stmedu == 6] <- 2
-d_cl$mother.education.level[d_cl$stmedu == 7] <- 3
-d_cl$mother.education.level[d_cl$stmedu == 8] <- 4
-d_cl$mother.education.level[d_cl$stmedu == 9] <- 5
+```{}
+d1 <- d1 %>% group_by(schids) %>%
+  mutate(
+    w1ttl_std = rescale(w1ttl),
+    w2ttl_std = rescale(w2ttl)
+    ) %>% ungroup()
 ```
 
-```{r Father education}
-d_cl <- d_cl |> mutate(father.education.level = NA)
-d_cl$father.education.level[d_cl$stfedu == 1|d_cl$stfedu == 2] <- 0
-d_cl$father.education.level[d_cl$stfedu == 3] <- 1
-d_cl$father.education.level[d_cl$stfedu == 4|d_cl$stfedu == 5|d_cl$stfedu == 6] <- 2
-d_cl$father.education.level[d_cl$stfedu == 7] <- 3
-d_cl$father.education.level[d_cl$stfedu == 8] <- 4
-d_cl$father.education.level[d_cl$stfedu == 9] <- 5
+Detect outliers
+```{}
+d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
+d_outlier1 <- d_outlier %>% select(clsids, schids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
+d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
 ```
 
-```{r Parent expectation}
-d_cl <- d_cl |> mutate(parent.expectation = NA)
-d_cl$parent.expectation[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
-d_cl$parent.expectation[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
-d_cl$parent.expectation[d_cl$ba18 == 6] <- 3
-d_cl$parent.expectation[d_cl$ba18 == 7] <- 4
-d_cl$parent.expectation[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
+Sample
+```{r}
+d_cl <- d1 %>% 
+  filter(w2a0801==1) %>% #keep parents who are married (and alive)
+  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
+  filter(stmigrant==1) #keep local children 
 ```
 
-```{r Child aspiration}
-d_cl <- d_cl |> mutate(child.education.aspiration = NA)
-d_cl$child.education.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
-d_cl$child.education.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
-d_cl$child.education.aspiration[d_cl$c22 == 6] <- 3
-d_cl$child.education.aspiration[d_cl$c22 == 7] <- 4
-d_cl$child.education.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
+## Variables
+
+Control variables
+```{r}
+d_cl <- d_cl %>% mutate(
+         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
+         ch.rural = sthktype, #student holds rural (agricultural) hukou
+         ch.boarding = stbrd, #student is boarding at school
+         ch.ethn.mnrt = if_else(a03 != 1, 1, 0), #student is ethnic minority
+         ch.health = a17, #student's self-rated health
+         ch.skip.grd = if_else(c03 == 0, 0, 1), #student had skipped grade
+         ch.repeat.grd = if_else(c04 == 0, 0, 1), #student had repeated grade
+         ch.aspr.univ = if_else(c22 <= 6 | c22 == 10, 0, 1), #student aspires to finish university bachelor's degree or above
+         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
+         ch.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
+         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
+         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
+         par.expt.univ = if_else(ba18 <= 6, 0, 1), #parent expects child to finish university bachelor's degree or above
+         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
+         par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
+         home.finances = steco_5c, #self-rated household financial situation
+         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
+         home.book = b12 #Amount of book at home, student self-rated 
+) %>% drop_na(
+ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.mnrt, ch.health, ch.skip.grd, ch.repeat.grd, ch.preschool, ch.aspr.univ, par.edu, par.ccp, par.expt.univ, home.internet, home.book, home.finances)
 ```
@@
 ```{r}
-d_cl <- d_cl |>  drop_na(
-  mother.education.level, 
-  father.education.level,
-  parent.expectation, 
-  child.education.aspiration)
+d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
+d_cl <- d_cl %>% mutate(ch.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
+  drop_na(ch.sibling)
+```
+
+Best-educated parent's years of education
+```{r}
+d_cl <- d_cl %>% mutate(par.edu.year = NA)
+d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
+d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
+d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
+d_cl$par.edu.year[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
+d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
+d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
+d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
+```
+
+```
+d_cl <- d_cl %>% mutate(fa.edu.year = NA)
+d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
+d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
+d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
+d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
+d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
+d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
+d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
+```
+
+```
+d_cl <- d_cl %>% mutate(mo.edu.year = NA)
+d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
+d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
+d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
+d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
+d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
+d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
+d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
 ```
@@
 ```{r}
-d_cl <- d_cl |> mutate(
-  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became Migrated from household between baseline and endline survey
+d_cl <- d_cl %>% mutate(
+  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
   migr_fa_only = NA,
-  #migr_fa = NA,
+  migr_fa = NA,
   migr_mo_only = NA,
-  #migr_mo = NA,
+  migr_mo = NA,
   migr_both = NA
-  ) |> drop_na(migr)
+  ) %>% drop_na(migr)
 ```
@@
 Only mother migrated
-```{r Any parent migrated}
-d_cl <- d_cl |> mutate(
-  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
-  migr_fa_only = NA,
-  migr_mo_only = NA,
-  migr_both = NA
-  ) |> drop_na(migr)
-```
-
-```{r Only mother migrated}
+```{r}
 d_cl$migr_mo_only[d_cl$migr == 0] <- 0
@@
 
-```{r Only father migrated}
+Mother migrated
+```{r}
+d_cl$migr_mo[d_cl$migr == 0] <- 0
+d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
+```
+
+Only father migrated
+```{r}
 d_cl$migr_fa_only[d_cl$migr == 0] <- 0
@@
 
-```{r Both parents migrated}
+Father migrated
+```{r}
+d_cl$migr_fa[d_cl$migr == 0] <- 0
+d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
+```
+
+Both parents migrated
+```{r}
 d_cl$migr_both[d_cl$migr == 0] <- 0
@@
 
+```{r}
+df <- d_cl %>% select(
+  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
+  cog3pl, w1ttl_100, cog_dif, ttl_dif,
+  ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.mnrt, ch.health, ch.skip.grd, ch.repeat.grd, ch.preschool, ch.aspr.univ, 
+  par.edu, par.ccp, par.expt.univ, 
+  home.internet, home.book, home.finances
+)
+```
+
 ## Descriptive statistics
-```{r Cleaned data}
-df <- d_cl |>
-  select(
-  migr, migr_mo_only, migr_fa_only, migr_both, schids, ctyids,
-  w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
-  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
-  child.health, child.education.aspiration, 
-  mother.education.level, father.education.level, parent.expectation, 
-  home.extracurricular.book, home.economic.resource) 
+```{r}
+d_migr <- d_cl %>% select(
+  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both) %>%
+  mutate_if(is.numeric, as.factor)
+datasummary_skim(
+  d_migr,
+  type='categorical')
 ```
@@
 ```{r}
-d_migr <- df |>
-  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) |>
-  select(!migr)
+d_covar <- d_cl %>% select(
+  ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.mnrt, ch.health, ch.skip.grd, ch.repeat.grd, ch.preschool, ch.aspr.univ, 
+  par.edu.year, par.ccp, par.expt.univ, 
+  home.internet, home.book, home.finances) %>%
+  mutate_if(is.numeric, as.factor)
+datasummary_skim(
+  d_covar,
+  type ='categorical',
+  output = "table.md")
+
 ```
 
-```{r Data for treatment variable summary}
-d_idpvar <- df |> 
-  select(migr:migr_both) |>
-  mutate(`Parental Migration` = if_else(migr==1, 'Yes', 'No')) |>
-  mutate(`Parental Migration Type` = NA) 
-d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents at Home'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
-d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
+t-test
+```{r}
+t.test(cog_dif ~ migr, data = d_cl)
+t.test(ttl_dif ~ migr, data = d_cl)
 ```
 
-```{r Treatment variable summary}
-tab_idpvar <- st(
-  data = d_idpvar,
-  out = 'return'
-)
-tab_idpvar[tab_idpvar == 4062] <- ''
-tab_idpvar
+## Descriptive statistics
+
+## DID unrestricted
+Regressing on cognitive test score (standardized)
+```{r}
+did_unres_cog <- feols(cog_dif ~ migr + cog3pl | clsids, data = d_cl) 
+did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | clsids, data = d_cl) 
+did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | clsids, data = d_cl) 
+did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | clsids, data = d_cl) 
+did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | clsids, data = d_cl) 
+did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | clsids, data = d_cl)
 ```
 
-```{r Data for outcome variable summary}
-d_dpvar <- d_migr |>
-  select(`Parental Migration`, cog_dif, w1cog_100, w2cog_100, avg_dif, w1avg_100, w2avg_100) |>
-  set_variable_labels(
-    w1cog_100 ='Wave 1 score',
-    w2cog_100 = 'Wave 2 score',
-    w1avg_100 ='Wave 1 score',
-    w2avg_100 = 'Wave 2 score',
-    cog_dif = 'Cognitive test score difference',
-    avg_dif = 'Academic exam score difference'
-  )
+Results
+```{r}
+models_unres_cog <- list(
+'Any Parent Absent' = did_unres_cog,
+'Only Mother Absent' = did_unres_cog_m_only,
+'Mother Absent' = did_unres_cog_m,
+'Only Father Absent' = did_unres_cog_f_only,
+'Father Absent' = did_unres_cog_f,
+'Both Parents Absent' = did_unres_cog_both) 
+table_unres_cog <- models_unres_cog %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+  fmt = 2,
+  title = 'Parental migration’s effect on children’s cognitive abilities',
+  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"), output = 'markdown')
+table_unres_cog
 ```
 
-```{r Outcome variable summary}
-tab_dpvar <- 
-  st(
-  data = d_dpvar,
-  summ = c('mean(x)', 'sd(x)'),
-  digits = 2, 
-  group = 'Parental Migration',
-  group.test = list(
-    star.cutoffs = c(0.001, 0.01, 0.05),
-    format = 'p={pval}{stars}'),
-  labels = T,
-  out = 'return') 
-tab_dpvar <- tab_dpvar[-c(1),]
-tab_dpvar[tab_dpvar =='p=&lt0.001***']<-'p<0.001***'
-tab_dpvar 
-```
-
-```{r Data for binary control variable summary}
-d_ctvar_dit <- d_migr |>
-  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |>
-  mutate_all(as_factor)
-```
-
-```{r Binary control variable summary}
-tab_ctvar_dit <- 
-  st(
-  data = d_ctvar_dit,
-  digits = 2,
-  group = 'Parental Migration',
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = "return"
-  )
-tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
-tab_ctvar_dit[tab_ctvar_dit == 3422|tab_ctvar_dit == 640] <- ''
-tab_ctvar_dit 
-```
-
-```{r Data for categorical control variable summary}
-d_ctvar_cnt <- d_migr |>
-  select(`Parental Migration`, child.age, child.number.of.sibling, child.health, child.education.aspiration, 
-  mother.education.level, father.education.level, parent.expectation, 
-  home.extracurricular.book, home.economic.resource)
-```
-
-```{r Categorical control variable summary}
-tab_ctvar_cnt <- d_ctvar_cnt |> st(
-  digits = 2, 
-  summ = c('mean(x)', 'sd(x)'),
-  group = 'Parental Migration',
-  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
-  out = "return")
-tab_ctvar_cnt <- tab_ctvar_cnt[-c(1),]
-tab_ctvar_cnt
-```
-
-```{r Data for categorical control variable measurement}
-d_ctvar_label <- d_ctvar_cnt|>
-  select(!(`Parental Migration`:child.number.of.sibling)) |> 
-  add_value_labels(
-    father.education.level = c(
-     '0 = Primary school and below' = 0,
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    mother.education.level = c(
-     '0 = Primary school and below' = 0,
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    child.education.aspiration = c(
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    child.education.aspiration = c(
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5), 
-    parent.expectation = c(
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    home.economic.resource = c(
-      '1 = Very poor' = 1,
-      '2 = Somewhat poor' = 2,
-      '3 = Moderate' = 3,
-      '4 = Somewhat rich' = 4,
-      '5 = Very rich' = 5),
-    child.health = c(
-      '1 = Very poor' = 1,
-      '2 = Somewhat poor' = 2,
-      '3 = Moderate' = 3,
-      '4 = Good' = 4,
-      '5 = Very good' = 5),
-    home.extracurricular.book = c(
-      '1 = Very few' = 1,
-      '2 = Not many' = 2,
-      '3 = Some' = 3,
-      '4 = Quite a few' = 4,
-      '5 = A great number' = 5),
-    ) |>
-  as_factor()
-```
-
-```{r Measurement for categorical control variable}
-tab_var <- st(
-  data = d_ctvar_label,
-  out = 'return'
-)
-tab_var[tab_var == 4062] <- ''
-tab_var
-```
-
-```{r Data for violin plots}
-d_smr <- d_migr |> 
-  mutate(`Parental Migration Type` = 0) 
-d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
-d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
-d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
-d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
-d_smr <- d_smr |> select(!migr_mo_only & !migr_fa_only & !migr_both)
+raw score
+```{r}
+did_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 | clsids, data = d_cl) 
+did_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 | clsids, data = d_cl) 
+did_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 | clsids, data = d_cl) 
+did_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 | clsids, data = d_cl) 
+did_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 | clsids, data = d_cl) 
+did_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 | clsids, data = d_cl)
 ```
@@
 ```{r}
-set.seed(1)
-fig_cog <- d_smr |>
-  ggplot(aes(x=`Parental Migration`, y=cog_dif, fill=`Parental Migration`)) + 
-    geom_violin()+
-    xlab('Parental Migration') +
-    theme(legend.position="none") +
-    ylab('Cognitive Test Score Difference') +
-    stat_summary(
-      fun = "mean",
-      geom = "crossbar", 
-      size = 0.4,
-      width = 0.5) +
-  scale_fill_manual(values = alpha(c("green", "red"), .4))
-fig_cog
+models_unres_ttl <- list(
+'Any Parent Absent' = did_unres_ttl,
+'Only Mother Absent' = did_unres_ttl_m_only,
+'Mother Absent' = did_unres_ttl_m,
+'Only Father Absent' = did_unres_ttl_f_only,
+'Father Absent' = did_unres_ttl_f,
+'Both Parents Absent' = did_unres_ttl_both) 
+table_unres_ttl <- models_unres_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
+  title = 'Parental migration’s effect on children’s academic abilities',
+  fmt = 2,
+  coef_rename = c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"), output = 'markdown')
+table_unres_ttl
+```
+
+z score
+```{}
+did_unres_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z | clsids, data = d_cl) 
+did_unres_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z | clsids, data = d_cl) 
+did_unres_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z | clsids, data = d_cl) 
+did_unres_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z | clsids, data = d_cl) 
+did_unres_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z | clsids, data = d_cl) 
+did_unres_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z | clsids, data = d_cl)
+```
+
+```{}
+models_unres_ttl_z <- list(
+'Any Parent Absent' = did_unres_ttl_z,
+'Only Mother Absent' = did_unres_ttl_z_m_only,
+'Mother Absent' = did_unres_ttl_z_m,
+'Only Father Absent' = did_unres_ttl_z_f_only,
+'Father Absent' = did_unres_ttl_z_f,
+'Both Parents Absent' = did_unres_ttl_z_both) 
+table_unres_ttl_z <- models_unres_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_z
+```
+
+std
+```{}
+did_unres_ttl_std <- feols(ttl_std_dif ~ migr + w1ttl_std | clsids, data = d_cl) 
+did_unres_ttl_std_m_only <- feols(ttl_std_dif ~ migr_mo_only + w1ttl_std | clsids, data = d_cl) 
+did_unres_ttl_std_m <- feols(ttl_std_dif ~ migr_mo + w1ttl_std | clsids, data = d_cl) 
+did_unres_ttl_std_f_only <- feols(ttl_std_dif ~ migr_fa_only + w1ttl_std | clsids, data = d_cl) 
+did_unres_ttl_std_f <- feols(ttl_std_dif ~ migr_fa + w1ttl_std | clsids, data = d_cl) 
+did_unres_ttl_std_both <- feols(ttl_std_dif ~ migr_both + w1ttl_std | clsids, data = d_cl)
+```
+
+```{}
+models_unres_ttl_std <- list(
+'Any Parent Absent' = did_unres_ttl_std,
+'Only Mother Absent' = did_unres_ttl_std_m_only,
+'Mother Absent' = did_unres_ttl_std_m,
+'Only Father Absent' = did_unres_ttl_std_f_only,
+'Father Absent' = did_unres_ttl_std_f,
+'Both Parents Absent' = did_unres_ttl_std_both) 
+table_unres_ttl_std <- models_unres_ttl_std %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_std
+```
+
+dif to mean
+```{}
+did_unres_ttl_dm <- feols(ttl_dm_dif ~ migr + w1ttl_100_dm | clsids, data = d_cl) 
+did_unres_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1ttl_100_dm | clsids, data = d_cl) 
+did_unres_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1ttl_100_dm | clsids, data = d_cl) 
+did_unres_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1ttl_100_dm | clsids, data = d_cl) 
+did_unres_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1ttl_100_dm | clsids, data = d_cl) 
+did_unres_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1ttl_100_dm | clsids, data = d_cl)
+```
+
+```{}
+models_unres_ttl_dm <- list(
+'Any Parent Absent' = did_unres_ttl_dm,
+'Only Mother Absent' = did_unres_ttl_dm_m_only,
+'Mother Absent' = did_unres_ttl_dm_m,
+'Only Father Absent' = did_unres_ttl_dm_f_only,
+'Father Absent' = did_unres_ttl_dm_f,
+'Both Parents Absent' = did_unres_ttl_dm_both) 
+table_unres_ttl_dm <- models_unres_ttl_dm %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+                              fmt = 2,
+                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_unres_ttl_dm
+```
+
+## DID adjusted unrestricted
+$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
+
+Regressing on cognitive test score (standardized)
+```{r}
+did_adj_unres_cog <- feols(cog_dif ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+did_adj_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+did_adj_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+did_adj_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+did_adj_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+did_adj_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book  + home.internet | clsids, data = d_cl)
+```
+
+Results
+```{r}
+models_adj_unres_cog <- list(
+'Any Parent Absent' = did_adj_unres_cog,
+'Only Mother Absent' = did_adj_unres_cog_m_only,
+'Mother Absent' = did_adj_unres_cog_m,
+'Only Father Absent' = did_adj_unres_cog_f_only,
+'Father Absent' = did_adj_unres_cog_f,
+'Both Parents Absent' = did_adj_unres_cog_both) 
+table_adj_unres_cog <- models_adj_unres_cog %>% 
+  msummary(stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001),
+           title = 'Parental migration’s effect on children’s cognitive abilities',
+           fmt = 2,
+           coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "W1 score"), output = 'markdown')
+table_adj_unres_cog
+```
+
+Regressing on total exam score
+```{r}
+did_adj_unres_ttl <- feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_m_only <- feols(ttl_dif ~ migr_mo_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_m <- feols(ttl_dif ~ migr_mo + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_f <- feols(ttl_dif ~ migr_fa + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_f_only <- feols(ttl_dif ~ migr_fa_only + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_both <- feols(ttl_dif ~ migr_both + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+```
+
+Results
+```{r}
+models_adj_unres_ttl <- list(
+'Any Parent Absent' = did_adj_unres_ttl,
+'Only Mother Absent' = did_adj_unres_ttl_m_only,
+'Mother Absent' = did_adj_unres_ttl_m,
+'Only Father Absent' = did_adj_unres_ttl_f_only,
+'Father Absent' = did_adj_unres_ttl_f,
+'Both Parents Absent' = did_adj_unres_ttl_both) 
+table_adj_unres_ttl <- models_adj_unres_ttl %>% msummary(
+  stars =  c('†' = .1, '*' = .05, '**' = .01, '***' = .001), 
+  title = 'Parental migration’s effect on children’s academic abilities',
+  fmt = 2, 
+  coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_100" = "W1 score"), output = 'markdown')
+table_adj_unres_ttl
+```
+
+Regressing on total exam score
+```{}
+did_adj_unres_ttl_z <- feols(ttl_z_dif ~ migr + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_z_m_only <- feols(ttl_z_dif ~ migr_mo_only + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_z_m <- feols(ttl_z_dif ~ migr_mo + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_z_f <- feols(ttl_z_dif ~ migr_fa + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_z_f_only <- feols(ttl_z_dif ~ migr_fa_only + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_z_both <- feols(ttl_z_dif ~ migr_both + w1ttl_z + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+```
+
+Results
+```{}
+models_adj_unres_ttl_z <- list(
+'Any Parent Absent' = did_adj_unres_ttl_z,
+'Only Mother Absent' = did_adj_unres_ttl_z_m_only,
+'Mother Absent' = did_adj_unres_ttl_z_m,
+'Only Father Absent' = did_adj_unres_ttl_z_f_only,
+'Father Absent' = did_adj_unres_ttl_z_f,
+'Both Parents Absent' = did_adj_unres_ttl_z_both) 
+table_adj_unres_ttl_z <- models_adj_unres_ttl_z %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_ttl_z
+```
+
+Regressing on total exam score
+```{}
+did_adj_unres_ttl_dm <- feols(ttl_dm_dif ~ migr + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_dm_m_only <- feols(ttl_dm_dif ~ migr_mo_only + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_dm_m <- feols(ttl_dm_dif ~ migr_mo + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_dm_f <- feols(ttl_dm_dif ~ migr_fa + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_dm_f_only <- feols(ttl_dm_dif ~ migr_fa_only + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+did_adj_unres_ttl_dm_both <- feols(ttl_dm_dif ~ migr_both + w1ttl_100_dm + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_cl)
+```
+
+Results
+```{}
+models_adj_unres_ttl_dm <- list(
+'Any Parent Absent' = did_adj_unres_ttl_dm,
+'Only Mother Absent' = did_adj_unres_ttl_dm_m_only,
+'Mother Absent' = did_adj_unres_ttl_dm_m,
+'Only Father Absent' = did_adj_unres_ttl_dm_f_only,
+'Father Absent' = did_adj_unres_ttl_dm_f,
+'Both Parents Absent' = did_adj_unres_ttl_dm_both) 
+table_adj_unres_ttl_dm <- models_adj_unres_ttl_dm %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), fmt = 2, coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "w1ttl_dif" = "Baseline difference"), output = 'markdown')
+table_adj_unres_ttl_dm
+```
+
+## Matching
+```{r}
+m.out <- matchit(migr ~ age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet, data = d_cl, method = "cem")
+summary(m.out, un = FALSE)
 ```
@@
 ```{r}
-set.seed(1)
-fig_ttl <-  d_smr |>
-  ggplot(aes(x=`Parental Migration`, y=avg_dif, fill=`Parental Migration`)) + 
-    geom_violin()+
-    xlab('Parental Migration') +
-    theme(legend.position="none") +
-    ylab('Academic Exam Score Difference') +
-    stat_summary(
-      fun = "mean",
-      geom = "crossbar", 
-      size = 0.4,
-      width = 0.5) +
-  scale_fill_manual(values = alpha(c("green", "red"), .4))
-fig_ttl
+d_match <- match.data(m.out)
 ```
@@
 ```{r}
-set.seed(1)
-fig_cog_by_migration_type <- d_smr |>
-  ggplot(aes(x=`Parental Migration Type`, y=cog_dif, fill = `Parental Migration Type`)) + 
-    geom_violin()+
-    xlab('Parental Migration Type') +
-    theme(legend.position="none") +
-    ylab('Cognitive Test Score Difference') +
-    stat_summary(
-      fun = "mean",
-      geom = "crossbar", 
-      width = 0.5)+
-  scale_fill_manual(values = alpha(c("green", "tomato1", "tomato2", "tomato3"), .4))
-fig_cog_by_migration_type
+feols(cog_dif ~ migr + cog3pl + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet | clsids, data = d_match, weights = d_match$weights) %>%
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2)
+feols(ttl_dif ~ migr + w1ttl_100 + age + ch.girl + ch.health + ch.rural + ch.sibling + ch.preschool + ch.skip.grd + ch.repeat.grd + ch.boarding + ch.aspr.univ + ch.ethn.mnrt + par.edu.year + par.expt.univ + par.ccp + home.finances + home.book + home.internet  | clsids, data = d_match, weights = d_match$weights) %>%
+  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
+           fmt = 2)
 ```
@@
 ```{r}
-set.seed(1)
-fig_ttl_by_migration_type <- d_smr |>
-  ggplot(aes(x=`Parental Migration Type`, y=avg_dif, fill = `Parental Migration Type`)) + 
-    geom_violin()+
-    xlab('Parental Migration Type') +
-    theme(legend.position="none") +
-    ylab('Academic Exam Score Difference') +
-    stat_summary(
-      fun = "mean",
-      geom = "crossbar", 
-      width = 0.5) +
-  scale_fill_manual(values = alpha(c("green", "tomato1", "tomato2", "tomato3"), .4))
-fig_ttl_by_migration_type
+datasummary_skim(d_asp)
 ```
-
-# Econometric models
-## DID without covariates
-```{r Unadjusted regression on cognitive score}
-did_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = df) 
-did_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = df) 
-did_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = df) 
-did_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = df)
-```
-
-```{r Unadjusted regression on exam grade}
-did_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = df) 
-did_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = df) 
-did_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = df) 
-did_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = df)
-```
-
-```{r}
-models_cog <- list(
-'Any Parent' = did_cog,
-'Only Mother' = did_cog_m_only,
-'Only Father' = did_cog_f_only,
-'Both Parents' = did_cog_both) 
-```
-
-```{r}
-models_ttl <- list(
-'Any Parent' = did_ttl,
-'Only Mother' = did_ttl_m_only,
-'Only Father' = did_ttl_f_only,
-'Both Parents' = did_ttl_both) 
-```
-
-```{r Info for regression tables}
-stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
-coef_rename <- c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1cog_100" = "Baseline.score", "w1avg_100" = "Baseline.score")
-title_cog <- 'Parental migration’s effect on children’s cognitive test score'
-title_ttl <- 'Parental migration’s effect on children’s academic exam score'
-gof_omit <- 'R2 Within|R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
-note_unadj <- 'No control variables included in these models'
-```
-
-```{r}
-models_cog <- list(
-'Any Parent' = did_cog,
-'Only Mother' = did_cog_m_only,
-'Only Father' = did_cog_f_only,
-'Both Parents' = did_cog_both) 
-```
-
-```{r}
-models_ttl <- list(
-'Any Parent' = did_ttl,
-'Only Mother' = did_ttl_m_only,
-'Only Father' = did_ttl_f_only,
-'Both Parents' = did_ttl_both) 
-```
-
-```{r}
-table_cog <- models_cog |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename,
-  notes = note_unadj,
-  output = 'latex')
-```
-
-```{r}
-table_ttl <- models_ttl |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_ttl,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_unadj,
-  output = 'latex')
-```
-
-## DID with covariates
-$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
-
-```{r Adjusted regression on cognitive score}
-did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-```
-
-```{r Adjusted regression on exam grade}
-did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-```
-
-```{r}
-models_adj_cog <- list(
-'Any Parent' = did_adj_cog,
-'Only Mother' = did_adj_cog_m_only,
-'Only Father' = did_adj_cog_f_only,
-'Both Parents' = did_adj_cog_both) 
-```
-
-```{r}
-models_adj_ttl <- list(
-'Any Parent' = did_adj_ttl,
-'Only Mother' = did_adj_ttl_m_only,
-'Only Father' = did_adj_ttl_f_only,
-'Both Parents' = did_adj_ttl_both)
-```
-
-```{r}
-table_adj_cog <- models_adj_cog |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  output = 'latex'
-  )
-```
-
-```{r}
-table_adj_ttl <- models_adj_ttl |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  output = 'latex'
-  )
-```
-
-## Matching
-```{r Match on any parent migration}
-m.out <- matchit(
-  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
-  data = df, 
-  ratio = 3,
-  method = "optimal", 
-  distance = "glm",
-  exact = migr ~ ctyids
-  )
-```
-
-```{r}
-dm <- match.data(m.out)
-```
-
-```{r Match on mother-only migration}
-d_mo_only <- d_cl |> drop_na(migr_mo_only)
-m.out_mo_only <- 
-  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
-  data = d_mo_only, 
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact = migr_mo_only ~ ctyids
-  )
-```
-
-```{r}
-dm_mo_only <- match.data(m.out_mo_only)
-```
-
-```{r Match on father-only migration}
-d_fa_only <- d_cl |> drop_na(migr_fa_only)
-m.out_fa_only <- matchit(
-  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
-  data = d_fa_only,
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact = migr_fa_only ~ ctyids
-  )
-```
-
-```{r}
-dm_fa_only <- match.data(m.out_fa_only)
-```
-
-```{r Match on both parents migration}
-d_both <- d_cl |> drop_na(migr_both) 
-m.out_both <- matchit(
-  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet,
-  data = d_both, 
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact = migr_both ~ ctyids
-  )
-```
-
-```{r}
-dm_both <- match.data(m.out_both)
-```
-
-## Balance Assessment
-```{r ASMD plot any-parent}
-m.out |> love.plot(
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-```{r ASMD plot only-mother}
-m.out_mo_only |> love.plot(
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-```{r ASMD plot only-father}
-m.out_fa_only |> love.plot(
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-```{r ASMD plot both-parents}
-m.out_both |> love.plot(
-  threshold = c(m = .1),
-  binary = "std", 
-  limits = c(0, 0.55),
-  abs = T
-  )
-```
-
-## Regression with matching
-
-```{r Unadjusted regression on cognitive score, with matching}
-didm_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = dm, weights = dm$weights)
-didm_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 | schids, data = dm_both, weights = dm_both$weights)
-```
-
-```{r Unadjusted regression on exam score, with matching}
-didm_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = dm, weights = dm$weights)
-didm_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 | schids, data = dm_both, weights = dm_both$weights)
-```
-
-```{r Adjusted regression on cognitive score, with matching}
-didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
-didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
-```
-
-```{r Adjusted regression on exam score, with matching}
-didm_adj_ttl <- feols(avg_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
-didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
-```
-
-```{r Info for regression table with matching}
-title_cog_matching <- 'Parental migration’s effect on children’s cognitive test scores, estimated with matching'
-title_ttl_matching <- 'Parental migration’s effect on children’s academic exam scores, estimated with matching'
-note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"
-```
-
-```{r}
-models_m_cog <- list(
-'Any Parent' = didm_cog,
-'Only Mother' = didm_cog_mo_only,
-'Only Father' = didm_cog_fa_only,
-'Both Parents' = didm_cog_both) 
-```
-
-```{r}
-models_m_ttl <- list(
-'Any Parent' = didm_ttl,
-'Only Mother' = didm_ttl_mo_only,
-'Only Father' = didm_ttl_fa_only,
-'Both Parents' = didm_ttl_both) 
-```
-
-```{r}
-models_m_adj_cog <- list(
-'Any Parent' = didm_adj_cog,
-'Only Mother' = didm_adj_cog_mo_only,
-'Only Father' = didm_adj_cog_fa_only,
-'Both Parents' = didm_adj_cog_both) 
-```
-
-```{r}
-models_m_adj_ttl <- list(
-'Any Parent' = didm_adj_ttl,
-'Only Mother' = didm_adj_ttl_mo_only,
-'Only Father' = didm_adj_ttl_fa_only,
-'Both Parents' = didm_adj_ttl_both) 
-```
-
-```{r}
-table_m_cog <- models_m_cog |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'latex'
-  )
-```
-
-```{r}
-table_m_ttl <- models_m_ttl |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_ttl_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'latex'
-)
-```
-
-```{r}
-table_m_adj_cog <- models_m_adj_cog |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'latex'
-  )
-```
-
-```{r}
-table_m_adj_ttl <- models_m_adj_ttl |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_ttl_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'latex'
- )
-```

### 2022-07-08 MScThesisText.Rmd

--- 2022-07-03 MScThesisText.Rmd
@@
 ---
-title             : "Newly Left-Behind Children's Educational Performance Drops Slightly After Parents Migrated"
+title             : "Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration"
 shorttitle        : "Left-Behind Children"
@@
   Millions of children worldwide are "left behind" at home communities as their parents migrate away for work. 
-  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on children's educational attainment. 
+  Parents' labor migration increases household income but decreases parental care, thereby exerting mixed influences on child development outcomes like educational attainment. 
   To what extent do different arrangements of parental migration affect children's educational performance in the short term? 
@@
 library("modelsummary")
+options(modelsummary_get="broom") 
 r_refs("references.bib")
@@
 Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause br on par with random assignment to participants, conditional on identification assumptions [@cunningham2021].
+It requires that the cause be on par with random assignment to participants, conditional on identification assumptions [@cunningham2021].
 
-In this thesis, my research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
+My research question is: To what extent do different arrangements of parental migration affect the educational performance of left-behind children in the short term?
 I choose China as the case and analyze data from a two-wave panel survey.
 The nationally representative sample includes children in both urban and rural areas.
-I develop a difference-in-differences model for causal inference and applied propensity score matching for robustness checks.
-The outcome was measured with children's cognitive test score and academic exam grade.
+I develop a difference-in-differences model for causal inference and apply propensity score matching for robustness checks.
+The outcome is measured with children's cognitive test score and academic exam grade.
 I demonstrate that parental migration reduces the educational performance of children staying behind, but only to a small extent.
@@
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers.
-They form the backbone of essential industries, such as retail, delivery, transportation, and manufacturing.
+They form the backbone of essential industries, such as retail, transportation, and manufacturing.
 The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind [@nbs2022; @nbs2017].
@@
 But China's welfare program, as @qian2021 argued, is fragmented and stratified.
-Those who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
+People who reap the greatest benefits are public servants, urban dwellers, and formally employed workers.
 As rural migrants arrive in the city, they find themselves with limited access to social welfare, such as health care and children's education [@qian2021].
@@
 
-The institutionalized discrimination against rural migrants finds its roots in China's "multilevel citizenship" system.
+The institutional discrimination against labor migrants finds its roots in China's "multilevel citizenship" system.
 As @vortherms2021 explained, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through the *hukou*, or household registration system:
+The local state confers most of the rights and defines who is eligible to these rights through *hukou*, or the household registration system:
 
@@
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-Criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
 This parallels how European states differentially incorporate foreign immigrants into national welfare regimes [@zhang2018].
-Another policy response, as stated by @roberts2018, is the centralized boarding schools.
+Another policy response, as stated by @roberts2018, is the centralized boarding school.
 The Ministry of Education promotes boarding schools in the rural county-seats.
-These schools serve as a cost-efficient way to enroll students in surrounding villages and to look after the left-behind children.
+These schools serve as a cost-effective way to enroll students in surrounding villages and to look after the left-behind children.
 In reality, such schools "are often ill-equipped to ensure the healthy upbringing and psychological wellbeing of children" (p.
@@
 The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
-My sample includes urban left-behind children as well.
 The second shortcoming lies in sampling and research design.
@@
 This subsequently boosted children's school enrollment and educational expenditure.
-@cebotari2020 developed a fixed effect model with three-wave panel data collected in Ghana.
-He found that stay-behind children's education benefits from "the steady inflow of both in-kind and monetary remittances" contributed by migrant parents.
+@cebotari2020 developed a fixed effect model with longitudinal data collected in Ghana.
+He found that stay-behind children's education benefited from "the steady inflow of both in-kind and monetary remittances" contributed by migrant parents.
 In China, @chang2019 interviewed migrant workers and their family members.
-Oftentimes, they found that labor migration presented the only way to sustain their children's education and livelihood.
+Oftentimes, labor migration presented the only way to sustain their children's education and livelihood.
 @peng2018 interviewed first-generation migrant mothers whose initial migration dated back to the 1990s.
-To them, "good mothering" primarily means offering economic support for their children in education, which can help their children climb the ladder of success.
+To them, "good mothering" primarily meant offering economic support for their children in education, which can help their children climb the ladder of success.
 
@@
 Children flourish under parental nurturing care.
-This term refers to the "stable environments that promote health and adequate nutrition, protect from threats, and provide opportunities for learning and responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.
+This term refers to the "stable environments that promote health and adequate nutrition, protect from threats ...
+opportunities for learning," and "responsive, emotionally supportive and developmentally enriching relationships" [@black2021, p.
 1].
@@
 They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
-@wang2019 collected data from junior high school students in central China.
-The researchers' two-way fixed-effect model showed no effect of parental on left-behind children's achievement in mathematical test.
-Studying four Chinese provinces, @debrauw2017 showed that as ample migration opportunities appeared in villages, enrollment to senior high school decreased.
+The team of @wang2019 collected data from junior high school students in central China.
+Their two-way fixed-effect model showed no significant effect of parental migration on left-behind children's achievement in mathematical test.
 @nguyen2016 conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
@@
 @chen2019 conducted structural equation modeling on the cross-sectional data collected from fourth to seventh graders in the countryside of one province.
-They found that mother migration was "negatively associated with children's social competence and academic performance," while father migration had no direct effects on the two outcomes (pp.
+They found that maternal migration was "negatively associated with children's social competence and academic performance," while paternal migration had no direct effects on the two outcomes (pp.
 860-861).
@@
 The survey team adopted multi-stage stratified probability proportional to size sampling and administered a paper-and-pencil questionnaire to each participant.
-The baseline survey (wave one) took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
-These students were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter 'counties').
-The follow-up survey (wave two) in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed `r printnum(nrow(d))` of the seventh grade cohort.
-I further restricted the sample to students living with both parents at the original domicile at the baseline survey.
+The wave one baseline survey took place in the 2013-2014 academic year with a sample size of about twenty thousand students in the seventh and ninth grades.
+They were nested in 438 classrooms of 112 schools in 28 urban districts or rural counties (hereafter 'counties').
+The wave two follow-up survey in the 2014-2015 academic year lost track of the ninth grade cohort and only surveyed `r printnum(nrow(d))` of the seventh grade cohort.
+I further restricted the sample to students living with both parents at the original domicile (place of hukou registry) at the baseline survey.
 To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
@@
 After the conversion, I checked for abnormal values lower than zero or higher than one hundred.
-`r printnum(num.outlier$n)` observations were outliers, accounting for less than one percent of the sample.
+`r printnum(nrow(outlier))` observations were outliers, accounting for less than one percent of the sample.
 I retained these observations in the sample and trimmed the subject exam scores.
@@
 
-The control variables on children's level include age, gender, ethnicity, self-rated health, hukou type, number of siblings, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+The control variables at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority of Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
 At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
-The lists of covariates are in Tables 3-5 in the Results section.
+The lists of covariates are in Table \@ref(tab:tab-ctvar-dit) -- Table \@ref(tab:tab-ctvar-msr) in the Results section.
 
@@
 The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \varepsilon_{i,j}$$ For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between baseline and follow-up surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
-School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in the same school are also in the same county.
-An alternative is to use a class fixed-effect to control for time-invariant factors in the classroom.
+I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}$$ For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between the two waves of surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
+School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in one school are also in the same county.
+An alternative is to use a class fixed-effect to control for time-invariant factors at the classroom level and above.
 However, about one-sixth of the students were reassigned into new classes at the end of baseline academic year.
@@
 Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
-The standard errors were clustered at the classroom level.
+The standard errors are clustered at the classroom level.
 
-In addition, I present an unrestricted and adjusted DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{i} + \theta \cdot X_{i} + \varepsilon_{i,j}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+In addition, I made an unrestricted and adjusted DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
 The control variables were measured in the baseline survey.
@@
 
-Table 1 summarizes the independent variables, namely the migration status reported in the wave two survey.
-All `r printnum(nrow(d_cl))` children were living with parents in one household in baseline, but about fifteen percent saw at least one parent migrated between the two waves of survey.
+Table \@ref(tab:tab-idpvar) summarizes the independent variables, namely the migration status reported in the wave two survey.
+All `r printnum(nrow(d_cl))` children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
 I call these students "newly left-behind children" and their households "new migration households." In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
-The remaining one-fifth was both-parents migration.
+The remaining one-fifth were both-parents migration.
 
@@
 
-```{r}
+```{r tab-idpvar}
 datasummary_df(
   data = tab_idpvar,
-  output = 'latex',
+  output = 'markdown',
   title = 'Independent variables by parental migration'
@@
 
-The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figures B1-B4 in the appendix.
-Compared to non-left-behind peers, newly left-behind children score lower in wave two's cognitive and academic tests; Their cognitive test score increases less and their academic exam score drops more.
+The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figure \@ref(fig:v-plot-cog) -- Figure \@ref(fig:v-plot-ttl-1) in the appendix.
+Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
 T-tests show that for the baseline outcomes, the differences of the mean values between-group are probably due to chance.
@@
 
-```{r}
+```{r tab-dpvar}
 tab_dpvar |> 
@@
 
-Table 3 summarizes the bivariate analysis on the binary control variables.
-New migration households have lower internet access rate.
+Table \@ref(tab:tab-ctvar-dit) summarizes the bivariate analysis on the binary control variables.
+New migration households had lower internet access rate.
 Among the newly left-behind children, male sex, past grade retention, and boarding at school were more common compared to the non-left-behind peers.
@@
 
-```{r}
+```{r tab-ctvar-dit}
 tab_ctvar_dit |>
@@
   add_header_above(c(" ", "Parental Migration" = 4)) |>
-  footnote(general = '* p < 0.05, ** p < 0.01, *** p < 0.001')
+  footnote(general = '0 = No, 1 = Yes; * p < 0.05, ** p < 0.01, *** p < 0.001')
 ```
@@
 
-Table 4 presents the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
-While the majority of mothers and fathers have only finished high school or below, they hold big expectations for children.
-Eight out of ten parents wish that their children complete university education.
+Table \@ref(tab:tab-ctvar-cnt) displays the bivariate analysis for categorical control variables, and Table \@ref(tab:tab-ctvar-msr) documents their measurement scales.
+While the majority of mothers and fathers had only finished high school or below, they held big expectations for children.
+Eight out of ten parents wished that their children complete university education.
 Scholars like @willis2019 explained this pattern with the Chinese social norms and cultural traditions.
@@
 Ordinary people could study for the highly competitive *keju* (civil service examination).
-As the world's "earliest meritocratic institution," this exam system recruited top performers into the imperial government and the elite class [@chen2020, p.
+As the world's "earliest meritocratic institution," this national exam system recruited top performers into the imperial government and the elite class [@chen2020, p.
 2030].
@@
 
-```{r}
+```{r tab-ctvar-cnt}
 tab_ctvar_cnt |>
@@
 
-```{r}
+```{r tab-ctvar-msr}
 datasummary_df(
   data = tab_var,
-  title = 'Measurement of categorical variables',
-  output = 'latex'
+  title = 'Measurement and distribution of categorical variables',
+  output = 'markdown'
 )
@@
 I first present the results on children's cognitive test score.
-According to the unadjusted DID models (see Table 6 below), newly left-behind adolescents are more likely to score lower in cognitive tests than their non-left-behind counterparts, lending support to Hypothesis 1a.
+The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6 below).
+This lends support to Hypothesis 1a.
 Parental migration is linked to a `r coef(did_cog)[1] |> abs() |> round(2)` points decrease in cognitive test score.
 Hypothesis 2a is only partially supported.
-Compared with the non-left-behind children, children with only father absent are associated with greater decrease (`r coef(did_cog_f_only)[1] |> abs() |> round(2)` points) in cognitive test score than those with only mother absent (`r coef(did_cog_m_only)[1] |> abs() |> round(2)` points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (See Table A1 in appendix).
+Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (`r coef(did_cog_f_only)[1] |> abs() |> round(2)` points) in cognitive test score than those with only mother absent (`r coef(did_cog_m_only)[1] |> abs() |> round(2)` points).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in appendix).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
 
-```{r reg-cog}
+```{r tab-reg-cog}
 table_cog
@@
 Next, I show the results on children's academic test grades.
-In line with Hypothesis 1b, the unadjusted DID models (see Table 7 below) show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers.
+In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
 Parental migration is associated with a drop of `r coef(did_ttl)[1] |> abs() |> round(2)` points in academic exam score.
@@
 
-```{r reg-ttl}
+```{r tab-reg-ttl}
 table_ttl
@@
 These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
-One year older in age is associated with decreases of `r coef(did_adj_cog)[3] |> abs() |> round(2)` points for cognitive test and of `r coef(did_adj_ttl)[3] |> abs() |> round(2)` points for academic exam.
+For students, one year older in age is associated with decreases of `r coef(did_adj_cog)[3] |> abs() |> round(2)` points for cognitive test and of `r coef(did_adj_ttl)[3] |> abs() |> round(2)` points for academic exam.
 Preschool attendance is linked to increases of `r round(coef(did_adj_cog)[8],2)` points for cognitive test and of `r round(coef(did_adj_ttl)[8],2)` points for academic exam.
 Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
-The coefficients are `r round(coef(did_adj_cog)[15],2)` points and `r round(coef(did_adj_cog)[12],2)` points for cognitive test, respectively; and `r round(coef(did_adj_ttl)[15],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
+The coefficients are `r round(coef(did_adj_cog)[14],2)` points and `r round(coef(did_adj_cog)[12],2)` points for cognitive test, respectively; and `r round(coef(did_adj_ttl)[14],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
 
 Several predictors are strong in predicting one outcome but not the other.
-Covariates related to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
-Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive test.
+Covariates that only relate to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
+Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive tests.
 Students who consider themselves healthier are associated with higher scores in academic exams.
-On the contrary, students who perceive their households having more extracurricular books are associated with lower scores in academic exams.
-Covariates related to cognitive scores is the number of siblings.
-Having an additional sibling is associated with lower cognitive score of `r coef(did_adj_cog)[7] |> abs() |> round(2)` points, but its effect for academic grade is not significant statistically.
+On the contrary, those who report having more extracurricular books at home are associated with lower scores in academic exams.
+Covariates that only relate to cognitive scores is the number of siblings.
+Having an additional sibling is associated with lower cognitive score of `r coef(did_adj_cog)[7] |> abs() |> round(2)` points.
 
@@
 A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
-Another scenario is that poverty may hamper children's educational achievement while driving parents to migrate.
+Another scenario is that poverty may hinder children's educational achievement while driving parents to migrate.
 To tackle the selection bias herein, an applicable technique is matching.
-It makes two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@greifer2022].
+It aims to two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@greifer2022].
 
@@
 This score serves as a measure of the distance between two units.
-PSM can match the units with two different approaches to handle distance.
-The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance to be paired.
-This approach does not try to optimize any condition; each pairing ignores how other pairing will occur or have occurred.
-The optimal-pair approach works in a similar fashion but tries to minimize the sum of the absolute pairwise distances [@pan2018].
+When handling this distance, PSM can match the units with two different approaches.
+The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance for pairing.
+This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
+The optimal-pair approach works in a similar fashion but tries to minimize the absolute pairwise distances in total [@pan2018].
 Regardless of specific approaches, @king2019 argued against PSM in general as it risks more "imbalance, model dependence, and bias" for already balanced data (p.
@@
 CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without an exact match and discards these unmatched units [@costalli2021].
+The downside is that it leaves many units without a match and discards these unmatched units [@costalli2021].
 
-I performed matching with all the covariates of the adjusted DID model.
+I performed matching with all the covariates of the adjusted DID model on the four treatments respectively.
 My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
-I then made do with the PSM.
+I then made do with PSM.
 I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
@@
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
-In the appendix, Figures B5-B8 presents the plots of absolute standardized mean differences before and after matching.
+In appendix, Figure \@ref(fig:cobal-any) -- Figure \@ref(fig:cobal-both) display the absolute standardized mean differences before and after matching.
 
-The results from models with matching strongly resemble the models without matching (see Tables 8 and 9 below, and Tables A3 and A4 in the appendix).
+The results from models with matching strongly resemble the models without matching (see Tables 8 -- 9 below, and Tables A3 -- A4 in appendix).
 In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
 In the models of academic exam score, the treatment variables' coefficients are negative and statistically significant for the any-parent-migrated scenario and the only-mother-migrated scenario.
-The magnitudes of the statistically significant coefficients are similar to those without matching.
+The magnitudes of the statistically significant coefficients are similar to those in the models without matching.
 
-```{r reg-m-cog}
-table_m_cog
+```{r tab-reg-m-cog}
+models_m_cog |> msummary(
+  stars =  stars,
+  fmt = 2,
+  title = title_cog_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
+  output = 'markdown'
+  )
 ```
 
-\newpage
-
-```{r reg-m-ttl}
-table_m_ttl
+```{r tab-reg-m-ttl}
+models_m_ttl |> msummary(
+  stars =  stars,
+  fmt = 2,
+  title = title_cog_matching,
+  gof_omit = gof_omit,
+  coef_rename =  coef_rename, 
+  notes = note_matching,
+  output = 'markdown'
+  )
 ```
@@
 
-This thesis proposes a model to infer the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
-I build econometric models in the difference-in-differences design to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance as shown by a 1.2 percent drop in academic exam grades and a 2.5 percent drop in cognitive test scores.
-This contrasts with the results of DID models by @bai2018: parental migration is linked to higher English test scores for stay-behind children.
-The discrepancy could be attributed the study's location, a poverty-stricken Northwestern province.
+This thesis infers the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
+I build difference-in-differences models with fixed-effect to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
+Results suggest that parental migration is, in the short run, negatively associated with children's educational performance.
+This is evidenced by a 1.2 points drop in academic exam grades and a 2.5 points drop in cognitive test scores.
+This result contrasts with that of DID models by @bai2018: parental migration is linked to higher English test scores for stay-behind children.
+The discrepancy could be attributed their study's location, a Northwestern province with grinding poverty.
 There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.
@@
 In my nationwide sample the reverse may hold.
-The households may be better off, so the labor migrant's additional income helps less.
+The households may be better off, so labor migration's additional income fails to compensate for the care deficit.
 Another plausibility is that family disruption precedes resource generation.
-The former's negative effect befalls the left-behind child at once, but the latter's positive effect occurs a while later.
+The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs a while later [@gao2019].
 Consequently, I obtain a short-term negative effect.
@@
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that in the short term, father's absence is not linked to children's academic exam scores; Mother's absence is negatively associated with children's academic and cognitive test results, with a 2.1 percent drop for both indicators.
-An explanation is that the mother's migration, by defying the cultural expectations on maternal care, harbors bitterness in the child's mind [@murphy2020].
-On the other hand, father's migration is negatively associated with children's cognitive test score with a 3 percent decrease.
+Results indicate that in the short term, only father's absence is not linked to children's academic performance; Only mother's absence is negatively associated with children's academic abilities, with a 2.1 points drop in the test score.
+This is in line with the findings of previous research.
+For example, @murphy2020 observed that when a Chinese mother migrates, she defies the cultural expectations on maternal care, thereby harboring bitterness in the child's mind.
+This bitter sentiment can arise even if there is care by father or other relatives.
+Besides, only-mother migration sometimes indicates deeper issues within the household.
+The father may be unfit for work or engaged in domestic violence, prompting the mother's labor migration [@murphy2020].
+These may all hamper children's educational performance.
+
+Compared to only mother's migration, only father's migration carries a stronger influence on children's cognitive capability, as shown by a further decrease of 1 point in cognitive test score.
 This echoes the findings of @shen2021 -- in rural China, the father is often a household's best educated adult.
@@
 Besides, I could not control for the migration history of parents, which are not included in the CEPS data.
-According to @liang2021, some parents out-migrated at an earlier date and returned before the baseline survey.
-These children would be attributed to the non-left-behind group.
-However, they "suffer similar disadvantage as that of left behind children" (p.
+According to @liang2021, some parents might have out-migrated at an earlier date and returned before the baseline survey.
+Their children would be attributed to the non-left-behind group.
+However, these children "suffer similar disadvantage as that of left behind children" (p.
 12).
@@
 Limitations also arise from unaccounted endogeneity and exogeneity.
-As @chen2009 discussed in their research on left-behind children, endogenous factors may create selection bias.
+As @chen2009 discussed in their paper on left-behind children, endogenous factors may create selection bias.
 When migration opportunities arise, some parents may worry that leaving children behind would hamper children's education, thereby giving up the opportunity.
@@
 Suppose that a natural hazard hit many counties of a province in the sample.
-This shock can simultaneously increase parents' out-migration and reduce stay-behind students' grades [@chen2009].
+This shock can increase parents' out-migration and reduce stay-behind students' grades [@chen2009].
 I could not account for such shocks as CEPS data does not include detailed geographic information.
@@
 Looking beyond outbound migration, return migration of parents also worth studying [@liang2021].
-Not many publications have explored return migrants and their formerly left-behind children in the Chinese context [@démurger2015; @liu2018].
+Not many publications have explored return migrants and their formerly left-behind children in China [@démurger2015; @liu2018].
 
@@
 Besides top-down policymaking, bottom-up approaches are also necessary.
-School administrators could dedicate advisory and counseling programs.
+School administrators could dedicate more advisory and counseling programs.
 Social workers could provide paraprofessional training in communities [@wang2020a].

### 2022-07-08 appendix-b.Rmd

# Figures

(ref:cog-dif) Changes in cognitive test score

(ref:ttl-dif) Changes in academic exam score

(ref:migr) for newly left-behind students and non-left-behind students

(ref:migr-type) by household migration arrangement

(ref:cobalt-match) Covariate balance before and after matching

(ref:cobalt-any) by any parent migration

(ref:cobalt-fa) by father-only migration

(ref:cobalt-mo) by mother-only migration

(ref:cobalt-both) by both parents migration

```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%'}
fig_cog
```

\newpage

```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%'}
fig_ttl
```

```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)"), out.height='40%'}
fig_cog_by_migration_type
```

```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)"), out.height='40%'}
fig_ttl_by_migration_type
```

\newpage

```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)"), out.height='40%'}
m.out |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)"), out.height='40%'}
m.out_mo_only |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

\newpage

```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)"), out.height='40%'}
m.out_fa_only |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)"), out.height='40%'}
m.out_both |> love.plot(
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
```

### 2022-07-11 data/Gu-thesis-script.Rmd
edit chunk names in R script

--- 2022-07-05 data/Gu-thesis-script.Rmd
@@
 
-```{r}
+```{r Violin plot 1}
 set.seed(1)
@@
 
-```{r}
+```{r Violin plot 2}
 set.seed(1)
@@
 
-```{r}
+```{r Violin plot 3}
 set.seed(1)
@@
 
-```{r}
+```{r Violin plot 4}
 set.seed(1)
@@
 
-```{r}
+```{r Table for unadjusted regression on cognitive score}
 table_cog <- models_cog |> msummary(
@@
 
-```{r}
+```{r Table for unadjusted regression on exam grade}
 table_ttl <- models_ttl |> msummary(
@@
 
-```{r}
+```{r Table for adjusted regression on cognitive score}
 table_adj_cog <- models_adj_cog |> msummary(
@@
 
-```{r}
+```{r Table for adjusted regression on exam grade}
 table_adj_ttl <- models_adj_ttl |> msummary(
@@
 
-```{r Unadjusted regression on cognitive score, with matching}
+```{r Unadjusted regression on cognitive score with matching}
 didm_cog <- feols(cog_dif ~ migr + w1cog_100 | schids, data = dm, weights = dm$weights)
@@
 
-```{r Unadjusted regression on exam score, with matching}
+```{r Unadjusted regression on exam score with matching}
 didm_ttl <- feols(avg_dif ~ migr + w1avg_100 | schids, data = dm, weights = dm$weights)
@@
 
-```{r Adjusted regression on cognitive score, with matching}
+```{r Adjusted regression on cognitive score with matching}
 didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
@@
 
-```{r Adjusted regression on exam score, with matching}
+```{r Adjusted regression on exam score with matching}
 didm_adj_ttl <- feols(avg_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
@@
 
-```{r}
+```{r Table for unadjusted regression on cognitive score with matching}
 table_m_cog <- models_m_cog |> msummary(
@@
 
-```{r}
+```{r Table for unadjusted regression on exam grade with matching}
 table_m_ttl <- models_m_ttl |> msummary(
@@
 
-```{r}
+```{r Table for adjusted regression on cognitive score with matching}
 table_m_adj_cog <- models_m_adj_cog |> msummary(
@@
 
-```{r}
+```{r Table for adjusted regression on exam grade with matching}
 table_m_adj_ttl <- models_m_adj_ttl |> msummary(
@@
 ```
+
+```{r save image}
+save.image('.RData')
+```

### 2022-07-15 analysis/Gu-thesis-script.Rmd
reorganize file path

--- 2022-07-11 data/Gu-thesis-script.Rmd
@@
 ```{r Read data}
-d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
-d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
-d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
-d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
+d_stu1 <- read_dta('cepsw1studentEN.dta') #wave 1 student
+d_stu2 <- read_dta('cepsw2studentEN.dta') #wave 2 student
+d_par1 <- read_dta('cepsw1parentEN.dta') #wave 1 parent
+d_par2 <- read_dta('cepsw2parentEN.dta') #wave 2 parent
 ```

### 2022-08-13 MScThesisText.Rmd
Revise based on supervisor's comment

@@
 keywords          : "labor migration, left-behind children, educational performance"
-wordcount         : "6,600"
+wordcount         : "6,789"
 
@@
 footnotelist      : no
+
+fontfamily: lmodern
 
@@
 Three features make China a suitable case for studying left-behind children.
-The first feature is the huge scale of internal labor migration.
+The most prominent feature is the huge scale of internal labor migration.
 According to the National Bureau of Statistics, the year 2021 recorded 292.5 million in-country migrant workers.
@@
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
+Only during the winter and summer breaks can these children reunite with parents.
 
@@
 
-Researchers have studied whether the impact differ between mother's migration and father's migration.
+Researchers have studied whether the impact differs between mother's migration and father's migration.
 @xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
@@
 
-The control variables at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority of Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+The control variables were all measured in the baseline survey.
+Covariates at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority of Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
 At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
@@
 
-I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' [-@bai2018; -@bai2020] approach.
-The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}$$ For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between the two waves of surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
+I built a two-way fixed effect model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018; @bai2020].
+The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
+I compared the treatment group's pre- and post-treatment outcomes in relation to the control group.
+
+Below is my first version of DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}$$ It is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The model is unadjusted as it does not adjust for additional covariates.
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
+For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between the two waves of surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
 School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in one school are also in the same county.
+The standard errors are clustered at the school level.
 An alternative is to use a class fixed-effect to control for time-invariant factors at the classroom level and above.
@@
 
-The DID model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
-The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
-The standard errors are clustered at the classroom level.
-
-In addition, I made an unrestricted and adjusted DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
-The control variables were measured in the baseline survey.
-This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
+In addition, I present the second version of DID model: $$\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}$$ where $X_{i}$ is the vector of covariates capturing the characteristics of children, their parents, and their households.
+This model includes covariate adjustment with an assumption: Covariates from the baseline survey may be associated with a coefficient that does not equal equal one.
 
 I adopted `R` (version 4.2.0) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 1.3.1) for data cleaning [@R-tidyverse]; `fixest` (version 0.10.4) for econometric modeling [@R-fixest]; `MatchIt` (version 4.4.0) and `cobalt` (version 4.3.2) for matching [@R-MatchIt; @R-cobalt]; `modelsummary` (version 1.0.0), `vtable` (version 1.3.3), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.0) for typesetting [@R-papaja].
+This involved the following packages: `tidyverse` (version 1.3.2) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.10.4) for econometric modeling [@berge2018; @R-fixest]; `MatchIt` (version 4.4.0) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.0.2), `vtable` (version 1.3.4), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
 
@@
 
-Table \@ref(tab:tab-idpvar) summarizes the independent variables, namely the migration status reported in the wave two survey.
+Table \@ref(tab:tab-idpvar) illustrates the independent variables, namely the migration status reported in the wave two survey.
 All `r printnum(nrow(d_cl))` children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
@@
 
-The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figure \@ref(fig:v-plot-cog) -- Figure \@ref(fig:v-plot-ttl-1) in the appendix.
+The dependent variables are summarized by the control group versus the treatment group in Table \@ref(tab:tab-dpvar) below and Figure \@ref(fig:v-plot-cog) -- Figure \@ref(fig:v-plot-ttl-1) in the appendix.
 Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
@@
 
-I first present the results on children's cognitive test score.
+I first explain the results on children's cognitive test score.
 The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6 below).
@@
 Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (`r coef(did_cog_f_only)[1] |> abs() |> round(2)` points) in cognitive test score than those with only mother absent (`r coef(did_cog_m_only)[1] |> abs() |> round(2)` points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in appendix).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in the appendix).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
@@
 
-Next, I show the results on children's academic test grades.
+Next, I set forth the results on children's academic test grades.
 In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
@@
 In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
-The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in appendix).
+The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in the appendix).
 Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
@@
 Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
+Possibly, smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
 Another scenario is that poverty may hinder children's educational achievement while driving parents to migrate.
-To tackle the selection bias herein, an applicable technique is matching.
-It aims to two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@greifer2022].
+The endogeneity leads to selection bias.
+To tackle this bias, an applicable technique is matching.
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@costalli2021].
 
-Popular choices for matching include propensity score matching (PSM) and coarsened exact matching (CEM).
-As @pan2018 introduced, PSM will first calculate the propensity score, namely the probability of receiving treatment based on the specified covariates.
+A popular choice for matching, as @pan2018 introduced, is propensity score matching (PSM).
+For each unit in the sample, PSM will first calculate a propensity score, namely the probability of receiving treatment based on the specified covariates.
 This score serves as a measure of the distance between two units.
-When handling this distance, PSM can match the units with two different approaches.
-The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance for pairing.
+When handling this distance, PSM can match the units with two approaches.
+One is the nearest-neighbor approach.
+It examines all the treated units and selects the control unit closest in distance for pairing.
 This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
-The optimal-pair approach works in a similar fashion but tries to minimize the absolute pairwise distances in total [@pan2018].
-Regardless of specific approaches, @king2019 argued against PSM in general as it risks more "imbalance, model dependence, and bias" for already balanced data (p.
+The second approach, the optimal-pair approach, works in a similar fashion but tries to minimize the absolute pairwise distances in total [@pan2018].
+
+Matching with propensity score does not guarantee a more balanced sample.
+Suppose that in the matching, some covariates are related the treatment but not to the outcome.
+In this case, the propensity score estimator's variance would increase.
+This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome [@adelson2017; @bergstra2019].
+@king2019 argued against PSM in general as it risks more "imbalance, model dependence, and bias" for already balanced data (p.
 444).
-They recommended CEM as a viable alternative "for data with continuous, discrete, and mixed variables" (p.
+They recommended coarsened exact matching (CEM) as a viable alternative "for data with continuous, discrete, and mixed variables" (p.
 450).
-CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without a match and discards these unmatched units [@costalli2021].
+CEM works better in achieving balance as it optimizes the entire joint distribution of covariates.
+The method's downside is that it leaves many units without a match and discards these unmatched units [@costalli2021].
 
@@
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
-In appendix, Figure \@ref(fig:cobal-any) -- Figure \@ref(fig:cobal-both) display the absolute standardized mean differences before and after matching.
+In the appendix, Figure \@ref(fig:cobal-any) -- Figure \@ref(fig:cobal-both) display the absolute standardized mean differences before and after matching.
 
-The results from models with matching strongly resemble the models without matching (see Tables 8 -- 9 below, and Tables A3 -- A4 in appendix).
+The results from models with matching strongly resemble the models without matching, as shown in Table 8 -- Table 9 below and Table A3 -- Table A4 in the appendix.
 In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
@@
 ```{r tab-reg-m-cog}
-models_m_cog |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'markdown'
-  )
-```
-
-```{r tab-reg-m-ttl}
-models_m_ttl |> msummary(
-  stars =  stars,
-  fmt = 2,
-  title = title_cog_matching,
-  gof_omit = gof_omit,
-  coef_rename =  coef_rename, 
-  notes = note_matching,
-  output = 'markdown'
-  )
+table_m_cog
 ```
@@
 
-# Discussion
+```{r tab-reg-m-ttl}
+table_m_ttl
+```
+
+\newpage
+
+# Discussion and Conclusion
 
@@
 
+## Limitations
+
 My research has limitations in sampling due to data constraint.
@@
 I could not account for such shocks as CEPS data does not include detailed geographic information.
+
+## Recommendations
 
@@
 
-# (APPENDIX) Appendix {.unnumbered}
+# (APPENDIX) the appendix {.unnumbered}
 

### 2022-08-13 MScThesisText.tex
Revise based on supervisor's comment

--- 2022-07-05 MScThesisText.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
+\usepackage[]{lmodern}
 \usepackage{iftex}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration},
-  pdfauthor={Jiancheng Gu1},
-  pdflang={en-EN},
-  pdfkeywords={labor migration, left-behind children, educational performance},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{longtable,booktabs,array}
@@
 {}{\PatchFailed}
-\keywords{labor migration, left-behind children, educational performance\newline\indent Word count: 6,600}
+\keywords{labor migration, left-behind children, educational performance\newline\indent Word count: 6,789}
 \usepackage{csquotes}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration},
+  pdfauthor={Jiancheng Gu1},
+  pdflang={en-EN},
+  pdfkeywords={labor migration, left-behind children, educational performance},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-Researchers have studied whether the impact differ between mother's migration and father's migration.
+Researchers have studied whether the impact differs between mother's migration and father's migration.
 Xu et al.
@@
 
-I built a two-way fixed effect model in a difference-in-differences (DID) design, following Bai and colleagues' (2018; 2020) approach.
-The model served to analyze the educational outcome of children newly left behind by parents vis-a-vis that of children staying together with parents.
-I first specified an unrestricted and unadjusted model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}\] For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between the two waves of surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
+I built a two-way fixed effect model in a difference-in-differences (DID) design, utilizing parental migration as the treatment (Bai et al., 2018; Bai et al., 2020).
+The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
+I compared the treatment group's pre- and post-treatment outcomes in relation to the control group.
+
+Below is my first version of DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \varepsilon_{i,j}\] It is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
+The model is unadjusted as it does not adjust for additional covariates.
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
+For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between the two waves of surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
 School fixed-effect can account for differences due to time-invariant factors at the school and county levels, as students nested in one school are also in the same county.
+The standard errors are clustered at the school level.
 An alternative is to use a class fixed-effect to control for time-invariant factors at the classroom level and above.
@@
 
-The DID model is unrestricted because it does not restrict on the coefficient associated with the baseline scores.
-The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
-The standard errors are clustered at the classroom level.
-
-In addition, I made an unrestricted and adjusted DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
-The control variables were measured in the baseline survey.
-This version of model lifts the restriction that covariates from the baseline survey would be associated with a coefficient that equals one.
+In addition, I present the second version of DID model: \[\Delta score_{i,j} = \alpha + \beta \cdot migr_{i} + \gamma \cdot score_{i;1} + \lambda \cdot S_{j} + \theta \cdot X_{i} + \varepsilon_{i,j}\] where \(X_{i}\) is the vector of covariates capturing the characteristics of children, their parents, and their households.
+This model includes covariate adjustment with an assumption: Covariates from the baseline survey may be associated with a coefficient that does not equal equal one.
 
 I adopted \texttt{R} (version 4.2.0) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 1.3.1) for data cleaning (Wickham et al., 2019); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022b; Ho et al., 2022); \texttt{modelsummary} (version 1.0.0), \texttt{vtable} (version 1.3.3), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.0) for typesetting (Aust \& Barth, 2022).
+This involved the following packages: \texttt{tidyverse} (version 1.3.2) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2022); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022; Berge, 2018); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022, 2011); \texttt{modelsummary} (version 1.0.2), \texttt{vtable} (version 1.3.4), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 
-Table~\ref{tab:tab-idpvar} summarizes the independent variables, namely the migration status reported in the wave two survey.
+Table~\ref{tab:tab-idpvar} illustrates the independent variables, namely the migration status reported in the wave two survey.
 All 4062 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
@@
 \caption{\label{tab:tab-idpvar}Independent variables by parental migration}\tabularnewline
-\toprule
+\toprule()
 Variable & N & Percent \\
-\midrule
+\midrule()
 \endfirsthead
-\toprule
+\toprule()
 Variable & N & Percent \\
-\midrule
+\midrule()
 \endhead
@@
 \ldots{} Only Mother Migrated & 258 & 6.4\% \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 
-The dependent variables are summarized by the control group versus the treatment group in Table 2 below and Figure~\ref{fig:v-plot-cog} -- Figure~\ref{fig:v-plot-ttl-1} in the appendix.
+The dependent variables are summarized by the control group versus the treatment group in Table~\ref{tab:tab-dpvar} below and Figure~\ref{fig:v-plot-cog} -- Figure~\ref{fig:v-plot-ttl-1} in the appendix.
 Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
@@
 \caption{\label{tab:tab-ctvar-msr}Measurement and distribution of categorical variables}\tabularnewline
-\toprule
+\toprule()
 Variable & N & Percent \\
-\midrule
+\midrule()
 \endfirsthead
-\toprule
+\toprule()
 Variable & N & Percent \\
-\midrule
+\midrule()
 \endhead
@@
 \ldots{} 5 = Very rich & 11 & 0.3\% \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.87 points) in cognitive test score than those with only mother absent (2.15 points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in appendix).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in the appendix).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
@@
 Parental migration is not a randomly assigned treatment.
-A possible circumstance is that smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
+Possibly, smart and ambitious students perform better at school, and high performance and ambition prompt parents to migrate to support children's schooling.
 Another scenario is that poverty may hinder children's educational achievement while driving parents to migrate.
-To tackle the selection bias herein, an applicable technique is matching.
-It aims to two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Greifer, 2022a).
-
-Popular choices for matching include propensity score matching (PSM) and coarsened exact matching (CEM).
-As Pan and Bai (2018) introduced, PSM will first calculate the propensity score, namely the probability of receiving treatment based on the specified covariates.
+The endogeneity leads to selection bias.
+To tackle this bias, an applicable technique is matching.
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Costalli \& Negri, 2021).
+
+A popular choice for matching, as Pan and Bai (2018) introduced, is propensity score matching (PSM).
+For each unit in the sample, PSM will first calculate a propensity score, namely the probability of receiving treatment based on the specified covariates.
 This score serves as a measure of the distance between two units.
-When handling this distance, PSM can match the units with two different approaches.
-The nearest-neighbor approach examines all the treated units and selects the control unit closest in distance for pairing.
+When handling this distance, PSM can match the units with two approaches.
+One is the nearest-neighbor approach.
+It examines all the treated units and selects the control unit closest in distance for pairing.
 This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
-The optimal-pair approach works in a similar fashion but tries to minimize the absolute pairwise distances in total (Pan \& Bai, 2018).
-Regardless of specific approaches, King and Nielsen (2019) argued against PSM in general as it risks more ``imbalance, model dependence, and bias'' for already balanced data (p.~444).
-They recommended CEM as a viable alternative ``for data with continuous, discrete, and mixed variables'' (p.~450).
-CEM is superior in achieving balance as it optimizes the entire joint distribution of covariates.
-The downside is that it leaves many units without a match and discards these unmatched units (Costalli \& Negri, 2021).
+The second approach, the optimal-pair approach, works in a similar fashion but tries to minimize the absolute pairwise distances in total (Pan \& Bai, 2018).
+
+Matching with propensity score does not guarantee a more balanced sample.
+Suppose that in the matching, some covariates are related the treatment but not to the outcome.
+In this case, the propensity score estimator's variance would increase.
+This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome (Adelson et al., 2017; Bergstra et al., 2019).
+King and Nielsen (2019) argued against PSM in general as it risks more ``imbalance, model dependence, and bias'' for already balanced data (p.~444).
+They recommended coarsened exact matching (CEM) as a viable alternative ``for data with continuous, discrete, and mixed variables'' (p.~450).
+CEM works better in achieving balance as it optimizes the entire joint distribution of covariates.
+The method's downside is that it leaves many units without a match and discards these unmatched units (Costalli \& Negri, 2021).
 
@@
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
-In appendix, Figure~\ref{fig:cobal-any} -- Figure~\ref{fig:cobal-both} display the absolute standardized mean differences before and after matching.
-
-The results from models with matching strongly resemble the models without matching (see Tables 8 -- 9 below, and Tables A3 -- A4 in appendix).
+In the appendix, Figure~\ref{fig:cobal-any} -- Figure~\ref{fig:cobal-both} display the absolute standardized mean differences before and after matching.
+
+The results from models with matching strongly resemble the models without matching, as shown in Table 8 -- Table 9 below and Table A3 -- Table A4 in the appendix.
 In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2239}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1791}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2090}}@{}}
-\caption{\label{tab:tab-reg-m-cog}Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents
-\end{minipage} \\
-\midrule
-\endfirsthead
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.64}*** & \num{-2.76}* & \num{-3.41}** & \num{-1.96}\\
+ & (\num{0.74}) & (\num{1.22}) & (\num{1.25}) & (\num{1.74})\\
+Baseline.score & \num{-0.70}*** & \num{-0.74}*** & \num{-0.62}*** & \num{-0.69}***\\
+ & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.392} & \num{0.450} & \num{0.423} & \num{0.467}\\
+R2 Adj. & \num{0.363} & \num{0.384} & \num{0.356} & \num{0.352}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam scores, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -2.64*** & -2.76* & -3.41** & -1.96 \\
-& (0.74) & (1.22) & (1.25) & (1.74) \\
-Baseline.score & -0.70*** & -0.74*** & -0.62*** & -0.69*** \\
-& (0.02) & (0.04) & (0.03) & (0.05) \\
-Num.Obs. & 2503 & 1032 & 1008 & 515 \\
-R2 & 0.392 & 0.450 & 0.423 & 0.467 \\
-R2 Adj. & 0.363 & 0.384 & 0.356 & 0.352 \\
-FE: schids & X & X & X & X \\
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.22}* & \num{-1.65}* & \num{-1.15} & \num{0.46}\\
+ & (\num{0.57}) & (\num{0.81}) & (\num{0.86}) & (\num{0.98})\\
+Baseline.score & \num{0.05}† & \num{0.07}† & \num{0.04} & \num{0.01}\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
+\midrule
+Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
+R2 & \num{0.468} & \num{0.587} & \num{0.480} & \num{0.501}\\
+R2 Adj. & \num{0.444} & \num{0.538} & \num{0.420} & \num{0.393}\\
+FE: schids & X & X & X & X\\
 \bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 optimal pair propensity score matching; exact matching by county
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2239}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1791}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1940}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2090}}@{}}
-\caption{\label{tab:tab-reg-m-ttl}Parental migration's effect on children's cognitive test scores, estimated with matching}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Any Parent
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Mother
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Only Father
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Both Parents
-\end{minipage} \\
-\midrule
-\endhead
-Migration & -1.22* & -1.65* & -1.15 & 0.46 \\
-& (0.57) & (0.81) & (0.86) & (0.98) \\
-Baseline.score & 0.05† & 0.07† & 0.04 & 0.01 \\
-& (0.03) & (0.04) & (0.04) & (0.04) \\
-Num.Obs. & 2503 & 1032 & 1008 & 515 \\
-R2 & 0.468 & 0.587 & 0.480 & 0.501 \\
-R2 Adj. & 0.444 & 0.538 & 0.420 & 0.393 \\
-FE: schids & X & X & X & X \\
-\bottomrule
-\end{longtable}
-
-\textbf{Note:}
-\^{}\^{} † p \textless{} 0.1, * p \textless{} 0.05, ** p \textless{} 0.01, *** p \textless{} 0.001
-
-\textbf{Note:}
-\^{}\^{} 3:1 optimal pair propensity score matching; exact matching by county
+\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{discussion-and-conclusion}{%
+\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
 
@@
 
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
 My research has limitations in sampling due to data constraint.
@@
 
+\hypertarget{recommendations}{%
+\subsection{Recommendations}\label{recommendations}}
+
 From my research, we can find new directions for scholarly inquiry.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-adelson2017}{}}%
+Adelson, J.
+L., McCoach, D.
+B., Rogers, H.
+J., Adelson, J.
+A., \& Sauer, T.
+M.
+(2017).
+Developing and applying the propensity score to make causal inferences: Variable selection and stratification.
+\emph{Frontiers in Psychology}, \emph{8}.
+\url{https://doi.org/10.3389/fpsyg.2017.01413}
+
 \leavevmode\vadjust pre{\hypertarget{ref-akezhuoli2022}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-berge2018}{}}%
+Berge, L. (2018). Efficient estimation of maximum likelihood models with multiple fixed-effects: The {R} package {FENmlm}. \emph{CREA Discussion Papers}, \emph{13}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-fixest}{}}%
 Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bergstra2019}{}}%
+Bergstra, S.
+A., Sepriano, A., Ramiro, S., \& Landewé, R.
+(2019).
+Three handy tips and a practical guide to improve your propensity score models.
+\emph{RMD Open}, \emph{5}(1), e000953.
+\url{https://doi.org/10.1136/rmdopen-2019-000953}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-greifer2022}{}}%
-Greifer, N. (2022a). \emph{MatchIt: Getting started}. \url{https://kosukeimai.github.io/MatchIt/articles/MatchIt.html}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-cobalt}{}}%
-Greifer, N. (2022b). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
+Greifer, N. (2022). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
 
@@
 \url{https://doi.org/10.1177/0011392120985874}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ho2011}{}}%
+Ho, D., Imai, K., King, G., \& Stuart, E.
+(2011).
+{MatchIt}: Nonparametric preprocessing for parametric causal inference.
+\emph{Journal of Statistical Software}, \emph{42}(8), 1--28.
+\url{https://doi.org/10.18637/jss.v042.i08}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
+Wickham, H., Miller, E., \& Smith, D. (2022). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}
+
 \leavevmode\vadjust pre{\hypertarget{ref-willis2019}{}}%
@@
 
-\hypertarget{appendix-appendix}{%
+\hypertarget{appendix-the-appendix}{%
 \appendix}

### 2023-02-24 MScThesisText.Rmd
Fix minor errors in tables

@@
 These are the so-called "left-behind children" or "stay-behind children." They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@popova2018], and one-fourth of Chinese children were separated from their migrating parents [@nbs2017].
+Researchers estimated that one-sixth of Mexican children [@dewaard2018], one-fifth of Bulgarian children [@romact2021], and one-fourth of Chinese children were separated from their migrating parents [@nbs2017].
 The issue of left-behind children has caught the attention of policymakers and legislators.
@@
 The control variables were all measured in the baseline survey.
-Covariates at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority of Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
+Covariates at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority or Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
 At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
@@
 
-I built a two-way fixed effect model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018; @bai2020].
+I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018; @bai2020].
 The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.

### 2023-02-24 appendix-b.Rmd
Fix minor errors in tables

@@
 
-```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%'}
+```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
 fig_cog
@@
 
-```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%'}
+```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
 fig_ttl
@@
 
-```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)"), out.height='40%'}
+```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
 fig_cog_by_migration_type
@@
 
-```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)"), out.height='40%'}
+```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
 fig_ttl_by_migration_type

### 2023-02-24 MScThesisText.Rmd
reference new studies

@@
   - name          : "Jiancheng Gu"
-    affiliation   : "1"
-    address       : "De Boelelaan 1105, 1081 HV - Amsterdam, The Netherlands"
-    email         : "j4.gu@student.vu.nl"
+    #affiliation   : "1"
 
@@
 
-fontfamily: lmodern
+#fontfamily: lmodern
 
@@
 Consider children's education.
-According to the review articles by @debrauw2019 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by @venta2022 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 To what degree can the inflow of remittances compensate for the loss of parental attention?
@@
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
-This parallels how European states differentially incorporate foreign immigrants into national welfare regimes [@zhang2018].
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment [@dong2020].
+This parallels how European states differentially incorporate foreign immigrants into national welfare regimes [@pasquali2022].
 Another policy response, as stated by @roberts2018, is the centralized boarding school.
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital.
+It holds that parental migration brings forth greater resources in the form of economic capital [@debrauw2019].
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
-Economic capital is transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
+Economic resources are transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
 @yang2008 noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
@@
 He found that stay-behind children's education benefited from "the steady inflow of both in-kind and monetary remittances" contributed by migrant parents.
-In China, @chang2019 interviewed migrant workers and their family members.
+In China, @gu2022a interviewed migrant workers and their family members.
+She found that they aspire to move up the social ladder; Such aspiration translates into "intensive and all-out investment in children's education" (p.
+526).
 Oftentimes, labor migration presented the only way to sustain their children's education and livelihood.
@@
 1].
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@wen2019].
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@].
 Hong talked to a group of left-behind children at a rural school [@hong2019].
@@
 186).
+According to @chen2023, caregiver-child interactions are infrequent and unstable for left-behind children.
+She showed that the loss in such interactions "mediates almost all of the adverse effects of parental absence." Her conclusion was based on structural equation modeling (SEM) using a cross-sectional survey with a sample of Chinese children aged 3-15.
 
@@
 The baseline and follow-up tests consisted of 20 and 35 items, respectively.
-The raw score was calculated based on the Item Response Theory [@wang2015].
+The raw score was calculated based on Three-Parameter Logistic model of Item Response Theory [@wang2015].
 I transformed the raw scores to the 100-point scale.
@@
 
-I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018; @bai2020].
+I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018].
 The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
@@
 Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
-Looking beyond outbound migration, return migration of parents also worth studying [@liang2021].
-Not many publications have explored return migrants and their formerly left-behind children in China [@démurger2015; @liu2018].
+Looking beyond outbound migration, the return migration of parents also worth studying [@liang2021].
+Not many publications have explored return migrants and their formerly left-behind children in China [see @démurger2015; @liu2018].
 

### 2023-02-24 MScThesisText.tex
reference new studies

@@
 \usepackage{amsmath,amssymb}
-\usepackage[]{lmodern}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 These are the so-called ``left-behind children'' or ``stay-behind children.'' They are common in migrant-sending regions, such as Latin America, Sub-Sahara Africa, East Europe, and large parts of Asia.
-Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (Popova, 2018), and one-fourth of Chinese children were separated from their migrating parents (NBS et al., 2017).
+Researchers estimated that one-sixth of Mexican children (DeWaard et al., 2018), one-fifth of Bulgarian children (ROMACT, 2021), and one-fourth of Chinese children were separated from their migrating parents (NBS et al., 2017).
 The issue of left-behind children has caught the attention of policymakers and legislators.
@@
 Consider children's education.
-According to the review articles by Brauw (2019) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to the review articles by Venta and Cuervo (2022) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 To what degree can the inflow of remittances compensate for the loss of parental attention?
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022).
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022b).
 Migrant workers have organized petitions, strikes, and protests.
@@
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
-This parallels how European states differentially incorporate foreign immigrants into national welfare regimes (Zhang, 2018).
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment (Dong \& Goodburn, 2020).
+This parallels how European states differentially incorporate foreign immigrants into national welfare regimes (Pasquali, 2022).
 Another policy response, as stated by Roberts and Hannum (2018), is the centralized boarding school.
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital.
+It holds that parental migration brings forth greater resources in the form of economic capital (Brauw, 2019).
 Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
 16).
-Economic capital is transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
+Economic resources are transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
 D.
@@
 He found that stay-behind children's education benefited from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
-In China, Chang et al.
-(2019) interviewed migrant workers and their family members.
+In China, Gu (2022a) interviewed migrant workers and their family members.
+She found that they aspire to move up the social ladder; Such aspiration translates into ``intensive and all-out investment in children's education'' (p.~526).
 Oftentimes, labor migration presented the only way to sustain their children's education and livelihood.
@@
 1).
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents (Wen \& Xie, 2019).
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents {[}@{]}.
 Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
@@
 Some of them ``embraced the `left-behind' label'' because it captured their need for more parental care (p.~185), ``especially companionship and affection in daily life'' (p.~186).
+According to C.
+Chen (2023), caregiver-child interactions are infrequent and unstable for left-behind children.
+She showed that the loss in such interactions ``mediates almost all of the adverse effects of parental absence.'' Her conclusion was based on structural equation modeling (SEM) using a cross-sectional survey with a sample of Chinese children aged 3-15.
 
@@
 The baseline and follow-up tests consisted of 20 and 35 items, respectively.
-The raw score was calculated based on the Item Response Theory (W.
+The raw score was calculated based on Three-Parameter Logistic model of Item Response Theory (W.
 Wang \& Li, 2015).
@@
 After the conversion, I checked for abnormal values lower than zero or higher than one hundred.
-30 observations were outliers, accounting for less than one percent of the sample.
+36 observations were outliers, accounting for less than one percent of the sample.
 I retained these observations in the sample and trimmed the subject exam scores.
@@
 
-I built a two-way fixed effect model in a difference-in-differences (DID) design, utilizing parental migration as the treatment (Bai et al., 2018; Bai et al., 2020).
+I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment (Bai et al., 2018).
 The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
@@
 \bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}No control variables included in these models}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \end{tabular}
@@
 
-\caption{Parental migration’s effect on children’s cognitive test scores, estimated with matching}
+\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
 \centering
@@
 \bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \end{tabular}
@@
 
-\caption{Parental migration’s effect on children’s academic exam scores, estimated with matching}
+\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
 \centering
@@
 Liu, 2021).
-Looking beyond outbound migration, return migration of parents also worth studying (Liang \& Li, 2021).
-Not many publications have explored return migrants and their formerly left-behind children in China (Démurger \& Xu, 2015; Z.
+Looking beyond outbound migration, the return migration of parents also worth studying (Liang \& Li, 2021).
+Not many publications have explored return migrants and their formerly left-behind children in China (see Démurger \& Xu, 2015; Z.
 Liu et al., 2018).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bai2020}{}}%
-Bai, Y., Neubauer, M., Ru, T., Shi, Y., Kenny, K., \& Rozelle, S.
-(2020).
-Impact of Second-Parent Migration on Student Academic Performance in Northwest China and its Implications.
-\emph{The Journal of Development Studies}, \emph{56}(8), 1523--1540.
-\url{https://doi.org/10.1080/00220388.2019.1690136}
-
 \leavevmode\vadjust pre{\hypertarget{ref-bai2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chen2023}{}}%
+Chen, C.
+(2023).
+Left-Behind Children{'}s Cognitive Development in China: Gain in Financial Capital Versus Loss in Parental Capital.
+\emph{Sociological Perspectives}, 073112142211450.
+\url{https://doi.org/10.1177/07311214221145059}
+
 \leavevmode\vadjust pre{\hypertarget{ref-chen2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-dong2020}{}}%
+Dong, Y., \& Goodburn, C.
+(2020).
+Residence Permits and Points Systems: New Forms of Educational and Social Stratification in Urban China.
+\emph{Journal of Contemporary China}, \emph{29}(125), 647--666.
+\url{https://doi.org/10.1080/10670564.2019.1704997}
+
 \leavevmode\vadjust pre{\hypertarget{ref-duckett2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gu2022a}{}}%
+Gu, X.
+(2022a).
+Sacrifice and Indebtedness: The Intergenerational Contract in Chinese Rural Migrant Families.
+\emph{Journal of Family Issues}, \emph{43}(2), 509--533.
+\url{https://doi.org/10.1177/0192513X21993890}
+
 \leavevmode\vadjust pre{\hypertarget{ref-gu2022}{}}%
 Gu, X.
-(2022).
+(2022b).
 {`}Save the children!{'}: Governing left-behind children through family in China{'}s Great Migration.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pasquali2022}{}}%
+Pasquali, P.
+(2022).
+Migration regimes and the governance of citizenship: a comparison between legal categories of migration in China and in the European Union.
+\emph{Journal of Chinese Governance}, \emph{7}(4), 633--657.
+\url{https://doi.org/10.1080/23812346.2020.1791505}
+
 \leavevmode\vadjust pre{\hypertarget{ref-peng2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-popova2018}{}}%
-Popova, A.
-(2018).
-Risk factors for the safety of the children from transnational families children left behind.
-\emph{Anthropological Researches and Studies}, \emph{1}(8), 25--35.
-\url{https://doi.org/10.26758/8.1.3}
-
 \leavevmode\vadjust pre{\hypertarget{ref-qian2021}{}}%
@@
 \url{https://doi.org/10.47381/aijre.v28i2.231}
+
+\leavevmode\vadjust pre{\hypertarget{ref-romact2021}{}}%
+ROMACT.
+(2021).
+\emph{Report on children left behind: Between labour migration, institutional standards, and extended family}.
+\url{https://coe-romact.org/sites/default/files/romact_resources_files/Report_Children\%20Left\%20Behind_ENG_0\%20\%281\%29.pdf}
 
@@
 \url{https://doi.org/10.1111/jomf.12621}
+
+\leavevmode\vadjust pre{\hypertarget{ref-venta2022}{}}%
+Venta, A., \& Cuervo, M. (2022). Attachment, loss, and related challenges in migration. \emph{Current Opinion in Psychology}, \emph{47}, 101406. \url{https://doi.org/10.1016/j.copsyc.2022.101406}
 
@@
 \url{https://doi.org/10.1177/1868102619894739}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wen2019}{}}%
-Wen, Y., \& Xie, J.
-(2019).
-Missing families and villages: The care deficit faced by rural left-behind children in china and its implications.
-\emph{International Journal of Care and Caring}, \emph{3}(2), 247--262.
-\url{https://doi.org/10.1332/239788218X15421003245041}
 
@@
 
-\caption{Parental migration’s effect on children’s cognitive test score}
+\caption{Parental migration’s effect on children’s academic exam score}
 \centering

### 2023-02-24 analysis/Gu-thesis-script.Rmd
reference new studies

@@
 d_cl <- d_cl |> mutate(
-  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
+  w1chn_100 = tr_chn/w2upchn*100, #raw exam score at 100-point scale
   w1mat_100 = tr_mat/w2upmat*100,
@@
   fmt = 2,
-  title = title_cog,
+  title = title_ttl,
   gof_omit = gof_omit,
@@
 ```{r Info for regression table with matching}
-title_cog_matching <- 'Parental migration’s effect on children’s cognitive test scores, estimated with matching'
-title_ttl_matching <- 'Parental migration’s effect on children’s academic exam scores, estimated with matching'
+title_cog_matching <- 'Parental migration’s effect on children’s cognitive test score, estimated with matching'
+title_ttl_matching <- 'Parental migration’s effect on children’s academic exam score, estimated with matching'
 note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"

### 2023-02-26 MScThesisText.Rmd
adjusted reference

@@
 The issue of left-behind children has caught the attention of policymakers and legislators.
-In a resolution, the Council of Europe's @parliamentaryassembly2021 expressed concern about "the scale of this phenomenon and the long-term damage it creates" and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights".
+In a resolution, the Parliamentary Assembly of the Council of Europe expressed concern about "the scale of this phenomenon and the long-term damage it creates" and declared that leaving "millions of labour migrants' children without parental care is a mass violation of human rights" [@pace2021].
 
@@
 
-Social scientists have researched extensively about China's left-behind children, but the current literature still has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue [@nbs2017].
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns [@liu2021; @yang2022; @shu2021].
-Others only estimated correlation using cross-sectional data [@akezhuoli2022; @jin2020; @huang2020].
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+Social scientists have researched extensively about the education of Chinese left-behind children, but the current literature still has three major shortcomings.
+The first shortcoming lies in sampling.
+For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas [see @hu2019; @zhou2014].
+@wang2023 noted that the number of urban left-behind children have been growing, and the trend is expected to continue.
+The second shortcoming is the usage of cross-sectional data [see @huang2022; @liu2022].
+@wassink2021 argued that cross-sectional surveys merely focus on single time points, thereby failing to capture the dynamic nature of migratory journey.
+Research results would be under- or over-estimated "depending on the timing of data collection" (p.
+1766).
 The third shortcoming lies in the measurement of outcome.
@@
 1].
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents [@].
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents.
 Hong talked to a group of left-behind children at a rural school [@hong2019].
@@
 According to @chen2023, caregiver-child interactions are infrequent and unstable for left-behind children.
-She showed that the loss in such interactions "mediates almost all of the adverse effects of parental absence." Her conclusion was based on structural equation modeling (SEM) using a cross-sectional survey with a sample of Chinese children aged 3-15.
+She showed that the loss in such interactions "mediates almost all of the adverse effects of parental absence." Her conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
 
@@
 
-I adopted `R` (version 4.2.0) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 1.3.2) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.10.4) for econometric modeling [@berge2018; @R-fixest]; `MatchIt` (version 4.4.0) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.0.2), `vtable` (version 1.3.4), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
+I adopted `R` (version 4.2.2) for all the analyses [@R-base].
+This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@berge2018; @R-fixest]; `MatchIt` (version 4.5.1) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.1), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
 
@@
 In this case, the propensity score estimator's variance would increase.
-This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome [@adelson2017; @bergstra2019].
+This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome [@adelson2017].
 @king2019 argued against PSM in general as it risks more "imbalance, model dependence, and bias" for already balanced data (p.
@@
 Another plausibility is that family disruption precedes resource generation.
-The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs a while later [@gao2019].
+The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs some time later [@wassink2021].
 Consequently, I obtain a short-term negative effect.
@@
 Novel methods also offer new possibilities.
-Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021a].
+Machine learning, for example, can estimate the heterogeneous effects across subgroups [@liu2021].
 Looking beyond outbound migration, the return migration of parents also worth studying [@liang2021].
@@
 Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020].
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020; @pang2022].
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.

### 2023-02-26 MScThesisText.tex
adjusted reference

@@
   pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration},
-  pdfauthor={Jiancheng Gu1},
+  pdfauthor={Jiancheng Gu},
   pdflang={en-EN},
@@
 \title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration}
-\author{Jiancheng Gu\textsuperscript{1}}
+\author{Jiancheng Gu\textsuperscript{}}
 \date{}
@@
 The issue of left-behind children has caught the attention of policymakers and legislators.
-In a resolution, the Council of Europe's Parliamentary Assembly (2021) expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights''.
+In a resolution, the Parliamentary Assembly of the Council of Europe expressed concern about ``the scale of this phenomenon and the long-term damage it creates'' and declared that leaving ``millions of labour migrants' children without parental care is a mass violation of human rights'' (PACE, 2021).
 
@@
 
-Social scientists have researched extensively about China's left-behind children, but the current literature still has three major shortcomings.
-The first is that most literature focuses on children left behind in rural areas while neglecting the urban counterparts.
-The National Bureau of Statistics stated that the number of urban left-behind children had been growing and expected that the trend would continue (NBS et al., 2017).
-The second shortcoming lies in sampling and research design.
-Some studies suffer from a limited sample size of less than one thousand participants or a limited geographic coverage of one to a few towns (Y.
-Liu et al., 2021; Shu, 2021; F.
-Yang et al., 2022).
-Others only estimated correlation using cross-sectional data (Akezhuoli et al., 2022; Huang et al., 2020; Jin et al., 2020).
-These studies could have employed causal inference techniques like fixed effect, matching, or inverse probability of treatment weighting.
+Social scientists have researched extensively about the education of Chinese left-behind children, but the current literature still has three major shortcomings.
+The first shortcoming lies in sampling.
+For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas (see Hu, 2019; Zhou et al., 2014).
+S.
+Wang (2023) noted that the number of urban left-behind children have been growing, and the trend is expected to continue.
+The second shortcoming is the usage of cross-sectional data (see Huang \& Gong, 2022; Y.
+Liu et al., 2022).
+Wassink and Viera (2021) argued that cross-sectional surveys merely focus on single time points, thereby failing to capture the dynamic nature of migratory journey.
+Research results would be under- or over-estimated ``depending on the timing of data collection'' (p.~1766).
 The third shortcoming lies in the measurement of outcome.
@@
 Economic resources are transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
-D.
 Yang (2008) noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
@@
 1).
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents {[}@{]}.
+Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents.
 Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
@@
 Chen (2023), caregiver-child interactions are infrequent and unstable for left-behind children.
-She showed that the loss in such interactions ``mediates almost all of the adverse effects of parental absence.'' Her conclusion was based on structural equation modeling (SEM) using a cross-sectional survey with a sample of Chinese children aged 3-15.
+She showed that the loss in such interactions ``mediates almost all of the adverse effects of parental absence.'' Her conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
 
@@
 
-I adopted \texttt{R} (version 4.2.0) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 1.3.2) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2022); \texttt{fixest} (version 0.10.4) for econometric modeling (Berge et al., 2022; Berge, 2018); \texttt{MatchIt} (version 4.4.0) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022, 2011); \texttt{modelsummary} (version 1.0.2), \texttt{vtable} (version 1.3.4), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
+I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2022); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2022; Berge, 2018); \texttt{MatchIt} (version 4.5.1) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.1), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 In this case, the propensity score estimator's variance would increase.
-This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome (Adelson et al., 2017; Bergstra et al., 2019).
+This is like the issue facing linear regression when variables are correlated with the treatment but not with the outcome (Adelson et al., 2017).
 King and Nielsen (2019) argued against PSM in general as it risks more ``imbalance, model dependence, and bias'' for already balanced data (p.~444).
@@
 Another plausibility is that family disruption precedes resource generation.
-The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs a while later (Gao et al., 2019).
+The former's negative effect befalls the left-behind child soon after parental migration, but the latter's positive effect occurs some time later (Wassink \& Viera, 2021).
 Consequently, I obtain a short-term negative effect.
@@
 Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020).
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020; Pang \& Lu, 2022).
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-akezhuoli2022}{}}%
-Akezhuoli, H., Lu, J., Zhao, G., Xu, J., Wang, M., Wang, F., Li, L., \& Zhou, X.
-(2022).
-Mother's and father's migrating in china: Differing relations to mental health and risk behaviors among left-behind children.
-\emph{Frontiers in Public Health}, \emph{10}.
-\url{https://www.frontiersin.org/article/10.3389/fpubh.2022.894741}
-
 \leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
@@
 Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bergstra2019}{}}%
-Bergstra, S.
-A., Sepriano, A., Ramiro, S., \& Landewé, R.
-(2019).
-Three handy tips and a practical guide to improve your propensity score models.
-\emph{RMD Open}, \emph{5}(1), e000953.
-\url{https://doi.org/10.1136/rmdopen-2019-000953}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-botev2019}{}}%
-Botev, J., Égert, B., Smidova, Z., \& Turner, D. (2019). \emph{A new macroeconomic measure of human capital with strong empirical links to productivity}. \url{https://doi.org/10.1787/d12d7305-en}
+Botev, J., Égert, B., Smidova, Z., \& Turner, D.
+(2019).
+\emph{A new macroeconomic measure of human capital with strong empirical links to productivity}.
+OECD Economics Department Working Papers.
+\url{https://doi.org/10.1787/d12d7305-en}
 
@@
 Left-Behind Children{'}s Cognitive Development in China: Gain in Financial Capital Versus Loss in Parental Capital.
-\emph{Sociological Perspectives}, 073112142211450.
+\emph{Sociological Perspectives}, In Press.
 \url{https://doi.org/10.1177/07311214221145059}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gao2019}{}}%
-Gao, Y., Bai, Y., Ma, Y., \& Shi, Y.
-(2019).
-Parental Migration{'}s Effects on the Academic and Non-Academic Performance of Left-Behind Children in Rural China.
-\emph{China Economist}, \emph{14}(5), 67--80.
-\url{https://doi.org/10.19602/j.chinaeconomist.2019.9.07}
-
 \leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-huang2020}{}}%
-Huang, Y., Liang, Z., Song, Q., \& Tao, R.
-(2020).
-Family Arrangements and Children's Education Among Migrants: A Case Study of China.
-\emph{International Journal of Urban and Regional Research}, \emph{44}(3), 484--504.
-\url{https://doi.org/10.1111/1468-2427.12649}
+\leavevmode\vadjust pre{\hypertarget{ref-hu2019}{}}%
+Hu, S.
+(2019).
+{``}It{'}s for Our Education{''}:~Perception of Parental Migration and Resilience Among Left-behind Children in Rural China.
+\emph{Social Indicators Research}, \emph{145}(2), 641--661.
+\url{https://doi.org/10.1007/s11205-017-1725-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-huang2022}{}}%
+Huang, Y., \& Gong, H.
+(2022).
+Educational Expectations of Left-behind Children in China: Determinants and Gender Differences.
+\emph{Applied Research in Quality of Life}, \emph{17}(5), 2501--2523.
+\url{https://doi.org/10.1007/s11482-021-09987-7}
 
@@
 Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality}. CRC Press. \url{https://theeffectbook.net/index.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jin2020}{}}%
-Jin, X., Chen, W., Sun, I.
-Y., \& Liu, L.
-(2020).
-Physical health, school performance and delinquency: A comparative study of left-behind and non-left-behind children in rural China.
-\emph{Child Abuse \& Neglect}, \emph{109}, 104707.
-\url{https://doi.org/10.1016/j.chiabu.2020.104707}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-liu2021a}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-liu2021}{}}%
 Liu, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-liu2021}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
 Liu, Y., Deng, Z., \& Katz, I.
-(2021).
+(2022).
 Transmission of Educational Outcomes Across Three Generations: Evidence From Migrant Workers{'} Children in China.
-\emph{Applied Research in Quality of Life}.
+\emph{Applied Research in Quality of Life}, \emph{17}(5), 2563--2595.
 \url{https://doi.org/10.1007/s11482-021-09990-y}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
-NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in Chinese{]}}. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}
+NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in Chinese{]}}. National Bureau of Statistics. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}
 
@@
 \emph{Population Status of Children in China in 2015: Facts and Figures}.
+National Bureau of Statistics, United Nations Children's Fund, United Nations Population Fund.
 \url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nsrc}{}}%
-NSRC. (n.d.). \emph{Overview-china education panel survey}. \url{http://ceps.ruc.edu.cn/English/Overview/Overview.htm}
+NSRC. (n.d.). \emph{Overview-china education panel survey}. National Survey Research Center. \url{http://ceps.ruc.edu.cn/English/Overview/Overview.htm}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pace2021}{}}%
+PACE. (2021). \emph{Resolution 2366: Impact of labour migration on {``}left-behind{''} children}. Parliamentary Assembly of the Council of Europe. \url{https://pace.coe.int/en/files/29077/html}
+
 \leavevmode\vadjust pre{\hypertarget{ref-pan2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-parliamentaryassembly2021}{}}%
-Parliamentary Assembly. (2021). \emph{Resolution 2366: Impact of labour migration on {``}left-behind{''} children}. \url{https://pace.coe.int/en/files/29077/html}
+\leavevmode\vadjust pre{\hypertarget{ref-pang2022}{}}%
+Pang, X., \& Lu, Z.
+(2022).
+Internal Migration and the Educational and Social Impacts on Children Left Behind in Rural China.
+In A.
+North \& E.
+Chase (Eds.), \emph{Education, Migration and Development: Critical Perspectives in a Moving World} (pp.
+189--210).
+Bloomsbury Academic.
+\url{https://doi.org/10.5040/9781350257573}
 
@@
 \emph{Report on children left behind: Between labour migration, institutional standards, and extended family}.
+The Council of Europe.
 \url{https://coe-romact.org/sites/default/files/romact_resources_files/Report_Children\%20Left\%20Behind_ENG_0\%20\%281\%29.pdf}
@@
 \url{https://doi.org/10.1016/j.ssresearch.2021.102576}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shu2021}{}}%
-Shu, B.
-(2021).
-Parental Migration, Parental Emotional Support, and Adolescent Children{'}s Life Satisfaction in Rural China: The Roles of Parent and Child Gender.
-\emph{Journal of Family Issues}, \emph{42}(8), 1663--1705.
-\url{https://doi.org/10.1177/0192513X20946345}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wang2023}{}}%
+Wang, S.
+(2023).
+Constructing children's psychological well-being: Sources of resilience for children left behind in Northeast China.
+\emph{International Migration}, In Press.
+\url{https://doi.org/10.1111/imig.13113}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
@@
 \url{https://doi.org/10.1177/1868102619894739}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wassink2021}{}}%
+Wassink, J.
+T., \& Viera, J.
+A.
+(2021).
+Does parental migration during childhood affect children's lifetime educational attainment?
+Evidence from mexico.
+\emph{Demography}, \emph{58}(5), 1765--1792.
+\url{https://doi.org/10.1215/00703370-9411336}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-yang2022}{}}%
-Yang, F., Wang, Z., Liu, J., \& Tang, S.
-(2022).
-The Effect of Social Interaction on Rural Children{'}s Self-identity: an Empirical Study Based on Survey Data from Jintang County, China.
-\emph{Child Indicators Research}, \emph{15}(3), 839--861.
-\url{https://doi.org/10.1007/s12187-021-09887-0}
-
 \leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
@@
 \url{https://doi.org/10.1080/13621025.2018.1531824}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhou2014}{}}%
+Zhou, M., Murphy, R., \& Tao, R.
+(2014).
+Effects of Parents' Migration on the Education of Children Left Behind in Rural China.
+\emph{Population and Development Review}, \emph{40}(2), 273--292.
+\url{https://doi.org/10.1111/j.1728-4457.2014.00673.x}
 

### 2023-03-06 MScThesisText.Rmd
adjusted references

@@
   - name          : "Jiancheng Gu"
-    #affiliation   : "1"
+    affiliation   : "1"
 
@@
 
+note: |
+  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)
 authornote: |
@@
 The internal migration stemmed from the neoliberal economic regime.
-Scholars like @duckett2020 and @zhan2020 argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
+Scholars like @duckett2020 and @zhang2018 argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
 In the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@gu2022].
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@wan2022].
 Migrant workers have organized petitions, strikes, and protests.
@@
 How does China counter the issue of labor migration and left-behind children?
-According to @wang2020 and @zhang2018, the government has gradually liberalized the multilevel citizenship scheme.
+According to @wang2020 and @dong2020, the government has gradually liberalized the multilevel citizenship scheme.
 It has introduced residence permit for internal migrants as the basis for social entitlements.
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment [@dong2020].
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
 This parallels how European states differentially incorporate foreign immigrants into national welfare regimes [@pasquali2022].
@@
 
-Scholars like @murphy2020 noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+@murphy2020 noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
 Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
@@
 Eight out of ten parents wished that their children complete university education.
-Scholars like @willis2019 explained this pattern with the Chinese social norms and cultural traditions.
+Scholars like @luo2013 and @ng2020 explained this pattern with the Chinese social norms and cultural traditions.
 In ancient China, the Confucian teaching emphasized the cultivation of personhood through learning, diligence, and persistence.
@@
 This thesis infers the causal relation between parents' migration and their stay-behind children's educational performance in the short run.
-I build difference-in-differences models with fixed-effect to analyze data from the 2013-2014 and 2014-2015 rounds of China Education Panel Survey.
-Results suggest that parental migration is, in the short run, negatively associated with children's educational performance.
+Using the 2013-2014 and 2014-2015 rounds of China Education Panel Survey, I build difference-in-differences regression models with fixed-effect and propensity score matching.
+Results suggest that in the short run, parental migration reduces children's educational performance.
 This is evidenced by a 1.2 points drop in academic exam grades and a 2.5 points drop in cognitive test scores.
@@
 The discrepancy could be attributed their study's location, a Northwestern province with grinding poverty.
-There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.
-1165).
-In my nationwide sample the reverse may hold.
-The households may be better off, so labor migration's additional income fails to compensate for the care deficit.
+As @chen2023 stated, household economic status conditions the income effect.
+Only for children in relative impoverishment is a greater amount of remittance associated with better cognitive abilities.
+This association does not hold for children in better-off households.
 Another plausibility is that family disruption precedes resource generation.

### 2023-03-06 MScThesisText.tex
adjusted references

@@
   pdftitle={Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration},
-  pdfauthor={Jiancheng Gu},
+  pdfauthor={Jiancheng Gu1},
   pdflang={en-EN},
@@
 \title{Newly Left-Behind Children's Educational Performance Drops Slightly After Parental Migration}
-\author{Jiancheng Gu\textsuperscript{}}
+\author{Jiancheng Gu\textsuperscript{1}}
 \date{}
@@
 \affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Social Sciences, Vrije Universiteit Amsterdam}
+
+\note{
+
+An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)
+
+}
 
@@
 The internal migration stemmed from the neoliberal economic regime.
-Scholars like Duckett (2020) and Zhan (2020) argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
+Scholars like Duckett (2020) and Zhang (2018) argued that China conforms to the neoliberal trend, extending the logic of the market to other domains of human life.
 In the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Gu, 2022b).
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Wan \& Vickers, 2022).
 Migrant workers have organized petitions, strikes, and protests.
@@
 According to X.
-Wang (2020) and Zhang (2018), the government has gradually liberalized the multilevel citizenship scheme.
+Wang (2020) and Dong and Goodburn (2020), the government has gradually liberalized the multilevel citizenship scheme.
 It has introduced residence permit for internal migrants as the basis for social entitlements.
 First-tier cities like Beijing and Shanghai have brought forth a point-based system to grant hukou to newcomers.
-The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment (Dong \& Goodburn, 2020).
+The system's evaluation criteria include in-demand talents and skills, educational and professional qualifications, and consecutive years of employment and tax-payment.
 This parallels how European states differentially incorporate foreign immigrants into national welfare regimes (Pasquali, 2022).
@@
 He found that stay-behind children's education benefited from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
-In China, Gu (2022a) interviewed migrant workers and their family members.
+In China, Gu (2022) interviewed migrant workers and their family members.
 She found that they aspire to move up the social ladder; Such aspiration translates into ``intensive and all-out investment in children's education'' (p.~526).
@@
 
-Scholars like Murphy (2020) noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Murphy (2020) noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
 Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
@@
 Eight out of ten parents wished that their children complete university education.
-Scholars like Willis (2019) explained this pattern with the Chinese social norms and cultural traditions.
+Scholars like Luo et al.
+(2013) and Ng and Wei (2020) explained this pattern with the Chinese social norms and cultural traditions.
 In ancient China, the Confucian teaching emphasized the cultivation of personhood through learning, diligence, and persistence.
@@
 The discrepancy could be attributed their study's location, a Northwestern province with grinding poverty.
-There, the positive impact of resource generation probably outweighs the negative impact of family disruption, resulting in an overall positive effect (p.~1165).
-In my nationwide sample the reverse may hold.
-The households may be better off, so labor migration's additional income fails to compensate for the care deficit.
+As C.
+Chen (2023) stated, household economic status conditions the income effect.
+Only for children in relative impoverishment is a greater amount of remittance associated with better cognitive abilities.
+This association does not hold for children in better-off households.
 Another plausibility is that family disruption precedes resource generation.
@@
 Gu, X.
-(2022a).
+(2022).
 Sacrifice and Indebtedness: The Intergenerational Contract in Chinese Rural Migrant Families.
@@
 \url{https://doi.org/10.1177/0192513X21993890}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gu2022}{}}%
-Gu, X.
-(2022b).
-{`}Save the children!{'}: Governing left-behind children through family in China{'}s Great Migration.
-\emph{Current Sociology}, \emph{70}(4), 513--538.
-\url{https://doi.org/10.1177/0011392120985874}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wan2022}{}}%
+Wan, Y., \& Vickers, E.
+(2022).
+Towards Meritocratic Apartheid?
+Points Systems and Migrant Access to China's Urban Public Schools.
+\emph{The China Quarterly}, \emph{249}, 210--238.
+\url{https://doi.org/10.1017/S0305741021000990}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wang2019}{}}%
@@
 Wickham, H., Miller, E., \& Smith, D. (2022). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}
-
-\leavevmode\vadjust pre{\hypertarget{ref-willis2019}{}}%
-Willis, P. (2019). \emph{Being Modern in China: A Western Cultural Analysis of Modernity, Tradition and Schooling in China Today}. Polity.
 

### 2023-03-23 MScThesisText.Rmd
Adjust sampling and reference entries

@@
 library("modelsummary")
-options(modelsummary_get="broom") 
 r_refs("references.bib")
@@
 In the 1980s, the ruling communist party ditched the planned economy, initiated market reforms, and opened up the country.
-Since then, China has integrated in the global economy and contributed substantial growth to it.
+Since then, China has integrated in the global economy and recorded substantial growth.
 The economic reform and globalization have enriched the coastal cities like Shanghai and Shenzhen.
@@
 
-In other words, the hukou system binds one's citizenship rights with one's place of registry.
+In other words, the hukou system binds one's citizenship rights with one's place of registration.
 In theory, Chinese citizens can migrate freely within the country.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@wan2022].
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@zhang2018; @wan2022].
 Migrant workers have organized petitions, strikes, and protests.
-These actions often fell on deaf ears and sometimes even ended with police crackdown [@chan2019].
+These actions often fell on deaf ears and sometimes even ended with police crackdown [@chan2019; @göbel2021].
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
@@
 For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas [see @hu2019; @zhou2014].
-@wang2023 noted that the number of urban left-behind children have been growing, and the trend is expected to continue.
-The second shortcoming is the usage of cross-sectional data [see @huang2022; @liu2022].
-@wassink2021 argued that cross-sectional surveys merely focus on single time points, thereby failing to capture the dynamic nature of migratory journey.
+@alpermann2020 pointed that the Chinese government reinforces "an urban hierarchy" besides the rural-urban divide.
+In the hierarchy's bottom are small- and medium-sized cities in the inland.
+They also see parents migrating to metropolises and leaving children behind [@wang2023].
+The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue [@nbs2017].
+The second shortcoming is the usage of cross-sectional data.
+@wassink2021 argued that when cross-sectional surveys merely focus on single time points, they fail to capture the dynamic nature of migratory journey.
 Research results would be under- or over-estimated "depending on the timing of data collection" (p.
@@
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
-Economic resources are transferable to human capital, which is the stock of "skills, talents, health, and expertise" in people that enhance their productivity [@goldin2016; @botev2019].
+Economic resources can help individuals acquire human capital, which is the stock of "knowledge, skills, and health that people accumulate over their lives" [@worldbank2020, p.1].
 @yang2008 noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
-This subsequently boosted children's school enrollment and educational expenditure.
-@cebotari2020 developed a fixed effect model with longitudinal data collected in Ghana.
-He found that stay-behind children's education benefited from "the steady inflow of both in-kind and monetary remittances" contributed by migrant parents.
+This subsequently boosted children's school enrollment and educational spending.
+@vikram2021 performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged 8-11.
+She showed that fathers' migration was linked with increases in left-behind children's reading capability and educational expenditure (p.
+991).
 In China, @gu2022a interviewed migrant workers and their family members.
@@
 14).
-Similarly, @murphy2022 talked to left-behind adolescents at a village.
+@murphy2022 talked to left-behind adolescents at a Chinese village.
 Some of them "embraced the 'left-behind' label" because it captured their need for more parental care (p.
@@
 
-The control variables were all measured in the baseline survey.
-Covariates at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority or Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
 The lists of covariates are in Table \@ref(tab:tab-ctvar-dit) -- Table \@ref(tab:tab-ctvar-msr) in the Results section.
+At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child attends boarding school, and whether the child had skipped grade or repeated grade.
+Age, sex, and health are associated with educational performance [@gu2021a].
+Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school [@hasmath2022; @xu2018; @huang2020].
+I controlled for boarding at school because research results vary regarding the effect of boarding at school on academic performance [@liu2020a; @guo2021].
+I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family [@guo2022].
+At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
+These variables indicate family socioeconomic status, which is related to children's educational achievement [@liu2020; @young2018].
+Finally, I controlled for the level of education that the child aspires to achieve and the parental expectation on the child's level of education.
+Children's academic achievement, their educational aspiration, and their parents' expectations are interrelated [@chen2023b; @xu2021].
+All control variables were measured in the baseline survey.
 
@@
 
-I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018].
+I built a two-way fixed-effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment [@bai2018].
 The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
@@
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model [@huntington-klein2022].
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed-effect model [@huntington-klein2022].
 For student $i$ in school $j$, $\Delta score_{i,j}$ is the change in test score between the two waves of surveys, $migr_{i}$ is the treatment dummy variable, $score_{i,j;1}$ is the test score at baseline, and $S_{j}$ is the school fixed-effect.
@@
 I adopted `R` (version 4.2.2) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@berge2018; @R-fixest]; `MatchIt` (version 4.5.1) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.1), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
+This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.1) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.1), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
 
@@
   add_indent(c(2,3,5,6)) |>
-  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
   kbl(booktabs = T, caption = 'Dichotomous control variables by parental migration', row.names = F) |>
-  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
   kbl(booktabs = T, caption = 'Categorical and continuous control variables by parental migration', row.names = F) |>
-  add_header_above(c(" ", "No = 3422" = 2, "Yes = 640" = 2)) |>
+  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
 To tackle this bias, an applicable technique is matching.
-It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@costalli2021].
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@sävje2021].
 
@@
 Matching with propensity score does not guarantee a more balanced sample.
-Suppose that in the matching, some covariates are related the treatment but not to the outcome.
+Suppose that in the matching, some covariates are related to the treatment but not to the outcome.
 In this case, the propensity score estimator's variance would increase.
@@
 
-Let us consider the policy implications.
-China's multilevel citizenship scheme shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
+My research adds to the burgeoning evidence in favor of policy change on the hukou system.
+China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
 The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive [@liang2020; @meng2017].

### 2023-03-23 MScThesisText.tex
Adjust sampling and reference entries

@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Wan \& Vickers, 2022).
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Wan \& Vickers, 2022; Zhang, 2018).
 Migrant workers have organized petitions, strikes, and protests.
-These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019).
+These actions often fell on deaf ears and sometimes even ended with police crackdown (Chan, 2019; Göbel, 2021).
 Facing financial and policy constraints, many migrant laborers have to leave children in their hometowns.
@@
 For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas (see Hu, 2019; Zhou et al., 2014).
-S.
-Wang (2023) noted that the number of urban left-behind children have been growing, and the trend is expected to continue.
-The second shortcoming is the usage of cross-sectional data (see Huang \& Gong, 2022; Y.
-Liu et al., 2022).
-Wassink and Viera (2021) argued that cross-sectional surveys merely focus on single time points, thereby failing to capture the dynamic nature of migratory journey.
+Alpermann (2020) pointed that the Chinese government reinforces ``an urban hierarchy'' besides the rural-urban divide.
+In the hierarchy's bottom are small- and medium-sized cities in the inland.
+They also see parents migrating to metropolises and leaving children behind (S.
+Wang, 2023).
+The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue (NBS et al., 2017).
+The second shortcoming is the usage of cross-sectional data.
+Wassink and Viera (2021) argued that when cross-sectional surveys merely focus on single time points, they fail to capture the dynamic nature of migratory journey.
 Research results would be under- or over-estimated ``depending on the timing of data collection'' (p.~1766).
@@
 16).
-Economic resources are transferable to human capital, which is the stock of ``skills, talents, health, and expertise'' in people that enhance their productivity (Botev et al., 2019; Goldin, 2016).
+Economic resources can help individuals acquire human capital, which is the stock of ``knowledge, skills, and health that people accumulate over their lives'' (World Bank, 2020, p.
+1).
 Yang (2008) noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
-This subsequently boosted children's school enrollment and educational expenditure.
-Cebotari (2020) developed a fixed effect model with longitudinal data collected in Ghana.
-He found that stay-behind children's education benefited from ``the steady inflow of both in-kind and monetary remittances'' contributed by migrant parents.
+This subsequently boosted children's school enrollment and educational spending.
+Vikram (2021) performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged 8-11.
+She showed that fathers' migration was linked with increases in left-behind children's reading capability and educational expenditure (p.~991).
 In China, Gu (2022) interviewed migrant workers and their family members.
@@
 Some even longed to quit school to pursue a free, independent life (p.~14).
-Similarly, Murphy (2022) talked to left-behind adolescents at a village.
+Murphy (2022) talked to left-behind adolescents at a Chinese village.
 Some of them ``embraced the `left-behind' label'' because it captured their need for more parental care (p.~185), ``especially companionship and affection in daily life'' (p.~186).
@@
 To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
-The final sample size amounts to 4062.
+The final sample size amounts to 4114.
 
@@
 
-The control variables were all measured in the baseline survey.
-Covariates at children's level included age, gender, self-rated health, hukou type, number of siblings, whether the child is ethnic minority or Han Chinese, whether the child had skipped grade or repeated grade, and the level of education that the child aspires to achieve.
-At the household level, I controlled the levels of education of father and mother, the parental expectation on the child's level of education, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
 The lists of covariates are in Table~\ref{tab:tab-ctvar-dit} -- Table~\ref{tab:tab-ctvar-msr} in the Results section.
+At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child attends boarding school, and whether the child had skipped grade or repeated grade.
+Age, sex, and health are associated with educational performance (Gu \& Yeung, 2021).
+Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school (Hasmath, 2022; Huang et al., 2020; D.
+Xu et al., 2018).
+I controlled for boarding at school because research results vary regarding the effect of boarding at school on academic performance (S.
+Guo et al., 2021; M.
+Liu \& Villa, 2020).
+I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family (R.
+Guo et al., 2022).
+At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
+These variables indicate family socioeconomic status, which is related to children's educational achievement (J.
+Liu et al., 2020; Young \& Hannum, 2018).
+Finally, I controlled for the level of education that the child aspires to achieve and the parental expectation on the child's level of education.
+Children's academic achievement, their educational aspiration, and their parents' expectations are interrelated (Chen et al., 2023; Xu \& Montgomery, 2021).
+All control variables were measured in the baseline survey.
 
@@
 
-I built a two-way fixed effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment (Bai et al., 2018).
+I built a two-way fixed-effect regression model in a difference-in-differences (DID) design, utilizing parental migration as the treatment (Bai et al., 2018).
 The treatment group consists of students left behind by migrating parents at a certain point of time between the two waves of survey, and the control group includes those who do not.
@@
 The model is unadjusted as it does not adjust for additional covariates.
-Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed effect model (Huntington-Klein, 2022).
+Theoretically, it is unnecessary to include covariates that vary over group but remain constant over time; They would cancel out in the two-way fixed-effect model (Huntington-Klein, 2022).
 For student \(i\) in school \(j\), \(\Delta score_{i,j}\) is the change in test score between the two waves of surveys, \(migr_{i}\) is the treatment dummy variable, \(score_{i,j;1}\) is the test score at baseline, and \(S_{j}\) is the school fixed-effect.
@@
 I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2022); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2022; Berge, 2018); \texttt{MatchIt} (version 4.5.1) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2022, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.1), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2021; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.1) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.1), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 Table~\ref{tab:tab-idpvar} illustrates the independent variables, namely the migration status reported in the wave two survey.
-All 4062 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
+All 4114 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
 I call these students ``newly left-behind children'' and their households ``new migration households.'' In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
@@
 Parental Migration & & \\
-\ldots{} No & 3422 & 84.2\% \\
-\ldots{} Yes & 640 & 15.8\% \\
+\ldots{} No & 3465 & 84\% \\
+\ldots{} Yes & 649 & 16\% \\
 Parental Migration Type & & \\
-\ldots{} Both Parents at Home & 3422 & 84.2\% \\
-\ldots{} Both Parents Migrated & 130 & 3.2\% \\
-\ldots{} Only Father Migrated & 252 & 6.2\% \\
-\ldots{} Only Mother Migrated & 258 & 6.4\% \\
+\ldots{} Both Parents at Home & 3465 & 84\% \\
+\ldots{} Both Parents Migrated & 132 & 3\% \\
+\ldots{} Only Father Migrated & 256 & 6\% \\
+\ldots{} Only Mother Migrated & 261 & 6\% \\
 \bottomrule()
@@
 \cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3422} & \multicolumn{2}{c}{Yes = 640} \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3465} & \multicolumn{2}{c}{Yes = 649} \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
@@
 \midrule
-Cognitive test score difference & 11.48 & 19.85 & 9.58 & 20.71 & p=0.028*\\
-\hspace{1em}Wave 1 score & 56.75 & 16.63 & 55.98 & 16.62 & p=0.282\\
-\hspace{1em}Wave 2 score & 68.22 & 18.45 & 65.56 & 19.54 & p<0.001***\\
-Academic exam score difference & -2.78 & 10.91 & -4 & 11.78 & p=0.01**\\
-\hspace{1em}Wave 1 score & 71.21 & 16.37 & 70.4 & 16.93 & p=0.256\\
+Cognitive test score difference & 11 & 20 & 9.6 & 21 & p=0.027*\\
+\hspace{1em}Wave 1 score & 57 & 17 & 56 & 17 & p=0.312\\
+\hspace{1em}Wave 2 score & 68 & 18 & 66 & 20 & p=0.001**\\
+Academic exam score difference & -2.8 & 11 & -4.1 & 12 & p=0.007**\\
+\hspace{1em}Wave 1 score & 71 & 16 & 70 & 17 & p=0.24\\
 \addlinespace
-\hspace{1em}Wave 2 score & 68.43 & 18.28 & 66.4 & 19.49 & p=0.011*\\
+\hspace{1em}Wave 2 score & 68 & 18 & 66 & 20 & p=0.008**\\
 \bottomrule
@@
 \midrule
-child.is.girl &  &  &  &  & X2=12.261***\\
-... 0 & 1637 & 48\% & 355 & 55\% & \\
-... 1 & 1785 & 52\% & 285 & 45\% & \\
-child.has.rural.hukou &  &  &  &  & X2=1.09\\
-... 0 & 1887 & 55\% & 338 & 53\% & \\
+child.is.girl &  &  &  &  & X2=12.716***\\
+... 0 & 1660 & 48\% & 361 & 56\% & \\
+... 1 & 1805 & 52\% & 288 & 44\% & \\
+child.has.rural.hukou &  &  &  &  & X2=1.106\\
+... 0 & 1912 & 55\% & 343 & 53\% & \\
 \addlinespace
-... 1 & 1535 & 45\% & 302 & 47\% & \\
-child.in.boarding.school &  &  &  &  & X2=4.49*\\
-... 0 & 2470 & 72\% & 435 & 68\% & \\
-... 1 & 952 & 28\% & 205 & 32\% & \\
-child.is.ethnic.minority &  &  &  &  & X2=0.514\\
+... 1 & 1553 & 45\% & 306 & 47\% & \\
+child.in.boarding.school &  &  &  &  & X2=3.876*\\
+... 0 & 2500 & 72\% & 443 & 68\% & \\
+... 1 & 965 & 28\% & 206 & 32\% & \\
+child.is.ethnic.minority &  &  &  &  & X2=0.585\\
 \addlinespace
-... 0 & 3190 & 93\% & 591 & 92\% & \\
-... 1 & 232 & 7\% & 49 & 8\% & \\
-child.had.skipped.grade &  &  &  &  & X2=0.056\\
-... 0 & 3386 & 99\% & 632 & 99\% & \\
+... 0 & 3230 & 93\% & 599 & 92\% & \\
+... 1 & 235 & 7\% & 50 & 8\% & \\
+child.had.skipped.grade &  &  &  &  & X2=0.054\\
+... 0 & 3429 & 99\% & 641 & 99\% & \\
 ... 1 & 36 & 1\% & 8 & 1\% & \\
 \addlinespace
-child.had.repeated.grade &  &  &  &  & X2=10.485**\\
-... 0 & 3121 & 91\% & 557 & 87\% & \\
-... 1 & 301 & 9\% & 83 & 13\% & \\
-child.went.to.preschool &  &  &  &  & X2=0.923\\
-... 0 & 523 & 15\% & 108 & 17\% & \\
+child.had.repeated.grade &  &  &  &  & X2=12.906***\\
+... 0 & 3160 & 91\% & 562 & 87\% & \\
+... 1 & 305 & 9\% & 87 & 13\% & \\
+child.went.to.preschool &  &  &  &  & X2=0.826\\
+... 0 & 530 & 15\% & 109 & 17\% & \\
 \addlinespace
-... 1 & 2899 & 85\% & 532 & 83\% & \\
+... 1 & 2935 & 85\% & 540 & 83\% & \\
 parent.has.white.collar.job &  &  &  &  & X2=0.001\\
-... 0 & 2705 & 79\% & 505 & 79\% & \\
-... 1 & 717 & 21\% & 135 & 21\% & \\
-home.has.internet &  &  &  &  & X2=12.967***\\
+... 0 & 2739 & 79\% & 512 & 79\% & \\
+... 1 & 726 & 21\% & 137 & 21\% & \\
+home.has.internet &  &  &  &  & X2=13.27***\\
 \addlinespace
-... 0 & 1054 & 31\% & 244 & 38\% & \\
-... 1 & 2368 & 69\% & 396 & 62\% & \\
+... 0 & 1064 & 31\% & 247 & 38\% & \\
+... 1 & 2401 & 69\% & 402 & 62\% & \\
 \bottomrule
@@
 \midrule
-child.age & 12.45 & 0.63 & 12.51 & 0.73 & F=4.263*\\
-child.number.of.sibling & 0.58 & 0.74 & 0.66 & 0.82 & F=4.896*\\
-child.health & 4.17 & 0.87 & 4.14 & 0.9 & F=0.576\\
-child.education.aspiration & 3.96 & 1.12 & 3.93 & 1.19 & F=0.522\\
-mother.education.level & 1.53 & 1.17 & 1.57 & 1.25 & F=0.468\\
+child.age & 12 & 0.63 & 13 & 0.73 & F=5.008*\\
+child.number.of.sibling & 0.58 & 0.74 & 0.66 & 0.82 & F=5.242*\\
+child.health & 4.2 & 0.87 & 4.1 & 0.89 & F=0.575\\
+child.education.aspiration & 4 & 1.1 & 3.9 & 1.2 & F=0.496\\
+mother.education.level & 1.5 & 1.2 & 1.6 & 1.3 & F=0.48\\
 \addlinespace
-father.education.level & 1.72 & 1.18 & 1.75 & 1.21 & F=0.274\\
-parent.expectation & 4.19 & 0.91 & 4.14 & 0.95 & F=1.627\\
-home.extracurricular.book & 3.42 & 1.18 & 3.32 & 1.28 & F=3.392\\
-home.economic.resource & 2.87 & 0.55 & 2.84 & 0.57 & F=1.52\\
+father.education.level & 1.7 & 1.2 & 1.8 & 1.2 & F=0.413\\
+parent.expectation & 4.2 & 0.91 & 4.1 & 0.95 & F=1.598\\
+home.extracurricular.book & 3.4 & 1.2 & 3.3 & 1.3 & F=3.82\\
+home.economic.resource & 2.9 & 0.55 & 2.8 & 0.57 & F=1.399\\
 \bottomrule
@@
 child.health & & \\
-\ldots{} 1 = Very poor & 21 & 0.5\% \\
-\ldots{} 2 = Somewhat poor & 112 & 2.8\% \\
-\ldots{} 3 = Moderate & 797 & 19.6\% \\
-\ldots{} 4 = Good & 1373 & 33.8\% \\
-\ldots{} 5 = Very good & 1759 & 43.3\% \\
+\ldots{} 1 = Very poor & 21 & 1\% \\
+\ldots{} 2 = Somewhat poor & 112 & 3\% \\
+\ldots{} 3 = Moderate & 811 & 20\% \\
+\ldots{} 4 = Good & 1391 & 34\% \\
+\ldots{} 5 = Very good & 1779 & 43\% \\
 child.education.aspiration & & \\
-\ldots{} 1 = Junior high school & 137 & 3.4\% \\
-\ldots{} 2 = Senior high school & 418 & 10.3\% \\
-\ldots{} 3 = Associate college & 615 & 15.1\% \\
-\ldots{} 4 = University & 1195 & 29.4\% \\
-\ldots{} 5 = Postgraduate & 1697 & 41.8\% \\
+\ldots{} 1 = Junior high school & 139 & 3\% \\
+\ldots{} 2 = Senior high school & 423 & 10\% \\
+\ldots{} 3 = Associate college & 622 & 15\% \\
+\ldots{} 4 = University & 1212 & 29\% \\
+\ldots{} 5 = Postgraduate & 1718 & 42\% \\
 mother.education.level & & \\
-\ldots{} 0 = Primary school and below & 702 & 17.3\% \\
-\ldots{} 1 = Junior high school & 1618 & 39.8\% \\
-\ldots{} 2 = Senior high school & 1034 & 25.5\% \\
-\ldots{} 3 = Associate college & 304 & 7.5\% \\
-\ldots{} 4 = University & 365 & 9\% \\
+\ldots{} 0 = Primary school and below & 710 & 17\% \\
+\ldots{} 1 = Junior high school & 1638 & 40\% \\
+\ldots{} 2 = Senior high school & 1048 & 25\% \\
+\ldots{} 3 = Associate college & 307 & 7\% \\
+\ldots{} 4 = University & 372 & 9\% \\
 \ldots{} 5 = Postgraduate & 39 & 1\% \\
 father.education.level & & \\
-\ldots{} 0 = Primary school and below & 441 & 10.9\% \\
-\ldots{} 1 = Junior high school & 1615 & 39.8\% \\
-\ldots{} 2 = Senior high school & 1170 & 28.8\% \\
-\ldots{} 3 = Associate college & 348 & 8.6\% \\
-\ldots{} 4 = University & 422 & 10.4\% \\
-\ldots{} 5 = Postgraduate & 66 & 1.6\% \\
+\ldots{} 0 = Primary school and below & 449 & 11\% \\
+\ldots{} 1 = Junior high school & 1634 & 40\% \\
+\ldots{} 2 = Senior high school & 1184 & 29\% \\
+\ldots{} 3 = Associate college & 350 & 9\% \\
+\ldots{} 4 = University & 430 & 10\% \\
+\ldots{} 5 = Postgraduate & 67 & 2\% \\
 parent.expectation & & \\
-\ldots{} 1 = Junior high school & 34 & 0.8\% \\
-\ldots{} 2 = Senior high school & 254 & 6.3\% \\
-\ldots{} 3 = Associate college & 426 & 10.5\% \\
-\ldots{} 4 = University & 1569 & 38.6\% \\
-\ldots{} 5 = Postgraduate & 1779 & 43.8\% \\
+\ldots{} 1 = Junior high school & 35 & 1\% \\
+\ldots{} 2 = Senior high school & 259 & 6\% \\
+\ldots{} 3 = Associate college & 432 & 11\% \\
+\ldots{} 4 = University & 1591 & 39\% \\
+\ldots{} 5 = Postgraduate & 1797 & 44\% \\
 home.extracurricular.book & & \\
-\ldots{} 1 = Very few & 386 & 9.5\% \\
-\ldots{} 2 = Not many & 411 & 10.1\% \\
-\ldots{} 3 = Some & 1302 & 32.1\% \\
-\ldots{} 4 = Quite a few & 1104 & 27.2\% \\
-\ldots{} 5 = A great number & 859 & 21.1\% \\
+\ldots{} 1 = Very few & 389 & 9\% \\
+\ldots{} 2 = Not many & 418 & 10\% \\
+\ldots{} 3 = Some & 1322 & 32\% \\
+\ldots{} 4 = Quite a few & 1115 & 27\% \\
+\ldots{} 5 = A great number & 870 & 21\% \\
 home.economic.resource & & \\
-\ldots{} 1 = Very poor & 110 & 2.7\% \\
-\ldots{} 2 = Somewhat poor & 589 & 14.5\% \\
-\ldots{} 3 = Moderate & 3112 & 76.6\% \\
-\ldots{} 4 = Somewhat rich & 240 & 5.9\% \\
-\ldots{} 5 = Very rich & 11 & 0.3\% \\
+\ldots{} 1 = Very poor & 110 & 3\% \\
+\ldots{} 2 = Somewhat poor & 595 & 14\% \\
+\ldots{} 3 = Moderate & 3155 & 77\% \\
+\ldots{} 4 = Somewhat rich & 243 & 6\% \\
+\ldots{} 5 = Very rich & 11 & 0\% \\
 \bottomrule()
@@
 This lends support to Hypothesis 1a.
-Parental migration is linked to a 2.56 points decrease in cognitive test score.
+Parental migration is linked to a 2.54 points decrease in cognitive test score.
 Hypothesis 2a is only partially supported.
-Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.87 points) in cognitive test score than those with only mother absent (2.15 points).
+Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.81 points) in cognitive test score than those with only mother absent (2.16 points).
 The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in the appendix).
@@
 \midrule
-Migration & \num{-2.56}*** & \num{-2.15}* & \num{-2.87}* & \num{-2.96}*\\
- & (\num{0.70}) & (\num{1.06}) & (\num{1.12}) & (\num{1.39})\\
+Migration & \num{-2.54}*** & \num{-2.16}* & \num{-2.81}* & \num{-2.94}*\\
+ & (\num{0.69}) & (\num{1.05}) & (\num{1.09}) & (\num{1.36})\\
 Baseline.score & \num{-0.71}*** & \num{-0.72}*** & \num{-0.71}*** & \num{-0.72}***\\
@@
 \midrule
-Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
-R2 & \num{0.379} & \num{0.382} & \num{0.386} & \num{0.389}\\
-R2 Adj. & \num{0.361} & \num{0.363} & \num{0.367} & \num{0.369}\\
+Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
+R2 & \num{0.378} & \num{0.381} & \num{0.385} & \num{0.388}\\
+R2 Adj. & \num{0.361} & \num{0.362} & \num{0.366} & \num{0.368}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}No control variables included in these models}\\
@@
 In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
-Parental migration is associated with a drop of 1.27 points in academic exam score.
+Parental migration is associated with a drop of 1.30 points in academic exam score.
 Hypothesis 2b finds partial support.
-The exam grade of only-mother-migrated children sees a 2.11 points decrease relative to non-left-behind counterparts.
+The exam grade of only-mother-migrated children sees a 2.13 points decrease relative to non-left-behind counterparts.
 In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
@@
 \midrule
-Migration & \num{-1.27}* & \num{-2.11}* & \num{-0.88} & \num{-0.19}\\
- & (\num{0.54}) & (\num{0.91}) & (\num{0.72}) & (\num{0.72})\\
-Baseline.score & \num{0.05} & \num{0.05} & \num{0.05} & \num{0.04}\\
+Migration & \num{-1.30}* & \num{-2.13}* & \num{-0.97} & \num{-0.12}\\
+ & (\num{0.53}) & (\num{0.89}) & (\num{0.69}) & (\num{0.71})\\
+Baseline.score & \num{0.05} & \num{0.05} & \num{0.05} & \num{0.05}\\
  & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
 \midrule
-Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
-R2 & \num{0.481} & \num{0.498} & \num{0.484} & \num{0.501}\\
-R2 Adj. & \num{0.466} & \num{0.483} & \num{0.468} & \num{0.485}\\
+Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
+R2 & \num{0.481} & \num{0.498} & \num{0.484} & \num{0.500}\\
+R2 Adj. & \num{0.466} & \num{0.482} & \num{0.468} & \num{0.484}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}No control variables included in these models}\\
@@
 These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
-For students, one year older in age is associated with decreases of 2.61 points for cognitive test and of 0.44 points for academic exam.
-Preschool attendance is linked to increases of 2.33 points for cognitive test and of 1.17 points for academic exam.
+For students, one year older in age is associated with decreases of 2.67 points for cognitive test and of 0.47 points for academic exam.
+Preschool attendance is linked to increases of 2.30 points for cognitive test and of 1.12 points for academic exam.
 Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
-The coefficients are 2.34 points and 2.03 points for cognitive test, respectively; and 0.58 points and 0.77 points for academic exams, respectively.
+The coefficients are 2.35 points and 2.05 points for cognitive test, respectively; and 0.57 points and 0.78 points for academic exams, respectively.
 
@@
 Covariates that only relate to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
-Girls outperform boys by 1.62 points in academic exams, but do not show advantage in cognitive tests.
+Girls outperform boys by 1.61 points in academic exams, but do not show advantage in cognitive tests.
 Students who consider themselves healthier are associated with higher scores in academic exams.
@@
 Covariates that only relate to cognitive scores is the number of siblings.
-Having an additional sibling is associated with lower cognitive score of 0.99 points.
+Having an additional sibling is associated with lower cognitive score of 1 points.
 
@@
 To tackle this bias, an applicable technique is matching.
-It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Costalli \& Negri, 2021).
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Sävje et al., 2021).
 
@@
 \midrule
-Migration & \num{-2.64}*** & \num{-2.76}* & \num{-3.41}** & \num{-1.96}\\
- & (\num{0.74}) & (\num{1.22}) & (\num{1.25}) & (\num{1.74})\\
-Baseline.score & \num{-0.70}*** & \num{-0.74}*** & \num{-0.62}*** & \num{-0.69}***\\
- & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
+Migration & \num{-2.53}** & \num{-2.82}* & \num{-2.78}* & \num{-1.72}\\
+ & (\num{0.75}) & (\num{1.18}) & (\num{1.16}) & (\num{1.56})\\
+Baseline.score & \num{-0.72}*** & \num{-0.72}*** & \num{-0.65}*** & \num{-0.74}***\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.05})\\
 \midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.392} & \num{0.450} & \num{0.423} & \num{0.467}\\
-R2 Adj. & \num{0.363} & \num{0.384} & \num{0.356} & \num{0.352}\\
+Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
+R2 & \num{0.402} & \num{0.454} & \num{0.405} & \num{0.493}\\
+R2 Adj. & \num{0.375} & \num{0.391} & \num{0.338} & \num{0.382}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
@@
 \midrule
-Migration & \num{-1.22}* & \num{-1.65}* & \num{-1.15} & \num{0.46}\\
- & (\num{0.57}) & (\num{0.81}) & (\num{0.86}) & (\num{0.98})\\
-Baseline.score & \num{0.05}† & \num{0.07}† & \num{0.04} & \num{0.01}\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
+Migration & \num{-1.17}* & \num{-1.61}* & \num{-1.48} & \num{0.05}\\
+ & (\num{0.57}) & (\num{0.76}) & (\num{0.89}) & (\num{0.93})\\
+Baseline.score & \num{0.05} & \num{0.10}** & \num{0.06} & \num{0.02}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.04})\\
 \midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.468} & \num{0.587} & \num{0.480} & \num{0.501}\\
-R2 Adj. & \num{0.444} & \num{0.538} & \num{0.420} & \num{0.393}\\
+Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
+R2 & \num{0.462} & \num{0.590} & \num{0.453} & \num{0.513}\\
+R2 Adj. & \num{0.437} & \num{0.542} & \num{0.391} & \num{0.406}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
@@
 
-Let us consider the policy implications.
-China's multilevel citizenship scheme shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
+My research adds to the burgeoning evidence in favor of policy change on the hukou system.
+China's multilevel citizenship scheme powered by hukou shall not remain as it is, despite the small reduction of newly left-behind children's schooling performance.
 The slight drop is only the short-term consequence; The lifelong cumulative effect on children may be extensive (Liang \& Sun, 2020; Meng \& Yamauchi, 2017).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-alpermann2020}{}}%
+Alpermann, B.
+(2020).
+{China}{'}s Rural{\textendash}Urban Transformation: New Forms of Inclusion and Exclusion.
+\emph{Journal of Current Chinese Affairs}, \emph{49}(3), 259--268.
+\url{https://doi.org/10.1177/18681026211004955}
+
 \leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
@@
 (2018).
-Effect of parental migration on the academic performance of left behind children in north western china.
+Effect of parental migration on the academic performance of left behind children in north western {China}.
 \emph{The Journal of Development Studies}, \emph{54}(7), 1154--1170.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-berge2018}{}}%
-Berge, L. (2018). Efficient estimation of maximum likelihood models with multiple fixed-effects: The {R} package {FENmlm}. \emph{CREA Discussion Papers}, \emph{13}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-fixest}{}}%
-Berge, L., Krantz, S., \& McDermott, G. (2022). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
+Berge, L., Krantz, S., \& McDermott, G. (2023). \emph{Fixest: Fast fixed-effects estimations}. \url{https://CRAN.R-project.org/package=fixest}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-botev2019}{}}%
-Botev, J., Égert, B., Smidova, Z., \& Turner, D.
-(2019).
-\emph{A new macroeconomic measure of human capital with strong empirical links to productivity}.
-OECD Economics Department Working Papers.
-\url{https://doi.org/10.1787/d12d7305-en}
-
 \leavevmode\vadjust pre{\hypertarget{ref-botezat2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cebotari2020}{}}%
-Cebotari, V.
-(2020).
-Migration, remittances, and child education in ghana.
-Evidence from a longitudinal study.
-In M.
-Konte \& L.
-Mously Mbaye (Eds.), \emph{Migration, remittances, and sustainable development in africa} (pp.
-99--116).
-Routledge.
-\url{https://doi.org/10.4324/9780429288814-8}
-
 \leavevmode\vadjust pre{\hypertarget{ref-chan2019}{}}%
-Chan, J. (2019). State and labor in China, 1978{\textendash}2018. \emph{Journal of Labor and Society}, \emph{22}(2), 461--475. \url{https://doi.org/10.1111/wusa.12408}
+Chan, J. (2019). State and labor in {China}, 1978{\textendash}2018. \emph{Journal of Labor and Society}, \emph{22}(2), 461--475. \url{https://doi.org/10.1111/wusa.12408}
 
@@
 (2019).
-Parental migration, educational achievement, and mental health of junior high school students in rural China.
-\emph{China Economic Review}, \emph{54}, 337--349.
+Parental migration, educational achievement, and mental health of junior high school students in rural {China}.
+\emph{{China} Economic Review}, \emph{54}, 337--349.
 \url{https://doi.org/10.1016/j.chieco.2019.01.007}
@@
 (2023).
-Left-Behind Children{'}s Cognitive Development in China: Gain in Financial Capital Versus Loss in Parental Capital.
+Left-Behind Children{'}s Cognitive Development in {China}: Gain in Financial Capital Versus Loss in Parental Capital.
 \emph{Sociological Perspectives}, In Press.
@@
 Long Live Keju!
-The Persistent Effects of China{'}s Civil Examination System.
+The Persistent Effects of {China}{'}s Civil Examination System.
 \emph{The Economic Journal}, \emph{130}(631), 2030--2064.
 \url{https://doi.org/10.1093/ej/ueaa043}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2023b}{}}%
+Chen, X., Allen, J.
+L., Flouri, E., Cao, X., \& Hesketh, T.
+(2023).
+Parent-Child Communication About Educational Aspirations: Experiences of Adolescents in Rural {China}.
+\emph{Journal of Child and Family Studies}.
+\url{https://doi.org/10.1007/s10826-023-02554-8}
 
@@
 (2009).
-Effect of Migration on Children's Educational Performance in Rural China.
+Effect of Migration on Children's Educational Performance in Rural {China}.
 \emph{Comparative Economic Studies}, \emph{51}(3), 323--343.
@@
 (2019).
-Father migration and mother migration: Different implications for social, school, and psychological adjustment of left-behind children in rural china.
-\emph{Journal of Contemporary China}, \emph{28}(120), 849--863.
+Father migration and mother migration: Different implications for social, school, and psychological adjustment of left-behind children in rural {China}.
+\emph{Journal of Contemporary {China}}, \emph{28}(120), 849--863.
 \url{https://doi.org/10.1080/10670564.2019.1594100}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-duxe9murger2015}{}}%
-Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in china. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
+Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in {China}. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
 
@@
 (2020).
-Residence Permits and Points Systems: New Forms of Educational and Social Stratification in Urban China.
-\emph{Journal of Contemporary China}, \emph{29}(125), 647--666.
+Residence Permits and Points Systems: New Forms of Educational and Social Stratification in Urban {China}.
+\emph{Journal of Contemporary {China}}, \emph{29}(125), 647--666.
 \url{https://doi.org/10.1080/10670564.2019.1704997}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-duckett2020}{}}%
-Duckett, J. (2020). Neoliberalism, Authoritarian Politics and Social Policy in China. \emph{Development and Change}, \emph{51}(2), 523--539. \url{https://doi.org/10.1111/dech.12568}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldin2016}{}}%
-Goldin, C. (2016). Human Capital. In C. Diebolt \& M. Haupert (Eds.), \emph{Handbook of Cliometrics} (pp. 55--86). Springer. \url{https://doi.org/10.1007/978-3-642-40406-1_23}
+Duckett, J. (2020). Neoliberalism, Authoritarian Politics and Social Policy in {China}. \emph{Development and Change}, \emph{51}(2), 523--539. \url{https://doi.org/10.1111/dech.12568}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guxf6bel2021}{}}%
+Göbel, C. (2021). The political logic of protest repression in {China}. \emph{Journal of Contemporary {China}}, \emph{30}(128), 169--185. \url{https://doi.org/10.1080/10670564.2020.1790897}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gu2021a}{}}%
+Gu, X., \& Yeung, W.
+J.
+(2021).
+Why do Chinese adolescent girls outperform boys in achievement tests?
+\emph{Chinese Journal of Sociology}, \emph{7}(2), 109--137.
+\url{https://doi.org/10.1177/2057150X211006586}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guo2022}{}}%
+Guo, R., Yi, J., \& Zhang, J. (2022). The Child Quantity{\textendash}Quality Trade-off. \emph{IZA Discussion Papers}. \url{https://doi.org/10.2139/ssrn.4114809}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guo2021}{}}%
+Guo, S., Li, L., Sun, Y., Houang, R., \& Schmidt, W.
+H.
+(2021).
+Does boarding benefit the mathematics achievement of primary and middle school students?
+Evidence from {China}.
+\emph{Asia Pacific Journal of Education}, \emph{41}(1), 16--38.
+\url{https://doi.org/10.1080/02188791.2020.1760081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hasmath2022}{}}%
+Hasmath, R. (2022, August). The Operations of Contemporary Han Chinese Privilege. \emph{American Sociological Association Annual Meeting}. \url{https://doi.org/10.2139/ssrn.3671496}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ho2011}{}}%
@@
 Ho, D., Imai, K., King, G., Stuart, E., Whitworth, A., \& Greifer, N.
-(2022).
+(2023).
 \emph{MatchIt: Nonparametric preprocessing for parametric causal inference}.
@@
 (2019).
-Alone and {``}left behind{''}: A case study of {``}left-behind children{''} in rural china.
+Alone and {``}left behind{''}: A case study of {``}left-behind children{''} in rural {China}.
 \emph{Cogent Education}, \emph{6}(1), 1654236.
@@
 (2019).
-{``}It{'}s for Our Education{''}:~Perception of Parental Migration and Resilience Among Left-behind Children in Rural China.
+{``}It{'}s for Our Education{''}:~Perception of Parental Migration and Resilience Among Left-behind Children in Rural {China}.
 \emph{Social Indicators Research}, \emph{145}(2), 641--661.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-huang2022}{}}%
-Huang, Y., \& Gong, H.
-(2022).
-Educational Expectations of Left-behind Children in China: Determinants and Gender Differences.
-\emph{Applied Research in Quality of Life}, \emph{17}(5), 2501--2523.
-\url{https://doi.org/10.1007/s11482-021-09987-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-vtable}{}}%
-Huntington-Klein, N. (2021). \emph{Vtable: Variable table for variable documentation}. \url{https://CRAN.R-project.org/package=vtable}
+\leavevmode\vadjust pre{\hypertarget{ref-huang2020}{}}%
+Huang, Y., Liang, Z., Song, Q., \& Tao, R.
+(2020).
+Family Arrangements and Children's Education Among Migrants: A Case Study of {China}.
+\emph{International Journal of Urban and Regional Research}, \emph{44}(3), 484--504.
+\url{https://doi.org/10.1111/1468-2427.12649}
 
@@
 Huntington-Klein, N. (2022). \emph{The Effect: An Introduction to Research Design and Causality}. CRC Press. \url{https://theeffectbook.net/index.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-vtable}{}}%
+Huntington-Klein, N. (2023). \emph{Vtable: Variable table for variable documentation}. \url{https://CRAN.R-project.org/package=vtable}
 
@@
 (2021).
-Migration and children in China: a review and future research agenda.
+Migration and children in {China}: a review and future research agenda.
 \emph{Chinese Sociological Review}, \emph{53}(3), 312--331.
@@
 (2020).
-The lasting impact of parental migration on children's education and health outcomes: The case of china.
+The lasting impact of parental migration on children's education and health outcomes: The case of {China}.
 \emph{Demographic Research}, \emph{S28}(9), 217--244.
 \url{https://doi.org/10.4054/DemRes.2020.43.9}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2020}{}}%
+Liu, J., Peng, P., \& Luo, L.
+(2020).
+The Relation Between Family Socioeconomic Status and Academic Achievement in {China}: A Meta-analysis.
+\emph{Educational Psychology Review}, \emph{32}(1), 49--76.
+\url{https://doi.org/10.1007/s10648-019-09494-0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liu2020a}{}}%
+Liu, M., \& Villa, K.
+M.
+(2020).
+Solution or isolation: Is boarding school a good solution for left-behind children in rural {China}?
+\emph{{China} Economic Review}, \emph{61}, 101456.
+\url{https://doi.org/10.1016/j.chieco.2020.101456}
 
@@
 (2021).
-Leveraging machine learning methods to estimate heterogeneous effects: Father absence in china as an example.
+Leveraging machine learning methods to estimate heterogeneous effects: Father absence in {China} as an example.
 \emph{Chinese Sociological Review}, \emph{54}(3), 223--251.
 \url{https://doi.org/10.1080/21620555.2021.1948828}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
-Liu, Y., Deng, Z., \& Katz, I.
-(2022).
-Transmission of Educational Outcomes Across Three Generations: Evidence From Migrant Workers{'} Children in China.
-\emph{Applied Research in Quality of Life}, \emph{17}(5), 2563--2595.
-\url{https://doi.org/10.1007/s11482-021-09990-y}
 
@@
 No longer left-behind: The impact of return migrant parents on children's performance.
-\emph{China Economic Review}, \emph{49}, 184--196.
+\emph{{China} Economic Review}, \emph{49}, 184--196.
 \url{https://doi.org/10.1016/j.chieco.2017.06.004}
@@
 (2017).
-Children of migrants: The cumulative impact of parental migration on children{'}s education and health outcomes in china.
+Children of migrants: The cumulative impact of parental migration on children{'}s education and health outcomes in {China}.
 \emph{Demography}, \emph{54}(5), 1677--1714.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2022}{}}%
-Murphy, R. (2022). What does {`}left behind{'} mean to children living in migratory regions in rural China? \emph{Geoforum}, \emph{129}, 181--190. \url{https://doi.org/10.1016/j.geoforum.2022.01.012}
+Murphy, R.
+(2022).
+What does {`}left behind{'} mean to children living in migratory regions in rural {China}?
+\emph{Geoforum}, \emph{129}, 181--190.
+\url{https://doi.org/10.1016/j.geoforum.2022.01.012}
 
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
-Murphy, R. (2020). \emph{The children of china{'}s great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
+Murphy, R. (2020). \emph{The children of {China}{'}s great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
 
@@
 (2017).
-\emph{Population Status of Children in China in 2015: Facts and Figures}.
+\emph{Population Status of Children in {China} in 2015: Facts and Figures}.
 National Bureau of Statistics, United Nations Children's Fund, United Nations Population Fund.
-\url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20China\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
+\url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20\%7BChina\%7D\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nsrc}{}}%
-NSRC. (n.d.). \emph{Overview-china education panel survey}. National Survey Research Center. \url{http://ceps.ruc.edu.cn/English/Overview/Overview.htm}
+NSRC. (n.d.). \emph{Overview-{China} education panel survey}. National Survey Research Center. \url{http://ceps.ruc.edu.cn/English/Overview/Overview.htm}
 
 \leavevmode\vadjust pre{\hypertarget{ref-oecd2016}{}}%
-OECD. (2016). \emph{Education in china: A snapshot}. \url{https://www.oecd.org/china/Education-in-China-a-snapshot.pdf}
+OECD. (2016). \emph{Education in {China}: A snapshot}. \url{https://www.oecd.org/\%7BChina\%7D/Education-in-\%7BChina\%7D-a-snapshot.pdf}
 
@@
 (2022).
-Internal Migration and the Educational and Social Impacts on Children Left Behind in Rural China.
+Internal Migration and the Educational and Social Impacts on Children Left Behind in Rural {China}.
 In A.
@@
 (2022).
-Migration regimes and the governance of citizenship: a comparison between legal categories of migration in China and in the European Union.
+Migration regimes and the governance of citizenship: a comparison between legal categories of migration in {China} and in the European Union.
 \emph{Journal of Chinese Governance}, \emph{7}(4), 633--657.
@@
 (2018).
-Migrant Mothering in Transition: A Qualitative Study of the Maternal Narratives and Practices of Two Generations of Rural-Urban Migrant Mothers in Southern China.
+Migrant Mothering in Transition: A Qualitative Study of the Maternal Narratives and Practices of Two Generations of Rural-Urban Migrant Mothers in Southern {China}.
 \emph{Sex Roles}, \emph{79}(1), 16--35.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-qian2021}{}}%
-Qian, J. (2021). \emph{The Political Economy of Making and Implementing Social Policy in China}. Springer Singapore. \url{https://doi.org/10.1007/978-981-16-5025-3}
+Qian, J. (2021). \emph{The Political Economy of Making and Implementing Social Policy in {China}}. Springer Singapore. \url{https://doi.org/10.1007/978-981-16-5025-3}
 
@@
 (2018).
-Education and Equity in Rural China: A critical introduction for the rural education field.
+Education and Equity in Rural {China}: A critical introduction for the rural education field.
 \emph{Australian and International Journal of Rural Education}, \emph{28}(2).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-suxe4vje2021}{}}%
+Sävje, F., Higgins, M. J., \& Sekhon, J. S. (2021). Generalized Full Matching. \emph{Political Analysis}, \emph{29}(4), 423--447. \url{https://doi.org/10.1017/pan.2020.32}
+
 \leavevmode\vadjust pre{\hypertarget{ref-shen2021}{}}%
@@
 (2021).
-Effect pathways of informal family separation on children's outcomes: Paternal labor migration and long-term educational attainment of left-behind children in rural China.
+Effect pathways of informal family separation on children's outcomes: Paternal labor migration and long-term educational attainment of left-behind children in rural {China}.
 \emph{Social Science Research}, \emph{97}, 102576.
@@
 Venta, A., \& Cuervo, M. (2022). Attachment, loss, and related challenges in migration. \emph{Current Opinion in Psychology}, \emph{47}, 101406. \url{https://doi.org/10.1016/j.copsyc.2022.101406}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vikram2021}{}}%
+Vikram, K.
+(2021).
+Fathers{'} Migration and Academic Achievement among Left-behind Children in India: Evidence of Continuity and Change in Gender Preferences.
+\emph{International Migration Review}, \emph{55}(4), 964--998.
+\url{https://doi.org/10.1177/0197918321989279}
 
@@
 Towards Meritocratic Apartheid?
-Points Systems and Migrant Access to China's Urban Public Schools.
-\emph{The China Quarterly}, \emph{249}, 210--238.
+Points Systems and Migrant Access to {China}'s Urban Public Schools.
+\emph{The {China} Quarterly}, \emph{249}, 210--238.
 \url{https://doi.org/10.1017/S0305741021000990}
@@
 (2019).
-Academic achievement and mental health of left-behind children in rural china: A causal study on parental migration.
-\emph{China Agricultural Economic Review}, \emph{11}(4), 569--582.
+Academic achievement and mental health of left-behind children in rural {China}: A causal study on parental migration.
+\emph{{China} Agricultural Economic Review}, \emph{11}(4), 569--582.
 \url{https://doi.org/10.1108/CAER-09-2018-0194}
@@
 (2020).
-A Scoping Review of Interventions to Promote Health and Well-Being of Left-behind Children in Mainland China.
+A Scoping Review of Interventions to Promote Health and Well-Being of Left-behind Children in Mainland {China}.
 \emph{The British Journal of Social Work}, \emph{50}(5), 1419--1439.
@@
 (2023).
-Constructing children's psychological well-being: Sources of resilience for children left behind in Northeast China.
+Constructing children's psychological well-being: Sources of resilience for children left behind in Northeast {China}.
 \emph{International Migration}, In Press.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
-Wickham, H., Miller, E., \& Smith, D. (2022). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}
+Wickham, H., Miller, E., \& Smith, D. (2023). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worldbank2020}{}}%
+World Bank. (2020). \emph{The human capital index 2020 update}. \url{http://hdl.handle.net/10986/34432}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xu2018}{}}%
+Xu, D., Wu, X., Zhang, Z., \& Dronkers, J.
+(2018).
+Not a zero-sum game: Migration and child well-being in contemporary {China}.
+\emph{Demographic Research}, \emph{38}, 691--726.
+\url{https://doi.org/10.4054/DemRes.2018.38.26}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xu2021}{}}%
+Xu, Y., \& Montgomery, C.
+(2021).
+Understanding the complexity of Chinese rural parents{'} roles in their children{'}s access to elite universities.
+\emph{British Journal of Sociology of Education}, \emph{42}(4), 555--570.
+\url{https://doi.org/10.1080/01425692.2021.1872364}
 
@@
 Does It Matter Which Parent is Absent?
-Labor Migration, Parenting, and Adolescent Development in China.
+Labor Migration, Parenting, and Adolescent Development in {China}.
 \emph{Journal of Child and Family Studies}, \emph{28}(6), 1635--1649.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-young2018}{}}%
+Young, N.
+A.
+E., \& Hannum, E.
+C.
+(2018).
+Childhood Inequality in {China}: Evidence from Recent Survey Data (2012{\textendash}2014).
+\emph{The {China} Quarterly}, \emph{236}, 1063--1087.
+\url{https://doi.org/10.1017/S0305741018001303}
+
 \leavevmode\vadjust pre{\hypertarget{ref-zhan2020}{}}%
@@
 (2020).
-The moralization of philanthropy in China: NGOs, voluntarism, and the reconfiguration of social responsibility.
-\emph{China Information}, \emph{34}(1), 68--87.
+The moralization of philanthropy in {China}: NGOs, voluntarism, and the reconfiguration of social responsibility.
+\emph{{China} Information}, \emph{34}(1), 68--87.
 \url{https://doi.org/10.1177/0920203X19879593}
@@
 (2018).
-Governing neoliberal authoritarian citizenship: Theorizing hukou and the changing mobility regime in china.
+Governing neoliberal authoritarian citizenship: Theorizing hukou and the changing mobility regime in {China}.
 \emph{Citizenship Studies}, \emph{22}(8), 855--881.
@@
 (2014).
-Effects of Parents' Migration on the Education of Children Left Behind in Rural China.
+Effects of Parents' Migration on the Education of Children Left Behind in Rural {China}.
 \emph{Population and Development Review}, \emph{40}(2), 273--292.
@@
 \midrule
-Migration & \num{-2.52}*** & \num{-2.12}* & \num{-3.00}** & \num{-2.43}†\\
- & (\num{0.69}) & (\num{1.05}) & (\num{1.12}) & (\num{1.37})\\
-Baseline.score & \num{-0.79}*** & \num{-0.79}*** & \num{-0.78}*** & \num{-0.79}***\\
+Migration & \num{-2.47}*** & \num{-2.16}* & \num{-2.87}* & \num{-2.37}\\
+ & (\num{0.68}) & (\num{1.04}) & (\num{1.10}) & (\num{1.36})\\
+Baseline.score & \num{-0.78}*** & \num{-0.79}*** & \num{-0.78}*** & \num{-0.79}***\\
  & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
-child.age & \num{-2.61}*** & \num{-2.56}*** & \num{-2.53}*** & \num{-2.51}***\\
- & (\num{0.48}) & (\num{0.51}) & (\num{0.49}) & (\num{0.49})\\
-child.is.girl & \num{-0.75} & \num{-0.46} & \num{-0.73} & \num{-0.58}\\
- & (\num{0.60}) & (\num{0.65}) & (\num{0.61}) & (\num{0.64})\\
-child.health & \num{-0.28} & \num{-0.22} & \num{-0.37} & \num{-0.25}\\
- & (\num{0.33}) & (\num{0.33}) & (\num{0.35}) & (\num{0.34})\\
-child.has.rural.hukou & \num{0.13} & \num{0.47} & \num{0.22} & \num{0.67}\\
- & (\num{0.63}) & (\num{0.64}) & (\num{0.67}) & (\num{0.70})\\
-child.number.of.sibling & \num{-0.99}* & \num{-1.06}* & \num{-0.89}* & \num{-0.96}*\\
+child.age & \num{-2.67}*** & \num{-2.64}*** & \num{-2.61}*** & \num{-2.60}***\\
+ & (\num{0.47}) & (\num{0.51}) & (\num{0.48}) & (\num{0.49})\\
+child.is.girl & \num{-0.73} & \num{-0.45} & \num{-0.70} & \num{-0.59}\\
+ & (\num{0.59}) & (\num{0.64}) & (\num{0.60}) & (\num{0.63})\\
+child.health & \num{-0.27} & \num{-0.22} & \num{-0.36} & \num{-0.25}\\
+ & (\num{0.33}) & (\num{0.33}) & (\num{0.35}) & (\num{0.35})\\
+child.has.rural.hukou & \num{0.16} & \num{0.50} & \num{0.21} & \num{0.70}\\
+ & (\num{0.62}) & (\num{0.63}) & (\num{0.67}) & (\num{0.69})\\
+child.number.of.sibling & \num{-1.00}* & \num{-1.07}* & \num{-0.88}* & \num{-0.98}*\\
  & (\num{0.41}) & (\num{0.44}) & (\num{0.43}) & (\num{0.44})\\
-child.went.to.preschool & \num{2.33}** & \num{2.02}* & \num{2.21}** & \num{2.12}*\\
- & (\num{0.79}) & (\num{0.87}) & (\num{0.83}) & (\num{0.87})\\
-child.had.skipped.grade & \num{-3.83} & \num{-3.84} & \num{-4.11} & \num{-2.98}\\
- & (\num{2.64}) & (\num{2.76}) & (\num{2.73}) & (\num{2.90})\\
-child.had.repeated.grade & \num{-1.59} & \num{-2.61}* & \num{-1.92}† & \num{-1.45}\\
- & (\num{0.96}) & (\num{1.19}) & (\num{1.14}) & (\num{1.14})\\
-child.in.boarding.school & \num{1.38} & \num{1.21} & \num{1.23} & \num{0.85}\\
- & (\num{1.03}) & (\num{0.99}) & (\num{1.02}) & (\num{0.99})\\
-child.education.aspiration & \num{2.03}*** & \num{1.97}*** & \num{2.01}*** & \num{2.09}***\\
- & (\num{0.29}) & (\num{0.31}) & (\num{0.29}) & (\num{0.31})\\
-child.is.ethnic.minority & \num{1.50} & \num{1.53} & \num{1.01} & \num{1.16}\\
- & (\num{1.50}) & (\num{1.62}) & (\num{1.69}) & (\num{1.84})\\
-parent.expectation & \num{2.34}*** & \num{2.40}*** & \num{2.36}*** & \num{2.28}***\\
- & (\num{0.35}) & (\num{0.35}) & (\num{0.34}) & (\num{0.34})\\
-parent.has.white.collar.job & \num{0.75} & \num{0.24} & \num{0.76} & \num{0.58}\\
- & (\num{0.69}) & (\num{0.74}) & (\num{0.74}) & (\num{0.77})\\
-mother.education.level & \num{-0.02} & \num{0.02} & \num{-0.08} & \num{-0.16}\\
+child.went.to.preschool & \num{2.30}** & \num{1.95}* & \num{2.16}** & \num{2.07}*\\
+ & (\num{0.78}) & (\num{0.86}) & (\num{0.81}) & (\num{0.86})\\
+child.had.skipped.grade & \num{-3.82} & \num{-3.81} & \num{-4.10} & \num{-2.95}\\
+ & (\num{2.62}) & (\num{2.74}) & (\num{2.71}) & (\num{2.88})\\
+child.had.repeated.grade & \num{-1.49} & \num{-2.59}* & \num{-1.84} & \num{-1.39}\\
+ & (\num{0.96}) & (\num{1.21}) & (\num{1.13}) & (\num{1.14})\\
+child.in.boarding.school & \num{1.34} & \num{1.20} & \num{1.22} & \num{0.82}\\
+ & (\num{1.04}) & (\num{0.99}) & (\num{1.03}) & (\num{0.99})\\
+child.education.aspiration & \num{2.05}*** & \num{1.98}*** & \num{2.02}*** & \num{2.09}***\\
+ & (\num{0.28}) & (\num{0.30}) & (\num{0.29}) & (\num{0.31})\\
+child.is.ethnic.minority & \num{1.56} & \num{1.60} & \num{1.08} & \num{1.23}\\
+ & (\num{1.49}) & (\num{1.61}) & (\num{1.68}) & (\num{1.82})\\
+parent.expectation & \num{2.35}*** & \num{2.43}*** & \num{2.38}*** & \num{2.30}***\\
+ & (\num{0.35}) & (\num{0.35}) & (\num{0.33}) & (\num{0.34})\\
+parent.has.white.collar.job & \num{0.90} & \num{0.39} & \num{0.89} & \num{0.72}\\
+ & (\num{0.69}) & (\num{0.74}) & (\num{0.74}) & (\num{0.76})\\
+mother.education.level & \num{-0.03} & \num{0.02} & \num{-0.08} & \num{-0.15}\\
  & (\num{0.31}) & (\num{0.33}) & (\num{0.36}) & (\num{0.35})\\
-father.education.level & \num{0.14} & \num{0.33} & \num{0.17} & \num{0.39}\\
- & (\num{0.31}) & (\num{0.31}) & (\num{0.32}) & (\num{0.33})\\
-home.economic.resource & \num{-0.55} & \num{-0.60} & \num{-0.15} & \num{-0.15}\\
- & (\num{0.52}) & (\num{0.53}) & (\num{0.52}) & (\num{0.55})\\
-home.extracurricular.book & \num{-0.03} & \num{-0.13} & \num{-0.09} & \num{-0.06}\\
- & (\num{0.26}) & (\num{0.27}) & (\num{0.26}) & (\num{0.26})\\
-home.has.internet & \num{-0.56} & \num{-0.92} & \num{-0.85} & \num{-1.07}\\
- & (\num{0.59}) & (\num{0.68}) & (\num{0.65}) & (\num{0.68})\\
+father.education.level & \num{0.14} & \num{0.31} & \num{0.16} & \num{0.38}\\
+ & (\num{0.30}) & (\num{0.30}) & (\num{0.32}) & (\num{0.32})\\
+home.economic.resource & \num{-0.55} & \num{-0.60} & \num{-0.15} & \num{-0.16}\\
+ & (\num{0.52}) & (\num{0.52}) & (\num{0.52}) & (\num{0.55})\\
+home.extracurricular.book & \num{-0.02} & \num{-0.11} & \num{-0.08} & \num{-0.04}\\
+ & (\num{0.26}) & (\num{0.26}) & (\num{0.26}) & (\num{0.26})\\
+home.has.internet & \num{-0.51} & \num{-0.87} & \num{-0.80} & \num{-1.03}\\
+ & (\num{0.61}) & (\num{0.70}) & (\num{0.67}) & (\num{0.70})\\
 \midrule
-Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
+Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
 R2 & \num{0.424} & \num{0.427} & \num{0.430} & \num{0.432}\\
-R2 Adj. & \num{0.405} & \num{0.406} & \num{0.409} & \num{0.410}\\
+R2 Adj. & \num{0.405} & \num{0.406} & \num{0.410} & \num{0.410}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \end{tabular}
@@
 \midrule
-Migration & \num{-1.23}* & \num{-2.08}* & \num{-0.82} & \num{-0.13}\\
- & (\num{0.53}) & (\num{0.84}) & (\num{0.71}) & (\num{0.76})\\
+Migration & \num{-1.26}* & \num{-2.11}* & \num{-0.91} & \num{-0.06}\\
+ & (\num{0.52}) & (\num{0.83}) & (\num{0.68}) & (\num{0.75})\\
 Baseline.score & \num{-0.01} & \num{-0.01} & \num{-0.01} & \num{-0.01}\\
  & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
-child.age & \num{-0.44}* & \num{-0.40}† & \num{-0.44}* & \num{-0.37}\\
- & (\num{0.19}) & (\num{0.20}) & (\num{0.21}) & (\num{0.22})\\
-child.is.girl & \num{1.62}*** & \num{1.68}*** & \num{1.60}*** & \num{1.54}***\\
+child.age & \num{-0.47}* & \num{-0.43}* & \num{-0.47}* & \num{-0.41}\\
+ & (\num{0.19}) & (\num{0.20}) & (\num{0.20}) & (\num{0.22})\\
+child.is.girl & \num{1.61}*** & \num{1.67}*** & \num{1.58}*** & \num{1.52}***\\
  & (\num{0.38}) & (\num{0.39}) & (\num{0.37}) & (\num{0.39})\\
-child.health & \num{0.37}** & \num{0.40}** & \num{0.27}† & \num{0.29}*\\
+child.health & \num{0.36}** & \num{0.38}** & \num{0.25} & \num{0.28}\\
  & (\num{0.13}) & (\num{0.13}) & (\num{0.15}) & (\num{0.14})\\
-child.has.rural.hukou & \num{0.34} & \num{0.41} & \num{0.21} & \num{0.33}\\
- & (\num{0.40}) & (\num{0.39}) & (\num{0.38}) & (\num{0.39})\\
-child.number.of.sibling & \num{0.29} & \num{0.22} & \num{0.39}† & \num{0.21}\\
+child.has.rural.hukou & \num{0.35} & \num{0.41} & \num{0.23} & \num{0.34}\\
+ & (\num{0.40}) & (\num{0.39}) & (\num{0.39}) & (\num{0.40})\\
+child.number.of.sibling & \num{0.29} & \num{0.24} & \num{0.40} & \num{0.23}\\
  & (\num{0.19}) & (\num{0.20}) & (\num{0.22}) & (\num{0.22})\\
-child.went.to.preschool & \num{1.17}* & \num{1.41}** & \num{0.75}† & \num{1.28}**\\
- & (\num{0.46}) & (\num{0.48}) & (\num{0.43}) & (\num{0.46})\\
-child.had.skipped.grade & \num{0.54} & \num{1.14} & \num{0.75} & \num{1.16}\\
- & (\num{1.79}) & (\num{1.58}) & (\num{2.01}) & (\num{1.62})\\
-child.had.repeated.grade & \num{-0.44} & \num{-0.16} & \num{-0.19} & \num{0.20}\\
- & (\num{0.70}) & (\num{0.77}) & (\num{0.80}) & (\num{0.85})\\
-child.in.boarding.school & \num{-0.38} & \num{-0.18} & \num{-0.29} & \num{-0.40}\\
- & (\num{0.52}) & (\num{0.48}) & (\num{0.48}) & (\num{0.53})\\
-child.education.aspiration & \num{0.77}*** & \num{0.87}*** & \num{0.79}*** & \num{0.79}**\\
+child.went.to.preschool & \num{1.12}* & \num{1.33}** & \num{0.70} & \num{1.22}*\\
+ & (\num{0.47}) & (\num{0.50}) & (\num{0.43}) & (\num{0.47})\\
+child.had.skipped.grade & \num{0.51} & \num{1.10} & \num{0.73} & \num{1.12}\\
+ & (\num{1.79}) & (\num{1.57}) & (\num{2.01}) & (\num{1.62})\\
+child.had.repeated.grade & \num{-0.37} & \num{-0.06} & \num{-0.16} & \num{0.31}\\
+ & (\num{0.72}) & (\num{0.81}) & (\num{0.82}) & (\num{0.88})\\
+child.in.boarding.school & \num{-0.37} & \num{-0.15} & \num{-0.27} & \num{-0.39}\\
+ & (\num{0.52}) & (\num{0.49}) & (\num{0.47}) & (\num{0.53})\\
+child.education.aspiration & \num{0.78}*** & \num{0.88}*** & \num{0.80}*** & \num{0.80}**\\
  & (\num{0.21}) & (\num{0.25}) & (\num{0.21}) & (\num{0.25})\\
-child.is.ethnic.minority & \num{-0.02} & \num{-0.12} & \num{-0.32} & \num{-0.51}\\
- & (\num{0.71}) & (\num{0.78}) & (\num{0.85}) & (\num{0.91})\\
-parent.expectation & \num{0.58}* & \num{0.52}* & \num{0.58}* & \num{0.59}*\\
- & (\num{0.25}) & (\num{0.24}) & (\num{0.28}) & (\num{0.27})\\
-parent.has.white.collar.job & \num{0.27} & \num{0.11} & \num{0.32} & \num{0.17}\\
- & (\num{0.40}) & (\num{0.43}) & (\num{0.42}) & (\num{0.45})\\
-mother.education.level & \num{0.00} & \num{-0.01} & \num{0.06} & \num{0.12}\\
- & (\num{0.18}) & (\num{0.19}) & (\num{0.17}) & (\num{0.18})\\
-father.education.level & \num{0.19} & \num{0.28} & \num{0.21} & \num{0.19}\\
- & (\num{0.19}) & (\num{0.19}) & (\num{0.19}) & (\num{0.19})\\
-home.economic.resource & \num{-0.25} & \num{-0.07} & \num{-0.14} & \num{-0.12}\\
+child.is.ethnic.minority & \num{0.01} & \num{-0.09} & \num{-0.29} & \num{-0.48}\\
+ & (\num{0.70}) & (\num{0.77}) & (\num{0.83}) & (\num{0.89})\\
+parent.expectation & \num{0.57}* & \num{0.52}* & \num{0.58}* & \num{0.58}*\\
+ & (\num{0.24}) & (\num{0.24}) & (\num{0.28}) & (\num{0.27})\\
+parent.has.white.collar.job & \num{0.32} & \num{0.18} & \num{0.39} & \num{0.23}\\
+ & (\num{0.39}) & (\num{0.43}) & (\num{0.42}) & (\num{0.44})\\
+mother.education.level & \num{-0.04} & \num{-0.05} & \num{0.01} & \num{0.08}\\
+ & (\num{0.18}) & (\num{0.19}) & (\num{0.18}) & (\num{0.18})\\
+father.education.level & \num{0.18} & \num{0.25} & \num{0.21} & \num{0.17}\\
+ & (\num{0.19}) & (\num{0.18}) & (\num{0.19}) & (\num{0.19})\\
+home.economic.resource & \num{-0.24} & \num{-0.05} & \num{-0.13} & \num{-0.09}\\
  & (\num{0.27}) & (\num{0.28}) & (\num{0.29}) & (\num{0.27})\\
-home.extracurricular.book & \num{-0.28}† & \num{-0.43}** & \num{-0.31}† & \num{-0.31}*\\
- & (\num{0.17}) & (\num{0.16}) & (\num{0.17}) & (\num{0.15})\\
-home.has.internet & \num{-0.41} & \num{-0.46} & \num{-0.32} & \num{-0.33}\\
- & (\num{0.37}) & (\num{0.39}) & (\num{0.40}) & (\num{0.41})\\
+home.extracurricular.book & \num{-0.28} & \num{-0.42}* & \num{-0.30} & \num{-0.30}\\
+ & (\num{0.17}) & (\num{0.16}) & (\num{0.16}) & (\num{0.15})\\
+home.has.internet & \num{-0.44} & \num{-0.50} & \num{-0.35} & \num{-0.35}\\
+ & (\num{0.36}) & (\num{0.39}) & (\num{0.40}) & (\num{0.41})\\
 \midrule
-Num.Obs. & \num{4062} & \num{3680} & \num{3674} & \num{3552}\\
-R2 & \num{0.499} & \num{0.518} & \num{0.502} & \num{0.518}\\
-R2 Adj. & \num{0.482} & \num{0.500} & \num{0.483} & \num{0.500}\\
+Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
+R2 & \num{0.499} & \num{0.517} & \num{0.501} & \num{0.517}\\
+R2 Adj. & \num{0.482} & \num{0.500} & \num{0.483} & \num{0.499}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \end{tabular}
@@
 \midrule
-Migration & \num{-2.52}*** & \num{-2.52}* & \num{-3.50}** & \num{-2.12}\\
- & (\num{0.72}) & (\num{1.14}) & (\num{1.27}) & (\num{1.71})\\
-Baseline.score & \num{-0.78}*** & \num{-0.81}*** & \num{-0.71}*** & \num{-0.75}***\\
- & (\num{0.02}) & (\num{0.04}) & (\num{0.03}) & (\num{0.05})\\
-child.age & \num{-3.14}*** & \num{-1.66} & \num{-3.31}*** & \num{-2.72}*\\
- & (\num{0.58}) & (\num{1.01}) & (\num{0.90}) & (\num{1.27})\\
-child.is.girl & \num{-1.27}† & \num{-0.63} & \num{-1.61} & \num{-1.89}\\
- & (\num{0.71}) & (\num{1.12}) & (\num{1.09}) & (\num{1.63})\\
-child.health & \num{-0.38} & \num{0.52} & \num{-0.68} & \num{0.36}\\
- & (\num{0.41}) & (\num{0.66}) & (\num{0.70}) & (\num{0.86})\\
-child.has.rural.hukou & \num{-0.72} & \num{-0.48} & \num{-2.46}† & \num{-3.39}†\\
- & (\num{0.89}) & (\num{1.45}) & (\num{1.41}) & (\num{1.85})\\
-child.number.of.sibling & \num{-0.60} & \num{-1.99}** & \num{-0.45} & \num{-1.43}\\
- & (\num{0.54}) & (\num{0.71}) & (\num{0.84}) & (\num{1.10})\\
-child.went.to.preschool & \num{2.11}* & \num{0.27} & \num{3.26}** & \num{4.12}*\\
- & (\num{0.91}) & (\num{1.45}) & (\num{1.03}) & (\num{1.94})\\
-child.had.skipped.grade & \num{-3.08} & \num{-2.72} & \num{-8.72}* & \num{2.29}\\
- & (\num{2.75}) & (\num{5.27}) & (\num{3.72}) & (\num{6.39})\\
-child.had.repeated.grade & \num{-0.95} & \num{-6.19}† & \num{-2.20} & \num{-0.01}\\
- & (\num{1.05}) & (\num{3.24}) & (\num{1.61}) & (\num{2.19})\\
-child.in.boarding.school & \num{1.73} & \num{1.97} & \num{0.55} & \num{-1.64}\\
- & (\num{1.23}) & (\num{2.06}) & (\num{1.99}) & (\num{2.64})\\
-child.education.aspiration & \num{1.73}*** & \num{1.18}* & \num{1.08}** & \num{2.07}**\\
- & (\num{0.36}) & (\num{0.58}) & (\num{0.37}) & (\num{0.79})\\
-child.is.ethnic.minority & \num{1.33} & \num{1.52} & \num{3.98} & \num{3.44}\\
- & (\num{1.59}) & (\num{2.04}) & (\num{3.21}) & (\num{3.82})\\
-parent.expectation & \num{2.34}*** & \num{3.45}*** & \num{2.40}*** & \num{1.37}\\
- & (\num{0.46}) & (\num{0.77}) & (\num{0.64}) & (\num{0.95})\\
-parent.has.white.collar.job & \num{1.19} & \num{0.37} & \num{0.32} & \num{-6.22}*\\
- & (\num{0.91}) & (\num{1.12}) & (\num{1.71}) & (\num{3.10})\\
-mother.education.level & \num{0.11} & \num{0.57} & \num{0.14} & \num{-1.02}\\
- & (\num{0.39}) & (\num{0.68}) & (\num{0.84}) & (\num{1.19})\\
-father.education.level & \num{0.05} & \num{-0.09} & \num{0.45} & \num{1.06}\\
- & (\num{0.41}) & (\num{0.50}) & (\num{0.69}) & (\num{1.13})\\
-home.economic.resource & \num{-0.58} & \num{-2.71}** & \num{0.40} & \num{0.43}\\
- & (\num{0.74}) & (\num{1.03}) & (\num{1.10}) & (\num{1.27})\\
-home.extracurricular.book & \num{0.03} & \num{0.02} & \num{-0.38} & \num{0.84}\\
- & (\num{0.37}) & (\num{0.48}) & (\num{0.50}) & (\num{0.70})\\
-home.has.internet & \num{-1.26} & \num{1.94} & \num{-0.44} & \num{-3.04}†\\
- & (\num{0.79}) & (\num{1.87}) & (\num{1.25}) & (\num{1.79})\\
+Migration & \num{-2.43}** & \num{-3.18}** & \num{-3.18}* & \num{-1.80}\\
+ & (\num{0.73}) & (\num{1.12}) & (\num{1.21}) & (\num{1.59})\\
+Baseline.score & \num{-0.79}*** & \num{-0.80}*** & \num{-0.75}*** & \num{-0.83}***\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
+child.age & \num{-2.74}*** & \num{-2.07}* & \num{-3.25}** & \num{-3.93}***\\
+ & (\num{0.59}) & (\num{0.92}) & (\num{0.99}) & (\num{1.08})\\
+child.is.girl & \num{-1.12} & \num{0.56} & \num{-1.35} & \num{-2.19}\\
+ & (\num{0.72}) & (\num{1.18}) & (\num{1.23}) & (\num{1.48})\\
+child.health & \num{-0.20} & \num{0.56} & \num{-1.40}* & \num{-0.49}\\
+ & (\num{0.41}) & (\num{0.58}) & (\num{0.65}) & (\num{0.90})\\
+child.has.rural.hukou & \num{-0.42} & \num{-0.08} & \num{-1.49} & \num{-3.06}\\
+ & (\num{0.87}) & (\num{1.28}) & (\num{1.32}) & (\num{2.18})\\
+child.number.of.sibling & \num{-0.75} & \num{-1.15} & \num{-0.32} & \num{-0.08}\\
+ & (\num{0.54}) & (\num{0.82}) & (\num{0.72}) & (\num{1.46})\\
+child.went.to.preschool & \num{2.22}* & \num{1.49} & \num{2.93}* & \num{6.00}**\\
+ & (\num{0.90}) & (\num{1.57}) & (\num{1.32}) & (\num{1.82})\\
+child.had.skipped.grade & \num{-2.14} & \num{-0.51} & \num{-5.84} & \num{1.59}\\
+ & (\num{2.92}) & (\num{3.94}) & (\num{4.78}) & (\num{5.92})\\
+child.had.repeated.grade & \num{-1.04} & \num{-6.67}* & \num{-2.16} & \num{-0.45}\\
+ & (\num{0.98}) & (\num{3.09}) & (\num{1.67}) & (\num{2.06})\\
+child.in.boarding.school & \num{1.92} & \num{2.78} & \num{2.32} & \num{0.67}\\
+ & (\num{1.35}) & (\num{2.58}) & (\num{2.06}) & (\num{2.31})\\
+child.education.aspiration & \num{1.93}*** & \num{1.03} & \num{1.69}*** & \num{2.20}**\\
+ & (\num{0.39}) & (\num{0.58}) & (\num{0.42}) & (\num{0.80})\\
+child.is.ethnic.minority & \num{3.65}** & \num{-0.21} & \num{-0.82} & \num{2.90}\\
+ & (\num{1.21}) & (\num{1.77}) & (\num{4.00}) & (\num{4.18})\\
+parent.expectation & \num{2.11}*** & \num{3.46}*** & \num{2.56}*** & \num{1.92}*\\
+ & (\num{0.46}) & (\num{0.89}) & (\num{0.59}) & (\num{0.91})\\
+parent.has.white.collar.job & \num{1.49} & \num{1.69} & \num{1.25} & \num{0.98}\\
+ & (\num{0.93}) & (\num{1.24}) & (\num{1.55}) & (\num{2.91})\\
+mother.education.level & \num{0.03} & \num{-0.16} & \num{-0.08} & \num{0.29}\\
+ & (\num{0.39}) & (\num{0.64}) & (\num{0.79}) & (\num{1.09})\\
+father.education.level & \num{0.41} & \num{0.48} & \num{0.21} & \num{-1.12}\\
+ & (\num{0.42}) & (\num{0.47}) & (\num{0.76}) & (\num{0.92})\\
+home.economic.resource & \num{-0.88} & \num{-3.04}** & \num{-0.03} & \num{0.63}\\
+ & (\num{0.73}) & (\num{1.13}) & (\num{1.20}) & (\num{1.44})\\
+home.extracurricular.book & \num{-0.12} & \num{0.16} & \num{0.53} & \num{0.62}\\
+ & (\num{0.38}) & (\num{0.55}) & (\num{0.51}) & (\num{0.69})\\
+home.has.internet & \num{-0.96} & \num{-0.30} & \num{-1.34} & \num{-2.55}\\
+ & (\num{0.70}) & (\num{1.91}) & (\num{1.31}) & (\num{2.37})\\
 \midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.438} & \num{0.495} & \num{0.477} & \num{0.523}\\
-R2 Adj. & \num{0.407} & \num{0.424} & \num{0.404} & \num{0.394}\\
+Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
+R2 & \num{0.448} & \num{0.502} & \num{0.473} & \num{0.566}\\
+R2 Adj. & \num{0.418} & \num{0.434} & \num{0.402} & \num{0.448}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
@@
 \midrule
-Migration & \num{-1.22}* & \num{-1.88}* & \num{-1.33} & \num{0.47}\\
- & (\num{0.55}) & (\num{0.81}) & (\num{0.87}) & (\num{1.06})\\
-Baseline.score & \num{0.06}** & \num{0.00} & \num{-0.02} & \num{-0.08}\\
- & (\num{0.02}) & (\num{0.05}) & (\num{0.04}) & (\num{0.06})\\
-child.age & \num{-0.08} & \num{-0.71} & \num{-0.43} & \num{-0.69}\\
- & (\num{0.27}) & (\num{0.50}) & (\num{0.44}) & (\num{0.56})\\
-child.is.girl & \num{1.99}*** & \num{1.69}*** & \num{1.99}** & \num{3.48}**\\
- & (\num{0.50}) & (\num{0.49}) & (\num{0.61}) & (\num{1.29})\\
-child.health & \num{0.47}* & \num{0.73}** & \num{0.75}* & \num{0.28}\\
- & (\num{0.20}) & (\num{0.26}) & (\num{0.34}) & (\num{0.65})\\
-child.has.rural.hukou & \num{0.03} & \num{0.60} & \num{0.31} & \num{2.16}†\\
- & (\num{0.47}) & (\num{0.65}) & (\num{0.65}) & (\num{1.12})\\
-child.number.of.sibling & \num{0.25} & \num{0.02} & \num{0.01} & \num{-0.30}\\
- & (\num{0.28}) & (\num{0.27}) & (\num{0.42}) & (\num{0.62})\\
-child.went.to.preschool & \num{1.27}* & \num{1.38}† & \num{-0.34} & \num{3.27}*\\
- & (\num{0.58}) & (\num{0.74}) & (\num{0.77}) & (\num{1.41})\\
-child.had.skipped.grade & \num{0.88} & \num{-0.66} & \num{0.43} & \num{5.78}†\\
- & (\num{2.20}) & (\num{1.42}) & (\num{3.12}) & (\num{3.44})\\
-child.had.repeated.grade & \num{-0.31} & \num{-2.82}† & \num{-2.23}* & \num{1.40}\\
- & (\num{0.84}) & (\num{1.54}) & (\num{0.97}) & (\num{1.85})\\
-child.in.boarding.school & \num{-0.30} & \num{1.60} & \num{0.66} & \num{-1.63}\\
- & (\num{0.74}) & (\num{1.13}) & (\num{0.85}) & (\num{1.70})\\
-child.education.aspiration & \num{0.52}* & \num{0.81}† & \num{0.85}** & \num{0.27}\\
- & (\num{0.21}) & (\num{0.41}) & (\num{0.30}) & (\num{0.56})\\
-child.is.ethnic.minority & \num{0.78} & \num{0.18} & \num{2.24} & \num{0.11}\\
- & (\num{0.72}) & (\num{1.05}) & (\num{1.42}) & (\num{2.54})\\
-parent.expectation & \num{0.64}** & \num{0.51} & \num{0.36} & \num{0.91}\\
- & (\num{0.23}) & (\num{0.36}) & (\num{0.44}) & (\num{0.60})\\
-parent.has.white.collar.job & \num{0.40} & \num{0.09} & \num{0.54} & \num{1.35}\\
- & (\num{0.44}) & (\num{0.57}) & (\num{0.75}) & (\num{1.24})\\
-mother.education.level & \num{-0.09} & \num{0.19} & \num{0.20} & \num{-0.79}\\
- & (\num{0.23}) & (\num{0.32}) & (\num{0.35}) & (\num{0.57})\\
-father.education.level & \num{0.14} & \num{-0.21} & \num{-0.01} & \num{0.04}\\
- & (\num{0.25}) & (\num{0.36}) & (\num{0.34}) & (\num{0.57})\\
-home.economic.resource & \num{-0.16} & \num{0.20} & \num{-0.39} & \num{-0.39}\\
- & (\num{0.36}) & (\num{0.59}) & (\num{0.51}) & (\num{0.69})\\
-home.extracurricular.book & \num{-0.42}† & \num{-0.35} & \num{-0.40} & \num{0.51}\\
- & (\num{0.23}) & (\num{0.31}) & (\num{0.30}) & (\num{0.49})\\
-home.has.internet & \num{-1.00}* & \num{-0.79} & \num{-1.48}* & \num{-0.83}\\
- & (\num{0.42}) & (\num{0.83}) & (\num{0.62}) & (\num{1.17})\\
+Migration & \num{-1.18}* & \num{-2.02}** & \num{-1.61} & \num{-0.35}\\
+ & (\num{0.55}) & (\num{0.76}) & (\num{0.88}) & (\num{1.02})\\
+Baseline.score & \num{0.06}* & \num{0.04} & \num{-0.02} & \num{-0.03}\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
+child.age & \num{-0.20} & \num{-0.33} & \num{-0.44} & \num{-0.60}\\
+ & (\num{0.29}) & (\num{0.45}) & (\num{0.47}) & (\num{0.54})\\
+child.is.girl & \num{1.83}*** & \num{1.90}*** & \num{1.99}** & \num{1.14}\\
+ & (\num{0.47}) & (\num{0.52}) & (\num{0.63}) & (\num{1.21})\\
+child.health & \num{0.68}** & \num{1.18}*** & \num{0.55} & \num{0.89}\\
+ & (\num{0.21}) & (\num{0.33}) & (\num{0.31}) & (\num{0.52})\\
+child.has.rural.hukou & \num{0.08} & \num{0.75} & \num{-0.10} & \num{0.95}\\
+ & (\num{0.50}) & (\num{0.75}) & (\num{0.71}) & (\num{1.09})\\
+child.number.of.sibling & \num{0.17} & \num{-0.09} & \num{0.26} & \num{0.59}\\
+ & (\num{0.26}) & (\num{0.32}) & (\num{0.43}) & (\num{0.65})\\
+child.went.to.preschool & \num{1.11} & \num{1.78}* & \num{0.05} & \num{2.59}*\\
+ & (\num{0.67}) & (\num{0.84}) & (\num{0.86}) & (\num{1.21})\\
+child.had.skipped.grade & \num{0.23} & \num{-2.73} & \num{0.15} & \num{7.91}\\
+ & (\num{2.71}) & (\num{2.36}) & (\num{2.91}) & (\num{4.33})\\
+child.had.repeated.grade & \num{-0.62} & \num{-2.74} & \num{-1.49} & \num{0.75}\\
+ & (\num{0.81}) & (\num{1.54}) & (\num{1.07}) & (\num{1.11})\\
+child.in.boarding.school & \num{0.02} & \num{1.63} & \num{0.05} & \num{-0.98}\\
+ & (\num{0.70}) & (\num{1.01}) & (\num{0.90}) & (\num{1.58})\\
+child.education.aspiration & \num{0.49}* & \num{0.85}** & \num{0.91}** & \num{-0.13}\\
+ & (\num{0.23}) & (\num{0.26}) & (\num{0.30}) & (\num{0.53})\\
+child.is.ethnic.minority & \num{0.36} & \num{-0.31} & \num{0.54} & \num{-2.08}\\
+ & (\num{0.86}) & (\num{0.88}) & (\num{1.42}) & (\num{1.93})\\
+parent.expectation & \num{0.60}** & \num{0.15} & \num{0.62} & \num{1.01}\\
+ & (\num{0.22}) & (\num{0.45}) & (\num{0.33}) & (\num{0.62})\\
+parent.has.white.collar.job & \num{0.65} & \num{0.10} & \num{1.08} & \num{-0.39}\\
+ & (\num{0.44}) & (\num{0.59}) & (\num{0.80}) & (\num{1.42})\\
+mother.education.level & \num{-0.20} & \num{0.12} & \num{-0.16} & \num{-0.20}\\
+ & (\num{0.26}) & (\num{0.28}) & (\num{0.32}) & (\num{0.58})\\
+father.education.level & \num{0.25} & \num{0.10} & \num{0.02} & \num{0.28}\\
+ & (\num{0.20}) & (\num{0.30}) & (\num{0.32}) & (\num{0.52})\\
+home.economic.resource & \num{-0.05} & \num{0.18} & \num{-0.14} & \num{-1.00}\\
+ & (\num{0.38}) & (\num{0.52}) & (\num{0.55}) & (\num{0.62})\\
+home.extracurricular.book & \num{-0.33} & \num{-0.59}* & \num{-0.25} & \num{0.52}\\
+ & (\num{0.22}) & (\num{0.30}) & (\num{0.30}) & (\num{0.40})\\
+home.has.internet & \num{-0.92}* & \num{-0.95} & \num{-0.64} & \num{0.79}\\
+ & (\num{0.42}) & (\num{0.73}) & (\num{0.59}) & (\num{1.09})\\
 \midrule
-Num.Obs. & \num{2503} & \num{1032} & \num{1008} & \num{515}\\
-R2 & \num{0.496} & \num{0.609} & \num{0.512} & \num{0.544}\\
-R2 Adj. & \num{0.469} & \num{0.554} & \num{0.445} & \num{0.421}\\
+Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
+R2 & \num{0.489} & \num{0.616} & \num{0.482} & \num{0.545}\\
+R2 Adj. & \num{0.461} & \num{0.563} & \num{0.412} & \num{0.420}\\
 FE: schids & X & X & X & X\\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}† p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
 \multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\

### 2023-03-23 analysis/Gu-thesis-script.Rmd
Adjust sampling and reference entries

@@
 library(DescTools)
-options(modelsummary_get="broom") 
 ```
@@
   left_join(d_stu2, by=c('ids', 'schids', 'clsids', 'ctyids')) |>
-  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) |> 
-  remove_labels() #Assemble a panel dataset in wide format
+  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) 
 ```
@@
          child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
-         child.health = a17, 
          child.had.skipped.grade = if_else(c03 == 0, 0, 1), 
@@
 ) |> drop_na(
-child.age, child.is.girl, child.has.rural.hukou, child.health, child.in.boarding.school, child.is.ethnic.minority, child.health, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
-parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
+child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
+parent.has.white.collar.job, 
+home.has.internet, home.extracurricular.book, home.economic.resource)
 ```
@@
 
+```{r Child health}
+d_cl <- d_cl |> remove_labels() |>
+  mutate(
+  child.health = 
+    if_else(
+      is.na(a17),
+        bd13,
+        a17
+    )
+  )
+```
+
+```{ Child short sighted}
+d_cl <- d_cl |> mutate(
+  a15 = if_else(a15 == 3, 0, 1),
+  bd14 = if_else(bd14 == 2, 0, 1)
+  )
+d_cl <- d_cl |> 
+  mutate(child.short.sighted = 
+           if_else(
+             is.na(a15),
+              bd14,
+              a15
+           ))
+
+```
+
 ```{r}
@@
   parent.expectation, 
+  child.health,
+  #child.short.sighted,
   child.education.aspiration)
@@
   w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
-  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
+  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, parent.expectation, home.has.internet,
   child.health, child.education.aspiration, 
-  mother.education.level, father.education.level, parent.expectation, 
+  mother.education.level, father.education.level, 
   home.extracurricular.book, home.economic.resource) 
@@
 )
-tab_idpvar[tab_idpvar == 4062] <- ''
+tab_idpvar[tab_idpvar == 4114] <- ''
 tab_idpvar
@@
 tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
-tab_ctvar_dit[tab_ctvar_dit == 3422|tab_ctvar_dit == 640] <- ''
+tab_ctvar_dit[tab_ctvar_dit == 3465|tab_ctvar_dit == 649] <- ''
 tab_ctvar_dit 
@@
 )
-tab_var[tab_var == 4062] <- ''
+tab_var[tab_var == 4114] <- ''
 tab_var
@@
 ```{r Info for regression tables}
-stars <- c('†' = .1, '*' = .05, '**' = .01, '***' = .001)
+stars <- c('*' = .05, '**' = .01, '***' = .001)
 coef_rename <- c("migr" = "Migration", "migr_mo_only" = "Migration", "migr_mo" = "Migration", "migr_fa" = "Migration", "migr_fa_only" = "Migration", "migr_both" = "Migration", "w1cog_100" = "Baseline.score", "w1avg_100" = "Baseline.score")
@@
 title_ttl <- 'Parental migration’s effect on children’s academic exam score'
-gof_omit <- 'R2 Within|R2 Pseudo|AIC|BIC|Log.Lik.|Std.Errors'
+gof_omit <- 'R2 Within|R2 Pseudo|RMSE|AIC|BIC|Log.Lik.|Std.Errors'
 note_unadj <- 'No control variables included in these models'
@@
 
+```{}
+table_cog
+table_ttl
+table_adj_cog
+table_adj_ttl
+```
+
 ## Matching
@@
   distance = "glm",
-  exact = migr ~ ctyids
+  exact= migr ~ ctyids
   )
@@
   ratio = 3,
-  exact = migr_mo_only ~ ctyids
+  exact= migr_mo_only ~ ctyids
   )
@@
   ratio = 3,
-  exact = migr_fa_only ~ ctyids
+  exact= migr_fa_only ~ ctyids
   )
@@
   ratio = 3,
-  exact = migr_both ~ ctyids
+  exact= migr_both ~ ctyids
   )
@@
 dm_both <- match.data(m.out_both)
+```
+
+```{}
+summary(m.out)
+summary(m.out_mo_only)
+summary(m.out_fa_only)
+summary(m.out_both)
 ```

### 2023-03-24 MScThesisText.Rmd
formatting

@@
 I adopted `R` (version 4.2.2) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.1) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.1), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
+This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.2) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
 

### 2023-03-24 MScThesisText.tex
formatting

@@
 I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.1) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.1), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
-NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in Chinese{]}}. National Bureau of Statistics. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}
+NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in {Chinese}{]}}. National Bureau of Statistics. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
-Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey (in chinese)}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
+Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of {CEPS} baseline survey (in {Chinese})}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
-Wickham, H., Miller, E., \& Smith, D. (2023). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}
+Wickham, H., Miller, E., \& Smith, D. (2023). \emph{Haven: Import and export {SPSS}, {Stata} and {SAS} files}. \url{https://CRAN.R-project.org/package=haven}
 

### 2023-03-24 analysis/Gu-thesis-script.Rmd
formatting

@@
   distance = "glm",
-  exact= migr ~ ctyids
+  exact = migr ~ ctyids
   )
@@
   ratio = 3,
-  exact= migr_mo_only ~ ctyids
+  exact = migr_mo_only ~ ctyids
   )
@@
   ratio = 3,
-  exact= migr_fa_only ~ ctyids
+  exact = migr_fa_only ~ ctyids
   )
@@
   ratio = 3,
-  exact= migr_both ~ ctyids
+  exact = migr_both ~ ctyids
   )

### 2023-03-24 data/Gu-thesis-script-more-control-var.Rmd

@@
          is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
-         siblings = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204),
-         health = NA,
+         ch.siblings = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204),
+         ch.health = NA,
+         ch.edu.aspr = NA,
          par.edu = if_else(b06 > b07, b06, b07), #best educated parent
@@
 ```{r}
-d_cl$health[d_cl$a17==1 | d_cl$a17==2] <- 1
-d_cl$health[d_cl$a17==3] <- 2
-d_cl$health[d_cl$a17==4 | d_cl$a17==5] <- 3
+d_cl$ch.health[d_cl$a17==1 | d_cl$a17==2] <- 1
+d_cl$ch.health[d_cl$a17==3] <- 2
+d_cl$ch.health[d_cl$a17==4 | d_cl$a17==5] <- 3
+```
+
+```{r}
+d_cl$ch.edu.aspr[d_cl$c22==10] <- 0
+d_cl$ch.edu.aspr[d_cl$c22==1 | d_cl$c22==2] <- 1
+d_cl$ch.edu.aspr[d_cl$c22==3 | d_cl$c22==4 | d_cl$c22==5] <- 2
+d_cl$ch.edu.aspr[d_cl$c22==6 | d_cl$c22==7] <- 3
+d_cl$ch.edu.aspr[d_cl$c22==8 | d_cl$c22==9] <- 4
 ```
@@
 ```{r}
-did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```
@@
 ```{r}
-did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
-did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
-did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
+did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
+did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
 ```

### 2023-03-25 MScThesisText.Rmd
Rewrite discussion and conclusion

@@
   Results show that the newly left-behind children's performance at school dropped slightly compared to that of non-left-behind peers. 
+  Father-only migration is negatively associated with children’s cognitive abilities.
   Mother-only migration is negatively associated with children’s academic grades and cognitive abilities.
-  Father-only migration is negatively associated with children’s cognitive abilities, but its magnitude is greater than mother-only migration.
 
@@
 Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause be on par with random assignment to participants, conditional on identification assumptions [@cunningham2021].
+It requires that the cause be on par with random assignment to participants, conditional on identification assumptions.
 
@@
 The first shortcoming lies in sampling.
-For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas [see @hu2019; @zhou2014].
+For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas [e.g.
+@hu2019; @zhou2014].
 @alpermann2020 pointed that the Chinese government reinforces "an urban hierarchy" besides the rural-urban divide.
@@
 The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue [@nbs2017].
-The second shortcoming is the usage of cross-sectional data.
-@wassink2021 argued that when cross-sectional surveys merely focus on single time points, they fail to capture the dynamic nature of migratory journey.
-Research results would be under- or over-estimated "depending on the timing of data collection" (p.
-1766).
+The second shortcoming lies in research design.
+Some studies rely on cross-sectional data that focus on single time points [e.g.
+@khalid2022].
+These studies fail to capture the dynamic nature of migratory journey.
+Some other studies probe correlation from panel data using basic ordinary least squares regression [e.g.
+@chen2023a].
+These studies could have employed causal inference techniques.
 The third shortcoming lies in the measurement of outcome.
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital [@debrauw2019].
+It holds that parental migration brings forth greater resources in the form of economic capital [@debrauw2019; @shen2021].
 Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
@@
 
-The other theoretical model is the family disruption model.
+The other theoretical model is the family disruption model [@shen2021].
 Children flourish under parental nurturing care.
@@
 At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
-These variables indicate family socioeconomic status, which is related to children's educational achievement [@liu2020; @young2018].
+These variables measure family socioeconomic status, which is related to children's educational achievement [@liu2020; @young2018].
 Finally, I controlled for the level of education that the child aspires to achieve and the parental expectation on the child's level of education.
@@
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that in the short term, only father's absence is not linked to children's academic performance; Only mother's absence is negatively associated with children's academic abilities, with a 2.1 points drop in the test score.
-This is in line with the findings of previous research.
-For example, @murphy2020 observed that when a Chinese mother migrates, she defies the cultural expectations on maternal care, thereby harboring bitterness in the child's mind.
-This bitter sentiment can arise even if there is care by father or other relatives.
+Results indicate that in the short term, children's cognitive ability would decline slightly when one parent migrates and the other one stays.
+Children's academic performance, however, would decrease mildly only when mother migrates while father stays.
+This discrepancy is in line with the findings of previous research.
+China's social norms expect that mothers provide daily care and emotional support to their children.
+When a mother migrates for work, she defies the cultural expectations on maternal care, thereby harboring bitter and depressive mood in the child's mind.
+This bitter sentiment can arise even if there is care by father or other relatives [@xu2019; @wang2023].
 Besides, only-mother migration sometimes indicates deeper issues within the household.
 The father may be unfit for work or engaged in domestic violence, prompting the mother's labor migration [@murphy2020].
-These may all hamper children's educational performance.
-
-Compared to only mother's migration, only father's migration carries a stronger influence on children's cognitive capability, as shown by a further decrease of 1 point in cognitive test score.
-This echoes the findings of @shen2021 -- in rural China, the father is often a household's best educated adult.
-His absence means a loss of household human capital, which slows the cognitive development of children.
-The stay-at-home mother may devote more to the caregiving role.
-This can partially buffer the impact by her husband's absence and help her child maintain academic performance.
+These factors may all hamper children's educational performance.
+When only father is absent, however, the stay-at-home mother may devote more to the caregiving role.
+This can partially buffer the impact by her husband's absence and help her child maintain educational performance [@shen2021].
 
@@
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
+In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023; @deng2023].
+This metropolis in central China set the precedant for offering hukou to all arriving migrants.
+Other main cities should follow suit.
 Besides top-down policymaking, bottom-up approaches are also necessary.

### 2023-03-25 MScThesisText.tex
Rewrite discussion and conclusion

@@
 Results show that the newly left-behind children's performance at school dropped slightly compared to that of non-left-behind peers.
+Father-only migration is negatively associated with children's cognitive abilities.
 Mother-only migration is negatively associated with children's academic grades and cognitive abilities.
-Father-only migration is negatively associated with children's cognitive abilities, but its magnitude is greater than mother-only migration.
 }
@@
 Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause be on par with random assignment to participants, conditional on identification assumptions (Cunningham, 2021).
+It requires that the cause be on par with random assignment to participants, conditional on identification assumptions.
 
@@
 The first shortcoming lies in sampling.
-For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas (see Hu, 2019; Zhou et al., 2014).
+For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas (e.g.
+Hu, 2019; Zhou et al., 2014).
 Alpermann (2020) pointed that the Chinese government reinforces ``an urban hierarchy'' besides the rural-urban divide.
@@
 The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue (NBS et al., 2017).
-The second shortcoming is the usage of cross-sectional data.
-Wassink and Viera (2021) argued that when cross-sectional surveys merely focus on single time points, they fail to capture the dynamic nature of migratory journey.
-Research results would be under- or over-estimated ``depending on the timing of data collection'' (p.~1766).
+The second shortcoming lies in research design.
+Some studies rely on cross-sectional data that focus on single time points (e.g.
+Khalid et al., 2022).
+These studies fail to capture the dynamic nature of migratory journey.
+Some other studies probe correlation from panel data using basic ordinary least squares regression (e.g.
+L.
+Chen et al., 2023).
+These studies could have employed causal inference techniques.
 The third shortcoming lies in the measurement of outcome.
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital (Brauw, 2019).
+It holds that parental migration brings forth greater resources in the form of economic capital (Brauw, 2019; Shen et al., 2021).
 Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
@@
 
-The other theoretical model is the family disruption model.
+The other theoretical model is the family disruption model (Shen et al., 2021).
 Children flourish under parental nurturing care.
@@
 At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
-These variables indicate family socioeconomic status, which is related to children's educational achievement (J.
+These variables measure family socioeconomic status, which is related to children's educational achievement (J.
 Liu et al., 2020; Young \& Hannum, 2018).
@@
 I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 I further examine whether the effect varies across different arrangements of parental migration.
-Results indicate that in the short term, only father's absence is not linked to children's academic performance; Only mother's absence is negatively associated with children's academic abilities, with a 2.1 points drop in the test score.
-This is in line with the findings of previous research.
-For example, Murphy (2020) observed that when a Chinese mother migrates, she defies the cultural expectations on maternal care, thereby harboring bitterness in the child's mind.
-This bitter sentiment can arise even if there is care by father or other relatives.
+Results indicate that in the short term, children's cognitive ability would decline slightly when one parent migrates and the other one stays.
+Children's academic performance, however, would decrease mildly only when mother migrates while father stays.
+This discrepancy is in line with the findings of previous research.
+China's social norms expect that mothers provide daily care and emotional support to their children.
+When a mother migrates for work, she defies the cultural expectations on maternal care, thereby harboring bitter and depressive mood in the child's mind.
+This bitter sentiment can arise even if there is care by father or other relatives (S.
+Wang, 2023; Xu et al., 2019).
 Besides, only-mother migration sometimes indicates deeper issues within the household.
 The father may be unfit for work or engaged in domestic violence, prompting the mother's labor migration (Murphy, 2020).
-These may all hamper children's educational performance.
-
-Compared to only mother's migration, only father's migration carries a stronger influence on children's cognitive capability, as shown by a further decrease of 1 point in cognitive test score.
-This echoes the findings of Shen et al.
-(2021) -- in rural China, the father is often a household's best educated adult.
-His absence means a loss of household human capital, which slows the cognitive development of children.
-The stay-at-home mother may devote more to the caregiving role.
-This can partially buffer the impact by her husband's absence and help her child maintain academic performance.
+These factors may all hamper children's educational performance.
+When only father is absent, however, the stay-at-home mother may devote more to the caregiving role.
+This can partially buffer the impact by her husband's absence and help her child maintain educational performance (Shen et al., 2021).
 
@@
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
+In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Deng, 2023; Jiemian News, 2023).
+This metropolis in central China set the precedant for offering hukou to all arriving migrants.
+Other main cities should follow suit.
 Besides top-down policymaking, bottom-up approaches are also necessary.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chen2023a}{}}%
+Chen, L., Wulczyn, F., \& Huhr, S.
+(2023).
+Parental absence, early reading, and human capital formation for rural children in China.
+\emph{Journal of Community Psychology}, \emph{51}(2), 662--675.
+\url{https://doi.org/10.1002/jcop.22786}
+
 \leavevmode\vadjust pre{\hypertarget{ref-chen2020}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cunningham2021}{}}%
-Cunningham, S. (2021). \emph{Causal inference: The mixtape}. Yale University Press. \url{https://mixtape.scunning.com/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-duxe9murger2015}{}}%
 Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in {China}. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-deng2023}{}}%
+Deng, I.
+(2023, February 28).
+\emph{Foxconn leases new site in China after government{'}s charm offensive}.
+South China Morning Post.
+\url{https://www.scmp.com/tech/big-tech/article/3211816/apples-iphone-supplier-foxconn-leases-new-site-zhengzhou-sign-commitment-chinas-supply-chain}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-cobalt}{}}%
-Greifer, N. (2022). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
+Greifer, N. (2023). \emph{Cobalt: Covariate balance tables and plots}. \url{https://CRAN.R-project.org/package=cobalt}
 
@@
 Huntington-Klein, N. (2023). \emph{Vtable: Variable table for variable documentation}. \url{https://CRAN.R-project.org/package=vtable}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jiemiannews2023}{}}%
+Jiemian News. (2023, January 3). \emph{Zhengzhou relaxes requirements for urban hukou applications {[}in {Chinese}{]}}. \url{https://www.jiemian.com/article/8677930.html}
+
+\leavevmode\vadjust pre{\hypertarget{ref-khalid2022}{}}%
+Khalid, S., Tadesse, E., Cai, L., \& Gao, C.
+(2022).
+Do Migrant Parents{'} Income or Relationships With Their Left-Behind Children Compensate for Their Physical Absence?
+\emph{Journal of Family Issues}, In Press.
+\url{https://doi.org/10.1177/0192513X221113853}
 

### 2023-06-09 MScThesisText.Rmd
Update code, writing, bibliography

@@
 note: |
-  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)
+  May 15, 2023
+
 authornote: | 
+  This paper's open science repository: https://github.com/jianchenggu/MScThesis
+  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).
 
@@
 
-I adopted `R` (version 4.2.2) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.2) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
+I adopted `R` (version 4.3.0) for all the analyses [@R-base].
+This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.3) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
 
@@
 Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020; @pang2022].
+
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
 In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023; @deng2023].
-This metropolis in central China set the precedant for offering hukou to all arriving migrants.
-Other main cities should follow suit.
+This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit.
 Besides top-down policymaking, bottom-up approaches are also necessary.

### 2023-06-09 MScThesisText.tex
Update code, writing, bibliography

@@
 
+\authornote{
+
+This paper's open science repository: \url{https://github.com/jianchenggu/MScThesis}
+An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).
+
+}
+
 \affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Social Sciences, Vrije Universiteit Amsterdam}
@@
 
-An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research)
+May 15, 2023
 
@@
 
-I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
+I adopted \texttt{R} (version 4.3.0) for all the analyses (R Core Team, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.3) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
 
@@
 \midrule
-Migration & \num{-2.53}** & \num{-2.82}* & \num{-2.78}* & \num{-1.72}\\
- & (\num{0.75}) & (\num{1.18}) & (\num{1.16}) & (\num{1.56})\\
-Baseline.score & \num{-0.72}*** & \num{-0.72}*** & \num{-0.65}*** & \num{-0.74}***\\
- & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.05})\\
+Migration & \num{-2.54}*** & \num{-2.55}* & \num{-2.65}* & \num{-0.34}\\
+ & (\num{0.75}) & (\num{1.14}) & (\num{1.10}) & (\num{1.54})\\
+Baseline.score & \num{-0.70}*** & \num{-0.70}*** & \num{-0.65}*** & \num{-0.71}***\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
 \midrule
 Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.402} & \num{0.454} & \num{0.405} & \num{0.493}\\
-R2 Adj. & \num{0.375} & \num{0.391} & \num{0.338} & \num{0.382}\\
+R2 & \num{0.396} & \num{0.445} & \num{0.410} & \num{0.486}\\
+R2 Adj. & \num{0.368} & \num{0.380} & \num{0.343} & \num{0.372}\\
 FE: schids & X & X & X & X\\
@@
 \midrule
-Migration & \num{-1.17}* & \num{-1.61}* & \num{-1.48} & \num{0.05}\\
- & (\num{0.57}) & (\num{0.76}) & (\num{0.89}) & (\num{0.93})\\
-Baseline.score & \num{0.05} & \num{0.10}** & \num{0.06} & \num{0.02}\\
- & (\num{0.03}) & (\num{0.03}) & (\num{0.04}) & (\num{0.04})\\
+Migration & \num{-1.15}* & \num{-1.72}* & \num{-1.53} & \num{0.50}\\
+ & (\num{0.56}) & (\num{0.75}) & (\num{0.81}) & (\num{0.84})\\
+Baseline.score & \num{0.05} & \num{0.08}* & \num{0.04} & \num{0.03}\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
 \midrule
 Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.462} & \num{0.590} & \num{0.453} & \num{0.513}\\
-R2 Adj. & \num{0.437} & \num{0.542} & \num{0.391} & \num{0.406}\\
+R2 & \num{0.456} & \num{0.574} & \num{0.436} & \num{0.522}\\
+R2 Adj. & \num{0.431} & \num{0.524} & \num{0.373} & \num{0.415}\\
 FE: schids & X & X & X & X\\
@@
 Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020; Pang \& Lu, 2022).
+
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
 In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Deng, 2023; Jiemian News, 2023).
-This metropolis in central China set the precedant for offering hukou to all arriving migrants.
-Other main cities should follow suit.
+This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit.
 Besides top-down policymaking, bottom-up approaches are also necessary.
@@
 \midrule
-Migration & \num{-2.43}** & \num{-3.18}** & \num{-3.18}* & \num{-1.80}\\
- & (\num{0.73}) & (\num{1.12}) & (\num{1.21}) & (\num{1.59})\\
-Baseline.score & \num{-0.79}*** & \num{-0.80}*** & \num{-0.75}*** & \num{-0.83}***\\
+Migration & \num{-2.51}*** & \num{-2.44}* & \num{-3.02}* & \num{-0.32}\\
+ & (\num{0.72}) & (\num{1.10}) & (\num{1.18}) & (\num{1.63})\\
+Baseline.score & \num{-0.78}*** & \num{-0.77}*** & \num{-0.74}*** & \num{-0.79}***\\
  & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
-child.age & \num{-2.74}*** & \num{-2.07}* & \num{-3.25}** & \num{-3.93}***\\
- & (\num{0.59}) & (\num{0.92}) & (\num{0.99}) & (\num{1.08})\\
-child.is.girl & \num{-1.12} & \num{0.56} & \num{-1.35} & \num{-2.19}\\
- & (\num{0.72}) & (\num{1.18}) & (\num{1.23}) & (\num{1.48})\\
-child.health & \num{-0.20} & \num{0.56} & \num{-1.40}* & \num{-0.49}\\
- & (\num{0.41}) & (\num{0.58}) & (\num{0.65}) & (\num{0.90})\\
-child.has.rural.hukou & \num{-0.42} & \num{-0.08} & \num{-1.49} & \num{-3.06}\\
- & (\num{0.87}) & (\num{1.28}) & (\num{1.32}) & (\num{2.18})\\
-child.number.of.sibling & \num{-0.75} & \num{-1.15} & \num{-0.32} & \num{-0.08}\\
- & (\num{0.54}) & (\num{0.82}) & (\num{0.72}) & (\num{1.46})\\
-child.went.to.preschool & \num{2.22}* & \num{1.49} & \num{2.93}* & \num{6.00}**\\
- & (\num{0.90}) & (\num{1.57}) & (\num{1.32}) & (\num{1.82})\\
-child.had.skipped.grade & \num{-2.14} & \num{-0.51} & \num{-5.84} & \num{1.59}\\
- & (\num{2.92}) & (\num{3.94}) & (\num{4.78}) & (\num{5.92})\\
-child.had.repeated.grade & \num{-1.04} & \num{-6.67}* & \num{-2.16} & \num{-0.45}\\
- & (\num{0.98}) & (\num{3.09}) & (\num{1.67}) & (\num{2.06})\\
-child.in.boarding.school & \num{1.92} & \num{2.78} & \num{2.32} & \num{0.67}\\
- & (\num{1.35}) & (\num{2.58}) & (\num{2.06}) & (\num{2.31})\\
-child.education.aspiration & \num{1.93}*** & \num{1.03} & \num{1.69}*** & \num{2.20}**\\
- & (\num{0.39}) & (\num{0.58}) & (\num{0.42}) & (\num{0.80})\\
-child.is.ethnic.minority & \num{3.65}** & \num{-0.21} & \num{-0.82} & \num{2.90}\\
- & (\num{1.21}) & (\num{1.77}) & (\num{4.00}) & (\num{4.18})\\
-parent.expectation & \num{2.11}*** & \num{3.46}*** & \num{2.56}*** & \num{1.92}*\\
- & (\num{0.46}) & (\num{0.89}) & (\num{0.59}) & (\num{0.91})\\
-parent.has.white.collar.job & \num{1.49} & \num{1.69} & \num{1.25} & \num{0.98}\\
- & (\num{0.93}) & (\num{1.24}) & (\num{1.55}) & (\num{2.91})\\
-mother.education.level & \num{0.03} & \num{-0.16} & \num{-0.08} & \num{0.29}\\
- & (\num{0.39}) & (\num{0.64}) & (\num{0.79}) & (\num{1.09})\\
-father.education.level & \num{0.41} & \num{0.48} & \num{0.21} & \num{-1.12}\\
- & (\num{0.42}) & (\num{0.47}) & (\num{0.76}) & (\num{0.92})\\
-home.economic.resource & \num{-0.88} & \num{-3.04}** & \num{-0.03} & \num{0.63}\\
- & (\num{0.73}) & (\num{1.13}) & (\num{1.20}) & (\num{1.44})\\
-home.extracurricular.book & \num{-0.12} & \num{0.16} & \num{0.53} & \num{0.62}\\
- & (\num{0.38}) & (\num{0.55}) & (\num{0.51}) & (\num{0.69})\\
-home.has.internet & \num{-0.96} & \num{-0.30} & \num{-1.34} & \num{-2.55}\\
- & (\num{0.70}) & (\num{1.91}) & (\num{1.31}) & (\num{2.37})\\
+child.age & \num{-2.77}*** & \num{-1.37} & \num{-3.19}** & \num{-3.23}*\\
+ & (\num{0.58}) & (\num{1.02}) & (\num{0.96}) & (\num{1.30})\\
+child.is.girl & \num{-1.73}* & \num{0.40} & \num{-1.44} & \num{-1.21}\\
+ & (\num{0.67}) & (\num{1.16}) & (\num{1.22}) & (\num{1.67})\\
+child.health & \num{-0.26} & \num{0.90} & \num{-1.22} & \num{-0.93}\\
+ & (\num{0.41}) & (\num{0.66}) & (\num{0.62}) & (\num{0.96})\\
+child.has.rural.hukou & \num{-0.33} & \num{-0.61} & \num{-1.68} & \num{-2.70}\\
+ & (\num{0.84}) & (\num{1.22}) & (\num{1.24}) & (\num{2.16})\\
+child.number.of.sibling & \num{-0.76} & \num{-1.32} & \num{-0.52} & \num{0.41}\\
+ & (\num{0.55}) & (\num{0.83}) & (\num{0.75}) & (\num{1.31})\\
+child.went.to.preschool & \num{1.97}* & \num{1.33} & \num{2.76}* & \num{6.17}***\\
+ & (\num{0.88}) & (\num{1.43}) & (\num{1.30}) & (\num{1.74})\\
+child.had.skipped.grade & \num{-1.81} & \num{-1.39} & \num{-7.72}* & \num{2.21}\\
+ & (\num{2.98}) & (\num{4.34}) & (\num{3.86}) & (\num{4.77})\\
+child.had.repeated.grade & \num{-1.02} & \num{-5.79}* & \num{-2.10} & \num{-1.29}\\
+ & (\num{1.02}) & (\num{2.69}) & (\num{1.78}) & (\num{2.08})\\
+child.in.boarding.school & \num{1.60} & \num{1.74} & \num{1.70} & \num{-0.47}\\
+ & (\num{1.30}) & (\num{1.85}) & (\num{2.08}) & (\num{2.50})\\
+child.education.aspiration & \num{1.97}*** & \num{0.84} & \num{1.48}*** & \num{2.08}*\\
+ & (\num{0.38}) & (\num{0.61}) & (\num{0.41}) & (\num{0.88})\\
+child.is.ethnic.minority & \num{3.12}* & \num{-2.31} & \num{0.02} & \num{3.82}\\
+ & (\num{1.34}) & (\num{2.56}) & (\num{4.54}) & (\num{4.98})\\
+parent.expectation & \num{2.19}*** & \num{3.56}*** & \num{2.36}*** & \num{2.11}*\\
+ & (\num{0.46}) & (\num{0.77}) & (\num{0.54}) & (\num{0.96})\\
+parent.has.white.collar.job & \num{0.84} & \num{0.14} & \num{0.13} & \num{0.94}\\
+ & (\num{0.95}) & (\num{1.28}) & (\num{1.41}) & (\num{2.98})\\
+mother.education.level & \num{0.26} & \num{-0.02} & \num{0.31} & \num{0.43}\\
+ & (\num{0.38}) & (\num{0.70}) & (\num{0.81}) & (\num{1.03})\\
+father.education.level & \num{0.66} & \num{0.78} & \num{0.41} & \num{-0.29}\\
+ & (\num{0.40}) & (\num{0.49}) & (\num{0.74}) & (\num{1.05})\\
+home.economic.resource & \num{-0.61} & \num{-2.22} & \num{0.00} & \num{0.72}\\
+ & (\num{0.70}) & (\num{1.31}) & (\num{1.11}) & (\num{1.55})\\
+home.extracurricular.book & \num{-0.15} & \num{0.43} & \num{0.58} & \num{1.31}\\
+ & (\num{0.38}) & (\num{0.57}) & (\num{0.50}) & (\num{0.74})\\
+home.has.internet & \num{-1.34} & \num{0.14} & \num{-1.52} & \num{-3.90}*\\
+ & (\num{0.72}) & (\num{1.87}) & (\num{1.20}) & (\num{1.94})\\
 \midrule
 Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.448} & \num{0.502} & \num{0.473} & \num{0.566}\\
-R2 Adj. & \num{0.418} & \num{0.434} & \num{0.402} & \num{0.448}\\
+R2 & \num{0.445} & \num{0.490} & \num{0.469} & \num{0.554}\\
+R2 Adj. & \num{0.415} & \num{0.419} & \num{0.397} & \num{0.431}\\
 FE: schids & X & X & X & X\\
@@
 \midrule
-Migration & \num{-1.18}* & \num{-2.02}** & \num{-1.61} & \num{-0.35}\\
- & (\num{0.55}) & (\num{0.76}) & (\num{0.88}) & (\num{1.02})\\
-Baseline.score & \num{0.06}* & \num{0.04} & \num{-0.02} & \num{-0.03}\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
-child.age & \num{-0.20} & \num{-0.33} & \num{-0.44} & \num{-0.60}\\
- & (\num{0.29}) & (\num{0.45}) & (\num{0.47}) & (\num{0.54})\\
-child.is.girl & \num{1.83}*** & \num{1.90}*** & \num{1.99}** & \num{1.14}\\
- & (\num{0.47}) & (\num{0.52}) & (\num{0.63}) & (\num{1.21})\\
-child.health & \num{0.68}** & \num{1.18}*** & \num{0.55} & \num{0.89}\\
- & (\num{0.21}) & (\num{0.33}) & (\num{0.31}) & (\num{0.52})\\
-child.has.rural.hukou & \num{0.08} & \num{0.75} & \num{-0.10} & \num{0.95}\\
- & (\num{0.50}) & (\num{0.75}) & (\num{0.71}) & (\num{1.09})\\
-child.number.of.sibling & \num{0.17} & \num{-0.09} & \num{0.26} & \num{0.59}\\
- & (\num{0.26}) & (\num{0.32}) & (\num{0.43}) & (\num{0.65})\\
-child.went.to.preschool & \num{1.11} & \num{1.78}* & \num{0.05} & \num{2.59}*\\
- & (\num{0.67}) & (\num{0.84}) & (\num{0.86}) & (\num{1.21})\\
-child.had.skipped.grade & \num{0.23} & \num{-2.73} & \num{0.15} & \num{7.91}\\
- & (\num{2.71}) & (\num{2.36}) & (\num{2.91}) & (\num{4.33})\\
-child.had.repeated.grade & \num{-0.62} & \num{-2.74} & \num{-1.49} & \num{0.75}\\
- & (\num{0.81}) & (\num{1.54}) & (\num{1.07}) & (\num{1.11})\\
-child.in.boarding.school & \num{0.02} & \num{1.63} & \num{0.05} & \num{-0.98}\\
- & (\num{0.70}) & (\num{1.01}) & (\num{0.90}) & (\num{1.58})\\
-child.education.aspiration & \num{0.49}* & \num{0.85}** & \num{0.91}** & \num{-0.13}\\
- & (\num{0.23}) & (\num{0.26}) & (\num{0.30}) & (\num{0.53})\\
-child.is.ethnic.minority & \num{0.36} & \num{-0.31} & \num{0.54} & \num{-2.08}\\
- & (\num{0.86}) & (\num{0.88}) & (\num{1.42}) & (\num{1.93})\\
-parent.expectation & \num{0.60}** & \num{0.15} & \num{0.62} & \num{1.01}\\
- & (\num{0.22}) & (\num{0.45}) & (\num{0.33}) & (\num{0.62})\\
-parent.has.white.collar.job & \num{0.65} & \num{0.10} & \num{1.08} & \num{-0.39}\\
- & (\num{0.44}) & (\num{0.59}) & (\num{0.80}) & (\num{1.42})\\
-mother.education.level & \num{-0.20} & \num{0.12} & \num{-0.16} & \num{-0.20}\\
- & (\num{0.26}) & (\num{0.28}) & (\num{0.32}) & (\num{0.58})\\
-father.education.level & \num{0.25} & \num{0.10} & \num{0.02} & \num{0.28}\\
- & (\num{0.20}) & (\num{0.30}) & (\num{0.32}) & (\num{0.52})\\
-home.economic.resource & \num{-0.05} & \num{0.18} & \num{-0.14} & \num{-1.00}\\
- & (\num{0.38}) & (\num{0.52}) & (\num{0.55}) & (\num{0.62})\\
-home.extracurricular.book & \num{-0.33} & \num{-0.59}* & \num{-0.25} & \num{0.52}\\
- & (\num{0.22}) & (\num{0.30}) & (\num{0.30}) & (\num{0.40})\\
-home.has.internet & \num{-0.92}* & \num{-0.95} & \num{-0.64} & \num{0.79}\\
- & (\num{0.42}) & (\num{0.73}) & (\num{0.59}) & (\num{1.09})\\
+Migration & \num{-1.18}* & \num{-1.89}* & \num{-1.52} & \num{0.20}\\
+ & (\num{0.55}) & (\num{0.73}) & (\num{0.81}) & (\num{0.87})\\
+Baseline.score & \num{0.06}* & \num{0.02} & \num{-0.04} & \num{-0.01}\\
+ & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
+child.age & \num{-0.15} & \num{-0.13} & \num{-0.67} & \num{-1.00}*\\
+ & (\num{0.30}) & (\num{0.45}) & (\num{0.48}) & (\num{0.48})\\
+child.is.girl & \num{1.74}*** & \num{1.61}** & \num{2.45}*** & \num{0.49}\\
+ & (\num{0.47}) & (\num{0.54}) & (\num{0.64}) & (\num{1.06})\\
+child.health & \num{0.60}** & \num{1.19}** & \num{0.51} & \num{0.65}\\
+ & (\num{0.21}) & (\num{0.36}) & (\num{0.29}) & (\num{0.52})\\
+child.has.rural.hukou & \num{-0.11} & \num{0.63} & \num{-0.13} & \num{0.84}\\
+ & (\num{0.50}) & (\num{0.73}) & (\num{0.69}) & (\num{1.02})\\
+child.number.of.sibling & \num{0.08} & \num{0.14} & \num{0.54} & \num{0.27}\\
+ & (\num{0.25}) & (\num{0.30}) & (\num{0.37}) & (\num{0.65})\\
+child.went.to.preschool & \num{1.34}* & \num{2.36}* & \num{0.02} & \num{2.57}*\\
+ & (\num{0.65}) & (\num{0.98}) & (\num{0.77}) & (\num{1.11})\\
+child.had.skipped.grade & \num{-0.13} & \num{-2.17} & \num{0.28} & \num{6.06}\\
+ & (\num{2.74}) & (\num{2.63}) & (\num{2.84}) & (\num{4.65})\\
+child.had.repeated.grade & \num{-0.19} & \num{-0.64} & \num{-1.02} & \num{0.19}\\
+ & (\num{0.85}) & (\num{1.52}) & (\num{1.06}) & (\num{1.09})\\
+child.in.boarding.school & \num{-0.28} & \num{-0.92} & \num{0.98} & \num{0.01}\\
+ & (\num{0.72}) & (\num{1.54}) & (\num{0.90}) & (\num{1.63})\\
+child.education.aspiration & \num{0.44} & \num{1.18}** & \num{0.78}* & \num{0.01}\\
+ & (\num{0.23}) & (\num{0.38}) & (\num{0.30}) & (\num{0.50})\\
+child.is.ethnic.minority & \num{0.23} & \num{-1.07} & \num{-0.35} & \num{-3.44}\\
+ & (\num{0.88}) & (\num{0.98}) & (\num{1.82}) & (\num{2.15})\\
+parent.expectation & \num{0.67}** & \num{0.02} & \num{0.98}* & \num{0.55}\\
+ & (\num{0.22}) & (\num{0.44}) & (\num{0.40}) & (\num{0.57})\\
+parent.has.white.collar.job & \num{0.37} & \num{-0.10} & \num{1.75}* & \num{-0.18}\\
+ & (\num{0.41}) & (\num{0.60}) & (\num{0.79}) & (\num{1.28})\\
+mother.education.level & \num{-0.08} & \num{-0.06} & \num{-0.15} & \num{-0.03}\\
+ & (\num{0.26}) & (\num{0.31}) & (\num{0.34}) & (\num{0.53})\\
+father.education.level & \num{0.25} & \num{0.24} & \num{-0.06} & \num{-0.01}\\
+ & (\num{0.21}) & (\num{0.33}) & (\num{0.32}) & (\num{0.46})\\
+home.economic.resource & \num{0.03} & \num{0.21} & \num{-0.24} & \num{-1.04}\\
+ & (\num{0.37}) & (\num{0.60}) & (\num{0.54}) & (\num{0.69})\\
+home.extracurricular.book & \num{-0.37} & \num{-0.67}* & \num{-0.08} & \num{0.33}\\
+ & (\num{0.22}) & (\num{0.27}) & (\num{0.31}) & (\num{0.36})\\
+home.has.internet & \num{-1.03}* & \num{-0.50} & \num{-0.55} & \num{0.25}\\
+ & (\num{0.43}) & (\num{0.71}) & (\num{0.68}) & (\num{1.11})\\
 \midrule
 Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.489} & \num{0.616} & \num{0.482} & \num{0.545}\\
-R2 Adj. & \num{0.461} & \num{0.563} & \num{0.412} & \num{0.420}\\
+R2 & \num{0.482} & \num{0.601} & \num{0.473} & \num{0.544}\\
+R2 Adj. & \num{0.454} & \num{0.545} & \num{0.402} & \num{0.419}\\
 FE: schids & X & X & X & X\\

### 2023-06-09 analysis/Gu-thesis-script.Rmd
Update code, writing, bibliography

--- 2023-03-23 analysis/Gu-thesis-script.Rmd
@@
   left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) 
+rm('d_stu1', 'd_stu2', 'd_par1', 'd_par2')
 ```
@@
 d_cl <- d_cl |> mutate(
-         child.age = 2013 - a02a, 
-         child.is.girl = if_else(a01 == 2, 1, 0), 
+         child.age = 
+           if_else(
+             fall == 1, 
+             2014 - a02a - a02b/12, 
+             2014 - a02a - a02b/12 + 0.5),
+         child.is.girl = if_else(stsex == 1, 0, 1), 
          child.has.rural.hukou = sthktype, 
@@
          child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
-         child.had.skipped.grade = if_else(c03 == 0, 0, 1), 
-         child.had.repeated.grade = if_else(c04 == 0, 0, 1), 
          child.went.to.preschool = if_else(c01 == 1, 1, 0), 
          child.number.of.sibling = if_else(stonly == 1, 0, stsib),
-         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
          home.economic.resource = steco_5c, 
@@
          home.extracurricular.book = b12 
-) |> drop_na(
-child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling,
-parent.has.white.collar.job, 
-home.has.internet, home.extracurricular.book, home.economic.resource)
+)  
 ```
 
-```{r Mother education}
-d_cl <- d_cl |> mutate(mother.education.level = NA)
-d_cl$mother.education.level[d_cl$stmedu == 1|d_cl$stmedu == 2] <- 0 
-d_cl$mother.education.level[d_cl$stmedu == 3] <- 1
-d_cl$mother.education.level[d_cl$stmedu == 4|d_cl$stmedu == 5|d_cl$stmedu == 6] <- 2
-d_cl$mother.education.level[d_cl$stmedu == 7] <- 3
-d_cl$mother.education.level[d_cl$stmedu == 8] <- 4
-d_cl$mother.education.level[d_cl$stmedu == 9] <- 5
-```
-
-```{r Father education}
-d_cl <- d_cl |> mutate(father.education.level = NA)
-d_cl$father.education.level[d_cl$stfedu == 1|d_cl$stfedu == 2] <- 0
-d_cl$father.education.level[d_cl$stfedu == 3] <- 1
-d_cl$father.education.level[d_cl$stfedu == 4|d_cl$stfedu == 5|d_cl$stfedu == 6] <- 2
-d_cl$father.education.level[d_cl$stfedu == 7] <- 3
-d_cl$father.education.level[d_cl$stfedu == 8] <- 4
-d_cl$father.education.level[d_cl$stfedu == 9] <- 5
+```{r Parent education}
+d_cl <- d_cl |> mutate(
+  parent.education.level = 
+    case_when(
+      stprhedu == 1|stprhedu == 2 ~ 0,
+      stprhedu == 3 ~ 1,
+      stprhedu == 4|stprhedu == 5|stprhedu == 6 ~ 2,
+      stprhedu == 7 ~ 3,
+      stprhedu == 8 ~ 4,
+      stprhedu == 9 ~ 5)
+)
 ```
@@
 ```{r Parent expectation}
-d_cl <- d_cl |> mutate(parent.expectation = NA)
-d_cl$parent.expectation[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
-d_cl$parent.expectation[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
-d_cl$parent.expectation[d_cl$ba18 == 6] <- 3
-d_cl$parent.expectation[d_cl$ba18 == 7] <- 4
-d_cl$parent.expectation[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
+d_cl <- d_cl |> mutate(
+  parexp = 
+    if_else(
+      is.na(ba18),
+        b31,
+        ba18)
+) |> mutate(
+  parent.expectation = 
+    case_when(
+      parexp == 10 ~ 0,
+      parexp == 1|parexp == 2 ~ 1,
+      parexp == 3|parexp == 4|parexp == 5 ~ 2,
+      parexp == 6 ~ 3,
+      parexp == 7 ~ 4,
+      parexp == 8|parexp == 9 ~ 5
+    )
+)
+```
+
+```{r Parent job}
+d_cl <- d_cl |> mutate(
+  b08ch = if_else(
+    b08a==1|b08a==2|b08a==3|b08b==1|b08b==2|b08b==3,
+    1,
+    0
+  ),
+  b08pr = 
+    if_else(be08==1|be08==2|be08==3, 1, 0)
+)
+d_cl <- d_cl |> mutate(
+  parent.has.white.collar.job = 
+    if_else(
+      is.na(b08ch),
+      b08pr,
+      b08ch
+    )
+)
 ```
@@
 ```{r Child aspiration}
-d_cl <- d_cl |> mutate(child.education.aspiration = NA)
-d_cl$child.education.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
-d_cl$child.education.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
-d_cl$child.education.aspiration[d_cl$c22 == 6] <- 3
-d_cl$child.education.aspiration[d_cl$c22 == 7] <- 4
-d_cl$child.education.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
+d_cl <- d_cl |> mutate(
+  child.education.aspiration = 
+    case_when(
+      c22 == 10 ~ 0,
+      c22 == 1|c22 == 2 ~ 1,
+      c22 == 3|c22 == 4|c22 == 5 ~ 2,
+      c22 == 6 ~ 3,
+      c22 == 7 ~ 4,
+      c22 == 8|c22 == 9 ~ 5
+    )
+)
 ```
@@
 
-```{r}
+```{r Drop NA}
 d_cl <- d_cl |>  drop_na(
-  mother.education.level, 
-  father.education.level,
+  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.went.to.preschool, child.number.of.sibling, 
+  #child.had.skipped.grade,
+  #child.had.repeated.grade,
+home.has.internet, home.extracurricular.book, home.economic.resource,
+  #mother.education.level, 
+  #father.education.level,
+  parent.education.level,
   parent.expectation, 
@@
 At least one parent migrated (Control group as no parent migrated)
-```{r}
-d_cl <- d_cl |> mutate(
-  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became Migrated from household between baseline and endline survey
-  migr_fa_only = NA,
-  #migr_fa = NA,
-  migr_mo_only = NA,
-  #migr_mo = NA,
-  migr_both = NA
-  ) |> drop_na(migr)
-```
-
-Only mother migrated
 ```{r Any parent migrated}
 d_cl <- d_cl |> mutate(
-  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
-  migr_fa_only = NA,
-  migr_mo_only = NA,
-  migr_both = NA
+  migr = if_else(w2ba0201==0 | w2ba0202==0, 1, 0) #Any parent became absent from household between baseline and endline survey
   ) |> drop_na(migr)
@@
 ```{r Only mother migrated}
-d_cl$migr_mo_only[d_cl$migr == 0] <- 0
-d_cl$migr_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
+d_cl <- d_cl |> 
+  mutate(
+    migr_mo_only = 
+      case_when(
+        w2ba0201==1 & w2ba0202==0 ~ 1,
+        migr == 0 ~ 0,
+        .default = NA
+      )
+  )
 ```
@@
 ```{r Only father migrated}
-d_cl$migr_fa_only[d_cl$migr == 0] <- 0
-d_cl$migr_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
+d_cl <- d_cl |> 
+  mutate(
+    migr_fa_only = 
+      case_when(
+        w2ba0201==0 & w2ba0202==1 ~ 1,
+        migr == 0 ~ 0,
+        .default = NA
+      )
+  )
 ```
@@
 ```{r Both parents migrated}
-d_cl$migr_both[d_cl$migr == 0] <- 0
-d_cl$migr_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
+d_cl <- d_cl |> 
+  mutate(
+    migr_both = 
+      case_when(
+        w2ba0201==0 & w2ba0202==0 ~ 1,
+        migr == 0 ~ 0,
+        .default = NA
+      )
+  )
 ```
@@
   w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
-  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, parent.expectation, home.has.internet,
+  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, #child.had.skipped.grade, child.had.repeated.grade, 
+  child.is.ethnic.minority, child.went.to.preschool, parent.has.white.collar.job, parent.expectation, parent.education.level, home.has.internet,
   child.health, child.education.aspiration, 
-  mother.education.level, father.education.level, 
+  #mother.education.level, father.education.level, 
   home.extracurricular.book, home.economic.resource) 
@@
   mutate(`Parental Migration` = if_else(migr==1, 'Yes', 'No')) |>
-  mutate(`Parental Migration Type` = NA) 
-d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents at Home'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
-d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
+  mutate(
+    `Parental Migration Type` = 
+      case_when(
+        migr==0 ~ 'Both Parents at Home',
+        migr_mo_only==1 ~ 'Only Mother Migrated',
+        migr_fa_only==1 ~ 'Only Father Migrated',
+        migr_both==1 ~ 'Both Parents Migrated'
+      )
+) 
 d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
@@
 )
-tab_idpvar[tab_idpvar == 4114] <- ''
+tab_idpvar[tab_idpvar == 4204] <- ''
 tab_idpvar
@@
 d_ctvar_dit <- d_migr |>
-  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |>
+  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school,
+         #child.had.skipped.grade, child.had.repeated.grade, 
+         child.is.ethnic.minority, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |> 
   mutate_all(as_factor)
@@
 tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
-tab_ctvar_dit[tab_ctvar_dit == 3465|tab_ctvar_dit == 649] <- ''
+tab_ctvar_dit[tab_ctvar_dit == 3529|tab_ctvar_dit == 675] <- ''
 tab_ctvar_dit 
@@
   select(`Parental Migration`, child.age, child.number.of.sibling, child.health, child.education.aspiration, 
-  mother.education.level, father.education.level, parent.expectation, 
+  parent.education.level, parent.expectation, 
   home.extracurricular.book, home.economic.resource)
@@
   add_value_labels(
-    father.education.level = c(
-     '0 = Primary school and below' = 0,
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    mother.education.level = c(
+    parent.education.level = c(
      '0 = Primary school and below' = 0,
@@
     child.education.aspiration = c(
-     '1 = Junior high school' = 1 ,
-     '2 = Senior high school' = 2,
-     '3 = Associate college' = 3,
-     '4 = University' = 4,
-     '5 = Postgraduate' = 5),
-    child.education.aspiration = c(
-     '1 = Junior high school' = 1 ,
+     '0 = Does not matter' = 0,
+     '1 = Junior high school' = 1,
      '2 = Senior high school' = 2,
@@
     parent.expectation = c(
+     '0 = Does not matter' = 0,
      '1 = Junior high school' = 1 ,
@@
 )
-tab_var[tab_var == 4114] <- ''
+tab_var[tab_var == 4204] <- ''
 tab_var
@@
 ```{r Data for violin plots}
-d_smr <- d_migr |> 
-  mutate(`Parental Migration Type` = 0) 
-d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
-d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
-d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
-d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
+d_smr <- df |> 
+  mutate(
+    `Parental Migration` = 
+      if_else(
+        (migr==1), 'Yes', 'No')
+    ) |>
+  mutate(
+    `Parental Migration Type` = 
+      case_when(
+        migr==0 ~ 'Both Parents at Home',
+        migr_mo_only==1 ~ 'Only Mother Migrated',
+        migr_fa_only==1 ~ 'Only Father Migrated',
+        migr_both==1 ~ 'Both Parents Migrated'
+      )
+  )
 d_smr <- d_smr |> select(!migr_mo_only & !migr_fa_only & !migr_both)
@@
 ```{r Adjusted regression on cognitive score}
-did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
-did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
+did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
 ```
@@
 ```{r Adjusted regression on exam grade}
-did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
-did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
+did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
 ```
@@
 m.out <- matchit(
-  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = df, 
-  ratio = 3,
-  method = "optimal", 
-  distance = "glm",
-  exact= migr ~ ctyids
+  method = "full", 
+  distance = "glm"
   )
@@
 m.out_mo_only <- 
-  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
+  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_mo_only, 
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact= migr_mo_only ~ ctyids
+  method = "full",
+  distance = "glm"
   )
@@
 m.out_fa_only <- matchit(
-  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_fa_only,
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact= migr_fa_only ~ ctyids
+  method = "full",
+  distance = "glm"
   )
@@
 m.out_both <- matchit(
-  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet,
+  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet,
   data = d_both, 
-  method = "optimal",
-  distance = "glm",
-  ratio = 3,
-  exact= migr_both ~ ctyids
+  method = "full",
+  distance = "glm"
   )
@@
 
-```{}
+```{r}
 summary(m.out)
@@
 ```{r Adjusted regression on cognitive score with matching}
-didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
-didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
+didm_adj_cog <- feols(cog_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
+didm_adj_cog_mo_only <- feols(cog_dif ~ migr_mo_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_adj_cog_fa_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm_both, weights = dm_both$weights)
 ```
@@
 ```{r Adjusted regression on exam score with matching}
-didm_adj_ttl <- feols(avg_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
-didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
-didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
-didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
+didm_adj_ttl <- feols(avg_dif ~ migr + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = dm, weights = dm$weights)
+didm_adj_ttl_mo_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_mo_only, weights = dm_mo_only$weights)
+didm_adj_ttl_fa_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_fa_only, weights = dm_fa_only$weights)
+didm_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet  | schids, data = dm_both, weights = dm_both$weights)
 ```
@@
 title_ttl_matching <- 'Parental migration’s effect on children’s academic exam score, estimated with matching'
-note_matching <- "3:1 optimal pair propensity score matching; exact matching by county"
+note_matching <- "Optimal full matching by propensity score"
 ```
@@
 
-```{r save image}
+```{}
+table_m_cog
+table_m_ttl
+table_m_adj_cog
+table_m_adj_ttl
+```
+
+```{ save image}
 save.image('.RData')

### 2023-06-09 appendix.Rmd
Update code, writing, bibliography

@@
-# Tables
+(ref:cog-dif) Changes in cognitive test score
 
-```{r tab-reg-cog-adj}
-table_adj_cog
+(ref:ttl-dif) Changes in academic exam score
+
+(ref:migr) for newly left-behind students and non-left-behind students
+
+(ref:migr-type) by household migration arrangement
+
+(ref:cobalt-match) Covariate balance before and after matching
+
+(ref:cobalt-any) by any parent migration
+
+(ref:cobalt-fa) by father-only migration
+
+(ref:cobalt-mo) by mother-only migration
+
+(ref:cobalt-both) by both parents migration
+
+```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
+fig_cog
 ```
 
-```{r tab-reg-ttl-adj}
-table_adj_ttl
+```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
+fig_ttl
 ```
 
-```{r tab-reg-m-adj-cog}
-table_m_adj_cog
+```{r v-plot-cog-1, fig.cap = paste("(ref:cog-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
+fig_cog_by_migration_type
 ```
 
-```{r tab-reg-m-adj-ttl}
-table_m_adj_ttl
+```{r v-plot-ttl-1, fig.cap = paste("(ref:ttl-dif)", "(ref:migr-type)"), out.height='40%', warning=FALSE}
+fig_ttl_by_migration_type
 ```
@@
 \newpage
+
+```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)"), out.height='40%'}
+m.out |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)"), out.height='40%'}
+m.out_mo_only |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)"), out.height='40%'}
+m.out_fa_only |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)"), out.height='40%'}
+m.out_both |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```

### 2023-11-09 MScThesisText.Rmd
Add latest literature

@@
     affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Dr.-Karl-Dorrek-Strasse 30, 3500 Krems, Austria"
+    email         : "jiancheng.gu@donau-uni.ac.at"
 
@@
   - id            : "1"
-    institution   : "Faculty of Social Sciences, Vrije Universiteit Amsterdam"
+    institution   : "Department for Migration and Globalisation, Universität für Weiterbildung Krems"
 
 note: |
-  May 15, 2023
+  `r format(Sys.time(), '%B %d, %Y')`
 
 authornote: | 
-  This paper's open science repository: https://github.com/jianchenggu/MScThesis
-  An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).
+  This paper's open science repository: https://github.com/jchgu/MScThesis
 
@@
 keywords          : "labor migration, left-behind children, educational performance"
-wordcount         : "6,789"
+wordcount         : "6,000"
 
-floatsintext      : yes
-linenumbers       : no
+floatsintext      : no
+linenumbers       : yes
 draft             : no
@@
   - "appendix.Rmd"
-  - "appendix-b.Rmd"
+
 bibliography: references.bib
@@
 
-# Introduction
+## Introduction
 
@@
 Consider children's education.
-According to the review articles by @venta2022 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to @venta2022 and @vanhook2020, labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 To what degree can the inflow of remittances compensate for the loss of parental attention?
@@
 
-A challenge arises in estimating the effect of parent's migration on children's educational achievement.
-Experiments can unveil causal relations.
-It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause be on par with random assignment to participants, conditional on identification assumptions.
+Quantitative social scientists have researched extensively about the education of left-behind children, but recent literature still has shortcomings.
+Some studies fail to capture the dynamic nature of migratory process as they draw upon cross-sectional data that focus on single time points [e.g.
+@ahmed2023; @vietnguyen2023; @gong2023].
+Some other studies only probe correlation using regression analysis [e.g.
+@chen2023a; @liu2023; @huang2020].
+These studies could have employed causal inference techniques.
 
@@
 
-## China's Context
+### China's Context
 
@@
 The institutional discrimination against labor migrants finds its roots in China's "multilevel citizenship" system.
-As @vortherms2021 explained, the constituents of citizenship -- "membership rules and rights entitlements" -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through *hukou*, or the household registration system:
-
-> A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status ...
-Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-[@vortherms2021]
-
-In other words, the hukou system binds one's citizenship rights with one's place of registration.
+As @vortherms2023 explained, the constituents of citizenship -- "membership rules" and "rights entitlements" -- operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through *hukou*, or the household registration system.
+The system differentiates people into local versus external and urban versus rural.
+In the rural-urban divide, urban hukou holders enjoy greater access to higher-quality welfare benefits and public services compared to rural hukou holders.
+In the local-external divide, local hukou holders are those registered in the same county where they live.
 In theory, Chinese citizens can migrate freely within the country.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city [@zhang2018; @wan2022].
+Before receiving urban hukou, they can hardly send their children into public schools in the host city [@zhang2018; @chen2023c].
+These institutions turn rural migrants into second-class citizens in effect.
 Migrant workers have organized petitions, strikes, and protests.
@@
 How does China counter the issue of labor migration and left-behind children?
-According to @wang2020 and @dong2020, the government has gradually liberalized the multilevel citizenship scheme.
+According to @dong2020, the government has gradually liberalized the multilevel citizenship scheme.
 It has introduced residence permit for internal migrants as the basis for social entitlements.
@@
 
-Social scientists have researched extensively about the education of Chinese left-behind children, but the current literature still has three major shortcomings.
-The first shortcoming lies in sampling.
-For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas [e.g.
-@hu2019; @zhou2014].
-@alpermann2020 pointed that the Chinese government reinforces "an urban hierarchy" besides the rural-urban divide.
-In the hierarchy's bottom are small- and medium-sized cities in the inland.
-They also see parents migrating to metropolises and leaving children behind [@wang2023].
-The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue [@nbs2017].
-The second shortcoming lies in research design.
-Some studies rely on cross-sectional data that focus on single time points [e.g.
-@khalid2022].
-These studies fail to capture the dynamic nature of migratory journey.
-Some other studies probe correlation from panel data using basic ordinary least squares regression [e.g.
-@chen2023a].
-These studies could have employed causal inference techniques.
-The third shortcoming lies in the measurement of outcome.
-@chang2019 and @wang2019 measured students' educational performance with the standardized test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-My sample includes urban left-behind children as well.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
-
-## Theory and Hypotheses
+### Theory and Hypotheses
 
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital [@debrauw2019; @shen2021].
-Economic capital is, in Bourdieu's words, "immediately and directly convertible into money and may be institutionalized in the form of property rights" [-@bourdieu2002, p.16].
-Economic resources can help individuals acquire human capital, which is the stock of "knowledge, skills, and health that people accumulate over their lives" [@worldbank2020, p.1].
+It holds that parental migration brings forth greater resources that can help children acquire human capital -- the stock of "knowledge, skills, and health that people accumulate over their lives" [@worldbank2020, p.1].
 @yang2008 noted that in the Philippines, a sharp depreciation of peso increased the amount of remittances from migrants working abroad.
 This subsequently boosted children's school enrollment and educational spending.
-@vikram2021 performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged 8-11.
+@vikram2021 performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged eight to eleven.
 She showed that fathers' migration was linked with increases in left-behind children's reading capability and educational expenditure (p.
@@
 1].
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents.
-Hong talked to a group of left-behind children at a rural school [@hong2019].
-These students expressed the utter sense of loneliness "with no advocate, no support and with no one looking out for them" (p.
-13).
-Many of them felt indifferent to grades and disengaged with school.
-Some even longed to quit school to pursue a free, independent life (p.
-14).
-@murphy2022 talked to left-behind adolescents at a Chinese village.
+According to @chen2023, caregiver-child interactions are infrequent and unstable for left-behind children.
+The loss in such interactions "mediates almost all of the adverse effects of parental absence." This conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
+@murphy2022 talked to children left behind in a Chinese village.
 Some of them "embraced the 'left-behind' label" because it captured their need for more parental care (p.
@@
 186).
-According to @chen2023, caregiver-child interactions are infrequent and unstable for left-behind children.
-She showed that the loss in such interactions "mediates almost all of the adverse effects of parental absence." Her conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
+In Romania, @udrea2022 and @diaconu-gherasim2023 interviewed left-behind adolescents.
+Many of them felt disorientated about the lack of parents' support and oversight in schoolwork.
 
@@
 They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
-The team of @wang2019 collected data from junior high school students in central China.
+@wang2019 collected data from junior high school students in central China.
 Their two-way fixed-effect model showed no significant effect of parental migration on left-behind children's achievement in mathematical test.
+@chae2019 analyzed the Migration and Remittances Household Survey of Kenya, Senegal, and Burkina Faso.
+They observed significant correlation between parental migration and left-behind children's school enrollment in Kenya, but not in the other two West African countries.
 @nguyen2016 conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
@@
 Researchers have studied whether the impact differs between mother's migration and father's migration.
+@liu2023 analyzed how fifteen-year-old students' academic performance is associated with parental absence across 59 countries, using the 2012 Program of International Student Assessment data.
+Compared to students living with both parents, students perform worse in academic tests when only mother is absent or both parents are absent; When only father is absent, however, students are not significantly below par.
 @xu2019 adopted a fixed-effects propensity score weighting model on cross-sectional data collected from seventh and ninth graders in rural areas across China.
@@
 
-@murphy2020 noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+@murphy2020 and @fan2023 noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
 Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles [@murphy2020].
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
 I propose the second hypothesis:
@@
 
-\newpage
+## Methods
 
-# Methods
-
-## Sampling
+### Sampling
 
@@
 
-## Measurement
+### Measurement
 
@@
 
-The lists of covariates are in Table \@ref(tab:tab-ctvar-dit) -- Table \@ref(tab:tab-ctvar-msr) in the Results section.
-At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child attends boarding school, and whether the child had skipped grade or repeated grade.
+The lists of covariates are in Table 1 -- Table 5 in the Results section.
+At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child had attended preschool, and whether the child attends boarding school.
 Age, sex, and health are associated with educational performance [@gu2021a].
-Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school [@hasmath2022; @xu2018; @huang2020].
-I controlled for boarding at school because research results vary regarding the effect of boarding at school on academic performance [@liu2020a; @guo2021].
-I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family [@guo2022].
+Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school [@hasmath2023; @xu2018; @huang2020].
+Attending preschool in early childhood and enrolling in boarding school in adolescence are predictors of educational performance [@liu2020a; @guo2021; @zheng2021].
+I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family [@doepke2015].
 At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
@@
 
-## Analytical Strategy
+### Analytical Strategy
 
@@
 
-I adopted `R` (version 4.3.0) for all the analyses [@R-base].
-This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.3) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].
+I adopted `R` (version 4.3.2) for all the analyses [@R-base].
+This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.3) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.5) and `cobalt` (version 4.5.1) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.4.3), `vtable` (version 1.4.5), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra].
 
-\newpage
+## Results
 
-# Results
+### Descriptive Statistics
 
-## Descriptive Statistics
-
-Table \@ref(tab:tab-idpvar) illustrates the independent variables, namely the migration status reported in the wave two survey.
+Table 1 illustrates the independent variables, namely the migration status reported in the wave two survey.
 All `r printnum(nrow(d_cl))` children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
@@
 
-\renewcommand{\arraystretch}{0.72}
+\renewcommand{\arraystretch}{0.8}
 
 ```{r tab-idpvar}
-datasummary_df(
-  data = tab_idpvar,
-  output = 'markdown',
-  title = 'Independent variables by parental migration'
-)
+tab_idpvar |>
+  kbl(booktabs = T, caption = 'Independent variables by parental migration')
 ```
 
-\newpage
-
-The dependent variables are summarized by the control group versus the treatment group in Table \@ref(tab:tab-dpvar) below and Figure \@ref(fig:v-plot-cog) -- Figure \@ref(fig:v-plot-ttl-1) in the appendix.
+The dependent variables are summarized by the control group versus the treatment group in Table 2 and Figure 1 -- Figure 2.
 Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
@@
   add_indent(c(2,3,5,6)) |>
-  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
+  add_header_above(c(" ", "No = 3529" = 2, "Yes = 675" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
 
-\newpage
-
-Table \@ref(tab:tab-ctvar-dit) summarizes the bivariate analysis on the binary control variables.
+Table 3 summarizes the bivariate analysis on the binary control variables.
 New migration households had lower internet access rate.
@@
   kbl(booktabs = T, caption = 'Dichotomous control variables by parental migration', row.names = F) |>
-  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
+  add_header_above(c(" ", "No = 3529" = 2, "Yes = 675" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
 
-\newpage
-
-Table \@ref(tab:tab-ctvar-cnt) displays the bivariate analysis for categorical control variables, and Table \@ref(tab:tab-ctvar-msr) documents their measurement scales.
+Table 4 displays the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
 While the majority of mothers and fathers had only finished high school or below, they held big expectations for children.
@@
   kbl(booktabs = T, caption = 'Categorical and continuous control variables by parental migration', row.names = F) |>
-  add_header_above(c(" ", "No = 3465" = 2, "Yes = 649" = 2)) |>
+  add_header_above(c(" ", "No = 3529" = 2, "Yes = 675" = 2)) |>
   add_header_above(c(" ", "Parental Migration" = 4)) |>
@@
 
-\newpage
-
 ```{r tab-ctvar-msr}
-datasummary_df(
-  data = tab_var,
-  title = 'Measurement and distribution of categorical variables',
-  output = 'markdown'
-)
+tab_var |>
+  kbl(booktabs = T, caption = 'Measurement and distribution of categorical variables')
 ```
 
-\newpage
-
-## Regression Analysis
+### Regression Analysis
 
 I first explain the results on children's cognitive test score.
-The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6 below).
+The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6).
 This lends support to Hypothesis 1a.
@@
 Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (`r coef(did_cog_f_only)[1] |> abs() |> round(2)` points) in cognitive test score than those with only mother absent (`r coef(did_cog_m_only)[1] |> abs() |> round(2)` points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in the appendix).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table 7).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
@@
 
+```{r tab-reg-cog-adj}
+table_adj_cog
+```
+
 Next, I set forth the results on children's academic test grades.
-In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
+In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 8 below).
 Parental migration is associated with a drop of `r coef(did_ttl)[1] |> abs() |> round(2)` points in academic exam score.
@@
 In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
-The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in the appendix).
+The adjusted DID models' results largely resemble those from the unadjusted models (See Table 9 in the appendix).
 Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
-
-\newpage
 
@@
 table_ttl
+```
+
+```{r tab-reg-ttl-adj}
+table_adj_ttl
 ```
@@
 The coefficients are `r round(coef(did_adj_cog)[14],2)` points and `r round(coef(did_adj_cog)[12],2)` points for cognitive test, respectively; and `r round(coef(did_adj_ttl)[14],2)` points and `r round(coef(did_adj_ttl)[12],2)` points for academic exams, respectively.
-
-Several predictors are strong in predicting one outcome but not the other.
-Covariates that only relate to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
+Some predictors are strong in predicting one outcome but not the other.
+The covariate that only relates to academic grades is children's gender.
 Girls outperform boys by `r round(coef(did_adj_ttl)[4],2)` points in academic exams, but do not show advantage in cognitive tests.
-Students who consider themselves healthier are associated with higher scores in academic exams.
-On the contrary, those who report having more extracurricular books at home are associated with lower scores in academic exams.
-Covariates that only relate to cognitive scores is the number of siblings.
+Another covariate, the number of siblings, i sonly relate to cognitive scores.
 Having an additional sibling is associated with lower cognitive score of `r coef(did_adj_cog)[7] |> abs() |> round(2)` points.
 
-\newpage
-
-## Matching
+### Matching
 
@@
 To tackle this bias, an applicable technique is matching.
-It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates [@sävje2021].
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
 
@@
 When handling this distance, PSM can match the units with two approaches.
-One is the nearest-neighbor approach.
+One is the nearest-neighbor matching.
 It examines all the treated units and selects the control unit closest in distance for pairing.
 This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
-The second approach, the optimal-pair approach, works in a similar fashion but tries to minimize the absolute pairwise distances in total [@pan2018].
+The second approach is the optimal approach.
+It minimizes the total distance in propensity scores between the treatment and control groups.
+Optimal matching can assign a treated unit with more than one control unit, thereby retaining the full sample [@hansen2023].
 
@@
 My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
-I then made do with PSM.
-I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
-Exact matching based on county of residence can preserve the original geographic distribution [@bai2018].
-The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio of 3:1 means that one treatment unit would pair with up to three control units.
+I then made do with PSM by performing optimal full matching.
+The propensity score was estimated using a logistic regression of the treatment on all the covariates.
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
@@
 
-The results from models with matching strongly resemble the models without matching, as shown in Table 8 -- Table 9 below and Table A3 -- Table A4 in the appendix.
+The results from models with matching strongly resemble the models without matching, as shown in Table 10 -- Table 13.
 In the models of cognitive test score, I obtained negative, statistically significant coefficients on all treatment variables except that of both-parents-migrated households.
@@
 
-\newpage
+```{r tab-reg-m-adj-cog}
+table_m_adj_cog
+```
 
@@
 
-\newpage
+```{r tab-reg-m-adj-ttl}
+table_m_adj_ttl
+```
 
-# Discussion and Conclusion
+## Discussion and Conclusion
 
@@
 
-## Limitations
+### Limitations
 
@@
 
-## Recommendations
+### Recommendations
 
@@
 Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@antia2020; @pang2022].
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence [@raturi2023; @zhao2022a].
 
+The children in the CEPS survey have grown into young adults.
+Would they repeat their parents' choice, leaving the next generation of children behind?
+That depends on the actions of stakeholders.
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
-In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023; @deng2023].
+In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant [@jiemiannews2023].
 This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit.
@@
 School administrators could dedicate more advisory and counseling programs.
-Social workers could provide paraprofessional training in communities [@wang2020a].
+Social workers could provide paraprofessional training and community workers can organize children's centers in local areas [@jiang2020; @wang2020a].
+
+\newpage
+
+(ref:cog-dif) Changes in cognitive test score
+
+(ref:ttl-dif) Changes in academic exam score
+
+(ref:migr) for newly left-behind students and non-left-behind students
+
+(ref:migr-type) by household migration arrangement
+
+(ref:cobalt-match) Covariate balance before and after matching
+
+(ref:cobalt-any) by any parent migration
+
+(ref:cobalt-fa) by father-only migration
+
+(ref:cobalt-mo) by mother-only migration
+
+(ref:cobalt-both) by both parents migration
+
+```{r v-plot-cog, fig.cap = paste("(ref:cog-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
+fig_cog
+```
+
+```{r v-plot-ttl, fig.cap = paste("(ref:ttl-dif)", "(ref:migr)"), out.height='40%', warning=FALSE}
+fig_ttl
+```
+
+\newpage
+
+```{r cobal-any, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-any)"), out.height='40%'}
+m.out |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-mo, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-mo)"), out.height='40%'}
+m.out_mo_only |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-fa, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-fa)"), out.height='40%'}
+m.out_fa_only |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
+
+```{r cobal-both, fig.cap = paste("(ref:cobalt-match)", "(ref:cobalt-both)"), out.height='40%'}
+m.out_both |> love.plot(
+  threshold = c(m = .1),
+  binary = "std", 
+  limits = c(0, 0.55),
+  abs = T
+  )
+```
 
@@
 
-# (APPENDIX) the appendix {.unnumbered}
+# (APPENDIX) Appendix {.unnumbered}
 
@@
 ```
-
-```{r child = "appendix-b.Rmd"}
-```

### 2023-11-09 MScThesisText.tex
Add latest literature

@@
 \documentclass[
-  man,floatsintext]{apa7}
+  man]{apa7}
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 {}{\PatchFailed}
-\keywords{labor migration, left-behind children, educational performance\newline\indent Word count: 6,789}
+\keywords{labor migration, left-behind children, educational performance\newline\indent Word count: 6,000}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-This paper's open science repository: \url{https://github.com/jianchenggu/MScThesis}
-An earlier version of this article was submitted in partial fulfillment of the requirements for the degree -- Master of Science in Societal Resilience (Research).
+This paper's open science repository: \url{https://github.com/jchgu/MScThesis}
+
+Correspondence concerning this article should be addressed to Jiancheng Gu, Dr.-Karl-Dorrek-Strasse 30, 3500 Krems, Austria.
+E-mail: \href{mailto:jiancheng.gu@donau-uni.ac.at}{\nolinkurl{jiancheng.gu@donau-uni.ac.at}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Social Sciences, Vrije Universiteit Amsterdam}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department for Migration and Globalisation, Universität für Weiterbildung Krems}
 
@@
 
-May 15, 2023
+November 09, 2023
 
@@
 \hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\subsection{Introduction}\label{introduction}}
 
@@
 Consider children's education.
-According to the review articles by Venta and Cuervo (2022) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
+According to Venta and Cuervo (2022) and Van Hook and Glick (2020), labor migrants send remittances back, which can fund children's schooling as well as improve their nutritional and living conditions.
 To what degree can the inflow of remittances compensate for the loss of parental attention?
@@
 
-A challenge arises in estimating the effect of parent's migration on children's educational achievement.
-Experiments can unveil causal relations.
-It is unfeasible and unethical to design an experiment that randomly assigns parents to migrate without their children.
-Alternatively, a quasi-experimental design can help with causal inference.
-It requires that the cause be on par with random assignment to participants, conditional on identification assumptions.
+Quantitative social scientists have researched extensively about the education of left-behind children, but recent literature still has shortcomings.
+Some studies fail to capture the dynamic nature of migratory process as they draw upon cross-sectional data that focus on single time points (e.g.
+Ahmed et al., 2023; Gong \& Rao, 2023; Viet Nguyen \& Hoang Vu, 2023).
+Some other studies only probe correlation using regression analysis (e.g.
+L.
+Chen et al., 2023; Huang et al., 2020; R.
+Liu \& Hannum, 2023).
+These studies could have employed causal inference techniques.
 
@@
 \hypertarget{chinas-context}{%
-\subsection{China's Context}\label{chinas-context}}
+\subsubsection{China's Context}\label{chinas-context}}
 
@@
 They form the backbone of essential industries, such as retail, transportation, and manufacturing.
-The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS, 2022; NBS et al., 2017).
+The 2015 one-percent National Population Sample Survey estimated that 68.7 million Chinese children were left behind (NBS et al., 2017; NBS, 2022).
 
@@
 The institutional discrimination against labor migrants finds its roots in China's ``multilevel citizenship'' system.
-As Vortherms (2021) explained, the constituents of citizenship -- ``membership rules and rights entitlements'' -- operate below the national level in China.
-The local state confers most of the rights and defines who is eligible to these rights through \emph{hukou}, or the household registration system:
-
-\begin{quote}
-A political institution rooted in centuries of Chinese bureaucracy, the modern hukou is the primary identity document defining membership and entitlements for local citizenship.
-Accessing fundamental citizenship rights depends on your registration status \ldots{} Registration includes basic identifying information, a specific address of registration, and a type: urban, rural, or resident.
-(Vortherms, 2021)
-\end{quote}
-
-In other words, the hukou system binds one's citizenship rights with one's place of registration.
+As Vortherms (2023) explained, the constituents of citizenship -- ``membership rules'' and ``rights entitlements'' -- operate below the national level in China.
+The local state confers most of the rights and defines who is eligible to these rights through \emph{hukou}, or the household registration system.
+The system differentiates people into local versus external and urban versus rural.
+In the rural-urban divide, urban hukou holders enjoy greater access to higher-quality welfare benefits and public services compared to rural hukou holders.
+In the local-external divide, local hukou holders are those registered in the same county where they live.
 In theory, Chinese citizens can migrate freely within the country.
@@
 When rural residents move to the city, it takes months -- if not years -- to apply for a new hukou.
-Before receiving urban hukou, they can hardly send their children into public schools in the host city (Wan \& Vickers, 2022; Zhang, 2018).
+Before receiving urban hukou, they can hardly send their children into public schools in the host city (Y.
+Chen \& Fu, 2023; Zhang, 2018).
+These institutions turn rural migrants into second-class citizens in effect.
 Migrant workers have organized petitions, strikes, and protests.
@@
 How does China counter the issue of labor migration and left-behind children?
-According to X.
-Wang (2020) and Dong and Goodburn (2020), the government has gradually liberalized the multilevel citizenship scheme.
+According to Dong and Goodburn (2020), the government has gradually liberalized the multilevel citizenship scheme.
 It has introduced residence permit for internal migrants as the basis for social entitlements.
@@
 
-Social scientists have researched extensively about the education of Chinese left-behind children, but the current literature still has three major shortcomings.
-The first shortcoming lies in sampling.
-For many studies, the geographic coverage is limited to one to a few counties; The participants are children left behind in rural areas but not those in urban areas (e.g.
-Hu, 2019; Zhou et al., 2014).
-Alpermann (2020) pointed that the Chinese government reinforces ``an urban hierarchy'' besides the rural-urban divide.
-In the hierarchy's bottom are small- and medium-sized cities in the inland.
-They also see parents migrating to metropolises and leaving children behind (S.
-Wang, 2023).
-The National Bureau of Statistics noted that the number of urban left-behind children have been growing, and the trend is expected to continue (NBS et al., 2017).
-The second shortcoming lies in research design.
-Some studies rely on cross-sectional data that focus on single time points (e.g.
-Khalid et al., 2022).
-These studies fail to capture the dynamic nature of migratory journey.
-Some other studies probe correlation from panel data using basic ordinary least squares regression (e.g.
-L.
-Chen et al., 2023).
-These studies could have employed causal inference techniques.
-The third shortcoming lies in the measurement of outcome.
-Chang et al.
-(2019) and L.
-Wang et al.
-(2019) measured students' educational performance with the standardized test score of only one academic subject, namely mathematics.
-To tackle these limitations, I adopted a nationally representative two-wave panel dataset.
-My sample includes urban left-behind children as well.
-I included the test results of multiple subjects to measure comprehensive academic achievement.
-
 \hypertarget{theory-and-hypotheses}{%
-\subsection{Theory and Hypotheses}\label{theory-and-hypotheses}}
+\subsubsection{Theory and Hypotheses}\label{theory-and-hypotheses}}
 
@@
 One is the resource generation model.
-It holds that parental migration brings forth greater resources in the form of economic capital (Brauw, 2019; Shen et al., 2021).
-Economic capital is, in Bourdieu's words, ``immediately and directly convertible into money and may be institutionalized in the form of property rights'' (2002, p.
-16).
-Economic resources can help individuals acquire human capital, which is the stock of ``knowledge, skills, and health that people accumulate over their lives'' (World Bank, 2020, p.
+It holds that parental migration brings forth greater resources that can help children acquire human capital -- the stock of ``knowledge, skills, and health that people accumulate over their lives'' (World Bank, 2020, p.
 1).
@@
 This subsequently boosted children's school enrollment and educational spending.
-Vikram (2021) performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged 8-11.
+Vikram (2021) performed propensity score matching and fixed-effect regression on a two-wave panel dataset featuring Indian children aged eight to eleven.
 She showed that fathers' migration was linked with increases in left-behind children's reading capability and educational expenditure (p.~991).
@@
 1).
-Parental migration decreases nurturing care, as characterized by less homework supervision and emotional support by parents.
-Hong talked to a group of left-behind children at a rural school (Hong \& Fuller, 2019).
-These students expressed the utter sense of loneliness ``with no advocate, no support and with no one looking out for them'' (p.~13).
-Many of them felt indifferent to grades and disengaged with school.
-Some even longed to quit school to pursue a free, independent life (p.~14).
-Murphy (2022) talked to left-behind adolescents at a Chinese village.
-Some of them ``embraced the `left-behind' label'' because it captured their need for more parental care (p.~185), ``especially companionship and affection in daily life'' (p.~186).
 According to C.
 Chen (2023), caregiver-child interactions are infrequent and unstable for left-behind children.
-She showed that the loss in such interactions ``mediates almost all of the adverse effects of parental absence.'' Her conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
+The loss in such interactions ``mediates almost all of the adverse effects of parental absence.'' This conclusion was based on structural equation modeling using a cross-sectional survey with a sample of Chinese children aged three to fifteen.
+Murphy (2022) talked to children left behind in a Chinese village.
+Some of them ``embraced the `left-behind' label'' because it captured their need for more parental care (p.~185), ``especially companionship and affection in daily life'' (p.~186).
+In Romania, Udrea and Guiu (2022) and Diaconu-Gherasim et al.
+(2023) interviewed left-behind adolescents.
+Many of them felt disorientated about the lack of parents' support and oversight in schoolwork.
 
@@
 They found a positive effect of parents' migration on academic grades of adolescents aged eleven to fifteen in Romania.
-The team of L.
+L.
 Wang et al.
@@
 Their two-way fixed-effect model showed no significant effect of parental migration on left-behind children's achievement in mathematical test.
+Chae and Glick (2019) analyzed the Migration and Remittances Household Survey of Kenya, Senegal, and Burkina Faso.
+They observed significant correlation between parental migration and left-behind children's school enrollment in Kenya, but not in the other two West African countries.
 Nguyen (2016) conducted fixed-effect regression and demonstrated that parental migration was associated with lower cognitive capabilities among Indian and Vietnamese children aged five to eight.
@@
 Researchers have studied whether the impact differs between mother's migration and father's migration.
+R.
+Liu and Hannum (2023) analyzed how fifteen-year-old students' academic performance is associated with parental absence across 59 countries, using the 2012 Program of International Student Assessment data.
+Compared to students living with both parents, students perform worse in academic tests when only mother is absent or both parents are absent; When only father is absent, however, students are not significantly below par.
 Xu et al.
@@
 
-Murphy (2020) noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
+Murphy (2020) and Fan (2023) noted that in some Asian and Latin American societies, the social norms designate men as breadwinners and women as caregivers.
 Under such norms, fathers' migration is more likely to win children's acceptance than does mothers' migration.
-Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles (Murphy, 2020).
+Left-behind children may even resent their migrant mothers for transgressing on the expected care-giving roles.
 I propose the second hypothesis:
@@
 
-\newpage
-
 \hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\subsection{Methods}\label{methods}}
 
 \hypertarget{sampling}{%
-\subsection{Sampling}\label{sampling}}
+\subsubsection{Sampling}\label{sampling}}
 
@@
 To tackle missing values, I adopted list-wise deletion for the dependent, independent, and control variables.
-The final sample size amounts to 4114.
+The final sample size amounts to 4204.
 
 \hypertarget{measurement}{%
-\subsection{Measurement}\label{measurement}}
+\subsubsection{Measurement}\label{measurement}}
 
@@
 
-The lists of covariates are in Table~\ref{tab:tab-ctvar-dit} -- Table~\ref{tab:tab-ctvar-msr} in the Results section.
-At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child attends boarding school, and whether the child had skipped grade or repeated grade.
+The lists of covariates are in Table 1 -- Table 5 in the Results section.
+At the children's level, I controlled for age, sex, self-rated health, ethnicity, hukou type, number of siblings, whether the child had attended preschool, and whether the child attends boarding school.
 Age, sex, and health are associated with educational performance (Gu \& Yeung, 2021).
-Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school (Hasmath, 2022; Huang et al., 2020; D.
+Regarding ethnicity and hukou status, Han Chinese and urban hukou holders outperform ethnic minorities and rural hukou holders at school (Hasmath, 2023; Huang et al., 2020; D.
 Xu et al., 2018).
-I controlled for boarding at school because research results vary regarding the effect of boarding at school on academic performance (S.
-Guo et al., 2021; M.
-Liu \& Villa, 2020).
-I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family (R.
-Guo et al., 2022).
+Attending preschool in early childhood and enrolling in boarding school in adolescence are predictors of educational performance (Guo et al., 2021; M.
+Liu \& Villa, 2020; Zheng et al., 2021).
+I also included the number of siblings as a covariate, considering the quantity-quality trade-off in multi-child family (Doepke, 2015).
 At the household level, I controlled for the levels of education of father and mother, whether the parent has a white collar job, whether the household has internet access, the perceived household financial conditions, and the number of extracurricular books at home.
@@
 \hypertarget{analytical-strategy}{%
-\subsection{Analytical Strategy}\label{analytical-strategy}}
+\subsubsection{Analytical Strategy}\label{analytical-strategy}}
 
@@
 
-I adopted \texttt{R} (version 4.3.0) for all the analyses (R Core Team, 2022).
-This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.3) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2023; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).
-
-\newpage
+I adopted \texttt{R} (version 4.3.2) for all the analyses (R Core Team, 2022).
+This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.3) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.5) and \texttt{cobalt} (version 4.5.1) for matching (Greifer, 2023; Ho et al., 2011, 2023); \texttt{modelsummary} (version 1.4.3), \texttt{vtable} (version 1.4.5), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021).
 
 \hypertarget{results}{%
-\section{Results}\label{results}}
+\subsection{Results}\label{results}}
 
 \hypertarget{descriptive-statistics}{%
-\subsection{Descriptive Statistics}\label{descriptive-statistics}}
-
-Table~\ref{tab:tab-idpvar} illustrates the independent variables, namely the migration status reported in the wave two survey.
-All 4114 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
+\subsubsection{Descriptive Statistics}\label{descriptive-statistics}}
+
+Table 1 illustrates the independent variables, namely the migration status reported in the wave two survey.
+All 4204 children were living with parents in one household in baseline, but about sixteen percent saw at least one parent migrated between the two waves of survey.
 I call these students ``newly left-behind children'' and their households ``new migration households.'' In these new migration households, only-mother migration and only-father migration each accounted for two out of five cases.
@@
 
-\renewcommand{\arraystretch}{0.72}
-
-\begin{longtable}[]{@{}lll@{}}
-\caption{\label{tab:tab-idpvar}Independent variables by parental migration}\tabularnewline
-\toprule()
-Variable & N & Percent \\
-\midrule()
-\endfirsthead
-\toprule()
-Variable & N & Percent \\
-\midrule()
-\endhead
+\renewcommand{\arraystretch}{0.8}
+
+\begin{table}
+
+\caption{\label{tab:tab-idpvar}Independent variables by parental migration}
+\centering
+\begin{tabular}[t]{lll}
+\toprule
+Variable & N & Percent\\
+\midrule
 Parental Migration &  & \\
-\ldots{} No & 3465 & 84\% \\
-\ldots{} Yes & 649 & 16\% \\
+... No & 3529 & 84\%\\
+... Yes & 675 & 16\%\\
 Parental Migration Type &  & \\
-\ldots{} Both Parents at Home & 3465 & 84\% \\
-\ldots{} Both Parents Migrated & 132 & 3\% \\
-\ldots{} Only Father Migrated & 256 & 6\% \\
-\ldots{} Only Mother Migrated & 261 & 6\% \\
-\bottomrule()
-\end{longtable}
-
-\newpage
-
-The dependent variables are summarized by the control group versus the treatment group in Table~\ref{tab:tab-dpvar} below and Figure~\ref{fig:v-plot-cog} -- Figure~\ref{fig:v-plot-ttl-1} in the appendix.
+... Both Parents at Home & 3529 & 84\%\\
+\addlinespace
+... Both Parents Migrated & 142 & 3\%\\
+... Only Father Migrated & 266 & 6\%\\
+... Only Mother Migrated & 267 & 6\%\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+The dependent variables are summarized by the control group versus the treatment group in Table 2 and Figure 1 -- Figure 2.
 Compared to non-left-behind peers, newly left-behind children scored lower in wave two's cognitive and academic tests; Their cognitive test score increased less and their academic exam score dropped more.
@@
 \cmidrule(l{3pt}r{3pt}){2-5}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3465} & \multicolumn{2}{c}{Yes = 649} \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{No = 3529} & \multicolumn{2}{c}{Yes = 675} \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
@@
 \midrule
-Cognitive test score difference & 11 & 20 & 9.6 & 21 & p=0.027*\\
-\hspace{1em}Wave 1 score & 57 & 17 & 56 & 17 & p=0.312\\
-\hspace{1em}Wave 2 score & 68 & 18 & 66 & 20 & p=0.001**\\
-Academic exam score difference & -2.8 & 11 & -4.1 & 12 & p=0.007**\\
-\hspace{1em}Wave 1 score & 71 & 16 & 70 & 17 & p=0.24\\
+Cognitive test score difference & 11 & 20 & 9.7 & 21 & p=0.031*\\
+\hspace{1em}Wave 1 score & 57 & 17 & 56 & 17 & p=0.174\\
+\hspace{1em}Wave 2 score & 68 & 19 & 65 & 20 & p<0.001***\\
+Academic exam score difference & -2.8 & 11 & -4 & 12 & p=0.01**\\
+\hspace{1em}Wave 1 score & 71 & 16 & 70 & 17 & p=0.077\\
 \addlinespace
-\hspace{1em}Wave 2 score & 68 & 18 & 66 & 20 & p=0.008**\\
+\hspace{1em}Wave 2 score & 68 & 18 & 66 & 20 & p=0.002**\\
 \bottomrule
@@
 
-\newpage
-
-Table~\ref{tab:tab-ctvar-dit} summarizes the bivariate analysis on the binary control variables.
+Table 3 summarizes the bivariate analysis on the binary control variables.
 New migration households had lower internet access rate.
@@
 \midrule
-child.is.girl &  &  &  &  & X2=12.716***\\
-... 0 & 1660 & 48\% & 361 & 56\% & \\
-... 1 & 1805 & 52\% & 288 & 44\% & \\
-child.has.rural.hukou &  &  &  &  & X2=1.106\\
-... 0 & 1912 & 55\% & 343 & 53\% & \\
+child.is.girl &  &  &  &  & X2=13.14***\\
+... 0 & 1694 & 48\% & 376 & 56\% & \\
+... 1 & 1835 & 52\% & 299 & 44\% & \\
+child.has.rural.hukou &  &  &  &  & X2=1.676\\
+... 0 & 1939 & 55\% & 352 & 52\% & \\
 \addlinespace
-... 1 & 1553 & 45\% & 306 & 47\% & \\
-child.in.boarding.school &  &  &  &  & X2=3.876*\\
-... 0 & 2500 & 72\% & 443 & 68\% & \\
-... 1 & 965 & 28\% & 206 & 32\% & \\
-child.is.ethnic.minority &  &  &  &  & X2=0.585\\
+... 1 & 1590 & 45\% & 323 & 48\% & \\
+child.in.boarding.school &  &  &  &  & X2=4.185*\\
+... 0 & 2545 & 72\% & 460 & 68\% & \\
+... 1 & 984 & 28\% & 215 & 32\% & \\
+child.is.ethnic.minority &  &  &  &  & X2=0.582\\
 \addlinespace
-... 0 & 3230 & 93\% & 599 & 92\% & \\
-... 1 & 235 & 7\% & 50 & 8\% & \\
-child.had.skipped.grade &  &  &  &  & X2=0.054\\
-... 0 & 3429 & 99\% & 641 & 99\% & \\
-... 1 & 36 & 1\% & 8 & 1\% & \\
+... 0 & 3289 & 93\% & 623 & 92\% & \\
+... 1 & 240 & 7\% & 52 & 8\% & \\
+child.went.to.preschool &  &  &  &  & X2=1.254\\
+... 0 & 538 & 15\% & 115 & 17\% & \\
+... 1 & 2991 & 85\% & 560 & 83\% & \\
 \addlinespace
-child.had.repeated.grade &  &  &  &  & X2=12.906***\\
-... 0 & 3160 & 91\% & 562 & 87\% & \\
-... 1 & 305 & 9\% & 87 & 13\% & \\
-child.went.to.preschool &  &  &  &  & X2=0.826\\
-... 0 & 530 & 15\% & 109 & 17\% & \\
+parent.has.white.collar.job &  &  &  &  & X2=0.125\\
+... 0 & 2531 & 72\% & 479 & 71\% & \\
+... 1 & 998 & 28\% & 196 & 29\% & \\
+home.has.internet &  &  &  &  & X2=15.73***\\
+... 0 & 1087 & 31\% & 261 & 39\% & \\
 \addlinespace
-... 1 & 2935 & 85\% & 540 & 83\% & \\
-parent.has.white.collar.job &  &  &  &  & X2=0.001\\
-... 0 & 2739 & 79\% & 512 & 79\% & \\
-... 1 & 726 & 21\% & 137 & 21\% & \\
-home.has.internet &  &  &  &  & X2=13.27***\\
-\addlinespace
-... 0 & 1064 & 31\% & 247 & 38\% & \\
-... 1 & 2401 & 69\% & 402 & 62\% & \\
+... 1 & 2442 & 69\% & 414 & 61\% & \\
 \bottomrule
@@
 
-\newpage
-
-Table~\ref{tab:tab-ctvar-cnt} displays the bivariate analysis for categorical control variables, and Table~\ref{tab:tab-ctvar-msr} documents their measurement scales.
+Table 4 displays the bivariate analysis for categorical control variables, and Table 5 documents their measurement scales.
 While the majority of mothers and fathers had only finished high school or below, they held big expectations for children.
@@
 \midrule
-child.age & 12 & 0.63 & 13 & 0.73 & F=5.008*\\
-child.number.of.sibling & 0.58 & 0.74 & 0.66 & 0.82 & F=5.242*\\
-child.health & 4.2 & 0.87 & 4.1 & 0.89 & F=0.575\\
-child.education.aspiration & 4 & 1.1 & 3.9 & 1.2 & F=0.496\\
-mother.education.level & 1.5 & 1.2 & 1.6 & 1.3 & F=0.48\\
+child.age & 13 & 0.61 & 13 & 0.73 & F=2.996\\
+child.number.of.sibling & 0.58 & 0.74 & 0.66 & 0.84 & F=6.155*\\
+child.health & 4.2 & 0.87 & 4.1 & 0.9 & F=1.105\\
+child.education.aspiration & 3.9 & 1.2 & 3.9 & 1.3 & F=0.861\\
+parent.education.level & 1.9 & 1.2 & 1.9 & 1.2 & F=0.18\\
 \addlinespace
-father.education.level & 1.7 & 1.2 & 1.8 & 1.2 & F=0.413\\
-parent.expectation & 4.2 & 0.91 & 4.1 & 0.95 & F=1.598\\
-home.extracurricular.book & 3.4 & 1.2 & 3.3 & 1.3 & F=3.82\\
-home.economic.resource & 2.9 & 0.55 & 2.8 & 0.57 & F=1.399\\
+parent.expectation & 4.2 & 0.92 & 4.1 & 0.97 & F=2.394\\
+home.extracurricular.book & 3.4 & 1.2 & 3.3 & 1.3 & F=4.042*\\
+home.economic.resource & 2.9 & 0.55 & 2.8 & 0.57 & F=1.503\\
 \bottomrule
@@
 
-\newpage
-
-\begin{longtable}[]{@{}lll@{}}
-\caption{\label{tab:tab-ctvar-msr}Measurement and distribution of categorical variables}\tabularnewline
-\toprule()
-Variable & N & Percent \\
-\midrule()
-\endfirsthead
-\toprule()
-Variable & N & Percent \\
-\midrule()
-\endhead
+\begin{table}
+
+\caption{\label{tab:tab-ctvar-msr}Measurement and distribution of categorical variables}
+\centering
+\begin{tabular}[t]{lll}
+\toprule
+Variable & N & Percent\\
+\midrule
 child.health &  & \\
-\ldots{} 1 = Very poor & 21 & 1\% \\
-\ldots{} 2 = Somewhat poor & 112 & 3\% \\
-\ldots{} 3 = Moderate & 811 & 20\% \\
-\ldots{} 4 = Good & 1391 & 34\% \\
-\ldots{} 5 = Very good & 1779 & 43\% \\
+... 1 = Very poor & 24 & 1\%\\
+... 2 = Somewhat poor & 118 & 3\%\\
+... 3 = Moderate & 829 & 20\%\\
+... 4 = Good & 1424 & 34\%\\
+\addlinespace
+... 5 = Very good & 1809 & 43\%\\
 child.education.aspiration &  & \\
-\ldots{} 1 = Junior high school & 139 & 3\% \\
-\ldots{} 2 = Senior high school & 423 & 10\% \\
-\ldots{} 3 = Associate college & 622 & 15\% \\
-\ldots{} 4 = University & 1212 & 29\% \\
-\ldots{} 5 = Postgraduate & 1718 & 42\% \\
-mother.education.level & & \\
-\ldots{} 0 = Primary school and below & 710 & 17\% \\
-\ldots{} 1 = Junior high school & 1638 & 40\% \\
-\ldots{} 2 = Senior high school & 1048 & 25\% \\
-\ldots{} 3 = Associate college & 307 & 7\% \\
-\ldots{} 4 = University & 372 & 9\% \\
-\ldots{} 5 = Postgraduate & 39 & 1\% \\
-father.education.level & & \\
-\ldots{} 0 = Primary school and below & 449 & 11\% \\
-\ldots{} 1 = Junior high school & 1634 & 40\% \\
-\ldots{} 2 = Senior high school & 1184 & 29\% \\
-\ldots{} 3 = Associate college & 350 & 9\% \\
-\ldots{} 4 = University & 430 & 10\% \\
-\ldots{} 5 = Postgraduate & 67 & 2\% \\
+... 0 = Does not matter & 87 & 2\%\\
+... 1 = Junior high school & 58 & 1\%\\
+... 2 = Senior high school & 436 & 10\%\\
+\addlinespace
+... 3 = Associate college & 639 & 15\%\\
+... 4 = University & 1241 & 30\%\\
+... 5 = Postgraduate & 1743 & 41\%\\
+parent.education.level &  & \\
+... 0 = Primary school and below & 254 & 6\%\\
+\addlinespace
+... 1 = Junior high school & 1631 & 39\%\\
+... 2 = Senior high school & 1278 & 30\%\\
+... 3 = Associate college & 397 & 9\%\\
+... 4 = University & 564 & 13\%\\
+... 5 = Postgraduate & 80 & 2\%\\
+\addlinespace
 parent.expectation &  & \\
-\ldots{} 1 = Junior high school & 35 & 1\% \\
-\ldots{} 2 = Senior high school & 259 & 6\% \\
-\ldots{} 3 = Associate college & 432 & 11\% \\
-\ldots{} 4 = University & 1591 & 39\% \\
-\ldots{} 5 = Postgraduate & 1797 & 44\% \\
+... 0 = Does not matter & 2 & 0\%\\
+... 1 = Junior high school & 36 & 1\%\\
+... 2 = Senior high school & 275 & 7\%\\
+... 3 = Associate college & 446 & 11\%\\
+\addlinespace
+... 4 = University & 1616 & 38\%\\
+... 5 = Postgraduate & 1829 & 44\%\\
 home.extracurricular.book &  & \\
-\ldots{} 1 = Very few & 389 & 9\% \\
-\ldots{} 2 = Not many & 418 & 10\% \\
-\ldots{} 3 = Some & 1322 & 32\% \\
-\ldots{} 4 = Quite a few & 1115 & 27\% \\
-\ldots{} 5 = A great number & 870 & 21\% \\
+... 1 = Very few & 401 & 10\%\\
+... 2 = Not many & 426 & 10\%\\
+\addlinespace
+... 3 = Some & 1360 & 32\%\\
+... 4 = Quite a few & 1135 & 27\%\\
+... 5 = A great number & 882 & 21\%\\
 home.economic.resource &  & \\
-\ldots{} 1 = Very poor & 110 & 3\% \\
-\ldots{} 2 = Somewhat poor & 595 & 14\% \\
-\ldots{} 3 = Moderate & 3155 & 77\% \\
-\ldots{} 4 = Somewhat rich & 243 & 6\% \\
-\ldots{} 5 = Very rich & 11 & 0\% \\
-\bottomrule()
-\end{longtable}
-
-\newpage
+... 1 = Very poor & 111 & 3\%\\
+\addlinespace
+... 2 = Somewhat poor & 611 & 15\%\\
+... 3 = Moderate & 3221 & 77\%\\
+... 4 = Somewhat rich & 249 & 6\%\\
+... 5 = Very rich & 12 & 0\%\\
+\bottomrule
+\end{tabular}
+\end{table}
 
 \hypertarget{regression-analysis}{%
-\subsection{Regression Analysis}\label{regression-analysis}}
+\subsubsection{Regression Analysis}\label{regression-analysis}}
 
 I first explain the results on children's cognitive test score.
-The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6 below).
+The unadjusted DID models show that newly left-behind adolescents are more likely to score lower in cognitive tests than do their non-left-behind counterparts (see Table 6).
 This lends support to Hypothesis 1a.
-Parental migration is linked to a 2.54 points decrease in cognitive test score.
+Parental migration is linked to a 2.59 points decrease in cognitive test score.
 Hypothesis 2a is only partially supported.
-Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.81 points) in cognitive test score than those with only mother absent (2.16 points).
-The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table A1 in the appendix).
+Compared with the non-left-behind peers, children with only father absent are associated with greater decrease (2.78 points) in cognitive test score than those with only mother absent (2.32 points).
+The adjusted DID models produce results similar to the unadjusted models, with one exception (see Table 7).
 That is, for the cognitive score, the both-parent-migrated coefficient's magnitude is lower than that of father-migrated.
@@
 \midrule
-Migration & \num{-2.54}*** & \num{-2.16}* & \num{-2.81}* & \num{-2.94}*\\
- & (\num{0.69}) & (\num{1.05}) & (\num{1.09}) & (\num{1.36})\\
-Baseline.score & \num{-0.71}*** & \num{-0.72}*** & \num{-0.71}*** & \num{-0.72}***\\
+Migration & \num{-2.59}*** & \num{-2.32}* & \num{-2.78}** & \num{-2.81}*\\
+ & (\num{0.63}) & (\num{1.01}) & (\num{1.00}) & (\num{1.26})\\
+Baseline.score & \num{-0.71}*** & \num{-0.71}*** & \num{-0.71}*** & \num{-0.71}***\\
  & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
 \midrule
-Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
-R2 & \num{0.378} & \num{0.381} & \num{0.385} & \num{0.388}\\
-R2 Adj. & \num{0.361} & \num{0.362} & \num{0.366} & \num{0.368}\\
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.376} & \num{0.379} & \num{0.383} & \num{0.385}\\
+R2 Adj. & \num{0.359} & \num{0.360} & \num{0.364} & \num{0.365}\\
 FE: schids & X & X & X & X\\
@@
 
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test score}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.41}*** & \num{-2.21}* & \num{-2.59}* & \num{-2.42}\\
+ & (\num{0.63}) & (\num{0.99}) & (\num{1.04}) & (\num{1.30})\\
+Baseline.score & \num{-0.78}*** & \num{-0.79}*** & \num{-0.78}*** & \num{-0.79}***\\
+ & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
+child.age & \num{-3.43}*** & \num{-3.55}*** & \num{-3.58}*** & \num{-3.39}***\\
+ & (\num{0.51}) & (\num{0.54}) & (\num{0.53}) & (\num{0.54})\\
+child.is.girl & \num{-0.65} & \num{-0.39} & \num{-0.62} & \num{-0.56}\\
+ & (\num{0.57}) & (\num{0.62}) & (\num{0.59}) & (\num{0.61})\\
+child.health & \num{-0.15} & \num{-0.06} & \num{-0.25} & \num{-0.15}\\
+ & (\num{0.32}) & (\num{0.32}) & (\num{0.35}) & (\num{0.34})\\
+child.has.rural.hukou & \num{0.32} & \num{0.59} & \num{0.25} & \num{0.81}\\
+ & (\num{0.65}) & (\num{0.66}) & (\num{0.68}) & (\num{0.70})\\
+child.number.of.sibling & \num{-0.93}* & \num{-0.99}* & \num{-0.82}* & \num{-0.92}*\\
+ & (\num{0.39}) & (\num{0.43}) & (\num{0.41}) & (\num{0.42})\\
+child.went.to.preschool & \num{2.28}** & \num{2.08}* & \num{2.15}** & \num{1.99}*\\
+ & (\num{0.77}) & (\num{0.83}) & (\num{0.80}) & (\num{0.82})\\
+child.in.boarding.school & \num{1.10} & \num{1.09} & \num{1.11} & \num{0.72}\\
+ & (\num{1.02}) & (\num{1.00}) & (\num{1.04}) & (\num{0.96})\\
+child.education.aspiration & \num{1.76}*** & \num{1.71}*** & \num{1.73}*** & \num{1.81}***\\
+ & (\num{0.27}) & (\num{0.29}) & (\num{0.27}) & (\num{0.29})\\
+child.is.ethnic.minority & \num{1.47} & \num{1.57} & \num{1.08} & \num{1.22}\\
+ & (\num{1.54}) & (\num{1.67}) & (\num{1.73}) & (\num{1.85})\\
+parent.expectation & \num{2.42}*** & \num{2.53}*** & \num{2.46}*** & \num{2.39}***\\
+ & (\num{0.34}) & (\num{0.35}) & (\num{0.33}) & (\num{0.34})\\
+parent.has.white.collar.job & \num{-0.84} & \num{-0.88} & \num{-0.69} & \num{-0.77}\\
+ & (\num{0.57}) & (\num{0.58}) & (\num{0.57}) & (\num{0.61})\\
+parent.education.level & \num{0.56} & \num{0.69}* & \num{0.41} & \num{0.55}\\
+ & (\num{0.31}) & (\num{0.32}) & (\num{0.34}) & (\num{0.34})\\
+home.economic.resource & \num{-0.55} & \num{-0.65} & \num{-0.14} & \num{-0.21}\\
+ & (\num{0.52}) & (\num{0.52}) & (\num{0.52}) & (\num{0.55})\\
+home.extracurricular.book & \num{0.00} & \num{-0.06} & \num{-0.05} & \num{-0.01}\\
+ & (\num{0.24}) & (\num{0.25}) & (\num{0.25}) & (\num{0.25})\\
+home.has.internet & \num{-0.46} & \num{-0.72} & \num{-0.68} & \num{-0.96}\\
+ & (\num{0.62}) & (\num{0.71}) & (\num{0.68}) & (\num{0.71})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.421} & \num{0.423} & \num{0.427} & \num{0.428}\\
+R2 Adj. & \num{0.403} & \num{0.403} & \num{0.407} & \num{0.407}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
 Next, I set forth the results on children's academic test grades.
-In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 7 below).
-Parental migration is associated with a drop of 1.30 points in academic exam score.
+In line with Hypothesis 1b, the unadjusted DID models show that newly left-behind adolescents tend to perform worse in school exams than their non-left-behind peers (see Table 8 below).
+Parental migration is associated with a drop of 1.13 points in academic exam score.
 Hypothesis 2b finds partial support.
-The exam grade of only-mother-migrated children sees a 2.13 points decrease relative to non-left-behind counterparts.
+The exam grade of only-mother-migrated children sees a 2.06 points decrease relative to non-left-behind counterparts.
 In the scenarios of only father migrated and both parents migrated, the results are not statistically significant.
-The adjusted DID models' results largely resemble those from the unadjusted models (See Table A2 in the appendix).
+The adjusted DID models' results largely resemble those from the unadjusted models (See Table 9 in the appendix).
 Adding control variables measured in the baseline survey does not change the coefficients for parental migration.
-
-\newpage
 
@@
 \midrule
-Migration & \num{-1.30}* & \num{-2.13}* & \num{-0.97} & \num{-0.12}\\
- & (\num{0.53}) & (\num{0.89}) & (\num{0.69}) & (\num{0.71})\\
-Baseline.score & \num{0.05} & \num{0.05} & \num{0.05} & \num{0.05}\\
+Migration & \num{-1.13}* & \num{-2.06}* & \num{-0.76} & \num{0.13}\\
+ & (\num{0.50}) & (\num{0.88}) & (\num{0.65}) & (\num{0.65})\\
+Baseline.score & \num{0.04} & \num{0.05} & \num{0.05} & \num{0.05}\\
  & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
 \midrule
-Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
-R2 & \num{0.481} & \num{0.498} & \num{0.484} & \num{0.500}\\
-R2 Adj. & \num{0.466} & \num{0.482} & \num{0.468} & \num{0.484}\\
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.469} & \num{0.485} & \num{0.473} & \num{0.488}\\
+R2 Adj. & \num{0.455} & \num{0.469} & \num{0.457} & \num{0.472}\\
 FE: schids & X & X & X & X\\
@@
 
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam score}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.07}* & \num{-2.05}* & \num{-0.66} & \num{0.22}\\
+ & (\num{0.48}) & (\num{0.82}) & (\num{0.64}) & (\num{0.66})\\
+Baseline.score & \num{-0.01} & \num{-0.01} & \num{-0.01} & \num{-0.01}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+child.age & \num{-0.74}*** & \num{-0.58}* & \num{-0.73}** & \num{-0.54}*\\
+ & (\num{0.22}) & (\num{0.23}) & (\num{0.23}) & (\num{0.25})\\
+child.is.girl & \num{1.65}*** & \num{1.72}*** & \num{1.62}*** & \num{1.56}***\\
+ & (\num{0.39}) & (\num{0.41}) & (\num{0.39}) & (\num{0.41})\\
+child.health & \num{0.28}* & \num{0.29}* & \num{0.19} & \num{0.21}\\
+ & (\num{0.13}) & (\num{0.14}) & (\num{0.16}) & (\num{0.15})\\
+child.has.rural.hukou & \num{0.47} & \num{0.57} & \num{0.34} & \num{0.47}\\
+ & (\num{0.45}) & (\num{0.47}) & (\num{0.43}) & (\num{0.43})\\
+child.number.of.sibling & \num{0.29} & \num{0.27} & \num{0.40} & \num{0.21}\\
+ & (\num{0.20}) & (\num{0.21}) & (\num{0.23}) & (\num{0.23})\\
+child.went.to.preschool & \num{1.05}* & \num{1.26}** & \num{0.65} & \num{1.10}*\\
+ & (\num{0.45}) & (\num{0.48}) & (\num{0.42}) & (\num{0.44})\\
+child.in.boarding.school & \num{-0.38} & \num{-0.11} & \num{-0.27} & \num{-0.33}\\
+ & (\num{0.52}) & (\num{0.49}) & (\num{0.49}) & (\num{0.53})\\
+child.education.aspiration & \num{0.61}** & \num{0.70}*** & \num{0.61}** & \num{0.62}**\\
+ & (\num{0.18}) & (\num{0.21}) & (\num{0.18}) & (\num{0.21})\\
+child.is.ethnic.minority & \num{-0.19} & \num{-0.27} & \num{-0.47} & \num{-0.66}\\
+ & (\num{0.67}) & (\num{0.74}) & (\num{0.80}) & (\num{0.85})\\
+parent.expectation & \num{0.61}* & \num{0.61}* & \num{0.65}* & \num{0.67}*\\
+ & (\num{0.25}) & (\num{0.25}) & (\num{0.29}) & (\num{0.28})\\
+parent.has.white.collar.job & \num{-0.18} & \num{-0.06} & \num{-0.08} & \num{0.00}\\
+ & (\num{0.27}) & (\num{0.31}) & (\num{0.33}) & (\num{0.34})\\
+parent.education.level & \num{0.27} & \num{0.29} & \num{0.33}* & \num{0.33}\\
+ & (\num{0.18}) & (\num{0.18}) & (\num{0.17}) & (\num{0.17})\\
+home.economic.resource & \num{-0.24} & \num{-0.12} & \num{-0.18} & \num{-0.11}\\
+ & (\num{0.27}) & (\num{0.27}) & (\num{0.28}) & (\num{0.27})\\
+home.extracurricular.book & \num{-0.26} & \num{-0.41}* & \num{-0.30} & \num{-0.30}*\\
+ & (\num{0.17}) & (\num{0.16}) & (\num{0.16}) & (\num{0.15})\\
+home.has.internet & \num{-0.41} & \num{-0.48} & \num{-0.32} & \num{-0.39}\\
+ & (\num{0.36}) & (\num{0.38}) & (\num{0.40}) & (\num{0.42})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.486} & \num{0.503} & \num{0.490} & \num{0.505}\\
+R2 Adj. & \num{0.470} & \num{0.486} & \num{0.473} & \num{0.487}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\end{tabular}
+\end{table}
+
 Some predictors are strong in both models of cognitive and academic abilities.
 These are children's age, preschool attendance, and educational aspiration as well as parents' expectation on children.
-For students, one year older in age is associated with decreases of 2.67 points for cognitive test and of 0.47 points for academic exam.
-Preschool attendance is linked to increases of 2.30 points for cognitive test and of 1.12 points for academic exam.
+For students, one year older in age is associated with decreases of 3.43 points for cognitive test and of 0.74 points for academic exam.
+Preschool attendance is linked to increases of 2.28 points for cognitive test and of 1.05 points for academic exam.
 Higher educational expectation from parents and greater educational aspiration from children are both linked to higher scores.
-The coefficients are 2.35 points and 2.05 points for cognitive test, respectively; and 0.57 points and 0.78 points for academic exams, respectively.
-
-Several predictors are strong in predicting one outcome but not the other.
-Covariates that only relate to academic grades are children's gender and self-reported health, and the number of extracurricular books at home.
-Girls outperform boys by 1.61 points in academic exams, but do not show advantage in cognitive tests.
-Students who consider themselves healthier are associated with higher scores in academic exams.
-On the contrary, those who report having more extracurricular books at home are associated with lower scores in academic exams.
-Covariates that only relate to cognitive scores is the number of siblings.
-Having an additional sibling is associated with lower cognitive score of 1 points.
-
-\newpage
+The coefficients are 0.56 points and 2.42 points for cognitive test, respectively; and 0.27 points and 0.61 points for academic exams, respectively.
+Some predictors are strong in predicting one outcome but not the other.
+The covariate that only relates to academic grades is children's gender.
+Girls outperform boys by 1.65 points in academic exams, but do not show advantage in cognitive tests.
+Another covariate, the number of siblings, i sonly relate to cognitive scores.
+Having an additional sibling is associated with lower cognitive score of 0.93 points.
 
 \hypertarget{matching}{%
-\subsection{Matching}\label{matching}}
+\subsubsection{Matching}\label{matching}}
 
@@
 To tackle this bias, an applicable technique is matching.
-It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates (Sävje et al., 2021).
+It aims to make two groups comparable by pairing a unit in the treatment group with one or several units in the control group based on observable covariates.
 
@@
 When handling this distance, PSM can match the units with two approaches.
-One is the nearest-neighbor approach.
+One is the nearest-neighbor matching.
 It examines all the treated units and selects the control unit closest in distance for pairing.
 This approach does not try to optimize any condition; each pair of units ignores how other pairing will occur or have occurred.
-The second approach, the optimal-pair approach, works in a similar fashion but tries to minimize the absolute pairwise distances in total (Pan \& Bai, 2018).
+The second approach is the optimal approach.
+It minimizes the total distance in propensity scores between the treatment and control groups.
+Optimal matching can assign a treated unit with more than one control unit, thereby retaining the full sample (Hansen \& Fredrickson, 2023).
 
@@
 My initial attempt with CEM left most units unmatched and resulted in a tiny sample.
-I then made do with PSM.
-I combined exact matching (based on the student's county of residence) and optimal-pair PSM (based on the other covariates).
-Exact matching based on county of residence can preserve the original geographic distribution (Bai et al., 2018).
-The propensity score was estimated using a logistic regression of the treatment on the covariates.
-The matching ratio of 3:1 means that one treatment unit would pair with up to three control units.
+I then made do with PSM by performing optimal full matching.
+The propensity score was estimated using a logistic regression of the treatment on all the covariates.
 According to the matching summary, most of the covariates' absolute standardized mean differences decrease and fall below 0.1 after matching, suggesting an improved overall balance.
@@
 \midrule
-Migration & \num{-2.54}*** & \num{-2.55}* & \num{-2.65}* & \num{-0.34}\\
- & (\num{0.75}) & (\num{1.14}) & (\num{1.10}) & (\num{1.54})\\
-Baseline.score & \num{-0.70}*** & \num{-0.70}*** & \num{-0.65}*** & \num{-0.71}***\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
-\midrule
-Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.396} & \num{0.445} & \num{0.410} & \num{0.486}\\
-R2 Adj. & \num{0.368} & \num{0.380} & \num{0.343} & \num{0.372}\\
+Migration & \num{-2.09}** & \num{-2.89}** & \num{-2.60}* & \num{-1.26}\\
+ & (\num{0.71}) & (\num{1.07}) & (\num{1.05}) & (\num{1.33})\\
+Baseline.score & \num{-0.72}*** & \num{-0.73}*** & \num{-0.71}*** & \num{-0.68}***\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.383} & \num{0.398} & \num{0.408} & \num{0.392}\\
+R2 Adj. & \num{0.366} & \num{0.380} & \num{0.390} & \num{0.373}\\
 FE: schids & X & X & X & X\\
@@
 \multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}Optimal full matching by propensity score}\\
 \end{tabular}
@@
 
-\newpage
+\begin{table}
+
+\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-2.10}** & \num{-2.60}* & \num{-2.58}* & \num{-1.59}\\
+ & (\num{0.71}) & (\num{1.03}) & (\num{1.07}) & (\num{1.39})\\
+Baseline.score & \num{-0.80}*** & \num{-0.80}*** & \num{-0.78}*** & \num{-0.76}***\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+child.age & \num{-2.54}*** & \num{-2.59}*** & \num{-3.73}*** & \num{-4.20}***\\
+ & (\num{0.73}) & (\num{0.69}) & (\num{0.73}) & (\num{0.78})\\
+child.is.girl & \num{-1.03} & \num{0.01} & \num{0.15} & \num{-1.12}\\
+ & (\num{0.73}) & (\num{0.87}) & (\num{0.71}) & (\num{0.93})\\
+child.health & \num{-0.03} & \num{-0.15} & \num{-0.09} & \num{0.46}\\
+ & (\num{0.40}) & (\num{0.42}) & (\num{0.44}) & (\num{0.63})\\
+child.has.rural.hukou & \num{0.09} & \num{-0.20} & \num{0.66} & \num{0.11}\\
+ & (\num{0.94}) & (\num{1.03}) & (\num{1.04}) & (\num{1.16})\\
+child.number.of.sibling & \num{-1.22}** & \num{-0.78} & \num{-1.19}* & \num{-0.96}\\
+ & (\num{0.43}) & (\num{0.80}) & (\num{0.53}) & (\num{0.70})\\
+child.went.to.preschool & \num{2.19}* & \num{1.99}* & \num{2.66}** & \num{-0.13}\\
+ & (\num{0.95}) & (\num{0.99}) & (\num{1.00}) & (\num{1.17})\\
+child.in.boarding.school & \num{0.54} & \num{0.84} & \num{0.85} & \num{-0.43}\\
+ & (\num{1.12}) & (\num{1.61}) & (\num{1.25}) & (\num{1.56})\\
+child.education.aspiration & \num{1.91}*** & \num{1.45}** & \num{1.17}*** & \num{1.45}***\\
+ & (\num{0.35}) & (\num{0.53}) & (\num{0.34}) & (\num{0.37})\\
+child.is.ethnic.minority & \num{2.14} & \num{-0.69} & \num{1.33} & \num{1.84}\\
+ & (\num{2.41}) & (\num{2.10}) & (\num{2.27}) & (\num{3.56})\\
+parent.expectation & \num{2.62}*** & \num{3.16}*** & \num{2.45}*** & \num{2.13}***\\
+ & (\num{0.47}) & (\num{0.59}) & (\num{0.49}) & (\num{0.49})\\
+parent.has.white.collar.job & \num{-1.20} & \num{-0.78} & \num{0.08} & \num{-1.90}*\\
+ & (\num{0.83}) & (\num{1.02}) & (\num{1.01}) & (\num{0.94})\\
+parent.education.level & \num{0.57} & \num{0.76} & \num{-0.23} & \num{0.80}\\
+ & (\num{0.39}) & (\num{0.45}) & (\num{0.57}) & (\num{0.63})\\
+home.economic.resource & \num{0.18} & \num{-0.66} & \num{0.84} & \num{0.15}\\
+ & (\num{0.69}) & (\num{1.01}) & (\num{0.71}) & (\num{0.80})\\
+home.extracurricular.book & \num{-0.15} & \num{0.04} & \num{0.54} & \num{0.11}\\
+ & (\num{0.35}) & (\num{0.35}) & (\num{0.38}) & (\num{0.40})\\
+home.has.internet & \num{-0.01} & \num{-1.96}* & \num{-1.15} & \num{-0.39}\\
+ & (\num{0.62}) & (\num{0.87}) & (\num{1.12}) & (\num{0.99})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.432} & \num{0.441} & \num{0.453} & \num{0.440}\\
+R2 Adj. & \num{0.415} & \num{0.421} & \num{0.434} & \num{0.420}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}Optimal full matching by propensity score}\\
+\end{tabular}
+\end{table}
 
@@
 \midrule
-Migration & \num{-1.15}* & \num{-1.72}* & \num{-1.53} & \num{0.50}\\
- & (\num{0.56}) & (\num{0.75}) & (\num{0.81}) & (\num{0.84})\\
-Baseline.score & \num{0.05} & \num{0.08}* & \num{0.04} & \num{0.03}\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
-\midrule
-Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.456} & \num{0.574} & \num{0.436} & \num{0.522}\\
-R2 Adj. & \num{0.431} & \num{0.524} & \num{0.373} & \num{0.415}\\
+Migration & \num{-1.09}* & \num{-2.12}* & \num{-0.45} & \num{0.00}\\
+ & (\num{0.47}) & (\num{0.87}) & (\num{0.66}) & (\num{0.77})\\
+Baseline.score & \num{0.04} & \num{0.05} & \num{0.05} & \num{0.00}\\
+ & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.480} & \num{0.490} & \num{0.465} & \num{0.515}\\
+R2 Adj. & \num{0.465} & \num{0.474} & \num{0.449} & \num{0.500}\\
 FE: schids & X & X & X & X\\
@@
 
-\newpage
+\begin{table}
+
+\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
+\centering
+\begin{tabular}[t]{lcccc}
+\toprule
+  & Any Parent & Only Mother & Only Father & Both Parents\\
+\midrule
+Migration & \num{-1.08}* & \num{-2.15}* & \num{-0.42} & \num{0.04}\\
+ & (\num{0.45}) & (\num{0.85}) & (\num{0.69}) & (\num{0.78})\\
+Baseline.score & \num{0.05}* & \num{-0.01} & \num{-0.01} & \num{-0.04}\\
+ & (\num{0.02}) & (\num{0.03}) & (\num{0.04}) & (\num{0.03})\\
+child.age & \num{-0.65} & \num{0.07} & \num{-0.74}* & \num{-0.38}\\
+ & (\num{0.41}) & (\num{0.45}) & (\num{0.37}) & (\num{0.44})\\
+child.is.girl & \num{1.66}*** & \num{1.80}*** & \num{2.18}*** & \num{1.87}***\\
+ & (\num{0.44}) & (\num{0.46}) & (\num{0.52}) & (\num{0.50})\\
+child.health & \num{0.38}* & \num{0.21} & \num{0.21} & \num{-0.25}\\
+ & (\num{0.18}) & (\num{0.17}) & (\num{0.23}) & (\num{0.27})\\
+child.has.rural.hukou & \num{0.52} & \num{0.54} & \num{0.95} & \num{0.34}\\
+ & (\num{0.50}) & (\num{0.55}) & (\num{0.65}) & (\num{0.70})\\
+child.number.of.sibling & \num{0.31} & \num{-0.15} & \num{0.59}* & \num{0.50}\\
+ & (\num{0.21}) & (\num{0.41}) & (\num{0.26}) & (\num{0.30})\\
+child.went.to.preschool & \num{0.43} & \num{1.18} & \num{0.38} & \num{1.22}\\
+ & (\num{0.46}) & (\num{0.61}) & (\num{0.55}) & (\num{0.80})\\
+child.in.boarding.school & \num{0.10} & \num{0.27} & \num{-0.33} & \num{-0.70}\\
+ & (\num{0.60}) & (\num{0.92}) & (\num{0.84}) & (\num{0.81})\\
+child.education.aspiration & \num{0.47}* & \num{0.50} & \num{0.56} & \num{0.38}\\
+ & (\num{0.22}) & (\num{0.26}) & (\num{0.32}) & (\num{0.29})\\
+child.is.ethnic.minority & \num{-0.31} & \num{-1.04} & \num{-1.40} & \num{-0.51}\\
+ & (\num{1.12}) & (\num{1.53}) & (\num{1.20}) & (\num{1.57})\\
+parent.expectation & \num{0.48} & \num{1.03}* & \num{0.47} & \num{0.47}\\
+ & (\num{0.30}) & (\num{0.43}) & (\num{0.26}) & (\num{0.27})\\
+parent.has.white.collar.job & \num{-0.15} & \num{0.13} & \num{0.21} & \num{0.29}\\
+ & (\num{0.37}) & (\num{0.49}) & (\num{0.51}) & (\num{0.47})\\
+parent.education.level & \num{0.38} & \num{0.23} & \num{0.28} & \num{0.39}\\
+ & (\num{0.20}) & (\num{0.23}) & (\num{0.26}) & (\num{0.32})\\
+home.economic.resource & \num{0.10} & \num{-0.17} & \num{0.09} & \num{-0.18}\\
+ & (\num{0.36}) & (\num{0.41}) & (\num{0.41}) & (\num{0.50})\\
+home.extracurricular.book & \num{-0.49}* & \num{-0.35} & \num{-0.15} & \num{-0.27}\\
+ & (\num{0.21}) & (\num{0.20}) & (\num{0.25}) & (\num{0.21})\\
+home.has.internet & \num{-0.04} & \num{-0.95} & \num{-0.14} & \num{-0.81}\\
+ & (\num{0.40}) & (\num{0.51}) & (\num{0.49}) & (\num{0.49})\\
+\midrule
+Num.Obs. & \num{4204} & \num{3796} & \num{3795} & \num{3671}\\
+R2 & \num{0.500} & \num{0.508} & \num{0.485} & \num{0.530}\\
+R2 Adj. & \num{0.485} & \num{0.491} & \num{0.467} & \num{0.514}\\
+FE: schids & X & X & X & X\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}Optimal full matching by propensity score}\\
+\end{tabular}
+\end{table}
 
 \hypertarget{discussion-and-conclusion}{%
-\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
+\subsection{Discussion and Conclusion}\label{discussion-and-conclusion}}
 
@@
 \hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
+\subsubsection{Limitations}\label{limitations}}
 
@@
 \hypertarget{recommendations}{%
-\subsection{Recommendations}\label{recommendations}}
+\subsubsection{Recommendations}\label{recommendations}}
 
@@
 Besides, educational attainment is only part of human development outcomes.
-Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Antia et al., 2020; Pang \& Lu, 2022).
-
+Other outcomes like mental health and non-cognitive skills are also subjected to parental absence's influence (Raturi \& Cebotari, 2023; Zhao \& Chen, 2022).
+
+The children in the CEPS survey have grown into young adults.
+Would they repeat their parents' choice, leaving the next generation of children behind?
+That depends on the actions of stakeholders.
 Policymakers should accelerate the reforms on hukou, opening more doors for parents to migrate together with their children.
-In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Deng, 2023; Jiemian News, 2023).
+In January 2023, local government officials lifted hukou restrictions in Zhengzhou, a city that hosts twelve million residents and the world's largest iPhone manufacturing plant (Jiemian News, 2023).
 This metropolis in central China set the precedant for offering hukou to all arriving migrants; Other main cities should follow suit.
@@
 School administrators could dedicate more advisory and counseling programs.
-Social workers could provide paraprofessional training in communities (M.
+Social workers could provide paraprofessional training and community workers can organize children's centers in local areas (Jiang et al., 2020; M.
 Wang et al., 2020).
+
+\newpage
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-cog-1} \caption{Changes in cognitive test score for newly left-behind students and non-left-behind students}\label{fig:v-plot-cog}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-ttl-1} \caption{Changes in academic exam score for newly left-behind students and non-left-behind students}\label{fig:v-plot-ttl}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-any-1} \caption{Covariate balance before and after matching by any parent migration}\label{fig:cobal-any}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-mo-1} \caption{Covariate balance before and after matching by mother-only migration}\label{fig:cobal-mo}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-fa-1} \caption{Covariate balance before and after matching by father-only migration}\label{fig:cobal-fa}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-both-1} \caption{Covariate balance before and after matching by both parents migration}\label{fig:cobal-both}
+\end{figure}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-alpermann2020}{}}%
-Alpermann, B.
-(2020).
-{China}{'}s Rural{\textendash}Urban Transformation: New Forms of Inclusion and Exclusion.
-\emph{Journal of Current Chinese Affairs}, \emph{49}(3), 259--268.
-\url{https://doi.org/10.1177/18681026211004955}
-
-\leavevmode\vadjust pre{\hypertarget{ref-antia2020}{}}%
-Antia, K., Boucsein, J., Deckert, A., Dambach, P., Račaitė, J., Šurkienė, G., Jaenisch, T., Horstick, O., \& Winkler, V.
-(2020).
-Effects of International Labour Migration on the Mental Health and Well-Being of Left-Behind Children: A Systematic Literature Review.
-\emph{International Journal of Environmental Research and Public Health}, \emph{17}(12), 4335.
-\url{https://doi.org/10.3390/ijerph17124335}
+\leavevmode\vadjust pre{\hypertarget{ref-ahmed2023}{}}%
+Ahmed, F., Dzator, J., \& Acheampong, A.
+O.
+(2023).
+Do remittances reduce school dropout in bangladesh?
+The role of government{'}s administrative and structural support.
+\emph{Journal of Policy Modeling}, \emph{45}(2), 388--404.
+\url{https://doi.org/10.1016/j.jpolmod.2023.04.002}
 
@@
 Arel-Bundock, V. (2022). {modelsummary}: Data and model summaries in {R}. \emph{Journal of Statistical Software}, \emph{103}(1), 1--23. \url{https://doi.org/10.18637/jss.v103.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://cran.r-project.org/web/packages/papaja/index.html}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bourdieu2002}{}}%
-Bourdieu, P. (2002). The Forms of Capital. In N. W. Biggart (Ed.), \emph{Readings in Economic Sociology} (pp. 280--291). Blackwell Publishers Ltd. \url{https://doi.org/10.1002/9780470755679.ch15}
-
-\leavevmode\vadjust pre{\hypertarget{ref-debrauw2019}{}}%
-Brauw, A.
-de.
+\leavevmode\vadjust pre{\hypertarget{ref-chae2019}{}}%
+Chae, S., \& Glick, J.
+E.
 (2019).
-Migration Out of Rural Areas and Implications for Rural Livelihoods.
-\emph{Annual Review of Resource Economics}, \emph{11}(1), 461--481.
-\url{https://doi.org/10.1146/annurev-resource-100518-093906}
+Educational Selectivity of Migrants and Current School Enrollment of Children Left behind: Analyses in Three African Countries.
+\emph{International Migration Review}, \emph{53}(3), 736--769.
+\url{https://doi.org/10.1177/0197918318772261}
 
@@
 Chan, J. (2019). State and labor in {China}, 1978{\textendash}2018. \emph{Journal of Labor and Society}, \emph{22}(2), 461--475. \url{https://doi.org/10.1111/wusa.12408}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chang2019}{}}%
-Chang, F., Jiang, Y., Loyalka, P., Chu, J., Shi, Y., Osborn, A., \& Rozelle, S.
-(2019).
-Parental migration, educational achievement, and mental health of junior high school students in rural {China}.
-\emph{{China} Economic Review}, \emph{54}, 337--349.
-\url{https://doi.org/10.1016/j.chieco.2019.01.007}
 
@@
 Left-Behind Children{'}s Cognitive Development in {China}: Gain in Financial Capital Versus Loss in Parental Capital.
-\emph{Sociological Perspectives}, In Press.
+\emph{Sociological Perspectives}, \emph{66}(3), 523--542.
 \url{https://doi.org/10.1177/07311214221145059}
@@
 (2023).
-Parental absence, early reading, and human capital formation for rural children in China.
+Parental absence, early reading, and human capital formation for rural children in {China}.
 \emph{Journal of Community Psychology}, \emph{51}(2), 662--675.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chen2023c}{}}%
+Chen, Y., \& Fu, W.
+(2023).
+Migration control policy and parent{\textendash}child separation among migrant families: evidence from China.
+\emph{Journal of Population Economics}, In Press.
+\url{https://doi.org/10.1007/s00148-023-00971-z}
+
 \leavevmode\vadjust pre{\hypertarget{ref-costalli2021}{}}%
@@
 Démurger, S., \& Xu, H. (2015). Left-behind children and return migration in {China}. \emph{IZA Journal of Migration}, \emph{4}(1), 10. \url{https://doi.org/10.1186/s40176-015-0035-x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-deng2023}{}}%
-Deng, I.
-(2023, February 28).
-\emph{Foxconn leases new site in China after government{'}s charm offensive}.
-South China Morning Post.
-\url{https://www.scmp.com/tech/big-tech/article/3211816/apples-iphone-supplier-foxconn-leases-new-site-zhengzhou-sign-commitment-chinas-supply-chain}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-diaconu-gherasim2023}{}}%
+Diaconu-Gherasim, L.
+R., Brumariu, L.
+E., \& Etengoff, C.
+M.
+(2023).
+Romanian early adolescents{'} perceptions of parental migration and the associated relational impact: A qualitative analysis.
+\emph{Journal of Ethnic and Migration Studies}, In Press.
+\url{https://doi.org/10.1080/1369183X.2023.2203845}
+
+\leavevmode\vadjust pre{\hypertarget{ref-doepke2015}{}}%
+Doepke, M. (2015). Gary Becker on the Quantity and Quality of Children. \emph{Journal of Demographic Economics}, \emph{81}(1), 59--66. \url{https://doi.org/10.1017/dem.2014.8}
+
 \leavevmode\vadjust pre{\hypertarget{ref-dong2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fan2023}{}}%
+Fan, C.
+C.
+(2023).
+Split households and migration in the {Global South}: Gender and intergenerational perspectives.
+In B.
+Yeoh (Ed.), \emph{Handbook on {Migration} and the {Family}} (pp.
+135--153).
+{Edward Elgar Publishing}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-guxf6bel2021}{}}%
 Göbel, C. (2021). The political logic of protest repression in {China}. \emph{Journal of Contemporary {China}}, \emph{30}(128), 169--185. \url{https://doi.org/10.1080/10670564.2020.1790897}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gong2023}{}}%
+Gong, J., \& Rao, N.
+(2023).
+Early learning opportunities of preschool children affected by migration in china.
+\emph{Early Childhood Research Quarterly}, \emph{63}, 228--239.
+\url{https://doi.org/10.1016/j.ecresq.2022.12.010}
 
@@
 (2021).
-Why do Chinese adolescent girls outperform boys in achievement tests?
+Why do {Chinese} adolescent girls outperform boys in achievement tests?
 \emph{Chinese Journal of Sociology}, \emph{7}(2), 109--137.
 \url{https://doi.org/10.1177/2057150X211006586}
-
-\leavevmode\vadjust pre{\hypertarget{ref-guo2022}{}}%
-Guo, R., Yi, J., \& Zhang, J. (2022). The Child Quantity{\textendash}Quality Trade-off. \emph{IZA Discussion Papers}. \url{https://doi.org/10.2139/ssrn.4114809}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hasmath2022}{}}%
-Hasmath, R. (2022, August). The Operations of Contemporary Han Chinese Privilege. \emph{American Sociological Association Annual Meeting}. \url{https://doi.org/10.2139/ssrn.3671496}
+\leavevmode\vadjust pre{\hypertarget{ref-hansen2023}{}}%
+Hansen, M.
+M., \& Fredrickson, B.
+(2023).
+Optimal full matching.
+In J.
+R.
+Zubizarreta, E.
+A.
+Stuart, D.
+S.
+Small, \& P.
+R.
+Rosenbaum (Eds.), \emph{Handbook of matching and weighting adjustments for causal inference} (pp.
+87--104).
+Chapman; Hall/CRC.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hasmath2023}{}}%
+Hasmath, R. (2023). The Operations of Contemporary Han Chinese Privilege. \emph{China Information}, In Press. \url{https://doi.org/10.1177/0920203X231193086}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hong2019}{}}%
-Hong, Y., \& Fuller, C.
-(2019).
-Alone and {``}left behind{''}: A case study of {``}left-behind children{''} in rural {China}.
-\emph{Cogent Education}, \emph{6}(1), 1654236.
-\url{https://doi.org/10.1080/2331186X.2019.1654236}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hu2019}{}}%
-Hu, S.
-(2019).
-{``}It{'}s for Our Education{''}:~Perception of Parental Migration and Resilience Among Left-behind Children in Rural {China}.
-\emph{Social Indicators Research}, \emph{145}(2), 641--661.
-\url{https://doi.org/10.1007/s11205-017-1725-y}
-
 \leavevmode\vadjust pre{\hypertarget{ref-huang2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-jiang2020}{}}%
+Jiang, M., Li, L., Zhu, W.
+X., \& Hesketh, T.
+(2020).
+Community-Based Intervention to Improve the Well-Being of Children Left Behind by Migrant Parents in Rural {China}.
+\emph{International Journal of Environmental Research and Public Health}, \emph{17}(19), 7218.
+\url{https://doi.org/10.3390/ijerph17197218}
+
 \leavevmode\vadjust pre{\hypertarget{ref-jiemiannews2023}{}}%
 Jiemian News. (2023, January 3). \emph{Zhengzhou relaxes requirements for urban hukou applications {[}in {Chinese}{]}}. \url{https://www.jiemian.com/article/8677930.html}
-
-\leavevmode\vadjust pre{\hypertarget{ref-khalid2022}{}}%
-Khalid, S., Tadesse, E., Cai, L., \& Gao, C.
-(2022).
-Do Migrant Parents{'} Income or Relationships With Their Left-Behind Children Compensate for Their Physical Absence?
-\emph{Journal of Family Issues}, In Press.
-\url{https://doi.org/10.1177/0192513X221113853}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-liu2023}{}}%
+Liu, R., \& Hannum, E.
+(2023).
+Parental absence and student academic performance in cross-national perspective: Heterogeneous forms of family separation and the buffering possibilities of grandparents.
+\emph{International Journal of Educational Development}, \emph{103}, In Press.
+\url{https://doi.org/10.1016/j.ijedudev.2023.102898}
+
 \leavevmode\vadjust pre{\hypertarget{ref-liu2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
+Murphy, R. (2020). \emph{The children of {China}{'}s great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
+
 \leavevmode\vadjust pre{\hypertarget{ref-murphy2022}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-murphy2020}{}}%
-Murphy, R. (2020). \emph{The children of {China}{'}s great migration}. Cambridge University Press. \url{https://doi.org/10.1017/9781108877251}
-
 \leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
@@
 National Bureau of Statistics, United Nations Children's Fund, United Nations Population Fund.
-\url{https://www.unicef.cn/media/9901/file/Population\%20Status\%20of\%20Children\%20in\%20\%7BChina\%7D\%20in\%202015\%20Facts\%20and\%20Figures.pdf}
+\url{https://www.unicef.cn/en/reports/population-status-children-china-2015}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pang2022}{}}%
-Pang, X., \& Lu, Z.
-(2022).
-Internal Migration and the Educational and Social Impacts on Children Left Behind in Rural {China}.
-In A.
-North \& E.
-Chase (Eds.), \emph{Education, Migration and Development: Critical Perspectives in a Moving World} (pp.
-189--210).
-Bloomsbury Academic.
-\url{https://doi.org/10.5040/9781350257573}
-
 \leavevmode\vadjust pre{\hypertarget{ref-pasquali2022}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-raturi2023}{}}%
+Raturi, R., \& Cebotari, V.
+(2023).
+The impact of parental migration on psychological well-being of children in ghana.
+\emph{Journal of Ethnic and Migration Studies}, \emph{49}(1), 192--211.
+\url{https://doi.org/10.1080/1369183X.2022.2076070}
+
 \leavevmode\vadjust pre{\hypertarget{ref-roberts2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-suxe4vje2021}{}}%
-Sävje, F., Higgins, M. J., \& Sekhon, J. S. (2021). Generalized Full Matching. \emph{Political Analysis}, \emph{29}(4), 423--447. \url{https://doi.org/10.1017/pan.2020.32}
-
 \leavevmode\vadjust pre{\hypertarget{ref-shen2021}{}}%
@@
 \url{https://doi.org/10.1016/j.ssresearch.2021.102576}
+
+\leavevmode\vadjust pre{\hypertarget{ref-udrea2022}{}}%
+Udrea, G., \& Guiu, G.
+(2022).
+The Impact of Parents{'} Work Migration on the Social, Communication and Educational Experiences of Left-Behind Adolescents.
+\emph{Central and Eastern European Migration Review}, \emph{11}(2), 101--117.
+\url{https://doi.org/10.54667/ceemr.2022.14}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vietnguyen2023}{}}%
+Viet Nguyen, C., \& Hoang Vu, L.
+(2023).
+Does Parental Absence Harm Children{'}s Education?
+Evidence from Vietnam.
+\emph{Journal of Asian and African Studies}, In Press.
+\url{https://doi.org/10.1177/00219096231176739}
+
 \leavevmode\vadjust pre{\hypertarget{ref-vikram2021}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vortherms2021}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-vortherms2023}{}}%
 Vortherms, S.
 A.
-(2021).
-Hukou as a case of multi-level citizenship.
-In Z.
-Guo (Ed.), \emph{The Routledge Handbook of Chinese Citizenship} (pp.
-132--142).
-Routledge.
-\href{https://doi.org/10.4324/9781003225843-12}{doi.org/10.4324/9781003225843-12}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wan2022}{}}%
-Wan, Y., \& Vickers, E.
-(2022).
-Towards Meritocratic Apartheid?
-Points Systems and Migrant Access to {China}'s Urban Public Schools.
-\emph{The {China} Quarterly}, \emph{249}, 210--238.
-\url{https://doi.org/10.1017/S0305741021000990}
+(2023).
+Dividing the {People}: {The Authoritarian Bargain}, {Development}, and {Authoritarian Citizenship}.
+\emph{Comparative Politics}, \emph{56}(1), 95--119.
+\url{https://doi.org/10.5129/001041523X16847804956763}
 
@@
 Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of {CEPS} baseline survey (in {Chinese})}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wang2020}{}}%
-Wang, X.
-(2020).
-Permits, Points, and Permanent Household Registration: Recalibrating Hukou Policy under {``}Top-Level Design{''}.
-\emph{Journal of Current Chinese Affairs}, \emph{49}(3), 269--290.
-\url{https://doi.org/10.1177/1868102619894739}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhou2014}{}}%
-Zhou, M., Murphy, R., \& Tao, R.
-(2014).
-Effects of Parents' Migration on the Education of Children Left Behind in Rural {China}.
-\emph{Population and Development Review}, \emph{40}(2), 273--292.
-\url{https://doi.org/10.1111/j.1728-4457.2014.00673.x}
+\leavevmode\vadjust pre{\hypertarget{ref-zhao2022a}{}}%
+Zhao, C., \& Chen, B.
+(2022).
+Parental migration and non-cognitive abilities of left-behind children in rural china: Causal effects by an instrumental variable approach.
+\emph{Child Abuse \& Neglect}, \emph{123}, 105389.
+\url{https://doi.org/10.1016/j.chiabu.2021.105389}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zheng2021}{}}%
+Zheng, L., Weng, Q., \& Gong, X.
+(2021).
+Does preschool attendance affect the urban-rural cognition gap among middle school students?
+Evidence from {China Education Panel Survey}.
+\emph{The Journal of Chinese Sociology}, \emph{8}(1), 14.
+\url{https://doi.org/10.1186/s40711-021-00150-1}
 
@@
 
-\hypertarget{appendix-the-appendix}{%
+\hypertarget{appendix-appendix}{%
 \appendix}
 
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s cognitive test score}
-\centering
-\begin{tabular}[t]{lcccc}
-\toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-2.47}*** & \num{-2.16}* & \num{-2.87}* & \num{-2.37}\\
- & (\num{0.68}) & (\num{1.04}) & (\num{1.10}) & (\num{1.36})\\
-Baseline.score & \num{-0.78}*** & \num{-0.79}*** & \num{-0.78}*** & \num{-0.79}***\\
- & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
-child.age & \num{-2.67}*** & \num{-2.64}*** & \num{-2.61}*** & \num{-2.60}***\\
- & (\num{0.47}) & (\num{0.51}) & (\num{0.48}) & (\num{0.49})\\
-child.is.girl & \num{-0.73} & \num{-0.45} & \num{-0.70} & \num{-0.59}\\
- & (\num{0.59}) & (\num{0.64}) & (\num{0.60}) & (\num{0.63})\\
-child.health & \num{-0.27} & \num{-0.22} & \num{-0.36} & \num{-0.25}\\
- & (\num{0.33}) & (\num{0.33}) & (\num{0.35}) & (\num{0.35})\\
-child.has.rural.hukou & \num{0.16} & \num{0.50} & \num{0.21} & \num{0.70}\\
- & (\num{0.62}) & (\num{0.63}) & (\num{0.67}) & (\num{0.69})\\
-child.number.of.sibling & \num{-1.00}* & \num{-1.07}* & \num{-0.88}* & \num{-0.98}*\\
- & (\num{0.41}) & (\num{0.44}) & (\num{0.43}) & (\num{0.44})\\
-child.went.to.preschool & \num{2.30}** & \num{1.95}* & \num{2.16}** & \num{2.07}*\\
- & (\num{0.78}) & (\num{0.86}) & (\num{0.81}) & (\num{0.86})\\
-child.had.skipped.grade & \num{-3.82} & \num{-3.81} & \num{-4.10} & \num{-2.95}\\
- & (\num{2.62}) & (\num{2.74}) & (\num{2.71}) & (\num{2.88})\\
-child.had.repeated.grade & \num{-1.49} & \num{-2.59}* & \num{-1.84} & \num{-1.39}\\
- & (\num{0.96}) & (\num{1.21}) & (\num{1.13}) & (\num{1.14})\\
-child.in.boarding.school & \num{1.34} & \num{1.20} & \num{1.22} & \num{0.82}\\
- & (\num{1.04}) & (\num{0.99}) & (\num{1.03}) & (\num{0.99})\\
-child.education.aspiration & \num{2.05}*** & \num{1.98}*** & \num{2.02}*** & \num{2.09}***\\
- & (\num{0.28}) & (\num{0.30}) & (\num{0.29}) & (\num{0.31})\\
-child.is.ethnic.minority & \num{1.56} & \num{1.60} & \num{1.08} & \num{1.23}\\
- & (\num{1.49}) & (\num{1.61}) & (\num{1.68}) & (\num{1.82})\\
-parent.expectation & \num{2.35}*** & \num{2.43}*** & \num{2.38}*** & \num{2.30}***\\
- & (\num{0.35}) & (\num{0.35}) & (\num{0.33}) & (\num{0.34})\\
-parent.has.white.collar.job & \num{0.90} & \num{0.39} & \num{0.89} & \num{0.72}\\
- & (\num{0.69}) & (\num{0.74}) & (\num{0.74}) & (\num{0.76})\\
-mother.education.level & \num{-0.03} & \num{0.02} & \num{-0.08} & \num{-0.15}\\
- & (\num{0.31}) & (\num{0.33}) & (\num{0.36}) & (\num{0.35})\\
-father.education.level & \num{0.14} & \num{0.31} & \num{0.16} & \num{0.38}\\
- & (\num{0.30}) & (\num{0.30}) & (\num{0.32}) & (\num{0.32})\\
-home.economic.resource & \num{-0.55} & \num{-0.60} & \num{-0.15} & \num{-0.16}\\
- & (\num{0.52}) & (\num{0.52}) & (\num{0.52}) & (\num{0.55})\\
-home.extracurricular.book & \num{-0.02} & \num{-0.11} & \num{-0.08} & \num{-0.04}\\
- & (\num{0.26}) & (\num{0.26}) & (\num{0.26}) & (\num{0.26})\\
-home.has.internet & \num{-0.51} & \num{-0.87} & \num{-0.80} & \num{-1.03}\\
- & (\num{0.61}) & (\num{0.70}) & (\num{0.67}) & (\num{0.70})\\
-\midrule
-Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
-R2 & \num{0.424} & \num{0.427} & \num{0.430} & \num{0.432}\\
-R2 Adj. & \num{0.405} & \num{0.406} & \num{0.410} & \num{0.410}\\
-FE: schids & X & X & X & X\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s academic exam score}
-\centering
-\begin{tabular}[t]{lcccc}
-\toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-1.26}* & \num{-2.11}* & \num{-0.91} & \num{-0.06}\\
- & (\num{0.52}) & (\num{0.83}) & (\num{0.68}) & (\num{0.75})\\
-Baseline.score & \num{-0.01} & \num{-0.01} & \num{-0.01} & \num{-0.01}\\
- & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
-child.age & \num{-0.47}* & \num{-0.43}* & \num{-0.47}* & \num{-0.41}\\
- & (\num{0.19}) & (\num{0.20}) & (\num{0.20}) & (\num{0.22})\\
-child.is.girl & \num{1.61}*** & \num{1.67}*** & \num{1.58}*** & \num{1.52}***\\
- & (\num{0.38}) & (\num{0.39}) & (\num{0.37}) & (\num{0.39})\\
-child.health & \num{0.36}** & \num{0.38}** & \num{0.25} & \num{0.28}\\
- & (\num{0.13}) & (\num{0.13}) & (\num{0.15}) & (\num{0.14})\\
-child.has.rural.hukou & \num{0.35} & \num{0.41} & \num{0.23} & \num{0.34}\\
- & (\num{0.40}) & (\num{0.39}) & (\num{0.39}) & (\num{0.40})\\
-child.number.of.sibling & \num{0.29} & \num{0.24} & \num{0.40} & \num{0.23}\\
- & (\num{0.19}) & (\num{0.20}) & (\num{0.22}) & (\num{0.22})\\
-child.went.to.preschool & \num{1.12}* & \num{1.33}** & \num{0.70} & \num{1.22}*\\
- & (\num{0.47}) & (\num{0.50}) & (\num{0.43}) & (\num{0.47})\\
-child.had.skipped.grade & \num{0.51} & \num{1.10} & \num{0.73} & \num{1.12}\\
- & (\num{1.79}) & (\num{1.57}) & (\num{2.01}) & (\num{1.62})\\
-child.had.repeated.grade & \num{-0.37} & \num{-0.06} & \num{-0.16} & \num{0.31}\\
- & (\num{0.72}) & (\num{0.81}) & (\num{0.82}) & (\num{0.88})\\
-child.in.boarding.school & \num{-0.37} & \num{-0.15} & \num{-0.27} & \num{-0.39}\\
- & (\num{0.52}) & (\num{0.49}) & (\num{0.47}) & (\num{0.53})\\
-child.education.aspiration & \num{0.78}*** & \num{0.88}*** & \num{0.80}*** & \num{0.80}**\\
- & (\num{0.21}) & (\num{0.25}) & (\num{0.21}) & (\num{0.25})\\
-child.is.ethnic.minority & \num{0.01} & \num{-0.09} & \num{-0.29} & \num{-0.48}\\
- & (\num{0.70}) & (\num{0.77}) & (\num{0.83}) & (\num{0.89})\\
-parent.expectation & \num{0.57}* & \num{0.52}* & \num{0.58}* & \num{0.58}*\\
- & (\num{0.24}) & (\num{0.24}) & (\num{0.28}) & (\num{0.27})\\
-parent.has.white.collar.job & \num{0.32} & \num{0.18} & \num{0.39} & \num{0.23}\\
- & (\num{0.39}) & (\num{0.43}) & (\num{0.42}) & (\num{0.44})\\
-mother.education.level & \num{-0.04} & \num{-0.05} & \num{0.01} & \num{0.08}\\
- & (\num{0.18}) & (\num{0.19}) & (\num{0.18}) & (\num{0.18})\\
-father.education.level & \num{0.18} & \num{0.25} & \num{0.21} & \num{0.17}\\
- & (\num{0.19}) & (\num{0.18}) & (\num{0.19}) & (\num{0.19})\\
-home.economic.resource & \num{-0.24} & \num{-0.05} & \num{-0.13} & \num{-0.09}\\
- & (\num{0.27}) & (\num{0.28}) & (\num{0.29}) & (\num{0.27})\\
-home.extracurricular.book & \num{-0.28} & \num{-0.42}* & \num{-0.30} & \num{-0.30}\\
- & (\num{0.17}) & (\num{0.16}) & (\num{0.16}) & (\num{0.15})\\
-home.has.internet & \num{-0.44} & \num{-0.50} & \num{-0.35} & \num{-0.35}\\
- & (\num{0.36}) & (\num{0.39}) & (\num{0.40}) & (\num{0.41})\\
-\midrule
-Num.Obs. & \num{4114} & \num{3726} & \num{3721} & \num{3597}\\
-R2 & \num{0.499} & \num{0.517} & \num{0.501} & \num{0.517}\\
-R2 Adj. & \num{0.482} & \num{0.500} & \num{0.483} & \num{0.499}\\
-FE: schids & X & X & X & X\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s cognitive test score, estimated with matching}
-\centering
-\begin{tabular}[t]{lcccc}
-\toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-2.51}*** & \num{-2.44}* & \num{-3.02}* & \num{-0.32}\\
- & (\num{0.72}) & (\num{1.10}) & (\num{1.18}) & (\num{1.63})\\
-Baseline.score & \num{-0.78}*** & \num{-0.77}*** & \num{-0.74}*** & \num{-0.79}***\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
-child.age & \num{-2.77}*** & \num{-1.37} & \num{-3.19}** & \num{-3.23}*\\
- & (\num{0.58}) & (\num{1.02}) & (\num{0.96}) & (\num{1.30})\\
-child.is.girl & \num{-1.73}* & \num{0.40} & \num{-1.44} & \num{-1.21}\\
- & (\num{0.67}) & (\num{1.16}) & (\num{1.22}) & (\num{1.67})\\
-child.health & \num{-0.26} & \num{0.90} & \num{-1.22} & \num{-0.93}\\
- & (\num{0.41}) & (\num{0.66}) & (\num{0.62}) & (\num{0.96})\\
-child.has.rural.hukou & \num{-0.33} & \num{-0.61} & \num{-1.68} & \num{-2.70}\\
- & (\num{0.84}) & (\num{1.22}) & (\num{1.24}) & (\num{2.16})\\
-child.number.of.sibling & \num{-0.76} & \num{-1.32} & \num{-0.52} & \num{0.41}\\
- & (\num{0.55}) & (\num{0.83}) & (\num{0.75}) & (\num{1.31})\\
-child.went.to.preschool & \num{1.97}* & \num{1.33} & \num{2.76}* & \num{6.17}***\\
- & (\num{0.88}) & (\num{1.43}) & (\num{1.30}) & (\num{1.74})\\
-child.had.skipped.grade & \num{-1.81} & \num{-1.39} & \num{-7.72}* & \num{2.21}\\
- & (\num{2.98}) & (\num{4.34}) & (\num{3.86}) & (\num{4.77})\\
-child.had.repeated.grade & \num{-1.02} & \num{-5.79}* & \num{-2.10} & \num{-1.29}\\
- & (\num{1.02}) & (\num{2.69}) & (\num{1.78}) & (\num{2.08})\\
-child.in.boarding.school & \num{1.60} & \num{1.74} & \num{1.70} & \num{-0.47}\\
- & (\num{1.30}) & (\num{1.85}) & (\num{2.08}) & (\num{2.50})\\
-child.education.aspiration & \num{1.97}*** & \num{0.84} & \num{1.48}*** & \num{2.08}*\\
- & (\num{0.38}) & (\num{0.61}) & (\num{0.41}) & (\num{0.88})\\
-child.is.ethnic.minority & \num{3.12}* & \num{-2.31} & \num{0.02} & \num{3.82}\\
- & (\num{1.34}) & (\num{2.56}) & (\num{4.54}) & (\num{4.98})\\
-parent.expectation & \num{2.19}*** & \num{3.56}*** & \num{2.36}*** & \num{2.11}*\\
- & (\num{0.46}) & (\num{0.77}) & (\num{0.54}) & (\num{0.96})\\
-parent.has.white.collar.job & \num{0.84} & \num{0.14} & \num{0.13} & \num{0.94}\\
- & (\num{0.95}) & (\num{1.28}) & (\num{1.41}) & (\num{2.98})\\
-mother.education.level & \num{0.26} & \num{-0.02} & \num{0.31} & \num{0.43}\\
- & (\num{0.38}) & (\num{0.70}) & (\num{0.81}) & (\num{1.03})\\
-father.education.level & \num{0.66} & \num{0.78} & \num{0.41} & \num{-0.29}\\
- & (\num{0.40}) & (\num{0.49}) & (\num{0.74}) & (\num{1.05})\\
-home.economic.resource & \num{-0.61} & \num{-2.22} & \num{0.00} & \num{0.72}\\
- & (\num{0.70}) & (\num{1.31}) & (\num{1.11}) & (\num{1.55})\\
-home.extracurricular.book & \num{-0.15} & \num{0.43} & \num{0.58} & \num{1.31}\\
- & (\num{0.38}) & (\num{0.57}) & (\num{0.50}) & (\num{0.74})\\
-home.has.internet & \num{-1.34} & \num{0.14} & \num{-1.52} & \num{-3.90}*\\
- & (\num{0.72}) & (\num{1.87}) & (\num{1.20}) & (\num{1.94})\\
-\midrule
-Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.445} & \num{0.490} & \num{0.469} & \num{0.554}\\
-R2 Adj. & \num{0.415} & \num{0.419} & \num{0.397} & \num{0.431}\\
-FE: schids & X & X & X & X\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{Parental migration’s effect on children’s academic exam score, estimated with matching}
-\centering
-\begin{tabular}[t]{lcccc}
-\toprule
-  & Any Parent & Only Mother & Only Father & Both Parents\\
-\midrule
-Migration & \num{-1.18}* & \num{-1.89}* & \num{-1.52} & \num{0.20}\\
- & (\num{0.55}) & (\num{0.73}) & (\num{0.81}) & (\num{0.87})\\
-Baseline.score & \num{0.06}* & \num{0.02} & \num{-0.04} & \num{-0.01}\\
- & (\num{0.03}) & (\num{0.04}) & (\num{0.04}) & (\num{0.04})\\
-child.age & \num{-0.15} & \num{-0.13} & \num{-0.67} & \num{-1.00}*\\
- & (\num{0.30}) & (\num{0.45}) & (\num{0.48}) & (\num{0.48})\\
-child.is.girl & \num{1.74}*** & \num{1.61}** & \num{2.45}*** & \num{0.49}\\
- & (\num{0.47}) & (\num{0.54}) & (\num{0.64}) & (\num{1.06})\\
-child.health & \num{0.60}** & \num{1.19}** & \num{0.51} & \num{0.65}\\
- & (\num{0.21}) & (\num{0.36}) & (\num{0.29}) & (\num{0.52})\\
-child.has.rural.hukou & \num{-0.11} & \num{0.63} & \num{-0.13} & \num{0.84}\\
- & (\num{0.50}) & (\num{0.73}) & (\num{0.69}) & (\num{1.02})\\
-child.number.of.sibling & \num{0.08} & \num{0.14} & \num{0.54} & \num{0.27}\\
- & (\num{0.25}) & (\num{0.30}) & (\num{0.37}) & (\num{0.65})\\
-child.went.to.preschool & \num{1.34}* & \num{2.36}* & \num{0.02} & \num{2.57}*\\
- & (\num{0.65}) & (\num{0.98}) & (\num{0.77}) & (\num{1.11})\\
-child.had.skipped.grade & \num{-0.13} & \num{-2.17} & \num{0.28} & \num{6.06}\\
- & (\num{2.74}) & (\num{2.63}) & (\num{2.84}) & (\num{4.65})\\
-child.had.repeated.grade & \num{-0.19} & \num{-0.64} & \num{-1.02} & \num{0.19}\\
- & (\num{0.85}) & (\num{1.52}) & (\num{1.06}) & (\num{1.09})\\
-child.in.boarding.school & \num{-0.28} & \num{-0.92} & \num{0.98} & \num{0.01}\\
- & (\num{0.72}) & (\num{1.54}) & (\num{0.90}) & (\num{1.63})\\
-child.education.aspiration & \num{0.44} & \num{1.18}** & \num{0.78}* & \num{0.01}\\
- & (\num{0.23}) & (\num{0.38}) & (\num{0.30}) & (\num{0.50})\\
-child.is.ethnic.minority & \num{0.23} & \num{-1.07} & \num{-0.35} & \num{-3.44}\\
- & (\num{0.88}) & (\num{0.98}) & (\num{1.82}) & (\num{2.15})\\
-parent.expectation & \num{0.67}** & \num{0.02} & \num{0.98}* & \num{0.55}\\
- & (\num{0.22}) & (\num{0.44}) & (\num{0.40}) & (\num{0.57})\\
-parent.has.white.collar.job & \num{0.37} & \num{-0.10} & \num{1.75}* & \num{-0.18}\\
- & (\num{0.41}) & (\num{0.60}) & (\num{0.79}) & (\num{1.28})\\
-mother.education.level & \num{-0.08} & \num{-0.06} & \num{-0.15} & \num{-0.03}\\
- & (\num{0.26}) & (\num{0.31}) & (\num{0.34}) & (\num{0.53})\\
-father.education.level & \num{0.25} & \num{0.24} & \num{-0.06} & \num{-0.01}\\
- & (\num{0.21}) & (\num{0.33}) & (\num{0.32}) & (\num{0.46})\\
-home.economic.resource & \num{0.03} & \num{0.21} & \num{-0.24} & \num{-1.04}\\
- & (\num{0.37}) & (\num{0.60}) & (\num{0.54}) & (\num{0.69})\\
-home.extracurricular.book & \num{-0.37} & \num{-0.67}* & \num{-0.08} & \num{0.33}\\
- & (\num{0.22}) & (\num{0.27}) & (\num{0.31}) & (\num{0.36})\\
-home.has.internet & \num{-1.03}* & \num{-0.50} & \num{-0.55} & \num{0.25}\\
- & (\num{0.43}) & (\num{0.71}) & (\num{0.68}) & (\num{1.11})\\
-\midrule
-Num.Obs. & \num{2540} & \num{1044} & \num{1024} & \num{523}\\
-R2 & \num{0.482} & \num{0.601} & \num{0.473} & \num{0.544}\\
-R2 Adj. & \num{0.454} & \num{0.545} & \num{0.402} & \num{0.419}\\
-FE: schids & X & X & X & X\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}3:1 optimal pair propensity score matching; exact matching by county}\\
-\end{tabular}
-\end{table}
-
-\newpage
-
-\hypertarget{figures}{%
-\section{Figures}\label{figures}}
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-cog-1} \caption{Changes in cognitive test score for newly left-behind students and non-left-behind students}\label{fig:v-plot-cog}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-ttl-1} \caption{Changes in academic exam score for newly left-behind students and non-left-behind students}\label{fig:v-plot-ttl}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-cog-1-1} \caption{Changes in cognitive test score by household migration arrangement}\label{fig:v-plot-cog-1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/v-plot-ttl-1-1} \caption{Changes in academic exam score by household migration arrangement}\label{fig:v-plot-ttl-1}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-any-1} \caption{Covariate balance before and after matching by any parent migration}\label{fig:cobal-any}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-mo-1} \caption{Covariate balance before and after matching by mother-only migration}\label{fig:cobal-mo}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-fa-1} \caption{Covariate balance before and after matching by father-only migration}\label{fig:cobal-fa}
-\end{figure}
-
-\begin{figure}
-\includegraphics[height=0.4\textheight]{MScThesisText_files/figure-latex/cobal-both-1} \caption{Covariate balance before and after matching by both parents migration}\label{fig:cobal-both}
-\end{figure}
-
 \end{document}
